### 2021-09-27 manuscript.Rmd
Add manuscript as dynamic document

---
title: 'Sampling Strategies in Decisions from Experience'
author: "Linus Hof, Thorsten Pachur, Veronika Zilker"
bibliography: sampling-strategies-in-dfe.bib
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
    number_sections: no
  pdf_document:
    toc: yes
csl: apa.csl
editor_options: 
  markdown: 
    wrap: sentence
---

```{r}
# load packages
pacman::p_load(repro,
               tidyverse,
               knitr, 
               viridis)
```

# Author Note

This document was created from the commit with the hash `r repro::current_hash()`.

- Add information on how to reproduce the project.
- Add contact.

# Abstract

A probability theoretic definition of prospects and a rough stochastic sampling model for decisions from experience is proposed.
It is demonstrated how the model can be used a) to explicate assumptions about the sampling and decision strategies that agents may apply and b) to derive predictions about function forms and parameter values that describe the resulting decision behavior. 
Synthetic choice data is simulated and modeled in cumulative prospect theory to test these predictions.

# Introduction

...

## Sampling in Decisions from Experience

In research on the decision theory, a standard paradigm is the choice between at least two (monetary) prospects.
Let a prospect be a probability space $(\Omega, \mathscr{F}, P)$.
$\Omega$ is the sample space

$$\begin{equation}
\Omega = \{\omega_1, ..., \omega_n\}
\end{equation}$$

containing a finite set of possible outcomes $\omega$, monetary gains and/or losses respectively. 
$\mathscr{F}$ is the set of all possible subsets of $\Omega$:

$$\begin{equation}
\mathscr{F} = \{A_1, A_2, ...\} = \mathscr{P}(\Omega) 
\; .
\end{equation}$$

$P$ is a probability mass function

$$\begin{equation}
P: \mathscr{F} \mapsto [0,1] 
\end{equation}$$

that assigns each outcome $\omega$ a probability $0 < p(\omega) \leq 1$ with $P(\Omega) = 1$ [ @kolmogorovFoundationsTheoryProbability1950, pp. 2-3].

In such a choice paradigm, agents are asked to evaluate the prospects and build a preference for either one of them. 
It is common to make a distinction between two variants of this evaluation process [cf. @hertwigDescriptionexperienceGapRisky2009]. 
For decisions from description (DfD), agents are provided a full symbolic description of the prospects.
For decisions from experience [DfE; e.g., @hertwigDecisionsExperienceEffect2004], prospects are not described but must be explored by the means of sampling.

To provide a formal definition of sampling in risky choice, we make use of the mathematical concept of a random variable and start by referring to a prospect as *"risky"* in the case where $p(\omega) \neq 1$ for all $\omega \in \Omega$.
Here, risky describes the fact that if agents would choose a prospect and any of its outcomes in $\Omega$ must occur, none of these outcomes will occur with certainty. 
It is acceptable to speak of the occurrence of $\omega$ as a realization of a random variable $X$ defined on a prospect iff the following conditions (1) and (2) are met:

(1) $X$ is a measurable function $$\begin{equation} X: (\Omega, \mathscr{F})  \mapsto (\Omega', \mathscr{F'}) \; , \end{equation}$$ where $\Omega'$ is a set of real numbered values $X$ can take and $\mathscr{F'}$ is a set of subsets of $\Omega'$. I.e., $\Omega$ maps into $\Omega'$ such that correspondingly each subset $A' \in \mathscr{F'}$ has a pre-image $X^{-1}A' \in \mathscr{F}$, which is the set $\{\omega \in \Omega: X(\omega) \in A'\}$ [@kolmogorovFoundationsTheoryProbability1950, p. 21].

(2) The mapping is such that $X(\omega) = x \equiv \omega$.

In (2), $x \equiv \omega$ means that the realization of a random variable $X(\omega) = x$ is numerically equivalent to its pre-image $\omega$.  
Given conditions (1) and (2), we denote any observation of $\omega$ as a *"single sample"*, or realization, of a random variable defined on a prospect and the act of generating a sequence of single samples in discrete time as *"sequential sampling"*. 
Note that, since random variables defined on the same prospect are independent and identically distributed (iid), the weak law of the large number applies to the relative frequency of occurrence of an outcome $\omega$ in a sequence of single samples originating from the same prospect [cf. @bernoulliArsConjectandiOpus1713].
Thus, long sample sequences in principle allow to obtain the same information about a prospect by sampling as by symbolic description.

Consider now a choice between prospects $1, ..., k$.
To construct a stochastic sampling model for DfE, we assume that agents base their decision on the information related to these prospects and define a decision variable as a function of the latter:

$$\begin{equation}
D:= f((\Omega, \mathscr{F}, P)_1, ..., (\Omega, \mathscr{F}, P)_k)
\;.
\end{equation}$$

Now, since in DfE no symbolic descriptions of the prospects are provided, the model must be restricted to the case where decisions are based on sequences of single samples originating from the respective prospects:

$$\begin{equation}
D := f(X_{i1}, ..., X_{ik}) 
\; ,
\end{equation}$$

where $i = 1, ..., N$ denotes a sequence of length $N$ of random variables that are iid.

Concerning the form of $f$ and the measures it utilizes, it is quite proper to say that they reflect our assumptions about the exact kind of information agents process and the way they do and that these choices should be informed by psychological theory and empirical protocols. 
Taking the case of different sampling and decision strategies previously assumed to play a role in DfE, the following section demonstrates how such assumptions can be explicated in a stochastic model that builds on the sampling approach outlined so far.

## A Stochastic Sampling Model Capturing Differences in Sampling and Decision Strategies

Hills and Hertwig [-@hillsInformationSearchDecisions2010] discussed a potential link between sampling and decision strategies in DfE. 
Specifically, the authors suppose that if single samples originating from different prospects are generated in direct succession (piecewise sampling), the evaluation of prospects is based on multiple ordinal comparisons of single samples (round-wise decisions).
In contrast, if single samples originating from the same prospect are generated in direct succession (comprehensive sampling), it is supposed that the evaluation of prospects is based on a single ordinal comparison of long sequences of single samples (summary decisions) [@hillsInformationSearchDecisions2010, Figure 1 for a graphical summary].

We now consider choices between two prospects and the assumptions of Hills and Hertwig [-@hillsInformationSearchDecisions2010] in more detail to build the respective stochastic sampling model for DfE.

Let $X$ and $Y$ be random variables defined on the prospects $(\Omega, \mathscr{F}, P)_X$ and $(\Omega, \mathscr{F}, P)_Y$.

Hills and Hertwig [-@hillsInformationSearchDecisions2010] suggest that any two sample sequences $X_i$ and $Y_i$ are compared by their means. 
Let thus $C = \mathbb{R}$ be the set of all possible outcomes of such a mean comparison for given sequence lengths $N_X$ and $N_Y$ and

$$\begin{equation}
\mathscr{C} = \left\{ \{c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\}, \{ c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} \leq 0\}
\right\}
\end{equation}$$

be a set of subsets of $C$, indicating that comparisons of prospects on the ordinal (rather than on the metric) scale are of primary interest. 
The outcome of such an ordinal comparison can be regarded as evidence for or against a prospect and the number of wins over a series of independent ordinal comparisons as accumulated evidence. 
To integrate the concept of evidence accumulation into the current model, we let $D$ be a measurable function that maps the possible outcomes of a mean comparison in $C$ onto a measure space $C' = \{0,1\}$, with $0$ ($1$) indicating a lost (won) comparison:

$$\begin{equation}
D(c \in C) = 
  \begin{cases}
    1 & \text{for} & \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0) \in \mathscr{C} \} \\
    0 & \text{else}. 
  \end{cases} 
\end{equation}$$

It can be shown that for fixed sequence lengths $N_X$ and $N_Y$, a sequence $D_i = D_1, ..., D_n$ is a Bernoulli process following the binomial distribution

$$\begin{equation}
D \sim B\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right) \; ,
\end{equation}$$

where $p$ is the probability of $X$ winning a single mean comparison and $n$ is the number of comparisons (see [Appendix]).
However, although $p$ can in principle be determined, it becomes intractable with increasing elements in $\Omega$ and growing sequence lengths.

## Predicting Choice Behavior in DfE

Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed the two different sampling strategies in combination with the respective decision strategies, i.e., piecewise sampling and round-wise comparison vs. comprehensive sampling and summary comparison, as an explanation for different choice patterns in DfE. 
How does the current version of the SSM support this proposition? 
Given prospects $X$ and $Y$, the sample spaces $S = \left\{\frac{\overline{X}_{N_X}} {\overline{Y}_{N_Y}}\right\}^{\mathbb{N}}$ can be varied by changes on three parameters, i.e., the number of comparisons $\mathbb{N}$ and the sample sizes $N_X$ and $N_Y$ on which these comparisons are based.
First, only considering the pure cases formulated by the above authors, the following restrictions are put the parameters:

$$\begin{equation}
\mathbb{N}
  =
  \begin{cases}
    1 & \text{if} & \text{Summary} \\ 
    \geq 1 & \text{if} & \text{Round-wise}  
  \end{cases}\\
\end{equation}$$

and

$$\begin{equation}
N_X \, \text{and} \, N_Y
  =
  \begin{cases}
    \geq 1 & \text{if} & \text{Summary} \\ 
    1 & \text{if} & \text{Round-wise}  
  \end{cases}\\
\end{equation}$$

For the summary strategy, the following prediction is obtained:

Given that

$$\begin{equation}
P\left(\lim_{N_X \to \infty} \overline{X}_{N_X} = E(X) \right) = 
P\left(\lim_{N_Y \to \infty} \overline{Y}_{N_Y} = E(Y) \right) = 
1 \; ,
\end{equation}$$

we obtain that

$$\begin{equation}
\left(
    \frac{\overline{X}_{N_X}} {\overline{Y}_{N_Y}}
\right)
\in S : 
P\left(\lim_{N_X \to \infty} \lim_{N_Y \to \infty} \frac{\overline{X}_{N_X}} {\overline{Y}_{N_Y}} = 
\frac{E(X)} {E(Y)}
\right ) =
1 \; ,
\end{equation}$$

I.e., for the summary strategy, we assume that for increasing sample sizes $N_X$ and $N_Y$, the prospect with the larger expected value is chosen almost surely.

For the round-wise strategy, the following prediction is obtained:

Given that $N_X$ and $N_Y$ are set to 1, $D$ follows the binomial distribution

$$\begin{equation}
B(k \, | \, p_X, \mathbb{N}) \; ,
\end{equation}$$

where $p$ is the probability that a single sample of prospect $X$ is larger than a single sample of prospect $Y$, $\mathbb{N}$ is the number of comparisons and $k$ is the number of times $x \in X$ is larger than $y \in Y$.

*Proof.*

For $N_X = N_Y = 1$, the sample space is

$$\begin{equation}
\left\{\frac{\overline{X}_{N_X = 1}} {\overline{Y}_{N_Y = 1}} \right\}^{\mathbb{N}} =
\left\{\frac{x_i \in \Omega'_X} {y_j \in \Omega'_Y}\right\}^{\mathbb{N}}
\end{equation}$$

# Method

## Test set

Under each condition, i.e., strategy-parameter combinations, all gambles are played by 100 synthetic agents.
We test a set of gambles, in which one of the prospects contains a safe outcome and the other two risky outcomes (*safe-risky gambles*).
Therefore, 60 gambles from an initial set of 10,000 are sampled.
Both outcomes and probabilities are drawn from uniform distributions, ranging from 0 to 20 for outcomes and from .01 to .99 for probabilities of the lower risky outcomes $p_{low}$.
The probabilities of the higher risky outcomes are $1-p_{low}$, respectively.
To omit dominant prospects, safe outcomes fall between both risky outcomes.
The table below contains the test set of 60 gambles.
Sampling of gambles was stratified, randomly drawing an equal number of 20 gambles with no, an attractive, and an unattractive rare outcome.
Risky outcomes are considered *"rare"* if their probability is $p < .2$ and *"attractive"* (*"unattractive"*) if they are higher (lower) than the safe outcome.

```{r message=FALSE}
gambles <- read_csv("data/gambles/sr_subset.csv")
gambles %>% kable()
```

## Model Parameters

**Switching probability** $s$ is the probability with which agents draw the following single sample from the prospect they did not get their most recent single sample from.
$s$ is varied between .1 to 1 in increments of .1.

The **boundary type** is either the minimum value any prospect's sample statistic must reach (absolute) or the minimum value for the difference of these statistics (relative).
Sample statistics are sums over outcomes (comprehensive strategy) and sums over wins (piecewise strategy), respectively.

For comprehensive integration, the **boundary value** $a$ is varied between 15 to 75 in increments of 15.
For piecewise integration $a$ is varied between 1 to 5 in increments of 1.

```{r message=FALSE}
# read choice data 
cols <- list(.default = col_double(),
             strategy = col_factor(),
             boundary = col_factor(),
             gamble = col_factor(),
             rare = col_factor(),
             agent = col_factor(),
             choice = col_factor())
choices <- read_csv("data/choices/choices.csv", col_types = cols)
```

In sum, 2 (strategies) x 60 (gambles) x 100 (agents) x 100 (parameter combinations) = `r nrow(choices)` choices are simulated.

# Results

Because we are not interested in deviations from normative choice due to sampling artifacts (e.g., ceiling effects produced by low boundaries), we remove trials in which only one prospect was attended.
In addition, we use relative frequencies of sampled outcomes rather than 'a priori' probabilities to compare actual against normative choice behavior.

```{r}
# remove choices where prospects were not attended
choices <- choices %>%
  filter(!(is.na(a_ev_exp) | is.na(b_ev_exp)))
```

```{r eval = FALSE}
# remove choices where not all outcomes were sampled
choices <- choices %>% 
  filter(!(is.na(a_ev_exp) | is.na(b_ev_exp) | a_p1_exp == 0 | a_p2_exp == 0))
```

Removing the respective trials, we are left with `r nrow(choices)` choices.

## Sample Size

```{r message=FALSE}
samples <- choices %>% 
  group_by(strategy, s, boundary, a) %>% 
  summarise(n_med = median(n_sample))
samples_piecewise <- samples %>% filter(strategy == "piecewise")
samples_comprehensive <- samples %>% filter(strategy == "comprehensive")
```

The median sample sizes generated by different parameter combinations ranged from `r min(samples_piecewise$n_med)` to `r max(samples_piecewise$n_med)` for piecewise integration and `r min(samples_comprehensive$n_med)` to `r max(samples_comprehensive$n_med)` for comprehensive integration.

### Boundary type and boundary value (a)

As evidence is accumulated sequentially, relative boundaries and large boundary values naturally lead to larger sample sizes, irrespective of the integration strategy.

```{r message=FALSE}
group_med <- samples_piecewise %>%
  group_by(boundary, a) %>% 
  summarise(group_med = median(n_med)) # to get the median across all s values

samples_piecewise %>%
  ggplot(aes(a, n_med, color = a)) + 
  geom_jitter(alpha = .5, size = 2) +
  geom_point(data = group_med, aes(y = group_med), size = 3) +
  facet_wrap(~boundary) + 
  scale_color_viridis() + 
  labs(title = "Piecewise Integration",
       x ="a", 
       y="Sample Size", 
       col="a") + 
  theme_minimal()
```

```{r message=FALSE}
group_med <- samples_comprehensive %>%
  group_by(boundary, a) %>% 
  summarise(group_med = median(n_med))

samples_comprehensive %>%
  ggplot(aes(a, n_med, color = a)) + 
  geom_jitter(alpha = .5, size = 2) +
  geom_point(data = group_med, aes(y = group_med), size = 3) +
  facet_wrap(~boundary) + 
  scale_color_viridis() + 
  labs(title = "Comprehensive Integration",
       x ="a", 
       y="Sample Size", 
       col="a") + 
  theme_minimal()
```

### Switching probability (s)

For piecewise integration, there is an inverse relationship between switching probability and sample size.
I.e., the lower s, the less frequent prospects are compared and thus, boundaries are only approached with larger sample sizes.
This effect is particularly pronounced for low probabilities such that the increase in sample size accelerates as switching probability decreases.

```{r message=FALSE}
group_med <- samples_piecewise %>%
  group_by(boundary, s) %>% 
  summarise(group_med = median(n_med)) # to get the median across all a values

samples_piecewise %>%
  ggplot(aes(s, n_med, color = s)) + 
  geom_jitter(alpha = .5, size = 2) +
  geom_point(data = group_med, aes(y = group_med), size = 3) +
  facet_wrap(~boundary) + 
  scale_color_viridis() + 
  labs(title = "Piecewise Integration",
       x ="s", 
       y="Sample Size", 
       col="s") + 
  theme_minimal()
```

For comprehensive integration, boundary types differ in the effects of switching probability.
For absolute boundaries, switching probability has no apparent effect on sample size as the distance of a given prospect to its absolute boundary is not changed by switching to (and sampling from) the other prospect.
For relative boundaries, however, samples sizes increase with switching probability.

```{r message=FALSE}
group_med <- samples_comprehensive %>%
  group_by(boundary, s) %>% 
  summarise(group_med = median(n_med)) # to get the median across all a values

samples_comprehensive %>%
  ggplot(aes(s, n_med, color = s)) + 
  geom_jitter(alpha = .5, size = 2) +
  geom_point(data = group_med, aes(y = group_med), size = 3) +
  facet_wrap(~boundary) + 
  scale_color_viridis() + 
  labs(title = "Comprehensive Integration",
       x ="s",
       y = "Sample Size", 
       col="s") + 
  theme_minimal()
```

## Choice Behavior

Below, in extension to Hills and Hertwig [-@hillsInformationSearchDecisions2010], the interplay of integration strategies, gamble features, and model parameters in their effects on choice behavior in general and their contribution to underweighting of rare events in particular is investigated.
We apply two definitions of underweighting of rare events: Considering false response rates, we define underweighting such that the rarity of an attractive (unattractive) outcome leads to choose the safe (risky) prospect although the risky (safe) prospect has a higher expected value.

```{r message=FALSE}
fr_rates <- choices %>% 
  mutate(ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2), 
         norm = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) %>% 
  filter(!is.na(norm)) %>% # exclude trials with normative indifferent options
  group_by(strategy, s, boundary, a, rare, norm, choice) %>% # group correct and incorrect responses
  summarise(n = n()) %>% # absolute numbers 
  mutate(rate = round(n/sum(n), 2), # response rates 
         type = case_when(norm == "A" & choice == "B" ~ "false safe", norm == "B" & choice == "A" ~ "false risky")) %>% 
  filter(!is.na(type)) # remove correct responses
```

Considering the parameters of Prelec's [-@prelecProbabilityWeightingFunction1998] implementation of the weighting function [CPT; cf. @tverskyAdvancesProspectTheory1992], underweighting is reflected by decisions weights estimated to be smaller than the corresponding objective probabilities.

### False Response Rates

```{r message=FALSE}
fr_rates_piecewise <- fr_rates %>% filter(strategy == "piecewise")
fr_rates_comprehensive <- fr_rates %>% filter(strategy == "comprehensive")
```

The false response rates generated by different parameter combinations ranged from `r min(fr_rates_piecewise$rate)` to `r max(fr_rates_piecewise$rate)` for piecewise integration and from `r min(fr_rates_comprehensive$rate)` to `r max(fr_rates_comprehensive$rate)` for comprehensive integration.
However, false response rates vary considerably as a function of rare events, indicating that their presence and attractiveness are large determinants of false response rates.

```{r message=FALSE}
fr_rates %>% 
  group_by(strategy, boundary, rare) %>% 
  summarise(min = min(rate),
            max = max(rate)) %>% 
  kable()
```

The heatmaps below show the false response rates for all strategy-parameter combinations.
Consistent with our - somewhat rough - definition of underweighting, the rate of false risky responses is generally higher, if the unattractive outcome of the risky prospect is rare (top panel).
Conversely, if the attractive outcome of the risky prospect is rare, the rate of false safe responses is generally higher (bottom panel).
As indicated by the larger range of false response rates, the effects of rare events are considerably larger for piecewise integration.

```{r message=FALSE}
fr_rates %>% 
  filter(strategy == "piecewise", boundary == "absolute") %>% 
  ggplot(aes(a, s, fill = rate)) + 
  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
  geom_tile(colour="white", size=0.25) + 
  scale_x_continuous(expand=c(0,0), breaks = seq(1, 5, 1)) +
  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
  scale_fill_viridis() + 
  labs(title = "Piecewise Integration | Absolute Boundary",
       x = "a", 
       y= "s", 
       fill = "% False Responses") + 
  theme_minimal() 
```

```{r message=FALSE}
fr_rates %>% 
  filter(strategy == "piecewise", boundary == "relative") %>% 
  ggplot(aes(a, s, fill = rate)) + 
  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
  geom_tile(colour="white", size=0.25) + 
  scale_x_continuous(expand=c(0,0), breaks = seq(1, 5, 1)) +
  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
  scale_fill_viridis() + 
  labs(title = "Piecewise Integration | Relative Boundary",
       x = "a", 
       y= "s", 
       fill = "% False Responses") + 
  theme_minimal() 
```

```{r message=FALSE}
fr_rates %>% 
  filter(strategy == "comprehensive", boundary == "absolute") %>% 
  ggplot(aes(a, s, fill = rate)) + 
  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
  geom_tile(colour="white", size=0.25) + 
  scale_x_continuous(expand=c(0,0), breaks = seq(15, 75, 15)) +
  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
  scale_fill_viridis() + 
  labs(title = "Comprehensive Integration | Absolute Boundary",
       x = "a", 
       y= "s", 
       fill = "% False Responses") + 
  theme_minimal() 
```

```{r message=FALSE}
fr_rates %>% 
  filter(strategy == "comprehensive", boundary == "relative") %>% 
  ggplot(aes(a, s, fill = rate)) + 
  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
  geom_tile(colour="white", size=0.25) + 
  scale_x_continuous(expand=c(0,0), breaks = seq(15, 75, 15)) +
  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
  scale_fill_viridis() + 
  labs(title = "Comprehensive Integration | Relative Boundary",
       x = "a", 
       y= "s", 
       fill = "% False Responses") + 
  theme_minimal() 
```

#### Switching Probability (s) and Boundary Value (a)

As for both piecewise and comprehensive integration the differences between boundary types are rather minor and of magnitude than of qualitative pattern, the remaining analyses of false response rates are summarized across absolute and relative boundaries.

Below, the $s$ and $a$ parameter are considered as additional sources of variation in the false response pattern above and beyond the interplay of integration strategies and the rarity and attractiveness of outcomes.

```{r message=FALSE}
fr_rates %>% 
  filter(strategy == "piecewise") %>% 
  ggplot(aes(s, rate, color = a)) + 
  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
  geom_jitter(size = 2) + 
  scale_x_continuous(breaks = seq(0, 1, .1)) +
  scale_y_continuous(breaks = seq(0, 1, .1)) +
  scale_color_viridis() + 
  labs(title = "Piecewise Integration",
       x = "s", 
       y= "% False Responses", 
       color = "a") + 
  theme_minimal() 
```

```{r message=FALSE}
fr_rates %>% 
  filter(strategy == "comprehensive") %>% 
  ggplot(aes(s, rate, color = a)) + 
  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
  geom_jitter(size = 2) + 
  scale_x_continuous(breaks = seq(0, 1, .1)) +
  scale_y_continuous(breaks = seq(0, 1, .1)) +
  scale_color_viridis() + 
  labs(title = "Comprehensive Integration",
       x = "s", 
       y= "% False Responses", 
       color = "a") + 
  theme_minimal() 
```

For piecewise integration, switching probability is naturally related to the size of the samples on which the round-wise comparisons of prospects are based on, with low values of $s$ indicating large samples and vice versa.
Accordingly, switching probability is positively related to false response rates.
I.e., the larger the switching probability, the smaller the round-wise sample size and the probability of experiencing a rare event within a given round.
Because round-wise comparisons are independent of each other and binomial distributions within a given round are skewed for small samples and outcome probabilities [@kolmogorovFoundationsTheoryProbability1950], increasing boundary values do not reverse but rather amplify this relation.

For comprehensive integration, switching probability is negatively related to false response rates, i.e., an increase in $s$ is associated with decreasing false response rates.
This relation, however, may be the result of an artificial interaction between the $s$ and $a$ parameter.
Precisely, in the current algorithmic implementation of sampling with a comprehensive integration mechanism, decreasing switching probabilities cause comparisons of prospects based on increasingly unequal sample sizes immediately after switching prospects.
Consequentially, reaching (low) boundaries is rather a function of switching probability and associated sample sizes than of actual evidence for a given prospect over the other.

### Cumulative Prospect Theory

In the following, we examine the possible relations between the parameters of the *choice-generating* sampling models and the *choice-describing* cumulative prospect theory.

For each distinct strategy-parameter combination, we ran 20 chains of 40,000 iterations each, after a warm-up period of 1000 samples.
To reduce potential autocorrelation during the sampling process, we only kept every 20th sample (thinning).

```{r}
# read CPT data
cols <- list(.default = col_double(),
             strategy = col_factor(),
             boundary = col_factor(),
             parameter = col_factor())
estimates <- read_csv("data/estimates/estimates_cpt_pooled_goldstein-einhorn-87.csv", col_types = cols)
```

#### Convergence

```{r}
gel_92 <- max(estimates$Rhat) # get largest scale reduction factor (Gelman & Rubin, 1992) 
```

The potential scale reduction factor $\hat{R}$ was $n \leq$ `r round(gel_92, 3)` for all estimates, indicating good convergence.

#### Piecewise Integration

```{r}
# generate subset of all strategy-parameter combinations (rows) and their parameters (columns)
curves_cpt <- estimates %>% 
  select(strategy, s, boundary, a, parameter, mean) %>% 
  pivot_wider(names_from = parameter, values_from = mean)
```

##### Weighting function w(p)

We start by plotting the weighting curves for all parameter combinations under piecewise integration.

```{r}

cpt_curves_piecewise <- curves_cpt %>% 
  filter(strategy == "piecewise") %>% 
  expand_grid(p = seq(0, 1, .1)) %>% # add vector of objective probabilities
  mutate(w = round(exp(-delta*(-log(p))^gamma), 2)) # compute decision weights (cf. Prelec, 1998)

# all strategy-parameter combinations

cpt_curves_piecewise %>% 
  ggplot(aes(p, w)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  labs(title = "Piecewise Integration: Weighting functions",
       x = "p", 
       y= "w(p)") + 
  theme_minimal() 
```

```{r}
cpt_curves_piecewise %>% 
  ggplot(aes(p, w)) + 
  geom_path() +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  facet_wrap(~a) + 
  labs(title = "Piecewise Integration: Weighting functions",
       x = "p",
       y= "w(p)",
       color = "Switching Probability") + 
  scale_color_viridis() +
  theme_minimal() 
```

```{r}
cpt_curves_piecewise %>% 
  ggplot(aes(p, w, color = s)) + 
  geom_path() +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  labs(title = "Piecewise Integration: Weighting functions",
       x = "p", 
       y= "w(p)", 
       color = "Switching Probability") + 
  scale_color_viridis() +
  theme_minimal() 
```

```{r}
cpt_curves_piecewise %>% 
  ggplot(aes(p, w, color = s)) + 
  geom_path() +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  facet_wrap(~a) + 
  labs(title = "Piecewise Integration: Weighting functions",
       x = "p",
       y= "w(p)",
       color = "Switching Probability") + 
  scale_color_viridis() +
  theme_minimal() 
```

##### Value function v(x)

```{r}

cpt_curves_piecewise <- curves_cpt %>% 
  filter(strategy == "piecewise") %>% 
  expand_grid(x = seq(0, 20, 2)) %>% # add vector of objective outcomes
  mutate(v = round(x^alpha, 2)) # compute decision weights (cf. Prelec, 1998)

# all strategy-parameter combinations

cpt_curves_piecewise %>% 
  ggplot(aes(x, v)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  labs(title = "Piecewise Integration: Value functions",
       x = "p", 
       y= "w(p)") + 
  theme_minimal() 
```

```{r}
cpt_curves_piecewise %>% 
  ggplot(aes(x, v, color = s)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  labs(title = "Piecewise Integration: Value functions",
       x = "p", 
       y= "w(p)") + 
  scale_color_viridis() + 
  theme_minimal() 
```

```{r}
cpt_curves_piecewise %>% 
  ggplot(aes(x, v, color = s)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  facet_wrap(~a) + 
  labs(title = "Piecewise Integration: Value functions",
       x = "p", 
       y= "w(p)") + 
  scale_color_viridis() + 
  theme_minimal() 
```

#### Comprehensive Integration

##### Weighting function w(p)

We start by plotting the weighting curves for all parameter combinations under piecewise integration.

```{r}

cpt_curves_comprehensive <- curves_cpt %>% 
  filter(strategy == "comprehensive") %>% 
  expand_grid(p = seq(0, 1, .1)) %>% # add vector of objective probabilities
  mutate(w = round(exp(-delta*(-log(p))^gamma), 2)) # compute decision weights (cf. Prelec, 1998)

# all strategy-parameter combinations

cpt_curves_comprehensive %>% 
  ggplot(aes(p, w)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  labs(title = "Comprehensive Integration: Weighting functions",
       x = "p", 
       y= "w(p)") + 
  theme_minimal() 
```

```{r}
cpt_curves_comprehensive %>% 
  ggplot(aes(p, w)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  labs(title = "Comprehensive Integration: Weighting functions",
       x = "p", 
       y= "w(p)") + 
  facet_wrap(~a) + 
  theme_minimal() 
```

```{r}
cpt_curves_comprehensive %>% 
  ggplot(aes(p, w, color = s)) + 
  geom_path() +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  labs(title = "Comprehensive Integration: Weighting functions",
       x = "p", 
       y= "w(p)", 
       color = "Switching Probability") + 
  scale_color_viridis() +
  theme_minimal() 
```

```{r}
cpt_curves_comprehensive %>% 
  ggplot(aes(p, w, color = s)) + 
  geom_path() +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  facet_wrap(~a) + 
  labs(title = "Comprehensive Integration: Weighting functions",
       x = "p",
       y= "w(p)",
       color = "Switching Probability") + 
  scale_color_viridis() +
  theme_minimal() 
```

```{r}
cpt_curves_comprehensive %>% 
  filter(s >= .7) %>% 
  ggplot(aes(p, w, color = s)) + 
  geom_path() +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  facet_wrap(~a) + 
  labs(title = "Comprehensive Integration: Weighting functions",
       x = "p",
       y= "w(p)",
       color = "Switching Probability") + 
  scale_color_viridis() +
  theme_minimal() 
```

##### Value function v(x)

```{r}

cpt_curves_comprehensive <- curves_cpt %>% 
  filter(strategy == "comprehensive") %>% 
  expand_grid(x = seq(0, 20, 2)) %>% # add vector of objective outcomes
  mutate(v = round(x^alpha, 2)) # compute decision weights (cf. Prelec, 1998)

# all strategy-parameter combinations

cpt_curves_comprehensive %>% 
  ggplot(aes(x, v)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  labs(title = "Comprehensive Integration: Value functions",
       x = "p", 
       y= "w(p)") + 
  theme_minimal() 
```

```{r}
cpt_curves_comprehensive %>% 
  ggplot(aes(x, v)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  facet_wrap(~a) + 
  labs(title = "Comprehensive Integration: Value functions",
       x = "p", 
       y= "w(p)") + 
  theme_minimal() 
```

```{r}
cpt_curves_comprehensive %>% 
  ggplot(aes(x, v, color = s)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  labs(title = "Comprehensive Integration: Value functions",
       x = "p", 
       y= "w(p)") + 
  scale_color_viridis() + 
  theme_minimal() 
```

```{r}
cpt_curves_comprehensive %>% 
  ggplot(aes(x, v, color = s)) + 
  geom_path(size = .5) +
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  facet_wrap(~a) + 
  labs(title = "Comprehensive Integration: Value functions",
       x = "p", 
       y= "w(p)") + 
  scale_color_viridis() + 
  theme_minimal() 
```

# Discussion

# Conclusion

# Appendix

Let

$$\begin{equation}
X_1, ..., X_{N_X}
\end{equation}$$

and

$$\begin{equation}
Y_1, ..., Y_{N_Y} 
\end{equation}$$

be sequences of random variables that are iid.
Then

$$\begin{equation}
P\left(\frac{\overline{X}_{N_X}}{\overline{Y}_{N_Y}} > 0 \right) = 
P\left(\frac{\frac{1}{N_X}\sum\limits_{n=1}^{N_X} (X(\omega_i) = A'_X \in \mathscr{F'}_X)_n} 
{\frac{1}{N_Y}\sum\limits_{m=1}^{N_Y} (Y(\omega_j) = A'_Y \in \mathscr{F'}_Y)_m} > 0 \right)
\end{equation}$$

is the probability that the quotient of the mean of both sequences takes on a value larger $0$.
Given the sample sizes $N_X = N_Y = 1$, the equation reduces to

$$\begin{equation}
P\left(\frac{X(\omega_i \in \Omega_X) = A'_X \in \mathscr{F'}_X}{Y(\omega_j \in \Omega_Y) = A'_Y \in \mathscr{F'}_Y} > 0 \right) \; ,
\end{equation}$$

which is the sum across all joint probabilities $p(\omega_i \cap \omega_j)$ for which the above inequation holds:.

$$\begin{equation}
D:= 
  f
  \left(
    \frac{\overline{X}_{N_X}} {\overline{Y}_{N_Y}}
  \right) 
  =
  \begin{cases}
    1 & \text{if} & \frac{\overline{X}_{N_X}}{\overline{Y}_{N_Y}} > 0 \in \mathscr{D} \\
    0 & \text{else}. 
  \end{cases} 
\end{equation}$$

# References

### 2021-09-27 R/prepare_choice_data.R
Add R scripts for generating and preparing simulation data

@@ -1,0 +1,73 @@
+pacman::p_load(tidyverse, digest)
+
+# load simulation data
+cols <- list(.default = col_double(),
+             boundary = col_factor(),
+             gamble = col_factor(),
+             agent = col_factor(),
+             rare = col_factor(),
+             attended = col_factor(),
+             choice = col_factor())
+sim_piecewise <- read_csv("data/simulation/sim_piecewise.csv", col_types = cols)
+sim_comprehensive <- read_csv("data/simulation/sim_comprehensive.csv", col_types = cols)
+
+# piecewise strategy
+
+## use hash to validate simulation data
+
+hash_piecewise <- digest(sim_piecewise, "md5")
+if(hash_piecewise != "295e1a7b23402dd50a1dae5a54141f78"){
+  warning("Mismatch between original and current data!\nCurrent hash is:\n    '", hash_piecewise, "'")
+}
+
+## transform data to obtain trial summaries
+
+choices_piecewise <- sim_piecewise %>%
+  group_by(s, boundary, a, gamble, agent) %>% # group by trials
+  mutate(n_sample = n(), # total number of single samples
+         n_a = n_sample - sum(is.na(A)), # number of single samples drawn from risky option
+         a_p2_exp = round(sum(if_else(A == a_o2, 1, 0), na.rm = TRUE)/n_a, 2), # experienced probability of higher risky outcome
+         a_p1_exp = round(1 - a_p2_exp, 2), # experienced probability of lower risky outcome
+         a_ev_exp = round(mean(A, na.rm = TRUE), 2), # experienced mean A
+         b_ev_exp = round(mean(B, na.rm = TRUE), 2)) %>%  # experienced mean B
+  ungroup() %>%
+  filter(!is.na(choice)) %>% # discard single samples
+
+  ## tidy data
+
+  mutate(strategy = "piecewise",
+         s = 1-(s+.5)) %>%  # to interpret parameter s as switching probability
+  select(strategy, s:gamble, rare, a_p1:ev_ratio, agent, n_sample, n_a, a_p1_exp, a_p2_exp, a_ev_exp, b_ev_exp, choice, A_sum, B_sum, diff)
+
+# comprehensive strategy
+
+## use hash to validate simulation data
+
+hash_comprehensive <- digest(sim_comprehensive, "md5")
[…]

### 2021-09-27 R/simulate_comprehensive.R

@@ -1,0 +1,91 @@
+pacman::p_load(tidyverse)
+source("R/fun_cumulative_stats.R") # call functions for computing cumulative stats
+
+# test set
+gambles <- read_csv("data/gambles/sr_subset.csv")
+n_agents <- 100
+
+# simulation parameters
+theta <- expand_grid(s = seq(-.5, .4, .1), # probability increment added to unbiased sampling probability of p = .5
+                     boundary = c("absolute", "relative"), # boundary type
+                     a = seq(15, 75, 15)) # boundaries
+
+# simulation
+## for each parameter combination (rows of theta), all gambles are played by all agents
+## 100 (parameter combinations) x 60 (gambles) x 100 (agents) = 600.000 trials
+
+set.seed(19543)
+param_list <- vector("list", length(nrow(theta)))
+for (set in seq_len(nrow(theta))) { # loop over parameter combinations
+  gamble_list <- vector("list", length(nrow(gambles)))
+  for (gamble in seq_len(nrow(gambles))) { # loop over gambles
+    agents_list <- vector("list", n_agents)
+    for (agent in seq_along(1:n_agents)){ # loop over agents
+
+      # initiate trials in a state of ignorance
+
+      fd <- tibble() # frequency distribution of sampled outcomes
+      p <- .5  # no attention bias
+      s <- 0  # no switching at process initiation
+      init <- sample(c("a", "b"), size = 1, prob = c(p + s, p - s)) # prospect attended first
+      attend <- init
+      boundary_reached <- FALSE
+
+      # sampling of outcomes from prospects A and B continues until boundary is reached
+
+      while(boundary_reached == FALSE) {
+
+        # draw single sample from either A or B
+
+        if(attend == "a") {
+          single_smpl <- gambles[gamble, ] %>%
+            mutate(attended = attend,
+                   A = sample(x = c(a_o1, a_o2), size = 1, prob = c(a_p1, 1-a_p1)),
+                   B = NA)
+          s <- theta[[set, "s"]] # to update the probability of sampling from A again
+        } else {
+          single_smpl <- gambles[gamble, ] %>%
+            mutate(attended = attend,
+                   A = NA,
+                   B = b_o1)
+          s <- -1*theta[[set, "s"]] # to update the probability of sampling from B again
+        }
+
[…]

### 2021-09-27 R/simulate_gambles.R

@@ -1,0 +1,25 @@
+pacman::p_load(tidyverse)
+source("R/fun_generate_gambles.R") # call function for generating 2-outcome gambles
+
+# generate 10,000 safe-risky gambles
+
+set.seed(349)
+sr_gambles <- generate_gambles(n = 10000, safe = TRUE, lower = 0, upper = 20)
+sr_gambles <- sr_gambles %>% mutate(rare = case_when(a_p1 >= .2 & a_p1 <= .8 ~ "none",
+                                                     a_p1 < .2 ~ "unattractive", # a_o1 is the smaller outcome
+                                                     a_p1 > .8 ~ "attractive"))
+write_csv(sr_gambles, "data/gambles/sr_gambles.csv")
+
+
+# select subset of 60 gambles
+# stratified sampling of 20 gambles with no/attractive/unattractive rare event
+
+sr_subset <- tibble()
+
+set.seed(735)
+for(i in unique(sr_gambles$rare)) {
+  type <- sr_gambles %>% filter(rare == i) # type of rare event
+  smpl <- sample(seq_len(nrow(type)), size = 20) # random sample of 20 rows/gambles
+  sr_subset <- bind_rows(sr_subset, type[smpl, ])
+}
+write_csv(sr_subset, "data/gambles/sr_subset.csv")

### 2021-09-27 R/simulate_piecewise.R

@@ -1,0 +1,139 @@
+pacman::p_load(tidyverse)
+source("R/fun_cumulative_stats.R") # call functions for computing cumulative stats
+
+# test set
+gambles <- read_csv("data/gambles/sr_subset.csv")
+n_agents <- 100
+
+# simulation parameters
+theta <- expand_grid(s = seq(-.5, .4, .1), # probability increment added to unbiased sampling probability of p = .5
+                     boundary = c("absolute", "relative"), # boundary type
+                     a = seq(1, 5, 1)) # boundaries (number of required round-wins)
+
+# simulation
+## for each parameter combination (rows of theta), all gambles are played by all agents
+## 100 (parameter combinations) x 60 (gambles) x 100 (agents) = 600.000 trials
+
+set.seed(56221)
+param_list <- vector("list", length(nrow(theta)))
+for (set in seq_len(nrow(theta))) {  # loop over parameter combinations
+  gamble_list <- vector("list", length(nrow(gambles)))
+  for (gamble in seq_len(nrow(gambles))) { # loop over gambles
+    agents_list <- vector("list", n_agents)
+    for (agent in seq_along(1:n_agents)){ # loop over agents
+
+      # initiate trials in a state of ignorance
+
+      fd <- tibble() # frequency distribution of sampled outcomes
+      p <- .5  # no attention bias
+      s <- 0  # no switching at process initiation
+      init <- sample(c("a", "b"), size = 1, prob = c(p + s, p - s)) # prospect attended first
+      attend <- init
+      round <- 1
+      boundary_reached <- FALSE
+
+      # sampling of outcomes from prospects A and B continues until boundary is reached
+
+      while(boundary_reached == FALSE) {
+
+        # prospects are compared round-wise
+        ## a round consists of an uninterrupted sequence of sampled outcomes each from A and B
+        ## prospects with a higher mean of sampled outcomes within a round earn a round-win
+
+        smpl_round <- tibble()
+        while(attend == init) {# sequence of single samples from prospect attended first
+
+          # draw single sample from either A or B
+
+          if(attend == "a") {
+            single_smpl <- gambles[gamble, ] %>%
+              mutate(round = round,
+                     attended = attend,
+                     A = sample(x = c(a_o1, a_o2), size = 1, prob = c(a_p1, 1-a_p1)),
[…]

### 2021-09-27 R/estimate_cpt_hierarchical_prelec-98.R
Add scripts and model files for estimating CPT

@@ -1,0 +1,104 @@
+pacman::p_load(tidyverse, R2jags)
+source("R/fun_inits_MCMC_hierarchical.R") # call function creating initial values for MCMC
+
+# read choice data
+
+cols <- list(.default = col_double(),
+             strategy = col_factor(),
+             boundary = col_factor(),
+             gamble = col_factor(),
+             rare = col_factor(),
+             agent = col_factor(),
+             choice = col_factor())
+choices <- read_csv("data/choices/choices.csv", col_types = cols)
+
+# prepare data for JAGS
+
+choices_cpt <- choices %>%
+  filter(!(is.na(a_ev_exp) | is.na(b_ev_exp))) %>% # remove choices where prospect were not attended
+  mutate(choice_A = if_else(choice == "A", 1, 0))
+
+gambles <- choices_cpt %>% select(gamble:ev_ratio) %>% distinct()
+n_gambles <- nrow(gambles)
+n_agents <- choices_cpt %>% distinct(agent) %>% nrow()
+
+## group trials of distinct strategy-parameter combinations of the generating model
+
+params_sim <- choices_cpt %>% distinct(strategy, s, boundary, a) # to get distinct strategy-parameter combinations
+params_grouped <- vector("list", nrow(params_sim))
+
+choices_cpt_grouped <- vector("list", nrow(params_sim))
+a_p1_exp_grouped <- vector("list", nrow(params_sim))
+a_p2_exp_grouped <- vector("list", nrow(params_sim))
+
+for(set in seq_len(nrow(params_sim))){
+
+  params_grouped[[set]] <- choices_cpt %>%
+    filter(strategy == params_sim[[set, "strategy"]] & s == params_sim[[set, "s"]] & boundary == params_sim[[set, "boundary"]] & a == params_sim[[set, "a"]])
+
+  choices_cpt_grouped[[set]] <- params_grouped[[set]] %>%
+    select(gamble, agent, choice_A) %>%
+    pivot_wider(names_from = "agent", values_from = "choice_A", names_prefix = "Ag_") %>%
+    select(-gamble)
+
+  a_p1_exp_grouped[[set]] <- params_grouped[[set]] %>%
+    select(gamble, agent, a_p1_exp) %>%
+    pivot_wider(names_from = "agent", values_from = "a_p1_exp", names_prefix = "Ag_") %>%
+    select(-gamble)
+
[…]

### 2021-09-27 R/estimate_cpt_pooled_goldstein-einhorn-1987.R

@@ -1,0 +1,94 @@
+pacman::p_load(tidyverse, R2jags)
+source("R/fun_inits_MCMC_pooled.R") # call function creating initial values for MCMC
+
+# read choice data
+
+cols <- list(.default = col_double(),
+             strategy = col_factor(),
+             boundary = col_factor(),
+             gamble = col_factor(),
+             rare = col_factor(),
+             agent = col_factor(),
+             choice = col_factor())
+choices <- read_csv("data/choices/choices.csv", col_types = cols)
+
+# prepare data for JAGS
+
+choices_cpt <- choices %>%
+  filter(!(is.na(a_ev_exp) | is.na(b_ev_exp))) %>% # remove choices where prospect were not attended
+  mutate(choice_A = if_else(choice == "A", 1, 0))
+
+
+#---- pooled estimates
+
+
+# group trials of distinct strategy-parameter combinations of the generating model
+
+params_sim <- choices_cpt %>% distinct(strategy, s, boundary, a) # to get distinct strategy-parameter combinations
+choices_grouped <- vector("list", nrow(params_sim))
+for(set in seq_len(nrow(params_sim))){
+  choices_grouped[[set]] <- choices_cpt %>%
+    filter(strategy == params_sim[[set, "strategy"]] & s == params_sim[[set, "s"]] & boundary == params_sim[[set, "boundary"]] & a == params_sim[[set, "a"]]) %>%
+    mutate(i = row_number()) # assign trial numbers
+}
+
+# allocate space for JAGS output
+
+estimates_cpt <- vector("list", nrow(params_sim)) # posterior statistics and MCMC diagnostics
+posteriors_cpt <- vector("list", nrow(params_sim)) # posterior distributions
+
+# set up MCMC simulations
+
+params_cpt <- c("alpha", "gamma", "delta", "rho")
+n_chains <- 20
+n_iter <- 41000
+n_burnin <- 1000
+n_thin <- 20 # to reduce autocorrelation during sampling process
+
+# MCMC simulation
+
+for(set in seq_len(nrow(params_sim))){
+
+  ## get trials of the respective strategy-parameter combination
+
+  current_trials <- list(choice = choices_grouped[[set]]$choice_A,
+                         a_o1 = choices_grouped[[set]]$a_o1,
+                         a_o2 = choices_grouped[[set]]$a_o2,
+                         b_o1 = choices_grouped[[set]]$b_o1,
+                         b_o2 = choices_grouped[[set]]$b_o2,
[…]

### 2021-09-27 R/fun_inits_MCMC_hierarchical.R

@@ -1,0 +1,4 @@
+inits_MCMC_hierarchical <- function(){list("mu.alpha.prob" = 1,
+                                           "mu.gamma.prob" = 2,
+                                           "mu.delta.prob" = 2,
+                                           "mu.rho.log" = -0.5)}

### 2021-09-27 R/fun_inits_MCMC_pooled.R

@@ -1,0 +1,4 @@
+inits_MCMC_pooled <- function(){list("alpha" = 1,
+                                     "gamma.pre" = .5,
+                                     "delta.pre" = .5,
+                                     "rho.pre" = 0)}

### 2021-09-28 manuscript.Rmd
Determining the distribution of the decision variable D

@@
 author: "Linus Hof, Thorsten Pachur, Veronika Zilker"
-bibliography: sampling-strategies-in-dfe.bib
+bibliography: references_sampling-in-dfe.bib
 output:
@@
 Hills and Hertwig [-@hillsInformationSearchDecisions2010] suggest that any two sample sequences $X_i$ and $Y_i$ are compared by their means. 
-Let thus $C = \mathbb{R}$ be the set of all possible outcomes of such a mean comparison for given sequence lengths $N_X$ and $N_Y$ and
+Let thus $C = \mathbb{R}$ be the set of all possible outcomes of the comparison of the means over two unordered sequences $X_i$ and $Y_i$ of given lengths $N_X$ and $N_Y$ and
 
 $$\begin{equation}
-\mathscr{C} = \left\{ \{c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\}, \{ c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} \leq 0\}
+\mathscr{C} = \left\{B_1 = \{c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\}, B_2 = \{ c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} \leq 0\}
 \right\}
@@
 The outcome of such an ordinal comparison can be regarded as evidence for or against a prospect and the number of wins over a series of independent ordinal comparisons as accumulated evidence. 
-To integrate the concept of evidence accumulation into the current model, we let $D$ be a measurable function that maps the possible outcomes of a mean comparison in $C$ onto a measure space $C' = \{0,1\}$, with $0$ ($1$) indicating a lost (won) comparison:
+To integrate the concept of evidence accumulation into the current model, we let $D$ be a measurable function
 
 $$\begin{equation}
-D(c \in C) = 
+D: C \mapsto C'
+\end{equation}$$
+
+that maps the possible outcomes of a mean comparison in $C$ onto a measure space $C' = \{0,1\}$, with $0$ ($1$) indicating a lost (won) comparison:
+
+$$\begin{equation}
+D(c \in C) \in C' = 
   \begin{cases}
-    1 & \text{for} & \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0) \in \mathscr{C} \} \\
+    1 & \text{for} & \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\}  \in \mathscr{C} \\
     0 & \text{else}. 
@@
 $$\begin{equation}
-D \sim B\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right) \; ,
+D \sim \mathcal{B}\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right) \; ,
 \end{equation}$$
 
-where $p$ is the probability of $X$ winning a single mean comparison and $n$ is the number of comparisons (see [Appendix]).
+where $p$ is the probability of $X$ winning a single mean comparison and $n$ is the number of comparisons (see [Proof A1][Proof A1: Distribution of the Decision Variable]).
 However, although $p$ can in principle be determined, it becomes intractable with increasing elements in $\Omega$ and growing sequence lengths.
@@
 
-Let
+## Proof A1: Distribution of the Decision Variable
+
+To proof is that a sequence $D_i = D_1, ..., D_n$ of decision variables with the mapping
 
 $$\begin{equation}
-X_1, ..., X_{N_X}
-\end{equation}$$
-
-and
-
-$$\begin{equation}
-Y_1, ..., Y_{N_Y} 
-\end{equation}$$
-
-be sequences of random variables that are iid.
-Then
-
-$$\begin{equation}
-P\left(\frac{\overline{X}_{N_X}}{\overline{Y}_{N_Y}} > 0 \right) = 
-P\left(\frac{\frac{1}{N_X}\sum\limits_{n=1}^{N_X} (X(\omega_i) = A'_X \in \mathscr{F'}_X)_n} 
-{\frac{1}{N_Y}\sum\limits_{m=1}^{N_Y} (Y(\omega_j) = A'_Y \in \mathscr{F'}_Y)_m} > 0 \right)
-\end{equation}$$
-
-is the probability that the quotient of the mean of both sequences takes on a value larger $0$.
-Given the sample sizes $N_X = N_Y = 1$, the equation reduces to
-
-$$\begin{equation}
-P\left(\frac{X(\omega_i \in \Omega_X) = A'_X \in \mathscr{F'}_X}{Y(\omega_j \in \Omega_Y) = A'_Y \in \mathscr{F'}_Y} > 0 \right) \; ,
-\end{equation}$$
-
-which is the sum across all joint probabilities $p(\omega_i \cap \omega_j)$ for which the above inequation holds:.
-
-$$\begin{equation}
-D:= 
-  f
-  \left(
-    \frac{\overline{X}_{N_X}} {\overline{Y}_{N_Y}}
-  \right) 
-  =
+D(c \in C) \in C' = 
   \begin{cases}
-    1 & \text{if} & \frac{\overline{X}_{N_X}}{\overline{Y}_{N_Y}} > 0 \in \mathscr{D} \\
-    0 & \text{else}. 
+    1 & \text{for} & B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathscr{C}  \\
+    0 & \text{else},
   \end{cases}
@@
 
+describes a Bernoulli process following a binomial distribution $\mathcal{B}\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right)$ for fixed sequence lengths $N_X$ and $N_Y$.
+Therefore, $p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right)$ must be identified.
+To demonstrate that this is the case, we assume independence of all random variables $X_i$ and $Y_i$:
+
+$$\begin{equation}
+  \begin{split}
+    p(D = 1) & = p\left( \; B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathscr{C} \; \right) \\ \\
+
+     & = \sum_{c=1}^{|B_1|} \left( \;
+      p(\overline{X}_{N_X})  \times p(\overline{Y}_{N_Y}) \;
+    \right)_{c \in B_1} \\ \\
+
+    & = \sum_{c=1}^{|B_1|} \left( \; 
+      p\left( \frac{1}{N_X} \sum\limits_{i = 1}^{N_X} X_i(\omega \in \Omega_X)\right) 
+      \times
+      p\left( \frac{1}{N_Y} \sum\limits_{i = 1}^{N_Y} Y_i(\omega \in \Omega_Y)\right) \;
+    \right)_{c \in B_1}
+    \; ,
+  \end{split}
+\end{equation}$$
+
+where the index $k = 1, ..., N_k$ can be paraphrased as follows: 
+For given sequence lengths $N_X$ and $N_Y$, $k$ denotes a pair of the two sequences $X_i$ and $Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs and which satisfies the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
+
+As the unordered sequence $k_{\omega_1}, ..., k_{\omega_n}$ follows the multinomial distribution $\mathcal{M}(N_X, p(\omega_1), ..., p(\omega_n))$, its probability is determined by the probability mass function
+
+$$\begin{equation}
+  \begin{split}
+    P(k_{\omega_1}, ..., k_{\omega_n}) &= {N_X\choose k_{\omega_1}, ..., k_{\omega_n} } \prod_{\omega \in \Omega_X} p(\omega)^{k_{\omega}} \\ \\
+    & = 
+    \; ,
+  \end{split}
+\end{equation}$$
+
+reduces to:
+
 # References

### 2021-09-29 manuscript.Rmd
Refinement of the stochastic model including interpretative text

@@
 $$\begin{equation}
-D:= f((\Omega, \mathscr{F}, P)_1, ..., (\Omega, \mathscr{F}, P)_k)
+D:= f((\Omega_1, \mathscr{F}_1, P_1), ..., (\Omega_k, \mathscr{F}_k, P_k))
 \;.
@@
 
-where $i = 1, ..., N$ denotes a sequence of length $N$ of random variables that are iid.
+where $i = \{1, ..., N\}$ denotes a sequence of length $N$ of random variables that are iid.
 
@@
 
-Let $X$ and $Y$ be random variables defined on the prospects $(\Omega, \mathscr{F}, P)_X$ and $(\Omega, \mathscr{F}, P)_Y$.
+Let $X$ and $Y$ be random variables defined on the prospects $(\Omega_X, \mathscr{F}_X, P_X)$ and $(\Omega_Y, \mathscr{F}_Y, P_Y)$.
 
 Hills and Hertwig [-@hillsInformationSearchDecisions2010] suggest that any two sample sequences $X_i$ and $Y_i$ are compared by their means. 
-Let thus $C = \mathbb{R}$ be the set of all possible outcomes of the comparison of the means over two unordered sequences $X_i$ and $Y_i$ of given lengths $N_X$ and $N_Y$ and
+Let thus $C = \mathbb{R}$ be the set of all possible outcomes of the comparison of the means over two unordered sequences $X_i$ and $Y_i$ of given lengths $N_X$ and $N_Y$.
+That is, each element $c \in C$ represents a pair $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs. 
+Let then
 
@@
 be a set of subsets of $C$, indicating that comparisons of prospects on the ordinal (rather than on the metric) scale are of primary interest. 
-The outcome of such an ordinal comparison can be regarded as evidence for or against a prospect and the number of wins over a series of independent ordinal comparisons as accumulated evidence. 
+We denote a single ordinal comparison by the event space $(C, \mathscr{C})$.
+The observed outcome of such an ordinal comparison can be regarded as evidence for or against a prospect and the number of wins over a series of independent ordinal comparisons as accumulated evidence.
 To integrate the concept of evidence accumulation into the current model, we let $D$ be a measurable function
@@
 
-It can be shown that for fixed sequence lengths $N_X$ and $N_Y$, a sequence $D_i = D_1, ..., D_n$ is a Bernoulli process following the binomial distribution
+It can be shown that for fixed sequence lengths $N_X$ and $N_Y$, a sequence $D_i = D_1, ..., D_n$ representing multiple independent comparisons is a Bernoulli process where the number of won comparisons follows the binomial distribution
 
@@
 
-where $p$ is the probability of $X$ winning a single mean comparison and $n$ is the number of comparisons (see [Proof A1][Proof A1: Distribution of the Decision Variable]).
-However, although $p$ can in principle be determined, it becomes intractable with increasing elements in $\Omega$ and growing sequence lengths.
+with $p$ denoting probability of $X_i$ winning a single comparison, i.e., the probability of success, and $n$ denoting the number of comparisons.
+
+It becomes evident that the two combinations of sampling and decision strategies proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010] are reflected in certain restrictions on the free parameters $N_X, N_Y$ and $n$ of the sampling model and that these restrictions translate to the shape of the binomial distribution, straightforwardly via the parameter $n$, more interestingly, however, via its parameter $p$.
+
+I.e., first, whether a single (summary decision) or multiple ordinal comparisons (round-wise decision) are conducted, is reflected by the length of the sequence $D_i = D_1, ..., D_n$ with $n = 1$ for summary decisions and $n \geq 1$ for round-wise decisions.
+The idea that multiple comparisons may be conducted can be formalized by extending the event space $(C, \mathscr{C})$ of a single comparison to its $n$-fold product
+
+$$\begin{equation}
+\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathscr{C}_i \right)
+\; .
+\end{equation}$$
+
+Second, whether comparisons are conducted on the basis of longer sample sequences (comprehensive sampling) or single samples (piecewise sampling) is reflected by the lengths of sample sequences from the same prospect with $N_X, N_Y \geq 1$ for comprehensive sampling and $N_X = N_Y = 1$ for piecewise sampling.
+
+although $p$ can in principle be determined (see [Appendix][A1.
+Determining the Probability of Success in a Comparison of Sample Means]), it becomes intractable with increasing elements in $\Omega$ and growing sequence lengths.
 
@@
 
-## Proof A1: Distribution of the Decision Variable
+## A1. Determining the Probability of Success in a Comparison of Sample Means
 
-To proof is that a sequence $D_i = D_1, ..., D_n$ of decision variables with the mapping
+To proof is that the sequence $D_i = D_1, ..., D_n$ (see [Definition of D][A Stochastic Sampling Model Capturing Differences in Sampling and Decision Strategies]) describes a Bernoulli process following the binomial distribution $\mathcal{B}\left(p(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0), n \right)$ for fixed sequence lengths $N_X$ and $N_Y$.
 
-$$\begin{equation}
-D(c \in C) \in C' = 
-  \begin{cases}
-    1 & \text{for} & B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathscr{C}  \\
-    0 & \text{else},
-  \end{cases}
-\end{equation}$$
+Therefore we must demonstrate that the probability of success, i.e., $p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right)$, is identified.
 
-describes a Bernoulli process following a binomial distribution $\mathcal{B}\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right)$ for fixed sequence lengths $N_X$ and $N_Y$.
-Therefore, $p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right)$ must be identified.
-To demonstrate that this is the case, we assume independence of all random variables $X_i$ and $Y_i$:
+We start by setting the probability of success equal to the probability of $B_1 \in \mathscr{C}$ which is the subset of the set of all mean comparisons resulting from the pairs $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ satisfying the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
 
@@
   \begin{split}
-    p(D = 1) & = p\left( \; B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathscr{C} \; \right) \\ \\
-
+    p(D = 1) 
+      & = p \left( \; B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathscr{C} \; \right) \\\\\\ 
       & = \sum_{c=1}^{|B_1|} \left( \;
-      p(\overline{X}_{N_X})  \times p(\overline{Y}_{N_Y}) \;
-    \right)_{c \in B_1} \\ \\
-
+          p(\overline{X}_{N_X})  
+          \times 
+          p(\overline{Y}_{N_Y}) \; 
+        \right)_{c \, \in \, B_1} \\\\\\
       & = \sum_{c=1}^{|B_1|} \left( \; 
-      p\left( \frac{1}{N_X} \sum\limits_{i = 1}^{N_X} X_i(\omega \in \Omega_X)\right) 
+        p \left( 
+          \frac{1}{N_X} \sum\limits_{i = 1}^{N_X} X_i(\omega \in \Omega_X)
+        \right) 
         \times
-      p\left( \frac{1}{N_Y} \sum\limits_{i = 1}^{N_Y} Y_i(\omega \in \Omega_Y)\right) \;
-    \right)_{c \in B_1}
-    \; ,
+        p \left( 
+          \frac{1}{N_Y} \sum\limits_{i = 1}^{N_Y} Y_i(\omega \in \Omega_Y)
+        \right) \; 
+        \right)_{c \, \in \, B_1} \\\\\\
+      & = \sum_{c=1}^{|B_1|} \left( \;
+        \left(
+          {N_X\choose k_{\omega_{1X}}, ..., k_{\omega_{nX}} } \prod_{\omega_{iX} \in \Omega_X} p(\omega_{iX})^{k_{\omega_{iX}}}
+        \right)
+        \times
+        \left(
+        {N_Y\choose k_{\omega_{1Y}}, ..., k_{\omega_{nY}} } \prod_{\omega_{iY} \in \Omega_Y} p(\omega_{iY})^{k_{\omega_{iY}}}
+        \right)
+        \right)_{c \, \in \, B_1} \\\\\\
+      & = \sum_{c=1}^{|B_1|} \left( \;
+        \left(
+          \frac{N_X!}{k_{\omega_{1X}}! \times ... \times k_{\omega_{nX}}!} 
+          \times 
+          p(\omega_{1X})^{k_{\omega_{1X}}} 
+          \times 
+          ... 
+          \times p(\omega_{nX})^{k_{\omega_{nX}}}
+        \right)
+        \times
+        \left(
+          \frac{N_Y!}{k_{\omega_{1Y}}! \times ... \times k_{\omega_{nY}}!} 
+          \times 
+          p(\omega_{1Y})^{k_{\omega_{1Y}}} 
+          \times 
+          ... 
+          \times p(\omega_{nY})^{k_{\omega_{nY}}}
+        \right)
+      \right)_{c \, \in \, B_1}
   \end{split}
@@
 
-where the index $k = 1, ..., N_k$ can be paraphrased as follows: 
-For given sequence lengths $N_X$ and $N_Y$, $k$ denotes a pair of the two sequences $X_i$ and $Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs and which satisfies the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
+where $|B_1|$ denotes the cardinality of the set $B_1$. 
+The above equation can be paraphrased as follows: 
+The probability that an unordered sequence $X_i$ of length $N_X$ has a higher mean than an unordered sequence $Y_i$ of length $N_Y$ is given by the sum of the probabilities of all $|B_1|$ pairs $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs and which satisfies the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
 
+Let $k_{\omega}$ be the number of times an outcome $\omega \in \Omega$ occurs in the sequence $X_i$.
 As the unordered sequence $k_{\omega_1}, ..., k_{\omega_n}$ follows the multinomial distribution $\mathcal{M}(N_X, p(\omega_1), ..., p(\omega_n))$, its probability is determined by the probability mass function
-
-$$\begin{equation}
-  \begin{split}
-    P(k_{\omega_1}, ..., k_{\omega_n}) &= {N_X\choose k_{\omega_1}, ..., k_{\omega_n} } \prod_{\omega \in \Omega_X} p(\omega)^{k_{\omega}} \\ \\
-    & = 
-    \; ,
-  \end{split}
-\end{equation}$$
 

### 2021-09-30 manuscript.Rmd
Minor changes of Author Note, Appendix, Interpretative Text to Stochastic Model

@@
 # load packages
-pacman::p_load(repro,
-               tidyverse,
+pacman::p_load(tidyverse,
                knitr, 
@@
 
+This document was created from the commit with the hash `r repro::current_hash()`.
+
 # Author Note
 
-This document was created from the commit with the hash `r repro::current_hash()`.
+All materials of this work in progress can be found on the accompanying GitHub repository: https://github.com/linushof/sampling-in-dfe
 
-- Add information on how to reproduce the project.
-- Add contact.
+- Add information on how to reproduce the project
+
+- Add contact
 
@@
 
-although $p$ can in principle be determined (see [Appendix][A1.
-Determining the Probability of Success in a Comparison of Sample Means]), it becomes intractable with increasing elements in $\Omega$ and growing sequence lengths.
+Note that, in order to derive predictions of the choice behavior from the stochastic model, the probability of success $p$ and therefore, necessarily, the probability of each possible outcome $c \in C$ of a mean comparison must be identified.
+Although this can be demonstrated for random variables defined on prospects of the kind considered so far (see [Appendix 1][Appendix 1: Determining the Probability of Success in a Comparison of Sample Means]), it becomes soon intractable with increasing elements in $\Omega$ and growing sequence lengths.
+However, in the following section and a subsequent simulation analysis, we demonstrate that the combinations of sampling and decision strategies and their corresponding parameter values in the stochastic model produce some principle and predictable trends in the choice behavior that can be modeled in the cumulative prospect theory.
 
-## Predicting Choice Behavior in DfE
+## Predicting Choice Behavior
 
-Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed the two different sampling strategies in combination with the respective decision strategies, i.e., piecewise sampling and round-wise comparison vs.
-comprehensive sampling and summary comparison, as an explanation for different choice patterns in DfE.
-How does the current version of the SSM support this proposition? 
-Given prospects $X$ and $Y$, the sample spaces $S = \left\{\frac{\overline{X}_{N_X}} {\overline{Y}_{N_Y}}\right\}^{\mathbb{N}}$ can be varied by changes on three parameters, i.e., the number of comparisons $\mathbb{N}$ and the sample sizes $N_X$ and $N_Y$ on which these comparisons are based.
-First, only considering the pure cases formulated by the above authors, the following restrictions are put the parameters:
+Note first that the current stochastic sampling model allows to treat sampling and decision strategies independently by parameterization of both lengths of sample sequences and the number of comparisons.
 
-$$\begin{equation}
-\mathbb{N}
-  =
-  \begin{cases}
-    1 & \text{if} & \text{Summary} \\ 
-    \geq 1 & \text{if} & \text{Round-wise}  
-  \end{cases}\\
-\end{equation}$$
-
-and
-
-$$\begin{equation}
-N_X \, \text{and} \, N_Y
-  =
-  \begin{cases}
-    \geq 1 & \text{if} & \text{Summary} \\ 
-    1 & \text{if} & \text{Round-wise}  
-  \end{cases}\\
-\end{equation}$$
-
-For the summary strategy, the following prediction is obtained:
+...
 
@@
 
-For the round-wise strategy, the following prediction is obtained:
-
-Given that $N_X$ and $N_Y$ are set to 1, $D$ follows the binomial distribution
-
-$$\begin{equation}
-B(k \, | \, p_X, \mathbb{N}) \; ,
-\end{equation}$$
-
-where $p$ is the probability that a single sample of prospect $X$ is larger than a single sample of prospect $Y$, $\mathbb{N}$ is the number of comparisons and $k$ is the number of times $x \in X$ is larger than $y \in Y$.
-
-*Proof.*
-
-For $N_X = N_Y = 1$, the sample space is
-
-$$\begin{equation}
-\left\{\frac{\overline{X}_{N_X = 1}} {\overline{Y}_{N_Y = 1}} \right\}^{\mathbb{N}} =
-\left\{\frac{x_i \in \Omega'_X} {y_j \in \Omega'_Y}\right\}^{\mathbb{N}}
-\end{equation}$$
-
 # Method
@@
 To omit dominant prospects, safe outcomes fall between both risky outcomes.
-The table below contains the test set of 60 gambles.
+Table A1 contains the test set of 60 gambles [Appendix 2][Appendix 2: Prospect Test Set].
 Sampling of gambles was stratified, randomly drawing an equal number of 20 gambles with no, an attractive, and an unattractive rare outcome.
 Risky outcomes are considered *"rare"* if their probability is $p < .2$ and *"attractive"* (*"unattractive"*) if they are higher (lower) than the safe outcome.
-
-```{r message=FALSE}
-gambles <- read_csv("data/gambles/sr_subset.csv")
-gambles %>% kable()
-```
 
@@
 
-## A1. Determining the Probability of Success in a Comparison of Sample Means
+## Appendix 1: Determining the Probability of Success in a Comparison of Sample Means
 
-To proof is that the sequence $D_i = D_1, ..., D_n$ (see [Definition of D][A Stochastic Sampling Model Capturing Differences in Sampling and Decision Strategies]) describes a Bernoulli process following the binomial distribution $\mathcal{B}\left(p(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0), n \right)$ for fixed sequence lengths $N_X$ and $N_Y$.
+To proof is that the sequence $D_i = D_1, ..., D_n$ (see [Definition of D][A Stochastic Sampling Model Capturing Differences in Sampling and Decision Strategies]) describes a Bernoulli process with the number of won comparisons following the binomial distribution $\mathcal{B}\left(p(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0), n \right)$ for fixed sequence lengths $N_X$ and $N_Y$.
 
-Therefore we must demonstrate that the probability of success, i.e., $p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right)$, is identified.
-
-We start by setting the probability of success equal to the probability of $B_1 \in \mathscr{C}$ which is the subset of the set of all mean comparisons resulting from the pairs $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ satisfying the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
+Therefore we must demonstrate that the probability of success, i.e., $p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right)$, is identified:
 
@@
       & = p \left( \; B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathscr{C} \; \right) \\\\\\ 
-      & = \sum_{c=1}^{|B_1|} \left( \;
+      & = \sum_{c_i=1}^{|B_1|} \left( \;
           p(\overline{X}_{N_X})  
@@
           p(\overline{Y}_{N_Y}) \; 
-        \right)_{c \, \in \, B_1} \\\\\\
-      & = \sum_{c=1}^{|B_1|} \left( \; 
+        \right)_{c_i \, \in \, B_1} \\\\\\
+      & = \sum_{c_i=1}^{|B_1|} \left( \; 
         p \left( 
@@
         \right) \; 
-        \right)_{c \, \in \, B_1} \\\\\\
-      & = \sum_{c=1}^{|B_1|} \left( \;
+        \right)_{c_i \, \in \, B_1} \\\\\\
+      & = \sum_{c_i=1}^{|B_1|} \left( \;
         \left(
@@
         \right)
-        \right)_{c \, \in \, B_1} \\\\\\
-      & = \sum_{c=1}^{|B_1|} \left( \;
+        \right)_{c_i \, \in \, B_1} \\\\\\
+      & = \sum_{c_i=1}^{|B_1|} \left( \;
         \left(
@@
         \right)
-      \right)_{c \, \in \, B_1}
+      \right)_{c_i \, \in \, B_1}
+      \; ,
   \end{split}
@@
 
-where $|B_1|$ denotes the cardinality of the set $B_1$. 
-The above equation can be paraphrased as follows: 
-The probability that an unordered sequence $X_i$ of length $N_X$ has a higher mean than an unordered sequence $Y_i$ of length $N_Y$ is given by the sum of the probabilities of all $|B_1|$ pairs $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs and which satisfies the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
+where $|B_1|$ denotes the cardinality of the set $B_1$, $c_i \in B_1$ a pair $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs, and $k$ denotes the number of times $\omega$ was observed within a sequence.
 
-Let $k_{\omega}$ be the number of times an outcome $\omega \in \Omega$ occurs in the sequence $X_i$.
-As the unordered sequence $k_{\omega_1}, ..., k_{\omega_n}$ follows the multinomial distribution $\mathcal{M}(N_X, p(\omega_1), ..., p(\omega_n))$, its probability is determined by the probability mass function
+## Appendix 2: Prospect Test Set
 
-reduces to:
+```{r message=FALSE}
+gambles <- read_csv("data/gambles/sr_subset.csv")
+gambles %>% kable()
+```
 

### 2021-10-01 R/estimate_cpt_hierarchical_prelec-98.R
Review dependencies between scripts and data

@@ -4,7 +4,6 @@ source("R/fun_inits_MCMC_hierarchical.R") # call function creating initial value
 # read choice data
 
 cols <- list(.default = col_double(),
-             strategy = col_factor(),
              boundary = col_factor(),
              gamble = col_factor(),
              rare = col_factor(),
@@ -14,29 +13,28 @@ choices <- read_csv("data/choices/choices.csv", col_types = cols)
 
 # prepare data for JAGS
 
-choices_cpt <- choices %>%
-  filter(!(is.na(a_ev_exp) | is.na(b_ev_exp))) %>% # remove choices where prospect were not attended
-  mutate(choice_A = if_else(choice == "A", 1, 0))
+choices <- choices %>%
+  mutate(choice_A = if_else(choice == "A", 1, 0)) # to apply logit choice rule
 
-gambles <- choices_cpt %>% select(gamble:ev_ratio) %>% distinct()
+gambles <- choices %>% select(gamble:ev_ratio) %>% distinct()
 n_gambles <- nrow(gambles)
-n_agents <- choices_cpt %>% distinct(agent) %>% nrow()
+n_agents <- choices %>% distinct(agent) %>% nrow()
 
 ## group trials of distinct strategy-parameter combinations of the generating model
 
-params_sim <- choices_cpt %>% distinct(strategy, s, boundary, a) # to get distinct strategy-parameter combinations
+params_sim <- choices %>% distinct(s, boundary, a) # to get distinct strategy-parameter combinations
 params_grouped <- vector("list", nrow(params_sim))
 
-choices_cpt_grouped <- vector("list", nrow(params_sim))
+choices_grouped <- vector("list", nrow(params_sim))
 a_p1_exp_grouped <- vector("list", nrow(params_sim))
 a_p2_exp_grouped <- vector("list", nrow(params_sim))
 
 for(set in seq_len(nrow(params_sim))){
 
-  params_grouped[[set]] <- choices_cpt %>%
-    filter(strategy == params_sim[[set, "strategy"]] & s == params_sim[[set, "s"]] & boundary == params_sim[[set, "boundary"]] & a == params_sim[[set, "a"]])
+  params_grouped[[set]] <- choices %>%
+    filter(s == params_sim[[set, "s"]] & boundary == params_sim[[set, "boundary"]] & a == params_sim[[set, "a"]])
 
-  choices_cpt_grouped[[set]] <- params_grouped[[set]] %>%
[…]

### 2021-10-01 R/prepare_choice_data.R

@@ -1,4 +1,4 @@
-pacman::p_load(tidyverse, digest)
+pacman::p_load(tidyverse, digest, crayon)
 
 # load simulation data
 cols <- list(.default = col_double(),
@@ -8,21 +8,20 @@ cols <- list(.default = col_double(),
              rare = col_factor(),
              attended = col_factor(),
              choice = col_factor())
-sim_piecewise <- read_csv("data/simulation/sim_piecewise.csv", col_types = cols)
-sim_comprehensive <- read_csv("data/simulation/sim_comprehensive.csv", col_types = cols)
+simulation <- read_csv("data/simulation/simulation.csv", col_types = cols)
 
-# piecewise strategy
+# use hash to validate simulation data
 
-## use hash to validate simulation data
-
-hash_piecewise <- digest(sim_piecewise, "md5")
-if(hash_piecewise != "295e1a7b23402dd50a1dae5a54141f78"){
-  warning("Mismatch between original and current data!\nCurrent hash is:\n    '", hash_piecewise, "'")
+hash_sim <- digest(simulation, "md5")
+if(hash_sim != "295e1a7b23402dd50a1dae5a54141f78"){
+  warning("Mismatch between original and current data!\nCurrent hash is:\n    '", hash_sim, "'")
+}else{
+  cat(green("Data is valid. You can continue."))
 }
 
 ## transform data to obtain trial summaries
 
-choices_piecewise <- sim_piecewise %>%
+choices <- simulation %>%
   group_by(s, boundary, a, gamble, agent) %>% # group by trials
   mutate(n_sample = n(), # total number of single samples
          n_a = n_sample - sum(is.na(A)), # number of single samples drawn from risky option
@@ -35,39 +34,9 @@ choices_piecewise <- sim_piecewise %>%
 
   ## tidy data
 
-  mutate(strategy = "piecewise",
-         s = 1-(s+.5)) %>%  # to interpret parameter s as switching probability
-  select(strategy, s:gamble, rare, a_p1:ev_ratio, agent, n_sample, n_a, a_p1_exp, a_p2_exp, a_ev_exp, b_ev_exp, choice, A_sum, B_sum, diff)
+  mutate(s = 1-(s+.5)) %>%  # to interpret parameter s as switching probability
[…]

### 2021-10-01 R/prepare_estimates.R

@@ -1,0 +1,18 @@
+pacman::p_load(tidyverse)
+
+# load estimates
+cols <- list(.default = col_double(),
+             boundary = col_factor(),
+             parameter = col_guess())
+cpt <- read_csv("data/estimates/estimates_hierarchical_cpt.csv", col_types = cols)
+
+
+# separate parameter type from hierarchy level
+cpt <- cpt %>%
+  mutate(parameter = str_replace_all(cpt$parameter, c("\\[" = "_",
+                                                            "\\]" = "",
+                                                            "mu.alpha" = "alpha_mu",
+                                                            "mu.gamma" = "gamma_mu",
+                                                            "mu.delta" = "delta_mu",
+                                                            "mu.rho" = "rho_mu"))) %>% # use uniform separators
+  separate(parameter, c("parameter", "level"), sep = "_") # separate variables into two columns

### 2021-10-01 R/estimate_cpt_pooled_goldstein-einhorn-1987.R
Delete old files

@@ -1,94 +1,0 @@
-pacman::p_load(tidyverse, R2jags)
-source("R/fun_inits_MCMC_pooled.R") # call function creating initial values for MCMC
-
-# read choice data
-
-cols <- list(.default = col_double(),
-             strategy = col_factor(),
-             boundary = col_factor(),
-             gamble = col_factor(),
-             rare = col_factor(),
-             agent = col_factor(),
-             choice = col_factor())
-choices <- read_csv("data/choices/choices.csv", col_types = cols)
-
-# prepare data for JAGS
-
-choices_cpt <- choices %>%
-  filter(!(is.na(a_ev_exp) | is.na(b_ev_exp))) %>% # remove choices where prospect were not attended
-  mutate(choice_A = if_else(choice == "A", 1, 0))
-
-
-#---- pooled estimates
-
-
-# group trials of distinct strategy-parameter combinations of the generating model
-
-params_sim <- choices_cpt %>% distinct(strategy, s, boundary, a) # to get distinct strategy-parameter combinations
-choices_grouped <- vector("list", nrow(params_sim))
-for(set in seq_len(nrow(params_sim))){
-  choices_grouped[[set]] <- choices_cpt %>%
-    filter(strategy == params_sim[[set, "strategy"]] & s == params_sim[[set, "s"]] & boundary == params_sim[[set, "boundary"]] & a == params_sim[[set, "a"]]) %>%
-    mutate(i = row_number()) # assign trial numbers
-}
-
-# allocate space for JAGS output
-
-estimates_cpt <- vector("list", nrow(params_sim)) # posterior statistics and MCMC diagnostics
-posteriors_cpt <- vector("list", nrow(params_sim)) # posterior distributions
-
-# set up MCMC simulations
-
-params_cpt <- c("alpha", "gamma", "delta", "rho")
-n_chains <- 20
-n_iter <- 41000
-n_burnin <- 1000
-n_thin <- 20 # to reduce autocorrelation during sampling process
-
-# MCMC simulation
-
-for(set in seq_len(nrow(params_sim))){
-
-  ## get trials of the respective strategy-parameter combination
-
-  current_trials <- list(choice = choices_grouped[[set]]$choice_A,
-                         a_o1 = choices_grouped[[set]]$a_o1,
-                         a_o2 = choices_grouped[[set]]$a_o2,
-                         b_o1 = choices_grouped[[set]]$b_o1,
-                         b_o2 = choices_grouped[[set]]$b_o2,
[…]

### 2021-10-01 R/fun_inits_MCMC_pooled.R

@@ -1,4 +1,0 @@
-inits_MCMC_pooled <- function(){list("alpha" = 1,
-                                     "gamma.pre" = .5,
-                                     "delta.pre" = .5,
-                                     "rho.pre" = 0)}

### 2021-10-01 R/simulate_comprehensive.R

@@ -1,91 +1,0 @@
-pacman::p_load(tidyverse)
-source("R/fun_cumulative_stats.R") # call functions for computing cumulative stats
-
-# test set
-gambles <- read_csv("data/gambles/sr_subset.csv")
-n_agents <- 100
-
-# simulation parameters
-theta <- expand_grid(s = seq(-.5, .4, .1), # probability increment added to unbiased sampling probability of p = .5
-                     boundary = c("absolute", "relative"), # boundary type
-                     a = seq(15, 75, 15)) # boundaries
-
-# simulation
-## for each parameter combination (rows of theta), all gambles are played by all agents
-## 100 (parameter combinations) x 60 (gambles) x 100 (agents) = 600.000 trials
-
-set.seed(19543)
-param_list <- vector("list", length(nrow(theta)))
-for (set in seq_len(nrow(theta))) { # loop over parameter combinations
-  gamble_list <- vector("list", length(nrow(gambles)))
-  for (gamble in seq_len(nrow(gambles))) { # loop over gambles
-    agents_list <- vector("list", n_agents)
-    for (agent in seq_along(1:n_agents)){ # loop over agents
-
-      # initiate trials in a state of ignorance
-
-      fd <- tibble() # frequency distribution of sampled outcomes
-      p <- .5  # no attention bias
-      s <- 0  # no switching at process initiation
-      init <- sample(c("a", "b"), size = 1, prob = c(p + s, p - s)) # prospect attended first
-      attend <- init
-      boundary_reached <- FALSE
-
-      # sampling of outcomes from prospects A and B continues until boundary is reached
-
-      while(boundary_reached == FALSE) {
-
-        # draw single sample from either A or B
-
-        if(attend == "a") {
-          single_smpl <- gambles[gamble, ] %>%
-            mutate(attended = attend,
-                   A = sample(x = c(a_o1, a_o2), size = 1, prob = c(a_p1, 1-a_p1)),
-                   B = NA)
-          s <- theta[[set, "s"]] # to update the probability of sampling from A again
-        } else {
-          single_smpl <- gambles[gamble, ] %>%
-            mutate(attended = attend,
-                   A = NA,
-                   B = b_o1)
-          s <- -1*theta[[set, "s"]] # to update the probability of sampling from B again
-        }
-
[…]

### 2021-10-01 R/estimate_hierarchical_cpt.R
Rename file and change dependencies

@@ -1,5 +1,5 @@
 pacman::p_load(tidyverse, R2jags)
-source("R/fun_inits_MCMC_hierarchical.R") # call function creating initial values for MCMC
+source("R/fun_inits_MCMC.R") # call function creating initial values for MCMC
 
 # read choice data
 
@@ -78,9 +78,9 @@ for(set in seq_len(nrow(params_sim))){
   ## sample from posterior distributions using MCMC
 
   current_sample <- jags.parallel(data = current_trials,
-                                  inits = inits_MCMC_hierarchical,
+                                  inits = inits_MCMC,
                                   parameters.to.save = params_cpt,
-                                  model.file = "JAGS/cpt_hierarchical_prelec-98.txt",
+                                  model.file = "JAGS/hierarchical_cpt.txt",
                                   n.chains = n_chains,
                                   n.iter = 21000,
                                   n.burnin = 1000,

### 2021-10-01 R/fun_inits_MCMC.R

@@ -1,0 +1,4 @@
+inits_MCMC <- function(){list("mu.alpha.prob" = 1,
+                              "mu.gamma.prob" = 2,
+                              "mu.delta.prob" = 2,
+                              "mu.rho.log" = -0.5)}

### 2021-10-01 R/fun_inits_MCMC_hierarchical.R

@@ -1,4 +1,0 @@
-inits_MCMC_hierarchical <- function(){list("mu.alpha.prob" = 1,
-                                           "mu.gamma.prob" = 2,
-                                           "mu.delta.prob" = 2,
-                                           "mu.rho.log" = -0.5)}

### 2021-10-01 R/simulate_dfe.R
Rename file

@@ -135,5 +135,5 @@ for (set in seq_len(nrow(theta))) {  # loop over parameter combinations
   all_gambles <- gamble_list %>% map_dfr(as.list)
   param_list[[set]] <- expand_grid(theta[set, ], all_gambles)
 }
-sim_piecewise <- param_list %>% map_dfr(as.list)
-write_csv(sim_piecewise, "data/simulation/sim_piecewise.csv")
+simulation <- param_list %>% map_dfr(as.list)
+write_csv(simulation, "data/simulation/simulation.csv")

### 2021-10-01 R/prepare_estimates.R
Ignore deviance data

@@ -6,6 +6,7 @@ cols <- list(.default = col_double(),
              parameter = col_guess())
 cpt <- read_csv("data/estimates/estimates_hierarchical_cpt.csv", col_types = cols)
 
+cpt <- cpt %>% filter(parameter != "deviance")
 
 # separate parameter type from hierarchy level
 cpt <- cpt %>%

### 2021-10-01 manuscript.Rmd
Restructuring of the manuscript + Analysis of Probability weighting function

@@
     wrap: sentence
+  chunk_output_type: console
 ---
@@
                knitr, 
-               viridis)
+               scico # for scientific color palettes
+               )
 ```
@@
 
-...
+[...]
 
@@
 
-...
-
-Given that
-
-$$\begin{equation}
-P\left(\lim_{N_X \to \infty} \overline{X}_{N_X} = E(X) \right) = 
-P\left(\lim_{N_Y \to \infty} \overline{Y}_{N_Y} = E(Y) \right) = 
-1 \; ,
-\end{equation}$$
-
-we obtain that
-
-$$\begin{equation}
-\left(
-    \frac{\overline{X}_{N_X}} {\overline{Y}_{N_Y}}
-\right)
-\in S : 
-P\left(\lim_{N_X \to \infty} \lim_{N_Y \to \infty} \frac{\overline{X}_{N_X}} {\overline{Y}_{N_Y}} = 
-\frac{E(X)} {E(Y)}
-\right ) =
-1 \; ,
-\end{equation}$$
-
-I.e., for the summary strategy, we assume that for increasing sample sizes $N_X$ and $N_Y$, the prospect with the larger expected value is chosen almost surely.
+[...]
 
@@
 
+## Generating Model
+
+[...]
+
+The *switching probability* $s$ is the probability with which agents draw a single sample from the prospect they did not get their most recent single sample from.
+$s$ is varied between .1 to 1 in increments of .1.
+The two boundary parameters resemble the concept of a decision threshold, i.e., if a prospect reaches a boundary, it is chosen by the synthetic agent.
+The *boundary type* is either the minimum number of comparisons any prospect must win (absolute boundary) or the minimum difference between the number of won comparisons (relative boundary).
+The **boundary value** $a$ is varied between 1 to 5 in increments of 1.
+
 ## Test set
 
-Under each condition, i.e., strategy-parameter combinations, all gambles are played by 100 synthetic agents.
-We test a set of gambles, in which one of the prospects contains a safe outcome and the other two risky outcomes (*safe-risky gambles*).
-Therefore, 60 gambles from an initial set of 10,000 are sampled.
-Both outcomes and probabilities are drawn from uniform distributions, ranging from 0 to 20 for outcomes and from .01 to .99 for probabilities of the lower risky outcomes $p_{low}$.
-The probabilities of the higher risky outcomes are $1-p_{low}$, respectively.
-To omit dominant prospects, safe outcomes fall between both risky outcomes.
-Table A1 contains the test set of 60 gambles [Appendix 2][Appendix 2: Prospect Test Set].
+For each parameter combination of the generating model, 100 synthetic agents are presented with 60 choices problems.
+In sum, 100 (parameter combinations), 100 (agents) x 60 (choices) = 600,000 choices are simulated.
+We test a set of 2-prospect choice problems, where one of the prospects contains a safe outcome, i.e., $p(\omega) = 1$ and the other two outcomes where all $p(\omega) \neq 1$.
+Both outcomes and probabilities are drawn from uniform distributions, ranging from 0 to 20 for outcomes and from .01 to .99 for probabilities of the smaller outcome of the risky prospect.
+To omit dominant prospects within a choice problem, outcomes of the safe prospect always fall between both outcomes of the risky prospect.
+Table A1 contains the test set of 60 choice problems [Appendix 2][Appendix 2: Choice Problems], which were sampled from an initial set of 10,000.
 Sampling of gambles was stratified, randomly drawing an equal number of 20 gambles with no, an attractive, and an unattractive rare outcome.
@@
 
-## Model Parameters
+## Describing Model: Cumulative Prospect Theory
 
-**Switching probability** $s$ is the probability with which agents draw the following single sample from the prospect they did not get their most recent single sample from.
-$s$ is varied between .1 to 1 in increments of .1.
+[...]
 
-The **boundary type** is either the minimum value any prospect's sample statistic must reach (absolute) or the minimum value for the difference of these statistics (relative).
-Sample statistics are sums over outcomes (comprehensive strategy) and sums over wins (piecewise strategy), respectively.
+For each distinct strategy-parameter combination, we ran 20 chains of 20,000 iterations each, after a warm-up period of 1000 samples.
+To reduce potential autocorrelation during the sampling process, we only kept every 20th sample (thinning). 
+Bar plots displaying the potential scale reduction factors $\hat{R}$ [@gelmanInferenceIterativeSimulation1992] of the group and agent level CPT parameters can be found in [Appendix 3][Appendix 3: Convergence Diagnostics for CPT Parameters].
 
-For comprehensive integration, the **boundary value** $a$ is varied between 15 to 75 in increments of 15.
-For piecewise integration $a$ is varied between 1 to 5 in increments of 1.
+# Results
+
+## Plausibility Check: Relationship between Switching Probability and Trial Sample Sizes
 
 ```{r message=FALSE}
+
 # read choice data
+
 cols <- list(.default = col_double(),
-             strategy = col_factor(),
              boundary = col_factor(),
@@
 choices <- read_csv("data/choices/choices.csv", col_types = cols)
+
+# get median trial length for each parameter combination
+
+trial_length <- choices %>% 
+  group_by(s, boundary, a) %>% 
+  summarise(med = median(n_sample))
 ```
 
-In sum, 2 (strategies) x 60 (gambles) x 100 (agents) x 100 (parameter combinations) = `r nrow(choices)` choices are simulated.
-
-# Results
-
-Because we are not interested in deviations from normative choice due to sampling artifacts (e.g., ceiling effects produced by low boundaries), we remove trials in which only one prospect was attended.
-In addition, we use relative frequencies of sampled outcomes rather than 'a priori' probabilities to compare actual against normative choice behavior.
-
-```{r}
-# remove choices where prospects were not attended
-choices <- choices %>%
-  filter(!(is.na(a_ev_exp) | is.na(b_ev_exp)))
-```
-
-```{r eval = FALSE}
-# remove choices where not all outcomes were sampled
-choices <- choices %>% 
-  filter(!(is.na(a_ev_exp) | is.na(b_ev_exp) | a_p1_exp == 0 | a_p2_exp == 0))
-```
-
-Removing the respective trials, we are left with `r nrow(choices)` choices.
-
-## Sample Size
+The median length of trials, i.e., the number of single samples drawn in trial, generated by different parameter combinations ranged from `r min(trial_length$med)` to `r max(trial_length$med)`.
+As expected, the scatter plot below shows an inverse relationship between switching probability and trial length.
+I.e., the lower the switching probability, the larger become the sample sequences on which each comparison between prospects is based.  
+This effect is particularly pronounced for low probabilities such that the increase in trial length accelerates as switching probability decreases.
 
 ```{r message=FALSE}
-samples <- choices %>% 
-  group_by(strategy, s, boundary, a) %>% 
-  summarise(n_med = median(n_sample))
-samples_piecewise <- samples %>% filter(strategy == "piecewise")
-samples_comprehensive <- samples %>% filter(strategy == "comprehensive")
-```
 
-The median sample sizes generated by different parameter combinations ranged from `r min(samples_piecewise$n_med)` to `r max(samples_piecewise$n_med)` for piecewise integration and `r min(samples_comprehensive$n_med)` to `r max(samples_comprehensive$n_med)` for comprehensive integration.
+# get median trial length for each switching probability
 
-### Boundary type and boundary value (a)
+trial_length_s <- choices %>% 
+  group_by(s) %>%
+  summarise(med = median(n_sample))
 
-As evidence is accumulated sequentially, relative boundaries and large boundary values naturally lead to larger sample sizes, irrespective of the integration strategy.
+# plot
 
-```{r message=FALSE}
-group_med <- samples_piecewise %>%
-  group_by(boundary, a) %>% 
-  summarise(group_med = median(n_med)) # to get the median across all s values
-
-samples_piecewise %>%
-  ggplot(aes(a, n_med, color = a)) + 
-  geom_jitter(alpha = .5, size = 2) +
-  geom_point(data = group_med, aes(y = group_med), size = 3) +
-  facet_wrap(~boundary) + 
-  scale_color_viridis() + 
-  labs(title = "Piecewise Integration",
-       x ="a", 
-       y="Sample Size", 
-       col="a") + 
+trial_length %>%
+  ggplot(aes(x = s, y = med)) +
+  geom_jitter(color = "#CECECE", size = 3) +
+  geom_point(data = trial_length_s, aes(color = s), size = 3) +
+  geom_path(data = trial_length_s, aes(color = s)) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) + 
+  scale_y_continuous(breaks = seq(0, 120, 10)) +
+  labs(x ="Switching Probability",
+       y = "Median Trial Length", 
+       color="Switching Probability") + 
   theme_minimal()
@@
 
-```{r message=FALSE}
-group_med <- samples_comprehensive %>%
-  group_by(boundary, a) %>% 
-  summarise(group_med = median(n_med))
+## Probability Weighting Function
 
-samples_comprehensive %>%
-  ggplot(aes(a, n_med, color = a)) + 
-  geom_jitter(alpha = .5, size = 2) +
-  geom_point(data = group_med, aes(y = group_med), size = 3) +
-  facet_wrap(~boundary) + 
-  scale_color_viridis() + 
-  labs(title = "Comprehensive Integration",
-       x ="a", 
-       y="Sample Size", 
-       col="a") + 
+The following analyses of choice behavior uses the modeling framework of CPT. 
+A non parametric approach, analyzing false response rates, can be found in [Appendix 4][Appendix 4: False Response Rates].
+
+```{r}
+
+# call script for preparing CPT data
+
+source("R/prepare_estimates.R") 
+gel_92 <- cpt %>% select(s, boundary, a, parameter, level, Rhat) # store scale reduction factor
+
+# Tidy: CPT parameters in columns
+
+cpt <- cpt %>% 
+  select(s, boundary, a, parameter, level, mean) %>% 
+  pivot_wider(names_from = parameter, values_from = mean)
+
+# agent level estimates
+
+cpt_agent <- cpt %>% filter(level != "mu") # agent level estimates
+
+## compute mean across all agent level estimates
+
+cpt_agent_mean <- cpt_agent %>% 
+  group_by(s, boundary, a) %>% 
+  summarise(alpha = round(mean(alpha), 2), 
+            gamma = round(mean(gamma), 2), 
+            delta = round(mean(delta), 2), 
+            rho = round(mean(rho), 2))
+
+# group level estimates
+
+cpt_mu <- cpt %>% filter(level == "mu") # group level posterior means
+```
+
+```{r}
+
+# gamma
+
+cpt_agent %>% 
+  ggplot(aes(x = s, y = gamma)) +
+  geom_jitter(color = "#CECECE" ) + 
+  geom_point(data = cpt_agent_mean, aes(color = s), size = 3) +
+  geom_line(data = cpt_agent_mean, aes(color = s), size = 1) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) + 
+  scale_y_continuous(breaks = seq(0, 2, .2)) +
+  facet_grid(boundary~a, switch = "y") +
+  labs(title = expression(paste("Curvature ", gamma)),
+       x ="Switching Probability",
+       y = expression(gamma), 
+       color="Switching Probability") + 
+  theme_minimal()
+
+# delta
+
+cpt_agent %>% 
+  ggplot(aes(x = s, y = delta)) +
+  geom_jitter(color = "#CECECE") + 
+  geom_point(data = cpt_agent_mean, aes(color = s), size = 3) +
+  geom_line(data = cpt_agent_mean, aes(color = s), size = 1) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) + 
+  scale_y_continuous(breaks = seq(0, 10, .5)) +
+  facet_grid(boundary~a, switch = "y") +
+  labs(title = expression(paste("Elevation ", delta)),
+       x ="Switching Probability",
+       y = expression(delta), 
+       color="Switching Probability") + 
+  theme_minimal()
+
+# weighting function
+
+## compute decision weights
+
+cpt_agent_w <- cpt_agent %>% 
+  select(-c(alpha, rho)) %>% 
+  expand_grid(ep = seq(0, 1, .1)) %>% # 
+  mutate(w = round(exp(-delta*(-log(ep))^gamma), 2))
+
+cpt_agent_mean_w <- cpt_agent %>% 
+  group_by(s) %>% 
+  summarise(gamma = round(mean(gamma), 2), 
+            delta = round(mean(delta), 2)) %>% 
+  expand_grid(ep = seq(0, 1, .1)) %>%
+  mutate(w = round(exp(-delta*(-log(ep))^gamma), 2))
+
+## plot curves
+
+cpt_agent_w %>% 
+  ggplot(aes(x = ep, y = w)) +
+  geom_path(color = "#CECECE") + 
+  geom_path(data = cpt_agent_mean_w, aes(color = s), size = 1.1) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_y_continuous(breaks = seq(0, 1, .1)) + 
+  labs(title = "Probability Weighting Function",
+       x ="Experienced Probability",
+       y = "Subjective Experienced Probability", 
+       color="Switching Probability") + 
+  theme_minimal()
+
+cpt_agent_w %>% 
+  ggplot(aes(x = ep, y = w, color = s)) +
+  geom_path() + 
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_y_continuous(breaks = seq(0, 1, .1)) + 
+  labs(title = "Probability Weighting Function",
+       x ="Experienced Probability ep",
+       y = "Subjective Experienced Probability", 
+       color="Switching Probability") + 
+  theme_minimal()
+
+## for separate a
+
+cpt_agent_mean_w <- cpt_agent %>% 
+  group_by(s, a) %>% 
+  summarise(gamma = round(mean(gamma), 2), 
+            delta = round(mean(delta), 2)) %>% 
+  expand_grid(ep = seq(0, 1, .1)) %>%
+  mutate(w = round(exp(-delta*(-log(ep))^gamma), 2))
+
+cpt_agent_w %>% 
+  ggplot(aes(x = ep, y = w)) +
+  geom_path(color = "#CECECE") + 
+  geom_path(data = cpt_agent_mean_w, aes(color = s), size = 1.1) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_y_continuous(breaks = seq(0, 1, .1)) +
+  facet_wrap(~a, nrow = 2) + 
+  labs(title = "Probability Weighting Function",
+       x ="Experienced Probability",
+       y = "Subjective Experienced Probability", 
+       color="Switching Probability") + 
+  theme_minimal()
+
+cpt_agent_w %>% 
+  ggplot(aes(x = ep, y = w, color = s)) +
+  geom_path() + 
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_y_continuous(breaks = seq(0, 1, .1)) + 
+  facet_wrap(~a, nrow = 2) + 
+  labs(title = "Probability Weighting Function",
+       x ="Experienced Probability ep",
+       y = "Subjective Experienced Probability", 
+       color="Switching Probability") + 
   theme_minimal()
@@
 
-### Switching probability (s)
+## Value Function
 
-For piecewise integration, there is an inverse relationship between switching probability and sample size.
-I.e., the lower s, the less frequent prospects are compared and thus, boundaries are only approached with larger sample sizes.
-This effect is particularly pronounced for low probabilities such that the increase in sample size accelerates as switching probability decreases.
-
-```{r message=FALSE}
-group_med <- samples_piecewise %>%
-  group_by(boundary, s) %>% 
-  summarise(group_med = median(n_med)) # to get the median across all a values
-
-samples_piecewise %>%
-  ggplot(aes(s, n_med, color = s)) + 
-  geom_jitter(alpha = .5, size = 2) +
-  geom_point(data = group_med, aes(y = group_med), size = 3) +
-  facet_wrap(~boundary) + 
-  scale_color_viridis() + 
-  labs(title = "Piecewise Integration",
-       x ="s", 
-       y="Sample Size", 
-       col="s") + 
-  theme_minimal()
-```
-
-For comprehensive integration, boundary types differ in the effects of switching probability.
-For absolute boundaries, switching probability has no apparent effect on sample size as the distance of a given prospect to its absolute boundary is not changed by switching to (and sampling from) the other prospect.
-For relative boundaries, however, samples sizes increase with switching probability.
-
-```{r message=FALSE}
-group_med <- samples_comprehensive %>%
-  group_by(boundary, s) %>% 
-  summarise(group_med = median(n_med)) # to get the median across all a values
-
-samples_comprehensive %>%
-  ggplot(aes(s, n_med, color = s)) + 
-  geom_jitter(alpha = .5, size = 2) +
-  geom_point(data = group_med, aes(y = group_med), size = 3) +
-  facet_wrap(~boundary) + 
-  scale_color_viridis() + 
-  labs(title = "Comprehensive Integration",
-       x ="s",
-       y = "Sample Size", 
-       col="s") + 
-  theme_minimal()
-```
-
-## Choice Behavior
-
-Below, in extension to Hills and Hertwig [-@hillsInformationSearchDecisions2010], the interplay of integration strategies, gamble features, and model parameters in their effects on choice behavior in general and their contribution to underweighting of rare events in particular is investigated.
-We apply two definitions of underweighting of rare events: Considering false response rates, we define underweighting such that the rarity of an attractive (unattractive) outcome leads to choose the safe (risky) prospect although the risky (safe) prospect has a higher expected value.
-
-```{r message=FALSE}
-fr_rates <- choices %>% 
-  mutate(ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2), 
-         norm = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) %>% 
-  filter(!is.na(norm)) %>% # exclude trials with normative indifferent options
-  group_by(strategy, s, boundary, a, rare, norm, choice) %>% # group correct and incorrect responses
-  summarise(n = n()) %>% # absolute numbers 
-  mutate(rate = round(n/sum(n), 2), # response rates 
-         type = case_when(norm == "A" & choice == "B" ~ "false safe", norm == "B" & choice == "A" ~ "false risky")) %>% 
-  filter(!is.na(type)) # remove correct responses
-```
-
-Considering the parameters of Prelec's [-@prelecProbabilityWeightingFunction1998] implementation of the weighting function [CPT; cf.
-@tverskyAdvancesProspectTheory1992], underweighting is reflected by decisions weights estimated to be smaller than the corresponding objective probabilities.
-
-### False Response Rates
-
-```{r message=FALSE}
-fr_rates_piecewise <- fr_rates %>% filter(strategy == "piecewise")
-fr_rates_comprehensive <- fr_rates %>% filter(strategy == "comprehensive")
-```
-
-The false response rates generated by different parameter combinations ranged from `r min(fr_rates_piecewise$rate)` to `r max(fr_rates_piecewise$rate)` for piecewise integration and from `r min(fr_rates_comprehensive$rate)` to `r max(fr_rates_comprehensive$rate)` for comprehensive integration.
-However, false response rates vary considerably as a function of rare events, indicating that their presence and attractiveness are large determinants of false response rates.
-
-```{r message=FALSE}
-fr_rates %>% 
-  group_by(strategy, boundary, rare) %>% 
-  summarise(min = min(rate),
-            max = max(rate)) %>% 
-  kable()
-```
-
-The heatmaps below show the false response rates for all strategy-parameter combinations.
-Consistent with our - somewhat rough - definition of underweighting, the rate of false risky responses is generally higher, if the unattractive outcome of the risky prospect is rare (top panel).
-Conversely, if the attractive outcome of the risky prospect is rare, the rate of false safe responses is generally higher (bottom panel).
-As indicated by the larger range of false response rates, the effects of rare events are considerably larger for piecewise integration.
-
-```{r message=FALSE}
-fr_rates %>% 
-  filter(strategy == "piecewise", boundary == "absolute") %>% 
-  ggplot(aes(a, s, fill = rate)) + 
-  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
-  geom_tile(colour="white", size=0.25) + 
-  scale_x_continuous(expand=c(0,0), breaks = seq(1, 5, 1)) +
-  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
-  scale_fill_viridis() + 
-  labs(title = "Piecewise Integration | Absolute Boundary",
-       x = "a", 
-       y= "s", 
-       fill = "% False Responses") + 
-  theme_minimal() 
-```
-
-```{r message=FALSE}
-fr_rates %>% 
-  filter(strategy == "piecewise", boundary == "relative") %>% 
-  ggplot(aes(a, s, fill = rate)) + 
-  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
-  geom_tile(colour="white", size=0.25) + 
-  scale_x_continuous(expand=c(0,0), breaks = seq(1, 5, 1)) +
-  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
-  scale_fill_viridis() + 
-  labs(title = "Piecewise Integration | Relative Boundary",
-       x = "a", 
-       y= "s", 
-       fill = "% False Responses") + 
-  theme_minimal() 
-```
-
-```{r message=FALSE}
-fr_rates %>% 
-  filter(strategy == "comprehensive", boundary == "absolute") %>% 
-  ggplot(aes(a, s, fill = rate)) + 
-  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
-  geom_tile(colour="white", size=0.25) + 
-  scale_x_continuous(expand=c(0,0), breaks = seq(15, 75, 15)) +
-  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
-  scale_fill_viridis() + 
-  labs(title = "Comprehensive Integration | Absolute Boundary",
-       x = "a", 
-       y= "s", 
-       fill = "% False Responses") + 
-  theme_minimal() 
-```
-
-```{r message=FALSE}
-fr_rates %>% 
-  filter(strategy == "comprehensive", boundary == "relative") %>% 
-  ggplot(aes(a, s, fill = rate)) + 
-  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
-  geom_tile(colour="white", size=0.25) + 
-  scale_x_continuous(expand=c(0,0), breaks = seq(15, 75, 15)) +
-  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
-  scale_fill_viridis() + 
-  labs(title = "Comprehensive Integration | Relative Boundary",
-       x = "a", 
-       y= "s", 
-       fill = "% False Responses") + 
-  theme_minimal() 
-```
-
-#### Switching Probability (s) and Boundary Value (a)
-
-As for both piecewise and comprehensive integration the differences between boundary types are rather minor and of magnitude than of qualitative pattern, the remaining analyses of false response rates are summarized across absolute and relative boundaries.
-
-Below, the $s$ and $a$ parameter are considered as additional sources of variation in the false response pattern above and beyond the interplay of integration strategies and the rarity and attractiveness of outcomes.
-
-```{r message=FALSE}
-fr_rates %>% 
-  filter(strategy == "piecewise") %>% 
-  ggplot(aes(s, rate, color = a)) + 
-  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
-  geom_jitter(size = 2) + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
-  scale_y_continuous(breaks = seq(0, 1, .1)) +
-  scale_color_viridis() + 
-  labs(title = "Piecewise Integration",
-       x = "s", 
-       y= "% False Responses", 
-       color = "a") + 
-  theme_minimal() 
-```
-
-```{r message=FALSE}
-fr_rates %>% 
-  filter(strategy == "comprehensive") %>% 
-  ggplot(aes(s, rate, color = a)) + 
-  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
-  geom_jitter(size = 2) + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
-  scale_y_continuous(breaks = seq(0, 1, .1)) +
-  scale_color_viridis() + 
-  labs(title = "Comprehensive Integration",
-       x = "s", 
-       y= "% False Responses", 
-       color = "a") + 
-  theme_minimal() 
-```
-
-For piecewise integration, switching probability is naturally related to the size of the samples on which the round-wise comparisons of prospects are based on, with low values of $s$ indicating large samples and vice versa.
-Accordingly, switching probability is positively related to false response rates.
-I.e., the larger the switching probability, the smaller the round-wise sample size and the probability of experiencing a rare event within a given round.
-Because round-wise comparisons are independent of each other and binomial distributions within a given round are skewed for small samples and outcome probabilities [@kolmogorovFoundationsTheoryProbability1950], increasing boundary values do not reverse but rather amplify this relation.
-
-For comprehensive integration, switching probability is negatively related to false response rates, i.e., an increase in $s$ is associated with decreasing false response rates.
-This relation, however, may be the result of an artificial interaction between the $s$ and $a$ parameter.
-Precisely, in the current algorithmic implementation of sampling with a comprehensive integration mechanism, decreasing switching probabilities cause comparisons of prospects based on increasingly unequal sample sizes immediately after switching prospects.
-Consequentially, reaching (low) boundaries is rather a function of switching probability and associated sample sizes than of actual evidence for a given prospect over the other.
-
-### Cumulative Prospect Theory
-
-In the following, we examine the possible relations between the parameters of the *choice-generating* sampling models and the *choice-describing* cumulative prospect theory.
-
-For each distinct strategy-parameter combination, we ran 20 chains of 40,000 iterations each, after a warm-up period of 1000 samples.
-To reduce potential autocorrelation during the sampling process, we only kept every 20th sample (thinning).
-
-```{r}
-# read CPT data
-cols <- list(.default = col_double(),
-             strategy = col_factor(),
-             boundary = col_factor(),
-             parameter = col_factor())
-estimates <- read_csv("data/estimates/estimates_cpt_pooled_goldstein-einhorn-87.csv", col_types = cols)
-```
-
-#### Convergence
-
-```{r}
-gel_92 <- max(estimates$Rhat) # get largest scale reduction factor (Gelman & Rubin, 1992) 
-```
-
-The potential scale reduction factor $\hat{R}$ was $n \leq$ `r round(gel_92, 3)` for all estimates, indicating good convergence.
-
-#### Piecewise Integration
-
-```{r}
-# generate subset of all strategy-parameter combinations (rows) and their parameters (columns)
-curves_cpt <- estimates %>% 
-  select(strategy, s, boundary, a, parameter, mean) %>% 
-  pivot_wider(names_from = parameter, values_from = mean)
-```
-
-##### Weighting function w(p)
-
-We start by plotting the weighting curves for all parameter combinations under piecewise integration.
-
-```{r}
-
-cpt_curves_piecewise <- curves_cpt %>% 
-  filter(strategy == "piecewise") %>% 
-  expand_grid(p = seq(0, 1, .1)) %>% # add vector of objective probabilities
-  mutate(w = round(exp(-delta*(-log(p))^gamma), 2)) # compute decision weights (cf. Prelec, 1998)
-
-# all strategy-parameter combinations
-
-cpt_curves_piecewise %>% 
-  ggplot(aes(p, w)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  labs(title = "Piecewise Integration: Weighting functions",
-       x = "p", 
-       y= "w(p)") + 
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_piecewise %>% 
-  ggplot(aes(p, w)) + 
-  geom_path() +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  facet_wrap(~a) + 
-  labs(title = "Piecewise Integration: Weighting functions",
-       x = "p",
-       y= "w(p)",
-       color = "Switching Probability") + 
-  scale_color_viridis() +
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_piecewise %>% 
-  ggplot(aes(p, w, color = s)) + 
-  geom_path() +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  labs(title = "Piecewise Integration: Weighting functions",
-       x = "p", 
-       y= "w(p)", 
-       color = "Switching Probability") + 
-  scale_color_viridis() +
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_piecewise %>% 
-  ggplot(aes(p, w, color = s)) + 
-  geom_path() +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  facet_wrap(~a) + 
-  labs(title = "Piecewise Integration: Weighting functions",
-       x = "p",
-       y= "w(p)",
-       color = "Switching Probability") + 
-  scale_color_viridis() +
-  theme_minimal() 
-```
-
-##### Value function v(x)
-
-```{r}
-
-cpt_curves_piecewise <- curves_cpt %>% 
-  filter(strategy == "piecewise") %>% 
-  expand_grid(x = seq(0, 20, 2)) %>% # add vector of objective outcomes
-  mutate(v = round(x^alpha, 2)) # compute decision weights (cf. Prelec, 1998)
-
-# all strategy-parameter combinations
-
-cpt_curves_piecewise %>% 
-  ggplot(aes(x, v)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  labs(title = "Piecewise Integration: Value functions",
-       x = "p", 
-       y= "w(p)") + 
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_piecewise %>% 
-  ggplot(aes(x, v, color = s)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  labs(title = "Piecewise Integration: Value functions",
-       x = "p", 
-       y= "w(p)") + 
-  scale_color_viridis() + 
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_piecewise %>% 
-  ggplot(aes(x, v, color = s)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  facet_wrap(~a) + 
-  labs(title = "Piecewise Integration: Value functions",
-       x = "p", 
-       y= "w(p)") + 
-  scale_color_viridis() + 
-  theme_minimal() 
-```
-
-#### Comprehensive Integration
-
-##### Weighting function w(p)
-
-We start by plotting the weighting curves for all parameter combinations under piecewise integration.
-
-```{r}
-
-cpt_curves_comprehensive <- curves_cpt %>% 
-  filter(strategy == "comprehensive") %>% 
-  expand_grid(p = seq(0, 1, .1)) %>% # add vector of objective probabilities
-  mutate(w = round(exp(-delta*(-log(p))^gamma), 2)) # compute decision weights (cf. Prelec, 1998)
-
-# all strategy-parameter combinations
-
-cpt_curves_comprehensive %>% 
-  ggplot(aes(p, w)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  labs(title = "Comprehensive Integration: Weighting functions",
-       x = "p", 
-       y= "w(p)") + 
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_comprehensive %>% 
-  ggplot(aes(p, w)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  labs(title = "Comprehensive Integration: Weighting functions",
-       x = "p", 
-       y= "w(p)") + 
-  facet_wrap(~a) + 
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_comprehensive %>% 
-  ggplot(aes(p, w, color = s)) + 
-  geom_path() +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  labs(title = "Comprehensive Integration: Weighting functions",
-       x = "p", 
-       y= "w(p)", 
-       color = "Switching Probability") + 
-  scale_color_viridis() +
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_comprehensive %>% 
-  ggplot(aes(p, w, color = s)) + 
-  geom_path() +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  facet_wrap(~a) + 
-  labs(title = "Comprehensive Integration: Weighting functions",
-       x = "p",
-       y= "w(p)",
-       color = "Switching Probability") + 
-  scale_color_viridis() +
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_comprehensive %>% 
-  filter(s >= .7) %>% 
-  ggplot(aes(p, w, color = s)) + 
-  geom_path() +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  facet_wrap(~a) + 
-  labs(title = "Comprehensive Integration: Weighting functions",
-       x = "p",
-       y= "w(p)",
-       color = "Switching Probability") + 
-  scale_color_viridis() +
-  theme_minimal() 
-```
-
-##### Value function v(x)
-
-```{r}
-
-cpt_curves_comprehensive <- curves_cpt %>% 
-  filter(strategy == "comprehensive") %>% 
-  expand_grid(x = seq(0, 20, 2)) %>% # add vector of objective outcomes
-  mutate(v = round(x^alpha, 2)) # compute decision weights (cf. Prelec, 1998)
-
-# all strategy-parameter combinations
-
-cpt_curves_comprehensive %>% 
-  ggplot(aes(x, v)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  labs(title = "Comprehensive Integration: Value functions",
-       x = "p", 
-       y= "w(p)") + 
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_comprehensive %>% 
-  ggplot(aes(x, v)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  facet_wrap(~a) + 
-  labs(title = "Comprehensive Integration: Value functions",
-       x = "p", 
-       y= "w(p)") + 
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_comprehensive %>% 
-  ggplot(aes(x, v, color = s)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  labs(title = "Comprehensive Integration: Value functions",
-       x = "p", 
-       y= "w(p)") + 
-  scale_color_viridis() + 
-  theme_minimal() 
-```
-
-```{r}
-cpt_curves_comprehensive %>% 
-  ggplot(aes(x, v, color = s)) + 
-  geom_path(size = .5) +
-  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
-  facet_wrap(~a) + 
-  labs(title = "Comprehensive Integration: Value functions",
-       x = "p", 
-       y= "w(p)") + 
-  scale_color_viridis() + 
-  theme_minimal() 
-```
+[...]
 
@@
 
+[...]
+
 # Conclusion
+
+[...]
 
@@
 
-## Appendix 2: Prospect Test Set
+## Appendix 2: Choice Problems
 
@@
 
+## Appendix 3: Convergence Diagnostics for CPT Parameters
+
+```{r}
+# group level
+
+gel_92 %>% 
+  filter(level == "mu") %>% 
+  ggplot(aes(x = boundary, y = Rhat, fill = s)) +
+  geom_bar(position = "dodge_2", stat = "identity") +
+  scale_fill_scico(palette = "buda") + 
+  scale_x_discrete(name = element_blank()) +
+  scale_y_continuous(breaks = seq(.1, 1.5, .2)) +
+  geom_hline(yintercept = 1, color = "black") +
+  geom_hline(yintercept = 1.1, color = "red", linetype = "dashed") +
+  facet_grid(parameter~a, switch = "y") +
+  labs(y = "Scale Reduction Factor", 
+       fill="Switching Probability") + 
+  theme_minimal()
+
+# agent level
+
+parameters <- c("alpha", "gamma", "delta", "rho")
+for(i in seq_along(parameters)) {
+
+print(gel_92 %>% 
+  filter(level != "mu", parameter == parameters[i]) %>% 
+  ggplot(aes(x = level, y = Rhat, fill = s)) +
+  geom_bar(stat = "identity", position = "dodge_2") +
+  scale_x_discrete(breaks = element_blank(), name = element_blank()) + 
+  scale_y_continuous(breaks = seq(.1, 1.5, .2)) +
+  geom_hline(yintercept = 1, color = "black") +
+  geom_hline(yintercept = 1.1, color = "red", linetype = "dashed") +
+  facet_grid(boundary~a, switch = "y") +
+  labs(title = parameters[i],
+       y = "Scale Reduction Factor", 
+       fill="Switching Probability") + 
+  scale_fill_scico(palette = "buda") + 
+  theme_minimal())
+}
+```
+
+## Appendix 4: False Response Rates
+
+[...]
+
 # References

### 2021-10-02 manuscript.Rmd
Derivation of the Probability Measure over the set of possible outcomes

@@
     toc_float: yes
-    number_sections: no
-  pdf_document:
-    toc: yes
+    fig_width: 10
+    fig_height: 7
 csl: apa.csl
@@
 
-This document was created from the commit with the hash `r repro::current_hash()`.
+This document was created from the commit with the hash ``r repro::current_hash()``
 
@@
 
-[...]
+...
 
@@
 
-where $i = \{1, ..., N\}$ denotes a sequence of length $N$ of random variables that are iid.
+where $i \in \{1, ..., N\}$ denotes a sequence of length $N$ of random variables that are iid.
 
@@
 
-## A Stochastic Sampling Model Capturing Differences in Sampling and Decision Strategies
+## Capturing Differences in Sampling and Decision Strategies
 
@@
 The observed outcome of such an ordinal comparison can be regarded as evidence for or against a prospect and the number of wins over a series of independent ordinal comparisons as accumulated evidence.
-To integrate the concept of evidence accumulation into the current model, we let $D$ be a measurable function
+To integrate the concept of evidence accumulation into the current model, we let the decision variable $D$ be a measurable function
 
@@
 
-It becomes evident that the two combinations of sampling and decision strategies proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010] are reflected in certain restrictions on the free parameters $N_X, N_Y$ and $n$ of the sampling model and that these restrictions translate to the shape of the binomial distribution, straightforwardly via the parameter $n$, more interestingly, however, via its parameter $p$.
+It becomes evident that the two combinations of sampling and decision strategies proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010] are reflected in certain restrictions on the free parameters $N_X, N_Y$ and $n$ of the sampling model and that these restrictions translate to the shape of the binomial distribution associated to the decision variables, straightforwardly via the parameter $n$, more interestingly, however, via its parameter $p$.
 
-I.e., first, whether a single (summary decision) or multiple ordinal comparisons (round-wise decision) are conducted, is reflected by the length of the sequence $D_i = D_1, ..., D_n$ with $n = 1$ for summary decisions and $n \geq 1$ for round-wise decisions.
+I.e., first, whether a single (summary decision) or multiple ordinal comparisons (round-wise decision) are conducted, is reflected by the length of the sequence $D_i = D_1, ..., D_n$, with $n = 1$ for summary decisions and $n \geq 1$ for round-wise decisions.
 The idea that multiple comparisons may be conducted can be formalized by extending the event space $(C, \mathscr{C})$ of a single comparison to its $n$-fold product
@@
 \left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathscr{C}_i \right)
-\; .
+\; ,
 \end{equation}$$
 
-Second, whether comparisons are conducted on the basis of longer sample sequences (comprehensive sampling) or single samples (piecewise sampling) is reflected by the lengths of sample sequences from the same prospect with $N_X, N_Y \geq 1$ for comprehensive sampling and $N_X = N_Y = 1$ for piecewise sampling.
+where $i \in \{1, ..., n\}$ denotes the number of comparisons.
 
-Note that, in order to derive predictions of the choice behavior from the stochastic model, the probability of success $p$ and therefore, necessarily, the probability of each possible outcome $c \in C$ of a mean comparison must be identified.
-Although this can be demonstrated for random variables defined on prospects of the kind considered so far (see [Appendix 1][Appendix 1: Determining the Probability of Success in a Comparison of Sample Means]), it becomes soon intractable with increasing elements in $\Omega$ and growing sequence lengths.
-However, in the following section and a subsequent simulation analysis, we demonstrate that the combinations of sampling and decision strategies and their corresponding parameter values in the stochastic model produce some principle and predictable trends in the choice behavior that can be modeled in the cumulative prospect theory.
+Second, whether comparisons are conducted on the basis of longer sample sequences or single samples is reflected by the lengths of sample sequences from the same prospect with $N_X, N_Y \geq 1$ for comprehensive sampling and $N_X = N_Y = 1$ for piecewise sampling.
+
+Note now that, in order to derive predictions of the choice behavior from the current stochastic model, the full product model
+
+$$\begin{equation}
+\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathscr{C}_i, \bigotimes_{i = 1}^{n} P_i \right)
+\; ,
+\end{equation}$$
+
+including the probability measure $P$, which assigns each $c \in C$, and each $B \in \mathscr{C}$ respectively, a probability, must be identified. 
+Although this can be demonstrated for the random variables considered so far, it becomes rather quickly intractable with increasing elements in $\Omega$ and growing sequence lengths. 
+However, by explicating the above probability measure ([Appendix 1][Appendix 1: Probability Measure Over Sample Mean Comparisons]), it becomes evident that it is largely influenced by the underlying sequence lengths $N_X$ and $N_Y$.
+In the following section and a subsequent simulation analysis, we demonstrate that this influence is of such a form that it produces some principle and predictable trends in the choice behavior that can be modeled in the cumulative prospect theory.
 
@@
 
-[...]
+...
 
-The *switching probability* $s$ is the probability with which agents draw a single sample from the prospect they did not get their most recent single sample from.
+The switching probability $s$ is the probability with which agents draw a single sample from the prospect they did not get their most recent single sample from.
 $s$ is varied between .1 to 1 in increments of .1.
 The two boundary parameters resemble the concept of a decision threshold, i.e., if a prospect reaches a boundary, it is chosen by the synthetic agent.
-The *boundary type* is either the minimum number of comparisons any prospect must win (absolute boundary) or the minimum difference between the number of won comparisons (relative boundary).
-The **boundary value** $a$ is varied between 1 to 5 in increments of 1.
+The boundary type is either the minimum number of comparisons any prospect must win (absolute boundary) or the minimum difference between the number of won comparisons (relative boundary).
+The boundary value $a$ is varied between 1 to 5 in increments of 1.
 
@@
 For each parameter combination of the generating model, 100 synthetic agents are presented with 60 choices problems.
-In sum, 100 (parameter combinations), 100 (agents) x 60 (choices) = 600,000 choices are simulated.
+In sum, 100 (parameter combinations) x 100 (agents) x 60 (choices) = 600,000 choices are simulated.
 We test a set of 2-prospect choice problems, where one of the prospects contains a safe outcome, i.e., $p(\omega) = 1$ and the other two outcomes where all $p(\omega) \neq 1$.
@@
 To omit dominant prospects within a choice problem, outcomes of the safe prospect always fall between both outcomes of the risky prospect.
-Table A1 contains the test set of 60 choice problems [Appendix 2][Appendix 2: Choice Problems], which were sampled from an initial set of 10,000.
+Table A1 in [Appendix 2][Appendix 2: Choice Problems] contains the test set of 60 choice problems, which were sampled from an initial set of 10,000.
 Sampling of gambles was stratified, randomly drawing an equal number of 20 gambles with no, an attractive, and an unattractive rare outcome.
@@
 
-## Plausibility Check: Relationship between Switching Probability and Trial Sample Sizes
+## Plausibility Check: Relationship between Switching Probability and Trial Length
 
@@
 
-The median length of trials, i.e., the number of single samples drawn in trial, generated by different parameter combinations ranged from `r min(trial_length$med)` to `r max(trial_length$med)`.
+The median length of trials, i.e., the number of single samples drawn in a trial, generated by different parameter combinations ranged from `r min(trial_length$med)` to `r max(trial_length$med)`.
 As expected, the scatter plot below shows an inverse relationship between switching probability and trial length.
-I.e., the lower the switching probability, the larger become the sample sequences on which each comparison between prospects is based.  
+I.e., the lower the switching probability, the larger become the sample sequences on which each comparison between prospects is based, which in turn leads to longer trials.  
 This effect is particularly pronounced for low probabilities such that the increase in trial length accelerates as switching probability decreases.
@@
 ## Probability Weighting Function
-
-The following analyses of choice behavior uses the modeling framework of CPT. 
-A non parametric approach, analyzing false response rates, can be found in [Appendix 4][Appendix 4: False Response Rates].
 
@@
   scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) + 
+  scale_x_continuous(breaks = seq(0, 1, .2)) + 
   scale_y_continuous(breaks = seq(0, 2, .2)) +
@@
   scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) + 
+  scale_x_continuous(breaks = seq(0, 1, .2)) + 
   scale_y_continuous(breaks = seq(0, 10, .5)) +
@@
   scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_x_continuous(breaks = seq(0, 1, .2)) +
   scale_y_continuous(breaks = seq(0, 1, .1)) + 
@@
        x ="Experienced Probability",
-       y = "Subjective Experienced Probability", 
-       color="Switching Probability") + 
-  theme_minimal()
-
-cpt_agent_w %>% 
-  ggplot(aes(x = ep, y = w, color = s)) +
-  geom_path() + 
-  scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
-  scale_y_continuous(breaks = seq(0, 1, .1)) + 
-  labs(title = "Probability Weighting Function",
-       x ="Experienced Probability ep",
        y = "Subjective Experienced Probability", 
@@
   scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_x_continuous(breaks = seq(0, 1, .2)) +
   scale_y_continuous(breaks = seq(0, 1, .1)) +
@@
   theme_minimal()
-
-cpt_agent_w %>% 
-  ggplot(aes(x = ep, y = w, color = s)) +
-  geom_path() + 
-  scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
-  scale_y_continuous(breaks = seq(0, 1, .1)) + 
-  facet_wrap(~a, nrow = 2) + 
-  labs(title = "Probability Weighting Function",
-       x ="Experienced Probability ep",
-       y = "Subjective Experienced Probability", 
-       color="Switching Probability") + 
-  theme_minimal()
 ```
@@
 
-[...]
+...
+
+# References
+
+<div id="refs"></div>
 
@@
 
-## Appendix 1: Determining the Probability of Success in a Comparison of Sample Means
+## Appendix 1: Probability Measure Over Sample Mean Comparisons
 
-To proof is that the sequence $D_i = D_1, ..., D_n$ (see [Definition of D][A Stochastic Sampling Model Capturing Differences in Sampling and Decision Strategies]) describes a Bernoulli process with the number of won comparisons following the binomial distribution $\mathcal{B}\left(p(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0), n \right)$ for fixed sequence lengths $N_X$ and $N_Y$.
+To proof is that the sequence $D_i = D_1, ..., D_n$ describes a Bernoulli process with the number of won comparisons following the binomial distribution $\mathcal{B}\left(p(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0), n \right)$ for fixed sequence lengths $N_X$ and $N_Y$.
 
-Therefore we must demonstrate that the probability of success, i.e., $p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right)$, is identified:
+Therefore we must demonstrate that the probability of success, i.e., $p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right)$, is identified.
+The derivation chain is first roughly paraphrased and then formalized as a mathematical equation.
+
+We start by noting that the probability of success equals the probability of the subset $B_1 \in \mathscr{C}$ which contains all comparisons $c \in C$ that satisfy the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
+Since the probability of the subset $B_1$ equals the probability that any of its elements occurs, the probabilities of all $c \in B_1$ are summed up. 
+We therefore use the sum operator with the limits $j \in \{1, ..., |B_1|\}$, with $|B_1|$ denoting the cardinality of the set $B_1$, i.e., the number of elements within the set. 
+As a major assumption is that the random variables within a sample sequence are iid and independent across sequences, the joint probability of a pair $\overline{X}_{N_X} \cap \overline{Y}_{N_Y}$, i.e., a pair $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs, is described by the product of their individual probabilities $p(\overline{X}_{N_X})$ and $p(\overline{Y}_{N_Y})$.
+Finally, to get these individual probabilities, we must determine the probability that each possible realization indeed occurs the respective number of times in the underlying sample sequence.
+This probability is given by the multinomial distribution which reduces to a binomial distribution in the case of only two possible realizations. 
+We denote the number of times a realization occurs in a sample sequence with $k_{\omega}$, where $\omega$ signals that the realizations of the random variables are numerical equivalent to the outcomes in the sample space of the prospects.
 
@@
       & = p \left( \; B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathscr{C} \; \right) \\\\\\ 
-      & = \sum_{c_i=1}^{|B_1|} \left( \;
-          p(\overline{X}_{N_X})  
+      & = \sum_{j=1}^{|B_1|} \left( \;
+          p(\overline{X}_{N_Xj})  
           \times 
-          p(\overline{Y}_{N_Y}) \; 
-        \right)_{c_i \, \in \, B_1} \\\\\\
-      & = \sum_{c_i=1}^{|B_1|} \left( \; 
+          p(\overline{Y}_{N_Yj}) \; 
+        \right)_{j \, \in \, \{1, ..., |B_1|\}} \\\\\\
+      & = \sum_{j=1}^{|B_1|} \left( \; 
         p \left( 
-          \frac{1}{N_X} \sum\limits_{i = 1}^{N_X} X_i(\omega \in \Omega_X)
+          \frac{1}{N_X} \sum\limits_{i = 1}^{N_X} X(\omega \in \Omega_X)_{ij}
         \right) 
@@
         p \left( 
-          \frac{1}{N_Y} \sum\limits_{i = 1}^{N_Y} Y_i(\omega \in \Omega_Y)
+          \frac{1}{N_Y} \sum\limits_{i = 1}^{N_Y} Y(\omega \in \Omega_Y)_{ij}
         \right) \; 
-        \right)_{c_i \, \in \, B_1} \\\\\\
-      & = \sum_{c_i=1}^{|B_1|} \left( \;
+        \right)_{j \, \in \, \{1, ..., |B_1|\}} \\\\\\
+      & = \sum_{j=1}^{|B_1|} \left( \;
         \left(
-          {N_X\choose k_{\omega_{1X}}, ..., k_{\omega_{nX}} } \prod_{\omega_{iX} \in \Omega_X} p(\omega_{iX})^{k_{\omega_{iX}}}
+          {N_X\choose k_{\omega_{1X}j}, ..., k_{\omega_{nX}j}} \prod_{\omega_{iX} \in \Omega_X} p(\omega_{iX})^{k_{\omega_{iX}j}}
         \right)
@@
         \left(
-        {N_Y\choose k_{\omega_{1Y}}, ..., k_{\omega_{nY}} } \prod_{\omega_{iY} \in \Omega_Y} p(\omega_{iY})^{k_{\omega_{iY}}}
+        {N_Y\choose k_{\omega_{1Y}j}, ..., k_{\omega_{nY}j} } \prod_{\omega_{iY} \in \Omega_Y} p(\omega_{iY})^{k_{\omega_{iY}j}}
         \right)
-        \right)_{c_i \, \in \, B_1} \\\\\\
-      & = \sum_{c_i=1}^{|B_1|} \left( \;
+        \right)_{j \, \in \, \{1, ..., |B_1|\}} \\\\\\
+      & = \sum_{j=1}^{|B_1|} \left( \;
         \left(
-          \frac{N_X!}{k_{\omega_{1X}}! \times ... \times k_{\omega_{nX}}!} 
+          \frac{N_X!}{k_{\omega_{1X}j}! \times ... \times k_{\omega_{nX}j}!} 
           \times 
-          p(\omega_{1X})^{k_{\omega_{1X}}} 
+          p(\omega_{1X})^{k_{\omega_{1X}j}} 
           \times 
           ... 
-          \times p(\omega_{nX})^{k_{\omega_{nX}}}
+          \times p(\omega_{nX})^{k_{\omega_{nX}j}}
         \right)
@@
         \left(
-          \frac{N_Y!}{k_{\omega_{1Y}}! \times ... \times k_{\omega_{nY}}!} 
+          \frac{N_Y!}{k_{\omega_{1Y}j}! \times ... \times k_{\omega_{nY}j}!} 
           \times 
-          p(\omega_{1Y})^{k_{\omega_{1Y}}} 
+          p(\omega_{1Y})^{k_{\omega_{1Y}j}} 
           \times 
           ... 
-          \times p(\omega_{nY})^{k_{\omega_{nY}}}
+          \times p(\omega_{nY})^{k_{\omega_{nY}j}}
         \right)
-      \right)_{c_i \, \in \, B_1}
-      \; ,
+      \right)_{j \, \in \, \{1, ..., |B_1|\}}
   \end{split}
 \end{equation}$$
-
-where $|B_1|$ denotes the cardinality of the set $B_1$, $c_i \in B_1$ a pair $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs, and $k$ denotes the number of times $\omega$ was observed within a sequence.
 
@@
 ```
-
-## Appendix 4: False Response Rates
-
-[...]
-
-# References

### 2021-10-02 manuscript.Rmd
Review of Simulation Analysis

@@
 
+The figures below display the estimates of the $\gamma$ and $\delta$ parameter of the probability weighting function [@prelecProbabilityWeightingFunction1998] fitted to DfE simulated for different parameter values of the generating model.
+The estimates are plotted against the switching probability, where each panel represents a distinct boundary type and level, i.e., number of comparisons. 
+Grey dots represent agent level estimates, colored dots represent the mean across all agent level estimates.
+
+Most significantly, there is a strong relationship between the switching probability in the generating model and the $\gamma$ parameter.
+I.e., large switching probabilities, which are indicative for small sample sequences, lead to larger estimates for $\gamma$. 
+The resulting strong curvature leads to a compression of probabilities in the lower and upper range, reflecting underweighting of small probabilities and overweighting of large probabilities. 
+This pattern is robust for varying degrees of the boundary level, except for $a = 1$. 
+The latter deviation may be explained by the potential scale reduction factors for the respective parameter estimates, which indicate that the MCMC chains did not converge (see [Appendix 3][Appendix 3: Convergence Diagnostics for CPT Parameters]).
+
 ```{r}
@@
   geom_jitter(color = "#CECECE" ) + 
-  geom_point(data = cpt_agent_mean, aes(color = s), size = 3) +
+  geom_point(data = cpt_agent_mean, aes(color = s), size = 2) +
   geom_line(data = cpt_agent_mean, aes(color = s), size = 1) +
@@
   geom_jitter(color = "#CECECE") + 
-  geom_point(data = cpt_agent_mean, aes(color = s), size = 3) +
+  geom_point(data = cpt_agent_mean, aes(color = s), size = 2) +
   geom_line(data = cpt_agent_mean, aes(color = s), size = 1) +
@@
   theme_minimal()
+```
 
+Below, the resulting probability weighting functions are displayed.
+
+```{r}
 # weighting function
@@
 ## plot curves
-
 cpt_agent_w %>% 
@@
 
+The false response rates for different parameter values of the generating model reflect the probability weighting patterns from above. 
+That is, the strong curvature resulting from large switching probabilities produces an underweighting of small probabilities.
+This in turn has the effect that the rarity of an attractive (unattractive) outcome leads to higher rates of choosing the safe (risky) prospect although the risky (safe) prospect had a higher experienced expected value.
+
+```{r}
+
+# compute false response rates
+
+fr_rates <- choices %>% 
+  mutate(ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2), # experienced EV (eEV)
+         norm = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) %>% # normative choice according to eEV
+  filter(!is.na(norm)) %>% # exclude trials with normative indifferent prospects
+  group_by(s, boundary, a, rare, norm, choice) %>% # group correct and incorrect responses
+  summarise(n = n()) %>% # absolute numbers 
+  mutate(rate = round(n/sum(n), 2), # response rates 
+         type = case_when(norm == "A" & choice == "B" ~ "false safe", norm == "B" & choice == "A" ~ "false risky")) %>% filter(!is.na(type))  # remove correct responses
+
+fr_rates %>% 
+  ggplot(aes(a, s, fill = rate)) + 
+  geom_tile(colour="white", size=0.1) +
+  scale_fill_scico(palette = "buda") + 
+  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
+  scale_x_continuous(expand=c(0,0), breaks = seq(1, 5, 1)) +
+  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
+  labs(x = "a", 
+       y= "s", 
+       fill = "% False Responses") + 
+  theme_minimal()
+
+fr_rates %>% 
+  ggplot(aes(s, rate, color = s)) + 
+  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
+  geom_jitter(size = 3) + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_y_continuous(breaks = seq(0, 1, .1)) +
+  scale_color_scico(palette = "buda") + 
+  labs(title = "Piecewise Integration",
+       x = "s", 
+       y= "% False Responses", 
+       color = "a") + 
+  theme_minimal()
+```
+
 ## Value Function
 
-...
+The figures below display the estimates of the $\alpha$ and the resulting value function.
+
+```{r}
+
+# alpha
+cpt_agent %>% 
+  ggplot(aes(x = s, y = alpha)) +
+  geom_jitter(color = "#CECECE" ) + 
+  geom_point(data = cpt_agent_mean, aes(color = s), size = 2) +
+  geom_line(data = cpt_agent_mean, aes(color = s), size = 1) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .2)) + 
+  scale_y_continuous(breaks = seq(0, 2, .2)) +
+  facet_grid(boundary~a, switch = "y") +
+  labs(title = expression(alpha),
+       x ="Switching Probability",
+       y = expression(alpha), 
+       color="Switching Probability") + 
+  theme_minimal()
+
+# value function
+
+## compute values
+
+cpt_agent_v <- cpt_agent %>% 
+  select(-c(gamma, delta, rho)) %>% 
+  expand_grid(x = seq(0, 20, 2)) %>%  
+  mutate(v = round(x^alpha, 2))
+
+cpt_agent_mean_v <- cpt_agent %>% 
+  select(-c(gamma, delta, rho)) %>% 
+  group_by(s) %>% 
+  summarise(alpha = round(mean(alpha), 2)) %>% 
+  expand_grid(x = seq(0, 20, 2)) %>%  
+  mutate(v = round(x^alpha, 2))
+
+## plot curves
+cpt_agent_v %>% 
+  ggplot(aes(x = x, y = v)) +
+  geom_path(color = "#CECECE") + 
+  geom_path(data = cpt_agent_mean_v, aes(color = s), size = 1.1) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 20, 5)) +
+  scale_y_continuous(breaks = seq(0, 20, 5)) + 
+  labs(title = "Value Function",
+       x ="Objective Value",
+       y = "Subjective Value", 
+       color="Switching Probability") + 
+  theme_minimal()
+
+## for separate a
+
+cpt_agent_mean_v <- cpt_agent %>% 
+  group_by(s, a) %>% 
+  summarise(alpha = round(mean(alpha), 2)) %>% 
+  expand_grid(x = seq(0, 20, 2)) %>%  
+  mutate(v = round(x^alpha, 2))
+
+cpt_agent_v %>% 
+  ggplot(aes(x = x, y = v)) +
+  geom_path(color = "#CECECE", size = 0.5) + 
+  geom_path(data = cpt_agent_mean_v, aes(color = s), size = 1.1) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 20, 5)) +
+  scale_y_continuous(breaks = seq(0, 20, 5)) + 
+  facet_wrap(~a, nrow = 2) + 
+  labs(title = "Value Function",
+       x ="Objective Value",
+       y = "Subjective Value", 
+       color="Switching Probability") + 
+  theme_minimal()
+```
 

### 2021-10-05 R/estimate_cpt.R
Add files for non-hierarchical estimation of CPT

@@ -1,0 +1,75 @@
+pacman::p_load(tidyverse, R2jags)
+source("R/fun_inits_MCMC.R") # call function creating initial values for MCMC
+
+# read choice data
+cols <- list(.default = col_double(),
+             boundary = col_factor(),
+             gamble = col_factor(),
+             rare = col_factor(),
+             agent = col_factor(),
+             choice = col_factor())
+choices <- read_csv("data/choices/choices.csv", col_types = cols)
+
+# prepare data for JAGS
+
+choices <- choices %>%
+  mutate(choice_A = if_else(choice == "A", 1, 0)) # to apply logit choice rule
+
+# group trials of distinct parameter combinations of the generating model
+params_sim <- choices %>% distinct(s, boundary, a) # to get distinct parameter combinations
+choices_grouped <- vector("list", nrow(params_sim))
+for(set in seq_len(nrow(params_sim))){
+  choices_grouped[[set]] <- choices_cpt %>%
+    filter(s == params_sim[[set, "s"]] & boundary == params_sim[[set, "boundary"]] & a == params_sim[[set, "a"]]) %>%
+    mutate(i = row_number()) # assign trial numbers
+}
+
+# allocate space for JAGS output
+
+estimates_cpt <- vector("list", nrow(params_sim)) # posterior statistics and MCMC diagnostics
+
+# MCMC simulation
+
+params_cpt <- c("alpha", "gamma", "delta", "rho")
+n_chains <- 20
+
+for(set in seq_len(nrow(params_sim))){
+
+  ## get trials of the respective parameter combination
+
+  current_trials <- list(choice = choices_grouped[[set]]$choice_A,
+                         a_o1 = choices_grouped[[set]]$a_o1,
+                         a_o2 = choices_grouped[[set]]$a_o2,
+                         b_o1 = choices_grouped[[set]]$b_o1,
+                         b_o2 = choices_grouped[[set]]$b_o2,
+                         a_p1_exp = choices_grouped[[set]]$a_p1_exp, # use relative frequencies to account for sampling error
+                         a_p2_exp = choices_grouped[[set]]$a_p2_exp,
+                         b_p1 = choices_grouped[[set]]$b_p1,
+                         b_p2 = choices_grouped[[set]]$b_p2,
+                         start = min(choices_grouped[[set]]$i),
+                         stop = max(choices_grouped[[set]]$i))
+
+  ## sample from posterior distributions using MCMC
+
+  current_sample <- jags.parallel(data = current_trials,
+                                  inits = inits_MCMC,
[…]

### 2021-10-05 R/prepare_choices.R

@@ -16,27 +16,30 @@ hash_sim <- digest(simulation, "md5")
 if(hash_sim != "295e1a7b23402dd50a1dae5a54141f78"){
   warning("Mismatch between original and current data!\nCurrent hash is:\n    '", hash_sim, "'")
 }else{
-  cat(green("Data is valid. You can continue."))
+
+  cat(green("Data is valid. Continuing preparation of choice data."))
+
+  ## transform data to obtain trial summaries
+
+  choices <- simulation %>%
+    group_by(s, boundary, a, gamble, agent) %>% # group by trials
+    mutate(n_sample = n(), # total number of single samples
+           n_a = n_sample - sum(is.na(A)), # number of single samples drawn from risky option
+           a_p2_exp = round(sum(if_else(A == a_o2, 1, 0), na.rm = TRUE)/n_a, 2), # experienced probability of higher risky outcome
+           a_p1_exp = round(1 - a_p2_exp, 2), # experienced probability of lower risky outcome
+           a_ev_exp = round(mean(A, na.rm = TRUE), 2), # experienced mean A
+           b_ev_exp = round(mean(B, na.rm = TRUE), 2)) %>%  # experienced mean B
+    ungroup() %>%
+    filter(!is.na(choice)) %>% # discard single samples
+
+    ## tidy data
+
+    mutate(s = 1-(s+.5)) %>%  # to interpret parameter s as switching probability
+    select(s:gamble, rare, a_p1:ev_ratio, agent, n_sample, n_a, a_p1_exp, a_p2_exp, a_ev_exp, b_ev_exp, choice, A_sum, B_sum, diff)
+
+  # save data
+  ## required: 60 gambles x 100 subjects x 100 parameter combinations = 600.000 choices
+  write_csv(choices, "data/choices/choices.csv")
+
 }
 
-## transform data to obtain trial summaries
-
-choices <- simulation %>%
-  group_by(s, boundary, a, gamble, agent) %>% # group by trials
-  mutate(n_sample = n(), # total number of single samples
-         n_a = n_sample - sum(is.na(A)), # number of single samples drawn from risky option
-         a_p2_exp = round(sum(if_else(A == a_o2, 1, 0), na.rm = TRUE)/n_a, 2), # experienced probability of higher risky outcome
-         a_p1_exp = round(1 - a_p2_exp, 2), # experienced probability of lower risky outcome
[…]

### 2021-10-05 R/prepare_estimates.R
Delete needless file

@@ -1,19 +1,0 @@
-pacman::p_load(tidyverse)
-
-# load estimates
-cols <- list(.default = col_double(),
-             boundary = col_factor(),
-             parameter = col_guess())
-cpt <- read_csv("data/estimates/estimates_hierarchical_cpt.csv", col_types = cols)
-
-cpt <- cpt %>% filter(parameter != "deviance")
-
-# separate parameter type from hierarchy level
-cpt <- cpt %>%
-  mutate(parameter = str_replace_all(cpt$parameter, c("\\[" = "_",
-                                                            "\\]" = "",
-                                                            "mu.alpha" = "alpha_mu",
-                                                            "mu.gamma" = "gamma_mu",
-                                                            "mu.delta" = "delta_mu",
-                                                            "mu.rho" = "rho_mu"))) %>% # use uniform separators
-  separate(parameter, c("parameter", "level"), sep = "_") # separate variables into two columns

### 2021-10-05 R/estimate_hierarchical_cpt.R
Delete files of hierarchical estimation

@@ -1,101 +1,0 @@
-pacman::p_load(tidyverse, R2jags)
-source("R/fun_inits_MCMC.R") # call function creating initial values for MCMC
-
-# read choice data
-
-cols <- list(.default = col_double(),
-             boundary = col_factor(),
-             gamble = col_factor(),
-             rare = col_factor(),
-             agent = col_factor(),
-             choice = col_factor())
-choices <- read_csv("data/choices/choices.csv", col_types = cols)
-
-# prepare data for JAGS
-
-choices <- choices %>%
-  mutate(choice_A = if_else(choice == "A", 1, 0)) # to apply logit choice rule
-
-gambles <- choices %>% select(gamble:ev_ratio) %>% distinct()
-n_gambles <- nrow(gambles)
-n_agents <- choices %>% distinct(agent) %>% nrow()
-
-## group trials of distinct strategy-parameter combinations of the generating model
-
-params_sim <- choices %>% distinct(s, boundary, a) # to get distinct strategy-parameter combinations
-params_grouped <- vector("list", nrow(params_sim))
-
-choices_grouped <- vector("list", nrow(params_sim))
-a_p1_exp_grouped <- vector("list", nrow(params_sim))
-a_p2_exp_grouped <- vector("list", nrow(params_sim))
-
-for(set in seq_len(nrow(params_sim))){
-
-  params_grouped[[set]] <- choices %>%
-    filter(s == params_sim[[set, "s"]] & boundary == params_sim[[set, "boundary"]] & a == params_sim[[set, "a"]])
-
-  choices_grouped[[set]] <- params_grouped[[set]] %>%
-    select(gamble, agent, choice_A) %>%
-    pivot_wider(names_from = "agent", values_from = "choice_A", names_prefix = "Ag_") %>%
-    select(-gamble)
-
-  a_p1_exp_grouped[[set]] <- params_grouped[[set]] %>%
-    select(gamble, agent, a_p1_exp) %>%
-    pivot_wider(names_from = "agent", values_from = "a_p1_exp", names_prefix = "Ag_") %>%
-    select(-gamble)
-
-  a_p2_exp_grouped[[set]] <- params_grouped[[set]] %>%
-    select(gamble, agent, a_p2_exp) %>%
-    pivot_wider(names_from = "agent", values_from = "a_p2_exp", names_prefix = "Ag_") %>%
-    select(-gamble)
-}
-
-# allocate space for JAGS output
-
[…]

### 2021-10-05 R/fun_inits_MCMC_hier.R

@@ -1,4 +1,0 @@
-inits_MCMC <- function(){list("mu.alpha.prob" = 1,
-                              "mu.gamma.prob" = 2,
-                              "mu.delta.prob" = 2,
-                              "mu.rho.log" = -0.5)}

### 2021-10-05 R/estimate_cpt.R
Delete old data file

@@ -19,7 +19,7 @@ choices <- choices %>%
 params_sim <- choices %>% distinct(s, boundary, a) # to get distinct parameter combinations
 choices_grouped <- vector("list", nrow(params_sim))
 for(set in seq_len(nrow(params_sim))){
-  choices_grouped[[set]] <- choices_cpt %>%
+  choices_grouped[[set]] <- choices %>%
     filter(s == params_sim[[set, "s"]] & boundary == params_sim[[set, "boundary"]] & a == params_sim[[set, "a"]]) %>%
     mutate(i = row_number()) # assign trial numbers
 }

### 2021-10-07 presentation/slides_modelers-meeting.Rmd
Add slides draft for ARC modeler's meeting

---
title: "Sampling in Decisions from Experience"
subtitle: https://github.com/linushof/sampling-in-dfe
author: "Linus, Veronika & Thorsten"
date: "October 11, 2021"
output:
  beamer_presentation: default
bibliography: references_sampling-in-dfe.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

pacman::p_load(tidyverse, 
               scico)
```

## Project Description

### Starting Ideas

1. Description-experience gap [cf. @wulffMetaanalyticReviewTwo2018]

2. Empirical samples that carry over to cognitive processes

### Core Question

- Does choice behavior reflect different sampling strategies?

## Prospects and Sampling

- Standard paradigm: Choice between 2 or multiple prospects

- *Prospects*: Probability spaces $(\Omega, \mathcal{F}, P)$, where 
$$
\Omega = \{\omega_1, ..., \omega_n\}
$$
and 
$$
P = \{p(\omega_1), ..., p(\omega_n)\}
$$

- *Single sample*: Realization of a random variable:
$$
X(\omega \in \Omega) = x 
$$

- *Sequential sampling*: Generating a sequence of single samples in discrete time: 
$$
X_i = X_1, ..., X_n 
$$

## Difference between DfD and DfE

- Decisions from Description (DfD): Function of symbolical descriptions of prospects:  
$$
D:= f((\Omega_1, \mathcal{F}_1, P_1), ..., (\Omega_k, \mathcal{F}_k, P_k))
$$

- Decisions from Experience (DfE): Function of sample sequences originating from prospects:
$$
D := f(X_{i1}, ..., X_{ik}) 
$$

- $f$ informed by psychological theory and empirical protocols

## Sampling and Decision Strategies

- Hills and Hertwig [-@hillsInformationSearchDecisions2010]: Assumption of a systematic link between sampling and decision strategies

- Sampling strategy: Succession of single samples in a sequence generated from multiple prospects

  + Piecewise: Single samples from **different** prospects 
  + Comprehensive: Single samples from **same** prospect

```{r, echo=FALSE, out.height="40%", out.width="40%", fig.align='center'}
knitr::include_graphics("hills-hertwig_2010_figure-1.png")
```

## Modeling the Assumptions of Hills & Hertwig (2010)

- Consider two prospects $(\Omega_X, \mathcal{F}_X, P_X)$ and $(\Omega_Y, \mathcal{F}_Y, P_Y)$ and the ground model for DfE
$$
D := f(X_i, Y_i) 
$$

- $f$ maps a comparison of $\overline{X}$ and $\overline{Y}$ on the set $\{0, 1\}$, with 0 (1) indicating a lost (won) comparison:
$$
D := f(\overline{X} - \overline{Y}) = 
  \begin{cases}
    1 \quad \text{for} \quad \overline{X} - \overline{Y} > 0 \\
    0 \quad \text{else}. 
  \end{cases} 
$$

- A series of ordinal comparisons $D_i = D_1, ..., D_n$ is a Bernoulli process where the number of won comparisons follows the binomial distribution
$$
D \sim \mathcal{B}\left( p \left(\overline{X} - \overline{Y}> 0\right), n\right)
$$

## Predicting Choices from the Stochastic Model

- $n$ and $p$ of the binomial distribution are influenced by the sampling and decision strategies:

### Comprehensive Sampling and Summary Decisions

- $n = 1$  
- $p$: For $\lim_{N_X, N_Y  \to \infty}$, $p (\overline{X} - \overline{Y}> 0) \approx p (E(X) - E(Y))$ 
- Choices should become *"normative"*, i.e., linear weighting and value function

### Piecewise Sampling and Round-wise Decisions

- $n \geq 1$ and $N_X, N_Y = 1$
- $p$: For $N_X, N_Y = 1$, $p (\overline{X} - \overline{Y} > 0) = p(\omega \in \Omega_X > \omega \in \Omega_Y)$
- Choices depend on probabilities in the mid-range, i.e., S-shaped weighting function and concave value function

## Probability Weighting

```{r}
cols <- list(.default = col_double(),
             boundary = col_factor(),
             a = col_factor(),
             parameter = col_factor())
cpt <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols)

cpt <- cpt %>% 
  select(s, boundary, a, parameter, mean) %>% 
  pivot_wider(names_from = parameter, values_from = mean)

cpt_w <- cpt %>% 
  select(-c(alpha, rho)) %>% 
  expand_grid(ep = seq(0, 1, .1)) %>% #
  mutate(w = round(  (delta * ep^gamma)/ ((delta * ep^gamma)+(1-ep)^gamma), 2))

## plot curves
cpt_w %>% 
  filter(a != 1) %>% 
  group_by(boundary, a, s) %>% 
  ggplot(aes(x = ep, y = w, color = s)) +
  geom_path(size = 1.2) + 
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .2)) +
  scale_y_continuous(breaks = seq(0, 1, .1)) + 
  labs(title = "Probability Weighting Function",
       x ="Experienced Probability",
       y = "Subjective Experienced Probability", 
       color="Switching Probability") + 
  theme_minimal()
```

## False Response Rates

```{r message=FALSE, warning=FALSE}
cols <- list(.default = col_double(),
             boundary = col_factor(),
             gamble = col_factor(),
             rare = col_factor(),
             agent = col_factor(),
             choice = col_factor())
choices <- read_csv("data/choices/choices.csv", col_types = cols)

# compute false response rates

fr_rates <- choices %>% 
  mutate(ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2), # experienced EV (eEV)
         norm = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) %>% # normative choice according to eEV
  filter(!is.na(norm)) %>% # exclude trials with normative indifferent prospects
  group_by(s, boundary, a, rare, norm, choice) %>% # group correct and incorrect responses
  summarise(n = n()) %>% # absolute numbers 
  mutate(rate = round(n/sum(n), 2), # response rates 
         type = case_when(norm == "A" & choice == "B" ~ "false safe", norm == "B" & choice == "A" ~ "false risky")) %>% filter(!is.na(type))  # remove correct responses

fr_rates %>% 
  ggplot(aes(s, rate, color = s)) + 
  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
  geom_jitter(size = 3) + 
  scale_x_continuous(breaks = seq(0, 1, .1)) +
  scale_y_continuous(breaks = seq(0, 1, .1)) +
  scale_color_scico(palette = "buda") + 
  labs(title = "False Response Rates", 
       x = "s", 
       y= "% False Responses", 
       color = "a") + 
  theme_minimal()
```

## Value Function

```{r}
cpt_v <- cpt %>% 
  select(-c(gamma, delta, rho)) %>% 
  expand_grid(x = seq(0, 20, 2)) %>%  
  mutate(v = round(x^alpha, 2))

## plot curves
cpt_v %>% 
  group_by(boundary, a, s) %>% 
  ggplot(aes(x = x, y = v)) +
  geom_path(aes(color = s)) +
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 20, 5)) +
  scale_y_continuous(breaks = seq(0, 20, 5)) + 
  labs(title = "Value Function",
       x ="Objective Value",
       y = "Subjective Value", 
       color="Switching Probability") + 
  theme_minimal()
```

## References

### 2021-10-08 slides_modelers-meeting.Rmd
Move document to main directory

--- 2021-10-07 presentation/slides_modelers-meeting.Rmd
@@
 csl: apa.csl
+editor_options: 
+  chunk_output_type: console
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-
 pacman::p_load(tidyverse, 
-               scico)
+               scico,
+               gridExtra)
 ```
@@
 ## plot curves
-cpt_w %>% 
-  filter(a != 1) %>% 
+curve <- cpt_w %>% 
   group_by(boundary, a, s) %>% 
   ggplot(aes(x = ep, y = w, color = s)) +
-  geom_path(size = 1.2) + 
+  geom_path(size = 1.1) + 
   scale_color_scico(palette = "buda") + 
@@
   scale_y_continuous(breaks = seq(0, 1, .1)) + 
-  labs(title = "Probability Weighting Function",
-       x ="Experienced Probability",
+  labs(x ="Experienced Probability",
        y = "Subjective Experienced Probability", 
@@
   theme_minimal()
+
+gamma <- cpt %>% 
+  group_by(boundary, a) %>% 
+  ggplot(aes(x = s, y = gamma, color = s)) +
+  geom_jitter(size = 3, show.legend = FALSE) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .2)) + 
+  scale_y_continuous(breaks = seq(0, 2, .2)) +
+  labs(title = expression(paste("Curvature ", gamma)),
+       x ="Switching Probability",
+       y = expression(gamma), 
+       color="Switching Probability") + 
+  theme_minimal()
+
+delta <- cpt %>% 
+  ggplot(aes(x = s, y = delta, color = s)) +
+  geom_jitter(size = 3, show.legend = FALSE) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .2)) + 
+  scale_y_continuous(limits = c(0.75, 2.25), breaks = seq(0.75, 2.25, .25)) +
+  labs(title = expression(paste("Elevation ", delta)),
+       x ="Switching Probability",
+       y = expression(delta), 
+       color="Switching Probability") + 
+  theme_minimal()
+
+plot_params <- grid.arrange(gamma, delta, nrow = 2)
+
+grid.arrange(plot_params, curve, nrow = 1)
 ```

### 2021-10-09 slides_modelers-meeting.Rmd
Add results and summary

--- 2021-10-07 presentation/slides_modelers-meeting.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-
 pacman::p_load(tidyverse, 
-               scico)
+               scico,
+               ggpubr)
 ```
@@
 
-- Does choice behavior reflect different sampling strategies?
+- May samples be generated in such a way that they produce systematic choice patterns?
 
@@
 
+## Method
+
+- 60 choices between a 2-outcome prospect and a safe prospect
+- 100 synthetic agents
+- Parameterization of the sampling and decision process
+  + Probability of switching between prospects
+  + Number of comparisons
+- Description of simulated DfE in Cumulative Prospect Theory
+
 ## Probability Weighting
 
-```{r}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 cols <- list(.default = col_double(),
@@
 ## plot curves
+curve_w <- cpt_w %>% 
+  group_by(boundary, a, s) %>% 
+  ggplot(aes(x = ep, y = w, color = s)) +
+  geom_path() + 
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_y_continuous(breaks = seq(0, 1, .1)) + 
+  labs(title = "Probability Weighting", 
+       x ="Experienced Probability p",
+       y = "w(p)", 
+       color="Switching Probability") + 
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="bottom")
+
+gamma <- cpt %>% 
+  group_by(boundary, a) %>% 
+  ggplot(aes(x = s, y = gamma, color = s)) +
+  geom_smooth(data = cpt %>% filter(a != 1), color = "grey") + 
+  geom_jitter(size = 3, show.legend = FALSE) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) + 
+  scale_y_continuous(breaks = seq(0, 2, .2)) +
+  labs(title = expression(gamma),
+       x ="",
+       y = "") + 
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5))
+
+delta <- cpt %>% 
+  ggplot(aes(x = s, y = delta, color = s)) +
+  geom_smooth(data = cpt %>% filter(a != 1), color = "grey") + 
+  geom_jitter(size = 3, show.legend = FALSE) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) + 
+  scale_y_continuous(limits = c(1, 2), breaks = seq(1, 2, .2)) +
+  labs(title = expression(delta),
+       x ="Switching Probability",
+       y = "") + 
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5))
+
+params <- ggarrange(gamma, delta, nrow = 2)
+ggarrange(curve_w, params)
+```
+
+## Probability Weighting: Multiple Comparisons
+
+```{r echo=FALSE}
 cpt_w %>% 
-  filter(a != 1) %>% 
   group_by(boundary, a, s) %>% 
@@
   scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .2)) +
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
   scale_y_continuous(breaks = seq(0, 1, .1)) + 
-  labs(title = "Probability Weighting Function",
-       x ="Experienced Probability",
-       y = "Subjective Experienced Probability", 
+  labs(x ="Experienced Probability p",
+       y = "w(p)", 
        color="Switching Probability") + 
-  theme_minimal()
+  facet_wrap(~a, nrow = 2) +  
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="bottom")
 ```
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 cols <- list(.default = col_double(),
@@
 fr_rates %>% 
-  ggplot(aes(s, rate, color = s)) + 
+  ggplot(aes(s, a, fill = rate)) + 
+  geom_tile(colour="white", size=0.1) +
+  scale_fill_scico(palette = "buda") + 
   facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
-  geom_jitter(size = 3) + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
-  scale_y_continuous(breaks = seq(0, 1, .1)) +
-  scale_color_scico(palette = "buda") + 
-  labs(title = "False Response Rates", 
-       x = "s", 
-       y= "% False Responses", 
-       color = "a") + 
-  theme_minimal()
+  scale_x_continuous(expand=c(0,0), breaks = seq(0, 1, .1)) +
+  scale_y_continuous(expand=c(0,0), breaks = seq(1, 5, 1)) +
+  labs(title = "Type of Rare Event", 
+       x = "Switching Probability", 
+       y= "Number of Comparisons", 
+       fill = "% False Responses") + 
+  theme_minimal() +
+    theme(plot.title = element_text(hjust = 0.5))
 ```
@@
 
-```{r}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 cpt_v <- cpt %>% 
@@
 ## plot curves
-cpt_v %>% 
+curve_v <- cpt_v %>% 
   group_by(boundary, a, s) %>% 
@@
   scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 20, 5)) +
-  scale_y_continuous(breaks = seq(0, 20, 5)) + 
+  scale_x_continuous(breaks = seq(0, 20, 2)) +
+  scale_y_continuous(breaks = seq(0, 20, 2)) + 
   labs(title = "Value Function",
-       x ="Objective Value",
-       y = "Subjective Value", 
+       x ="Objective Value x",
+       y = "v(x)", 
        color="Switching Probability") + 
-  theme_minimal()
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="bottom")
+
+alpha <- cpt %>% 
+  group_by(boundary, a) %>% 
+  ggplot(aes(x = s, y = alpha, color = s)) +
+  geom_smooth(data = cpt %>% filter(a != 1), color = "grey") + 
+  geom_jitter(size = 3, show.legend = FALSE) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) + 
+  scale_y_continuous(breaks = seq(0, 2, .1)) +
+  labs(title = expression(alpha),
+       x ="Switching Probability",
+       y = "") + 
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5))
+
+ggarrange(curve_v, alpha)
 ```
 
+## Value Function: Multiple Comparisons
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+cpt_v %>% 
+  group_by(boundary, a, s) %>% 
+  ggplot(aes(x = x, y = v, color = s)) +
+  geom_path(size = 1.2) + 
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 20, 2)) +
+  scale_y_continuous(breaks = seq(0, 20, 2)) + 
+  labs(x ="Objective Value x",
+       y = "v(x)", 
+       color="Switching Probability") + 
+  facet_wrap(~a, nrow = 2) +  
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="bottom")
+```
+
+## Summary and Q&A
+
+Random processes underlying DfE ...
+
+- ... can be modeled according to probability theory
+
+- ... can be integrated into current decision theories
+
+- ... could be shaped by sampling and decision strategies
+
+- ... could explain empirically observed choice patterns
+
+I happily take your questions, comments and critique.
+
 ## References

### 2021-10-11 slides_modelers-meeting.Rmd
Final version

@@
 
-## Prospects and Sampling
-
-- Standard paradigm: Choice between 2 or multiple prospects
-
-- *Prospects*: Probability spaces $(\Omega, \mathcal{F}, P)$, where 
-$$
-\Omega = \{\omega_1, ..., \omega_n\}
-$$
-and 
-$$
-P = \{p(\omega_1), ..., p(\omega_n)\}
-$$
-
-- *Single sample*: Realization of a random variable:
-$$
-X(\omega \in \Omega) = x 
-$$
-
-- *Sequential sampling*: Generating a sequence of single samples in discrete time: 
-$$
-X_i = X_1, ..., X_n 
-$$
-
 ## Difference between DfD and DfE
 
-- Decisions from Description (DfD): Function of symbolical descriptions of prospects:  
+- Decisions from Description (DfD): Function of symbolical descriptions of prospects (gambles):  
 $$
-D:= f((\Omega_1, \mathcal{F}_1, P_1), ..., (\Omega_k, \mathcal{F}_k, P_k))
+D:= f((\Omega_1, P_1), ..., (\Omega_k, P_k))
 $$
@@
 
-- Consider two prospects $(\Omega_X, \mathcal{F}_X, P_X)$ and $(\Omega_Y, \mathcal{F}_Y, P_Y)$ and the ground model for DfE
-$$
-D := f(X_i, Y_i) 
-$$
-
 - $f$ maps a comparison of $\overline{X}$ and $\overline{Y}$ on the set $\{0, 1\}$, with 0 (1) indicating a lost (won) comparison:
@@
 $$
-
-## Predicting Choices from the Stochastic Model
-
-- $n$ and $p$ of the binomial distribution are influenced by the sampling and decision strategies:
-
-### Comprehensive Sampling and Summary Decisions
-
-- $n = 1$  
-- $p$: For $\lim_{N_X, N_Y  \to \infty}$, $p (\overline{X} - \overline{Y}> 0) \approx p (E(X) - E(Y))$ 
-- Choices should become *"normative"*, i.e., linear weighting and value function
-
-### Piecewise Sampling and Round-wise Decisions
-
-- $n \geq 1$ and $N_X, N_Y = 1$
-- $p$: For $N_X, N_Y = 1$, $p (\overline{X} - \overline{Y} > 0) = p(\omega \in \Omega_X > \omega \in \Omega_Y)$
-- Choices depend on probabilities in the mid-range, i.e., S-shaped weighting function and concave value function
 

### 2021-11-03 manuscript.Rmd
Review of data visualization

--- 2021-10-02 manuscript.Rmd
@@
                knitr, 
+               ggbeeswarm,
                scico # for scientific color palettes
@@
 ```
-
-This document was created from the commit with the hash ``r repro::current_hash()``
-
-# Author Note
-
-All materials of this work in progress can be found on the accompanying GitHub repository: https://github.com/linushof/sampling-in-dfe
-
-- Add information on how to reproduce the project
-
-- Add contact
-
-# Abstract
-
-A probability theoretic definition of prospects and a rough stochastic sampling model for decisions from experience is proposed.
-It is demonstrated how the model can be used a) to explicate assumptions about the sampling and decision strategies that agents may apply and b) to derive predictions about function forms and parameter values that describe the resulting decision behavior.
-Synthetic choice data is simulated and modeled in cumulative prospect theory to test these predictions.
 
@@
 
-## Sampling in Decisions from Experience
+# Sampling in Decisions from Experience
 
 In research on the decision theory, a standard paradigm is the choice between at least two (monetary) prospects.
-Let a prospect be a probability space $(\Omega, \mathscr{F}, P)$.
+Let a prospect be a probability space $(\Omega, \mathcal{F}, P)$.
 $\Omega$ is the sample space
 
-$$\begin{equation}
+$$
 \Omega = \{\omega_1, ..., \omega_n\}
-\end{equation}$$
+$$
 
 containing a finite set of possible outcomes $\omega$, monetary gains and/or losses respectively. 
-$\mathscr{F}$ is the set of all possible subsets of $\Omega$:
+$\mathcal{F}$ is the set of all possible subsets of $\Omega$:
 
-$$\begin{equation}
-\mathscr{F} = \{A_1, A_2, ...\} = \mathscr{P}(\Omega) 
+$$
+\mathcal{F} = \{A_1, A_2, ...\} = \mathcal{P}(\Omega) 
 \; .
-\end{equation}$$
+$$
 
@@
 
-$$\begin{equation}
-P: \mathscr{F} \mapsto [0,1] 
-\end{equation}$$
+$$
+P: \mathcal{F} \mapsto [0,1] 
+$$
 
@@
 
-(1) $X$ is a measurable function $$\begin{equation} X: (\Omega, \mathscr{F})  \mapsto (\Omega', \mathscr{F'}) \; , \end{equation}$$ where $\Omega'$ is a set of real numbered values $X$ can take and $\mathscr{F'}$ is a set of subsets of $\Omega'$.
-I.e., $\Omega$ maps into $\Omega'$ such that correspondingly each subset $A' \in \mathscr{F'}$ has a pre-image $X^{-1}A' \in \mathscr{F}$, which is the set $\{\omega \in \Omega: X(\omega) \in A'\}$ [@kolmogorovFoundationsTheoryProbability1950, p.
+(1) $X$ is a measurable function $$X: (\Omega, \mathcal{F})  \mapsto (\Omega', \mathcal{F'}) \; ,$$ where $\Omega'$ is a set of real numbered values $X$ can take and $\mathcal{F'}$ is a set of subsets of $\Omega'$.
+I.e., $\Omega$ maps into $\Omega'$ such that correspondingly each subset $A' \in \mathcal{F'}$ has a pre-image $X^{-1}A' \in \mathcal{F}$, which is the set $\{\omega \in \Omega: X(\omega) \in A'\}$ [@kolmogorovFoundationsTheoryProbability1950, p.
 21].
@@
 
-$$\begin{equation}
-D:= f((\Omega_1, \mathscr{F}_1, P_1), ..., (\Omega_k, \mathscr{F}_k, P_k))
+$$
+D:= f((\Omega_1, \mathcal{F}_1, P_1), ..., (\Omega_k, \mathcal{F}_k, P_k))
 \;.
-\end{equation}$$
+$$
 
@@
 
-$$\begin{equation}
+$$
 D := f(X_{i1}, ..., X_{ik}) 
 \; ,
-\end{equation}$$
+$$
 
@@
 
-## Capturing Differences in Sampling and Decision Strategies
+# Capturing Differences in Sampling and Decision Strategies
 
@@
 
-Let $X$ and $Y$ be random variables defined on the prospects $(\Omega_X, \mathscr{F}_X, P_X)$ and $(\Omega_Y, \mathscr{F}_Y, P_Y)$.
+Let $X$ and $Y$ be random variables defined on the prospects $(\Omega_X, \mathcal{F}_X, P_X)$ and $(\Omega_Y, \mathcal{F}_Y, P_Y)$.
 
@@
 
-$$\begin{equation}
-\mathscr{C} = \left\{B_1 = \{c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\}, B_2 = \{ c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} \leq 0\}
+$$
+\mathcal{G} = \left\{B_1 = \{c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\}, B_2 = \{ c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} \leq 0\}
 \right\}
-\end{equation}$$
+$$
 
 be a set of subsets of $C$, indicating that comparisons of prospects on the ordinal (rather than on the metric) scale are of primary interest. 
-We denote a single ordinal comparison by the event space $(C, \mathscr{C})$.
+We denote a single ordinal comparison by the event space $(C, \mathcal{G})$.
 The observed outcome of such an ordinal comparison can be regarded as evidence for or against a prospect and the number of wins over a series of independent ordinal comparisons as accumulated evidence.
@@
 
-$$\begin{equation}
+$$
 D: C \mapsto C'
-\end{equation}$$
+$$
 
-that maps the possible outcomes of a mean comparison in $C$ onto a measure space $C' = \{0,1\}$, with $0$ ($1$) indicating a lost (won) comparison:
+that maps the possible outcomes of a mean comparison in $C$ onto a measure space $C' = \{0,1\}$, with $0$ $(1)$ indicating a lost (won) comparison:
 
-$$\begin{equation}
+$$
 D(c \in C) \in C' = 
   \begin{cases}
-    1 & \text{for} & \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\}  \in \mathscr{C} \\
-    0 & \text{else}. 
+    1 \quad \text{for} \quad \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\}  \in \mathcal{G} \\
+    0 \quad \text{else}. 
   \end{cases} 
-\end{equation}$$
+$$
 
@@
 
-$$\begin{equation}
+$$
 D \sim \mathcal{B}\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right) \; ,
-\end{equation}$$
+$$
 
@@
 I.e., first, whether a single (summary decision) or multiple ordinal comparisons (round-wise decision) are conducted, is reflected by the length of the sequence $D_i = D_1, ..., D_n$, with $n = 1$ for summary decisions and $n \geq 1$ for round-wise decisions.
-The idea that multiple comparisons may be conducted can be formalized by extending the event space $(C, \mathscr{C})$ of a single comparison to its $n$-fold product
+The idea that multiple comparisons may be conducted can be formalized by extending the event space $(C, \mathcal{G})$ of a single comparison to its $n$-fold product
 
-$$\begin{equation}
-\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathscr{C}_i \right)
+$$
+\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathcal{G}_i \right)
 \; ,
-\end{equation}$$
+$$
 
@@
 
-$$\begin{equation}
-\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathscr{C}_i, \bigotimes_{i = 1}^{n} P_i \right)
+$$
+\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathcal{G}_i, \bigotimes_{i = 1}^{n} P_i \right)
 \; ,
-\end{equation}$$
+$$
 
-including the probability measure $P$, which assigns each $c \in C$, and each $B \in \mathscr{C}$ respectively, a probability, must be identified. 
+including the probability measure $P$, which assigns each $c \in C$, and each $B \in \mathcal{G}$ respectively, a probability, must be identified. 
 Although this can be demonstrated for the random variables considered so far, it becomes rather quickly intractable with increasing elements in $\Omega$ and growing sequence lengths. 
@@
 
-## Predicting Choice Behavior
+# Predicting Choice Behavior
 
@@
 
-For each distinct strategy-parameter combination, we ran 20 chains of 20,000 iterations each, after a warm-up period of 1000 samples.
+```{r}
+
+# read cpt data
+
+cols <- list(.default = col_double(),
+             boundary = col_factor(),
+             a = col_factor(),
+             parameter = col_factor())
+cpt_long <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols)
+
+# store convergence diagnostics
+
+gel_92 <- cpt_long %>% select(s, boundary, a, parameter, Rhat, n.eff) 
+```
+
+For each distinct parameter combination, we ran 20 chains of 40,000 iterations each, after a warm-up period of 1000 samples.
 To reduce potential autocorrelation during the sampling process, we only kept every 20th sample (thinning).
-Bar plots displaying the potential scale reduction factors $\hat{R}$ [@gelmanInferenceIterativeSimulation1992] of the group and agent level CPT parameters can be found in [Appendix 3][Appendix 3: Convergence Diagnostics for CPT Parameters].
+The potential scale reduction factor $\hat{R}$ [@gelmanInferenceIterativeSimulation1992] was $\leq$ `r round(max(gel_92$Rhat), 3)` for all parameters, indicating good convergence.
+The minimum effective sample size was `r min(gel_92$n.eff)`.
 
@@
   scale_y_continuous(breaks = seq(0, 120, 10)) +
-  labs(x ="Switching Probability",
+  labs(title = "Trial Length", 
+       x ="Switching Probability",
        y = "Median Trial Length", 
@@
 
-# call script for preparing CPT data
+# tidy CPT data: parameters as separate columns
 
-source("R/prepare_estimates.R") 
-gel_92 <- cpt %>% select(s, boundary, a, parameter, level, Rhat) # store scale reduction factor
+cpt_wide <- cpt_long %>% 
+  select(s, boundary, a, parameter, mean) %>% 
+  pivot_wider(names_from = parameter, values_from = mean)
+```
 
-# Tidy: CPT parameters in columns
+The figures below display the estimates of the $\gamma$ and $\delta$ parameter of the probability weighting function [@prelecProbabilityWeightingFunction1998] fitted to DfE simulated for different parameter values of the generating model.
+The estimates are plotted against the switching probability, where each panel represents a distinct boundary type and level, i.e., number of comparisons. 
+Grey dots represent agent level estimates, colored dots represent the mean across all agent level estimates.
 
-cpt <- cpt %>% 
-  select(s, boundary, a, parameter, level, mean) %>% 
-  pivot_wider(names_from = parameter, values_from = mean)
-
-# agent level estimates
-
-cpt_agent <- cpt %>% filter(level != "mu") # agent level estimates
-
-## compute mean across all agent level estimates
-
-cpt_agent_mean <- cpt_agent %>% 
-  group_by(s, boundary, a) %>% 
-  summarise(alpha = round(mean(alpha), 2), 
-            gamma = round(mean(gamma), 2), 
-            delta = round(mean(delta), 2), 
-            rho = round(mean(rho), 2))
-
-# group level estimates
-
-cpt_mu <- cpt %>% filter(level == "mu") # group level posterior means
-```
+Most significantly, there is a strong relationship between the switching probability in the generating model and the $\gamma$ parameter.
+I.e., large switching probabilities, which are indicative for small sample sequences, lead to larger estimates for $\gamma$. 
+The resulting strong curvature leads to a compression of probabilities in the lower and upper range, reflecting underweighting of small probabilities and overweighting of large probabilities. 
+This pattern is robust for varying degrees of the boundary level, except for $a = 1$. 
+The latter deviation may be explained by the potential scale reduction factors for the respective parameter estimates, which indicate that the MCMC chains did not converge (see [Appendix 3][Appendix 3: Convergence Diagnostics for CPT Parameters]).
 
@@
 
-# gamma
+# Density Plot
 
-cpt_agent %>% 
-  ggplot(aes(x = s, y = gamma)) +
-  geom_jitter(color = "#CECECE" ) + 
-  geom_point(data = cpt_agent_mean, aes(color = s), size = 3) +
-  geom_line(data = cpt_agent_mean, aes(color = s), size = 1) +
+cpt_long %>% 
+  filter(parameter == "gamma" | parameter == "delta") %>% 
+  ggplot(aes(x = s, y = mean)) +
+  geom_density_2d_filled(contour_var = "ndensity") + 
+  scale_fill_scico_d(palette = "buda") +
+  scale_x_continuous(breaks = seq(0, 1, .2)) + 
+  scale_y_continuous(limits = c(0,2), breaks = seq(0, 2, .2)) +
+  labs(x ="Switching Probability",
+       y = "Parameter Value",  
+       fill="Density") + 
+  facet_grid(parameter~a) + 
+  theme_minimal()
+```
+
+```{r eval=FALSE, include=FALSE}
+
+# Scatter Plots
+
+# Gamma
+
+cpt_wide %>% 
+  ggplot(aes(x = s, y = gamma, color = s)) +
+  geom_point(size = 2) +
+  geom_line(size = 1) +
   scale_color_scico(palette = "buda") + 
@@
   scale_y_continuous(breaks = seq(0, 2, .2)) +
-  facet_grid(boundary~a, switch = "y") +
+  facet_grid(boundary~a) +
   labs(title = expression(paste("Curvature ", gamma)),
@@
 
-# delta
+# Delta
 
-cpt_agent %>% 
-  ggplot(aes(x = s, y = delta)) +
-  geom_jitter(color = "#CECECE") + 
-  geom_point(data = cpt_agent_mean, aes(color = s), size = 3) +
-  geom_line(data = cpt_agent_mean, aes(color = s), size = 1) +
+cpt_wide %>% 
+  ggplot(aes(x = s, y = delta, color = s)) +
+  geom_point(size = 2) +
+  geom_line(size = 1) +
   scale_color_scico(palette = "buda") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) + 
-  scale_y_continuous(breaks = seq(0, 10, .5)) +
+  scale_y_continuous(breaks = seq(0, 2, .2)) +
   facet_grid(boundary~a, switch = "y") +
-  labs(title = expression(paste("Elevation ", delta)),
+  labs(title = expression(paste("Curvature ", delta)),
        x ="Switching Probability",
@@
   theme_minimal()
+```
 
-# weighting function
+Below, the resulting probability weighting functions are displayed.
+
+```{r}
+
+# Weighting Functions
 
@@
 
-cpt_agent_w <- cpt_agent %>% 
+cpt_w <- cpt_wide %>% 
   select(-c(alpha, rho)) %>% 
   expand_grid(ep = seq(0, 1, .1)) %>% #
-  mutate(w = round(exp(-delta*(-log(ep))^gamma), 2))
-
-cpt_agent_mean_w <- cpt_agent %>% 
-  group_by(s) %>% 
-  summarise(gamma = round(mean(gamma), 2), 
-            delta = round(mean(delta), 2)) %>% 
-  expand_grid(ep = seq(0, 1, .1)) %>%
-  mutate(w = round(exp(-delta*(-log(ep))^gamma), 2))
+  mutate(w = round(  (delta * ep^gamma)/ ((delta * ep^gamma)+(1-ep)^gamma), 2))
 
@@
 
-cpt_agent_w %>% 
-  ggplot(aes(x = ep, y = w)) +
-  geom_path(color = "#CECECE") + 
-  geom_path(data = cpt_agent_mean_w, aes(color = s), size = 1.1) +
+cpt_w %>% 
+  group_by(boundary, a, s) %>% 
+  ggplot(aes(x = ep, y = w, color = s)) +
+  geom_path() + 
   scale_color_scico(palette = "buda") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +
-  scale_y_continuous(breaks = seq(0, 1, .1)) + 
-  labs(title = "Probability Weighting Function",
-       x ="Experienced Probability",
-       y = "Subjective Experienced Probability", 
+  scale_y_continuous(breaks = seq(0, 1, .2)) + 
+  labs(x ="Experienced Probability",
+       y = "Probability Weighting", 
        color="Switching Probability") + 
@@
 
-## for separate a
-
-cpt_agent_mean_w <- cpt_agent %>% 
-  group_by(s, a) %>% 
-  summarise(gamma = round(mean(gamma), 2), 
-            delta = round(mean(delta), 2)) %>% 
-  expand_grid(ep = seq(0, 1, .1)) %>%
-  mutate(w = round(exp(-delta*(-log(ep))^gamma), 2))
-
-cpt_agent_w %>% 
-  ggplot(aes(x = ep, y = w)) +
-  geom_path(color = "#CECECE") + 
-  geom_path(data = cpt_agent_mean_w, aes(color = s), size = 1.1) +
+cpt_w %>% 
+  group_by(boundary, a, s) %>% 
+  ggplot(aes(x = ep, y = w, color = s)) +
+  geom_path() + 
   scale_color_scico(palette = "buda") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +
+  scale_y_continuous(breaks = seq(0, 1, .2)) + 
+  facet_wrap(~a) +
+  labs(x ="Experienced Probability",
+       y = "Probability Weighting", 
+       color="Switching Probability") + 
+  theme_minimal()
+```
+
+The false response rates for different parameter values of the generating model reflect the probability weighting patterns from above. 
+That is, the strong curvature resulting from large switching probabilities produces an underweighting of small probabilities.
+This in turn has the effect that the rarity of an attractive (unattractive) outcome leads to higher rates of choosing the safe (risky) prospect although the risky (safe) prospect had a higher experienced expected value.
+
+```{r}
+
+# compute false response rates
+
+fr_rates <- choices %>% 
+  mutate(ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2), # experienced EV (eEV)
+         norm = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) %>% # normative choice according to eEV
+  filter(!is.na(norm)) %>% # exclude trials with normative indifferent prospects
+  group_by(s, boundary, a, rare, norm, choice) %>% # group correct and incorrect responses
+  summarise(n = n()) %>% # absolute numbers 
+  mutate(rate = round(n/sum(n), 2), # response rates 
+         type = case_when(norm == "A" & choice == "B" ~ "false safe", norm == "B" & choice == "A" ~ "false risky")) %>% filter(!is.na(type))  # remove correct responses
+
+# violin scatter plot
+
+fr_rates %>% 
+  ggplot(aes(x = rare, y = rate, color = s)) +
+  geom_quasirandom(aes(shape = type), size = 3) +  
+  scale_y_continuous(breaks = seq(0, 1, .2)) +
+  scale_color_scico(palette = "buda") + 
+  scale_shape_manual(values=c(8, 16))+
+  labs(x = "Rare Event", 
+       y = "False Response Rate", 
+       color = "Switching Probability",
+       shape = "False Response") + 
+  theme_minimal() 
+```
+
+```{r eval=FALSE, include=FALSE}
+fr_rates %>% 
+  ggplot(aes(a, s, fill = rate)) + 
+  geom_tile(colour="white", size=0.1) +
+  scale_fill_scico(palette = "buda") + 
+  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
+  scale_x_continuous(expand=c(0,0), breaks = seq(1, 5, 1)) +
+  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
+  labs(title = "False Response Rates", 
+       x = "a", 
+       y= "s", 
+       fill = "% False Responses") + 
+  theme_minimal()
+
+fr_rates %>% 
+  ggplot(aes(s, rate, color = s)) + 
+  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
+  geom_jitter(size = 3) + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
   scale_y_continuous(breaks = seq(0, 1, .1)) +
-  facet_wrap(~a, nrow = 2) + 
-  labs(title = "Probability Weighting Function",
-       x ="Experienced Probability",
-       y = "Subjective Experienced Probability", 
-       color="Switching Probability") + 
+  scale_color_scico(palette = "buda") + 
+  labs(title = "False Response Rates", 
+       x = "s", 
+       y= "% False Responses", 
+       color = "a") + 
   theme_minimal()
@@
 
-...
+```{r}
+
+# Density Plot
+
+cpt_wide %>%
+  ggplot(aes(x = s, y = alpha)) +
+  geom_density_2d_filled(contour_var = "ndensity") + 
+  scale_fill_scico_d(palette = "buda") +
+  scale_x_continuous(breaks = seq(0, 1, .2)) + 
+  scale_y_continuous(limits = c(0,2), breaks = seq(0, 2, .2)) +
+  labs(x ="Switching Probability",
+       y = "Parameter Value",  
+       fill="Density") + 
+  facet_wrap(~a, nrow = 1) + 
+  theme_minimal()
+```
+
+```{r}
+# value function
+
+## compute values
+
+cpt_v <- cpt_wide %>% 
+  select(-c(gamma, delta, rho)) %>% 
+  expand_grid(x = seq(0, 20, 2)) %>%  
+  mutate(v = round(x^alpha, 2))
+
+## plot curves
+
+cpt_v %>% 
+  group_by(boundary, a, s) %>% 
+  ggplot(aes(x = x, y = v)) +
+  geom_path(aes(color = s)) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 20, 5)) +
+  scale_y_continuous(breaks = seq(0, 20, 5)) + 
+  labs(title = "Value Function",
+       x ="Objective Value",
+       y = "Subjective Value", 
+       color="Switching Probability") + 
+  theme_minimal()
+
+cpt_v %>% 
+  group_by(boundary, a, s) %>% 
+  ggplot(aes(x = x, y = v)) +
+  geom_path(aes(color = s)) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 20, 5)) +
+  scale_y_continuous(breaks = seq(0, 20, 5)) + 
+  facet_wrap(~a) +
+  labs(title = "Value Function",
+       x ="Objective Value",
+       y = "Subjective Value", 
+       color="Switching Probability") + 
+  theme_minimal()
+```
+
+```{r eval=FALSE, include=FALSE}
+
+# alpha
+cpt_wide %>% 
+  ggplot(aes(x = s, y = alpha, color = s)) +
+  geom_point(size = 2) +
+  geom_line(size = 1) +
+  scale_color_scico(palette = "buda") + 
+  scale_x_continuous(breaks = seq(0, 1, .2)) + 
+  scale_y_continuous(breaks = seq(0, 2, .2)) +
+  facet_grid(boundary~a, switch = "y") +
+  labs(title = expression(alpha),
+       x ="Switching Probability",
+       y = expression(alpha), 
+       color="Switching Probability") + 
+  theme_minimal()
+
+```
 
@@
 ...
+
+# Acknowledgements
 
@@
 
-We start by noting that the probability of success equals the probability of the subset $B_1 \in \mathscr{C}$ which contains all comparisons $c \in C$ that satisfy the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
+We start by noting that the probability of success equals the probability of the subset $B_1 \in \mathcal{G}$ which contains all comparisons $c \in C$ that satisfy the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
 Since the probability of the subset $B_1$ equals the probability that any of its elements occurs, the probabilities of all $c \in B_1$ are summed up. 
@@
 
-$$\begin{equation}
+$$
   \begin{split}
     p(D = 1) 
-      & = p \left( \; B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathscr{C} \; \right) \\\\\\ 
+      & = p \left( \; B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathcal{G} \; \right) \\\\\\ 
       & = \sum_{j=1}^{|B_1|} \left( \;
@@
   \end{split}
-\end{equation}$$
+$$
 
@@
 ```
-
-## Appendix 3: Convergence Diagnostics for CPT Parameters
-
-```{r}
-# group level
-
-gel_92 %>% 
-  filter(level == "mu") %>% 
-  ggplot(aes(x = boundary, y = Rhat, fill = s)) +
-  geom_bar(position = "dodge_2", stat = "identity") +
-  scale_fill_scico(palette = "buda") + 
-  scale_x_discrete(name = element_blank()) +
-  scale_y_continuous(breaks = seq(.1, 1.5, .2)) +
-  geom_hline(yintercept = 1, color = "black") +
-  geom_hline(yintercept = 1.1, color = "red", linetype = "dashed") +
-  facet_grid(parameter~a, switch = "y") +
-  labs(y = "Scale Reduction Factor", 
-       fill="Switching Probability") + 
-  theme_minimal()
-
-# agent level
-
-parameters <- c("alpha", "gamma", "delta", "rho")
-for(i in seq_along(parameters)) {
-
-print(gel_92 %>% 
-  filter(level != "mu", parameter == parameters[i]) %>% 
-  ggplot(aes(x = level, y = Rhat, fill = s)) +
-  geom_bar(stat = "identity", position = "dodge_2") +
-  scale_x_discrete(breaks = element_blank(), name = element_blank()) + 
-  scale_y_continuous(breaks = seq(.1, 1.5, .2)) +
-  geom_hline(yintercept = 1, color = "black") +
-  geom_hline(yintercept = 1.1, color = "red", linetype = "dashed") +
-  facet_grid(boundary~a, switch = "y") +
-  labs(title = parameters[i],
-       y = "Scale Reduction Factor", 
-       fill="Switching Probability") + 
-  scale_fill_scico(palette = "buda") + 
-  theme_minimal())
-}
-```

### 2021-11-27 manuscript.Rmd
Use papaja package to format the document as APA7 style manuscript

@@
 ---
-title: 'Sampling Strategies in Decisions from Experience'
-author: "Linus Hof, Thorsten Pachur, Veronika Zilker"
-bibliography: references_sampling-in-dfe.bib
-output:
-  html_document:
-    code_folding: hide
-    toc: yes
-    toc_float: yes
-    fig_width: 10
-    fig_height: 7
-csl: apa.csl
-editor_options: 
-  markdown: 
-    wrap: sentence
-  chunk_output_type: console
+title             : "Sampling Strategies in Decisions from Experience"
+shorttitle        : "Sampling in Decisions from Experience"
+
+header-includes: 
+  - \renewcommand\author[1]{}
+  - \renewcommand\affiliation[1]{}
+  - \authorsnames[1, 2, 2]{Linus Hof, Thorsten Pachur, Veronika Zilker}
+  - \authorsaffiliations{{Department of Psychology, Heidelberg University}, {Center for Adaptive Rationality, Max Planck Institute for Human Development}}
+
+author: 
+  - name          : "Linus Hof"
+    affiliation   : "1"
+    corresponding : yes    
+    address       : "Department of Psychology, Heidelberg University, Hauptstraße 47-51, 69117 Heidelberg, Germany"
+    email         : "linushof@posteo.de"
+    role:
+      - Conceptualization
+      - Methodology
+      - Formal Analysis
+      - Visualization
+      - Software
+      - Validation
+      - Writing---original draft
+  - name          : "Thorsten Pachur"
+    role:
+      - Conceptualization
+      - Methodology
+      - Supervision
+  - name          : "Veronika Zilker" 
+    role:
+      - Conceptualization
+      - Methodology
+      - Supervision
+
+note: | 
+  Unsubmitted draft
+
+authornote: |
+ This is a dynamic document which can be reproduced from the accompanying GitHub repository: https://github.com/linushof/sampling-in-dfe.
+This version was created from the commit with the hash ``r repro::current_hash()``.
+
+abstract: |
+  Add abstract
+
+keywords          : ""
+wordcount         : ""
+
+bibliography      : ["references_sampling-in-dfe.bib"]
+csl               : apa.csl
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : no
+linkcolor         : "blue"
+mask              : no
+draft             : no
+
+classoption       : "man"
+documentclass     : "apa7"
+output            : papaja::apa6_pdf
 ---
@@
 
-# Introduction
-
 ...
-
-# Sampling in Decisions from Experience
 
@@
   geom_density_2d_filled(contour_var = "ndensity") + 
+  geom_density_2d(contour_var = "ndensity") +
   scale_fill_scico_d(palette = "buda") +
+  scale_color_scico_d(palette = "buda") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) + 

### 2021-12-06 manuscript.Rmd
Start introduction text

--- 2021-11-03 manuscript.Rmd
@@
 ---
-title: 'Sampling Strategies in Decisions from Experience'
-author: "Linus Hof, Thorsten Pachur, Veronika Zilker"
-bibliography: references_sampling-in-dfe.bib
-output:
-  html_document:
-    code_folding: hide
-    toc: yes
-    toc_float: yes
-    fig_width: 10
-    fig_height: 7
-csl: apa.csl
-editor_options: 
-  markdown: 
-    wrap: sentence
-  chunk_output_type: console
+title             : "Sampling Strategies in Decisions from Experience"
+shorttitle        : "Sampling in Decisions from Experience"
+
+header-includes: 
+  - \renewcommand\author[1]{}
+  - \renewcommand\affiliation[1]{}
+  - \authorsnames[1]{Linus Hof}
+  - \authorsaffiliations{{Department of Psychology, Heidelberg University}}
+
+author: 
+  - name          : "Linus Hof"
+    affiliation   : "1"
+    corresponding : yes    
+    address       : "Department of Psychology, Heidelberg University, Hauptstraße 47-51, 69117 Heidelberg, Germany"
+    email         : "linushof@posteo.de"
+
+note: | 
+  **Unsubmitted draft created from the commit with the hash**: ``r repro::current_hash()``
+
+authornote: |
+ This is a dynamic document which can be reproduced from the accompanying GitHub repository: https://github.com/linushof/sampling-in-dfe.
+
+ The current version of this manuscript is prepared for submission as a master's thesis. A modified later version might be prepared together with co-authors and submitted for peer-review.
+
+abstract: |
+  Add abstract
+
+keywords          : ""
+wordcount         : ""
+
+bibliography      : ["references_sampling-in-dfe.bib"]
+csl               : apa.csl
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : no
+linkcolor         : "blue"
+mask              : no
+draft             : no
+
+classoption       : "man"
+documentclass     : "apa7"
+output            : papaja::apa6_pdf
 ---
@@
                ggbeeswarm,
-               scico # for scientific color palettes
-               )
+               scico, # for scientific color palettes
+               papaja)
 ```
 
-# Introduction
+<!-- Computational level -->
 
-...
+Decision making is an information-processing problem whose solution requires a selection among choice alternatives. 
+The basic structure of the problem may be modeled by the inclusion map $\iota : A' \mapsto A$, indicating that decision making is a *process* that starts from an initial set $A$, including all choice alternatives, and stops at a proper subset $A' \subset A$, only including the chosen alternatives.
+Given that this selection process is systematic---as opposed to random---the chosen alternatives in $A'$ possess the same *property* or combination of several properties which the other alternatives in the complementary subset $A \setminus A'$ do not possess.
+We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
 
-# Sampling in Decisions from Experience
+<!-- Algorithmic Level -->
+
+Thus, a rather important part---although by far not the only one---of the computation that connects the initial set with its subset is the comparison of the properties of the choice alternatives against some selection criteria.
+At the algorithmic level, such comparisons require an explicit description of the properties using a representation system which is useful to the processing system, i.e., a living organism or a computer [@marrRepresentationRecognitionSpatial1978; @marrVisionComputationalInvestigation1982].
+In quite many cases, however, the selection process is not restricted to one particular representation system but a number of different representations can be used to describe the properties of a given set of choice alternatives.
+E.g., an important difference that has emerged in behavioral decision research is whether the probability of a risky outcome is readily described as a decimal number, ratio, or percentage or whether it must be inferred from the relative frequency of occurrence of the particular outcome in a collection of random variables [@hertwigDescriptionexperienceGapRisky2009].
+
+<!-- Samples as representation -->
 
@@
 
-```{r message=FALSE}
+```{r fig.cap="Test"}
 
@@
        color="Switching Probability") + 
-  theme_minimal()
+  theme_apa()
 ```
@@
 
-```{r}
+```{r fig.cap="test 2"}
 
@@
   scale_fill_scico_d(palette = "buda") +
+  scale_color_scico_d(palette = "buda") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) + 
@@
   facet_grid(parameter~a) + 
-  theme_minimal()
+  theme_apa()
 ```
@@
   theme_minimal()
-
 ```
@@
 
-...
-
 # Conclusion
-
-...
-
-# Acknowledgements
 
@@
 <div id="refs"></div>
+
+# Software
 
@@
 gambles <- read_csv("data/gambles/sr_subset.csv")
-gambles %>% kable()
+gambles %>% apa_table()
 ```

### 2021-12-08 manuscript.Rmd
Review set theoretic considerations in the Introduction

@@
 abstract: |
-  Add abstract
+  Add short abstract.
 
@@
 Decision making is an information-processing problem whose solution requires a selection among choice alternatives. 
-The basic structure of the problem may be modeled by the inclusion map $\iota : A' \mapsto A$, indicating that decision making is a *process* that starts from an initial set $A$, including all choice alternatives, and stops at a proper subset $A' \subset A$, only including the chosen alternatives.
-Given that this selection process is systematic---as opposed to random---the chosen alternatives in $A'$ possess the same *property* or combination of several properties which the other alternatives in the complementary subset $A \setminus A'$ do not possess.
+The basic structure of the problem may be modeled by the inclusion map $\iota : A' \mapsto A$, where $\iota(a) = a$ for all $a \in A'$, indicating that decision making is a *process* that starts from an initial set $A$, including all choice alternatives, and stops at a proper subset $A' \subset A$, including only the chosen alternatives.
+Given that the selection process is systematic---as opposed to random---the chosen alternatives in $A'$ should possess the same *property* or combination of several properties which the other alternatives in the complementary subset $A \setminus A'$ do not possess.
 We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
+
+Now, consider the power set $\cal{P}(A)$, which is the set of all possible subsets of $A$.
+Each of the subsets $A' \in \cal{P}(A)$ corresponds to a possible distinction between choice alternatives that can be made after assessing for each alternative whether it fulfills the selection criteria or not [@jostMathematicalConcepts2015, p.
+16].
+The concept of the power set thereby illustrates in a primitive way how different selection criteria can affect the consequential choice, provided the properties that can be captured and manipulated by a particular processing system, i.e., a living organism or a computer, are not uniformly distributed among the alternatives.
 
@@
 
-Thus, a rather important part---although by far not the only one---of the computation that connects the initial set with its subset is the comparison of the properties of the choice alternatives against some selection criteria.
-At the algorithmic level, such comparisons require an explicit description of the properties using a representation system which is useful to the processing system, i.e., a living organism or a computer [@marrRepresentationRecognitionSpatial1978; @marrVisionComputationalInvestigation1982].
-In quite many cases, however, the selection process is not restricted to one particular representation system but a number of different representations can be used to describe the properties of a given set of choice alternatives.
-E.g., an important difference that has emerged in behavioral decision research is whether the probability of a risky outcome is readily described as a decimal number, ratio, or percentage or whether it must be inferred from the relative frequency of occurrence of the particular outcome in a collection of random variables [@hertwigDescriptionexperienceGapRisky2009].
+A rather important part---though by far not the only one---of the computation that connects the initial set with its subset is the comparison of the properties of the choice alternatives against some selection criteria.
+At the algorithmic level [cf.
+@marrVisionComputationalInvestigation1982], such comparisons require an explicit description of the properties using a representation system which is useful to the processing system, i.e., a living organism or a computer [@marrRepresentationRecognitionSpatial1978].
+In quite many cases, however, the selection process is not restricted to one particular representation system but a number of different representations can be used to describe the properties of choice alternatives in a given set.
+Yet, not every representation system permits the description of a given property.
+E.g., a consequential difference that has emerged in behavioral decision research is whether the probability of a risky outcome is readily described, i.e., as a decimal number (.2), ratio (2/10), or percentage (20%), or whether it must be inferred from the relative frequency of occurrence of the particular outcome in a collection of i.i.d.
+random variables [@hertwigDescriptionexperienceGapRisky2009].
+Whereas all four representation systems can in principal be used to describe the probabilities of given outcomes, only the representation which uses collections of random variables can, for example, plausibly produce wavy recency effects due to the perception of spurious temporal outcome patterns [@plonskyRelianceSmallSamples2015; @plonskyLearningSettingsPartial2017].
+Although a discrete-time collection of i.i.d.
+random variables cannot, by definition, exhibit temporal regularity in the sequence of sampled outcomes, spurious temporal patterns might nevertheless be regarded as a property of choice alternatives and affect the consequential decision behavior in a way that would not be possible in other representation systems.
+The reason is simply that such a (spurious) property could not emerge in the other representations.
+
+The preceding example illustrates how some properties can be described in one representation but not in another and how representation systems can differ with regards to the processing effort required to describe the same property.
+Thus, there is generally a trade-off between different representation systems, where in a given representation certain properties become explicit while others are pushed into the background [@marrVisionComputationalInvestigation1982, p.
+21].
+
+<!-- In the same vein, there is a call for *representational pluralism* in cognition research [@griffithsProbabilisticModelsCognition2010] -->
 

### 2021-12-09 manuscript.Rmd
Review of Introduction

@@
 Now, consider the power set $\cal{P}(A)$, which is the set of all possible subsets of $A$.
-Each of the subsets $A' \in \cal{P}(A)$ corresponds to a possible distinction between choice alternatives that can be made after assessing for each alternative whether it fulfills the selection criteria or not [@jostMathematicalConcepts2015, p.
+Each of the subsets $A' \in \cal{P}(A)$ corresponds to a possible distinction between choice alternatives that can be made after assessing for each alternative whether it fulfills the selection criteria or not [cf.
+@jostMathematicalConcepts2015, p.
 16].
@@
 
-A rather important part---though by far not the only one---of the computation that connects the initial set with its subset is the comparison of the properties of the choice alternatives against some selection criteria.
-At the algorithmic level [cf.
-@marrVisionComputationalInvestigation1982], such comparisons require an explicit description of the properties using a representation system which is useful to the processing system, i.e., a living organism or a computer [@marrRepresentationRecognitionSpatial1978].
-In quite many cases, however, the selection process is not restricted to one particular representation system but a number of different representations can be used to describe the properties of choice alternatives in a given set.
-Yet, not every representation system permits the description of a given property.
-E.g., a consequential difference that has emerged in behavioral decision research is whether the probability of a risky outcome is readily described, i.e., as a decimal number (.2), ratio (2/10), or percentage (20%), or whether it must be inferred from the relative frequency of occurrence of the particular outcome in a collection of i.i.d.
-random variables [@hertwigDescriptionexperienceGapRisky2009].
-Whereas all four representation systems can in principal be used to describe the probabilities of given outcomes, only the representation which uses collections of random variables can, for example, plausibly produce wavy recency effects due to the perception of spurious temporal outcome patterns [@plonskyRelianceSmallSamples2015; @plonskyLearningSettingsPartial2017].
+A rather important part---though by far not the only one---of the computation that connects the initial set with its subset is then the comparison of the properties of the choice alternatives against some selection criteria.
+At the algorithmic level, such a comparison requires an explicit description of the properties using a *representation* which is useful to the processing system [cf.
+@marrVisionComputationalInvestigation1982].
+In quite many cases, however, a number of different representations can be used to describe the properties of choice alternatives in a given set.
+Yet, not every representation permits an accurate description of a given property at reasonable expenses or allows to describe a property at all [cf. @marrRepresentationRecognitionSpatial1978].
+E.g., a consequential difference that has emerged in behavioral research on risky choice is whether the probability of a risky outcome is described using a decimal number (.2), ratio (2/10), or percentage (20%), or whether it must be inferred from the relative frequency of occurrence of the particular outcome in a collection of independent and identically distributed (i.i.d.) random variables, i.e., a *random sample*.
+Noteworthy, for the latter case, which is usually referred to as *decisions from experience*, empirical protocols indicate that people decide as if they were underweighting small probability events [@barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004].
+One undisputed factor that contributes to this underweighting pattern is the sampling error associated with people's reliance on small samples [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018 for a meta-analytic review], indicating that, although the probabilities of outcomes can in principle be accurately described in decisions from experience, the actual description is rather inaccurate because it cannot be done at reasonable expenses.
+
+Another property of choice alternatives that is likely to play a role in risky choice but can only be made explicit using a sample representation as in decisions from experience is the sequence in which outcomes occur.
 Although a discrete-time collection of i.i.d.
-random variables cannot, by definition, exhibit temporal regularity in the sequence of sampled outcomes, spurious temporal patterns might nevertheless be regarded as a property of choice alternatives and affect the consequential decision behavior in a way that would not be possible in other representation systems.
-The reason is simply that such a (spurious) property could not emerge in the other representations.
+random variables cannot, by definition, exhibit temporal regularity, i.e., it cannot produce a stable sequence of sampled outcomes, spurious temporal patterns might nevertheless be regarded as a property of choice alternatives and affect the consequential choice behavior.
+Indeed, the underweighting pattern and other behavioral phenomena like the wavy recency effect and probability matching, are reasonably well captured by models which incorporate the assumption that people rely on (spurious) outcome sequences [@cohenEffectPerceivedPatterns2021; @gaissmaierSmartPotentialProbability2008; @plonskyRelianceSmallSamples2015; @plonskyLearningSettingsPartial2017;  @yuSequentialEffectsSupersition2009].
 
-The preceding example illustrates how some properties can be described in one representation but not in another and how representation systems can differ with regards to the processing effort required to describe the same property.
-Thus, there is generally a trade-off between different representation systems, where in a given representation certain properties become explicit while others are pushed into the background [@marrVisionComputationalInvestigation1982, p.
+The preceding two examples illustrate how some properties of choice alternatives can be described in one representation but not in another and how representations can differ with regards to the processing effort required to describe the same property.
+Thus, there is generally a trade-off between different representations, where in a given representation certain properties become explicit while others are pushed into the background [@marrVisionComputationalInvestigation1982, p.
 21].

### 2021-12-10 manuscript.Rmd
Change thesis title

@@
 ---
-title             : "Sampling Strategies in Decisions from Experience"
-shorttitle        : "Sampling in Decisions from Experience"
+title             : "Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation"
+shorttitle        : "Sampling strategies in decisions from experience"
 

### 2021-12-19 manuscript.Rmd
Introduction

--- 2021-12-09 manuscript.Rmd
@@
 ---
-title             : "Sampling Strategies in Decisions from Experience"
-shorttitle        : "Sampling in Decisions from Experience"
+title             : "Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation"
+shorttitle        : "Sampling strategies"
 
@@
 
+<!-- Introduction -->
+
+Any cognitive system operates on information inputs from an environment or memory. 
+Often, however, these inputs do not readily describe the *properties* that the operating system uses to produce meaningful outputs. 
+To obtain useful descriptions of the properties of interest, it is rather required to make inferences from incomplete or noisy inputs, and the feasibility and ease of these inferences is partly determined by how the inputs are represented.
+
+<!-- The way shape information is organized by a representation.
+Different information/properties require different organizations of the inputs ...
+some information may be costly to obtain in a certain representaion ...
+-->
+
+<!--- Still introduction: Problems/Issues of property induction carry over to the decision making process; "I argue that statement" -->
+
 <!-- Computational level -->
@@
 The basic structure of the problem may be modeled by the inclusion map $\iota : A' \mapsto A$, where $\iota(a) = a$ for all $a \in A'$, indicating that decision making is a *process* that starts from an initial set $A$, including all choice alternatives, and stops at a proper subset $A' \subset A$, including only the chosen alternatives.
-Given that the selection process is systematic---as opposed to random---the chosen alternatives in $A'$ should possess the same *property* or combination of several properties which the other alternatives in the complementary subset $A \setminus A'$ do not possess.
+Given that the selection process is systematic---as opposed to random---the chosen alternatives in $A'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $A \setminus A'$ do not possess.
 We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
@@
 16].
-The concept of the power set thereby illustrates in a primitive way how different selection criteria can affect the consequential choice, provided the properties that can be captured and manipulated by a particular processing system, i.e., a living organism or a computer, are not uniformly distributed among the alternatives.
+The concept of the power set thereby illustrates in a primitive way how different selection criteria can affect the consequential choice, provided the properties that can be captured and manipulated by a particular processing system, i.e., a living organism or a computer, are not uniformly distributed among the alternatives [cf.
+@kempStructuredStatisticalModels2009].
 

### 2021-12-19 manuscript.Rmd
Update introduction

@@
 Often, however, these inputs do not readily describe the *properties* that the operating system uses to produce meaningful outputs. 
-To obtain useful descriptions of the properties of interest, it is rather required to make inferences from incomplete or noisy inputs, and the feasibility and ease of these inferences is partly determined by how the inputs are represented.
-
-<!-- The way shape information is organized by a representation.
-Different information/properties require different organizations of the inputs ...
-some information may be costly to obtain in a certain representaion ...
--->
+To obtain useful descriptions of the properties of interest, it is rather required to make inferences from incomplete or noisy inputs.
+Yet, the feasibility and ease of these inferences depends on how the inputs are represented, since the *representation* determines the information that is made explicit and the costs at which certain operations can be carried out [@marrVisionComputationalInvestigation1982].
+For example, probabilistic models of cognition suggest that qualitatively different assumptions about how people may represent input information are required to capture their inferences in different inductive contexts [@griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
 
@@
 A rather important part---though by far not the only one---of the computation that connects the initial set with its subset is then the comparison of the properties of the choice alternatives against some selection criteria.
-At the algorithmic level, such a comparison requires an explicit description of the properties using a *representation* which is useful to the processing system [cf.
+At the algorithmic level, such a comparison requires an explicit description of the properties using a representation which is useful to the processing system [cf.
 @marrVisionComputationalInvestigation1982].

### 2021-12-20 manuscript.Rmd
Update introduction

--- 2021-12-10 manuscript.Rmd
@@
 title             : "Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation"
-shorttitle        : "Sampling strategies in decisions from experience"
+shorttitle        : "Sampling strategies"
 
@@
 
+<!-- Introduction -->
+
+Any cognitive system operates on information inputs from an environment or memory. 
+Often, however, these inputs do not readily describe the *properties* that the operating system uses to control the output. 
+To obtain useful descriptions of the properties of interest, it is rather required to make inferences from incomplete or noisy inputs.
+Since how the input is represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information [@marrVisionComputationalInvestigation1982], the feasibility and ease of these inferences depends greatly on the choice of *representation*.
+For example, probabilistic models of cognition suggest that a broad range of different assumptions about how people may structurally represent input information are required to capture their inferences about the extensions of novel properties in different inductive contexts [@griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
+Hence, to explain the operations that turn an input into an output, one needs to understand the properties that control the output, the representation that is used by the cognitive system to describe these properties, and the costs of making the descriptions in that representation, including their susceptibility to distortions from noise or uncertainty.
+
 <!-- Computational level -->

### 2021-12-21 manuscript.Rmd
Update introduction

@@
 
-Any cognitive system operates on information inputs from an environment or memory. 
-Often, however, these inputs do not readily describe the *properties* that the operating system uses to control the output. 
-To obtain useful descriptions of the properties of interest, it is rather required to make inferences from incomplete or noisy inputs.
-Since how the input is represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information [@marrVisionComputationalInvestigation1982], the feasibility and ease of these inferences depends greatly on the choice of *representation*.
-For example, probabilistic models of cognition suggest that a broad range of different assumptions about how people may structurally represent input information are required to capture their inferences about the extensions of novel properties in different inductive contexts [@griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
-Hence, to explain the operations that turn an input into an output, one needs to understand the properties that control the output, the representation that is used by the cognitive system to describe these properties, and the costs of making the descriptions in that representation, including their susceptibility to distortions from noise or uncertainty.
+The mind is a cognitive system that operates on inputs from an environment or memory.
+Such inputs may be treated as a set *I* and its elements, the latter being distinguishable from each other on the basis of the *properties* they possess [cf. @jostMathematicalConcepts2015].
+Often, however, the properties that the mind uses to control the output are not readily described, but must be inferred from incomplete or noisy information. 
+Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982; see also @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
+Hence, to explain how the mind turns certain inputs into meaningful outputs, one needs to understand the properties that control the output, the representation that is used to describe these properties, and the costs of making the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
+
+In what follows, the discussion will turn to the domain of decision making and elaborate on the concepts touched upon thus far, however, primarily to illustrate one rather important point:
+Given that the properties of choice alternatives serve as *selection criteria*, the more accurately these properties are described, the more systematic the choices should become.
+Importantly, this principle is not restricted to any specific property, but rather does the choice pattern reflect the bias that the designation of a property as a selection criterion imposes on the assessment of choice alternatives.
 
@@
 Decision making is an information-processing problem whose solution requires a selection among choice alternatives. 
-The basic structure of the problem may be modeled by the inclusion map $\iota : A' \mapsto A$, where $\iota(a) = a$ for all $a \in A'$, indicating that decision making is a *process* that starts from an initial set $A$, including all choice alternatives, and stops at a proper subset $A' \subset A$, including only the chosen alternatives.
-Given that the selection process is systematic---as opposed to random---the chosen alternatives in $A'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $A \setminus A'$ do not possess.
+The basic structure of the problem may be modeled by the inclusion map $\iota : I' \mapsto I$, where $\iota(i) = i$ for all $i \in I'$, indicating that decision making is a *process* that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
+Given that the selection process is systematic---as opposed to random---the chosen alternatives in $I'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
 We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
 
-Now, consider the power set $\cal{P}(A)$, which is the set of all possible subsets of $A$.
-Each of the subsets $A' \in \cal{P}(A)$ corresponds to a possible distinction between choice alternatives that can be made after assessing for each alternative whether it fulfills the selection criteria or not [cf.
+Now, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$.
+Each of the subsets $A' \in \mathcal{P}(I)$ corresponds to a possible distinction between choice alternatives that can be made after assessing for each alternative whether it fulfills the selection criteria or not [cf.
 @jostMathematicalConcepts2015, p.

### 2021-12-22 manuscript.Rmd
Update introduction

@@
 The mind is a cognitive system that operates on inputs from an environment or memory.
-Such inputs may be treated as a set *I* and its elements, the latter being distinguishable from each other on the basis of the *properties* they possess [cf. @jostMathematicalConcepts2015].
+Such inputs may be treated as a set $I$ and its elements, the latter being distinguishable from each other on the basis of the *properties* they possess [cf. @jostMathematicalConcepts2015].
 Often, however, the properties that the mind uses to control the output are not readily described, but must be inferred from incomplete or noisy information. 
@@
 
-In what follows, the discussion will turn to the domain of decision making and elaborate on the concepts touched upon thus far, however, primarily to illustrate one rather important point:
-Given that the properties of choice alternatives serve as *selection criteria*, the more accurately these properties are described, the more systematic the choices should become.
-Importantly, this principle is not restricted to any specific property, but rather does the choice pattern reflect the bias that the designation of a property as a selection criterion imposes on the assessment of choice alternatives.
+In what follows, the discussion will turn to the domain of decision making and elaborate on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate one rather important mechanism:
+Given that the properties of choice alternatives serve as *selection criteria* and the mind is indeed sensitive to variations in their values, the more accurately these properties are described, the more systematic the choices should become.
+Importantly, this principle is not restricted to any one specific property, but rather does the choice pattern reflect the bias that the designation of a property as a selection criterion imposes on the assessment of choice alternatives.
 

### 2021-12-22 manuscript.Rmd
Update introduction

@@
 
+As the discussion proceeds and for the sake of example, I argue that a choice pattern robustly emerging in so-called *decisions from experience* (DfE), i.e., the underweighting of small probability events, may be due to the constraints set by a certain selection criterion.
+Considering in some detail *sampling strategies* as input representations used to describe the property of interest, I illustrate that if the sample size increases and thereby uncertainty is reduced, property induction should become more accurate and underweighting more pronounced.
+Interestingly, this prediction diverges from the common theme that an increase in the sample size will reduce the underweighting. 
+The sampling and decision process are mathematically formalized and implemented into a computational model to simulate choice data [cf.
+@guestHowComputationalModeling2021; @haslbeckModelingPsychopathologyData2021].
+Simulation data is analyzed using descriptive statistics and cumulative prospect theory (CPT) as a commonly used data model [@tverskyAdvancesProspectTheory1992; @goldsteinExpressionTheoryPreference1987].
+All simulations and analyses are reproducible---materials and instructions can be found on the accompanying GitHub repository.
+
+# Header
 <!-- Computational level -->
@@
 Given that the selection process is systematic---as opposed to random---the chosen alternatives in $I'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
-We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
+We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as selection criteria.
 

### 2021-12-23 manuscript.Rmd
Finished Draft Introduction

--- 2021-12-22 manuscript.Rmd
@@
 Such inputs may be treated as a set $I$ and its elements, the latter being distinguishable from each other on the basis of the *properties* they possess [cf. @jostMathematicalConcepts2015].
-Often, however, the properties that the mind uses to control the output are not readily described, but must be inferred from incomplete or noisy information. 
+Often, however, the properties used by the mind to control the outputs are not readily described, but proper descriptions must be inferred from incomplete or noisy information. 
 Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982; see also @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
-Hence, to explain how the mind turns certain inputs into meaningful outputs, one needs to understand the properties that control the output, the representation that is used to describe these properties, and the costs of making the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
+Hence, to explain how the mind turns certain inputs into meaningful outputs, one needs to understand the properties that control the output, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
 
 In what follows, the discussion will turn to the domain of decision making and elaborate on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate one rather important mechanism:
-Given that the properties of choice alternatives serve as *selection criteria* and the mind is indeed sensitive to variations in their values, the more accurately these properties are described, the more systematic the choices should become.
-Importantly, this principle is not restricted to any one specific property, but rather does the choice pattern reflect the bias that the designation of a property as a selection criterion imposes on the assessment of choice alternatives.
+Given that the properties of choice alternatives serve as *selection criteria* and the mind is indeed sensitive to variations in their values, the more accurately the descriptions of these properties are inferred, the more systematic the choices should become.
+Importantly, this principle is not restricted to any one specific property, but rather does the choice pattern result from the constraints that the designation of a property as a selection criterion imposes on the assessment of choice alternatives.
+
+As the discussion proceeds and for the sake of example, I argue that a choice pattern robustly emerging in so-called *decisions from experience* (DfE), i.e., the apparent underweighting of small probability events, may be caused by the assessment constraints associated with a round-wise decision rule.
+This particular argument has already been made by @hillsInformationSearchDecisions2010, however, decision rules, as I try to explain below, are for several reasons better formulated as selection criteria whose descriptions are rarely restricted to one representation.
+Considering *sampling strategies* as representations used to describe the properties of interest in DfE, I illustrate how the inferred descriptions of these properties indeed become more accurate with increasing sample sizes.
+Yet, caused by the selection criterion corresponding to the round-wise decision rule, the underweighting pattern is a priori predicted to become more pronounced in such a case. 
+This prediction is different from the relatively undisputed explanation that underweighting is caused by the reliance on small samples and the skewness of the binomial distribution, indicating that the effects of sample size on underweighting are conditional on the selection criterion.
+I will elaborate on this matter as I proceed, however, to be rather clear from the outset, what the mind does in neither case is performing an underweighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level.
+
+The theoretical argument is substantiated by a simulation study [cf. @guestHowComputationalModeling2021]. 
+For this purpose, the sampling and decision processes are expressed mathematically and implemented in a computational model.
+Choice data from DfE is simulated and modeled using cumulative prospect theory (CPT), a data model commonly used for describing decisions under risk and uncertainty [@tverskyAdvancesProspectTheory1992].
+All simulations and analyses are reproducible---materials and instructions can be found on the accompanying GitHub repository.
+
+# Heading Section 1
 
@@
 
-<!-- In the same vein, there is a call for *representational pluralism* in cognition research [@griffithsProbabilisticModelsCognition2010] -->
+# Heading Section 2
 
@@
 
-# Capturing Differences in Sampling and Decision Strategies
+## Subheading: Capturing Differences in Sampling and Decision Strategies
 
@@
 
-# Predicting Choice Behavior
+## Subheading: Predicting Choice Behavior
 
@@
 
-# Method
-
-## Generating Model
+# Simulation Study
 
@@
 
-## Describing Model: Cumulative Prospect Theory
+## Results
 
@@
 
-# Results
-
-## Plausibility Check: Relationship between Switching Probability and Trial Length
+### Plausibility Check: Relationship between Switching Probability and Trial Length
 
@@
 
-## Probability Weighting Function
+### Probability Weighting Function
 
@@
 
-## Value Function
+### Value Function
 
@@
 
-# Discussion
-
-# Conclusion
+# Discussion and Conclusion
 
@@
 <div id="refs"></div>
-
-# Software
 

### 2021-12-28 manuscript.Rmd
Change YAML to put captions above figur / include figures 1 and 2

@@
 shorttitle        : "Sampling strategies"
-
-header-includes: 
-  - \renewcommand\author[1]{}
-  - \renewcommand\affiliation[1]{}
-  - \authorsnames[1]{Linus Hof}
-  - \authorsaffiliations{{Department of Psychology, Heidelberg University}}
 
@@
 
-floatsintext      : yes
 figurelist        : no
@@
 output            : papaja::apa6_pdf
+
+header-includes:
+   - \usepackage[capposition=top]{floatrow}
+   - \renewcommand\author[1]{}
+   - \renewcommand\affiliation[1]{}
+   - \authorsnames[1]{Linus Hof}
+   - \authorsaffiliations{{Department of Psychology, Heidelberg University}}
 ---
@@
 The mind is a cognitive system that operates on inputs from an environment or memory.
-Such inputs may be treated as a set $I$ and its elements, the latter being distinguishable from each other on the basis of the *properties* they possess [cf. @jostMathematicalConcepts2015].
+Such inputs may be treated as a set $I$ and its elements $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess [cf. @jostMathematicalConcepts2015].
 Often, however, the properties used by the mind to control the outputs are not readily described, but proper descriptions must be inferred from incomplete or noisy information. 
@@
 Hence, to explain how the mind turns certain inputs into meaningful outputs, one needs to understand the properties that control the output, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
+The process is schematically shown in Figure 1.
+\
+
+(ref:figure1) A sketch of the structure of information processing.
+To turn inputs into meaningful outputs, the mind is required to describe the relevant properties before they can be evaluated.
+Descriptions are inferred from the inputs using a representation.
+
+```{r fig.cap="(ref:figure1)", fig.align='left'}
+knitr::include_graphics("manuscript_files/figure-png/figure1.png")
+```
 
@@
 Given that the properties of choice alternatives serve as *selection criteria* and the mind is indeed sensitive to variations in their values, the more accurately the descriptions of these properties are inferred, the more systematic the choices should become.
-Importantly, this principle is not restricted to any one specific property, but rather does the choice pattern result from the constraints that the designation of a property as a selection criterion imposes on the assessment of choice alternatives.
+Importantly, this principle is not restricted to any one specific property, but rather does a characteristic choice pattern result from the constraints that the designation of a property as a selection criterion imposes on the assessment of choice alternatives.
 
@@
 This particular argument has already been made by @hillsInformationSearchDecisions2010, however, decision rules, as I try to explain below, are for several reasons better formulated as selection criteria whose descriptions are rarely restricted to one representation.
-Considering *sampling strategies* as representations used to describe the properties of interest in DfE, I illustrate how the inferred descriptions of these properties indeed become more accurate with increasing sample sizes.
-Yet, caused by the selection criterion corresponding to the round-wise decision rule, the underweighting pattern is a priori predicted to become more pronounced in such a case. 
-This prediction is different from the relatively undisputed explanation that underweighting is caused by the reliance on small samples and the skewness of the binomial distribution, indicating that the effects of sample size on underweighting are conditional on the selection criterion.
-I will elaborate on this matter as I proceed, however, to be rather clear from the outset, what the mind does in neither case is performing an underweighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level.
+Considering *sampling strategies* as representations used to describe the properties of interest in DfE, I illustrate how the inferred descriptions of properties indeed become more accurate with increasing sample sizes.
+Yet, caused by the selection criterion corresponding to a round-wise decision rule, the underweighting pattern is a priori predicted to become more pronounced in such a case. 
+This prediction is different from the explanation that underweighting is partly caused by the reliance on small samples and the skewness of the binomial distribution [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009], indicating that the effects of sample size on the choice pattern are conditional on the selection criterion.
+I will elaborate on this matter as I proceed, however, to be rather clear from the outset, what the mind does in neither case is performing an underweighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [cf.
+@griffithsRationalUseCognitive2015].
 
-The theoretical argument is substantiated by a simulation study [cf. @guestHowComputationalModeling2021]. 
-For this purpose, the sampling and decision processes are expressed mathematically and implemented in a computational model.
+The theoretical argument is supported by a simulation study. 
+For this purpose, the sampling and decision making processes are expressed mathematically and implemented in a computational model.
 Choice data from DfE is simulated and modeled using cumulative prospect theory (CPT), a data model commonly used for describing decisions under risk and uncertainty [@tverskyAdvancesProspectTheory1992].
-All simulations and analyses are reproducible---materials and instructions can be found on the accompanying GitHub repository.
+All simulations and analyses are reproducible---materials and instructions can be found on the GitHub repository.
 
-# Heading Section 1
-
-<!-- Computational level -->
+# The Decision Making Process and the Properties of Choice Alternatives
 
@@
 The basic structure of the problem may be modeled by the inclusion map $\iota : I' \mapsto I$, where $\iota(i) = i$ for all $i \in I'$, indicating that decision making is a *process* that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
-Given that the selection process is systematic---as opposed to random---the chosen alternatives in $I'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
+Given that the selection is systematic---as opposed to random---the chosen alternatives in $I'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
 We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as selection criteria. 
+I.e., with regards to a given selection criteria, all chosen alternatives are equal to each other but different from the non-chosen alternatives.
 
-Now, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$.
-Each of the subsets $A' \in \mathcal{P}(I)$ corresponds to a possible distinction between choice alternatives that can be made after assessing for each alternative whether it fulfills the selection criteria or not [cf.
+Now, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).
+Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that can be made after assessing for each alternative whether it fulfills the selection criteria or not [cf.
 @jostMathematicalConcepts2015, p.
 16].
-The concept of the power set thereby illustrates in a primitive way how different selection criteria can affect the consequential choice, provided the properties that can be captured and manipulated by a particular processing system, i.e., a living organism or a computer, are not uniformly distributed among the alternatives.
+The concept of the power set thereby illustrates in a plain way how different selection criteria can alter the consequential choice, provided the properties are not uniformly distributed among the alternatives.
+\
 
-<!-- Algorithmic Level -->
+(ref:figure2) The power set of the set $I$ including the choice alternatives A, B, and C.
+Black (white) circles indicate that an alternative does (not) possess a property.
+Each column displays a possible subset that could result from assessing whether the alternatives posses a relevant property.
+
+```{r fig.cap="(ref:figure2)", fig.align='left'}
+knitr::include_graphics("manuscript_files/figure-png/figure2.png")
+```
 
@@
 Yet, not every representation permits an accurate description of a given property at reasonable expenses or allows to describe a property at all [cf. @marrRepresentationRecognitionSpatial1978].
+
 E.g., a consequential difference that has emerged in behavioral research on risky choice is whether the probability of a risky outcome is described using a decimal number (.2), ratio (2/10), or percentage (20%), or whether it must be inferred from the relative frequency of occurrence of the particular outcome in a collection of independent and identically distributed (i.i.d.) random variables, i.e., a *random sample*.
-Noteworthy, for the latter case, which is usually referred to as *decisions from experience*, empirical protocols indicate that people decide as if they were underweighting small probability events [@barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004].
+Noteworthy, for the latter case, which is usually referred to as decisions from experience, empirical protocols indicate that people decide as if they were underweighting small probability events [@barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004].
 One undisputed factor that contributes to this underweighting pattern is the sampling error associated with people's reliance on small samples [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018 for a meta-analytic review], indicating that, although the probabilities of outcomes can in principle be accurately described in decisions from experience, the actual description is rather inaccurate because it cannot be done at reasonable expenses.
@@
 
-# Heading Section 2
+# Sampling Strategies
 

### 2021-12-29 manuscript.Rmd
Update Section 2

@@
 The mind is a cognitive system that operates on inputs from an environment or memory.
-Such inputs may be treated as a set $I$ and its elements $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess [cf. @jostMathematicalConcepts2015].
-Often, however, the properties used by the mind to control the outputs are not readily described, but proper descriptions must be inferred from incomplete or noisy information. 
-Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982; see also @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
+Such inputs may be treated as a set $I$ and its elements $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess [@jostMathematicalConcepts2015, p.
+1].
+Often, however, the properties used by the mind to control the outputs are not readily described, but proper descriptions must be inferred from the available information. 
+Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982, p.
+21; see also @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
 Hence, to explain how the mind turns certain inputs into meaningful outputs, one needs to understand the properties that control the output, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
@@
 16].
-The concept of the power set thereby illustrates in a plain way how different selection criteria can alter the consequential choice, provided the properties are not uniformly distributed among the alternatives.
+The concept of the power set thereby illustrates in a plain way how different selection criteria can alter the consequential choice, provided the properties are not uniformly distributed among the alternatives and the mind is sensitive to whatever relations the alternatives have with each other.
 \
@@
 Each column displays a possible subset that could result from assessing whether the alternatives posses a relevant property.
+The properties determine the various relations among the choice alternatives.
+Note that properties resulting in the empty set $\{\}$ and the subset $\{A,B,C\}$ do not discriminate between choice alternatives.
 
@@
 
-A rather important part---though by far not the only one---of the computation that connects the initial set with its subset is then the comparison of the properties of the choice alternatives against some selection criteria.
-At the algorithmic level, such a comparison requires an explicit description of the properties using a representation which is useful to the processing system [cf.
-@marrVisionComputationalInvestigation1982].
+Using Marr's [-@marrVisionComputationalInvestigation1982] framework, the sensitivity aspect addresses the algorithmic level and refers to the achievement that the true properties of the choice alternatives are accurately described and the resulting relations among the alternatives are properly evaluated [cf.
+@brunswikOrganismicAchievementEnvironmental1943].
+Note that if the descriptions of the relevant properties were available, the process sketched out in Figure 1 would be substantially simplified since the two intermediate steps of representation and property description would be omitted.
+For quite many decisions the mind faces, however, it is simply not the case that the properties of interest, e.g., outcome probabilities, are readily described and amenable to direct assessment, as has been repeatedly stated [e.g., @busemeyerChoiceBehaviorSequential1982; @fiedlerBewareSamplesCognitiveecological2000; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; see also @brunswikRepresentativeDesignProbabilistic1955; @brunswikPerceptionRepresentativeDesign1956, for a detailed treatment].
+In such cases, to obtain the respective descriptions from the inputs, the mind is required to make an inference from the available information.
+
+impose a proper organization on them, with the rules for doing so determined by the representation [cf.
+@marrVisionComputationalInvestigation1982; @marrRepresentationRecognitionSpatial1978], or it must make an inference from incomplete information, or both.
+Consider a prospect $P$ with the following outcomes (probabilities):
+
+$$
+\tag{1}
+P = 
+  \begin{cases}
+    8.0 \quad (.9) \\
+    2.5 \quad (.1) 
+  \end{cases} 
+$$
+
+In (1), outcomes and probabilities are properties of $P$ and readily described using the decimal number system as a representation.
+Now, if the expected value as another property of $P$ is to be described, the organizational rule would be to first multiply the outcomes by their probability and then sum the resulting products, i.e., $8 \times .9 + 2.5 \times .1 = 7.45$.
+For the sake of example, one could think of another prospect
+
+$$
+\tag{2}
+P = \{8.0, 8.0\}
+$$
+
+where the probability of the outcome $2.5$ must be inferred from the facts that the prospect has only two outcomes and the other outcome has a probability of $.9$. 
+Therefore, in (2), the explicit description of the probability as one property of $P$ requires an inference, whereas the description of the expected value as another property now requires both, an inference and a calculus.
+
 In quite many cases, however, a number of different representations can be used to describe the properties of choice alternatives in a given set.

### 2021-12-30 manuscript.Rmd
Update Introduction

@@
 The mind is a cognitive system that operates on inputs from an environment or memory.
-Such inputs may be treated as a set $I$ and its elements $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess [@jostMathematicalConcepts2015, p.
+In the domain of decision making, such inputs may be treated abstractly as a set $I$ of choice alternatives $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess [cf.
+@jostMathematicalConcepts2015, p.
 1].
-Often, however, the properties used by the mind to control the outputs are not readily described, but proper descriptions must be inferred from the available information. 
-Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982, p.
+Often, however, the properties used by the mind to control the outputs/decisions, are not readily described, but proper descriptions must be inferred from the available information. 
+These inferences are part of the algorithm the mind executes to make a decision and may rely on transformation rules, statistical generalizations, or both.
+Since how the input set is represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982, p.
 21; see also @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
-Hence, to explain how the mind turns certain inputs into meaningful outputs, one needs to understand the properties that control the output, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
+Hence, to explain how the mind turns certain inputs into meaningful outputs/decisions, one needs to understand the output-controlling properties, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
 The process is schematically shown in Figure 1.
@@
 
-(ref:figure1) A sketch of the structure of information processing.
-To turn inputs into meaningful outputs, the mind is required to describe the relevant properties before they can be evaluated.
-Descriptions are inferred from the inputs using a representation.
+(ref:figure1) An abstract sketch of the decision making process.
+To turn inputs into meaningful outputs, the mind requires explicit descriptions of the output-controlling properties before they can be evaluated.
+Descriptions are either readily available or must be inferred from the inputs.
 
@@
 
-In what follows, the discussion will turn to the domain of decision making and elaborate on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate one rather important mechanism:
+In what follows, the discussion will elaborate on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate one rather important mechanism:
 Given that the properties of choice alternatives serve as *selection criteria* and the mind is indeed sensitive to variations in their values, the more accurately the descriptions of these properties are inferred, the more systematic the choices should become.

### 2022-01-11 manuscript.Rmd
Review Introduction

--- 2021-12-29 manuscript.Rmd
@@
 The mind is a cognitive system that operates on inputs from an environment or memory.
-Such inputs may be treated as a set $I$ and its elements $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess [@jostMathematicalConcepts2015, p.
-1].
-Often, however, the properties used by the mind to control the outputs are not readily described, but proper descriptions must be inferred from the available information. 
-Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982, p.
-21; see also @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
-Hence, to explain how the mind turns certain inputs into meaningful outputs, one needs to understand the properties that control the output, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
+In the domain of decision making, such inputs can be treated as a set $I$ of choice alternatives $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess [cf.
+@jostMathematicalConcepts2015].
+The basic structure of decision making may then be modeled by the inclusion map $\iota : I' \mapsto I$, where $\iota(i) = i$ for all $i \in I'$, indicating that decision making is a *process* that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
+Given that the choice is systematic---as opposed to random---the chosen alternatives in $I'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
+We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
+
+Often, however, the properties used by the mind to make a choice are not readily described and cannot be directly evaluated; rather, proper descriptions must be inferred from whatever information the inputs provide about the properties of choice alternatives, using transformation rules, statistical generalizations, or both.
+Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [cf.
+@marrVisionComputationalInvestigation1982; see also @gigerenzerHowImproveBayesian1995; @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
+Hence, to explain how the mind makes a selection among choice alternatives, one needs to understand the output controlling properties, i.e., the applied selection criteria, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
 The process is schematically shown in Figure 1.
@@
 
-(ref:figure1) A sketch of the structure of information processing.
-To turn inputs into meaningful outputs, the mind is required to describe the relevant properties before they can be evaluated.
-Descriptions are inferred from the inputs using a representation.
+(ref:figure1) A computational level sketch of decision making as an information processing problem.
+To make a selection among choice alternatives on the basis of particular selection criteria, the mind requires explicit descriptions of the relevant properties before they can be evaluated.
+Descriptions are either readily available or must be inferred from the inputs.
 
@@
 
-In what follows, the discussion will turn to the domain of decision making and elaborate on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate one rather important mechanism:
-Given that the properties of choice alternatives serve as *selection criteria* and the mind is indeed sensitive to variations in their values, the more accurately the descriptions of these properties are inferred, the more systematic the choices should become.
-Importantly, this principle is not restricted to any one specific property, but rather does a characteristic choice pattern result from the constraints that the designation of a property as a selection criterion imposes on the assessment of choice alternatives.
+In what follows, the discussion will elaborate on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate one rather important principle:
+Given that the mind is indeed sensitive to variations in the property values, the more accurately their descriptions are inferred, the more systematic the choices should become.
+Importantly, this principle is not restricted to any one specific property. 
+Rather, each selection criterion or combination thereof imposes constraints on the assessment of choice alternatives, leading to characteristic choice patterns that are eventually blurred by inaccurate property descriptions.
 
-As the discussion proceeds and for the sake of example, I argue that a choice pattern robustly emerging in so-called *decisions from experience* (DfE), i.e., the apparent underweighting of small probability events, may be caused by the assessment constraints associated with a round-wise decision rule.
-This particular argument has already been made by @hillsInformationSearchDecisions2010, however, decision rules, as I try to explain below, are for several reasons better formulated as selection criteria whose descriptions are rarely restricted to one representation.
-Considering *sampling strategies* as representations used to describe the properties of interest in DfE, I illustrate how the inferred descriptions of properties indeed become more accurate with increasing sample sizes.
-Yet, caused by the selection criterion corresponding to a round-wise decision rule, the underweighting pattern is a priori predicted to become more pronounced in such a case. 
-This prediction is different from the explanation that underweighting is partly caused by the reliance on small samples and the skewness of the binomial distribution [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009], indicating that the effects of sample size on the choice pattern are conditional on the selection criterion.
+As the discussion proceeds and for the sake of example, I argue that a choice pattern robustly emerging in *decisions from experience* (DfE), the apparent underweighting of small probability events [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; see also @wulffMetaanalyticReviewTwo2018, for a meta-analytic review], may be caused by the assessment constraints associated with a round-wise decision strategy.
+This particular claim has already been made by @hillsInformationSearchDecisions2010, is in principle not restricted to DfE, and follows quite directly from probability theory.
+However, the current article treats decision strategies explicitly as selection criteria and addresses in some detail a few of the problems associated with DfE, in which descriptions of the properties of choice alternatives must be inferred from sampling data.
+
+For one, there is the well-known statistical *induction problem* that the sample size determines the margin of error within which any true property of a choice alternative can be inferred, given an otherwise perfect inference process.
+Yet, the underweighting pattern that is caused by the adoption of a certain selection criterion is a priori predicted to become more pronounced with increasing sample size. 
+This prediction is in line with the principle already stated above, i.e., that choice patterns should become more systematic as property descriptions become more accurate.
+Nevertheless, the prediction is different from the explanation that underweighting is caused by the reliance on small samples and the skewness of the binomial distribution [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @rakowBiasedSamplesNot2008], highlighting that outside the *statistical* models used to describe the choice data, *causal* decision making models of quite different nature may be at play, and that a rather important difference between the latter resides in the selection criteria they include.
 I will elaborate on this matter as I proceed, however, to be rather clear from the outset, what the mind does in neither case is performing an underweighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [cf.
@@
 
-The theoretical argument is supported by a simulation study. 
+The theoretical argument is substantiated by a simulation study. 
 For this purpose, the sampling and decision making processes are expressed mathematically and implemented in a computational model.
@@
 Decision making is an information-processing problem whose solution requires a selection among choice alternatives. 
-The basic structure of the problem may be modeled by the inclusion map $\iota : I' \mapsto I$, where $\iota(i) = i$ for all $i \in I'$, indicating that decision making is a *process* that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
-Given that the selection is systematic---as opposed to random---the chosen alternatives in $I'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
-We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as selection criteria. 
 I.e., with regards to a given selection criteria, all chosen alternatives are equal to each other but different from the non-chosen alternatives.
-
 Now, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).

### 2022-01-12 manuscript.Rmd
Preliminary Introduction

@@
 This prediction is in line with the principle already stated above, i.e., that choice patterns should become more systematic as property descriptions become more accurate.
-Nevertheless, the prediction is different from the explanation that underweighting is caused by the reliance on small samples and the skewness of the binomial distribution [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @rakowBiasedSamplesNot2008], highlighting that outside the *statistical* models used to describe the choice data, *causal* decision making models of quite different nature may be at play, and that a rather important difference between the latter resides in the selection criteria they include.
-I will elaborate on this matter as I proceed, however, to be rather clear from the outset, what the mind does in neither case is performing an underweighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [cf.
+Nevertheless, the prediction is different from the explanation that underweighting is caused by the reliance on small samples and the skewness of the binomial distribution [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @rakowBiasedSamplesNot2008], highlighting that outside the *statistical* models used to describe the choice data, *causal* decision making models of quite different nature may be at play [cf.
+@mcelreathStatisticalRethinkingBayesian2020], and that a rather important difference between the latter resides in the selection criteria they include.
+I will elaborate on this matter as I proceed, however, to be clear from the outset, what the mind does in neither case is performing an underweighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [cf.
 @griffithsRationalUseCognitive2015].
 
-The theoretical argument is substantiated by a simulation study. 
-For this purpose, the sampling and decision making processes are expressed mathematically and implemented in a computational model.
-Choice data from DfE is simulated and modeled using cumulative prospect theory (CPT), a data model commonly used for describing decisions under risk and uncertainty [@tverskyAdvancesProspectTheory1992].
+For another, this article approaches the problem of organizing the sampling data in such a way that it allows chains of inferences connecting the input set $I$ with the output set $I' \subset I$ that are algorithmically short and simple enough to be carried out by minds whose cognitive capacities are bounded [see @simonBehavioralModelRational1955; @simonInvariantsHumanBehavior1990].
+This may be considered a *representation problem* since the inference chains are constructed around explicit descriptions of the properties of choice alternatives and representations are the "formal schemes" of symbols and rules with which these descriptions are derived [@marrRepresentationRecognitionSpatial1978, p.
+270].
+Specifically, representations differ in how they organize the information used to infer the descriptions of certain properties and these organizations determine the algorithms that can be built into the inference chain [@marrVisionComputationalInvestigation1982].
+In this article, *sampling strategies* in DfE are considered as representation systems used to organize the samples in a way that subserves the property inferences required by the application of particular selection criteria.
+Though most of my expositions on the role of sampling strategies remain speculative, the core idea is not new to decision research [see, e.g., @hillsInformationSearchDecisions2010; @wulffHowShortLongrun2015].
+By restating this idea and adopting some terms and concepts that have well-defined meaning in math and cognitive science, I hope to integrate it into the rich study of the computationally limited mind as an adaptive cognitive system whose processes interact with the information structures in the environment or memory [e.g., @simonRationalChoiceStructure1956; @hertwigTamingUncertainty2019].
+
+The theoretical arguments sketched in this admittingly dense introduction are substantiated by a simulation study. 
+For this purpose, the sampling and decision making processes are expressed mathematically and implemented in a computational model to simulate choice data from DfE.
+The simulated data is modeled in cumulative prospect theory (CPT), a data model commonly used for describing decisions under risk and uncertainty [@goldsteinExpressionTheoryPreference1987; see also @tverskyAdvancesProspectTheory1992].
 All simulations and analyses are reproducible---materials and instructions can be found on the GitHub repository.
@@
 
-Decision making is an information-processing problem whose solution requires a selection among choice alternatives. 
-I.e., with regards to a given selection criteria, all chosen alternatives are equal to each other but different from the non-chosen alternatives.
+We already stated that decision making is an information-processing problem whose solution requires a selection among choice alternatives.
+all chosen alternatives are equal to each other but different from the non-chosen alternatives.
+
 Now, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).

### 2022-01-14 manuscript.Rmd
Update Section 2

@@
 The mind is a cognitive system that operates on inputs from an environment or memory.
-In the domain of decision making, such inputs can be treated as a set $I$ of choice alternatives $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess [cf.
-@jostMathematicalConcepts2015].
-The basic structure of decision making may then be modeled by the inclusion map $\iota : I' \mapsto I$, where $\iota(i) = i$ for all $i \in I'$, indicating that decision making is a *process* that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
-Given that the choice is systematic---as opposed to random---the chosen alternatives in $I'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
+In the domain of decision making, such inputs can be organized in a set $I$ of choice alternatives $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess.
+The basic structure of decision making may then be modeled by the inclusion map
+
+$$
+\begin{aligned}
+  & \iota : I' \mapsto I \\
+  & \iota(i) = i \ \text{for all} \ i \in I' 
+\end{aligned}
+\tag{1}
+$$
+
+[cf.
+@jostMathematicalConcepts2015, pp.
+14-15], indicating that decision making is a *process* that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
+Given that the choice is perfectly systematic---as opposed to random or noisy---the chosen alternatives in $I'$ should share some property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
 We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
 
-Often, however, the properties used by the mind to make a choice are not readily described and cannot be directly evaluated; rather, proper descriptions must be inferred from whatever information the inputs provide about the properties of choice alternatives, using transformation rules, statistical generalizations, or both.
-Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [cf.
-@marrVisionComputationalInvestigation1982; see also @gigerenzerHowImproveBayesian1995; @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
+Often, however, the properties used by the mind to make a choice are not readily described and cannot be directly evaluated [cf.
+@brunswikRepresentativeDesignProbabilistic1955; see @brunswikPerceptionRepresentativeDesign1956, for a detailed treatment]; rather, proper descriptions must be inferred from whatever information the inputs provide about the properties of choice alternatives, using transformation rules, statistical generalizations, or both.
+Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982; see also, e.g., @gigerenzerHowImproveBayesian1995; @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
 Hence, to explain how the mind makes a selection among choice alternatives, one needs to understand the output controlling properties, i.e., the applied selection criteria, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
@@
 
-In what follows, the discussion will elaborate on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate one rather important principle:
+In what follows, this paper will elaborate on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate a rather important principle:
 Given that the mind is indeed sensitive to variations in the property values, the more accurately their descriptions are inferred, the more systematic the choices should become.
@@
 
-As the discussion proceeds and for the sake of example, I argue that a choice pattern robustly emerging in *decisions from experience* (DfE), the apparent underweighting of small probability events [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; see also @wulffMetaanalyticReviewTwo2018, for a meta-analytic review], may be caused by the assessment constraints associated with a round-wise decision strategy.
-This particular claim has already been made by @hillsInformationSearchDecisions2010, is in principle not restricted to DfE, and follows quite directly from probability theory.
-However, the current article treats decision strategies explicitly as selection criteria and addresses in some detail a few of the problems associated with DfE, in which descriptions of the properties of choice alternatives must be inferred from sampling data.
+For the sake of example, I argue that a choice pattern robustly emerging in *decisions from experience* (DfE), the apparent underweighting of small probability events [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; see also @wulffMetaanalyticReviewTwo2018, for a meta-analytic review], may be caused by the assessment constraints associated with a round-wise decision strategy.
+This particular claim has already been made by @hillsInformationSearchDecisions2010 and follows quite directly from probability theory.
+However, the current paper suggests to subordinate decision strategies to the adoption of selection criteria and addresses in some detail two "problems" in the context of DfE, in which descriptions of the properties of choice alternatives must be inferred from sampling data.
 
-For one, there is the well-known statistical *induction problem* that the sample size determines the margin of error within which any true property of a choice alternative can be inferred, given an otherwise perfect inference process.
-Yet, the underweighting pattern that is caused by the adoption of a certain selection criterion is a priori predicted to become more pronounced with increasing sample size. 
-This prediction is in line with the principle already stated above, i.e., that choice patterns should become more systematic as property descriptions become more accurate.
-Nevertheless, the prediction is different from the explanation that underweighting is caused by the reliance on small samples and the skewness of the binomial distribution [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @rakowBiasedSamplesNot2008], highlighting that outside the *statistical* models used to describe the choice data, *causal* decision making models of quite different nature may be at play [cf.
-@mcelreathStatisticalRethinkingBayesian2020], and that a rather important difference between the latter resides in the selection criteria they include.
-I will elaborate on this matter as I proceed, however, to be clear from the outset, what the mind does in neither case is performing an underweighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [cf.
-@griffithsRationalUseCognitive2015].
+For one, there is an *induction problem*, well known from inferential statistics, according to which the sample size determines the margin of error within which any true property of a choice alternative can be inferred, given an otherwise perfect inference process.
+Yet, it follows that the underweighting pattern that is caused by the adoption of an arbitrary selection criterion is a priori predicted to become more stable with increasing sample size. 
+This prediction is in line with the principle already stated above, i.e., that selection-criteria-induced choice patterns should become more systematic as property descriptions become more accurate.
+Nevertheless, the prediction contrasts the explanation that underweighting is caused by the reliance on small samples [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @rakowBiasedSamplesNot2008], highlighting that outside of the *statistical* models used to describe the choice data, *causal* decision making models of quite different nature may be at play, and that a rather important difference between these causal models resides in the selection criteria they incorporate.
+I will elaborate on this matter as I proceed, however, to be clear from the outset, what the mind does in neither case is performing a probability weighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [cf., e.g., @griffithsRationalUseCognitive2015].
 
-For another, this article approaches the problem of organizing the sampling data in such a way that it allows chains of inferences connecting the input set $I$ with the output set $I' \subset I$ that are algorithmically short and simple enough to be carried out by minds whose cognitive capacities are bounded [see @simonBehavioralModelRational1955; @simonInvariantsHumanBehavior1990].
+For another, this paper approaches the problem of organizing the sampling data in such a way that it allows chains of inferences connecting the input set $I$ with the output set $I' \subset I$ that are algorithmically short and simple enough to be carried out by minds whose cognitive capacities are bounded [cf.
+@simonInvariantsHumanBehavior1990; @simonBehavioralModelRational1955].
 This may be considered a *representation problem* since the inference chains are constructed around explicit descriptions of the properties of choice alternatives and representations are the "formal schemes" of symbols and rules with which these descriptions are derived [@marrRepresentationRecognitionSpatial1978, p.
@@
 Though most of my expositions on the role of sampling strategies remain speculative, the core idea is not new to decision research [see, e.g., @hillsInformationSearchDecisions2010; @wulffHowShortLongrun2015].
-By restating this idea and adopting some terms and concepts that have well-defined meaning in math and cognitive science, I hope to integrate it into the rich study of the computationally limited mind as an adaptive cognitive system whose processes interact with the information structures in the environment or memory [e.g., @simonRationalChoiceStructure1956; @hertwigTamingUncertainty2019].
+By restating this idea and adopting some terms and concepts that have well defined meaning in math and cognitive science, I hope to integrate it into the rich study of the computationally limited mind as an adaptive cognitive system whose processes interact with the information structures in the environment or memory.
 
-The theoretical arguments sketched in this admittingly dense introduction are substantiated by a simulation study. 
+The theoretical arguments sketched in this introduction are substantiated by a simulation study. 
 For this purpose, the sampling and decision making processes are expressed mathematically and implemented in a computational model to simulate choice data from DfE.
@@
 
-# The Decision Making Process and the Properties of Choice Alternatives
+# Selection Criteria / Properties of Choice Alternatives / Sampling
 
-We already stated that decision making is an information-processing problem whose solution requires a selection among choice alternatives.
-all chosen alternatives are equal to each other but different from the non-chosen alternatives.
-
-Now, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).
-Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that can be made after assessing for each alternative whether it fulfills the selection criteria or not [cf.
-@jostMathematicalConcepts2015, p.
-16].
-The concept of the power set thereby illustrates in a plain way how different selection criteria can alter the consequential choice, provided the properties are not uniformly distributed among the alternatives and the mind is sensitive to whatever relations the alternatives have with each other.
+By defining decision making as an information-processing problem whose solution requires a selection among choice alternatives of the form described in (1), much weight is given to the properties of choice alternatives---whatever those may be for the moment---since it is only through them that any necessary distinction between the alternatives or collections thereof can be made.
+To stress this point, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).
 \
 
-(ref:figure2) The power set of the set $I$ including the choice alternatives A, B, and C.
+(ref:figure2) A.
+The power set of the set $I$ including the choice alternatives A, B, and C.
 Black (white) circles indicate that an alternative does (not) possess a property.
@@
 Note that properties resulting in the empty set $\{\}$ and the subset $\{A,B,C\}$ do not discriminate between choice alternatives.
+B.
+A Venn diagram showing the relation between a subset $I'$ and its superset $I$.
 
@@
 ```
+
+Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that could result from assessing for each alternative whether it possesses an arbitrary property (collection) or not [cf.
+@jostMathematicalConcepts2015, p.
+16].
+The concept of the power set thereby illustrates how different selection criteria can alter the consequential choice.
+That is, in rather abstract terms, selection criteria are statements regarding the properties of choice alternatives that the mind evaluates as either true or false during the decision making process; accordingly, the subset $I'$ only contains the alternatives for which the statement is evaluated to be true.
+It follows that if there is some variance in the properties across choice alternatives and the properties are not perfectly correlated, changing the selection criteria can eventually change the subset $I'$.
+<!-- Of course, the whole argument rests on the assumption that ... -->
+
+## What are the properties of choice alternatives and the selection criteria?
+
+This paper refrains from making inroads into the questions of whether and why *prospects* are useful abstractions of the choice alternatives the mind is required to evaluate in natural world decisions.
+It just considers choices between at least two prospects because they are the standard paradigm in research on decision theory and they suffice
 
@@
 $$
-\tag{1}
+\tag{2}
 P = 
@@
 $$
-\tag{2}
+\tag{3}
 P = \{8.0, 8.0\}

### 2022-01-18 manuscript.Rmd
Update section 2: Definition of prospects

@@
 
- The current version of this manuscript is prepared for submission as a master's thesis. A modified later version might be prepared together with co-authors and submitted for peer-review.
+ The current version of this manuscript is prepared for submission as a master's thesis.
 
@@
 
-(ref:figure1) A computational level sketch of decision making as an information processing problem.
+(ref:figure1) A rough computational level sketch of decision making as an information processing problem.
 To make a selection among choice alternatives on the basis of particular selection criteria, the mind requires explicit descriptions of the relevant properties before they can be evaluated.
@@
 For one, there is an *induction problem*, well known from inferential statistics, according to which the sample size determines the margin of error within which any true property of a choice alternative can be inferred, given an otherwise perfect inference process.
-Yet, it follows that the underweighting pattern that is caused by the adoption of an arbitrary selection criterion is a priori predicted to become more stable with increasing sample size. 
+Yet, it follows that if an underweighting pattern is caused by the adoption of an arbitrary selection criterion, it is *a priori* predicted to become more stable with increasing sample size. 
 This prediction is in line with the principle already stated above, i.e., that selection-criteria-induced choice patterns should become more systematic as property descriptions become more accurate.
@@
 Specifically, representations differ in how they organize the information used to infer the descriptions of certain properties and these organizations determine the algorithms that can be built into the inference chain [@marrVisionComputationalInvestigation1982].
-In this article, *sampling strategies* in DfE are considered as representation systems used to organize the samples in a way that subserves the property inferences required by the application of particular selection criteria.
+In this paper, *sampling strategies* in DfE are considered as representation systems used to organize the samples in a way that subserves the property inferences required by the application of particular selection criteria.
 Though most of my expositions on the role of sampling strategies remain speculative, the core idea is not new to decision research [see, e.g., @hillsInformationSearchDecisions2010; @wulffHowShortLongrun2015].
@@
 The theoretical arguments sketched in this introduction are substantiated by a simulation study. 
-For this purpose, the sampling and decision making processes are expressed mathematically and implemented in a computational model to simulate choice data from DfE.
+For this purpose, the sampling and decision making processes are implemented in a computational model to simulate choice data from DfE.
 The simulated data is modeled in cumulative prospect theory (CPT), a data model commonly used for describing decisions under risk and uncertainty [@goldsteinExpressionTheoryPreference1987; see also @tverskyAdvancesProspectTheory1992].
@@
 
-By defining decision making as an information-processing problem whose solution requires a selection among choice alternatives of the form described in (1), much weight is given to the properties of choice alternatives---whatever those may be for the moment---since it is only through them that any necessary distinction between the alternatives or collections thereof can be made.
+By defining decision making as an information processing problem whose solution requires a selection among choice alternatives of the form described in (1), much weight is given to the properties of choice alternatives---whatever those may be for the moment---since it is only through them that any necessary distinction between the alternatives or collections thereof can be made.
 To stress this point, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).
@@
 B.
-A Venn diagram showing the relation between a subset $I'$ and its superset $I$.
+A Venn diagram visualizing the inclusion map $\iota : I' \mapsto I$.
+$\iota$ maps every element $i$ of the subset $I'$ to its image $i$, treated as element of the superset $I$.
 
@@
 
-## What are the properties of choice alternatives and the selection criteria?
+## What Are the Properties of Choice Alternatives and the Selection Criteria?
 
-This paper refrains from making inroads into the questions of whether and why *prospects* are useful abstractions of the choice alternatives the mind is required to evaluate in natural world decisions.
-It just considers choices between at least two prospects because they are the standard paradigm in research on decision theory and they suffice
+The argument so far has been quite general and abstract, since there is no complete answer to the question raised above this paragraph---there is, of course, an uncountable number of decisions and so are there choice alternatives, properties, and selection criteria.
+Therefore, in the present paper, *prospects* are used as a proxy for the variety of choice alternatives the mind is required to evaluate in natural world decisions. 
+Consequently, the argument continues to proceed at an abstract level: with choices between at least two prospects, the current paper considers a case which is counterfactual, since it is freed from many varieties and complexities that the mind is normally confronted with.
+The case is, however, quite paradigmatic in research on decision theory and there are good reasons for that [cf.
+@knightRiskUncertaintyProfit1921, especially Chapter 1 for a brief discussion closely related to the current subject].
+Moreover, the case suffices to answer the above question and to subsequently address the induction and representation problem, at least within the stated limitations.
+
+Now, let a prospect be a *probability space* denoted by the tuple $(\Omega, \mathcal{F}, P)$. 
+Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ is the sample space
+
+$$
+\Omega = \{\omega_1, ..., \omega_n\}
+\; ,
+\tag{2.1}
+$$
+
+containing a finite set of possible outcomes $\omega$. 
+$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$.^[Note that this paper considers only the case of finite sample spaces containing of a small number of outcomes.
+The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
+2-3 and 14-15], also covers infinite sample spaces and is that of a $\sigma$-algebra.
+For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such.
+See Georgii [-@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1] for a comprehensive mathematical treatment of this matter.]
+$P$ is a probability measure
+
+$$
+P: \mathcal{F} \mapsto [0,1]
+\; ,
+\tag{2.2}
+$$
+
+which assigns each subset $A \in \mathcal{F}$, or *event*, a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probability measure formally assigns probabilities to sets of outcomes $A \in F$ rather than the elementary outcomes $\omega \in \Omega$.
+The probabilities of $\omega$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure according to the equation $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{P}(\Omega)$ [cf.
+@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.2].
+The literature on behavioral decision research usually forgoes the admittedly technical definition of probability spaces and defines prospects as probability mass functions.
+Nonetheless, even though probability spaces are idealized models, they provide a useful mathematical foundation for the case where the simultaneous occurrence of more than one elementary outcome is of interest.]
 

### 2022-01-19 manuscript.Rmd
Definition of paper structure (sections etc.) + add note document

@@
 Given that the choice is perfectly systematic---as opposed to random or noisy---the chosen alternatives in $I'$ should share some property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
-We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
+In the following, I will refer to statements about properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
 
@@
 
-# Selection Criteria / Properties of Choice Alternatives / Sampling
+# Section 1: Selection Criteria / Properties of Choice Alternatives / Sampling
 
@@
 For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such.
-See Georgii [-@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1] for a comprehensive mathematical treatment of this matter.]
+See Georgii [-@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1] for a comprehensive mathematical treatment.]
 $P$ is a probability measure
@@
 
-which assigns each subset $A \in \mathcal{F}$, or *event*, a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probability measure formally assigns probabilities to sets of outcomes $A \in F$ rather than the elementary outcomes $\omega \in \Omega$.
-The probabilities of $\omega$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure according to the equation $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{P}(\Omega)$ [cf.
-@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.2].
-The literature on behavioral decision research usually forgoes the admittedly technical definition of probability spaces and defines prospects as probability mass functions.
-Nonetheless, even though probability spaces are idealized models, they provide a useful mathematical foundation for the case where the simultaneous occurrence of more than one elementary outcome is of interest.]
+which assigns each subset $A \in \mathcal{F}$, also referred to as *events*, a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probability measure formally assigns probabilities to sets of outcomes $A \in F$ rather than the elementary outcomes $\omega \in \Omega$.
+The probabilities of $\omega$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure according to the equation $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$ [cf.
+@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.2].]
+In less technical terms, following the choice of a prospect, one of the outcomes associated with this particular prospect is obtained, a gain or loss respectively.
+If there is just one outcome associated with a prospect, it is obtained with certainty.
+However, if there is a collection of outcomes, just one outcome out of this collection is obtained according to some probability, where the probabilities can vary between outcomes and are given by the measure of the form described in (2.2) (see also Footnote 2).
+
+Since it was stated that the inputs to the decision making process can be organized in a set of choice alternatives, we can adapt (1) for the case of a choice between $1, ..., n$ prospects to obtain:
+
+$$
+\iota : I' \mapsto I, \ \text{where} \ I = \{(\Omega_1,  \mathcal{F}_1, P_1), ..., (\Omega_n,  \mathcal{F}_n, P_n)\}
+\; .
+\tag{3}
+$$
+
+Given (3), it is evident that the prospects can only be distinguished by the elements of their tuples, and these elements are properties---be that a smallest single element, e.g., an outcome, collections thereof, e.g., the sample space $\Omega$, or more complex combinations of elements, e.g., the weighted average which is obtained by first multiplying all outcomes in $\Omega$ by their respective probabilities in $P$ and then summing the resulting products.^[I do not refer to this quantity as expected value, since the term is reserved for random variables, which were not introduced so far.]
+In turn, for choices between prospects, selection criteria are statements about the elements of their tuples that are true or false and these statements imply relations among prospects that are at least nominal, e.g., *"One of the prospect's outcome is positive in value"*, but may also draw on other levels of measurement, e.g., *"The prospect's average mean is the largest among the prospects"* refers to an ordinal level.
+
+## Inferring Property Descriptions by Sampling
 
@@
 In such cases, to obtain the respective descriptions from the inputs, the mind is required to make an inference from the available information.
-
-impose a proper organization on them, with the rules for doing so determined by the representation [cf.
-@marrVisionComputationalInvestigation1982; @marrRepresentationRecognitionSpatial1978], or it must make an inference from incomplete information, or both.
-Consider a prospect $P$ with the following outcomes (probabilities):
-
-$$
-\tag{2}
-P = 
-  \begin{cases}
-    8.0 \quad (.9) \\
-    2.5 \quad (.1) 
-  \end{cases} 
-$$
-
-In (1), outcomes and probabilities are properties of $P$ and readily described using the decimal number system as a representation.
-Now, if the expected value as another property of $P$ is to be described, the organizational rule would be to first multiply the outcomes by their probability and then sum the resulting products, i.e., $8 \times .9 + 2.5 \times .1 = 7.45$.
-For the sake of example, one could think of another prospect
-
-$$
-\tag{3}
-P = \{8.0, 8.0\}
-$$
-
-where the probability of the outcome $2.5$ must be inferred from the facts that the prospect has only two outcomes and the other outcome has a probability of $.9$. 
-Therefore, in (2), the explicit description of the probability as one property of $P$ requires an inference, whereas the description of the expected value as another property now requires both, an inference and a calculus.
-
-In quite many cases, however, a number of different representations can be used to describe the properties of choice alternatives in a given set.
-Yet, not every representation permits an accurate description of a given property at reasonable expenses or allows to describe a property at all [cf. @marrRepresentationRecognitionSpatial1978].
-
-E.g., a consequential difference that has emerged in behavioral research on risky choice is whether the probability of a risky outcome is described using a decimal number (.2), ratio (2/10), or percentage (20%), or whether it must be inferred from the relative frequency of occurrence of the particular outcome in a collection of independent and identically distributed (i.i.d.) random variables, i.e., a *random sample*.
-Noteworthy, for the latter case, which is usually referred to as decisions from experience, empirical protocols indicate that people decide as if they were underweighting small probability events [@barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004].
-One undisputed factor that contributes to this underweighting pattern is the sampling error associated with people's reliance on small samples [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018 for a meta-analytic review], indicating that, although the probabilities of outcomes can in principle be accurately described in decisions from experience, the actual description is rather inaccurate because it cannot be done at reasonable expenses.
-
-Another property of choice alternatives that is likely to play a role in risky choice but can only be made explicit using a sample representation as in decisions from experience is the sequence in which outcomes occur.
-Although a discrete-time collection of i.i.d.
-random variables cannot, by definition, exhibit temporal regularity, i.e., it cannot produce a stable sequence of sampled outcomes, spurious temporal patterns might nevertheless be regarded as a property of choice alternatives and affect the consequential choice behavior.
-Indeed, the underweighting pattern and other behavioral phenomena like the wavy recency effect and probability matching, are reasonably well captured by models which incorporate the assumption that people rely on (spurious) outcome sequences [@cohenEffectPerceivedPatterns2021; @gaissmaierSmartPotentialProbability2008; @plonskyRelianceSmallSamples2015; @plonskyLearningSettingsPartial2017;  @yuSequentialEffectsSupersition2009].
-
-The preceding two examples illustrate how some properties of choice alternatives can be described in one representation but not in another and how representations can differ with regards to the processing effort required to describe the same property.
-Thus, there is generally a trade-off between different representations, where in a given representation certain properties become explicit while others are pushed into the background [@marrVisionComputationalInvestigation1982, p.
-21].
-
-# Sampling Strategies
-
-<!-- Samples as representation -->
-
-In research on the decision theory, a standard paradigm is the choice between at least two (monetary) prospects.
-Let a prospect be a probability space $(\Omega, \mathcal{F}, P)$.
-$\Omega$ is the sample space
-
-$$
-\Omega = \{\omega_1, ..., \omega_n\}
-$$
-
-containing a finite set of possible outcomes $\omega$, monetary gains and/or losses respectively. 
-$\mathcal{F}$ is the set of all possible subsets of $\Omega$:
-
-$$
-\mathcal{F} = \{A_1, A_2, ...\} = \mathcal{P}(\Omega) 
-\; .
-$$
-
-$P$ is a probability mass function
-
-$$
-P: \mathcal{F} \mapsto [0,1] 
-$$
-
-that assigns each outcome $\omega$ a probability $0 < p(\omega) \leq 1$ with $P(\Omega) = 1$ [ @kolmogorovFoundationsTheoryProbability1950, pp. 2-3].
 
@@
 
-## Subheading: Capturing Differences in Sampling and Decision Strategies
+# Section 2: Underweighting Pattern / Hills and Hertwig (2010) / Induction
 
-Hills and Hertwig [-@hillsInformationSearchDecisions2010] discussed a potential link between sampling and decision strategies in DfE. 
-Specifically, the authors suppose that if single samples originating from different prospects are generated in direct succession (piecewise sampling), the evaluation of prospects is based on multiple ordinal comparisons of single samples (round-wise decisions).
-In contrast, if single samples originating from the same prospect are generated in direct succession (comprehensive sampling), it is supposed that the evaluation of prospects is based on a single ordinal comparison of long sequences of single samples (summary decisions) [@hillsInformationSearchDecisions2010, Figure 1 for a graphical summary].
+# Section 3: Representation
 
-We now consider choices between two prospects and the assumptions of Hills and Hertwig [-@hillsInformationSearchDecisions2010] in more detail to build the respective stochastic sampling model for DfE.
-
-Let $X$ and $Y$ be random variables defined on the prospects $(\Omega_X, \mathcal{F}_X, P_X)$ and $(\Omega_Y, \mathcal{F}_Y, P_Y)$.
-
-Hills and Hertwig [-@hillsInformationSearchDecisions2010] suggest that any two sample sequences $X_i$ and $Y_i$ are compared by their means. 
-Let thus $C = \mathbb{R}$ be the set of all possible outcomes of the comparison of the means over two unordered sequences $X_i$ and $Y_i$ of given lengths $N_X$ and $N_Y$.
-That is, each element $c \in C$ represents a pair $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs. 
-Let then
-
-$$
-\mathcal{G} = \left\{B_1 = \{c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\}, B_2 = \{ c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} \leq 0\}
-\right\}
-$$
-
-be a set of subsets of $C$, indicating that comparisons of prospects on the ordinal (rather than on the metric) scale are of primary interest. 
-We denote a single ordinal comparison by the event space $(C, \mathcal{G})$.
-The observed outcome of such an ordinal comparison can be regarded as evidence for or against a prospect and the number of wins over a series of independent ordinal comparisons as accumulated evidence.
-To integrate the concept of evidence accumulation into the current model, we let the decision variable $D$ be a measurable function
-
-$$
-D: C \mapsto C'
-$$
-
-that maps the possible outcomes of a mean comparison in $C$ onto a measure space $C' = \{0,1\}$, with $0$ $(1)$ indicating a lost (won) comparison:
-
-$$
-D(c \in C) \in C' = 
-  \begin{cases}
-    1 \quad \text{for} \quad \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\}  \in \mathcal{G} \\
-    0 \quad \text{else}. 
-  \end{cases} 
-$$
-
-It can be shown that for fixed sequence lengths $N_X$ and $N_Y$, a sequence $D_i = D_1, ..., D_n$ representing multiple independent comparisons is a Bernoulli process where the number of won comparisons follows the binomial distribution
-
-$$
-D \sim \mathcal{B}\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right) \; ,
-$$
-
-with $p$ denoting probability of $X_i$ winning a single comparison, i.e., the probability of success, and $n$ denoting the number of comparisons.
-
-It becomes evident that the two combinations of sampling and decision strategies proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010] are reflected in certain restrictions on the free parameters $N_X, N_Y$ and $n$ of the sampling model and that these restrictions translate to the shape of the binomial distribution associated to the decision variables, straightforwardly via the parameter $n$, more interestingly, however, via its parameter $p$.
-
-I.e., first, whether a single (summary decision) or multiple ordinal comparisons (round-wise decision) are conducted, is reflected by the length of the sequence $D_i = D_1, ..., D_n$, with $n = 1$ for summary decisions and $n \geq 1$ for round-wise decisions.
-The idea that multiple comparisons may be conducted can be formalized by extending the event space $(C, \mathcal{G})$ of a single comparison to its $n$-fold product
-
-$$
-\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathcal{G}_i \right)
-\; ,
-$$
-
-where $i \in \{1, ..., n\}$ denotes the number of comparisons.
-
-Second, whether comparisons are conducted on the basis of longer sample sequences or single samples is reflected by the lengths of sample sequences from the same prospect with $N_X, N_Y \geq 1$ for comprehensive sampling and $N_X = N_Y = 1$ for piecewise sampling.
-
-Note now that, in order to derive predictions of the choice behavior from the current stochastic model, the full product model
-
-$$
-\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathcal{G}_i, \bigotimes_{i = 1}^{n} P_i \right)
-\; ,
-$$
-
-including the probability measure $P$, which assigns each $c \in C$, and each $B \in \mathcal{G}$ respectively, a probability, must be identified. 
-Although this can be demonstrated for the random variables considered so far, it becomes rather quickly intractable with increasing elements in $\Omega$ and growing sequence lengths. 
-However, by explicating the above probability measure ([Appendix 1][Appendix 1: Probability Measure Over Sample Mean Comparisons]), it becomes evident that it is largely influenced by the underlying sequence lengths $N_X$ and $N_Y$.
-In the following section and a subsequent simulation analysis, we demonstrate that this influence is of such a form that it produces some principle and predictable trends in the choice behavior that can be modeled in the cumulative prospect theory.
-
-## Subheading: Predicting Choice Behavior
-
-Note first that the current stochastic sampling model allows to treat sampling and decision strategies independently by parameterization of both lengths of sample sequences and the number of comparisons.
-
-...
-
-# Simulation Study
+# Section 4: Simulation Study
 
@@
 
-# Discussion and Conclusion
+# Section 5: Discussion and Conclusion
 
@@
 # Appendix
-
-## Appendix 1: Probability Measure Over Sample Mean Comparisons
-
-To proof is that the sequence $D_i = D_1, ..., D_n$ describes a Bernoulli process with the number of won comparisons following the binomial distribution $\mathcal{B}\left(p(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0), n \right)$ for fixed sequence lengths $N_X$ and $N_Y$.
-
-Therefore we must demonstrate that the probability of success, i.e., $p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right)$, is identified.
-The derivation chain is first roughly paraphrased and then formalized as a mathematical equation.
-
-We start by noting that the probability of success equals the probability of the subset $B_1 \in \mathcal{G}$ which contains all comparisons $c \in C$ that satisfy the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
-Since the probability of the subset $B_1$ equals the probability that any of its elements occurs, the probabilities of all $c \in B_1$ are summed up. 
-We therefore use the sum operator with the limits $j \in \{1, ..., |B_1|\}$, with $|B_1|$ denoting the cardinality of the set $B_1$, i.e., the number of elements within the set. 
-As a major assumption is that the random variables within a sample sequence are iid and independent across sequences, the joint probability of a pair $\overline{X}_{N_X} \cap \overline{Y}_{N_Y}$, i.e., a pair $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs, is described by the product of their individual probabilities $p(\overline{X}_{N_X})$ and $p(\overline{Y}_{N_Y})$.
-Finally, to get these individual probabilities, we must determine the probability that each possible realization indeed occurs the respective number of times in the underlying sample sequence.
-This probability is given by the multinomial distribution which reduces to a binomial distribution in the case of only two possible realizations. 
-We denote the number of times a realization occurs in a sample sequence with $k_{\omega}$, where $\omega$ signals that the realizations of the random variables are numerical equivalent to the outcomes in the sample space of the prospects.
-
-$$
-  \begin{split}
-    p(D = 1) 
-      & = p \left( \; B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathcal{G} \; \right) \\\\\\ 
-      & = \sum_{j=1}^{|B_1|} \left( \;
-          p(\overline{X}_{N_Xj})  
-          \times 
-          p(\overline{Y}_{N_Yj}) \; 
-        \right)_{j \, \in \, \{1, ..., |B_1|\}} \\\\\\
-      & = \sum_{j=1}^{|B_1|} \left( \; 
-        p \left( 
-          \frac{1}{N_X} \sum\limits_{i = 1}^{N_X} X(\omega \in \Omega_X)_{ij}
-        \right) 
-        \times
-        p \left( 
-          \frac{1}{N_Y} \sum\limits_{i = 1}^{N_Y} Y(\omega \in \Omega_Y)_{ij}
-        \right) \; 
-        \right)_{j \, \in \, \{1, ..., |B_1|\}} \\\\\\
-      & = \sum_{j=1}^{|B_1|} \left( \;
-        \left(
-          {N_X\choose k_{\omega_{1X}j}, ..., k_{\omega_{nX}j}} \prod_{\omega_{iX} \in \Omega_X} p(\omega_{iX})^{k_{\omega_{iX}j}}
-        \right)
-        \times
-        \left(
-        {N_Y\choose k_{\omega_{1Y}j}, ..., k_{\omega_{nY}j} } \prod_{\omega_{iY} \in \Omega_Y} p(\omega_{iY})^{k_{\omega_{iY}j}}
-        \right)
-        \right)_{j \, \in \, \{1, ..., |B_1|\}} \\\\\\
-      & = \sum_{j=1}^{|B_1|} \left( \;
-        \left(
-          \frac{N_X!}{k_{\omega_{1X}j}! \times ... \times k_{\omega_{nX}j}!} 
-          \times 
-          p(\omega_{1X})^{k_{\omega_{1X}j}} 
-          \times 
-          ... 
-          \times p(\omega_{nX})^{k_{\omega_{nX}j}}
-        \right)
-        \times
-        \left(
-          \frac{N_Y!}{k_{\omega_{1Y}j}! \times ... \times k_{\omega_{nY}j}!} 
-          \times 
-          p(\omega_{1Y})^{k_{\omega_{1Y}j}} 
-          \times 
-          ... 
-          \times p(\omega_{nY})^{k_{\omega_{nY}j}}
-        \right)
-      \right)_{j \, \in \, \{1, ..., |B_1|\}}
-  \end{split}
-$$
-
-## Appendix 2: Choice Problems
-
-```{r message=FALSE}
-gambles <- read_csv("data/gambles/sr_subset.csv")
-gambles %>% apa_table()
-```

### 2022-01-19 notes.Rmd
Definition of paper structure (sections etc.) + add note document

# General

- For example, probabilistic models of cognition suggest that a broad range of different assumptions about how people may structurally represent input information are required to capture their inferences about the extensions of novel properties in different inductive contexts [@griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].

# Sections

## Introduction

- Of course, the whole argument rests on the assumption that the mind is indeed sensitive to whatever relations the alternatives have with each other, however, it is hard to think of a situation
- In other words, by the end of the decision making process as illustrated in Figure 1, the selected choice alternatives form the exact same subset as the one which is indicated by a given selection criterion.

- Footnote 2: The literature on behavioral decision research usually forgoes the admittedly technical definition of probability spaces and defines prospects as probability mass functions. Nonetheless, even though probability spaces are idealized models, they provide a useful mathematical foundation for the case where the simultaneous occurrence of more than one elementary outcome is of interest.

## Section 1: Properties / Selection Criteria / Sampling

## Section 2: Underweighting / Hills and Hertwig / etc.

Hills and Hertwig [-@hillsInformationSearchDecisions2010] discussed a potential link between sampling and decision strategies in DfE. 
Specifically, the authors suppose that if single samples originating from different prospects are generated in direct succession (piecewise sampling), the evaluation of prospects is based on multiple ordinal comparisons of single samples (round-wise decisions).
In contrast, if single samples originating from the same prospect are generated in direct succession (comprehensive sampling), it is supposed that the evaluation of prospects is based on a single ordinal comparison of long sequences of single samples (summary decisions) [@hillsInformationSearchDecisions2010, Figure 1 for a graphical summary].

We now consider choices between two prospects and the assumptions of Hills and Hertwig [-@hillsInformationSearchDecisions2010] in more detail to build the respective stochastic sampling model for DfE.

Let $X$ and $Y$ be random variables defined on the prospects $(\Omega_X, \mathcal{F}_X, P_X)$ and $(\Omega_Y, \mathcal{F}_Y, P_Y)$.

Hills and Hertwig [-@hillsInformationSearchDecisions2010] suggest that any two sample sequences $X_i$ and $Y_i$ are compared by their means. 
Let thus $C = \mathbb{R}$ be the set of all possible outcomes of the comparison of the means over two unordered sequences $X_i$ and $Y_i$ of given lengths $N_X$ and $N_Y$.
That is, each element $c \in C$ represents a pair $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs. 
Let then

$$
\mathcal{G} = \left\{B_1 = \{c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\}, B_2 = \{ c \in C: \overline{X}_{N_X} - \overline{Y}_{N_Y} \leq 0\}
\right\}
$$

be a set of subsets of $C$, indicating that comparisons of prospects on the ordinal (rather than on the metric) scale are of primary interest. 
We denote a single ordinal comparison by the event space $(C, \mathcal{G})$.
The observed outcome of such an ordinal comparison can be regarded as evidence for or against a prospect and the number of wins over a series of independent ordinal comparisons as accumulated evidence. 
To integrate the concept of evidence accumulation into the current model, we let the decision variable $D$ be a measurable function

$$
D: C \mapsto C'
$$

that maps the possible outcomes of a mean comparison in $C$ onto a measure space $C' = \{0,1\}$, with $0$ $(1)$ indicating a lost (won) comparison:

$$
D(c \in C) \in C' = 
  \begin{cases}
    1 \quad \text{for} \quad \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\}  \in \mathcal{G} \\
    0 \quad \text{else}. 
  \end{cases} 
$$

It can be shown that for fixed sequence lengths $N_X$ and $N_Y$, a sequence $D_i = D_1, ..., D_n$ representing multiple independent comparisons is a Bernoulli process where the number of won comparisons follows the binomial distribution

$$
D \sim \mathcal{B}\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right) \; ,
$$

with $p$ denoting probability of $X_i$ winning a single comparison, i.e., the probability of success, and $n$ denoting the number of comparisons.

It becomes evident that the two combinations of sampling and decision strategies proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010] are reflected in certain restrictions on the free parameters $N_X, N_Y$ and $n$ of the sampling model and that these restrictions translate to the shape of the binomial distribution associated to the decision variables, straightforwardly via the parameter $n$, more interestingly, however, via its parameter $p$.

I.e., first, whether a single (summary decision) or multiple ordinal comparisons (round-wise decision) are conducted, is reflected by the length of the sequence $D_i = D_1, ..., D_n$, with $n = 1$ for summary decisions and $n \geq 1$ for round-wise decisions. 
The idea that multiple comparisons may be conducted can be formalized by extending the event space $(C, \mathcal{G})$ of a single comparison to its $n$-fold product

$$
\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathcal{G}_i \right)
\; ,
$$

where $i \in \{1, ..., n\}$ denotes the number of comparisons.

Second, whether comparisons are conducted on the basis of longer sample sequences or single samples is reflected by the lengths of sample sequences from the same prospect with $N_X, N_Y \geq 1$ for comprehensive sampling and $N_X = N_Y = 1$ for piecewise sampling.

Note now that, in order to derive predictions of the choice behavior from the current stochastic model, the full product model

$$
\left(\prod_{i = 1}^{n} C_i, \bigotimes_{i = 1}^{n} \mathcal{G}_i, \bigotimes_{i = 1}^{n} P_i \right)
\; ,
$$

including the probability measure $P$, which assigns each $c \in C$, and each $B \in \mathcal{G}$ respectively, a probability, must be identified. 
Although this can be demonstrated for the random variables considered so far, it becomes rather quickly intractable with increasing elements in $\Omega$ and growing sequence lengths. 
However, by explicating the above probability measure ([Appendix 1][Appendix 1: Probability Measure Over Sample Mean Comparisons]), it becomes evident that it is largely influenced by the underlying sequence lengths $N_X$ and $N_Y$.
In the following section and a subsequent simulation analysis, we demonstrate that this influence is of such a form that it produces some principle and predictable trends in the choice behavior that can be modeled in the cumulative prospect theory.

Note first that the current stochastic sampling model allows to treat sampling and decision strategies independently by parameterization of both lengths of sample sequences and the number of comparisons.

## Section 3: Representation

In quite many cases, however, a number of different representations can be used to describe the properties of choice alternatives in a given set.
Yet, not every representation permits an accurate description of a given property at reasonable expenses or allows to describe a property at all [cf. @marrRepresentationRecognitionSpatial1978].
E.g., a consequential difference that has emerged in behavioral research on risky choice is whether the probability of a risky outcome is described using a decimal number (.2), ratio (2/10), or percentage (20%), or whether it must be inferred from the relative frequency of occurrence of the particular outcome in a collection of independent and identically distributed (i.i.d.) random variables, i.e., a *random sample*.
Noteworthy, for the latter case, which is usually referred to as decisions from experience, empirical protocols indicate that people decide as if they were underweighting small probability events [@barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004].
One undisputed factor that contributes to this underweighting pattern is the sampling error associated with people's reliance on small samples [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018 for a meta-analytic review], indicating that, although the probabilities of outcomes can in principle be accurately described in decisions from experience, the actual description is rather inaccurate because it cannot be done at reasonable expenses.

Another property of choice alternatives that is likely to play a role in risky choice but can only be made explicit using a sample representation as in decisions from experience is the sequence in which outcomes occur.
Although a discrete-time collection of i.i.d. random variables cannot, by definition, exhibit temporal regularity, i.e., it cannot produce a stable sequence of sampled outcomes, spurious temporal patterns might nevertheless be regarded as a property of choice alternatives and affect the consequential choice behavior. 
Indeed, the underweighting pattern and other behavioral phenomena like the wavy recency effect and probability matching, are reasonably well captured by models which incorporate the assumption that people rely on (spurious) outcome sequences [@cohenEffectPerceivedPatterns2021; @gaissmaierSmartPotentialProbability2008; @plonskyRelianceSmallSamples2015; @plonskyLearningSettingsPartial2017;  @yuSequentialEffectsSupersition2009].

The preceding two examples illustrate how some properties of choice alternatives can be described in one representation but not in another and how representations can differ with regards to the processing effort required to describe the same property.
Thus, there is generally a trade-off between different representations, where in a given representation certain properties become explicit while others are pushed into the background [@marrVisionComputationalInvestigation1982, p. 21].

## Section 4: Simulation Study

# Appendix

## A1: Probability Measure Over Sample Mean Comparisons

To proof is that the sequence $D_i = D_1, ..., D_n$ describes a Bernoulli process with the number of won comparisons following the binomial distribution $\mathcal{B}\left(p(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0), n \right)$ for fixed sequence lengths $N_X$ and $N_Y$.

Therefore we must demonstrate that the probability of success, i.e., $p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right)$, is identified.
The derivation chain is first roughly paraphrased and then formalized as a mathematical equation.

We start by noting that the probability of success equals the probability of the subset $B_1 \in \mathcal{G}$ which contains all comparisons $c \in C$ that satisfy the inequation $\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0$.
Since the probability of the subset $B_1$ equals the probability that any of its elements occurs, the probabilities of all $c \in B_1$ are summed up. 
We therefore use the sum operator with the limits $j \in \{1, ..., |B_1|\}$, with $|B_1|$ denoting the cardinality of the set $B_1$, i.e., the number of elements within the set. 
As a major assumption is that the random variables within a sample sequence are iid and independent across sequences, the joint probability of a pair $\overline{X}_{N_X} \cap \overline{Y}_{N_Y}$, i.e., a pair $X_i \cap Y_i$ with a unique combination of the number of times any possible realization of $X$ and $Y$ occurs, is described by the product of their individual probabilities $p(\overline{X}_{N_X})$ and $p(\overline{Y}_{N_Y})$.
Finally, to get these individual probabilities, we must determine the probability that each possible realization indeed occurs the respective number of times in the underlying sample sequence.
This probability is given by the multinomial distribution which reduces to a binomial distribution in the case of only two possible realizations. 
We denote the number of times a realization occurs in a sample sequence with $k_{\omega}$, where $\omega$ signals that the realizations of the random variables are numerical equivalent to the outcomes in the sample space of the prospects.

$$
  \begin{split}
    p(D = 1) 
      & = p \left( \; B_1 = \{c \in C: (\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0)\} \in \mathcal{G} \; \right) \\\\\\ 
      & = \sum_{j=1}^{|B_1|} \left( \;
          p(\overline{X}_{N_Xj})  
          \times 
          p(\overline{Y}_{N_Yj}) \; 
        \right)_{j \, \in \, \{1, ..., |B_1|\}} \\\\\\
      & = \sum_{j=1}^{|B_1|} \left( \; 
        p \left( 
          \frac{1}{N_X} \sum\limits_{i = 1}^{N_X} X(\omega \in \Omega_X)_{ij}
        \right) 
        \times
        p \left( 
          \frac{1}{N_Y} \sum\limits_{i = 1}^{N_Y} Y(\omega \in \Omega_Y)_{ij}
        \right) \; 
        \right)_{j \, \in \, \{1, ..., |B_1|\}} \\\\\\
      & = \sum_{j=1}^{|B_1|} \left( \;
        \left(
          {N_X\choose k_{\omega_{1X}j}, ..., k_{\omega_{nX}j}} \prod_{\omega_{iX} \in \Omega_X} p(\omega_{iX})^{k_{\omega_{iX}j}}
        \right)
        \times
        \left(
        {N_Y\choose k_{\omega_{1Y}j}, ..., k_{\omega_{nY}j} } \prod_{\omega_{iY} \in \Omega_Y} p(\omega_{iY})^{k_{\omega_{iY}j}}
        \right)
        \right)_{j \, \in \, \{1, ..., |B_1|\}} \\\\\\
      & = \sum_{j=1}^{|B_1|} \left( \;
        \left(
          \frac{N_X!}{k_{\omega_{1X}j}! \times ... \times k_{\omega_{nX}j}!} 
          \times 
          p(\omega_{1X})^{k_{\omega_{1X}j}} 
          \times 
          ... 
          \times p(\omega_{nX})^{k_{\omega_{nX}j}}
        \right)
        \times
        \left(
          \frac{N_Y!}{k_{\omega_{1Y}j}! \times ... \times k_{\omega_{nY}j}!} 
          \times 
          p(\omega_{1Y})^{k_{\omega_{1Y}j}} 
          \times 
          ... 
          \times p(\omega_{nY})^{k_{\omega_{nY}j}}
        \right)
      \right)_{j \, \in \, \{1, ..., |B_1|\}}
  \end{split}
$$

## A2: Choice Problems

```{r message=FALSE}
gambles <- read_csv("data/gambles/sr_subset.csv")
gambles %>% apa_table()
```

### 2022-01-19 manuscript.Rmd
Renaming of sections and change of figure options

@@
     email         : "linushof@posteo.de"
+
+affiliation:
+  - id            : "1"
+    institution   : "Heidelberg University"
 
@@
    - \usepackage[capposition=top]{floatrow}
-   - \renewcommand\author[1]{}
-   - \renewcommand\affiliation[1]{}
-   - \authorsnames[1]{Linus Hof}
-   - \authorsaffiliations{{Department of Psychology, Heidelberg University}}
 ---
@@
                papaja)
+
+knitr::opts_chunk$set(fig.pos = "tb")
 ```
@@
 The process is schematically shown in Figure 1.
-\
 
@@
 
-# Section 1: Selection Criteria / Properties of Choice Alternatives / Sampling
+# Inputs to the Decision Making Process and Property Descriptions
 
@@
 To stress this point, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2). 
-\
+Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that could result from assessing for each alternative whether it possesses an arbitrary property (collection) or not [cf.
+@jostMathematicalConcepts2015, p.
+16].
 
@@
 
-Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that could result from assessing for each alternative whether it possesses an arbitrary property (collection) or not [cf.
-@jostMathematicalConcepts2015, p.
-16].
 The concept of the power set thereby illustrates how different selection criteria can alter the consequential choice.
@@
 It follows that if there is some variance in the properties across choice alternatives and the properties are not perfectly correlated, changing the selection criteria can eventually change the subset $I'$.
-<!-- Of course, the whole argument rests on the assumption that ... -->
 
-## What Are the Properties of Choice Alternatives and the Selection Criteria?
+## What Are the Choice Alternatives and Their Properties?
 
-The argument so far has been quite general and abstract, since there is no complete answer to the question raised above this paragraph---there is, of course, an uncountable number of decisions and so are there choice alternatives, properties, and selection criteria.
+The argument so far has been quite general and abstract, since there is no complete answer to the question raised above this paragraph---there is, of course, an uncountable number of decisions and so are there choice alternatives and properties.
 Therefore, in the present paper, *prospects* are used as a proxy for the variety of choice alternatives the mind is required to evaluate in natural world decisions. 
@@
 
-## Inferring Property Descriptions by Sampling
+## Inferring Property Descriptions from Sampling Data
 
@@
 
-# Section 2: Underweighting Pattern / Hills and Hertwig (2010) / Induction
+# Evaluation of Choice Alternatives and Outputs of the Decision Making Process
 
-# Section 3: Representation
+...
 
-# Section 4: Simulation Study
+# Sampling Strategies as Representation Systems
+
+...
+
+# Simulation Study
 
@@
   geom_density_2d_filled(contour_var = "ndensity") + 
-  scale_fill_scico_d(palette = "buda") +
-  scale_color_scico_d(palette = "buda") + 
+  scale_fill_scico_d(palette = "grayC") +
+  scale_color_scico_d(palette = "grayC") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) + 
@@
   geom_path() + 
-  scale_color_scico(palette = "buda") + 
+  scale_color_scico(palette = "grayC") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +
@@
   geom_density_2d_filled(contour_var = "ndensity") + 
-  scale_fill_scico_d(palette = "buda") +
+  scale_fill_scico_d(palette = "grayC") +
   scale_x_continuous(breaks = seq(0, 1, .2)) + 
@@
   geom_path(aes(color = s)) +
-  scale_color_scico(palette = "buda") + 
+  scale_color_scico(palette = "grayC") + 
   scale_x_continuous(breaks = seq(0, 20, 5)) +
@@
 
-# Section 5: Discussion and Conclusion
+# Discussion and Conclusion
 
 # References
-
-<div id="refs"></div>
-
-# Appendix

### 2022-01-20 talk-modelers-meeting/slides_modelers-meeting.Rmd
Add slides from modelers' meeting talk

--- 2021-10-11 slides_modelers-meeting.Rmd
@@
   beamer_presentation: default
-bibliography: references_sampling-in-dfe.bib
-csl: apa.csl
 editor_options: 
@@
                scico,
-               ggpubr)
+               ggpubr,
+               here)
 ```
@@
 
-1. Description-experience gap [cf. @wulffMetaanalyticReviewTwo2018]
+1. Description-experience gap [cf. Wulff et al. 2018](https://doi.org/10.1037/bul0000115)
 
@@
 
-- Hills and Hertwig [-@hillsInformationSearchDecisions2010]: Assumption of a systematic link between sampling and decision strategies
+- [Hills and Hertwig (2010)](https://doi.org/10.1177/0956797610387443): Assumption of a systematic link between sampling and decision strategies
 
@@
   + Comprehensive: Single samples from **same** prospect
-
-```{r, echo=FALSE, out.height="40%", out.width="40%", fig.align='center'}
-knitr::include_graphics("hills-hertwig_2010_figure-1.png")
-```
 
@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
+
 cols <- list(.default = col_double(),
@@
              parameter = col_factor())
-cpt <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols)
+cpt <- read_csv(here("data", "estimates", "estimates_cpt.csv"), col_types = cols)
 
@@
              choice = col_factor())
-choices <- read_csv("data/choices/choices.csv", col_types = cols)
+choices <- read_csv(here("data", "choices", "choices.csv"), col_types = cols)
 
@@
 I happily take your questions, comments and critique.
-
-## References

### 2022-01-21 manuscript.Rmd
Update Section 2

@@
  The current version of this manuscript is prepared for submission as a master's thesis.
+ Supervisors: Thorsten Pachur & Veronika Zilker.
 
@@
 
-```{r}
-# load packages
-pacman::p_load(tidyverse, 
-               knitr, 
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(echo = F, fig.pos = "t", fig.align = "l")
+```
+
+```{r packages}
+# load required packages
+pacman::p_load(papaja,
+               readr,
+               tidyr, 
+               dplyr,
+               ggplot2,
                ggbeeswarm,
-               scico, # for scientific color palettes
-               papaja)
-
-knitr::opts_chunk$set(fig.pos = "tb")
+               scico)
 ```
@@
 Hence, to explain how the mind makes a selection among choice alternatives, one needs to understand the output controlling properties, i.e., the applied selection criteria, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
-The process is schematically shown in Figure 1.
+The process is sketched in Figure 1.
 
@@
 
-```{r fig.cap="(ref:figure1)", fig.align='left'}
-knitr::include_graphics("manuscript_files/figure-png/figure1.png")
+```{r fig.cap= "(ref:figure1)"}
+knitr::include_graphics("images/dm-sketch.png")
 ```
 
-In what follows, this paper will elaborate on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate a rather important principle:
+In what follows, the paper elaborates on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate a rather important principle:
 Given that the mind is indeed sensitive to variations in the property values, the more accurately their descriptions are inferred, the more systematic the choices should become.
@@
 To stress this point, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).
-Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that could result from assessing for each alternative whether it possesses an arbitrary property (collection) or not [cf.
-@jostMathematicalConcepts2015, p.
-16].
 
@@
 
-```{r fig.cap="(ref:figure2)", fig.align='left'}
-knitr::include_graphics("manuscript_files/figure-png/figure2.png")
+```{r fig.cap= "(ref:figure2)"}
+knitr::include_graphics("images/power-set.png")
 ```
 
+Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that could result from assessing for each alternative whether it possesses an arbitrary property (collection) or not [cf.
+@jostMathematicalConcepts2015, p.
+16].
 The concept of the power set thereby illustrates how different selection criteria can alter the consequential choice.
@@
 @knightRiskUncertaintyProfit1921, especially Chapter 1 for a brief discussion closely related to the current subject].
-Moreover, the case suffices to answer the above question and to subsequently address the induction and representation problem, at least within the stated limitations.
 
@@
 For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such.
-See Georgii [-@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1] for a comprehensive mathematical treatment.]
+See Georgii [-@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1] for a comprehensive but accessible mathematical treatment.]
+
 $P$ is a probability measure
@@
 @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.2].]
+
 In less technical terms, following the choice of a prospect, one of the outcomes associated with this particular prospect is obtained, a gain or loss respectively.
@@
 
-Given (3), it is evident that the prospects can only be distinguished by the elements of their tuples, and these elements are properties---be that a smallest single element, e.g., an outcome, collections thereof, e.g., the sample space $\Omega$, or more complex combinations of elements, e.g., the weighted average which is obtained by first multiplying all outcomes in $\Omega$ by their respective probabilities in $P$ and then summing the resulting products.^[I do not refer to this quantity as expected value, since the term is reserved for random variables, which were not introduced so far.]
-In turn, for choices between prospects, selection criteria are statements about the elements of their tuples that are true or false and these statements imply relations among prospects that are at least nominal, e.g., *"One of the prospect's outcome is positive in value"*, but may also draw on other levels of measurement, e.g., *"The prospect's average mean is the largest among the prospects"* refers to an ordinal level.
+Given (3), it is evident that the prospects can only be distinguished by the elements of their tuples. 
+These elements are, generally speaking, symbols, some of which describe properties on their own, e.g., the outcome $\omega$, whereas other properties can only be described by collections of symbols, e.g., the sample space $\Omega$ by a set of outcomes as in (2.1), or more complex combinations thereof, e.g., the weighted average which is obtained by first multiplying all outcomes in $\Omega$ by their respective probabilities in $P$ and then summing the resulting products.^[I do not refer to this quantity as expected value, since the term is reserved for random variables, which were not introduced so far.]
+In turn, for choices between prospects, selection criteria are statements about the elements of their tuples that are true or false and these statements imply relations among prospects that are at least nominal, but may also draw on other levels of measurement.
 
@@
 
-Using Marr's [-@marrVisionComputationalInvestigation1982] framework, the sensitivity aspect addresses the algorithmic level and refers to the achievement that the true properties of the choice alternatives are accurately described and the resulting relations among the alternatives are properly evaluated [cf.
-@brunswikOrganismicAchievementEnvironmental1943].
-Note that if the descriptions of the relevant properties were available, the process sketched out in Figure 1 would be substantially simplified since the two intermediate steps of representation and property description would be omitted.
-For quite many decisions the mind faces, however, it is simply not the case that the properties of interest, e.g., outcome probabilities, are readily described and amenable to direct assessment, as has been repeatedly stated [e.g., @busemeyerChoiceBehaviorSequential1982; @fiedlerBewareSamplesCognitiveecological2000; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; see also @brunswikRepresentativeDesignProbabilistic1955; @brunswikPerceptionRepresentativeDesign1956, for a detailed treatment].
-In such cases, to obtain the respective descriptions from the inputs, the mind is required to make an inference from the available information.
+Note that a selection criterion may refer to a property for which the raw input, i.e., the symbols, their organization, and the information they encode, do not yet provide an explicit description.
+Even more so, it has been repeatedly stated that for quite many decisions the mind faces, it is simply not possible to draw on direct descriptions of the properties, since they are part of the distal environment  [e.g., @fiedlerExplainingSimulatingJudgment1996; @hertwigDescriptionexperienceGapRisky2009; see also @brunswikRepresentativeDesignProbabilistic1955; @brunswikPerceptionRepresentativeDesign1956; @kozyrevaInterpretationUncertaintyEcological2021].
+In either case, some form of description must be inferred from whatever information the input provides about the property in question.
+Consider first the counterfactual case of the prospect whose tuple is not part of the distal environment but is directly described. 
+Since all information about the prospect is given, one may in principle consider the input complete, yet, the tuple implies properties of the prospect which are not explicitly described.
+For example, to obtain the description of the prospect's weighted average, still a calculus according to the algebraic rules described in the preceding paragraph must be carried out. 
+In general, in cases like the one just considered, where the properties are not distal and all information about them is available, property inferences take the form of a mere transformation, where the symbols from the input are ordered and/or combined according to some transformation rules [cf.
+@marrVisionComputationalInvestigation1982, p.
+20].
+In natural world decisions, however, the relevant properties of choice alternatives are often distal and amenable only through a *sample* which, by definition, cannot provide complete information.
+Such a sample requires the mind to make an inductive inference, leading to a description which, according to the law of large numbers [cf., e.g., @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 5.1], is only probable in proportion to the size of the (representative) sample [but see @fiedlerInformationSamplingAdaptive2006, for a selection of papers which goes beyond the mere discussion of statistically representative samples].
 
-In such a choice paradigm, agents are asked to evaluate the prospects and build a preference for either one of them. 
-It is common to make a distinction between two variants of this evaluation process [cf. @hertwigDescriptionexperienceGapRisky2009]. 
+To express the idea that the tuple of a prospect is not given
+
+As for prospects, a sample is  sample has a well defined meaning
 For decisions from description (DfD), agents are provided a full symbolic description of the prospects.
@@
 
-```{r message=FALSE}
+```{r include=FALSE}
 
@@
 
-```{r fig.cap="Test"}
+```{r eval=FALSE}
 
@@
 
-```{r}
+```{r eval=FALSE}
 
@@
 
-```{r fig.cap="test 2"}
+```{r eval=FALSE}
 
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r eval=FALSE}
 
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r eval=FALSE}
 fr_rates %>% 
@@
 
-```{r}
+```{r eval=FALSE}
 # value function

### 2022-01-22 manuscript.Rmd
Update section 2

@@
 20].
-In natural world decisions, however, the relevant properties of choice alternatives are often distal and amenable only through a *sample* which, by definition, cannot provide complete information.
-Such a sample requires the mind to make an inductive inference, leading to a description which, according to the law of large numbers [cf., e.g., @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 5.1], is only probable in proportion to the size of the (representative) sample [but see @fiedlerInformationSamplingAdaptive2006, for a selection of papers which goes beyond the mere discussion of statistically representative samples].
 
-To express the idea that the tuple of a prospect is not given
+In natural world decisions, however, the properties of choice alternatives are often distal and amenable only through their probabilistic relation to proximal cues or samples.
+Such a proximal information basis, obtained by experience or, more technically, by *sampling*, is neither consistent nor complete but requires the mind to draw inductive inferences to arrive at property descriptions which then, by definition, are only probable.
+In turn, the "achievement" [@brunswikOrganismicAchievementEnvironmental1943, p.
+255] of the mind, i.e., highly probable descriptions, depends in part ...
+[but see @fiedlerInformationSamplingAdaptive2006, for a selection of papers which goes beyond the mere discussion of statistically representative samples].
 
-As for prospects, a sample is  sample has a well defined meaning
-For decisions from description (DfD), agents are provided a full symbolic description of the prospects.
-For decisions from experience [DfE; e.g., @hertwigDecisionsExperienceEffect2004], prospects are not described but must be explored by the means of sampling.
+To adapt (3) such that it fits to the sampling, as it is done for decisions from experience [@hertwigDecisionsExperienceEffect2004], we define sampling as follows:
 

### 2022-01-23 manuscript.Rmd
Update Section 2

@@
 
-Since it was stated that the inputs to the decision making process can be organized in a set of choice alternatives, we can adapt (1) for the case of a choice between $1, ..., n$ prospects to obtain:
+Since it was stated that the inputs to the decision making process can be organized in a set of choice alternatives, we can adapt (1) for the case of a choice between $1, ..., k$ prospects to obtain:
 
 $$
-\iota : I' \mapsto I, \ \text{where} \ I = \{(\Omega_1,  \mathcal{F}_1, P_1), ..., (\Omega_n,  \mathcal{F}_n, P_n)\}
+\iota : I' \mapsto I, \ \text{where} \ I = \{(\Omega_1,  \mathcal{F}_1, P_1), ..., (\Omega_k,  \mathcal{F}_k, P_k)\}
 \; .
@@
 Note that a selection criterion may refer to a property for which the raw input, i.e., the symbols, their organization, and the information they encode, do not yet provide an explicit description.
-Even more so, it has been repeatedly stated that for quite many decisions the mind faces, it is simply not possible to draw on direct descriptions of the properties, since they are part of the distal environment  [e.g., @fiedlerExplainingSimulatingJudgment1996; @hertwigDescriptionexperienceGapRisky2009; see also @brunswikRepresentativeDesignProbabilistic1955; @brunswikPerceptionRepresentativeDesign1956; @kozyrevaInterpretationUncertaintyEcological2021].
+Even more so, it has been repeatedly stated that for quite many decisions the mind faces, it is simply not possible to draw on direct descriptions of the properties, since they are part of the distal environment  [e.g., @brunswikOrganismicAchievementEnvironmental1943; @fiedlerExplainingSimulatingJudgment1996; @hertwigDescriptionexperienceGapRisky2009; see also @brunswikRepresentativeDesignProbabilistic1955; @brunswikPerceptionRepresentativeDesign1956; @kozyrevaInterpretationUncertaintyEcological2021].
 In either case, some form of description must be inferred from whatever information the input provides about the property in question.
@@
 For example, to obtain the description of the prospect's weighted average, still a calculus according to the algebraic rules described in the preceding paragraph must be carried out. 
-In general, in cases like the one just considered, where the properties are not distal and all information about them is available, property inferences take the form of a mere transformation, where the symbols from the input are ordered and/or combined according to some transformation rules [cf.
+In general, in cases like the one just considered, where the properties are not distal and all information about them is available, property inferences take the form of a mere transformation, where the symbols from the input are ordered and combined according to some transformation rules [cf.
 @marrVisionComputationalInvestigation1982, p.
@@
 
-In natural world decisions, however, the properties of choice alternatives are often distal and amenable only through their probabilistic relation to proximal cues or samples.
-Such a proximal information basis, obtained by experience or, more technically, by *sampling*, is neither consistent nor complete but requires the mind to draw inductive inferences to arrive at property descriptions which then, by definition, are only probable.
-In turn, the "achievement" [@brunswikOrganismicAchievementEnvironmental1943, p.
-255] of the mind, i.e., highly probable descriptions, depends in part ...
-[but see @fiedlerInformationSamplingAdaptive2006, for a selection of papers which goes beyond the mere discussion of statistically representative samples].
+In natural world decisions, however, the properties of choice alternatives are often distal and amenable only through their probabilistic relation to proximal cues or samples, which provide the input to the decision making process [cf.
+@brunswikOrganismicAchievementEnvironmental1943].
+Such a proximal information basis is obtained by experience or, more technically, by *sampling*, and is neither consistent nor complete but varies in its degree of representativeness. 
+In turn, the mind is not merely required to transform the inputs but to draw inductive inferences to arrive at property descriptions which then, by definition, are only probable. 
+Importantly, the probability, or accuracy, of the description depends on both the sampling process that determines the representativeness of the sample and the use of the probabilistic information that is entailed in the sample [e.g., @fiedlerBewareSamplesCognitiveecological2000].
 
-To adapt (3) such that it fits to the sampling, as it is done for decisions from experience [@hertwigDecisionsExperienceEffect2004], we define sampling as follows:
+To adapt (3) for the case of decisions from experience [@hertwigDecisionsExperienceEffect2004], the tuples $(\Omega, \mathcal{F}, P)$ must be replaced by samples, which in this paper are treated as collections of independent and identically distributed (i.i.d.) random variables $X$.^[Note that this paper considers the counterfactual case where samples are random, although it has been stated that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+660].
+To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
+Specifically, random variables are defined as a measurable function
+
+$$
+X: (\Omega, \mathcal{F})  \mapsto (\Omega', \mathcal{F'}) 
+\; ,
+\tag{4}
+$$
+
+where $\Omega'$ is a set of real numbered values $X$ can take and $\mathcal{F'}$ is a set of subsets of $\Omega'$. 
+I.e., $\Omega$ maps into $\Omega'$ such that correspondingly each subset $A' \in \mathcal{F'}$ has a pre-image $X^{-1}A' \in \mathcal{F}$, which is the set $\{\omega \in \Omega: X(\omega) \in A'\}$ [@kolmogorovFoundationsTheoryProbability1950, p.
+21].
+
+$$
+\begin{aligned}
+  & \iota : I' \mapsto I, \ \text{where} \ I = \{X_{1i}, ..., X_{ki}\} \\
+  & i \in \{1, ..., N\} 
+  \; .
+\end{aligned}
+\tag{5}
+$$
 
@@
 It is acceptable to speak of the occurrence of $\omega$ as a realization of a random variable $X$ defined on a prospect iff the following conditions (1) and (2) are met:
-
-(1) $X$ is a measurable function $$X: (\Omega, \mathcal{F})  \mapsto (\Omega', \mathcal{F'}) \; ,$$ where $\Omega'$ is a set of real numbered values $X$ can take and $\mathcal{F'}$ is a set of subsets of $\Omega'$.
-I.e., $\Omega$ maps into $\Omega'$ such that correspondingly each subset $A' \in \mathcal{F'}$ has a pre-image $X^{-1}A' \in \mathcal{F}$, which is the set $\{\omega \in \Omega: X(\omega) \in A'\}$ [@kolmogorovFoundationsTheoryProbability1950, p.
-21].
 

### 2022-01-27 manuscript.Rmd
Update Introduction

@@
 @jostMathematicalConcepts2015, pp.
-14-15], indicating that decision making is a *process* that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
+14-15], indicating that decision making is a process that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives [see @heOntologyDecisionModels2020].
+
+Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from particular decisions, e.g., the choice between job offers, political parties to vote for, travel destinations, investment plans, and so on.
+Rather, with the choice between at least two *prospects*, it considers a case which is counterfactual in that it omits the many particularities of decisions and the differences among them, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See also @knightRiskUncertaintyProfit1921, especially Chapter 1, for a brief discussion of the reasonableness of such abstractions.]
+These fundamental properties are conceived of as the possible outcomes of a choice alternative and the probabilities with which these outcomes occur following the choice of the respective alternative.
+Prospects therefore resemble a probability mass function
+
+$$
+p: \Omega \mapsto [0,1]
+\; ,
+\tag{2}
+$$
+
+which assigns each possible outcome in the finite set $\Omega = \{\omega_1, ..., \omega_n\}$ a probability $0 < p(\omega) \leq 1$ with $\sum_{\omega \in \Omega} p(\omega) = 1$.
+
+The actual choices of people in such a decision paradigm are often assessed in terms of their deviation from choosing the prospect with the largest expected value (EV), a quantity obtained by first multiplying all outcomes in $\Omega$ by their respective probabilities and then summing the resulting products:
+
+$$
+EV = \sum_{\omega \in \Omega} \omega \times p(\omega)
+\; .
+\tag{3}
+$$
+
+In fact, the many assessments of peoples' choices neither corroborate the theory that people follow the principle of EV maximization nor that of expected utility (EU) maximization [e.g., @kahnemanProspectTheoryAnalysis1979, ...].^[Following the EU principle [@bernoulliExpositionNewTheory1954], the objective outcomes in (3) are transformed by a concave utility function.
+This transformation expresses the idea that an increase of the objective outcome yields a diminishing increase in its subjective utility, where the latter are weighted by the objective probability to assess the value of a prospect.]
+To *describe* the deviations from EV/EU maximization, the models of subjective expected utility theory [for an overview, see @heOntologyDecisionModels2020; @stottCumulativeProspectTheory2006] replace the objective outcomes and probabilities in (3) by parameterized nonlinear transformations thereof to obtain:
+
+$$
+V_{SEUT} = \sum_{\omega \in \Omega} v(\omega) \times w(p(\omega))
+\; .
+\tag{4}
+$$
+
+Importantly, 
+Rather, the 
+, which has lead to the description of some robust phenomena.  
+The parameters of the outcome function $v(\omega)$ and the probability weighting function $w(p(\omega))$ can 
+One such model is the cumulative prospect theory [@tverskyAdvancesProspectTheory1992]
+
 Given that the choice is perfectly systematic---as opposed to random or noisy---the chosen alternatives in $I'$ should share some property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
@@
 Given conditions (1) and (2), we denote any observation of $\omega$ as a *"single sample"*, or realization, of a random variable defined on a prospect and the act of generating a sequence of single samples in discrete time as *"sequential sampling"*.
-Note that, since random variables defined on the same prospect are independent and identically distributed (iid), the weak law of the large number applies to the relative frequency of occurrence of an outcome $\omega$ in a sequence of single samples originating from the same prospect [cf.
-@bernoulliArsConjectandiOpus1713].
+Note that, since random variables defined on the same prospect are independent and identically distributed (iid), the weak law of the large number applies to the relative frequency of occurrence of an outcome $\omega$ in a sequence of single samples originating from the same prospect.
 Thus, long sample sequences in principle allow to obtain the same information about a prospect by sampling as by symbolic description.

### 2022-01-31 manuscript.Rmd
Update introduction

--- 2022-01-23 manuscript.Rmd
@@
 
-<!-- Introduction -->
-
-The mind is a cognitive system that operates on inputs from an environment or memory.
+<!--The mind is a cognitive system that operates on inputs from an environment or memory.
 In the domain of decision making, such inputs can be organized in a set $I$ of choice alternatives $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess.
@@
 @jostMathematicalConcepts2015, pp.
-14-15], indicating that decision making is a *process* that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
+14-15], indicating that decision making is a process that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives [see @heOntologyDecisionModels2020].-->
+
+Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from particular decisions, e.g., the choice between job offers, political parties to vote for, travel destinations, investment plans, and whatnot.
+Rather, with the choice between at least two *prospects* (or: gambles), it studies a case which is counterfactual in that it omits the many particularities of each decision and the differences between them, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See Chapter 1 in @knightRiskUncertaintyProfit1921, for a discussion of the reasonableness of such abstractions.]
+These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by the Greek letter $\omega$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p(\omega)$.
+Thus, prospects are abstract surrogates for choice alternatives in the natural world, resembling probability mass functions of the form 
+$$
+p: \Omega \mapsto [0,1]
+\; ,
+\tag{1}
+$$ 
+each of which assigns the possible outcomes in a finite set $\Omega = \{\omega_1, ..., \omega_n\}$ a probability $0 < p(\omega_i) \leq 1$, where $i \in \{1, ..., n\}$ and $\sum_i^n p(\omega_i) = 1$.
+
+The choices people actually make between such prospects are often described in terms of their deviation from the principle of expected value (EV) maximization, where the EV is given by 
+$$
+EV = \sum_i^n \omega_i \times p(\omega_i)
+\; .
+\tag{2}
+$$ 
+That is, following the principle of EV maximization, people would first calculate the prospects' EV according to (2) and thereafter chose the prospect for which the EV is maximized.
+<!--However, the many assessments of peoples' choices in these decisions neither corroborate the theory that people follow the principle of EV maximization nor that of expected utility (EU) maximization [e.g., @kahnemanProspectTheoryAnalysis1979, ...].^[Following the EU principle [@bernoulliExpositionNewTheory1954], the objective outcomes in (2) are transformed by a concave utility function.
+This transformation expresses the idea that an increase in the objective outcome yields a diminishing increase in its subjective utility, where the latter is weighted by the objective probability to compute the expected utility of a prospect.
+Note that for negative outcomes the transformation function is convex.]-->
+To *describe* peoples' deviations from EV <!--and EU--> maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; see also @stottCumulativeProspectTheory2006, for an overview of models] may replace the objective outcomes and probabilities in (2) by nonlinear transformations thereof.
+More specifically, the models contain a combination of two parameterized <!--monotonic--> functions, one transforming the objective outcomes---referred to as the *value function*, $\omega \mapsto v(\omega)$---and the other transforming the cumulative distribution function of objective probabilities---referred to as the *probability weighting function*, $p(\omega) \mapsto w(p(\omega))$ or $p(\omega) \mapsto w(p(\omega))$.
+<!--Note that the probability weighting function is a composition of two functions $\omega \maps to p(\omega) \maps to w(p(\omega))$.-->
+
+The shape of the probability weighting function lead to the common interpretation that people choose as if they were over- or underweighting outcomes of certain probability (see Figure 1). 
+```{r}
+wf <- tibble(gamma = c(.7, 1, 1.5), 
+             type = c("overweighting", "linear", "underweighting")) %>%
+  expand_grid(prob = seq(0, 1, .01)) %>%
+  mutate(w = exp(-1*(-log(prob))^gamma)) %>% 
+  select(-gamma)
+
+ggplot(wf) +
+  geom_path(aes(prob, w, linetype = type)) +
+   scale_linetype_manual(values=c("solid", "dotted", "longdash")) +
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_y_continuous(breaks = seq(0, 1, .1)) + 
+  labs(x = expression(paste("p(", omega, ")")),
+       y = expression(paste("w(p(", omega, "))")),
+       linetype = "Weighting Pattern") + 
+  theme_apa() 
+```
+
+One such model is the cumulative prospect theory [@tverskyAdvancesProspectTheory1992]
+
+$$
+\tag{3}
+$$
+
 Given that the choice is perfectly systematic---as opposed to random or noisy---the chosen alternatives in $I'$ should share some property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.

### 2022-02-02 manuscript.Rmd
Update introduction

--- 2022-01-23 manuscript.Rmd
@@
 
-The mind is a cognitive system that operates on inputs from an environment or memory.
-In the domain of decision making, such inputs can be organized in a set $I$ of choice alternatives $i \in I$, the latter being distinguishable from each other on the basis of the *properties* they possess.
-The basic structure of decision making may then be modeled by the inclusion map
-
+The human mind is a cognitive system that operates on inputs from an environment or memory. 
+In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose. 
+Given that each choice alternative is an element $i$ of the set $I$, the basic structure of decision making may be modeled by the inclusion map
 $$
 \begin{aligned}
-  & \iota : I' \mapsto I \\
-  & \iota(i) = i \ \text{for all} \ i \in I' 
+  \iota : I' &\to I \\
+  i &\mapsto i \quad \text{for all} \ i \in I' 
 \end{aligned}
@@
 $$
+[@jostMathematicalConcepts2015, pp.
+14-15], indicating that decision making is an information processing problem which starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
+Indeed, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives to return a subset thereof as outputs [@heOntologyDecisionModels2020].
 
-[cf.
-@jostMathematicalConcepts2015, pp.
-14-15], indicating that decision making is a *process* that starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
+However, information about the choice alternatives may come in many forms.
+Rarely in their daily life, people make *decisions from description*, since in such a case all information about the choice alternatives is available through symbolic descriptions of their *properties*.
+Yet, rather often, people make *decisions from experience* [@hertwigDecisionsExperienceEffect2004], since
+
+# Header
+
+Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from particular decisions, e.g., the choice between job offers, political parties to vote for, travel destinations, investment plans, and whatnot.
+Rather, with the choice between at least two *prospects* (or: gambles), it studies a case which is counterfactual in that it omits the many particularities of each decision and the differences between them, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983; see also @knightRiskUncertaintyProfit1921, for a discussion of the reasonableness of such abstractions].
+These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by the Greek letter $\omega$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p(\omega)$.
+
+Now, let a prospect be a *probability space* denoted by the tuple $(\Omega, \mathcal{F}, P)$. 
+Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ denotes the sample space, containing a finite set of possible outcomes:
+$$
+\omega_i \in \{\omega_1, ..., \omega_n\} = \Omega
+\; .
+\tag{2}
+$$ 
+$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$.^[Note that this paper considers only the case of finite sample spaces.
+The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
+2-3 and 14-15], also covers infinite sample spaces and is that of a $\sigma$-algebra.
+For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such [@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1].]
+$P$ is a probability measure
+$$
+P: \mathcal{F} \mapsto [0,1]
+\; ,
+\tag{3}
+$$
+which assigns each subset $A \in \mathcal{F}$, also referred to as *events*, a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$ [@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.2].]
+
+The choices people actually make between such prospects are often described in terms of deviations from expected value (EV) maximization, where the EV is given by 
+$$
+EV = \sum_i^n \omega_i \times P(X = \omega_i)
+\; ,
+\tag{4}
+$$ 
+with $X$ being a random variable defined on the respective probability space.^[$X$ is measurable function $X: \Omega \to \Omega'$ [see @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.3] with $\omega \mapsto \omega$ for all $\omega \in \Omega$.]
+That is, following the principle of EV maximization, one would first calculate the prospects' EV according to (3) and thereafter chose the prospect with the largest EV.
+To *describe* how peoples' choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data with a combination of two parameterized functions that may replace the objective outcomes and probabilities in (3) by nonlinear transformations thereof.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
+That is, the models of CPT fit choice data by maximizing the value 
+$$
+V = \sum_i^n v(\omega_i) \times \pi_i
+\; ,
+\tag{5}
+$$ 
+with subjective values $v(\omega)$ derived from a *value function* that may transform the objective outcomes, and decision weights $\pi$ derived from the objective probabilities' cumulative distribution function that may be transformed by a *probability weighting function* (see below).
+Now, since the probability weighting function may redistribute the entire probability mass of $\sum_i^n p(\omega_i) = 1$ across outcomes, the decision weights 
+$$
+\pi =
+  \begin{cases}
+     w(P(X \geq \omega_i)) - w(P(X > \omega_i)) \quad \text{for} \ 1, \\
+     w(P(X \leq \omega_i)) - w(P(X < \omega_i)) \quad \text{else}, 
+  \end{cases}
+\tag{5}
+$$
+may 
+people's deviations from EV maximization is often described in terms of the probability weighting pattern.
+
+Now, in rather general terms, if people were following the principle of EV maximization, the estimates for the parameters of both functions (see below) would be such that the resulting subjective values and decision weights are equal to the objective outcomes and probabilities, i.e., $v(\omega) = \omega$ and $\pi = p(\omega)$.
+However, for deviations from EV maximization, at least one of the equations should not hold.
+
+The value function 
+$$
+\begin{aligned}
+  v : \Omega &\to \mathbb{R} \\
+  \omega &\mapsto
+  \begin{cases}
+     \omega^a \qquad \qquad \text{for} \ \omega > 0, \\
+    -\lambda \times|\omega|^a \quad \text{else}, 
+  \end{cases}
+\end{aligned}
+\tag{4}
+$$ 
+where $a \in [0,1]$ and $\lambda > 1$ [but see @stottCumulativeProspectTheory2006, for alternative functional forms], transforms the objective outcomes $\omega$ into subjective values $v(\omega)$.
+The *probability weighting function*, for which several functional forms have been proposed [e.g., @goldsteinExpressionTheoryPreference1987, see also Equation 5]  
+$$
+w
+\tag{5}
+$$ 
+transforms the cumulative distribution function of the objective probabilities to derive the subjective decision weights.
+
+The shape of the probability weighting function lead to the common interpretation that people choose as if they were over- or underweighting outcomes of certain probability (see Figure 1).
+
+```{r}
+wf <- tibble(gamma = seq(.1, 1.9, .05)) %>%
+  expand_grid(prob = seq(0, 1, .01)) %>%
+  mutate(w = (prob^gamma)/((prob^gamma)+(1-prob)^gamma))
+
+ggplot(wf) +
+  geom_line(aes(prob, w, group = gamma, color = gamma)) +
+  scale_color_scico(palette = "cork") + 
+  scale_x_continuous(breaks = seq(0, 1, .1)) +
+  scale_y_continuous(breaks = seq(0, 1, .1)) + 
+  labs(x = expression(paste("p(", omega, ")")),
+       y = expression(pi), 
+       color = expression(gamma)) + 
+  theme_apa() 
+```
+
 Given that the choice is perfectly systematic---as opposed to random or noisy---the chosen alternatives in $I'$ should share some property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.

### 2022-02-04 manuscript.Rmd
Update Introduction

@@
 The human mind is a cognitive system that operates on inputs from an environment or memory. 
-In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose. 
-Given that each choice alternative is an element $i$ of the set $I$, the basic structure of decision making may be modeled by the inclusion map
-$$
-\begin{aligned}
-  \iota : I' &\to I \\
-  i &\mapsto i \quad \text{for all} \ i \in I' 
-\end{aligned}
-\tag{1}
-$$
-[@jostMathematicalConcepts2015, pp.
-14-15], indicating that decision making is an information processing problem which starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
+In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose and may therefore be organized in a set $I$ with each element $i \in I$ denoting a choice alternative.
+That is, each element $i \in I$ is assigned some information from the inputs and this information may be used by the mind to learn about the respective choice alternative.
+In turn, decision making can be considered an information processing problem which starts from the set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
 Indeed, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives to return a subset thereof as outputs [@heOntologyDecisionModels2020].
 
-However, information about the choice alternatives may come in many forms.
-Rarely in their daily life, people make *decisions from description*, since in such a case all information about the choice alternatives is available through symbolic descriptions of their *properties*.
-Yet, rather often, people make *decisions from experience* [@hertwigDecisionsExperienceEffect2004], since
+Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, travel destinations, investment plans, and whatnot.
+Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental *properties* that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, for a discussion of the reasonableness of such abstractions.]
+These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by the Greek letter $\omega$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p(\omega)$.
+That is, any choice alternative that can be fully described by its outcomes and their probabilities is a prospect. 
+For illustration, take the choice alternatives in the following example with monetary outcomes:
 
-# Header
+\noindent
+**Example 1.** 
+*A1 gives \$1 with 100%.*
+*A2 gives \$10 with 90% and \$0 with 10%.*
 
-Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from particular decisions, e.g., the choice between job offers, political parties to vote for, travel destinations, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* (or: gambles), it studies a case which is counterfactual in that it omits the many particularities of each decision and the differences between them, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983; see also @knightRiskUncertaintyProfit1921, for a discussion of the reasonableness of such abstractions].
-These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by the Greek letter $\omega$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p(\omega)$.
-
-Now, let a prospect be a *probability space* denoted by the tuple $(\Omega, \mathcal{F}, P)$. 
+Now, let the exact axiomatic definition of a prospect be that of a *probability space* denoted by the tuple $(\Omega, \mathcal{F}, P)$. 
 Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ denotes the sample space, containing a finite set of possible outcomes:
@@
 \; .
-\tag{2}
+\tag{1}
 $$ 
-$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$.^[Note that this paper considers only the case of finite sample spaces.
+$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$, with each element $A \in P(\Omega)$ being a subset of $\Omega$.^[Note that this paper considers only the case of finite sample spaces.
 The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
@@
 \; ,
+\tag{2}
+$$
+which assigns each subset $A \in \mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$.]
+Given a choice between 1, ..., k prospects, the inputs from the environment or memory should therefore provide information about the set
+$$
+I = \{(\Omega_1, \mathcal{F}_1, P_1), ... ,(\Omega_k, \mathcal{F}_k, P_k)\}
+\; .
 \tag{3}
 $$
-which assigns each subset $A \in \mathcal{F}$, also referred to as *events*, a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$ [@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.2].]
 
-The choices people actually make between such prospects are often described in terms of deviations from expected value (EV) maximization, where the EV is given by 
+However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes and their probabilities (as in Example 1).
+In such cases, people would make *decisions from description* (DfD), since the information from which the mind learns about the choice alternatives---the probability spaces in (3)---are complete descriptions thereof.
+Yet, rather often, people make *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], where the mind can learn about the choice alternatives only from a record of past experiences with them, which necessarily provides only incomplete and probable information.
+That is, people may have experienced the possible outcomes of a choice alternative when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular choice alternative is denoted a *sample*.
+The mind may then infer from the relative frequency with which an outcome occurs in such a sample of past decisions its probability of occurrence for a future decision. 
+Of course, all other things being equal, the accuracy of this inference depends on the size of the sample.
+<!--For illustration, take the sampled outcomes in the following example, where alternative A2 from Example 1 was chosen ten times without prior knowledge about the possible outcomes of this alternative and their probabilities:
+
+\noindent
+**Example 2.** *A2 gave: \$0, \$0, \$10, \$0, \$0, \$0, \$0, \$10, \$0, \$0*
+
+\noindent
+One may now make an inference from the sample about the possible outcomes of choice alternative A2 and their probabilities. 
+However, this conclusion is not certain, but only probable, since the relative frequencies of the results will almost surely change as the sample size increases.-->
+
+To provide a mathematical definition, this paper treats a sample as a collection of independent and identically distributed (i.i.d.) random variables $X$, each of which is a measurable function defined on the same probability space:^[Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+660].
+To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
+$$
+\begin{aligned}
+  X : (\Omega, \mathcal{F}) &\to (\Omega', \mathcal{F}') \\
+  \omega &\mapsto \omega  \quad \text{for all} \ \omega \in \Omega
+\end{aligned}
+\tag{4}
+$$
+[see @kolmogorovFoundationsTheoryProbability1950, p. 21; see also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.3, for a more accessible and comprehensive treatment]. 
+Accordingly, the inputs to DfE 
+$$
+S = \{X_{1i}, ... , X_{ki}\}
+\; ,
+\tag{5}
+$$
+where $i \in \{1, ..., n\}$.
+
+The choices people actually make between prospects---be that on the basis of ---are often described in terms of deviations from expected value (EV) maximization, where the EV is given by 
 $$
 EV = \sum_i^n \omega_i \times P(X = \omega_i)
-\; ,
-\tag{4}
+\; .
+\tag{6}
 $$ 
-with $X$ being a random variable defined on the respective probability space.^[$X$ is measurable function $X: \Omega \to \Omega'$ [see @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.3] with $\omega \mapsto \omega$ for all $\omega \in \Omega$.]
-That is, following the principle of EV maximization, one would first calculate the prospects' EV according to (3) and thereafter chose the prospect with the largest EV.
+That is, following the principle of EV maximization, one would first calculate the prospects' EV according to (6) and thereafter chose the prospect with the largest EV.
 To *describe* how peoples' choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data with a combination of two parameterized functions that may replace the objective outcomes and probabilities in (3) by nonlinear transformations thereof.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function [see, e.g., @rieskampProbabilisticNaturePreferential2008].]

### 2022-02-06 manuscript.Rmd
Change Figure 1

@@
 Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, travel destinations, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental *properties* that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, for a discussion of the reasonableness of such abstractions.]
+Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental *properties* that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion of the reasonableness of such abstractions.]
 These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by the Greek letter $\omega$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p(\omega)$.
@@
 $$ 
-$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$, with each element $A \in P(\Omega)$ being a subset of $\Omega$.^[Note that this paper considers only the case of finite sample spaces.
+$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$ with each element $A \in P(\Omega)$ being a subset of $\Omega$.^[Note that this paper considers only the case of finite sample spaces.
 The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
@@
 Of course, all other things being equal, the accuracy of this inference depends on the size of the sample.
-<!--For illustration, take the sampled outcomes in the following example, where alternative A2 from Example 1 was chosen ten times without prior knowledge about the possible outcomes of this alternative and their probabilities:
+For illustration, take the sampled outcomes in the following example, where alternative A2 from Example 1 was chosen ten times without prior knowledge about the possible outcomes of this alternative and their actual probabilities:
 
@@
 One may now make an inference from the sample about the possible outcomes of choice alternative A2 and their probabilities. 
-However, this conclusion is not certain, but only probable, since the relative frequencies of the results will almost surely change as the sample size increases.-->
+However, this conclusion is not certain, but only probable, since the relative frequencies of the results will almost surely change as the sample size increases.
 
@@
 That is, following the principle of EV maximization, one would first calculate the prospects' EV according to (6) and thereafter chose the prospect with the largest EV.
-To *describe* how peoples' choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data with a combination of two parameterized functions that may replace the objective outcomes and probabilities in (3) by nonlinear transformations thereof.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
+To *describe* how peoples' choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data with a combination of two parameterized functions that may replace the objective outcomes and probabilities in (6) by nonlinear transformations thereof.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
 That is, the models of CPT fit choice data by maximizing the value 
@@
 \; ,
-\tag{5}
+\tag{7}
 $$ 
-with subjective values $v(\omega)$ derived from a *value function* that may transform the objective outcomes, and decision weights $\pi$ derived from the objective probabilities' cumulative distribution function that may be transformed by a *probability weighting function* (see below).
-Now, since the probability weighting function may redistribute the entire probability mass of $\sum_i^n p(\omega_i) = 1$ across outcomes, the decision weights 
+with subjective values $v(\omega)$ derived from a *value function* that may transform the objective outcomes, and decision weights $\pi$ derived from the objective probabilities' cumulative distribution function that may be transformed by a *probability weighting function*.
+Now, since the probability weighting function may redistribute the entire probability mass of $P(\Omega) = 1$ across outcomes [@zilkerNonlinearProbabilityWeighting2021], the decision weights 
 $$
@@
   \begin{cases}
-     w(P(X \geq \omega_i)) - w(P(X > \omega_i)) \quad \text{for} \ 1, \\
+     w(P(X \geq \omega_i)) - w(P(X > \omega_i)) \quad \text{for} \ \omega \geq 1, \\
      w(P(X \leq \omega_i)) - w(P(X < \omega_i)) \quad \text{else}, 
   \end{cases}
-\tag{5}
+\tag{8}
 $$
-may 
-people's deviations from EV maximization is often described in terms of the probability weighting pattern.
+may be larger or smaller than the objective probabilities.
 
@@
 ```{r}
-wf <- tibble(gamma = seq(.1, 1.9, .05)) %>%
-  expand_grid(prob = seq(0, 1, .01)) %>%
-  mutate(w = (prob^gamma)/((prob^gamma)+(1-prob)^gamma))
+wf <- tibble(gamma = seq(.1, 2, .1)) %>%
+  expand_grid(delta = c(.1, .5, 1, 2, 5, 10),
+              prob = seq(0, 1, .01)) %>%
+  mutate(w = (delta*prob^gamma)/((delta*prob^gamma)+(1-prob)^gamma))
 
@@
   geom_line(aes(prob, w, group = gamma, color = gamma)) +
+  geom_segment(x = 0, xend = 1, y =  0, yend = 1, linetype = "dashed") +
   scale_color_scico(palette = "cork") + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
-  scale_y_continuous(breaks = seq(0, 1, .1)) + 
+  scale_x_continuous(breaks = seq(0, 1, .2)) +
+  scale_y_continuous(breaks = seq(0, 1, .2)) + 
   labs(x = expression(paste("p(", omega, ")")),
@@
        color = expression(gamma)) + 
+  facet_wrap(~delta, scales = "fixed") + 
   theme_apa() 

### 2022-02-08 manuscript.Rmd
Update Introduction + Section 1

--- 2022-02-02 manuscript.Rmd
@@
 The human mind is a cognitive system that operates on inputs from an environment or memory. 
-In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose. 
-Given that each choice alternative is an element $i$ of the set $I$, the basic structure of decision making may be modeled by the inclusion map
+In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose and may therefore be organized in a set $C$ with each element $c \in C$ denoting a choice alternative.
+That is, each element $c \in C$ is assigned some information from the inputs and this information may be used by the mind to learn about the respective choice alternative.
+In turn, decision making can be considered an information processing problem which starts from the set $C$, containing all choice alternatives, and stops at a proper subset $C' \subset C$ with the inclusion map
 $$
 \begin{aligned}
-  \iota : I' &\to I \\
-  i &\mapsto i \quad \text{for all} \ i \in I' 
+  \iota : C' &\to C \\
+  c &\mapsto c  \quad \text{for all} \ c \in C'
 \end{aligned}
@@
 $$
-[@jostMathematicalConcepts2015, pp.
-14-15], indicating that decision making is an information processing problem which starts from an input set $I$, including all choice alternatives, and stops at a proper subset $I' \subset I$, including only the chosen alternatives.
+[@jostMathematicalConcepts2015, p. 15], containing only the chosen alternatives.
 Indeed, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives to return a subset thereof as outputs [@heOntologyDecisionModels2020].
 
-However, information about the choice alternatives may come in many forms.
-Rarely in their daily life, people make *decisions from description*, since in such a case all information about the choice alternatives is available through symbolic descriptions of their *properties*.
-Yet, rather often, people make *decisions from experience* [@hertwigDecisionsExperienceEffect2004], since
+<!-- Add short and general outlook on the paper -->
 
-# Header
+# The Description of Choices in Cumulative Prospect Theory
 
-Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from particular decisions, e.g., the choice between job offers, political parties to vote for, travel destinations, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* (or: gambles), it studies a case which is counterfactual in that it omits the many particularities of each decision and the differences between them, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983; see also @knightRiskUncertaintyProfit1921, for a discussion of the reasonableness of such abstractions].
+Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
+Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental *properties* that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion of the reasonableness of such abstractions.]
 These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by the Greek letter $\omega$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p(\omega)$.
+That is, all choice alternatives that can be fully described by their outcomes and probabilities are prospects, which are exclusively considered below. 
+<!--For illustration, take the choice alternatives in the following example with monetary outcomes:
 
-Now, let a prospect be a *probability space* denoted by the tuple $(\Omega, \mathcal{F}, P)$. 
+\noindent
+**Example 1.** 
+```{r echo=TRUE}
+# Alternative 1
+a1_outcomes <- 1 
+a1_prob <- 1
+
+# Alternative 2
+a2_outcomes <- c(10, 0)
+a2_prob <- c(.1, .9)
+```
+-->
+
+Now, let the exact axiomatic definition of a prospect be that of a *probability space* denoted by the tuple $(\Omega, \mathcal{F}, P)$. 
 Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ denotes the sample space, containing a finite set of possible outcomes:
@@
 $$ 
-$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$.^[Note that this paper considers only the case of finite sample spaces.
+$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$ with each element $A \in P(\Omega)$ being a subset of $\Omega$.^[Note that this paper considers only the case of finite sample spaces.
 The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
@@
 $$
-which assigns each subset $A \in \mathcal{F}$, also referred to as *events*, a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$ [@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.2].]
+which assigns each subset $A \in \mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$.]
+Given a choice between $c \in \{1, ..., k\}$ prospects, the inputs from the environment or memory should therefore provide information about the set
+$$
+C = \{(\Omega_1, \mathcal{F}_1, P_1), ... ,(\Omega_k, \mathcal{F}_k, P_k)\}
+\; .
+\tag{4}
+$$
 
-The choices people actually make between such prospects are often described in terms of deviations from expected value (EV) maximization, where the EV is given by 
+However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes and their probabilities<!--(as in Example 1)-->.
+In such cases, people would make *decisions from description* (DfD), since the information from which the mind learns about the prospects---the probability spaces in (3)---are complete descriptions thereof.
+Yet, rather often, people make *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], where the mind can learn about the prospects only from a record of past experiences with them<!--, which necessarily provides only incomplete and probable information-->.
+That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is denoted a *sample*.
+<!--The mind may then infer from the relative frequency with which an outcome occurs in such a sample of past decisions its probability of occurrence for a future decision. 
+Of course, ceteris paribus, the accuracy of this inference depends on the size of the sample.
+For illustration, take the sampled outcomes in the following example, where alternative A2 from Example 1 was chosen ten times without prior knowledge about the possible outcomes and their actual probabilities:
+
+\noindent
+**Example 2.**
+```{r echo=TRUE}
+set.seed(1)
+sample(a2_outcomes, size = 10, prob = a2_prob, replace = TRUE)
+```
+
+\noindent
+One may now make an inference from the sample about the possible outcomes of alternative A2 and their probabilities. 
+However, this inference is only probable, since the relative frequencies of outcomes will almost surely change with increasing sample size.-->
+
+More formally, let the sample of a prospect be a set of realizations of independent and identically distributed (i.i.d.) random variables, where each random variable
+$$
+\begin{aligned}
+  X : (\Omega, \mathcal{F}) &\to (\Omega', \mathcal{F'})  \\
+  \omega &\mapsto X(\omega), \ \text{with} \ X(\omega) = \omega \ \text{for all} \ \omega \in \Omega,
+\end{aligned}
+\tag{5}
+$$
+is a measurable function from the prospect's respective sample space $\Omega$ to a measurable space $\Omega'$ that takes the same values [see @kolmogorovFoundationsTheoryProbability1950, p.
+21; see also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.3, for a more accessible and comprehensive treatment].^[Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+660].
+To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
+Accordingly, for the choice between $c \in \{1, ..., k\}$ prospects, the inputs to DfE are generated by the following set of stochastic sampling processes:
+$$
+S = \{X_{1t}, ... , X_{kt}\}
+\; ,
+\tag{6}
+$$
+with $t \in \{1, ..., N\}$ denoting a sequence of realizations of $X$ and $N$ denoting the size of the respective sequence.
+
+The choices people actually make between prospects---be that in DfD or DfE---are often described in terms of deviations from expected value (EV) maximization, where the EV is given by 
 $$
 EV = \sum_i^n \omega_i \times P(X = \omega_i)
-\; ,
-\tag{4}
+\; .
+\tag{7}
 $$ 
-with $X$ being a random variable defined on the respective probability space.^[$X$ is measurable function $X: \Omega \to \Omega'$ [see @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.3] with $\omega \mapsto \omega$ for all $\omega \in \Omega$.]
-That is, following the principle of EV maximization, one would first calculate the prospects' EV according to (3) and thereafter chose the prospect with the largest EV.
-To *describe* how peoples' choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data with a combination of two parameterized functions that may replace the objective outcomes and probabilities in (3) by nonlinear transformations thereof.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
+That is, following the principle of EV maximization, one would first calculate the prospects' EV according to (7) and thereafter chose the prospect with the largest EV.
+To *describe* how peoples' choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data with a combination of two parameterized functions that may replace the objective outcomes and probabilities in (7) by nonlinear transformations thereof.
 That is, the models of CPT fit choice data by maximizing the value 
@@
 \; ,
-\tag{5}
+\tag{8}
 $$ 
-with subjective values $v(\omega)$ derived from a *value function* that may transform the objective outcomes, and decision weights $\pi$ derived from the objective probabilities' cumulative distribution function that may be transformed by a *probability weighting function* (see below).
-Now, since the probability weighting function may redistribute the entire probability mass of $\sum_i^n p(\omega_i) = 1$ across outcomes, the decision weights 
+with subjective values $v(\omega)$ derived from a *value function* $v$ that may transform the objective outcomes, and decision weights $\pi$ derived from the objective probabilities' cumulative distribution function that may be transformed by a *probability weighting function* $w$.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
+
+## Probability Weighting and The Description-Experience Gap
+
+Since the nonlinear probability weighting function may redistribute the entire probability mass of $P(\Omega) = 1$ [@zilkerNonlinearProbabilityWeighting2021], the estimated decision weights 
 $$
-\pi =
+\pi_i =
   \begin{cases}
-     w(P(X \geq \omega_i)) - w(P(X > \omega_i)) \quad \text{for} \ 1, \\
+     w(P(X \geq \omega_i)) - w(P(X > \omega_i)) \quad \text{for} \ \omega \geq 0, \\
      w(P(X \leq \omega_i)) - w(P(X < \omega_i)) \quad \text{else}, 
   \end{cases}
-\tag{5}
+\tag{9}
 $$
-may 
-people's deviations from EV maximization is often described in terms of the probability weighting pattern.
+may deviate---i.e., they may be smaller or greater---from the respective objective probabilities<!-- and these deviations are usually regressive-->.
+Although the possible deviation patterns, which span the entire probability scale, depend on the exact parameterization of the probability weighting function [e.g., @goldsteinExpressionTheoryPreference1987; @prelecProbabilityWeightingFunction1998; see also @stottCumulativeProspectTheory2006], they allow the adoption of an as-if weighting terminology for the description of choice behavior, which was originally introduced outside of the CPT models [see @pachurWeightUncertainEvents2019].
+Figure 1 illustrates such a description in CPT with different parameter settings for the two-parameter probability weighting function of @goldsteinExpressionTheoryPreference1987 with
+$$
+\begin{aligned}
+  w : P &\to [0,1] \\
+  p(\omega) &\mapsto \frac{\delta \times p(\omega)^{\gamma}}
+  {\delta \times p(\omega)^{\gamma} + (1-p(\omega))^{\gamma}}
+  \; ,
+\end{aligned}
+\tag{10}
+$$
+where $\gamma \in [0,2]$ and $\delta \geq 0$ determine the function's curvature and elevation, respectively.
+Essentially, if the estimate of a decision weight is larger (smaller) than the objective probability from which it is derived, the weighting function runs above (below) the dashed identity line.
+The choice data are then described *as if* people maximized the value in (8) and applied the over- and underweighting pattern indicated by the estimated shape of the overall probability weighting function.
+Importantly, the as-if prefix indicates that it cannot be concluded from the inferred decision weights that the mind does perform a probability weighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [see, e.g., @griffithsRationalUseCognitive2015].
 
-Now, in rather general terms, if people were following the principle of EV maximization, the estimates for the parameters of both functions (see below) would be such that the resulting subjective values and decision weights are equal to the objective outcomes and probabilities, i.e., $v(\omega) = \omega$ and $\pi = p(\omega)$.
-However, for deviations from EV maximization, at least one of the equations should not hold.
+(ref:weighting) Probability Weighting Function of @goldsteinExpressionTheoryPreference1987 for Different Values of the Curvature Parameter $\gamma$ and the Elevation Parameter $\delta$.
+
+```{r fig.cap="(ref:weighting)"}
+wf <- tibble(gamma = seq(.1, 2, .1)) %>%
+  expand_grid(delta = c(.1, .5, 1, 2, 5, 10),
+              prob = seq(0, 1, .01)) %>%
+  mutate(w = (delta*(prob^gamma))/((delta*prob^gamma)+(1-prob)^gamma))
+
+ggplot(wf) +
+  geom_line(aes(prob, w, group = gamma, color = gamma)) +
+  geom_segment(x = 0, xend = 1, y =  0, yend = 1, linetype = "dashed") +
+  scale_color_scico(palette = "acton") + 
+  scale_x_continuous(breaks = seq(0, 1, .2)) +
+  scale_y_continuous(breaks = seq(0, 1, .2)) + 
+  labs(x = expression(paste("p(", omega, ")")),
+       y = expression(paste("w(p(", omega, "))")), 
+       color = expression(gamma)) + 
+  facet_wrap(~delta, scales = "fixed") + 
+  theme_apa() 
+```
+
+Research on choices in DfD and DfE 
+Specifically, when people make DfD, decision weights are typically estimated to be larger than the objective probabilities in the lower probability range.
+However, for DfE, this pattern reverses and decisions weights are typically estimated to be smaller than the objective probabilities in the lower probability range [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; also see @wulffMetaanalyticReviewTwo2018].
 
@@
 $$
-where $a \in [0,1]$ and $\lambda > 1$ [but see @stottCumulativeProspectTheory2006, for alternative functional forms], transforms the objective outcomes $\omega$ into subjective values $v(\omega)$.
-The *probability weighting function*, for which several functional forms have been proposed [e.g., @goldsteinExpressionTheoryPreference1987, see also Equation 5]  
-$$
-w
-\tag{5}
-$$ 
-transforms the cumulative distribution function of the objective probabilities to derive the subjective decision weights.
 
-The shape of the probability weighting function lead to the common interpretation that people choose as if they were over- or underweighting outcomes of certain probability (see Figure 1).
-
-```{r}
-wf <- tibble(gamma = seq(.1, 1.9, .05)) %>%
-  expand_grid(prob = seq(0, 1, .01)) %>%
-  mutate(w = (prob^gamma)/((prob^gamma)+(1-prob)^gamma))
-
-ggplot(wf) +
-  geom_line(aes(prob, w, group = gamma, color = gamma)) +
-  scale_color_scico(palette = "cork") + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
-  scale_y_continuous(breaks = seq(0, 1, .1)) + 
-  labs(x = expression(paste("p(", omega, ")")),
-       y = expression(pi), 
-       color = expression(gamma)) + 
-  theme_apa() 
-```
+<!-- old -->
 
@@
   geom_density_2d_filled(contour_var = "ndensity") + 
-  scale_fill_scico_d(palette = "grayC") +
-  scale_color_scico_d(palette = "grayC") + 
+  scale_fill_scico_d(palette = "acton") +
+  scale_color_scico_d(palette = "acton") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) + 

### 2022-02-09 manuscript.Rmd
Review of the axiomatic definition of prospects

@@
 The human mind is a cognitive system that operates on inputs from an environment or memory.
-In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose and may therefore be organized in a set $C$ with each element $c \in C$ denoting a choice alternative.
-That is, each element $c \in C$ is assigned some information from the inputs and this information may be used by the mind to learn about the respective choice alternative.
+In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose, the latter being hereafter treated as elements $c$ of the set $C$.
+That is, each choice alternative $c \in C$ is assigned some information from the inputs and this information may be used by the mind to learn about the *properties* of the respective alternative.
 In turn, decision making can be considered an information processing problem which starts from the set $C$, containing all choice alternatives, and stops at a proper subset $C' \subset C$ with the inclusion map
@@
 Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental *properties* that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion of the reasonableness of such abstractions.]
-These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by the Greek letter $\omega$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p(\omega)$.
-That is, all choice alternatives that can be fully described by their outcomes and probabilities are prospects, which are exclusively considered below. 
+Rather, with the choice between at least two *prospects* [@kahnemanProspectTheoryAnalysis1979, see below], it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion of the reasonableness of such abstractions.]
+These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by $x$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p_X(x)$.
+Roughly speaking, then, all choice alternatives that can be fully described by their outcomes and probabilities are prospects (or: gambles), which are exclusively considered below. 
 <!--For illustration, take the choice alternatives in the following example with monetary outcomes:
@@
 
-Now, let the exact axiomatic definition of a prospect be that of a *probability space* denoted by the tuple $(\Omega, \mathcal{F}, P)$. 
-Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ denotes the sample space, containing a finite set of possible outcomes:
+Now, let the exact axiomatic definition of a prospect be that of a discrete random variable's distribution.
+Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space. 
+Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ is the sample space containing a finite set of elements
 $$
@@
 $$
-P: \mathcal{F} \mapsto [0,1]
+P: \mathcal{F} \to [0,1]
 \; ,
@@
 $$
-which assigns each subset $A \in \mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$.]
-Given a choice between $c \in \{1, ..., k\}$ prospects, the inputs from the environment or memory should therefore provide information about the set
+which assigns each subset $A \in \mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.<!--^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \to [0,1]$, which is used to construct the probability measures $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$.]-->
+The random variable $X$ is then a measurable function
 $$
-C = \{(\Omega_1, \mathcal{F}_1, P_1), ... ,(\Omega_k, \mathcal{F}_k, P_k)\}
-\; .
+\begin{aligned}
+  X : (\Omega, \mathcal{F}) &\to (\Omega', \mathcal{F'})  \\
+  \omega &\mapsto x
+  \; ,
+\end{aligned}
 \tag{4}
 $$
+where $(\Omega', \mathcal{F'})$ is a measurable space with each element $x \in \Omega'$ being a possible outcome of a prospect and each element $A' \in \mathcal{F'}$ being a subset of $\Omega'$.
+An outcome's probability $p(x)$ is then provided by the probability measure
+$$
+P_X : \mathcal{F'} \to [0,1]
+\tag{5}
+$$
+with 
+$$
+P_X(A' \in \mathcal{F'}) := P(X^{-1} \times A') = P(\{\omega: X(\omega) \in A'\})
+\tag{6}
+$$
+[see @kolmogorovFoundationsTheoryProbability1950, p. 21; see also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive introduction to random variables].
+To summarize and simplify, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
+$$
+C = \{P_{X_1}, ... , P_{X_k}\}
+\tag{6}
+$$
+with each element $c \in C$ being a distribution $P_X$ of a random variable defined on a different probability space.
+Accordingly, each $c$ can itself be considered a set of outcome-probability pairs $(x_i, p(x_i)) \in \{(x_1, p(x_1)), ..., (x_n, p(x_n))\}$.
 
-However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes and their probabilities<!--(as in Example 1)-->.
-In such cases, people would make *decisions from description* (DfD), since the information from which the mind learns about the prospects---the probability spaces in (3)---are complete descriptions thereof.
+However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes-probability pairs<!--(as in Example 1)-->.
+In such cases, people would make *decisions from description* (DfD), since the information from which the mind learns about the prospects are complete descriptions thereof.
 Yet, rather often, people make *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], where the mind can learn about the prospects only from a record of past experiences with them<!--, which necessarily provides only incomplete and probable information-->.
-That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is denoted a *sample*.
+That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is a rough description of a *sample*.
 <!--The mind may then infer from the relative frequency with which an outcome occurs in such a sample of past decisions its probability of occurrence for a future decision. 
@@
 
-More formally, let the sample of a prospect be a set of realizations of independent and identically distributed (i.i.d.) random variables, where each random variable
-$$
-\begin{aligned}
-  X : (\Omega, \mathcal{F}) &\to (\Omega', \mathcal{F'})  \\
-  \omega &\mapsto X(\omega), \ \text{with} \ X(\omega) = \omega \ \text{for all} \ \omega \in \Omega,
-\end{aligned}
-\tag{5}
-$$
-is a measurable function from the prospect's respective sample space $\Omega$ to a measurable space $\Omega'$ that takes the same values [see @kolmogorovFoundationsTheoryProbability1950, p.
-21; see also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.3, for a more accessible and comprehensive treatment].^[Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+More formally, let the sample of a prospect be a set of realizations of independent and identically distributed (i.i.d.) random variables.^[Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
 660].
-To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
-Accordingly, for the choice between $c \in \{1, ..., k\}$ prospects, the inputs to DfE are generated by the following set of stochastic sampling processes:
+To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, whi
+ch is out of the scope of this paper.]
+Accordingly, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by the following set of stochastic processes:
 $$
@@
 $$
-with $t \in \{1, ..., N\}$ denoting a sequence of realizations of $X$ and $N$ denoting the size of the respective sequence.
+with $t \in \{1, ..., N\}$ denoting a sequence of realizations of $X_c$ and $N$ denoting the size of the respective sequence.
 
@@
 $$
-EV = \sum_i^n \omega_i \times P(X = \omega_i)
+EV = \sum_i^n x_i \times P(X = x_i)
 \; .
@@
 $$
-V = \sum_i^n v(\omega_i) \times \pi_i
+V = \sum_i^n v(x_i) \times \pi_i
 \; ,
@@
 $$ 
-with subjective values $v(\omega)$ derived from a *value function* $v$ that may transform the objective outcomes, and decision weights $\pi$ derived from the objective probabilities' cumulative distribution function that may be transformed by a *probability weighting function* $w$.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
+with subjective values $v(x_i)$ derived from a *value function* $v$ that may transform the objective outcomes, and decision weights $\pi_i$ derived from the objective probabilities' cumulative distribution function that may be transformed by a *probability weighting function* $w$.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
 
@@
 \begin{aligned}
-  w : P &\to [0,1] \\
+  w : [0,1] &\to [0,1] \\
   p(\omega) &\mapsto \frac{\delta \times p(\omega)^{\gamma}}
@@
 However, for DfE, this pattern reverses and decisions weights are typically estimated to be smaller than the objective probabilities in the lower probability range [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; also see @wulffMetaanalyticReviewTwo2018].
-
-The value function 
-$$
-\begin{aligned}
-  v : \Omega &\to \mathbb{R} \\
-  \omega &\mapsto
-  \begin{cases}
-     \omega^a \qquad \qquad \text{for} \ \omega > 0, \\
-    -\lambda \times|\omega|^a \quad \text{else}, 
-  \end{cases}
-\end{aligned}
-\tag{4}
-$$
 

### 2022-02-11 manuscript.Rmd
Update CPT

@@
 The human mind is a cognitive system that operates on inputs from an environment or memory.
-In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose, the latter being hereafter treated as elements $c$ of the set $C$.
+In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose, hereafter treated as elements $c$ of the set $C$.
 That is, each choice alternative $c \in C$ is assigned some information from the inputs and this information may be used by the mind to learn about the *properties* of the respective alternative.
@@
   \iota : C' &\to C \\
-  c &\mapsto c  \quad \text{for all} \ c \in C'
+  c &\mapsto c  \quad \forall c \in C'
 \end{aligned}
@@
 Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* [@kahnemanProspectTheoryAnalysis1979, see below], it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion of the reasonableness of such abstractions.]
+Rather, with the choice between at least two *prospects* [see @kahnemanProspectTheoryAnalysis1979, see also below], it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion of the reasonableness of such abstractions.]
 These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by $x$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p_X(x)$.
@@
 where $(\Omega', \mathcal{F'})$ is a measurable space with each element $x \in \Omega'$ being a possible outcome of a prospect and each element $A' \in \mathcal{F'}$ being a subset of $\Omega'$.
-An outcome's probability $p(x)$ is then provided by the probability measure
+An outcome's probability $p_X(x)$ is then provided by the probability measure
 $$
@@
 $$
-P_X(A' \in \mathcal{F'}) := P(X^{-1} \times A') = P(\{\omega: X(\omega) \in A'\})
+P_X(A' \in \mathcal{F'}) := P(X^{-1} \times A') = P(\{\omega: X(\omega) = x \in A'\})
 \tag{6}
@@
 [see @kolmogorovFoundationsTheoryProbability1950, p. 21; see also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive introduction to random variables].
+That is, the set consisting of a single outcome $x$ can be treated as a subset $\{x\} \in \mathcal{F'}$ and one therefore obtains $p_X(x) = P(X(\omega) = x)$.
+Note that the probability measure in (5) and (6), respectively, is the discrete random variable's distribution and therefore a prospect.
 To summarize and simplify, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
@@
 C = \{P_{X_1}, ... , P_{X_k}\}
-\tag{6}
+\tag{7}
 $$
 with each element $c \in C$ being a distribution $P_X$ of a random variable defined on a different probability space.
-Accordingly, each $c$ can itself be considered a set of outcome-probability pairs $(x_i, p(x_i)) \in \{(x_1, p(x_1)), ..., (x_n, p(x_n))\}$.
+Accordingly, each $c$ can itself be considered a set of outcome-probability pairs $(x_i, p_X(x_i)) \in \{(x_1, p_X(x_1)), ..., (x_n, p_X(x_n))\}$.
 
@@
 One may now make an inference from the sample about the possible outcomes of alternative A2 and their probabilities. 
-However, this inference is only probable, since the relative frequencies of outcomes will almost surely change with increasing sample size.-->
+However, this inference is only probable, since the relative frequencies of outcomes will almost surely change with increasing sample size.
 
-More formally, let the sample of a prospect be a set of realizations of independent and identically distributed (i.i.d.) random variables.^[Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
-660].
-To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, whi
-ch is out of the scope of this paper.]
-Accordingly, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by the following set of stochastic processes:
+-->
+More formally, let the sample of a prospect be a set of realizations of the respective random variable $X$ according to its distribution $P_X$.
+Accordingly, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set $S$ of stochastic processes
 $$
 S = \{X_{1t}, ... , X_{kt}\}
-\; ,
-\tag{6}
+\tag{8}
 $$
-with $t \in \{1, ..., N\}$ denoting a sequence of realizations of $X_c$ and $N$ denoting the size of the respective sequence.
+with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the size of the respective sequence.^[Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+660].
+To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
+The sets of realizations that result from these stochastic processes may then be used to make an uncertain inference about the respective sets of outcome-probability pairs in (7).
 
-The choices people actually make between prospects---be that in DfD or DfE---are often described in terms of deviations from expected value (EV) maximization, where the EV is given by 
+The choices people actually make between prospects---be that in DfD or DfE---are often described in terms of deviations from expected value (EV) maximization, where the EV of a prospect is given by 
 $$
-EV = \sum_i^n x_i \times P(X = x_i)
+EV = \sum_i^n x_i \times p_X(x_i)
 \; .
-\tag{7}
+\tag{9}
 $$ 
-That is, following the principle of EV maximization, one would first calculate the prospects' EV according to (7) and thereafter chose the prospect with the largest EV.
-To *describe* how peoples' choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data with a combination of two parameterized functions that may replace the objective outcomes and probabilities in (7) by nonlinear transformations thereof.
-That is, the models of CPT fit choice data by maximizing the value 
+That is, following the principle of EV maximization, one would first calculate the prospects' EV according to (9) and thereafter chose the prospect with the largest EV.
+To *describe* how peoples' choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data with a combination of two parameterized, monotonic functions that may replace the objective outcomes and probabilities in (9) by nonlinear transformations thereof.
+More specifically, the models of CPT fit choice data by maximizing the value 
 $$
@@
 \; ,
-\tag{8}
+\tag{10}
 $$ 
-with subjective values $v(x_i)$ derived from a *value function* $v$ that may transform the objective outcomes, and decision weights $\pi_i$ derived from the objective probabilities' cumulative distribution function that may be transformed by a *probability weighting function* $w$.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
+with objective outcomes $x_i$ being transformed by a *value function* $v$, and cumulative decision weights $\pi_i$ being derived from cumulative probabilities of the distribution $P_X$ that may be transformed by a *weighting function* $w$ (see (11) and (12) below).^[Note that in CPT, the value and weighting functions are sign-dependent.
+Accordingly, two value and weighting functions are needed for prospects with positive and negative outcomes, respectively [see @tverskyAdvancesProspectTheory1992].
+Note further that CPT or other originally deterministic decision models may be amended by a stochastic choice function to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
 
@@
 
-Since the nonlinear probability weighting function may redistribute the entire probability mass of $P(\Omega) = 1$ [@zilkerNonlinearProbabilityWeighting2021], the estimated decision weights 
+According to @tverskyAdvancesProspectTheory1992, let the cumulative decision weights be defined by
 $$
@@
   \begin{cases}
-     w(P(X \geq \omega_i)) - w(P(X > \omega_i)) \quad \text{for} \ \omega \geq 0, \\
-     w(P(X \leq \omega_i)) - w(P(X < \omega_i)) \quad \text{else}, 
+     w^+(P(X \geq x_i)) - w^+(P(X > x_i)) \quad \forall x \geq 0, \\
+     w^-(P(X \leq x_i)) - w^-(P(X < x_i)) \quad \text{else}, 
   \end{cases}
-\tag{9}
+\tag{11}
 $$
-may deviate---i.e., they may be smaller or greater---from the respective objective probabilities<!-- and these deviations are usually regressive-->.
-Although the possible deviation patterns, which span the entire probability scale, depend on the exact parameterization of the probability weighting function [e.g., @goldsteinExpressionTheoryPreference1987; @prelecProbabilityWeightingFunction1998; see also @stottCumulativeProspectTheory2006], they allow the adoption of an as-if weighting terminology for the description of choice behavior, which was originally introduced outside of the CPT models [see @pachurWeightUncertainEvents2019].
+with $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
+Now, given that $w(P_X(\Omega')) = w(1) = 1$, it follows from (11) that for any prospect that is strictly positive or strictly negative, the weighting function may redistribute the entire probability mass $P_X(\Omega') = 1$ across outcomes [see @zilkerNonlinearProbabilityWeighting2021].
+As a consequence, the decision weights may deviate---i.e., they may be smaller or greater---from the respective objective probabilities<!-- and these deviations are usually regressive-->.
+Although the possible deviation patterns, which span the entire probability scale, depend on the exact parameterization of the weighting function [e.g., @goldsteinExpressionTheoryPreference1987; @tverskyAdvancesProspectTheory1992; @prelecProbabilityWeightingFunction1998; see also @stottCumulativeProspectTheory2006], they allow the adoption of an as-if weighting terminology for the description of choice behavior, which was originally introduced outside of the CPT models [see @pachurWeightUncertainEvents2019].
 Figure 1 illustrates such a description in CPT with different parameter settings for the two-parameter probability weighting function of @goldsteinExpressionTheoryPreference1987 with
@@
   w : [0,1] &\to [0,1] \\
-  p(\omega) &\mapsto \frac{\delta \times p(\omega)^{\gamma}}
-  {\delta \times p(\omega)^{\gamma} + (1-p(\omega))^{\gamma}}
+  p_X(x) &\mapsto \frac{\delta \times p_X(x)^{\gamma}}
+  {\delta \times p_X(x)^{\gamma} + (1-p_X(x))^{\gamma}}
   \; ,
 \end{aligned}
-\tag{10}
+\tag{12}
 $$
@@
   geom_line(aes(prob, w, group = gamma, color = gamma)) +
-  geom_segment(x = 0, xend = 1, y =  0, yend = 1, linetype = "dashed") +
-  scale_color_scico(palette = "acton") + 
+  geom_segment(x = 0, xend = 1, y =  0, yend = 1, linetype = "dashed", size = .3) +
+  scale_color_scico(palette = "cork") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +

### 2022-02-14 manuscript.Rmd
Updates CPT

@@
 The human mind is a cognitive system that operates on inputs from an environment or memory.
-In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose, hereafter treated as elements $c$ of the set $C$.
-That is, each choice alternative $c \in C$ is assigned some information from the inputs and this information may be used by the mind to learn about the *properties* of the respective alternative.
+In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose.
+Let us treat these choice alternatives hereafter as elements $c$ of the set $C$.
+To each $c \in C$ is then assigned some information from the inputs and this information may be used by the mind to learn about the *properties* of the respective choice alternative.
 In turn, decision making can be considered an information processing problem which starts from the set $C$, containing all choice alternatives, and stops at a proper subset $C' \subset C$ with the inclusion map
@@
 
-# The Description of Choices in Cumulative Prospect Theory
+# Prospects, Decisions from Description, and Decisions from Experience
 
 Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* [see @kahnemanProspectTheoryAnalysis1979, see also below], it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion of the reasonableness of such abstractions.]
-These fundamental properties are considered to be the possible outcomes of a choice alternative---hereafter denoted by $x$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p_X(x)$.
-Roughly speaking, then, all choice alternatives that can be fully described by their outcomes and probabilities are prospects (or: gambles), which are exclusively considered below. 
+Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion of the reasonableness of such abstractions.]
+These fundamental properties are considered the possible outcomes of a choice alternative---hereafter $x_i$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p_X(x_i)$.
+Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs $(x_i, p_X(x_i))$ are prospects (or: gambles), which are exclusively considered below. 
 <!--For illustration, take the choice alternatives in the following example with monetary outcomes:
@@
 
-Now, let the exact axiomatic definition of a prospect be that of a discrete random variable's distribution.
+Now, more formally, let the axiomatic definition of a prospect be that of a discrete random variable's distribution.
 Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space. 
@@
 $$ 
-$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$ with each element $A \in P(\Omega)$ being a subset of $\Omega$.^[Note that this paper considers only the case of finite sample spaces.
+$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$ with each element $A \in P(\Omega) = \mathcal{F}$ being a subset of $\Omega$.^[Note that this paper considers only the case of finite sample spaces.
 The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
@@
 which assigns each subset $A \in \mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.<!--^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \to [0,1]$, which is used to construct the probability measures $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$.]-->
-The random variable $X$ is then a measurable function
+The random variable $X$ is the measurable function
 $$
@@
 $$
-P_X(A' \in \mathcal{F'}) := P(X^{-1} \times A') = P(\{\omega: X(\omega) = x \in A'\})
+P_X(A' \in \mathcal{F'}) := P(X^{-1} \ A') = P(\{\omega: X(\omega) = x \in A'\})
 \tag{6}
@@
 [see @kolmogorovFoundationsTheoryProbability1950, p. 21; see also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive introduction to random variables].
-That is, the set consisting of a single outcome $x$ can be treated as a subset $\{x\} \in \mathcal{F'}$ and one therefore obtains $p_X(x) = P(X(\omega) = x)$.
-Note that the probability measure in (5) and (6), respectively, is the discrete random variable's distribution and therefore a prospect.
+That is, the set consisting of a single outcome $x$ can be treated as a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(X(\omega) = x)$.
+Note that the probability measure in (5) and (6), respectively, is a discrete random variable's distribution and therefore a prospect.
 To summarize and simplify, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
@@
 
-However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes-probability pairs<!--(as in Example 1)-->.
+However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes-probability pairs.
 In such cases, people would make *decisions from description* (DfD), since the information from which the mind learns about the prospects are complete descriptions thereof.
-Yet, rather often, people make *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], where the mind can learn about the prospects only from a record of past experiences with them<!--, which necessarily provides only incomplete and probable information-->.
+Yet, rather often, people make *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], where the mind can learn about the prospects only from a record of past experiences with them.
 That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is a rough description of a *sample*.
-<!--The mind may then infer from the relative frequency with which an outcome occurs in such a sample of past decisions its probability of occurrence for a future decision. 
-Of course, ceteris paribus, the accuracy of this inference depends on the size of the sample.
-For illustration, take the sampled outcomes in the following example, where alternative A2 from Example 1 was chosen ten times without prior knowledge about the possible outcomes and their actual probabilities:
+The mind may then infer from the relative frequency with which an outcome occurred in such a sample of past decisions its probability of occurrence following a future decision.
 
-\noindent
-**Example 2.**
-```{r echo=TRUE}
-set.seed(1)
-sample(a2_outcomes, size = 10, prob = a2_prob, replace = TRUE)
-```
-
-\noindent
-One may now make an inference from the sample about the possible outcomes of alternative A2 and their probabilities. 
-However, this inference is only probable, since the relative frequencies of outcomes will almost surely change with increasing sample size.
-
--->
-More formally, let the sample of a prospect be a set of realizations of the respective random variable $X$ according to its distribution $P_X$.
-Accordingly, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set $S$ of stochastic processes
+Now, more formally, let the sample of a prospect be a set of realizations of the respective random variable $X$ according to its distribution $P_X$.^[Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+660].
+To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
+So, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set $S$ of stochastic processes
 $$
@@
 $$
-with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the size of the respective sequence.^[Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
-660].
-To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
+with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the size of the respective sequence.
 The sets of realizations that result from these stochastic processes may then be used to make an uncertain inference about the respective sets of outcome-probability pairs in (7).
+
+Of course, the accuracy of such inferences depends, ceteris paribus, on the size of the samples, since from the laws of large numbers it follows that the relative frequency with which an outcome occurs in a sample converges to the outcome's objective probability only as the size of a sample increases [see @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 5].
+However, if the choices that people actually make between prospects are described, robust differences can be found between the choices in DfD and DfE, and the size of samples in DfE provides just one and only a partial explanation for this *description-experience gap* [see @hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018].
+The following section briefly addresses how choices between prospects in general and the description-experience gap in particular can be described using cumulative prospect theory's [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] *weighting function*.^[This paper also considers CPT's value function, but emphasis is put on the weighting function.]
+<!-- The two sections thereafter ... -->
+
+# The Description of Choices in CPT and the Description-Experience Gap
 
@@
 $$ 
-That is, following the principle of EV maximization, one would first calculate the prospects' EV according to (9) and thereafter chose the prospect with the largest EV.
-To *describe* how peoples' choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data with a combination of two parameterized, monotonic functions that may replace the objective outcomes and probabilities in (9) by nonlinear transformations thereof.
-More specifically, the models of CPT fit choice data by maximizing the value 
+That is, following the principle of EV maximization, one would calculate the prospects' EV---each by first multiplying its outcomes $x_i$ by their respective probabilities $p_X(x_i)$ and then summing the resulting products---to subsequently choose the prospect with the largest EV.
+To *describe* how people's actual choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing the value
 $$
@@
 $$ 
-with objective outcomes $x_i$ being transformed by a *value function* $v$, and cumulative decision weights $\pi_i$ being derived from cumulative probabilities of the distribution $P_X$ that may be transformed by a *weighting function* $w$ (see (11) and (12) below).^[Note that in CPT, the value and weighting functions are sign-dependent.
-Accordingly, two value and weighting functions are needed for prospects with positive and negative outcomes, respectively [see @tverskyAdvancesProspectTheory1992].
-Note further that CPT or other originally deterministic decision models may be amended by a stochastic choice function to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
+with objective outcomes $x_i$ being transformed by a *value function* $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P_X$.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
+Importantly, the transformation of cumulative probabilities is carried out by a weighting function $w$ (see (11) and (12) below).
+More specifically, CPT proposes cumulative decision weights as replacements for objective probabilities to account for empirical regularities in the deviations from EV maximization in DfD^[@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects such as the *certainty effect* and the *reflection effect* that were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
+Together, these empirical choice patterns indicate a violation of the EV principle and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].] that cannot be captured by the transformation of objective outcomes into subjective values $v(x)$ alone (see Footnote 6).
+In essence, to provide a proper description of people's choices between prospects in terms of their deviation from EV maximization, the proposed model is such that the inferred cumulative decision weights may be larger or smaller than the respective objective probabilities in (9); and they may therefore give more or less weight to subjective values for the overall valuation of a prospect in CPT than would be objectively warranted.
+In other words, for an inferred cumulative decision weight that is greater (smaller) than the objective probability it replaces, the respective outcome is overweighted (underweighted) in CPT.
+Accordingly one may---but must not---adopt an as-if weighting terminology for the description of choices by stating that people decide *as if* they maximized the value in (10) and applied the inferred over- and underweighting pattern.
+Importantly, the as-if prefix indicates that it cannot be concluded from the inferred cumulative decision weights that the mind does indeed perform the weighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [see, e.g., @griffithsRationalUseCognitive2015].
 
-## Probability Weighting and The Description-Experience Gap
-
-According to @tverskyAdvancesProspectTheory1992, let the cumulative decision weights be defined by
+Now, more formally, cumulative decision weights in CPT take the form
 $$
@@
   \begin{cases}
-     w^+(P(X \geq x_i)) - w^+(P(X > x_i)) \quad \forall x \geq 0, \\
+     w^+(P(X \geq x_i)) - w^+(P(X > x_i)) \quad \forall x_i \geq 0, \\
      w^-(P(X \leq x_i)) - w^-(P(X < x_i)) \quad \text{else}, 
@@
 $$
-with $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
-Now, given that $w(P_X(\Omega')) = w(1) = 1$, it follows from (11) that for any prospect that is strictly positive or strictly negative, the weighting function may redistribute the entire probability mass $P_X(\Omega') = 1$ across outcomes [see @zilkerNonlinearProbabilityWeighting2021].
-As a consequence, the decision weights may deviate---i.e., they may be smaller or greater---from the respective objective probabilities<!-- and these deviations are usually regressive-->.
-Although the possible deviation patterns, which span the entire probability scale, depend on the exact parameterization of the weighting function [e.g., @goldsteinExpressionTheoryPreference1987; @tverskyAdvancesProspectTheory1992; @prelecProbabilityWeightingFunction1998; see also @stottCumulativeProspectTheory2006], they allow the adoption of an as-if weighting terminology for the description of choice behavior, which was originally introduced outside of the CPT models [see @pachurWeightUncertainEvents2019].
-Figure 1 illustrates such a description in CPT with different parameter settings for the two-parameter probability weighting function of @goldsteinExpressionTheoryPreference1987 with
+where $w$ is a monotonic, nonlinear function satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$ [@tverskyAdvancesProspectTheory1992].
+From the transformation of cumulative probabilities in (11), it follows that the replacement of objective probabilities by cumulative decision weights depends on the rank of the outcome to which the decision weight is assigned and the shape of the weighting function, which itself depends on the exact parameterization of the function [e.g., @goldsteinExpressionTheoryPreference1987; @tverskyAdvancesProspectTheory1992; @prelecProbabilityWeightingFunction1998; see also @stottCumulativeProspectTheory2006].
+That is, the shape of the weighting function determines over which interval on the probability scale [0, 1] cumulative probabilities are overweighted or underweighted.
+In turn, the same difference in the objective cumulative probability ...
+
+Now, although the possible deviation patterns, which span the entire probability scale, depend on the exact parameterization of the cumulative weighting function, they allow the adoption of an as-if weighting terminology for the description of choice behavior, which was originally introduced outside of the CPT models [see @pachurWeightUncertainEvents2019].
+
+Figure 1 illustrates such a description in CPT with different parameter settings for the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987 with
 $$
@@
 where $\gamma \in [0,2]$ and $\delta \geq 0$ determine the function's curvature and elevation, respectively.
-Essentially, if the estimate of a decision weight is larger (smaller) than the objective probability from which it is derived, the weighting function runs above (below) the dashed identity line.
+In essence, if the estimate of a cumulative decision weight is larger (smaller) than the objective probability from which it is derived, the weighting function runs above (below) the dashed identity line.
 The choice data are then described *as if* people maximized the value in (8) and applied the over- and underweighting pattern indicated by the estimated shape of the overall probability weighting function.
-Importantly, the as-if prefix indicates that it cannot be concluded from the inferred decision weights that the mind does perform a probability weighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [see, e.g., @griffithsRationalUseCognitive2015].
 
@@
   geom_line(aes(prob, w, group = gamma, color = gamma)) +
-  geom_segment(x = 0, xend = 1, y =  0, yend = 1, linetype = "dashed", size = .3) +
-  scale_color_scico(palette = "cork") + 
+  geom_segment(x = 0, xend = 1, y =  0, yend = 1, linetype = "dashed", size = .2, color = "gray") +
+  scale_color_scico(palette = "lisbon") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +
   scale_y_continuous(breaks = seq(0, 1, .2)) + 
-  labs(x = expression(paste("p(", omega, ")")),
-       y = expression(paste("w(p(", omega, "))")), 
+  labs(x = "p",
+       y = "w(p)", 
        color = expression(gamma)) + 
-  facet_wrap(~delta, scales = "fixed") + 
-  theme_apa() 
+  facet_wrap(. ~ delta, labeller = label_bquote(cols = delta: .(delta))) + 
+  theme_minimal()
 ```
@@
 However, for DfE, this pattern reverses and decisions weights are typically estimated to be smaller than the objective probabilities in the lower probability range [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; also see @wulffMetaanalyticReviewTwo2018].
+
+# Explanations for Underweighting in DfE
+
+# Decision and Sampling Strategies
 
@@
 ## What Are the Choice Alternatives and Their Properties?
-
-The argument so far has been quite general and abstract, since there is no complete answer to the question raised above this paragraph---there is, of course, an uncountable number of decisions and so are there choice alternatives and properties.
-Therefore, in the present paper, *prospects* are used as a proxy for the variety of choice alternatives the mind is required to evaluate in natural world decisions. 
-Consequently, the argument continues to proceed at an abstract level: with choices between at least two prospects, the current paper considers a case which is counterfactual, since it is freed from many varieties and complexities that the mind is normally confronted with.
-The case is, however, quite paradigmatic in research on decision theory and there are good reasons for that [cf.
-@knightRiskUncertaintyProfit1921, especially Chapter 1 for a brief discussion closely related to the current subject].
-
-Now, let a prospect be a *probability space* denoted by the tuple $(\Omega, \mathcal{F}, P)$. 
-Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ is the sample space
-
-$$
-\Omega = \{\omega_1, ..., \omega_n\}
-\; ,
-\tag{2.1}
-$$
-
-containing a finite set of possible outcomes $\omega$. 
-$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$.^[Note that this paper considers only the case of finite sample spaces containing of a small number of outcomes.
-The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
-2-3 and 14-15], also covers infinite sample spaces and is that of a $\sigma$-algebra.
-For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such.
-See Georgii [-@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1] for a comprehensive but accessible mathematical treatment.]
-
-$P$ is a probability measure
-
-$$
-P: \mathcal{F} \mapsto [0,1]
-\; ,
-\tag{2.2}
-$$
-
-which assigns each subset $A \in \mathcal{F}$, also referred to as *events*, a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.^[The probability measure formally assigns probabilities to sets of outcomes $A \in F$ rather than the elementary outcomes $\omega \in \Omega$.
-The probabilities of $\omega$ are determined by the probability mass function $p : \Omega \mapsto [0,1]$, which is used to construct the probability measure according to the equation $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$ [cf.
-@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.2].]
-
-In less technical terms, following the choice of a prospect, one of the outcomes associated with this particular prospect is obtained, a gain or loss respectively.
-If there is just one outcome associated with a prospect, it is obtained with certainty.
-However, if there is a collection of outcomes, just one outcome out of this collection is obtained according to some probability, where the probabilities can vary between outcomes and are given by the measure of the form described in (2.2) (see also Footnote 2).
-
-Since it was stated that the inputs to the decision making process can be organized in a set of choice alternatives, we can adapt (1) for the case of a choice between $1, ..., k$ prospects to obtain:
-
-$$
-\iota : I' \mapsto I, \ \text{where} \ I = \{(\Omega_1,  \mathcal{F}_1, P_1), ..., (\Omega_k,  \mathcal{F}_k, P_k)\}
-\; .
-\tag{3}
-$$
 

### 2022-02-15 manuscript.Rmd
Update: Review of structure

@@
 The human mind is a cognitive system that operates on inputs from an environment or memory.
-In the domain of decision making, such inputs provide information about the choice alternatives among which people can choose.
-Let us treat these choice alternatives hereafter as elements $c$ of the set $C$.
-To each $c \in C$ is then assigned some information from the inputs and this information may be used by the mind to learn about the *properties* of the respective choice alternative.
-In turn, decision making can be considered an information processing problem which starts from the set $C$, containing all choice alternatives, and stops at a proper subset $C' \subset C$ with the inclusion map
+In the domain of decision making, such inputs provide information about the *properties* of the choice alternatives among which people can choose.
+Hereafter, let us treat these alternatives as elements $c$ of the set $C$.
+To each $c \in C$ is then assigned some information from the inputs and this information may be used by the mind to learn about the properties of the respective alternative.
+Accordingly, decision making can be considered an information processing problem which starts from the set $C$, containing all choice alternatives, and stops at a proper subset $C' \subset C$ with the inclusion map
 $$
@@
 
-<!-- Add short and general outlook on the paper -->
+Importantly, information about the choice alternatives can come in many formats.
+In *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all relevant properties of the choice alternatives.
+In *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], inputs take the form of *samples* (see below).
+In this latter case---perhaps, the one that more closely resembles decisions in people's daily life---the properties of the choice alternatives are not described and therefore not known with certainty, but they must be inferred from the consequences that occurred or were absent after the alternatives were chosen in similar decisions in the past.
+Although these different formats may in principle carry the same information about given choice alternatives, behavioral decision research has yet produced a large body of papers indicating that, taking a quite general perspective, there are robust differences between the choices that are made in DfD and DfE.
+That is, all other things being equal, empirical choice patterns across studies indicate that in DfD people choose *as if* a rare consequence of a choice alternative has more impact on the latter's evaluation than would be objectively warranted by the principle of mathematical expectation (see below); in turn, in DfE, people choose *as if* the same rare consequence has less impact on the evaluation than warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @hauDescriptionexperienceGapRisky2008; @rakowBiasedSamplesNot2008; @ungemachAreProbabilitiesOverweighted2009; @camilleriWhenWhyRare2011; @kellenHowVariantAre2016; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructBehaviorGap2017; see also @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+
+This paper uses the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009] as an entry point for a closer inquiry into the sampling process as an essential part of sample-based decision making.
+
+<!--
+The paper is structured as follows: 
+...
+
+All simulations and analyses are reproducible---materials and instructions can be found on the GitHub repository.
+-->
 
@@
 Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion of the reasonableness of such abstractions.]
+Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a discussion of the reasonableness of such abstractions.]
 These fundamental properties are considered the possible outcomes of a choice alternative---hereafter $x_i$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p_X(x_i)$.
@@
 
-Now, more formally, let the axiomatic definition of a prospect be that of a discrete random variable's distribution.
+Now, more formally,^[Paragraphs with this beginning usually formalize the main ideas of the preceding paragraphs or elaborate on them by using mathematical expressions and concepts.
+Although important, the gist of this paper should be captured despite skipping these paragraphs.]  let the axiomatic definition of a prospect be that of a discrete random variable's distribution.
 Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space. 
@@
 Yet, rather often, people make *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], where the mind can learn about the prospects only from a record of past experiences with them.
-That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is a rough description of a *sample*.
+That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is a rough description of a sample.
 The mind may then infer from the relative frequency with which an outcome occurred in such a sample of past decisions its probability of occurrence following a future decision.
@@
 In other words, for an inferred cumulative decision weight that is greater (smaller) than the objective probability it replaces, the respective outcome is overweighted (underweighted) in CPT.
-Accordingly one may---but must not---adopt an as-if weighting terminology for the description of choices by stating that people decide *as if* they maximized the value in (10) and applied the inferred over- and underweighting pattern.
-Importantly, the as-if prefix indicates that it cannot be concluded from the inferred cumulative decision weights that the mind does indeed perform the weighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [see, e.g., @griffithsRationalUseCognitive2015].
+Accordingly one may adopt an as-if weighting terminology for the description of choices by stating that people decide *as if* they maximized the value in (10) and applied the inferred over- and underweighting pattern [@pachurWeightUncertainEvents2019].
+Importantly, the as-if prefix indicates that it cannot be concluded from the inferred cumulative decision weights that the mind does indeed perform any of the computations associated with the weighting of outcomes in CPT; rather, it processes the inputs in a way that the outputs, i.e., the resulting choice patterns, approximate the solutions from the inferred CPT model [see, e.g., @griffithsRationalUseCognitive2015].
+Below, CPT will therefore only be used as a model to describe choices between prospects and it will be discussed---and demonstrated in a simulation---how distinct strategies of generating and integrating samples in DfE can contribute to weighting patterns that are commonly inferred when modeling respective empirical choice data.
 

### 2022-02-16 manuscript.Rmd
Review of papaer structure + update of introduction

@@
 
-The human mind is a cognitive system that operates on inputs from an environment or memory.
-In the domain of decision making, such inputs provide information about the *properties* of the choice alternatives among which people can choose.
-Hereafter, let us treat these alternatives as elements $c$ of the set $C$.
+The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the *properties* of the choice alternatives between which people can choose.
+In fact, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives to return a subset thereof as outputs [@heOntologyDecisionModels2020].
+
+Now, more formally,^[Paragraphs with this beginning usually formalize the main ideas of the preceding paragraphs or elaborate on them by using mathematical expressions and concepts.
+Although important, the gist of this paper should be captured despite skipping these paragraphs.] let us treat the choice alternatives as elements $c$ of the set $C$.
 To each $c \in C$ is then assigned some information from the inputs and this information may be used by the mind to learn about the properties of the respective alternative.
-Accordingly, decision making can be considered an information processing problem which starts from the set $C$, containing all choice alternatives, and stops at a proper subset $C' \subset C$ with the inclusion map
+Accordingly, decision making can be considered an information-processing problem which starts from the set $C$, containing all choice alternatives, and stops at a proper subset $C' \subset C$ with the inclusion map
 $$
@@
 [@jostMathematicalConcepts2015, p. 15], containing only the chosen alternatives.
-Indeed, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives to return a subset thereof as outputs [@heOntologyDecisionModels2020].
 
-Importantly, information about the choice alternatives can come in many formats.
+Importantly, the information that is provided about the choice alternatives can come in many forms.
 In *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all relevant properties of the choice alternatives.
-In *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], inputs take the form of *samples* (see below).
-In this latter case---perhaps, the one that more closely resembles decisions in people's daily life---the properties of the choice alternatives are not described and therefore not known with certainty, but they must be inferred from the consequences that occurred or were absent after the alternatives were chosen in similar decisions in the past.
-Although these different formats may in principle carry the same information about given choice alternatives, behavioral decision research has yet produced a large body of papers indicating that, taking a quite general perspective, there are robust differences between the choices that are made in DfD and DfE.
-That is, all other things being equal, empirical choice patterns across studies indicate that in DfD people choose *as if* a rare consequence of a choice alternative has more impact on the latter's evaluation than would be objectively warranted by the principle of mathematical expectation (see below); in turn, in DfE, people choose *as if* the same rare consequence has less impact on the evaluation than warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @hauDescriptionexperienceGapRisky2008; @rakowBiasedSamplesNot2008; @ungemachAreProbabilitiesOverweighted2009; @camilleriWhenWhyRare2011; @kellenHowVariantAre2016; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructBehaviorGap2017; see also @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], inputs take the form of *samples*.
+In this latter case, the properties of the choice alternatives are not described and therefore not known with certainty, but they must be inferred from the outcomes that occurred when the alternatives were chosen in similar past decisions.
+Although these distinct input forms may in principle carry the same information about a given set of choice alternatives, behavioral decision research has so far produced a large body of papers indicating that---if a quite general perspective is taken---there are robust differences between the choices that are made in DfD and DfE.
+That is, ceteris paribus, empirical choice patterns across studies indicate that in DfD people choose *as if* a rare outcome is given more weight in the evaluation of a choice alternative than would be objectively warranted by the principle of mathematical expectation (see below); in turn, in DfE, people choose *as if* the same rare outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @hauDescriptionexperienceGapRisky2008; @rakowBiasedSamplesNot2008; @ungemachAreProbabilitiesOverweighted2009; @camilleriWhenWhyRare2011; @kellenHowVariantAre2016; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructBehaviorGap2017].
+Hereafter, we refer to these patterns as the as-if overweighting and underweighting of rare outcomes, respectively.
 
-This paper uses the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009] as an entry point for a closer inquiry into the sampling process as an essential part of sample-based decision making.
+This paper uses the choice pattern in DfE as an entry point for an inquiry into the sampling process as a consequential part of the information processing upfront choices in DfE.
+More specifically, it will be discussed and demonstrated in a simulation how changes to the strategy of sequentially generating outcomes and integrating them into samples (hereafter: sampling strategies) can produce distinct choice patterns in DfE---among them, the as-if underweighting of rare outcomes [see @hillsInformationSearchDecisions2010, for the original formulation of this idea].
 
-<!--
-The paper is structured as follows: 
-...
-
-All simulations and analyses are reproducible---materials and instructions can be found on the GitHub repository.
--->
+The rest of the paper is structured as follows.
+In the first brief section, a formal definition of DfE is provided.
+In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices in DfE in terms of deviations from the principle of mathematical expectation.
+<!-- Outline of the section -->
+In the section that follows, sampling strategies are treated in quite some detail.
+<!-- Outline of the section -->
+Thereafter, a simulation is presented in which the theoretical claims that are made in the preceding section are implemented in a computational model to simulate choice data in DfE.
+The predictions of the model are summarized by fitting the choice data in CPT.
+The paper closes with a summary and a conclusion.
+Note that this paper, including the simulations and data analyses, is reproducible---materials and instructions can be found on the GitHub repository.
 
@@
 
-Now, more formally,^[Paragraphs with this beginning usually formalize the main ideas of the preceding paragraphs or elaborate on them by using mathematical expressions and concepts.
-Although important, the gist of this paper should be captured despite skipping these paragraphs.]  let the axiomatic definition of a prospect be that of a discrete random variable's distribution.
+Now, more formally, let the axiomatic definition of a prospect be that of a discrete random variable's distribution.
 Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space. 
@@
 Of course, the accuracy of such inferences depends, ceteris paribus, on the size of the samples, since from the laws of large numbers it follows that the relative frequency with which an outcome occurs in a sample converges to the outcome's objective probability only as the size of a sample increases [see @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 5].
-However, if the choices that people actually make between prospects are described, robust differences can be found between the choices in DfD and DfE, and the size of samples in DfE provides just one and only a partial explanation for this *description-experience gap* [see @hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018].
+However, if the choices that people actually make between prospects are described, robust differences can be found between the choices in DfD and DfE, and the size of samples in DfE provides just one and only a partial explanation for this *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009; see also @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-anayltic review].
 The following section briefly addresses how choices between prospects in general and the description-experience gap in particular can be described using cumulative prospect theory's [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] *weighting function*.^[This paper also considers CPT's value function, but emphasis is put on the weighting function.]
@@
 
-# The Description of Choices in CPT and the Description-Experience Gap
+# The Description of Choices in CPT and As-If Underweighting in DfE
 
@@
 
-# Explanations for Underweighting in DfE
+# Sampling Strategies
 
-# Decision and Sampling Strategies
-
-<!-- old -->
+<!-- Old
 
@@
 Consider first the counterfactual case of the prospect whose tuple is not part of the distal environment but is directly described. 
-Since all information about the prospect is given, one may in principle consider the input complete, yet, the tuple implies properties of the prospect which are not explicitly described.
+Since all information about the prospect is given, one may in principle consider the input complete, yet, 
+the tuple implies properties of the prospect which are not explicitly described.
 For example, to obtain the description of the prospect's weighted average, still a calculus according to the algebraic rules described in the preceding paragraph must be carried out. 
@@
 
-# Evaluation of Choice Alternatives and Outputs of the Decision Making Process
-
-...
-
-# Sampling Strategies as Representation Systems
-
-...
+-->
 
@@
 
-## Test set
+<!-- Test set-->
 
@@
 
-## Results
+<!-- Results -->
 
@@
 
-### Plausibility Check: Relationship between Switching Probability and Trial Length
+<!-- Plausibility Check: Relationship between Switching Probability and Trial Length -->
 
@@
 
-### Probability Weighting Function
+<!-- Weighting function -->
 
@@
 
-### Value Function
+<!-- Weighting function -->
 
@@
 
-# Discussion and Conclusion
+# Summary and Conclusion
+
+# Acknowledgement
 

### 2022-02-16 manuscript.Rmd
Minor Reviews

@@
 
-Now, more formally,^[Paragraphs with this beginning usually formalize the main ideas of the preceding paragraphs or elaborate on them by using mathematical expressions and concepts.
-Although important, the gist of this paper should be captured despite skipping these paragraphs.] let us treat the choice alternatives as elements $c$ of the set $C$.
+Now, more formally,^[Paragraphs with this beginning usually formalize the ideas of the preceding paragraphs or elaborate on them by using mathematical expressions and concepts.
+Although I consider these paragraphs important, the major propositions of this paper should be captured despite skipping them.] let us treat the choice alternatives as elements $c$ of the set $C$.
 To each $c \in C$ is then assigned some information from the inputs and this information may be used by the mind to learn about the properties of the respective alternative.
@@
 
-This paper uses the choice pattern in DfE as an entry point for an inquiry into the sampling process as a consequential part of the information processing upfront choices in DfE.
-More specifically, it will be discussed and demonstrated in a simulation how changes to the strategy of sequentially generating outcomes and integrating them into samples (hereafter: sampling strategies) can produce distinct choice patterns in DfE---among them, the as-if underweighting of rare outcomes [see @hillsInformationSearchDecisions2010, for the original formulation of this idea].
+This paper uses the as-if underweighting of rare outcomes as a starting point for an inquiry into the sampling process upfront choices in DfE.
+Essentially, it discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into samples (hereafter: sampling strategies) can produce distinct choice patterns in DfE---among them, the as-if underweighting of rare outcomes [see @hillsInformationSearchDecisions2010, for the original formulation of this claim].
+<!-- It thereby proposes that ... -->
 
-The rest of the paper is structured as follows.
+The rest of the paper is therefore structured as follows.
 In the first brief section, a formal definition of DfE is provided.
@@
 Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a discussion of the reasonableness of such abstractions.]
-These fundamental properties are considered the possible outcomes of a choice alternative---hereafter $x_i$---and the probabilities with which these outcomes occur following the choice of the alternative---hereafter $p_X(x_i)$.
+These fundamental properties are considered the possible outcomes of a choice alternative (hereafter: $x_i$) and the probabilities with which these outcomes occur following the choice of the alternative (hereafter: $p_X(x_i)$).
 Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs $(x_i, p_X(x_i))$ are prospects (or: gambles), which are exclusively considered below. 
@@
 $$
-[see @kolmogorovFoundationsTheoryProbability1950, p. 21; see also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive introduction to random variables].
+[see @kolmogorovFoundationsTheoryProbability1950, p.
+21-22].^[See also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive yet accessible introduction to random variables.]
 That is, the set consisting of a single outcome $x$ can be treated as a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(X(\omega) = x)$.
@@
 However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes-probability pairs.
-In such cases, people would make *decisions from description* (DfD), since the information from which the mind learns about the prospects are complete descriptions thereof.
-Yet, rather often, people make *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], where the mind can learn about the prospects only from a record of past experiences with them.
+In such cases, people would make decisions from description (DfD), since the information from which the mind learns about the prospects are complete descriptions thereof.
+Yet, rather often, people make decisions from experience (DfE), where the mind can learn about the prospects only from a record of past experiences with them.
 That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is a rough description of a sample.
@@
 $$
-with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the size of the respective sequence.
+with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the length of the respective sequence.
 The sets of realizations that result from these stochastic processes may then be used to make an uncertain inference about the respective sets of outcome-probability pairs in (7).
 
-Of course, the accuracy of such inferences depends, ceteris paribus, on the size of the samples, since from the laws of large numbers it follows that the relative frequency with which an outcome occurs in a sample converges to the outcome's objective probability only as the size of a sample increases [see @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 5].
-However, if the choices that people actually make between prospects are described, robust differences can be found between the choices in DfD and DfE, and the size of samples in DfE provides just one and only a partial explanation for this *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009; see also @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-anayltic review].
-The following section briefly addresses how choices between prospects in general and the description-experience gap in particular can be described using cumulative prospect theory's [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] *weighting function*.^[This paper also considers CPT's value function, but emphasis is put on the weighting function.]
-<!-- The two sections thereafter ... -->
+Of course, the accuracy of such inferences depends, ceteris paribus, on the size of the samples, since from the laws of large numbers [see, e.g., @kolmogorovFoundationsTheoryProbability1950] it follows that the relative frequency with which an outcome occurs in a sample converges to the outcome's objective probability only as the size of a sample increases.
+Yet, if the choices that people actually make between prospects in DfD and in DfE are described, the differences that were already outlined in the introduction are found, and the size of samples in DfE provides just one and only a partial explanation for this so-called *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009; see also @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+This paper will address this issue<!-- review-->.
+Before that, however, the following section reviews how choices between prospects can be described using cumulative prospect theory's (CPT) *weighting function*.^[This paper also considers CPT's value function, but emphasis is put on the weighting function.]
 
-# The Description of Choices in CPT and As-If Underweighting in DfE
+# The Description of Choices in CPT and the As-If Underweighting in DfE
 
@@
 That is, following the principle of EV maximization, one would calculate the prospects' EV---each by first multiplying its outcomes $x_i$ by their respective probabilities $p_X(x_i)$ and then summing the resulting products---to subsequently choose the prospect with the largest EV.
-To *describe* how people's actual choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing the value
+To *describe* how people's actual choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of CPT [@tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing the value
 $$
@@
 Importantly, the as-if prefix indicates that it cannot be concluded from the inferred cumulative decision weights that the mind does indeed perform any of the computations associated with the weighting of outcomes in CPT; rather, it processes the inputs in a way that the outputs, i.e., the resulting choice patterns, approximate the solutions from the inferred CPT model [see, e.g., @griffithsRationalUseCognitive2015].
-Below, CPT will therefore only be used as a model to describe choices between prospects and it will be discussed---and demonstrated in a simulation---how distinct strategies of generating and integrating samples in DfE can contribute to weighting patterns that are commonly inferred when modeling respective empirical choice data.
+Below, CPT will therefore only be used as a data model to describe choices between prospects and it will be discussed---and demonstrated in a simulation---how distinct strategies of generating and integrating samples in DfE can contribute to weighting patterns that are commonly inferred when modeling respective empirical choice data.
 
@@
 
-(ref:weighting) Probability Weighting Function of @goldsteinExpressionTheoryPreference1987 for Different Values of the Curvature Parameter $\gamma$ and the Elevation Parameter $\delta$.
+(ref:weighting) Possible Shapes of Goldstein and Einhorn's -@goldsteinExpressionTheoryPreference1987 Weighting Function
 
@@
   geom_segment(x = 0, xend = 1, y =  0, yend = 1, linetype = "dashed", size = .2, color = "gray") +
-  scale_color_scico(palette = "lisbon") + 
+  scale_color_scico(palette = "cork") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +
@@
   geom_path() + 
-  scale_color_scico(palette = "grayC") + 
+  scale_color_scico(palette = "tokyo") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +
@@
   ggplot(aes(x = ep, y = w, color = s)) +
-  geom_path() + 
-  scale_color_scico(palette = "buda") + 
+  geom_path(size = 1) + 
+  scale_color_scico(palette = "tokyo") + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +
   scale_y_continuous(breaks = seq(0, 1, .2)) + 
-  facet_wrap(~a) +
+  facet_grid(boundary~a) +
   labs(x ="Experienced Probability",
@@
        color="Switching Probability") + 
-  theme_minimal()
+  theme_dark()
 ```

### 2022-02-17 manuscript.Rmd
Update Section 2

@@
 
-Now, more formally,^[Paragraphs with this beginning usually formalize the ideas of the preceding paragraphs or elaborate on them by using mathematical expressions and concepts.
-Although I consider these paragraphs important, the major propositions of this paper should be captured despite skipping them.] let us treat the choice alternatives as elements $c$ of the set $C$.
+Now, more formally,^[<!--Open footnote-->Paragraphs with this beginning usually formalize the ideas of the preceding paragraphs or elaborate on them by using mathematical expressions and concepts.
+Although I consider these paragraphs important, the major propositions of this paper should be captured despite skipping them.<!--Close footnote-->]
+let us treat the choice alternatives as elements $c$ of the set $C$.
 To each $c \in C$ is then assigned some information from the inputs and this information may be used by the mind to learn about the properties of the respective alternative.
@@
 That is, ceteris paribus, empirical choice patterns across studies indicate that in DfD people choose *as if* a rare outcome is given more weight in the evaluation of a choice alternative than would be objectively warranted by the principle of mathematical expectation (see below); in turn, in DfE, people choose *as if* the same rare outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @hauDescriptionexperienceGapRisky2008; @rakowBiasedSamplesNot2008; @ungemachAreProbabilitiesOverweighted2009; @camilleriWhenWhyRare2011; @kellenHowVariantAre2016; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructBehaviorGap2017].
-Hereafter, we refer to these patterns as the as-if overweighting and underweighting of rare outcomes, respectively.
+Hereafter, we refer to these choice patterns as the as-if overweighting and underweighting of rare outcomes, respectively.
 
@@
 Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[See @knightRiskUncertaintyProfit1921, Chapter 1, for a discussion of the reasonableness of such abstractions.]
+Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[<!--Open footnote-->See @knightRiskUncertaintyProfit1921, Chapter 1, for a discussion of the reasonableness of such abstractions.<!--Close footnote-->]
 These fundamental properties are considered the possible outcomes of a choice alternative (hereafter: $x_i$) and the probabilities with which these outcomes occur following the choice of the alternative (hereafter: $p_X(x_i)$).
 Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs $(x_i, p_X(x_i))$ are prospects (or: gambles), which are exclusively considered below.
-<!--For illustration, take the choice alternatives in the following example with monetary outcomes:
-
-\noindent
-**Example 1.** 
-```{r echo=TRUE}
-# Alternative 1
-a1_outcomes <- 1 
-a1_prob <- 1
-
-# Alternative 2
-a2_outcomes <- c(10, 0)
-a2_prob <- c(.1, .9)
-```
--->
 
@@
 $$ 
-$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$ with each element $A \in P(\Omega) = \mathcal{F}$ being a subset of $\Omega$.^[Note that this paper considers only the case of finite sample spaces.
+$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$ with each element $A \in P(\Omega) = \mathcal{F}$ being a subset of $\Omega$.^[<!--Open footnote-->Note that this paper considers only the case of finite sample spaces.
 The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
 2-3 and 14-15], also covers infinite sample spaces and is that of a $\sigma$-algebra.
-For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such [@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1].]
+For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such [@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1].<!--Close footnote-->]
 $P$ is a probability measure
@@
 [see @kolmogorovFoundationsTheoryProbability1950, p.
-21-22].^[See also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive yet accessible introduction to random variables.]
+21-22].^[<!--Open footnote-->See also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive yet accessible introduction to random variables.<!--Close footnote-->]
 That is, the set consisting of a single outcome $x$ can be treated as a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(X(\omega) = x)$.
@@
 
-Now, more formally, let the sample of a prospect be a set of realizations of the respective random variable $X$ according to its distribution $P_X$.^[Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+Now, more formally, let the sample of a prospect be a set of realizations of the respective random variable $X$ according to its distribution $P_X$.^[<!--Open footnote-->Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
 660].
-To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
+To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.<!--Close footnote-->]
 So, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set $S$ of stochastic processes
@@
 
-Of course, the accuracy of such inferences depends, ceteris paribus, on the size of the samples, since from the laws of large numbers [see, e.g., @kolmogorovFoundationsTheoryProbability1950] it follows that the relative frequency with which an outcome occurs in a sample converges to the outcome's objective probability only as the size of a sample increases.
-Yet, if the choices that people actually make between prospects in DfD and in DfE are described, the differences that were already outlined in the introduction are found, and the size of samples in DfE provides just one and only a partial explanation for this so-called *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009; see also @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
-This paper will address this issue<!-- review-->.
-Before that, however, the following section reviews how choices between prospects can be described using cumulative prospect theory's (CPT) *weighting function*.^[This paper also considers CPT's value function, but emphasis is put on the weighting function.]
+Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply perfectly well to DfE and it follows that the accuracy of such inferences from a sample to a prospect depends, ceteris paribus, on the size of the samples.
+Yet, when describing the choices that people actually make between prospects in DfD and in DfE, the differences outlined in the introduction are robustly found---i.e., as-if overweighting (underweighting) of rare outcomes in DfD (DfE)---and the size of samples in DfE provides just one and only a partial explanation for this so-called *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009; see also @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+More so, despite the LLN, the description-experience gap need not decrease at all, even for ever increasing sample sizes that DfE fully take into account.
+<!--Add outlook-->>
+Before so doing, however, the following section reviews in general how choices between prospects are described in cumulative prospect theory (CPT), and in particular how CPT's *weighting function* captures as-if weighting patterns.
 
@@
 
-The choices people actually make between prospects---be that in DfD or DfE---are often described in terms of deviations from expected value (EV) maximization, where the EV of a prospect is given by 
+The choices people actually make between prospects---be that in DfD or DfE---are often described in terms of deviations from the principle of mathematical expectation, according to which the prospect with the largest expected value (EV)
 $$
@@
 $$ 
-That is, following the principle of EV maximization, one would calculate the prospects' EV---each by first multiplying its outcomes $x_i$ by their respective probabilities $p_X(x_i)$ and then summing the resulting products---to subsequently choose the prospect with the largest EV.
-To *describe* how people's actual choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of CPT [@tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing the value
+should be chosen.
+To *describe* how people's actual choices deviate from this principle [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of CPT [@tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT or other originally deterministic decision models may be amended by a stochastic choice rule to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].<!--Close footnote-->]
+the value
 $$
@@
 $$ 
-with objective outcomes $x_i$ being transformed by a *value function* $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P_X$.^[Note that CPT or other originally deterministic decision models may be amended by a stochastic choice function to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].]
-Importantly, the transformation of cumulative probabilities is carried out by a weighting function $w$ (see (11) and (12) below).
-More specifically, CPT proposes cumulative decision weights as replacements for objective probabilities to account for empirical regularities in the deviations from EV maximization in DfD^[@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects such as the *certainty effect* and the *reflection effect* that were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
-Together, these empirical choice patterns indicate a violation of the EV principle and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].] that cannot be captured by the transformation of objective outcomes into subjective values $v(x)$ alone (see Footnote 6).
-In essence, to provide a proper description of people's choices between prospects in terms of their deviation from EV maximization, the proposed model is such that the inferred cumulative decision weights may be larger or smaller than the respective objective probabilities in (9); and they may therefore give more or less weight to subjective values for the overall valuation of a prospect in CPT than would be objectively warranted.
-In other words, for an inferred cumulative decision weight that is greater (smaller) than the objective probability it replaces, the respective outcome is overweighted (underweighted) in CPT.
-Accordingly one may adopt an as-if weighting terminology for the description of choices by stating that people decide *as if* they maximized the value in (10) and applied the inferred over- and underweighting pattern [@pachurWeightUncertainEvents2019].
-Importantly, the as-if prefix indicates that it cannot be concluded from the inferred cumulative decision weights that the mind does indeed perform any of the computations associated with the weighting of outcomes in CPT; rather, it processes the inputs in a way that the outputs, i.e., the resulting choice patterns, approximate the solutions from the inferred CPT model [see, e.g., @griffithsRationalUseCognitive2015].
-Below, CPT will therefore only be used as a data model to describe choices between prospects and it will be discussed---and demonstrated in a simulation---how distinct strategies of generating and integrating samples in DfE can contribute to weighting patterns that are commonly inferred when modeling respective empirical choice data.
+with objective outcomes $x_i$ being transformed by a *value function* $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P_X$.
+Importantly, the transformation of cumulative probabilities---i.e., either the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x_i$, or the probability of obtaining a strictly greater (smaller) outcome---is carried out by a weighting function $w$ (see (11) and (12) below).
+
+Let us break down (9) and (10) and provide some further background to the as-if weighting terminology in the description of choices, first by omitting mathematical detail and much of the modeling jargon:^[<!--Open footnote-->See, @farrellComputationalModelingCognition2018, for an accessible introduction to fundamental modeling concepts.<!--Close footnote-->]
+Following the principle of mathematical expectation, one would calculate the prospects' EVs according to (9) to subsequently choose the prospect with the greatest EV (EV maximization).
+However, in quite many occasions, people do not choose the prospect with the greatest EV [e.g., @erevAnomaliesForecastsDescriptive2017; @kahnemanProspectTheoryAnalysis1979].
+To describe people's actual choices in a way that effectively captures the deviations from the principle of mathematical expectation,^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, that were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
+Together, these empirical choice patterns indicate a violation of the principle of mathematical expectation and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
+CPT uses a value function $v$ and a weighting function $w$ to estimate how the objective outcomes and probabilities in (9) can be adjusted, i.e., replaced by subjective values $v(x_i)$ and cumulative decision weights $\pi_i$, respectively, so that the maximization of the value in (10) would produce synthetic choice data that is, roughly speaking, similar to the actual choice data.
+Essentially, the proposed model is such that the estimated cumulative decision weights in (10) may be greater or smaller than the respective objective probabilities in (9); and they may therefore give more or less weight to the subjective values than would be warranted by the objective probability.
+In other words, for a cumulative decision weight that is greater (smaller) than the objective probability it replaces, the respective outcome---which is transformed into a subjective value---is overweighted (underweighted) *in* CPT.
+Accordingly, to describe an empirical choice pattern, one may adopt the as-if weighting terminology which was already used in the introduction by stating that people decide *as if* they maximized the value in (10) and applied the over- and underweighting pattern that was estimated in CPT [@pachurWeightUncertainEvents2019].
+Notably, the as-if prefix indicates that it cannot be concluded from the estimated cumulative decision weights that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, it processes the inputs in a way that the outputs, i.e., the actual choice patterns, approximate the solutions from the estimated CPT model [see, e.g., @griffithsRationalUseCognitive2015].
+Therefore, this paper uses CPT merely as a data model to describe choices between prospects and it discusses---and demonstrates in a simulation---how different strategies of sequentially generating outcomes and integrating them into samples can produce weighting patterns in CPT resembling those that were estimated for empirical choice data from DfE.
 
@@
   \end{cases}
-\tag{11}
+\tag{12}
 $$
@@
 \end{aligned}
-\tag{12}
+\tag{13}
 $$

### 2022-02-18 manuscript.Rmd
Update Section 2

@@
 
-Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply perfectly well to DfE and it follows that the accuracy of such inferences from a sample to a prospect depends, ceteris paribus, on the size of the samples.
+Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply to DfE and it follows that the accuracy of inferences from a sample to a prospect depends, ceteris paribus, on the size of the samples.
 Yet, when describing the choices that people actually make between prospects in DfD and in DfE, the differences outlined in the introduction are robustly found---i.e., as-if overweighting (underweighting) of rare outcomes in DfD (DfE)---and the size of samples in DfE provides just one and only a partial explanation for this so-called *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009; see also @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
-More so, despite the LLN, the description-experience gap need not decrease at all, even for ever increasing sample sizes that DfE fully take into account.
-<!--Add outlook-->>
+More so, despite the LLN, the description-experience gap need not decrease at all, even for ever increasing sample sizes in DfE that are fully taken into account.
+Below, this paper discusses---and demonstrates in a simulation---how different strategies of sequentially generating outcomes and integrating them into samples interact with the LLN to produce distinct as-if weighting patterns, including the underweighting of rare outcomes, which may stabilize as the sample size increases.
 Before so doing, however, the following section reviews in general how choices between prospects are described in cumulative prospect theory (CPT), and in particular how CPT's *weighting function* captures as-if weighting patterns.
@@
 $$ 
-should be chosen.
-To *describe* how people's actual choices deviate from this principle [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of CPT [@tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT or other originally deterministic decision models may be amended by a stochastic choice rule to account for the probabilistic nature of choices [see, e.g., @rieskampProbabilisticNaturePreferential2008].<!--Close footnote-->]
+should be chosen (EV maximization).
+To *describe* how people's actual choices deviate from this principle [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of CPT [@tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT may be amended by a stochastic choice rule to account for the probabilistic nature of choices [@rieskampProbabilisticNaturePreferential2008].
+Most choice rules [@stottCumulativeProspectTheory2006, for an overview] are functions of the prospects' values $V$ and make a choice of a prospect with a greater $V$ only probable but not deterministic.<!--Close footnote-->]
 the value
@@
 with objective outcomes $x_i$ being transformed by a *value function* $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P_X$.
-Importantly, the transformation of cumulative probabilities---i.e., either the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x_i$, or the probability of obtaining a strictly greater (smaller) outcome---is carried out by a weighting function $w$ (see (11) and (12) below).
+Importantly, the transformation of cumulative probabilities is carried out by a nonlinear weighting function $w$ (see (12) and (13) below).
 
-Let us break down (9) and (10) and provide some further background to the as-if weighting terminology in the description of choices, first by omitting mathematical detail and much of the modeling jargon:^[<!--Open footnote-->See, @farrellComputationalModelingCognition2018, for an accessible introduction to fundamental modeling concepts.<!--Close footnote-->]
+To break down (9) and (10) and give some further background on the as-if weighting terminology in the description of choices, leaving out mathematical detail and much of the modeling jargon for now:^[<!--Open footnote-->See, @farrellComputationalModelingCognition2018, for an accessible introduction to fundamental modeling concepts.<!--Close footnote-->]
 Following the principle of mathematical expectation, one would calculate the prospects' EVs according to (9) to subsequently choose the prospect with the greatest EV (EV maximization).
@@
 Together, these empirical choice patterns indicate a violation of the principle of mathematical expectation and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
-CPT uses a value function $v$ and a weighting function $w$ to estimate how the objective outcomes and probabilities in (9) can be adjusted, i.e., replaced by subjective values $v(x_i)$ and cumulative decision weights $\pi_i$, respectively, so that the maximization of the value in (10) would produce synthetic choice data that is, roughly speaking, similar to the actual choice data.
+CPT uses a value function $v$ and a weighting function $w$ to estimate how the objective outcomes and probabilities in (9) can be adjusted, i.e., replaced by subjective values $v(x_i)$ and cumulative decision weights $\pi_i$, respectively, so that the maximization of the value in (10) would produce model-implied choice data that is, roughly speaking, similar to the actual choice data.
 Essentially, the proposed model is such that the estimated cumulative decision weights in (10) may be greater or smaller than the respective objective probabilities in (9); and they may therefore give more or less weight to the subjective values than would be warranted by the objective probability.
 In other words, for a cumulative decision weight that is greater (smaller) than the objective probability it replaces, the respective outcome---which is transformed into a subjective value---is overweighted (underweighted) *in* CPT.
-Accordingly, to describe an empirical choice pattern, one may adopt the as-if weighting terminology which was already used in the introduction by stating that people decide *as if* they maximized the value in (10) and applied the over- and underweighting pattern that was estimated in CPT [@pachurWeightUncertainEvents2019].
-Notably, the as-if prefix indicates that it cannot be concluded from the estimated cumulative decision weights that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, it processes the inputs in a way that the outputs, i.e., the actual choice patterns, approximate the solutions from the estimated CPT model [see, e.g., @griffithsRationalUseCognitive2015].
-Therefore, this paper uses CPT merely as a data model to describe choices between prospects and it discusses---and demonstrates in a simulation---how different strategies of sequentially generating outcomes and integrating them into samples can produce weighting patterns in CPT resembling those that were estimated for empirical choice data from DfE.
+Accordingly, to describe an empirical choice pattern, one may adopt the as-if weighting terminology which was already used in the introduction by stating that people decide *as if* they maximized the value in (10) and applied the over- and underweighting pattern that was estimated in CPT [see @pachurWeightUncertainEvents2019].
+<!--Notably, the as-if prefix indicates that it cannot be concluded from the estimated cumulative decision weights that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, it processes the inputs in a way that the outputs, i.e., the actual choice patterns, approximate the solutions from the estimated CPT model [see, e.g., @griffithsRationalUseCognitive2015].
+Therefore, this paper uses CPT merely as a data model to describe choices between prospects and to demonstrate how different sampling strategies can produce weighting patterns in CPT resembling those that were estimated for empirical choice data from DfE.-->
 
-Now, more formally, cumulative decision weights in CPT take the form
+Now, more formally, following @tverskyAdvancesProspectTheory1992, the objective outcomes are transformed by a value function
+$$
+\begin{aligned}
+  v : \Omega' &\to \mathbb{R} \\
+  x &\mapsto 
+  \begin{cases}
+     x_i^\alpha &\forall x_i \geq 0, \\
+     -\lambda \times |x_i|^\alpha &\text{else}
+     \; ,
+  \end{cases}
+\end{aligned}
+\tag{11}
+$$
+with $\alpha \in [0,1]$ determining the degree of the function's concavity (convexity) over the positive (negative) outcome interval, and $\lambda > 1$ increasing the function's slope over the negative outcome interval only.
+Each subjective value $v(x)$ is then multiplied (or: weighted) with a cumulative decision weight that takes the form
 $$
@@
      w^+(P(X \geq x_i)) - w^+(P(X > x_i)) \quad \forall x_i \geq 0, \\
-     w^-(P(X \leq x_i)) - w^-(P(X < x_i)) \quad \text{else}, 
+     w^-(P(X \leq x_i)) - w^-(P(X < x_i)) \quad \text{else}
+     \; , 
   \end{cases}
@@
 $$
-where $w$ is a monotonic, nonlinear function satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$ [@tverskyAdvancesProspectTheory1992].
-From the transformation of cumulative probabilities in (11), it follows that the replacement of objective probabilities by cumulative decision weights depends on the rank of the outcome to which the decision weight is assigned and the shape of the weighting function, which itself depends on the exact parameterization of the function [e.g., @goldsteinExpressionTheoryPreference1987; @tverskyAdvancesProspectTheory1992; @prelecProbabilityWeightingFunction1998; see also @stottCumulativeProspectTheory2006].
-That is, the shape of the weighting function determines over which interval on the probability scale [0, 1] cumulative probabilities are overweighted or underweighted.
-In turn, the same difference in the objective cumulative probability ...
+where $w$ is a monotonic increasing, nonlinear function $w: [0,1] \to [0,1]$ satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
+Several consequences for the weighting pattern that can be estimated in CPT follow from (12) and are reviewed one by one next:
 
-Now, although the possible deviation patterns, which span the entire probability scale, depend on the exact parameterization of the cumulative weighting function, they allow the adoption of an as-if weighting terminology for the description of choice behavior, which was originally introduced outside of the CPT models [see @pachurWeightUncertainEvents2019].
+* From the transformation of cumulative probabilities it necessarily follows that the value of a cumulative decision weight $\pi$ depends on the rank of the outcome $x$ for which $\pi$ is determined.
 
-Figure 1 illustrates such a description in CPT with different parameter settings for the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987 with
+* The value of a cumulative decision weight depends on the estimated shape of $w$.
+That is, the shape of $w$ determines over which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities---i.e., the preimages---and how much greater or smaller these image values are.
+Hence, assuming a nonlinear shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
+
+* For prospects containing either only positive or only negative outcomes, $\sum_i^n\pi_i = 1$ is satisfied.
+Accordingly, for such prospects, the replacement of objective probabilities as in (9) by cumulative decision weights as in (10) may be roughly understood as a redistribution of the entire probability mass of $P(\Omega') = 1$ across outcomes [@zilkerNonlinearProbabilityWeighting2021].
+
+\noindent
+Given that the value of each cumulative decision weight depends on the two respective cumulative probabilities in (12)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the weighting pattern in CPT may be reviewed by considering the actual shape of the weighting function.
+Therefore, Figure 1 illustrates some of the possible shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
+Now, let each $p$ on the abscissa be one of the four cumulative probabilities from (12). 
+Then each graph in Figure 1 illustrates the shape of the weighting function
 $$
@@
   w : [0,1] &\to [0,1] \\
-  p_X(x) &\mapsto \frac{\delta \times p_X(x)^{\gamma}}
-  {\delta \times p_X(x)^{\gamma} + (1-p_X(x))^{\gamma}}
+  p &\mapsto \frac{\delta \times p^{\gamma}}
+  {\delta \times p^{\gamma} + (1-p)^{\gamma}}
   \; ,
@@
 $$
-where $\gamma \in [0,2]$ and $\delta \geq 0$ determine the function's curvature and elevation, respectively.
+for the respective values of $\gamma \in [0,2]$ and $\delta > 0$.
+
 In essence, if the estimate of a cumulative decision weight is larger (smaller) than the objective probability from which it is derived, the weighting function runs above (below) the dashed identity line.
@@
 
-Research on choices in DfD and DfE 
-Specifically, when people make DfD, decision weights are typically estimated to be larger than the objective probabilities in the lower probability range.
+<!-- Brief review of CPT in DfE: Specifically, when people make DfD, decision weights are typically estimated to be larger than the objective probabilities in the lower probability range.
 However, for DfE, this pattern reverses and decisions weights are typically estimated to be smaller than the objective probabilities in the lower probability range [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; also see @wulffMetaanalyticReviewTwo2018].
+-->
 

### 2022-02-19 manuscript.Rmd
Update Section 2 (CPT)

@@
 should be chosen (EV maximization).
-To *describe* how people's actual choices deviate from this principle [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations], the models of CPT [@tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT may be amended by a stochastic choice rule to account for the probabilistic nature of choices [@rieskampProbabilisticNaturePreferential2008].
-Most choice rules [@stottCumulativeProspectTheory2006, for an overview] are functions of the prospects' values $V$ and make a choice of a prospect with a greater $V$ only probable but not deterministic.<!--Close footnote-->]
+To *describe* how people's actual choices deviate from this principle [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, that were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
+Together, these empirical choice patterns indicate a violation of the principle of mathematical expectation and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
+the models of CPT [@tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT may be amended by a stochastic choice rule to account for the probabilistic nature of choices [@rieskampProbabilisticNaturePreferential2008].
+Most choice rules [@stottCumulativeProspectTheory2006, for an overview] are functions of the prospects' values $V$ and make the choice of a prospect more probable the greater its $V$ relative to those of other prospects.
+That is, the greatest $V$ does not determine that the respect prospect is chosen by the model.<!--Close footnote-->]
 the value
@@
 with objective outcomes $x_i$ being transformed by a *value function* $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P_X$.
-Importantly, the transformation of cumulative probabilities is carried out by a nonlinear weighting function $w$ (see (12) and (13) below).
+<!--Importantly, the transformation of cumulative probabilities is carried out by a nonlinear weighting function $w$ (see (12) and (13) below).
 
-To break down (9) and (10) and give some further background on the as-if weighting terminology in the description of choices, leaving out mathematical detail and much of the modeling jargon for now:^[<!--Open footnote-->See, @farrellComputationalModelingCognition2018, for an accessible introduction to fundamental modeling concepts.<!--Close footnote-->]
-Following the principle of mathematical expectation, one would calculate the prospects' EVs according to (9) to subsequently choose the prospect with the greatest EV (EV maximization).
-However, in quite many occasions, people do not choose the prospect with the greatest EV [e.g., @erevAnomaliesForecastsDescriptive2017; @kahnemanProspectTheoryAnalysis1979].
-To describe people's actual choices in a way that effectively captures the deviations from the principle of mathematical expectation,^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, that were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
-Together, these empirical choice patterns indicate a violation of the principle of mathematical expectation and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
-CPT uses a value function $v$ and a weighting function $w$ to estimate how the objective outcomes and probabilities in (9) can be adjusted, i.e., replaced by subjective values $v(x_i)$ and cumulative decision weights $\pi_i$, respectively, so that the maximization of the value in (10) would produce model-implied choice data that is, roughly speaking, similar to the actual choice data.
+To break down (9) and (10) and give some further background on the as-if weighting terminology in the description of choices, leaving out mathematical detail and much of the modeling jargon for now:
+Following the principle of mathematical expectation, one would calculate the prospects' EVs according to (9) to subsequently choose the prospect with the greatest EV.
+However, quite often, people do not choose the prospect with the greatest EV [e.g., @erevAnomaliesForecastsDescriptive2017; @kahnemanProspectTheoryAnalysis1979].
+To describe people's actual choices in a way that effectively captures the deviations from the principle of mathematical expectation,^[@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, that were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
+Together, these empirical choice patterns indicate a violation of the principle of mathematical expectation and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].]
+CPT uses a value function $v$ and a weighting function $w$ to estimate how the objective outcomes and probabilities in (9) can be adjusted, i.e., replaced by subjective values $v(x_i)$ and cumulative decision weights $\pi_i$, respectively, so that the maximization of the value in (10) would produce model-implied choice data that are, roughly speaking, similar to the actual choice data.
 Essentially, the proposed model is such that the estimated cumulative decision weights in (10) may be greater or smaller than the respective objective probabilities in (9); and they may therefore give more or less weight to the subjective values than would be warranted by the objective probability.
-In other words, for a cumulative decision weight that is greater (smaller) than the objective probability it replaces, the respective outcome---which is transformed into a subjective value---is overweighted (underweighted) *in* CPT.
-Accordingly, to describe an empirical choice pattern, one may adopt the as-if weighting terminology which was already used in the introduction by stating that people decide *as if* they maximized the value in (10) and applied the over- and underweighting pattern that was estimated in CPT [see @pachurWeightUncertainEvents2019].
-<!--Notably, the as-if prefix indicates that it cannot be concluded from the estimated cumulative decision weights that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, it processes the inputs in a way that the outputs, i.e., the actual choice patterns, approximate the solutions from the estimated CPT model [see, e.g., @griffithsRationalUseCognitive2015].
-Therefore, this paper uses CPT merely as a data model to describe choices between prospects and to demonstrate how different sampling strategies can produce weighting patterns in CPT resembling those that were estimated for empirical choice data from DfE.-->
-
-Now, more formally, following @tverskyAdvancesProspectTheory1992, the objective outcomes are transformed by a value function
+In other words, for a cumulative decision weight that is greater (smaller) than the objective probability it replaces, the respective transformed outcome is overweighted (underweighted) *in* CPT.
+Accordingly, to describe empirical choices, one may adopt the as-if weighting terminology which was already used in the introduction by stating that people choose *as if* they maximized the value in (10) and applied the weighting pattern that was estimated in CPT [see @pachurWeightUncertainEvents2019].
+Importantly, the exact weighting pattern is captured by CPT's weighting function which, as illustrated in Figure 1, can take rather distinct graphical shapes.
+That is, each graph in Figure 1 implies a particular weighting pattern, with some of them being similar and others being rather distinct, as is described below the following paragraph.--> 
+More specifically, following @tverskyAdvancesProspectTheory1992, the objective outcomes are transformed by a value function
 $$
@@
 $$
-where $w$ is a monotonic increasing, nonlinear function $w: [0,1] \to [0,1]$ satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
+where $w$ is a monotonic increasing, nonlinear *weighting function* $w: [0,1] \to [0,1]$ satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
+
 Several consequences for the weighting pattern that can be estimated in CPT follow from (12) and are reviewed one by one next:
@@
 
-* The value of a cumulative decision weight depends on the estimated shape of $w$.
-That is, the shape of $w$ determines over which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities---i.e., the preimages---and how much greater or smaller these image values are.
-Hence, assuming a nonlinear shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
+* The value of a cumulative decision weight depends on the estimated shape of the graph of $w$, the function's parameters respectively.
+That is, the shape of the graph of $w$ displays over which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities---i.e., the preimages---and how much greater or smaller these image values are.
+Hence, assuming a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
 
@@
 \noindent
-Given that the value of each cumulative decision weight depends on the two respective cumulative probabilities in (12)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the weighting pattern in CPT may be reviewed by considering the actual shape of the weighting function.
-Therefore, Figure 1 illustrates some of the possible shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
+Given that the value of each cumulative decision weight depends on the two respective cumulative probabilities in (12)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the weighting pattern in CPT may be reviewed by considering the actual weighting function.
+Therefore, Figure 1 illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
 Now, let each $p$ on the abscissa be one of the four cumulative probabilities from (12). 
-Then each graph in Figure 1 illustrates the shape of the weighting function
+Then each graph in Figure 1 displays the graphical shape of the weighting function
 $$
@@
 $$
-for the respective values of $\gamma \in [0,2]$ and $\delta > 0$.
+for the respective values of the free parameters $\gamma \in [0,2]$ and $\delta > 0$. 
+Evidently, both parameters have distinct effects on the graphs' shape, with $\gamma$ affecting its curvature and $\delta$ the elevation.
 
-In essence, if the estimate of a cumulative decision weight is larger (smaller) than the objective probability from which it is derived, the weighting function runs above (below) the dashed identity line.
-The choice data are then described *as if* people maximized the value in (8) and applied the over- and underweighting pattern indicated by the estimated shape of the overall probability weighting function.
-
-(ref:weighting) Possible Shapes of Goldstein and Einhorn's -@goldsteinExpressionTheoryPreference1987 Weighting Function
+(ref:weighting) Possible Graphical Shapes of Goldstein and Einhorn's -@goldsteinExpressionTheoryPreference1987 Weighting Function
 
@@
 ```
+
+To begin with, the gray-dashed identity lines in Figure 1 imply a linear weighting pattern.
+That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are retrieved according to (12) would be equal to the difference between the respective objective cumulative probabilities and therefore also to the objective probabilities of the outcomes.
+Such a linear weighting pattern is implied by $\gamma = 1$ and $\delta = 1$. 
+Now, both, deviations from $\gamma = 1$ and $\delta = 1$ produce a nonlinear graphical shape. 
+That is, for $\gamma > 1$ (green graphs), the graphs take a S-shape---running below (above) the identity line for small (large) cumulative probabilities---which is more pronounced for larger deviations from $\gamma = 1$.
+Importantly, the same *small* numerical difference between two cumulative probabilities $p$ translates to varying differences between the respective images $w(p)$ depending on the interval on the cumulative probability scale.
+That is, because of the S-shaped curvature, the differences between the images $w(p)$ may be smaller than those of the respective cumulative probabilities in the lower and upper part of the cumulative probability scale, but may be considerably greater in the middle part.
+As a consequence, the cumulative decisions weights that are retrieved from the images of $w$ may be smaller than the respective objective probabilities for small-probability outcomes of either a low rank or a high rank, but may be larger for small-probability outcomes of middle ranks.
+Regarding the underweighting of small-probability outcomes of low or high rank, the weighting pattern that is captured by the graphical S-shape of CPT's weighting function is denoted the underweighting of rare outcomes.
+Note that for all $\gamma < 1$ (blue graphs) the graph of $w$ takes an inverse S-shape and the entire weighting pattern---denoted as the overweighting of rare outcomes---is reversed.
+Nonetheless, the effects of $\gamma$ depend rather strongly on $\delta$, which affects the elevation of the graph.
+As can be seen,
 

### 2022-02-22 manuscript.Rmd
Preliminary Draft Section 2

@@
 
-Now, more formally,^[<!--Open footnote-->Paragraphs with this beginning usually formalize the ideas of the preceding paragraphs or elaborate on them by using mathematical expressions and concepts.
-Although I consider these paragraphs important, the major propositions of this paper should be captured despite skipping them.<!--Close footnote-->]
-let us treat the choice alternatives as elements $c$ of the set $C$.
+Now, more formally, let us treat the choice alternatives as elements $c$ of the set $C$.
 To each $c \in C$ is then assigned some information from the inputs and this information may be used by the mind to learn about the properties of the respective alternative.
@@
 Importantly, the information that is provided about the choice alternatives can come in many forms.
-In *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all relevant properties of the choice alternatives.
+For example, in *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all relevant properties of the choice alternatives.
 Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], inputs take the form of *samples*.
-In this latter case, the properties of the choice alternatives are not described and therefore not known with certainty, but they must be inferred from the outcomes that occurred when the alternatives were chosen in similar past decisions.
-Although these distinct input forms may in principle carry the same information about a given set of choice alternatives, behavioral decision research has so far produced a large body of papers indicating that---if a quite general perspective is taken---there are robust differences between the choices that are made in DfD and DfE.
-That is, ceteris paribus, empirical choice patterns across studies indicate that in DfD people choose *as if* a rare outcome is given more weight in the evaluation of a choice alternative than would be objectively warranted by the principle of mathematical expectation (see below); in turn, in DfE, people choose *as if* the same rare outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @hauDescriptionexperienceGapRisky2008; @rakowBiasedSamplesNot2008; @ungemachAreProbabilitiesOverweighted2009; @camilleriWhenWhyRare2011; @kellenHowVariantAre2016; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructBehaviorGap2017].
-Hereafter, we refer to these choice patterns as the as-if overweighting and underweighting of rare outcomes, respectively.
+In this latter case, the properties of the choice alternatives are not described and therefore not known with certainty, but they must be inferred from the consequences (hereafter: outcomes) that occurred when the alternatives were chosen in similar past decisions.
+Although these distinct input forms may in principle carry the same information about a given set of choice alternatives, behavioral decision research has so far produced a large body of papers indicating that---if a quite general perspective is taken---there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
+In one reading of the gap, empirical choice patterns indicate that in DfD people choose *as if* a rare outcome is given more weight in the evaluation of a choice alternative than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose *as if* the same rare outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+Hereafter, these choice patterns are referred to as the as-if overweighting and underweighting of rare outcomes, respectively.
 
@@
 Essentially, it discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into samples (hereafter: sampling strategies) can produce distinct choice patterns in DfE---among them, the as-if underweighting of rare outcomes [see @hillsInformationSearchDecisions2010, for the original formulation of this claim].
-<!-- It thereby proposes that ... -->
 
@@
 In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices in DfE in terms of deviations from the principle of mathematical expectation.
-<!-- Outline of the section -->
 In the section that follows, sampling strategies are treated in quite some detail.
@@
 Thereafter, a simulation is presented in which the theoretical claims that are made in the preceding section are implemented in a computational model to simulate choice data in DfE.
-The predictions of the model are summarized by fitting the choice data in CPT.
+The predictions of the model are summarized and fitted in CPT.
 The paper closes with a summary and a conclusion.
@@
 Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[<!--Open footnote-->See @knightRiskUncertaintyProfit1921, Chapter 1, for a discussion of the reasonableness of such abstractions.<!--Close footnote-->]
+Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].
 These fundamental properties are considered the possible outcomes of a choice alternative (hereafter: $x_i$) and the probabilities with which these outcomes occur following the choice of the alternative (hereafter: $p_X(x_i)$).
@@
 
-Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply to DfE and it follows that the accuracy of inferences from a sample to a prospect depends, ceteris paribus, on the size of the samples.
-Yet, when describing the choices that people actually make between prospects in DfD and in DfE, the differences outlined in the introduction are robustly found---i.e., as-if overweighting (underweighting) of rare outcomes in DfD (DfE)---and the size of samples in DfE provides just one and only a partial explanation for this so-called *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009; see also @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
-More so, despite the LLN, the description-experience gap need not decrease at all, even for ever increasing sample sizes in DfE that are fully taken into account.
-Below, this paper discusses---and demonstrates in a simulation---how different strategies of sequentially generating outcomes and integrating them into samples interact with the LLN to produce distinct as-if weighting patterns, including the underweighting of rare outcomes, which may stabilize as the sample size increases.
-Before so doing, however, the following section reviews in general how choices between prospects are described in cumulative prospect theory (CPT), and in particular how CPT's *weighting function* captures as-if weighting patterns.
+Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply to DfE and it follows that the accuracy of such inferences from a sample to a prospect depends, ceteris paribus, on the size of the samples.
+In fact, one explanation for the as-if underweighting of rare outcomes in DfE and the description-experience gap outlined in the introduction is that people rely on small samples, which, due to the skewness of the binomial distribution, cause the relative frequencies with which rare outcomes occur in a sample to be smaller than their objective probabilities [@hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; see also @hertwigDecisionsExperienceWhy2010].
+The invoked argument is then that what may appear as if people were underweighting rare outcomes relative to what would be warranted on the basis of their objective probabilities---following the principle of mathematical expectation---may in fact be consistent with an as-if overweighting relative to what would be warranted on the basis of the experienced probabilities [@foxDecisionsExperienceSampling2006].
+Yet, it seems that the small size of samples in DfE provides just one and only a partial explanation for the description-experience gap [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
+More so, despite the LLN, the gap need not narrow at all, even for ever increasing sample sizes that are fully taken into account.
+Particularly, this paper discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into samples interact with the LLN to produce distinct choice patterns in DfE---including the as-if underweighting of rare outcomes---that tend to stabilize as the sample size increases.
+Before so doing, however, the following section reviews how cumulative prospect theory (CPT) can be used as a data model that captures systematic deviations from the principle of mathematical expectation in the parameter estimates of a *value* and a *weighting function*.
 
-# The Description of Choices in CPT and the As-If Underweighting in DfE
+# The Description of Choices and Weighting Patterns in CPT
 
@@
 EV = \sum_i^n x_i \times p_X(x_i)
-\; .
 \tag{9}
@@
 the models of CPT [@tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT may be amended by a stochastic choice rule to account for the probabilistic nature of choices [@rieskampProbabilisticNaturePreferential2008].
-Most choice rules [@stottCumulativeProspectTheory2006, for an overview] are functions of the prospects' values $V$ and make the choice of a prospect more probable the greater its $V$ relative to those of other prospects.
-That is, the greatest $V$ does not determine that the respect prospect is chosen by the model.<!--Close footnote-->]
+Most choice rules [@stottCumulativeProspectTheory2006, for an overview] are functions of the prospects' values $V$ and make the choice of a prospect more probable the greater its $V$ relative to those of other prospects.<!--Close footnote-->]
 the value
@@
 $$ 
-with objective outcomes $x_i$ being transformed by a *value function* $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P_X$.
-<!--Importantly, the transformation of cumulative probabilities is carried out by a nonlinear weighting function $w$ (see (12) and (13) below).
-
-To break down (9) and (10) and give some further background on the as-if weighting terminology in the description of choices, leaving out mathematical detail and much of the modeling jargon for now:
-Following the principle of mathematical expectation, one would calculate the prospects' EVs according to (9) to subsequently choose the prospect with the greatest EV.
-However, quite often, people do not choose the prospect with the greatest EV [e.g., @erevAnomaliesForecastsDescriptive2017; @kahnemanProspectTheoryAnalysis1979].
-To describe people's actual choices in a way that effectively captures the deviations from the principle of mathematical expectation,^[@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, that were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
-Together, these empirical choice patterns indicate a violation of the principle of mathematical expectation and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].]
-CPT uses a value function $v$ and a weighting function $w$ to estimate how the objective outcomes and probabilities in (9) can be adjusted, i.e., replaced by subjective values $v(x_i)$ and cumulative decision weights $\pi_i$, respectively, so that the maximization of the value in (10) would produce model-implied choice data that are, roughly speaking, similar to the actual choice data.
-Essentially, the proposed model is such that the estimated cumulative decision weights in (10) may be greater or smaller than the respective objective probabilities in (9); and they may therefore give more or less weight to the subjective values than would be warranted by the objective probability.
-In other words, for a cumulative decision weight that is greater (smaller) than the objective probability it replaces, the respective transformed outcome is overweighted (underweighted) *in* CPT.
-Accordingly, to describe empirical choices, one may adopt the as-if weighting terminology which was already used in the introduction by stating that people choose *as if* they maximized the value in (10) and applied the weighting pattern that was estimated in CPT [see @pachurWeightUncertainEvents2019].
-Importantly, the exact weighting pattern is captured by CPT's weighting function which, as illustrated in Figure 1, can take rather distinct graphical shapes.
-That is, each graph in Figure 1 implies a particular weighting pattern, with some of them being similar and others being rather distinct, as is described below the following paragraph.--> 
+with objective outcomes $x_i$ being transformed by a value function $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P_X$.
 More specifically, following @tverskyAdvancesProspectTheory1992, the objective outcomes are transformed by a value function
@@
 $$
-where $w$ is a monotonic increasing, nonlinear *weighting function* $w: [0,1] \to [0,1]$ satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
+where $w$ is a monotonic increasing, nonlinear weighting function $w: [0,1] \to [0,1]$ satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
 
-Several consequences for the weighting pattern that can be estimated in CPT follow from (12) and are reviewed one by one next:
+Essentially, the proposed model is such that the cumulative decision weights derived for the outcomes may be greater or smaller than their objective probabilities, causing the transformed outcomes---i.e., the subjective values---to be over- or underweighted *in* CPT, respectively.
+<!--Accordingly, one may adopt an as-if weighting terminology, stating that people choose *as if* they maximized the value in (10) and applied the weighting pattern that was estimated in CPT.-->
+Now, several consequences for the weighting pattern that can be estimated in CPT follow from (12), which are reviewed one by one next:
 
@@
 
-* The value of a cumulative decision weight depends on the estimated shape of the graph of $w$, the function's parameters respectively.
-That is, the shape of the graph of $w$ displays over which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities---i.e., the preimages---and how much greater or smaller these image values are.
+* The value of a cumulative decision weight depends on the estimated shape of the graph of $w$, the weighting function's parameters respectively.
+That is, the shape of the graph of $w$ displays in which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities---i.e., the preimages---and how much greater or smaller these image values are.
 Hence, assuming a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
@@
 * For prospects containing either only positive or only negative outcomes, $\sum_i^n\pi_i = 1$ is satisfied.
-Accordingly, for such prospects, the replacement of objective probabilities as in (9) by cumulative decision weights as in (10) may be roughly understood as a redistribution of the entire probability mass of $P(\Omega') = 1$ across outcomes [@zilkerNonlinearProbabilityWeighting2021].
+Accordingly, for such prospects, the weighting of subjective values with cumulative decision weights rather than with objective probabilities may be roughly understood as a redistribution of the entire probability mass of $P(\Omega') = 1$ across outcomes [@zilkerNonlinearProbabilityWeighting2021].
 
 \noindent
-Given that the value of each cumulative decision weight depends on the two respective cumulative probabilities in (12)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the weighting pattern in CPT may be reviewed by considering the actual weighting function.
-Therefore, Figure 1 illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
+Given that the value of each cumulative decision weight depends on the two transformed cumulative probabilities in (12)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the weighting pattern are reviewed by considering the actual weighting function.
+Therefore, Figure\ \@ref(fig:w-shapes) illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
 Now, let each $p$ on the abscissa be one of the four cumulative probabilities from (12). 
-Then each graph in Figure 1 displays the graphical shape of the weighting function
+Then each graph in Figure\ \@ref(fig:w-shapes) displays the graphical shape of the weighting function
 $$
@@
 $$
-for the respective values of the free parameters $\gamma \in [0,2]$ and $\delta > 0$. 
-Evidently, both parameters have distinct effects on the graphs' shape, with $\gamma$ affecting its curvature and $\delta$ the elevation.
+for the respective values of the parameters $\gamma \in [0,2]$ and $\delta > 0$.
+Evidently, both parameters have distinct effects on the graphs' shape, with $\gamma$ affecting the curvature and $\delta$ the elevation.
+As a consequence from (12) then, each combination of parameters implies a particular weighting pattern, with some of them being similar and others being rather distinct.
 
@@
 
-```{r fig.cap="(ref:weighting)"}
+```{r w-shapes, fig.cap="(ref:weighting)"}
 wf <- tibble(gamma = seq(.1, 2, .1)) %>%
@@
 
-To begin with, the gray-dashed identity lines in Figure 1 imply a linear weighting pattern.
-That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are retrieved according to (12) would be equal to the difference between the respective objective cumulative probabilities and therefore also to the objective probabilities of the outcomes.
+To begin with, the gray-dashed identity lines in Figure\ \@ref(fig:w-shapes) imply a linear weighting pattern.
+That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are derived according to (12) would be equal to the differences between the respective objective cumulative probabilities and therefore also to the objective probabilities of the outcomes for which the weights are determined.
 Such a linear weighting pattern is implied by $\gamma = 1$ and $\delta = 1$. 
-Now, both, deviations from $\gamma = 1$ and $\delta = 1$ produce a nonlinear graphical shape. 
-That is, for $\gamma > 1$ (green graphs), the graphs take a S-shape---running below (above) the identity line for small (large) cumulative probabilities---which is more pronounced for larger deviations from $\gamma = 1$.
-Importantly, the same *small* numerical difference between two cumulative probabilities $p$ translates to varying differences between the respective images $w(p)$ depending on the interval on the cumulative probability scale.
-That is, because of the S-shaped curvature, the differences between the images $w(p)$ may be smaller than those of the respective cumulative probabilities in the lower and upper part of the cumulative probability scale, but may be considerably greater in the middle part.
-As a consequence, the cumulative decisions weights that are retrieved from the images of $w$ may be smaller than the respective objective probabilities for small-probability outcomes of either a low rank or a high rank, but may be larger for small-probability outcomes of middle ranks.
-Regarding the underweighting of small-probability outcomes of low or high rank, the weighting pattern that is captured by the graphical S-shape of CPT's weighting function is denoted the underweighting of rare outcomes.
-Note that for all $\gamma < 1$ (blue graphs) the graph of $w$ takes an inverse S-shape and the entire weighting pattern---denoted as the overweighting of rare outcomes---is reversed.
-Nonetheless, the effects of $\gamma$ depend rather strongly on $\delta$, which affects the elevation of the graph.
-As can be seen,
+Now, both deviations from $\gamma = 1$ and $\delta = 1$ produce a nonlinear graphical shape.
+That is, for $\gamma > 1$ (green graphs), the graphs take a S-shape---running below (above) the identity line for small (large) cumulative probabilities---which is more accentuated for larger deviations from $\gamma = 1$.
+Importantly, the same *small* numerical difference between two cumulative probabilities $p$ then translates to varying differences between the respective images $w(p)$ depending on the interval on the cumulative probability scale.
+Specifically, because of the S-shaped curvature, the differences between the images $w(p)$ may be smaller than those of the respective cumulative probabilities in the lower and upper part of the cumulative probability scale, but may be considerably greater in the middle part.
+As a consequence, the cumulative decisions weights that are retrieved from the images of $w$ are smaller than the respective objective probabilities for small-probability outcomes of either a low rank or a high rank, but are larger for small-probability outcomes of middle ranks.^[<!--Open footnote-->Note that the distinction between outcomes of low/high rank and outcomes of middle rank is unnecessary for two-outcome prospects [see @tverskyAdvancesProspectTheory1992].
+However, for prospects with finite many outcomes, this distinction is rather critical.
+E.g., the fact that CPT may then weigh outcomes of the same small probability differently, is one reason why the description-experience gap should not be equated with a reversed weighting pattern in CPT [see @hertwigConstructBehaviorGap2018].
+I.e., neither could the gap then be interpreted in terms of an as-if underweighting (overweighting) of rare events in DfE (DfD), nor can any of the factors so far considered as a contributor to the gap (e.g., sample size, optional stopping, recency, etc.) plausibly explain why not all small-probability outcomes are affected in the same way.<!--Close footnote-->]
+Note that for all $\gamma < 1$ (blue graphs) the graph of $w$ takes an inverse S-shape and the entire weighting pattern is reversed.
+Moreover, the shape of the weighting function, and thus the weighting pattern, also depends strongly on $\delta$, which affects the overall elevation of the graph.
+That is, for $\delta < 1$, the interval on the cumulative probability scale over which the weighting function runs below the identity line is greater than the interval over which the weighting function runs above the identity line; and this pattern reverses for $\delta > 1$.
+More specifically, $\delta$ shifts across the entire cumulative probability scale the intervals within which small differences between objective cumulative probabilities translate to either smaller or greater cumulative decision weights.
+In other words then, for any decrease (increase) in $\delta$, the underweighting of small probability outcomes extends to more outcomes at the lower (higher) end of the outcome range.
 
-<!-- Brief review of CPT in DfE: Specifically, when people make DfD, decision weights are typically estimated to be larger than the objective probabilities in the lower probability range.
-However, for DfE, this pattern reverses and decisions weights are typically estimated to be smaller than the objective probabilities in the lower probability range [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; also see @wulffMetaanalyticReviewTwo2018].
--->
+To summarize the preceding paragraphs, CPT can be used as a data model to describe choices between prospects by reducing systematic deviations from the principle of mathematical expectation to the parameter estimates of its value and weighting function.
+Moreover, each estimated weighting function captures a weighting pattern.
+Although the possible weighting patterns that can be captured depend on the exact parameterization of the weighting function [e.g., @goldsteinExpressionTheoryPreference1987], the latter's graph can usually take a more or less accentuated (inverse) S-shape.
+The parameter estimates and the implied graphical shape of the weighting function then translate to a weighting pattern where small-probability outcomes of low or high rank are underweighted (overweighted) in the overall evaluation of a prospect according to (10).
+Notably, the distinction between outcomes of low/high rank and outcomes of middle rank can be omitted for two-outcome prospects.
+In such a case, the weighting pattern reduces to either an underweighting or an overweighting of rare outcomes in CPT. 
+For the description of choices between at most two-outcome gambles, one may then adopt the as-if weighting terminology from above, by stating that people decide as if they were either underweighting or overweighting rare outcomes.
+Nevertheless, it cannot be concluded from the estimated weighting pattern that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, the mind processes the inputs in a way that the outputs, i.e., the actual choice patterns, approximate the solutions from the estimated CPT model [see, e.g., @griffithsRationalUseCognitive2015].
+Therefore, this paper uses CPT merely as a data model to describe choices between prospects and to demonstrate how different sampling strategies can produce weighting patterns in CPT resembling those that were estimated for empirical choice data from DfE.
 
@@
 # get median trial length for each parameter combination
-
 trial_length <- choices %>% 
@@
 The latter deviation may be explained by the potential scale reduction factors for the respective parameter estimates, which indicate that the MCMC chains did not converge (see [Appendix 3][Appendix 3: Convergence Diagnostics for CPT Parameters]).
+
+```{r eval=FALSE}
+cpt_long %>% 
+  filter(parameter == "gamma") %>% 
+  ggplot(aes(x=s, y = mean, color = s)) +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point(size = 2) +
+  scale_color_scico(palette = "acton") + 
+  scale_x_continuous(breaks = seq(0,1,.2)) +
+  facet_grid(boundary~a) + 
+  theme_minimal() 
+```
 

### 2022-02-23 manuscript.Rmd
Update Section 2 and 3

@@
 For example, in *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all relevant properties of the choice alternatives.
-Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], inputs take the form of *samples*.
-In this latter case, the properties of the choice alternatives are not described and therefore not known with certainty, but they must be inferred from the consequences (hereafter: outcomes) that occurred when the alternatives were chosen in similar past decisions.
+Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], the properties of the choice alternatives are latent---i.e., not described---and therefore not known with certainty, but they must be inferred from the consequences (hereafter: outcomes) that occurred when the alternatives were chosen in similar past decisions.
 Although these distinct input forms may in principle carry the same information about a given set of choice alternatives, behavioral decision research has so far produced a large body of papers indicating that---if a quite general perspective is taken---there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
-In one reading of the gap, empirical choice patterns indicate that in DfD people choose *as if* a rare outcome is given more weight in the evaluation of a choice alternative than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose *as if* the same rare outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+In one reading of the gap, empirical choice patterns indicate that in DfD people choose as if a rare outcome is given more weight in the evaluation of a choice alternative than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose as if the same rare outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
 Hereafter, these choice patterns are referred to as the as-if overweighting and underweighting of rare outcomes, respectively.
@@
 This paper uses the as-if underweighting of rare outcomes as a starting point for an inquiry into the sampling process upfront choices in DfE.
-Essentially, it discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into samples (hereafter: sampling strategies) can produce distinct choice patterns in DfE---among them, the as-if underweighting of rare outcomes [see @hillsInformationSearchDecisions2010, for the original formulation of this claim].
+Essentially, it discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into *samples* (hereafter: sampling strategies) can produce distinct choice patterns in DfE---among them, the as-if underweighting of rare outcomes [see @hillsInformationSearchDecisions2010, for the original formulation of this claim].
 
@@
 In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices in DfE in terms of deviations from the principle of mathematical expectation.
-In the section that follows, sampling strategies are treated in quite some detail.
+In the section that follows, sampling strategies are treated.
 <!-- Outline of the section -->
@@
 Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space. 
-Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ is the sample space containing a finite set of elements
+Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ is the sample space containing a finite set of elements, one of which results from choosing the respective prospect:
 $$
@@
 21-22].^[<!--Open footnote-->See also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive yet accessible introduction to random variables.<!--Close footnote-->]
-That is, the set consisting of a single outcome $x$ can be treated as a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(X(\omega) = x)$.
+That is, the set consisting of a single outcome $x$ is a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(X(\omega) = x)$.
 Note that the probability measure in (5) and (6), respectively, is a discrete random variable's distribution and therefore a prospect.
@@
 $$
-with each element $c \in C$ being a distribution $P_X$ of a random variable defined on a different probability space.
+with each element $c \in C$ being a distribution $P_X$ of a random variable defined on its own probability space.
 Accordingly, each $c$ can itself be considered a set of outcome-probability pairs $(x_i, p_X(x_i)) \in \{(x_1, p_X(x_1)), ..., (x_n, p_X(x_n))\}$.
@@
 However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes-probability pairs.
-In such cases, people would make decisions from description (DfD), since the information from which the mind learns about the prospects are complete descriptions thereof.
-Yet, rather often, people make decisions from experience (DfE), where the mind can learn about the prospects only from a record of past experiences with them.
+In such cases, people would make DfD, since the information from which the mind learns about the prospects are complete descriptions thereof.
+Yet, rather often, people make DfE, where the mind can learn about the latent prospects only from a record of past experiences with them.
 That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is a rough description of a sample.
@@
 
-Now, more formally, let the sample of a prospect be a set of realizations of the respective random variable $X$ according to its distribution $P_X$.^[<!--Open footnote-->Note that this paper considers the counterfactual case where samples are random, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+Now, more formally, let the sample of a prospect be a set of realizations of the respective random variable according to its distribution $P_X$.^[<!--Open footnote-->Note that this paper considers random samples, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
 660].
-To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.<!--Close footnote-->]
+To account for non-random sampling, e.g., in the form of sampling biases [see @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [see, e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped.<!--Close footnote-->]
 So, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set $S$ of stochastic processes
@@
 with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the length of the respective sequence.
-The sets of realizations that result from these stochastic processes may then be used to make an uncertain inference about the respective sets of outcome-probability pairs in (7).
+The realizations that result from each stochastic process $s \in S$ may then be integrated into a sample of $N$ experienced outcomes or into multiple smaller samples.
+The samples may then be used to make an uncertain inference about the latent prospects in (7), the sets of outcome-probability pairs respectively.
 
-Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply to DfE and it follows that the accuracy of such inferences from a sample to a prospect depends, ceteris paribus, on the size of the samples.
-In fact, one explanation for the as-if underweighting of rare outcomes in DfE and the description-experience gap outlined in the introduction is that people rely on small samples, which, due to the skewness of the binomial distribution, cause the relative frequencies with which rare outcomes occur in a sample to be smaller than their objective probabilities [@hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; see also @hertwigDecisionsExperienceWhy2010].
-The invoked argument is then that what may appear as if people were underweighting rare outcomes relative to what would be warranted on the basis of their objective probabilities---following the principle of mathematical expectation---may in fact be consistent with an as-if overweighting relative to what would be warranted on the basis of the experienced probabilities [@foxDecisionsExperienceSampling2006].
+Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply to DfE and it follows that the accuracy of an inference from a sample about the properties of a latent prospect depends, ceteris paribus, on the size of the sample.
+In fact, one explanation for the as-if underweighting of rare outcomes in DfE and the description-experience gap outlined in the introduction is that people rely on too small samples, which, due to the skewness of the binomial distribution, cause the relative frequencies with which rare outcomes occur in a sample to be smaller than their objective probabilities [@hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; see also @hertwigDecisionsExperienceWhy2010].
+The invoked argument is then that what may appear as if people were underweighting rare outcomes relative to what would be warranted on the basis of their objective probabilities---following the principle of mathematical expectation---may in fact be consistent with an as-if overweighting relative to what would be warranted on the basis of the experienced relative frequencies [@foxDecisionsExperienceSampling2006].
 Yet, it seems that the small size of samples in DfE provides just one and only a partial explanation for the description-experience gap [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
@@
 Particularly, this paper discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into samples interact with the LLN to produce distinct choice patterns in DfE---including the as-if underweighting of rare outcomes---that tend to stabilize as the sample size increases.
-Before so doing, however, the following section reviews how cumulative prospect theory (CPT) can be used as a data model that captures systematic deviations from the principle of mathematical expectation in the parameter estimates of a *value* and a *weighting function*.
+Before so doing, however, the following section reviews how CPT can be used as a data model that captures systematic deviations from the principle of mathematical expectation in the parameter estimates of a *value* and a *weighting function*.
 
@@
 should be chosen (EV maximization).
-To *describe* how people's actual choices deviate from this principle [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, that were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
+To *describe* how people's actual choices deviate from this principle [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, which were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
 Together, these empirical choice patterns indicate a violation of the principle of mathematical expectation and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
-the models of CPT [@tverskyAdvancesProspectTheory1992] and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT may be amended by a stochastic choice rule to account for the probabilistic nature of choices [@rieskampProbabilisticNaturePreferential2008].
-Most choice rules [@stottCumulativeProspectTheory2006, for an overview] are functions of the prospects' values $V$ and make the choice of a prospect more probable the greater its $V$ relative to those of other prospects.<!--Close footnote-->]
+CPT and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT may be amended by a stochastic choice rule to account for the probabilistic nature of choices [@rieskampProbabilisticNaturePreferential2008].
+Stochastic choice rules [@stottCumulativeProspectTheory2006, for an overview] make the choice of a prospect more probable the better its valuation relative to those of other prospects.<!--Close footnote-->]
 the value
@@
 <!--Accordingly, one may adopt an as-if weighting terminology, stating that people choose *as if* they maximized the value in (10) and applied the weighting pattern that was estimated in CPT.-->
-Now, several consequences for the weighting pattern that can be estimated in CPT follow from (12), which are reviewed one by one next:
+Now, several consequences for the weighting pattern that can be estimated in CPT follow from (12), which are reviewed next:
 
@@
 * The value of a cumulative decision weight depends on the estimated shape of the graph of $w$, the weighting function's parameters respectively.
-That is, the shape of the graph of $w$ displays in which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities---i.e., the preimages---and how much greater or smaller these image values are.
+That is, the shape of the graph of $w$ displays in which interval on the cumulative probability scale $[0,1]$ the images of $w$, $w(p)$ take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
 Hence, assuming a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
@@
 Importantly, the same *small* numerical difference between two cumulative probabilities $p$ then translates to varying differences between the respective images $w(p)$ depending on the interval on the cumulative probability scale.
-Specifically, because of the S-shaped curvature, the differences between the images $w(p)$ may be smaller than those of the respective cumulative probabilities in the lower and upper part of the cumulative probability scale, but may be considerably greater in the middle part.
-As a consequence, the cumulative decisions weights that are retrieved from the images of $w$ are smaller than the respective objective probabilities for small-probability outcomes of either a low rank or a high rank, but are larger for small-probability outcomes of middle ranks.^[<!--Open footnote-->Note that the distinction between outcomes of low/high rank and outcomes of middle rank is unnecessary for two-outcome prospects [see @tverskyAdvancesProspectTheory1992].
-However, for prospects with finite many outcomes, this distinction is rather critical.
-E.g., the fact that CPT may then weigh outcomes of the same small probability differently, is one reason why the description-experience gap should not be equated with a reversed weighting pattern in CPT [see @hertwigConstructBehaviorGap2018].
-I.e., neither could the gap then be interpreted in terms of an as-if underweighting (overweighting) of rare events in DfE (DfD), nor can any of the factors so far considered as a contributor to the gap (e.g., sample size, optional stopping, recency, etc.) plausibly explain why not all small-probability outcomes are affected in the same way.<!--Close footnote-->]
+Specifically, because of the S-shaped curvature, the differences between the images $w(p)$ may be smaller than those between the respective cumulative probabilities in the lower and upper part of the cumulative probability scale, but may be considerably greater in the middle part.
+As a consequence, the cumulative decisions weights are smaller than the respective objective probabilities for small-probability outcomes of either a low rank or a high rank, but they are larger for small-probability outcomes of a middle rank.^[<!--Open footnote-->Note that the distinction between outcomes of either low/high rank or middle rank is unnecessary for two-outcome prospects [see @tverskyAdvancesProspectTheory1992].
+However, for finite many outcomes, the distinction is critical.
+More so, the fact that CPT may weigh outcomes of the same small probability differently, adds another reasons why the description-experience gap should not be equated with a reversed weighting pattern in CPT [see @hertwigConstructBehaviorGap2018].
+I.e., neither could the gap then be interpreted in terms of an as-if underweighting (overweighting) of rare outcomes in DfE (DfD), nor would any of the potential contributors to the gap considered so far [see, e.g., @hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than others.<!--Close footnote-->]
 Note that for all $\gamma < 1$ (blue graphs) the graph of $w$ takes an inverse S-shape and the entire weighting pattern is reversed.
-Moreover, the shape of the weighting function, and thus the weighting pattern, also depends strongly on $\delta$, which affects the overall elevation of the graph.
+Moreover, the shape of the weighting function, and thus the weighting pattern, depends strongly on $\delta$, which affects the overall elevation of the graph.
 That is, for $\delta < 1$, the interval on the cumulative probability scale over which the weighting function runs below the identity line is greater than the interval over which the weighting function runs above the identity line; and this pattern reverses for $\delta > 1$.
@@
 
-To summarize the preceding paragraphs, CPT can be used as a data model to describe choices between prospects by reducing systematic deviations from the principle of mathematical expectation to the parameter estimates of its value and weighting function.
-Moreover, each estimated weighting function captures a weighting pattern.
-Although the possible weighting patterns that can be captured depend on the exact parameterization of the weighting function [e.g., @goldsteinExpressionTheoryPreference1987], the latter's graph can usually take a more or less accentuated (inverse) S-shape.
-The parameter estimates and the implied graphical shape of the weighting function then translate to a weighting pattern where small-probability outcomes of low or high rank are underweighted (overweighted) in the overall evaluation of a prospect according to (10).
-Notably, the distinction between outcomes of low/high rank and outcomes of middle rank can be omitted for two-outcome prospects.
-In such a case, the weighting pattern reduces to either an underweighting or an overweighting of rare outcomes in CPT. 
-For the description of choices between at most two-outcome gambles, one may then adopt the as-if weighting terminology from above, by stating that people decide as if they were either underweighting or overweighting rare outcomes.
-Nevertheless, it cannot be concluded from the estimated weighting pattern that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, the mind processes the inputs in a way that the outputs, i.e., the actual choice patterns, approximate the solutions from the estimated CPT model [see, e.g., @griffithsRationalUseCognitive2015].
-Therefore, this paper uses CPT merely as a data model to describe choices between prospects and to demonstrate how different sampling strategies can produce weighting patterns in CPT resembling those that were estimated for empirical choice data from DfE.
+To summarize the preceding paragraphs, CPT is data model that can be used to describe choices between prospects by capturing systematic deviations from the principle of mathematical expectation in the parameter estimates of its value and weighting function.
+Importantly, each estimated weighting function implies a weighting pattern.
+Although the possible weighting patterns depend on the exact parameterization of the weighting function [e.g., @goldsteinExpressionTheoryPreference1987], the latter's graph usually takes a more or less accentuated (inverse) S-shape, which implies a weighting pattern where small-probability outcomes of low and high rank are underweighted (overweighted) in CPT's overall evaluation of a prospect according to (10).
+Notably, for the case of choices between at most two-outcome prospects, the weighting pattern reduces to either an underweighting or overweighting of rare outcomes.
+For the description of such choices, one may then adopt the as-if weighting terminology from above, by stating that people decide as if they were either underweighting or overweighting rare outcomes.
+<!-- Add paragraph about CPT analysis of DfE-->
 
-# Sampling Strategies
+To be clear, however, the as-if prefix indicates that it cannot be concluded from the estimated weighting pattern that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, the mind processes the information about the choice alternatives in a way that the resulting choices translate to the estimated CPT model.
+The as-if weighting terminology is therefore reminiscent of the distinction between different levels of explanation [@marrVisionComputationalInvestigation1982].
+That is, CPT may be considered a computational-level theory that specifies the computational problem the mind faces during decisions between prospects, and how this problem may be solved by the abstract calculus reviewed above.
+However, as such, CPT cannot substitute algorithmic-level theories that make claims about how exactly the mind transforms the inputs to the decision making process into outputs---i.e., into choices---which approximate the solutions of CPT's calculus [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
+Therefore, this paper uses CPT merely as a data model and continues to inquire how on the algorithmic level the mind may integrate sampling strategies into the information-processing chain upfront choices in DfE.
+More specifically, the following two sections discuss and demonstrate how different strategies of generating outcomes and integrating them into samples produce distinct choice patterns in DfE, and how these choice patterns translate to the weighting pattern in CPT.^[<!--Open footnote-->CPT's value function will also be considered but emphasis is put on the weighting function.<!--Close footnote-->]
+
+# Sampling Strategies in DfE
+
+The need to distinguish between the computational and the algorithmic level in the domain of decision making is exemplified by the fact that information about prospects may come in the form of descriptions or samples.
+Whereas CPT can be used to model choices in DfD and DfE, the information-processing chains upfront choices in DfE cannot be identical to those in DfD.
+That is, inputs in the form of experienced outcomes require different algorithms to be processed than do descriptions of outcomes and their probabilities.
+Specifically, the mind must integrate the experienced outcomes into a sample in order to make an inference about the properties of the latent prospects, the outcome-probability pairs respectively.
 

### 2022-02-25 manuscript.Rmd
Update Simulation Study

@@
                ggplot2,
-               ggbeeswarm,
-               scico)
+               viridis,
+               scico,
+               latex2exp)
 ```
@@
 
-Now, more formally, let the sample of a prospect be a set of realizations of the respective random variable according to its distribution $P_X$.^[<!--Open footnote-->Note that this paper considers random samples, although it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
-660].
-To account for non-random sampling, e.g., in the form of sampling biases [see @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [see, e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped.<!--Close footnote-->]
-So, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set $S$ of stochastic processes
+Now, more formally, let the sample of a prospect be a set of realizations of the respective random variable according to its distribution $P_X$.
+That is, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set $S$ of stochastic processes
 $$
@@
 $$
-with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the length of the respective sequence.
-The realizations that result from each stochastic process $s \in S$ may then be integrated into a sample of $N$ experienced outcomes or into multiple smaller samples.
-The samples may then be used to make an uncertain inference about the latent prospects in (7), the sets of outcome-probability pairs respectively.
+with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the length of the respective sequence [but see, e.g., @plonskyRelianceSmallSamples2015, where the i.i.d.-assumption is dropped].
+So, given a stochastic process $s \in S$, the obtained realizations---i.e., the experienced outcomes---may be sequentially integrated into a sample of size $N$ or into multiple smaller samples.
+Then, the samples so obtained can serve probabilistic inferences about the properties of the latent prospects in (7), the sets of outcome-probability pairs respectively.
 
-Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply to DfE and it follows that the accuracy of an inference from a sample about the properties of a latent prospect depends, ceteris paribus, on the size of the sample.
-In fact, one explanation for the as-if underweighting of rare outcomes in DfE and the description-experience gap outlined in the introduction is that people rely on too small samples, which, due to the skewness of the binomial distribution, cause the relative frequencies with which rare outcomes occur in a sample to be smaller than their objective probabilities [@hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; see also @hertwigDecisionsExperienceWhy2010].
+Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply to DfE and it follows that the accuracy of inferences from samples to latent prospects depend, ceteris paribus, on the size of the samples.
+In fact, one explanation for the as-if underweighting of rare outcomes in DfE and the description-experience gap outlined in the introduction is that people rely on too small samples, which, due to the skewness of the binomial distribution, cause the relative frequencies with which rare outcomes occur in the samples to be smaller than their objective probabilities [@hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; see also @hertwigDecisionsExperienceWhy2010].
 The invoked argument is then that what may appear as if people were underweighting rare outcomes relative to what would be warranted on the basis of their objective probabilities---following the principle of mathematical expectation---may in fact be consistent with an as-if overweighting relative to what would be warranted on the basis of the experienced relative frequencies [@foxDecisionsExperienceSampling2006].
@@
 ```{r w-shapes, fig.cap="(ref:weighting)"}
-wf <- tibble(gamma = seq(.1, 2, .1)) %>%
-  expand_grid(delta = c(.1, .5, 1, 2, 5, 10),
-              prob = seq(0, 1, .01)) %>%
-  mutate(w = (delta*(prob^gamma))/((delta*prob^gamma)+(1-prob)^gamma))
 
-ggplot(wf) +
-  geom_line(aes(prob, w, group = gamma, color = gamma)) +
-  geom_segment(x = 0, xend = 1, y =  0, yend = 1, linetype = "dashed", size = .2, color = "gray") +
-  scale_color_scico(palette = "cork") + 
+# prepare vector with cumulative probabilities
+p <- tibble(p = seq(0, 1, .01))
+
+# compute weighting function for different combinations of gamma and delta 
+wf <- p %>% expand_grid(gamma = seq(.1, 2, .1), 
+                        delta = c(.1, .5, 1, 2, 5, 10)) %>%
+  mutate(wp = (delta*(p^gamma))/((delta*p^gamma)+(1-p)^gamma))
+
+# labeller function for LaTeX math expressions in facet labels 
+labeller_delta <- function(string) {
+  TeX(paste("$\\delta=$", string, sep = ""))  
+}
+
+# plot
+ggplot(wf, aes(p, wp, group = gamma)) +
+  facet_wrap(~delta, labeller = as_labeller(labeller_delta, default = label_parsed)) + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +
   scale_y_continuous(breaks = seq(0, 1, .2)) + 
-  labs(x = "p",
-       y = "w(p)", 
+  labs(x = expression(p),
+       y = expression(w(p)), 
        color = expression(gamma)) + 
-  facet_wrap(. ~ delta, labeller = label_bquote(cols = delta: .(delta))) + 
-  theme_minimal()
+  theme_apa() + 
+  geom_line(aes(color = gamma)) +
+  scale_color_scico(palette = "berlin") + 
+  geom_abline(intercept = 0, slope = 1, color = "gray", linetype = "dashed", size = 1) # identity line
 ```
@@
 Now, both deviations from $\gamma = 1$ and $\delta = 1$ produce a nonlinear graphical shape.
-That is, for $\gamma > 1$ (green graphs), the graphs take a S-shape---running below (above) the identity line for small (large) cumulative probabilities---which is more accentuated for larger deviations from $\gamma = 1$.
+That is, for $\gamma > 1$, the graphs take a S-shape---running below (above) the identity line for small (large) cumulative probabilities---which is more accentuated for larger deviations from $\gamma = 1$.
 Importantly, the same *small* numerical difference between two cumulative probabilities $p$ then translates to varying differences between the respective images $w(p)$ depending on the interval on the cumulative probability scale.
@@
 More so, the fact that CPT may weigh outcomes of the same small probability differently, adds another reasons why the description-experience gap should not be equated with a reversed weighting pattern in CPT [see @hertwigConstructBehaviorGap2018].
-I.e., neither could the gap then be interpreted in terms of an as-if underweighting (overweighting) of rare outcomes in DfE (DfD), nor would any of the potential contributors to the gap considered so far [see, e.g., @hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than others.<!--Close footnote-->]
-Note that for all $\gamma < 1$ (blue graphs) the graph of $w$ takes an inverse S-shape and the entire weighting pattern is reversed.
+I.e., neither could the gap then be interpreted in terms of an as-if underweighting (overweighting) of rare outcomes in DfE (DfD), nor would any of the potential contributors to the gap considered so far [see, e.g., @hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than other small-probability outcomes.<!--Close footnote-->]
+Note that for all $\gamma < 1$ the graph of $w$ takes an inverse S-shape and the entire weighting pattern is reversed.
 Moreover, the shape of the weighting function, and thus the weighting pattern, depends strongly on $\delta$, which affects the overall elevation of the graph.
@@
 
+```{r}
+cols <- list(.default = col_double(),
+             boundary = col_factor(),
+             gamble = col_factor(),
+             rare = col_factor(),
+             agent = col_factor(),
+             choice = col_factor())
+choices_p <- read_csv("data/choices/choices.csv", col_types = cols) # piecewise integration
+
+# Choices
+
+# determine normative choice objective and experienced
+fr_rates_p <- choices_p %>%
+  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B"), # normative choice objective EV
+         ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2),
+         norm_exp = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) # normative choice experienced EV / mean
+
+# objective
+fr_rates_p_o <- fr_rates_p %>%
+  filter(!is.na(norm)) %>%
+  group_by(s, boundary, a, rare, norm, choice) %>%
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), # false response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", norm == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>% # remove correct responses
+  select(-c(norm, n)) %>% 
+  mutate(norm = "Latent")
+
+# experienced
+fr_rates_p_e <- fr_rates_p %>%
+  filter(!is.na(norm_exp)) %>%
+  group_by(s, boundary, a, rare, norm_exp, choice) %>%
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), # false response rates
+         type = case_when(norm_exp == "A" & choice == "B" ~ "Safe", norm_exp == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>%  # remove correct responses
+  select(-c(norm_exp, n)) %>% 
+  mutate(norm = "Sample")
+
+# merge data frame
+fr_rates_p <- bind_rows(fr_rates_p_o, fr_rates_p_e) %>% 
+  mutate(rare = case_when(rare == "none" ~ "Middle",
+                          rare == "attractive" ~ "High", 
+                          rare == "unattractive" ~ "Low"))
+
+labeller_a <- function(string) {
+  TeX(paste("$\\a=$", string, sep = ""))  
+}
+
+fr_rates_p %>% 
+  ggplot(aes(s, rate)) +
+  geom_point(aes(color = norm, shape = type)) +
+  facet_grid(rare~a, labeller = labeller(rare = label_value, a = as_labeller(labeller_a, default = label_parsed))) + 
+  scale_color_scico_d(palette = "berlin")+ 
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, .5, 1)) + 
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, .5, 1)) +
+  labs(x = "s",
+       y = "False Response Rate", 
+       color = "Normative\nEV",
+       shape = "False\nResponse") +
+  theme_apa()
+```
+
 <!-- Test set-->
@@
   geom_path(data = trial_length_s, aes(color = s)) +
-  scale_color_scico(palette = "buda") + 
+  scale_color_scico(palette = "acton") + 
   scale_x_continuous(breaks = seq(0, 1, .1)) + 
@@
 cpt_long %>% 
-  filter(parameter == "gamma") %>% 
+  filter(parameter == "delta", a!= 1) %>% 
   ggplot(aes(x=s, y = mean, color = s)) +

### 2022-02-26 manuscript.Rmd
Update Results

@@
                viridis,
-               scico,
+               ggpubr,
                latex2exp)
@@
 
-```{r w-shapes, fig.cap="(ref:weighting)"}
+```{r w-shapes, fig.cap="(ref:weighting)", fig.height=7, fig.width=10}
 
@@
   geom_line(aes(color = gamma)) +
-  scale_color_scico(palette = "berlin") + 
-  geom_abline(intercept = 0, slope = 1, color = "gray", linetype = "dashed", size = 1) # identity line
+  scale_color_viridis(option = "plasma") + 
+  geom_abline(intercept = 0, slope = 1, color = "gray", linetype = "dashed") # identity line
 ```
@@
 
-```{r}
+(ref:fr-rates-p) Effect of Switching Probability on Rates of False Risky and False Safe Choices for 2-Outcome Prospects with High Rank Outcomes of Different Probability
+
+```{r fig.cap="(ref:fr-rates-p)", fig.height=7, fig.width=10}
 cols <- list(.default = col_double(),
@@
 
-# Choices
+# false response (fr) rates
 
-# determine normative choice objective and experienced
+## determine normative choice according to latent and sampled EV
 fr_rates_p <- choices_p %>%
-  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B"), # normative choice objective EV
+  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B"), # normative choice latent EV
          ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2),
-         norm_exp = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) # normative choice experienced EV / mean
+         norm_exp = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) # normative choice sampled EV
 
-# objective
+# fr rates latent EV
 fr_rates_p_o <- fr_rates_p %>%
-  filter(!is.na(norm)) %>%
-  group_by(s, boundary, a, rare, norm, choice) %>%
-  summarise(n = n()) %>%
-  mutate(rate = round(n/sum(n), 2), # false response rates
-         type = case_when(norm == "A" & choice == "B" ~ "Safe", norm == "B" & choice == "A" ~ "Risky")) %>%
+  filter(!is.na(norm)) %>% # exclude choices under EV equality
+  group_by(s, boundary, a, rare, norm, choice) %>% # to distinguish type of rare event and type of false response
+  summarise(n = n()) %>% # determine absolute number of responses per category
+  mutate(rate = round(n/sum(n), 2), # determine correct and false response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", norm == "B" & choice == "A" ~ "Risky")) %>% # type false response
   ungroup() %>%
-  filter(!is.na(type)) %>% # remove correct responses
-  select(-c(norm, n)) %>% 
-  mutate(norm = "Latent")
+  filter(!is.na(type)) %>% # remove correct response rates
+  select(-c(norm, choice, n)) %>%
+  mutate(norm_ev = "Latent")
 
-# experienced
+# fr rates sampled EV
 fr_rates_p_e <- fr_rates_p %>%
@@
   summarise(n = n()) %>%
-  mutate(rate = round(n/sum(n), 2), # false response rates
+  mutate(rate = round(n/sum(n), 2),
          type = case_when(norm_exp == "A" & choice == "B" ~ "Safe", norm_exp == "B" & choice == "A" ~ "Risky")) %>%
   ungroup() %>%
-  filter(!is.na(type)) %>%  # remove correct responses
-  select(-c(norm_exp, n)) %>% 
-  mutate(norm = "Sample")
+  filter(!is.na(type)) %>%
+  select(-c(norm_exp, choice, n)) %>%
+  mutate(norm_ev = "Sample")
 
@@
 fr_rates_p <- bind_rows(fr_rates_p_o, fr_rates_p_e) %>%
-  mutate(rare = case_when(rare == "none" ~ "Middle",
-                          rare == "attractive" ~ "High", 
-                          rare == "unattractive" ~ "Low"))
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]",
+                          rare == "attractive" ~ "\\in (0,.2)",
+                          rare == "unattractive" ~ "\\in (.8,1)")) # Change fact labels
 
+# labeller function for LaTeX math expressions in facet labels
 labeller_a <- function(string) {
@@
 
-fr_rates_p %>% 
-  ggplot(aes(s, rate)) +
-  geom_point(aes(color = norm, shape = type)) +
-  facet_grid(rare~a, labeller = labeller(rare = label_value, a = as_labeller(labeller_a, default = label_parsed))) + 
-  scale_color_scico_d(palette = "berlin")+ 
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, .5, 1)) + 
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, .5, 1)) +
+labeller_rare <- function(string) {
+  TeX(paste("$\\p_{High}$", string, sep = ""))
+}
+
+ggplot(fr_rates_p, aes(s, rate)) +
+  facet_grid(rare~a, labeller = labeller(rare = as_labeller(labeller_rare, default = label_parsed), a = as_labeller(labeller_a, default = label_parsed))) +
   labs(x = "s",
@@
        shape = "False\nResponse") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  labs(x = "Switching Probability",
+       y = "False Response Rate",
+       color = "Normative\nExpected\nValue",
+       shape = "False\nResponse\nType") +
+  geom_point(aes(color = norm_ev, shape = type)) +
+  scale_shape_manual(values = c(4, 16)) +
+  scale_color_viridis_d(option = "plasma", end = .7) +
   theme_apa()
@@
 
-<!-- Results -->
+(ref:weighting-parameters) Parameter Estimates of the Weighting Function of @goldsteinExpressionTheoryPreference1987 for Different Simulation Parameters
 
-...
+```{r fig.cap="(ref:weighting-parameters)", fig.height=7, fig.width=10}
+
+# load data
+
+cols <- list(.default = col_double(),
+             boundary = col_factor(),
+             a = col_factor(),
+             parameter = col_factor())
+cpt_p <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols) # piecewise integration
+cpt_p <- cpt_p %>% mutate(boundary = if_else(boundary == "absolute", "Absolute", "Relative"))
+
+gamma <- cpt_p %>%
+  filter(parameter == "gamma") %>% 
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_color_viridis(option = "plasma") +
+  scale_shape_manual(values = c(4, 16)) +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+  labs(x = "Switching Probability",
+       y = expression(gamma),
+       color = "Switching\nProbability",
+       shape = "Boundary") +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(labeller_a, default = label_parsed))) + 
+  theme_apa() + 
+  theme(axis.title.x = element_blank())
+
+delta <- cpt_p %>%
+  filter(parameter == "delta") %>% 
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_color_viridis(option = "plasma") +
+  scale_shape_manual(values = c(4, 16)) +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+  facet_wrap(~a, nrow = 1) + 
+  labs(x = "Switching Probability",
+       y = expression(delta),
+       color = "Switching\nProbability",
+       shape = "Boundary") +
+  theme_apa() + 
+  theme(strip.text.x = element_blank())
+
+ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
+```
+
+(ref:value-choice-parameters) Parameter Estimates of the Value Function of @tverskyAdvancesProspectTheory1992 and of the Logit Choice Rule for Different Simulation Parameters
+
+```{r fig.cap="(ref:value-choice-parameters)", fig.height=7, fig.width=10}
+
+alpha <- cpt_p %>%
+  filter(parameter == "alpha") %>% 
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_color_viridis(option = "plasma") +
+  scale_shape_manual(values = c(4, 16)) +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+  labs(x = "Switching Probability",
+       y = expression(alpha),
+       color = "Switching\nProbability",
+       shape = "Boundary") +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(labeller_a, default = label_parsed))) + 
+  theme_apa() + 
+  theme(axis.title.x = element_blank())
+
+rho <- cpt_p %>%
+  filter(parameter == "rho") %>% 
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_color_viridis(option = "plasma") +
+  scale_shape_manual(values = c(4, 16)) +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1,.5)) +
+  labs(x = "Switching Probability",
+       y = expression(rho),
+       color = "Switching\nProbability",
+       shape = "Boundary") +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(labeller_a, default = label_parsed))) + 
+  theme_apa() + 
+  theme(strip.text.x = element_blank())
+
+ggarrange(alpha, rho, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
+```
+
+(ref:shapes) Estimated Graphical Shapes of the Weighting and Value Function for Different Simulation Parameters
+
+```{r fig.cap="(ref:shapes)", fig.height=7, fig.width=10}
+
+## weighting function
+
+wf_p <- cpt_p %>%
+  select(s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
+  select(-c(alpha, rho)) %>%
+  expand_grid(p = seq(0, 1, .05)) %>%
+  mutate(w = round(  (delta * p^gamma)/ ((delta * p^gamma)+(1-p)^gamma), 2))
+
+wf_p_a <- wf_p %>%
+  filter(boundary == "Absolute")
+wf_p_r <- wf_p %>%
+  filter(boundary == "Relative")
+weight <- ggplot(wf_p_a, aes(x = p, y = w, group = s, color = s)) +
+  geom_line(size = .5) +
+  geom_line(data = wf_p_r, size = .5) + 
+  scale_color_viridis(option = "plasma") +
+  scale_x_continuous(breaks = seq(0, 1, .5)) +
+  scale_y_continuous(breaks = seq(0, 1, .5)) +
+  labs(x = "Experienced Probability",
+       y = "Decision Weight",
+       color = "Switching\nProbability") +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(labeller_a, default = label_parsed))) + 
+  theme_apa() + 
+  theme(strip.text.x = element_blank())
+
+vf_p <- cpt_p %>%
+  select(s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
+  select(-c(gamma, delta, rho)) %>%
+  expand_grid(x = seq(0, 20, .5)) %>%  
+  mutate(v = round(x^alpha, 2))
+
+vf_p_a <- vf_p %>%
+  filter(boundary == "Absolute")
+vf_p_r <- vf_p %>%
+  filter(boundary == "Relative")
+value <- ggplot(vf_p_a, aes(x = x, y = v, group = s, color = s)) +
+  geom_line(size = .5) +
+  geom_line(data = vf_p_r, size = .5) + 
+  scale_color_viridis(option = "plasma") +
+  scale_x_continuous(breaks = seq(0, 20, 10)) +
+  scale_y_continuous(breaks = seq(0, 20, 10)) +
+  labs(x = "Objective Outcome",
+       y = "Subjective Value",
+       color="Switching\nProbability") +
+  facet_wrap(~a, nrow = 1)+ 
+  theme_apa() + 
+  theme(strip.text.x = element_blank())
+
+ggarrange(weight, value, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
+```
 

### 2022-03-02 manuscript.Rmd
Prelimary Draft Intro, Sec 1 & 2

@@
 
-The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the *properties* of the choice alternatives between which people can choose.
-In fact, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives to return a subset thereof as outputs [@heOntologyDecisionModels2020].
-
-Now, more formally, let us treat the choice alternatives as elements $c$ of the set $C$.
-To each $c \in C$ is then assigned some information from the inputs and this information may be used by the mind to learn about the properties of the respective alternative.
-Accordingly, decision making can be considered an information-processing problem which starts from the set $C$, containing all choice alternatives, and stops at a proper subset $C' \subset C$ with the inclusion map
+The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the choice alternatives between which people can choose.
+In fact, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and returns a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
+Let us therefore treat the choice alternatives as elements $c$ of the set $C$, and decision making as an information-processing problem starting from $C$ and stopping at a proper subset $C' \subset C$ with the inclusion map
 $$
@@
 $$
-[@jostMathematicalConcepts2015, p. 15], containing only the chosen alternatives.
-
-Importantly, the information that is provided about the choice alternatives can come in many forms.
-For example, in *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all relevant properties of the choice alternatives.
-Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], the properties of the choice alternatives are latent---i.e., not described---and therefore not known with certainty, but they must be inferred from the consequences (hereafter: outcomes) that occurred when the alternatives were chosen in similar past decisions.
-Although these distinct input forms may in principle carry the same information about a given set of choice alternatives, behavioral decision research has so far produced a large body of papers indicating that---if a quite general perspective is taken---there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
-In one reading of the gap, empirical choice patterns indicate that in DfD people choose as if a rare outcome is given more weight in the evaluation of a choice alternative than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose as if the same rare outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
-Hereafter, these choice patterns are referred to as the as-if overweighting and underweighting of rare outcomes, respectively.
-
-This paper uses the as-if underweighting of rare outcomes as a starting point for an inquiry into the sampling process upfront choices in DfE.
-Essentially, it discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into *samples* (hereafter: sampling strategies) can produce distinct choice patterns in DfE---among them, the as-if underweighting of rare outcomes [see @hillsInformationSearchDecisions2010, for the original formulation of this claim].
-
-The rest of the paper is therefore structured as follows.
-In the first brief section, a formal definition of DfE is provided.
-In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices in DfE in terms of deviations from the principle of mathematical expectation.
-In the section that follows, sampling strategies are treated.
-<!-- Outline of the section -->
-Thereafter, a simulation is presented in which the theoretical claims that are made in the preceding section are implemented in a computational model to simulate choice data in DfE.
-The predictions of the model are summarized and fitted in CPT.
+[cf. @jostMathematicalConcepts2015, p. 15].
+
+Now, let a *prospect* be a choice alternative that possesses only two kinds of properties: the possible outcomes of the alternative and the probabilities with which these outcomes occur following its choice.
+Importantly, the information that inputs provide about the properties of a prospect can come in different forms.
+For example, in *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
+Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in past decisions.
+The inputs to DfE therefore take the form of samples.
+Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
+In one reading of the gap, empirical choice patterns indicate that in DfD people choose as if a small-probability outcome is given more weight in the evaluation of a prospect than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+Hereafter, these choice patterns are referred to as the *as-if overweighting* and *as-if underweighting of rare outcomes*, respectively.
+
+Similar to other behavioral phenomena that can be explained by the mind being sensitive to the composition of the samples on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE can be explained by the tendency to rely on small samples [see, e.g., @hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+That is, following from the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequency with which a prospect's outcome occurs in a sample of infinite size converges almost surely to its objective probability.
+In such a case, but also in the less strict case of large samples, then, the binomial distribution of each prospect's outcome can be approximated by a symmetric normal distribution [see @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
+However, for small samples, the binomial distribution of small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
+Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
+As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities---without correction of sampling error---and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
+Since the same line of reasoning applies would the mind approximate the principle of mathematical expectation by choosing the prospect that produced the greater sample mean, the following discussion focuses on choices in DfE that are based on comparisons of sampled means.
+The relevance of making the inference about latent properties explicit, however, is addressed in the last section of this paper.
+
+Now, this paper uses the outlined effect of small samples as a starting point for an inquiry into the sampling process upfront choices in DfE.
+Specifically, in one paradigm used to study DfE, i.e., the sampling paradigm [see @weberPredictingRiskSensitivity2004], before making a single choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
+Considering this paradigm, the current paper discusses how different strategies of sampling and integrating the prospects' outcomes (hereafter: *sampling strategies*) can produce distinct choice patterns in DfE by altering the number and size of the samples that are used by the mind to accumulate evidence over time [see @hillsInformationSearchDecisions2010, for the original formulation of this claim].
+The paper proceeds as follows:
+In the first section, a formal definition of DfE is provided.
+In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices between prospects in terms of deviations from the principle of mathematical expectation.
+In the section that follows, using an evidence accumulation approach, different sampling strategies are discussed, how they produce distinct choice patterns in DfE, and how these patterns may be captured in the parameters of CPT.
+Thereafter, a simulation is presented in which these sampling strategies are implemented in a computational model to simulate choices between a safe and a two-outcome prospect.
+By proposing distinct links between the parameter capturing different sampling strategies, the resulting choices, and the estimated CPT parameters, the simulation substantiates the core claim of this paper, namely, that sampling effects on choices in DfE may not be reduced to the overall number of sampled outcomes.
+That is, the simulation demonstrates how the overall number of sampled outcomes can increase without the underweighting of rare outcomes fading, assuming that the sampling strategy translates this increase in overall number into a greater number of samples over which evidence is accumulated, but not samples of greater size.
+The last section supplements the rather technical inquiry into the sampling process and its consequences with a theoretical inroad into the question how the idea of sampling strategies can be integrated into the broader study of the computationally limited mind as an adaptive cognitive system.
 The paper closes with a summary and a conclusion.
@@
 
-Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].
-These fundamental properties are considered the possible outcomes of a choice alternative (hereafter: $x_i$) and the probabilities with which these outcomes occur following the choice of the alternative (hereafter: $p_X(x_i)$).
-Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs $(x_i, p_X(x_i))$ are prospects (or: gambles), which are exclusively considered below.
-
-Now, more formally, let the axiomatic definition of a prospect be that of a discrete random variable's distribution.
+To begin with, let the axiomatic definition of a prospect be that of a discrete random variable's distribution [see @tverskyAdvancesProspectTheory1992].
 Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space. 
-Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ is the sample space containing a finite set of elements, one of which results from choosing the respective prospect:
+Following the @kolmogorovFoundationsTheoryProbability1950 axioms and the notation of @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, $\Omega$ is the sample space containing a finite set of elements, one of which results from choosing the respective prospect:
 $$
@@
 $$ 
-$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$ with each element $A \in P(\Omega) = \mathcal{F}$ being a subset of $\Omega$.^[<!--Open footnote-->Note that this paper considers only the case of finite sample spaces.
+$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$, where each element $A \in \mathcal{P}(\Omega) = \mathcal{F}$ is a subset of $\Omega$.^[<!--Open footnote-->Note that this paper considers only the case of finite sample spaces.
 The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
@@
 which assigns each subset $A \in \mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.<!--^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \to [0,1]$, which is used to construct the probability measures $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$.]-->
-The random variable $X$ is the measurable function
+According to Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, p.
+21-22],^[<!--Open footnote-->See also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive yet accessible introduction to random variables.<!--Close footnote-->]
+the random variable $X$ is the measure
 $$
@@
 where $(\Omega', \mathcal{F'})$ is a measurable space with each element $x \in \Omega'$ being a possible outcome of a prospect and each element $A' \in \mathcal{F'}$ being a subset of $\Omega'$.
-An outcome's probability $p_X(x)$ is then provided by the probability measure
+An outcome's probability $p_X(x)$ is then provided by the pushforward probability measure
 $$
@@
 P_X(A' \in \mathcal{F'}) := P(X^{-1} \ A') = P(\{\omega: X(\omega) = x \in A'\})
+\; .
 \tag{6}
 $$
-[see @kolmogorovFoundationsTheoryProbability1950, p.
-21-22].^[<!--Open footnote-->See also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive yet accessible introduction to random variables.<!--Close footnote-->]
-That is, the set consisting of a single outcome $x$ is a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(X(\omega) = x)$.
+That is, the set consisting of a single outcome $x$ is a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(\{\omega : X(\omega) = x \in \{x\}\})$.
 Note that the probability measure in (5) and (6), respectively, is a discrete random variable's distribution and therefore a prospect.
@@
 
-However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes-probability pairs.
-In such cases, people would make DfD, since the information from which the mind learns about the prospects are complete descriptions thereof.
-Yet, rather often, people make DfE, where the mind can learn about the latent prospects only from a record of past experiences with them.
-That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is a rough description of a sample.
-The mind may then infer from the relative frequency with which an outcome occurred in such a sample of past decisions its probability of occurrence following a future decision.
-
-Now, more formally, let the sample of a prospect be a set of realizations of the respective random variable according to its distribution $P_X$.
-That is, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set $S$ of stochastic processes
-$$
-S = \{X_{1t}, ... , X_{kt}\}
+However, only occasionally in peoples' daily life, inputs take the form of explicit descriptions of all outcome-probability pairs.
+In such cases, people would make DfD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
+Yet, rather often, people make DfE, where the mind can learn about the latent properties of prospects only by experiental sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
+Accordingly, considering the sampling paradigm,^[<!--Open footnote-->Note that it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+660].
+See, e.g., @plonskyRelianceSmallSamples2015, who drop the i.i.d.-assumption for DfE.<!--Close footnote-->]
+let a sample of a prospect be a set of realizations of the respective random variable.
+More specifically, for the choice between $1, ..., k$ prospects, the inputs to DfE---i.e., the sampled outcomes---are generated by a set $S$ of prospect-specific discrete-time stochastic processes
+$$
+S = \{\{X_{1t}\}, ... , \{X_{kt}\}\}
+\; ,
 \tag{8}
 $$
-with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the length of the respective sequence [but see, e.g., @plonskyRelianceSmallSamples2015, where the i.i.d.-assumption is dropped].
-So, given a stochastic process $s \in S$, the obtained realizations---i.e., the experienced outcomes---may be sequentially integrated into a sample of size $N$ or into multiple smaller samples.
-Then, the samples so obtained can serve probabilistic inferences about the properties of the latent prospects in (7), the sets of outcome-probability pairs respectively.
-
-Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply to DfE and it follows that the accuracy of inferences from samples to latent prospects depend, ceteris paribus, on the size of the samples.
-In fact, one explanation for the as-if underweighting of rare outcomes in DfE and the description-experience gap outlined in the introduction is that people rely on too small samples, which, due to the skewness of the binomial distribution, cause the relative frequencies with which rare outcomes occur in the samples to be smaller than their objective probabilities [@hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; see also @hertwigDecisionsExperienceWhy2010].
-The invoked argument is then that what may appear as if people were underweighting rare outcomes relative to what would be warranted on the basis of their objective probabilities---following the principle of mathematical expectation---may in fact be consistent with an as-if overweighting relative to what would be warranted on the basis of the experienced relative frequencies [@foxDecisionsExperienceSampling2006].
-Yet, it seems that the small size of samples in DfE provides just one and only a partial explanation for the description-experience gap [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
-More so, despite the LLN, the gap need not narrow at all, even for ever increasing sample sizes that are fully taken into account.
-Particularly, this paper discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into samples interact with the LLN to produce distinct choice patterns in DfE---including the as-if underweighting of rare outcomes---that tend to stabilize as the sample size increases.
+where each $s \in S$ is a sequence of independent and identically distributed (i.i.d.) random variables, each $t \in \{t_1, ..., t_N\}$ corresponds to the position of the respective random variable in such a sequence, and $N$ denotes the length of the respective sequence, which corresponds to the overall number of sampled outcomes for this prospect.
+Now, one core assumption of this paper is that, for a stochastic process $s \in S$ of length $N$, the mind sequentially integrates the sampled outcomes into either one enumerated sample growing to the size $N$ or into multiple smaller enumerated samples, each corresponding to a unique sub-sequence of s.
+Assuming that the mind uses all samples so obtained during a process of evidence accumulation, this paper discusses and demonstrates how different sampling strategies that alter the number and size of these samples can produce distinct choice patterns in DfE.
 Before so doing, however, the following section reviews how CPT can be used as a data model that captures systematic deviations from the principle of mathematical expectation in the parameter estimates of a *value* and a *weighting function*.
@@
 
-<!-- Old
-
-Given that the choice is perfectly systematic---as opposed to random or noisy---the chosen alternatives in $I'$ should share some property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
-In the following, I will refer to statements about properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
-
-Often, however, the properties used by the mind to make a choice are not readily described and cannot be directly evaluated [cf.
-@brunswikRepresentativeDesignProbabilistic1955; see @brunswikPerceptionRepresentativeDesign1956, for a detailed treatment]; rather, proper descriptions must be inferred from whatever information the inputs provide about the properties of choice alternatives, using transformation rules, statistical generalizations, or both.
-Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982; see also, e.g., @gigerenzerHowImproveBayesian1995; @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
-Hence, to explain how the mind makes a selection among choice alternatives, one needs to understand the output controlling properties, i.e., the applied selection criteria, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
-The process is sketched in Figure 1.
-
-(ref:figure1) A rough computational level sketch of decision making as an information processing problem.
-To make a selection among choice alternatives on the basis of particular selection criteria, the mind requires explicit descriptions of the relevant properties before they can be evaluated.
-Descriptions are either readily available or must be inferred from the inputs.
-
-```{r fig.cap= "(ref:figure1)"}
-knitr::include_graphics("images/dm-sketch.png")
-```
-
-In what follows, the paper elaborates on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate a rather important principle:
-Given that the mind is indeed sensitive to variations in the property values, the more accurately their descriptions are inferred, the more systematic the choices should become.
-Importantly, this principle is not restricted to any one specific property. 
-Rather, each selection criterion or combination thereof imposes constraints on the assessment of choice alternatives, leading to characteristic choice patterns that are eventually blurred by inaccurate property descriptions.
-
-For the sake of example, I argue that a choice pattern robustly emerging in *decisions from experience* (DfE), the apparent underweighting of small probability events [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; see also @wulffMetaanalyticReviewTwo2018, for a meta-analytic review], may be caused by the assessment constraints associated with a round-wise decision strategy.
-This particular claim has already been made by @hillsInformationSearchDecisions2010 and follows quite directly from probability theory.
-However, the current paper suggests to subordinate decision strategies to the adoption of selection criteria and addresses in some detail two "problems" in the context of DfE, in which descriptions of the properties of choice alternatives must be inferred from sampling data.
-
-For one, there is an *induction problem*, well known from inferential statistics, according to which the sample size determines the margin of error within which any true property of a choice alternative can be inferred, given an otherwise perfect inference process.
-Yet, it follows that if an underweighting pattern is caused by the adoption of an arbitrary selection criterion, it is *a priori* predicted to become more stable with increasing sample size. 
-This prediction is in line with the principle already stated above, i.e., that selection-criteria-induced choice patterns should become more systematic as property descriptions become more accurate.
-Nevertheless, the prediction contrasts the explanation that underweighting is caused by the reliance on small samples [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @rakowBiasedSamplesNot2008], highlighting that outside of the *statistical* models used to describe the choice data, *causal* decision making models of quite different nature may be at play, and that a rather important difference between these causal models resides in the selection criteria they incorporate.
-I will elaborate on this matter as I proceed, however, to be clear from the outset, what the mind does in neither case is performing a probability weighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [cf., e.g., @griffithsRationalUseCognitive2015].
-
-For another, this paper approaches the problem of organizing the sampling data in such a way that it allows chains of inferences connecting the input set $I$ with the output set $I' \subset I$ that are algorithmically short and simple enough to be carried out by minds whose cognitive capacities are bounded [cf.
-@simonInvariantsHumanBehavior1990; @simonBehavioralModelRational1955].
-This may be considered a *representation problem* since the inference chains are constructed around explicit descriptions of the properties of choice alternatives and representations are the "formal schemes" of symbols and rules with which these descriptions are derived [@marrRepresentationRecognitionSpatial1978, p.
-270].
-Specifically, representations differ in how they organize the information used to infer the descriptions of certain properties and these organizations determine the algorithms that can be built into the inference chain [@marrVisionComputationalInvestigation1982].
-In this paper, *sampling strategies* in DfE are considered as representation systems used to organize the samples in a way that subserves the property inferences required by the application of particular selection criteria.
-Though most of my expositions on the role of sampling strategies remain speculative, the core idea is not new to decision research [see, e.g., @hillsInformationSearchDecisions2010; @wulffHowShortLongrun2015].
-By restating this idea and adopting some terms and concepts that have well defined meaning in math and cognitive science, I hope to integrate it into the rich study of the computationally limited mind as an adaptive cognitive system whose processes interact with the information structures in the environment or memory.
-
-The theoretical arguments sketched in this introduction are substantiated by a simulation study. 
-For this purpose, the sampling and decision making processes are implemented in a computational model to simulate choice data from DfE.
-The simulated data is modeled in cumulative prospect theory (CPT), a data model commonly used for describing decisions under risk and uncertainty [@goldsteinExpressionTheoryPreference1987; see also @tverskyAdvancesProspectTheory1992].
-All simulations and analyses are reproducible---materials and instructions can be found on the GitHub repository.
-
-# Inputs to the Decision Making Process and Property Descriptions
-
-By defining decision making as an information processing problem whose solution requires a selection among choice alternatives of the form described in (1), much weight is given to the properties of choice alternatives---whatever those may be for the moment---since it is only through them that any necessary distinction between the alternatives or collections thereof can be made.
-To stress this point, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).
-
-(ref:figure2) A.
-The power set of the set $I$ including the choice alternatives A, B, and C.
-Black (white) circles indicate that an alternative does (not) possess a property.
-Each column displays a possible subset that could result from assessing whether the alternatives posses a relevant property.
-The properties determine the various relations among the choice alternatives.
-Note that properties resulting in the empty set $\{\}$ and the subset $\{A,B,C\}$ do not discriminate between choice alternatives.
-B.
-A Venn diagram visualizing the inclusion map $\iota : I' \mapsto I$.
-$\iota$ maps every element $i$ of the subset $I'$ to its image $i$, treated as element of the superset $I$.
-
-```{r fig.cap= "(ref:figure2)"}
-knitr::include_graphics("images/power-set.png")
-```
-
-Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that could result from assessing for each alternative whether it possesses an arbitrary property (collection) or not [cf.
-@jostMathematicalConcepts2015, p.
-16].
-The concept of the power set thereby illustrates how different selection criteria can alter the consequential choice.
-That is, in rather abstract terms, selection criteria are statements regarding the properties of choice alternatives that the mind evaluates as either true or false during the decision making process; accordingly, the subset $I'$ only contains the alternatives for which the statement is evaluated to be true.
-It follows that if there is some variance in the properties across choice alternatives and the properties are not perfectly correlated, changing the selection criteria can eventually change the subset $I'$.
-
-## What Are the Choice Alternatives and Their Properties?
-
-Given (3), it is evident that the prospects can only be distinguished by the elements of their tuples. 
-These elements are, generally speaking, symbols, some of which describe properties on their own, e.g., the outcome $\omega$, whereas other properties can only be described by collections of symbols, e.g., the sample space $\Omega$ by a set of outcomes as in (2.1), or more complex combinations thereof, e.g., the weighted average which is obtained by first multiplying all outcomes in $\Omega$ by their respective probabilities in $P$ and then summing the resulting products.^[I do not refer to this quantity as expected value, since the term is reserved for random variables, which were not introduced so far.]
-In turn, for choices between prospects, selection criteria are statements about the elements of their tuples that are true or false and these statements imply relations among prospects that are at least nominal, but may also draw on other levels of measurement.
-
-## Inferring Property Descriptions from Sampling Data
-
-Note that a selection criterion may refer to a property for which the raw input, i.e., the symbols, their organization, and the information they encode, do not yet provide an explicit description.
-Even more so, it has been repeatedly stated that for quite many decisions the mind faces, it is simply not possible to draw on direct descriptions of the properties, since they are part of the distal environment  [e.g., @brunswikOrganismicAchievementEnvironmental1943; @fiedlerExplainingSimulatingJudgment1996; @hertwigDescriptionexperienceGapRisky2009; see also @brunswikRepresentativeDesignProbabilistic1955; @brunswikPerceptionRepresentativeDesign1956; @kozyrevaInterpretationUncertaintyEcological2021].
-In either case, some form of description must be inferred from whatever information the input provides about the property in question.
-Consider first the counterfactual case of the prospect whose tuple is not part of the distal environment but is directly described. 
-Since all information about the prospect is given, one may in principle consider the input complete, yet, 
-the tuple implies properties of the prospect which are not explicitly described.
-For example, to obtain the description of the prospect's weighted average, still a calculus according to the algebraic rules described in the preceding paragraph must be carried out. 
-In general, in cases like the one just considered, where the properties are not distal and all information about them is available, property inferences take the form of a mere transformation, where the symbols from the input are ordered and combined according to some transformation rules [cf.
-@marrVisionComputationalInvestigation1982, p.
-20].
-
-In natural world decisions, however, the properties of choice alternatives are often distal and amenable only through their probabilistic relation to proximal cues or samples, which provide the input to the decision making process [cf.
-@brunswikOrganismicAchievementEnvironmental1943].
-Such a proximal information basis is obtained by experience or, more technically, by *sampling*, and is neither consistent nor complete but varies in its degree of representativeness. 
-In turn, the mind is not merely required to transform the inputs but to draw inductive inferences to arrive at property descriptions which then, by definition, are only probable. 
-Importantly, the probability, or accuracy, of the description depends on both the sampling process that determines the representativeness of the sample and the use of the probabilistic information that is entailed in the sample [e.g., @fiedlerBewareSamplesCognitiveecological2000].
-
-To adapt (3) for the case of decisions from experience [@hertwigDecisionsExperienceEffect2004], the tuples $(\Omega, \mathcal{F}, P)$ must be replaced by samples, which in this paper are treated as collections of independent and identically distributed (i.i.d.) random variables $X$.^[Note that this paper considers the counterfactual case where samples are random, although it has been stated that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
-660].
-To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
-Specifically, random variables are defined as a measurable function
-
-$$
-X: (\Omega, \mathcal{F})  \mapsto (\Omega', \mathcal{F'}) 
-\; ,
-\tag{4}
-$$
-
-where $\Omega'$ is a set of real numbered values $X$ can take and $\mathcal{F'}$ is a set of subsets of $\Omega'$. 
-I.e., $\Omega$ maps into $\Omega'$ such that correspondingly each subset $A' \in \mathcal{F'}$ has a pre-image $X^{-1}A' \in \mathcal{F}$, which is the set $\{\omega \in \Omega: X(\omega) \in A'\}$ [@kolmogorovFoundationsTheoryProbability1950, p.
-21].
-
-$$
-\begin{aligned}
-  & \iota : I' \mapsto I, \ \text{where} \ I = \{X_{1i}, ..., X_{ki}\} \\
-  & i \in \{1, ..., N\} 
-  \; .
-\end{aligned}
-\tag{5}
-$$
-
-To provide a formal definition of sampling in risky choice, we make use of the mathematical concept of a random variable and start by referring to a prospect as *"risky"* in the case where $p(\omega) \neq 1$ for all $\omega \in \Omega$.
-Here, risky describes the fact that if agents would choose a prospect and any of its outcomes in $\Omega$ must occur, none of these outcomes will occur with certainty. 
-It is acceptable to speak of the occurrence of $\omega$ as a realization of a random variable $X$ defined on a prospect iff the following conditions (1) and (2) are met:
-
-(2) The mapping is such that $X(\omega) = x \equiv \omega$.
-
-In (2), $x \equiv \omega$ means that the realization of a random variable $X(\omega) = x$ is numerically equivalent to its pre-image $\omega$.  
-Given conditions (1) and (2), we denote any observation of $\omega$ as a *"single sample"*, or realization, of a random variable defined on a prospect and the act of generating a sequence of single samples in discrete time as *"sequential sampling"*.
-Note that, since random variables defined on the same prospect are independent and identically distributed (iid), the weak law of the large number applies to the relative frequency of occurrence of an outcome $\omega$ in a sequence of single samples originating from the same prospect.
-Thus, long sample sequences in principle allow to obtain the same information about a prospect by sampling as by symbolic description.
-
-Consider now a choice between prospects $1, ..., k$.
-To construct a stochastic sampling model for DfE, we assume that agents base their decision on the information related to these prospects and define a decision variable as a function of the latter:
-
-$$
-D:= f((\Omega_1, \mathcal{F}_1, P_1), ..., (\Omega_k, \mathcal{F}_k, P_k))
-\;.
-$$
-
-Now, since in DfE no symbolic descriptions of the prospects are provided, the model must be restricted to the case where decisions are based on sequences of single samples originating from the respective prospects:
-
-$$
-D := f(X_{i1}, ..., X_{ik}) 
-\; ,
-$$
-
-where $i \in \{1, ..., N\}$ denotes a sequence of length $N$ of random variables that are iid.
-
-Concerning the form of $f$ and the measures it utilizes, it is quite proper to say that they reflect our assumptions about the exact kind of information agents process and the way they do and that these choices should be informed by psychological theory and empirical protocols.
-Taking the case of different sampling and decision strategies previously assumed to play a role in DfE, the following section demonstrates how such assumptions can be explicated in a stochastic model that builds on the sampling approach outlined so far.
-
--->
-
 # Simulation Study
 
-...
+To demonstrate the impact of different sampling strategies on the inferences about the latent properties of prospects and the resulting choices in DfE, a simulation study was conducted.
+Therefore, computational models were implemented that generate and integrate samples from prospects according to varying parameters reflecting different sampling strategies.
+
+## Choice Problems
+
+We test a set of 2-prospect choice problems, where one of the prospects contains a safe outcome, i.e., $p(\omega) = 1$ and the other two outcomes where all $p(\omega) \neq 1$.
+Both outcomes and probabilities are drawn from uniform distributions, ranging from 0 to 20 for outcomes and from .01 to .99 for probabilities of the smaller outcome of the risky prospect.
+To omit dominant prospects within a choice problem, outcomes of the safe prospect always fall between both outcomes of the risky prospect.
+Table A1 in contains the test set of 60 choice problems, which were sampled from an initial set of 10,000.
+Sampling of gambles was stratified, randomly drawing an equal number of 20 gambles with no, an attractive, and an unattractive rare outcome.
+Risky outcomes are considered *"rare"* if their probability is $p < .2$ and *"attractive"* (*"unattractive"*) if they are higher (lower) than the safe outcome.
+
+For each parameter combination of the generating model, 100 synthetic agents are presented with 60 choices problems.
+In sum, 100 (parameter combinations) x 100 (agents) x 60 (choices) = 600,000 choices are simulated.
+
+## Data Generation
 
@@
 The boundary value $a$ is varied between 1 to 5 in increments of 1.
+
+## Results
 
@@
 
-For each parameter combination of the generating model, 100 synthetic agents are presented with 60 choices problems.
-In sum, 100 (parameter combinations) x 100 (agents) x 60 (choices) = 600,000 choices are simulated.
-We test a set of 2-prospect choice problems, where one of the prospects contains a safe outcome, i.e., $p(\omega) = 1$ and the other two outcomes where all $p(\omega) \neq 1$.
-Both outcomes and probabilities are drawn from uniform distributions, ranging from 0 to 20 for outcomes and from .01 to .99 for probabilities of the smaller outcome of the risky prospect.
-To omit dominant prospects within a choice problem, outcomes of the safe prospect always fall between both outcomes of the risky prospect.
-Table A1 in [Appendix 2][Appendix 2: Choice Problems] contains the test set of 60 choice problems, which were sampled from an initial set of 10,000.
-Sampling of gambles was stratified, randomly drawing an equal number of 20 gambles with no, an attractive, and an unattractive rare outcome.
-Risky outcomes are considered *"rare"* if their probability is $p < .2$ and *"attractive"* (*"unattractive"*) if they are higher (lower) than the safe outcome.
-
 (ref:weighting-parameters) Parameter Estimates of the Weighting Function of @goldsteinExpressionTheoryPreference1987 for Different Simulation Parameters
@@
 
+# Discussion
+
+<!-- Old
+
+Given that the choice is perfectly systematic---as opposed to random or noisy---the chosen alternatives in $I'$ should share some property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
+In the following, I will refer to statements about properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
+
+Often, however, the properties used by the mind to make a choice are not readily described and cannot be directly evaluated [cf.
+@brunswikRepresentativeDesignProbabilistic1955; see @brunswikPerceptionRepresentativeDesign1956, for a detailed treatment]; rather, proper descriptions must be inferred from whatever information the inputs provide about the properties of choice alternatives, using transformation rules, statistical generalizations, or both.
+Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982; see also, e.g., @gigerenzerHowImproveBayesian1995; @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
+Hence, to explain how the mind makes a selection among choice alternatives, one needs to understand the output controlling properties, i.e., the applied selection criteria, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
+The process is sketched in Figure 1.
+
+(ref:figure1) A rough computational level sketch of decision making as an information processing problem.
+To make a selection among choice alternatives on the basis of particular selection criteria, the mind requires explicit descriptions of the relevant properties before they can be evaluated.
+Descriptions are either readily available or must be inferred from the inputs.
+
+```{r fig.cap= "(ref:figure1)"}
+knitr::include_graphics("images/dm-sketch.png")
+```
+
+In what follows, the paper elaborates on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate a rather important principle:
+Given that the mind is indeed sensitive to variations in the property values, the more accurately their descriptions are inferred, the more systematic the choices should become.
+Importantly, this principle is not restricted to any one specific property. 
+Rather, each selection criterion or combination thereof imposes constraints on the assessment of choice alternatives, leading to characteristic choice patterns that are eventually blurred by inaccurate property descriptions.
+
+For the sake of example, I argue that a choice pattern robustly emerging in *decisions from experience* (DfE), the apparent underweighting of small probability events [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; see also @wulffMetaanalyticReviewTwo2018, for a meta-analytic review], may be caused by the assessment constraints associated with a round-wise decision strategy.
+This particular claim has already been made by @hillsInformationSearchDecisions2010 and follows quite directly from probability theory.
+However, the current paper suggests to subordinate decision strategies to the adoption of selection criteria and addresses in some detail two "problems" in the context of DfE, in which descriptions of the properties of choice alternatives must be inferred from sampling data.
+
+For one, there is an *induction problem*, well known from inferential statistics, according to which the sample size determines the margin of error within which any true property of a choice alternative can be inferred, given an otherwise perfect inference process.
+Yet, it follows that if an underweighting pattern is caused by the adoption of an arbitrary selection criterion, it is *a priori* predicted to become more stable with increasing sample size. 
+This prediction is in line with the principle already stated above, i.e., that selection-criteria-induced choice patterns should become more systematic as property descriptions become more accurate.
+Nevertheless, the prediction contrasts the explanation that underweighting is caused by the reliance on small samples [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @rakowBiasedSamplesNot2008], highlighting that outside of the *statistical* models used to describe the choice data, *causal* decision making models of quite different nature may be at play, and that a rather important difference between these causal models resides in the selection criteria they incorporate.
+I will elaborate on this matter as I proceed, however, to be clear from the outset, what the mind does in neither case is performing a probability weighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [cf., e.g., @griffithsRationalUseCognitive2015].
+
+For another, this paper approaches the problem of organizing the sampling data in such a way that it allows chains of inferences connecting the input set $I$ with the output set $I' \subset I$ that are algorithmically short and simple enough to be carried out by minds whose cognitive capacities are bounded [cf.
+@simonInvariantsHumanBehavior1990; @simonBehavioralModelRational1955].
+This may be considered a *representation problem* since the inference chains are constructed around explicit descriptions of the properties of choice alternatives and representations are the "formal schemes" of symbols and rules with which these descriptions are derived [@marrRepresentationRecognitionSpatial1978, p.
+270].
+Specifically, representations differ in how they organize the information used to infer the descriptions of certain properties and these organizations determine the algorithms that can be built into the inference chain [@marrVisionComputationalInvestigation1982].
+In this paper, *sampling strategies* in DfE are considered as representation systems used to organize the samples in a way that subserves the property inferences required by the application of particular selection criteria.
+Though most of my expositions on the role of sampling strategies remain speculative, the core idea is not new to decision research [see, e.g., @hillsInformationSearchDecisions2010; @wulffHowShortLongrun2015].
+By restating this idea and adopting some terms and concepts that have well defined meaning in math and cognitive science, I hope to integrate it into the rich study of the computationally limited mind as an adaptive cognitive system whose processes interact with the information structures in the environment or memory.
+
+The theoretical arguments sketched in this introduction are substantiated by a simulation study. 
+For this purpose, the sampling and decision making processes are implemented in a computational model to simulate choice data from DfE.
+The simulated data is modeled in cumulative prospect theory (CPT), a data model commonly used for describing decisions under risk and uncertainty [@goldsteinExpressionTheoryPreference1987; see also @tverskyAdvancesProspectTheory1992].
+All simulations and analyses are reproducible---materials and instructions can be found on the GitHub repository.
+
+# Inputs to the Decision Making Process and Property Descriptions
+
+By defining decision making as an information processing problem whose solution requires a selection among choice alternatives of the form described in (1), much weight is given to the properties of choice alternatives---whatever those may be for the moment---since it is only through them that any necessary distinction between the alternatives or collections thereof can be made.
+To stress this point, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).
+
+(ref:figure2) A.
+The power set of the set $I$ including the choice alternatives A, B, and C.
+Black (white) circles indicate that an alternative does (not) possess a property.
+Each column displays a possible subset that could result from assessing whether the alternatives posses a relevant property.
+The properties determine the various relations among the choice alternatives.
+Note that properties resulting in the empty set $\{\}$ and the subset $\{A,B,C\}$ do not discriminate between choice alternatives.
+B.
+A Venn diagram visualizing the inclusion map $\iota : I' \mapsto I$.
+$\iota$ maps every element $i$ of the subset $I'$ to its image $i$, treated as element of the superset $I$.
+
+```{r fig.cap= "(ref:figure2)"}
+knitr::include_graphics("images/power-set.png")
+```
+
+Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that could result from assessing for each alternative whether it possesses an arbitrary property (collection) or not [cf.
+@jostMathematicalConcepts2015, p.
+16].
+The concept of the power set thereby illustrates how different selection criteria can alter the consequential choice.
+That is, in rather abstract terms, selection criteria are statements regarding the properties of choice alternatives that the mind evaluates as either true or false during the decision making process; accordingly, the subset $I'$ only contains the alternatives for which the statement is evaluated to be true.
+It follows that if there is some variance in the properties across choice alternatives and the properties are not perfectly correlated, changing the selection criteria can eventually change the subset $I'$.
+
+## What Are the Choice Alternatives and Their Properties?
+
+Given (3), it is evident that the prospects can only be distinguished by the elements of their tuples. 
+These elements are, generally speaking, symbols, some of which describe properties on their own, e.g., the outcome $\omega$, whereas other properties can only be described by collections of symbols, e.g., the sample space $\Omega$ by a set of outcomes as in (2.1), or more complex combinations thereof, e.g., the weighted average which is obtained by first multiplying all outcomes in $\Omega$ by their respective probabilities in $P$ and then summing the resulting products.^[I do not refer to this quantity as expected value, since the term is reserved for random variables, which were not introduced so far.]
+In turn, for choices between prospects, selection criteria are statements about the elements of their tuples that are true or false and these statements imply relations among prospects that are at least nominal, but may also draw on other levels of measurement.
+
+## Inferring Property Descriptions from Sampling Data
+
+Note that a selection criterion may refer to a property for which the raw input, i.e., the symbols, their organization, and the information they encode, do not yet provide an explicit description.
+Even more so, it has been repeatedly stated that for quite many decisions the mind faces, it is simply not possible to draw on direct descriptions of the properties, since they are part of the distal environment  [e.g., @brunswikOrganismicAchievementEnvironmental1943; @fiedlerExplainingSimulatingJudgment1996; @hertwigDescriptionexperienceGapRisky2009; see also @brunswikRepresentativeDesignProbabilistic1955; @brunswikPerceptionRepresentativeDesign1956; @kozyrevaInterpretationUncertaintyEcological2021].
+In either case, some form of description must be inferred from whatever information the input provides about the property in question.
+Consider first the counterfactual case of the prospect whose tuple is not part of the distal environment but is directly described. 
+Since all information about the prospect is given, one may in principle consider the input complete, yet, 
+the tuple implies properties of the prospect which are not explicitly described.
+For example, to obtain the description of the prospect's weighted average, still a calculus according to the algebraic rules described in the preceding paragraph must be carried out. 
+In general, in cases like the one just considered, where the properties are not distal and all information about them is available, property inferences take the form of a mere transformation, where the symbols from the input are ordered and combined according to some transformation rules [cf.
+@marrVisionComputationalInvestigation1982, p.
+20].
+
+In natural world decisions, however, the properties of choice alternatives are often distal and amenable only through their probabilistic relation to proximal cues or samples, which provide the input to the decision making process [cf.
+@brunswikOrganismicAchievementEnvironmental1943].
+Such a proximal information basis is obtained by experience or, more technically, by *sampling*, and is neither consistent nor complete but varies in its degree of representativeness. 
+In turn, the mind is not merely required to transform the inputs but to draw inductive inferences to arrive at property descriptions which then, by definition, are only probable. 
+Importantly, the probability, or accuracy, of the description depends on both the sampling process that determines the representativeness of the sample and the use of the probabilistic information that is entailed in the sample [e.g., @fiedlerBewareSamplesCognitiveecological2000].
+
+To adapt (3) for the case of decisions from experience [@hertwigDecisionsExperienceEffect2004], the tuples $(\Omega, \mathcal{F}, P)$ must be replaced by samples, which in this paper are treated as collections of independent and identically distributed (i.i.d.) random variables $X$.^[Note that this paper considers the counterfactual case where samples are random, although it has been stated that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+660].
+To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
+Specifically, random variables are defined as a measurable function
+
+$$
+X: (\Omega, \mathcal{F})  \mapsto (\Omega', \mathcal{F'}) 
+\; ,
+\tag{4}
+$$
+
+where $\Omega'$ is a set of real numbered values $X$ can take and $\mathcal{F'}$ is a set of subsets of $\Omega'$. 
+I.e., $\Omega$ maps into $\Omega'$ such that correspondingly each subset $A' \in \mathcal{F'}$ has a pre-image $X^{-1}A' \in \mathcal{F}$, which is the set $\{\omega \in \Omega: X(\omega) \in A'\}$ [@kolmogorovFoundationsTheoryProbability1950, p.
+21].
+
+$$
+\begin{aligned}
+  & \iota : I' \mapsto I, \ \text{where} \ I = \{X_{1i}, ..., X_{ki}\} \\
+  & i \in \{1, ..., N\} 
+  \; .
+\end{aligned}
+\tag{5}
+$$
+
+To provide a formal definition of sampling in risky choice, we make use of the mathematical concept of a random variable and start by referring to a prospect as *"risky"* in the case where $p(\omega) \neq 1$ for all $\omega \in \Omega$.
+Here, risky describes the fact that if agents would choose a prospect and any of its outcomes in $\Omega$ must occur, none of these outcomes will occur with certainty. 
+It is acceptable to speak of the occurrence of $\omega$ as a realization of a random variable $X$ defined on a prospect iff the following conditions (1) and (2) are met:
+
+(2) The mapping is such that $X(\omega) = x \equiv \omega$.
+
+In (2), $x \equiv \omega$ means that the realization of a random variable $X(\omega) = x$ is numerically equivalent to its pre-image $\omega$.  
+Given conditions (1) and (2), we denote any observation of $\omega$ as a *"single sample"*, or realization, of a random variable defined on a prospect and the act of generating a sequence of single samples in discrete time as *"sequential sampling"*.
+Note that, since random variables defined on the same prospect are independent and identically distributed (iid), the weak law of the large number applies to the relative frequency of occurrence of an outcome $\omega$ in a sequence of single samples originating from the same prospect.
+Thus, long sample sequences in principle allow to obtain the same information about a prospect by sampling as by symbolic description.
+
+Consider now a choice between prospects $1, ..., k$.
+To construct a stochastic sampling model for DfE, we assume that agents base their decision on the information related to these prospects and define a decision variable as a function of the latter:
+
+$$
+D:= f((\Omega_1, \mathcal{F}_1, P_1), ..., (\Omega_k, \mathcal{F}_k, P_k))
+\;.
+$$
+
+Now, since in DfE no symbolic descriptions of the prospects are provided, the model must be restricted to the case where decisions are based on sequences of single samples originating from the respective prospects:
+
+$$
+D := f(X_{i1}, ..., X_{ik}) 
+\; ,
+$$
+
+where $i \in \{1, ..., N\}$ denotes a sequence of length $N$ of random variables that are iid.
+
+Concerning the form of $f$ and the measures it utilizes, it is quite proper to say that they reflect our assumptions about the exact kind of information agents process and the way they do and that these choices should be informed by psychological theory and empirical protocols.
+Taking the case of different sampling and decision strategies previously assumed to play a role in DfE, the following section demonstrates how such assumptions can be explicated in a stochastic model that builds on the sampling approach outlined so far.
+
+-->
+
 # Summary and Conclusion

### 2022-03-04 manuscript.Rmd
Review Introduction

@@
 Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in past decisions.
-The inputs to DfE therefore take the form of samples.
+The inputs to DfE therefore take the form of sets of sampled outcomes (hereafter: samples).^[<!--Open footnote-->Note that a sample is defined as a set, with each of its elements being a sampled outcome (or: observation).
+Accordingly, aside empty and infinite sets, a sample can contain one or finite many sampled outcomes.<!--Close footnote-->]
 Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
@@
 
-Similar to other behavioral phenomena that can be explained by the mind being sensitive to the composition of the samples on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE can be explained by the tendency to rely on small samples [see, e.g., @hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+Similar to other behavioral phenomena that can be explained by the mind being sensitive to the composition of the samples on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE can be explained by the tendency to rely on small samples [see @hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
 That is, following from the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequency with which a prospect's outcome occurs in a sample of infinite size converges almost surely to its objective probability.
-In such a case, but also in the less strict case of large samples, then, the binomial distribution of each prospect's outcome can be approximated by a symmetric normal distribution [see @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
-However, for small samples, the binomial distribution of small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
+In such a case, but also in the less strict case where the samples grow large, then, the binomial distribution associated with each prospect's outcome can be approximated by a symmetric normal distribution [cf.
+@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
+However, for small samples, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
 Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
-As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities---without correction of sampling error---and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
-Since the same line of reasoning applies would the mind approximate the principle of mathematical expectation by choosing the prospect that produced the greater sample mean, the following discussion focuses on choices in DfE that are based on comparisons of sampled means.
-The relevance of making the inference about latent properties explicit, however, is addressed in the last section of this paper.
-
-Now, this paper uses the outlined effect of small samples as a starting point for an inquiry into the sampling process upfront choices in DfE.
-Specifically, in one paradigm used to study DfE, i.e., the sampling paradigm [see @weberPredictingRiskSensitivity2004], before making a single choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
-Considering this paradigm, the current paper discusses how different strategies of sampling and integrating the prospects' outcomes (hereafter: *sampling strategies*) can produce distinct choice patterns in DfE by altering the number and size of the samples that are used by the mind to accumulate evidence over time [see @hillsInformationSearchDecisions2010, for the original formulation of this claim].
-The paper proceeds as follows:
+
+Different approaches linking the sampling process to the choices in DfE can explain the as-if underweighting of rare outcomes by the reliance on small samples.
+That is, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a single choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
+To couple the sampling process with the decision-making process, sequential sampling models [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] propose that evidence is accumulated over time.
+The core assumption shared by these models is that the sampled outcomes are sequentially integrated into one or more dynamic decision variables (or: preference states), and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+Here, the overall number of sample outcomes decreases with threshold values, which can explain an as-if underweighting of rare outcomes [see @markantModelingChoiceSearch2015].
+
+In another approach, @hillsInformationSearchDecisions2010 propose a dependency between sampling patterns and decision strategies.
+This approach distinguishes sampling patterns along the frequency of switches between prospects during the sampling phase.
+Depending on the decision strategy, then, all outcomes sampled for a prospect are integrated into either the same sample or integrated into multiple, non-overlapping smaller samples, each of which is used for an independent (mean-based) comparison with a sample of another prospect.
+Accordingly, the choice is determined by the number of won comparisons.
+Here, the core assumption is that a high switching frequency coincides with a larger number of comparisons based on respectively smaller samples, which can explain an as-if underweighting of rare outcomes despite a large overall number of sampled outcomes.
+Indeed, some studies have found the description-experience gap to appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
+
+Now, considering the sampling paradigm, this paper discusses and demonstrates in a simulation how an integration of both outlined approaches can explain distinct sampling effects on choices in DfE.
+The paper therefore proceeds as follows:
 In the first section, a formal definition of DfE is provided.
 In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices between prospects in terms of deviations from the principle of mathematical expectation.
-In the section that follows, using an evidence accumulation approach, different sampling strategies are discussed, how they produce distinct choice patterns in DfE, and how these patterns may be captured in the parameters of CPT.
-Thereafter, a simulation is presented in which these sampling strategies are implemented in a computational model to simulate choices between a safe and a two-outcome prospect.
-By proposing distinct links between the parameter capturing different sampling strategies, the resulting choices, and the estimated CPT parameters, the simulation substantiates the core claim of this paper, namely, that sampling effects on choices in DfE may not be reduced to the overall number of sampled outcomes.
-That is, the simulation demonstrates how the overall number of sampled outcomes can increase without the underweighting of rare outcomes fading, assuming that the sampling strategy translates this increase in overall number into a greater number of samples over which evidence is accumulated, but not samples of greater size.
-The last section supplements the rather technical inquiry into the sampling process and its consequences with a theoretical inroad into the question how the idea of sampling strategies can be integrated into the broader study of the computationally limited mind as an adaptive cognitive system.
+In the section that follows, a computational model is proposed that integrates the assumption of evidence accumulation over time and of a link between sampling patterns and decision strategies. 
+More specifically, the model sequentially accumulates evidence obtained from ordinal comparisons between the prospects' samples, with different strategies of sampling and integrating the prospects outcomes (hereafter: *sampling strategies*) altering the size of these samples.
+Thereafter, choices between a safe and a two-outcome prospect are simulated from the model.
+The simulations demonstrate how different sampling strategies and thresholds interact with the LLN to produce distinct choice patterns in DfE that can be captured in the parameters of CPT.
+In this regard, one key prediction of the model is that the overall number of sampled outcomes can increase without the underweighting of rare outcomes fading, given the sampling strategy translates this increase into a greater number of samples over which evidence is accumulated, but not samples of greater size.
+<!--The last section supplements the rather technical inquiry into the sampling process and its consequences with a theoretical inroad into the question how the idea of sampling strategies can be integrated into the broader study of the computationally limited mind as an adaptive cognitive system.-->
 The paper closes with a summary and a conclusion.
@@
 * The value of a cumulative decision weight depends on the estimated shape of the graph of $w$, the weighting function's parameters respectively.
-That is, the shape of the graph of $w$ displays in which interval on the cumulative probability scale $[0,1]$ the images of $w$, $w(p)$ take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
+That is, the shape of the graph of $w$ displays in which interval on the cumulative probability scale $[0,1]$ the images of $w$, $w(p)$, take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
 Hence, assuming a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
@@
 
-To begin with, the gray-dashed identity lines in Figure\ \@ref(fig:w-shapes) imply a linear weighting pattern.
+In some more detail, the gray-dashed identity lines in Figure\ \@ref(fig:w-shapes) imply a linear weighting pattern.
 That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are derived according to (12) would be equal to the differences between the respective objective cumulative probabilities and therefore also to the objective probabilities of the outcomes for which the weights are determined.
@@
 That is, CPT may be considered a computational-level theory that specifies the computational problem the mind faces during decisions between prospects, and how this problem may be solved by the abstract calculus reviewed above.
-However, as such, CPT cannot substitute algorithmic-level theories that make claims about how exactly the mind transforms the inputs to the decision making process into outputs---i.e., into choices---which approximate the solutions of CPT's calculus [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
+However, as such, CPT cannot substitute algorithmic-level theories that make claims about how exactly the mind transforms the inputs to the decision making process into outputs which approximate the solutions of CPT's calculus [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
 Therefore, this paper uses CPT merely as a data model and continues to inquire how on the algorithmic level the mind may integrate sampling strategies into the information-processing chain upfront choices in DfE.
@@
 
-The need to distinguish between the computational and the algorithmic level in the domain of decision making is exemplified by the fact that information about prospects may come in the form of descriptions or samples.
-Whereas CPT can be used to model choices in DfD and DfE, the information-processing chains upfront choices in DfE cannot be identical to those in DfD.
-That is, inputs in the form of experienced outcomes require different algorithms to be processed than do descriptions of outcomes and their probabilities.
-Specifically, the mind must integrate the experienced outcomes into a sample in order to make an inference about the properties of the latent prospects, the outcome-probability pairs respectively.
+The need to distinguish between the computational and the algorithmic level in the domain of decision making is exemplified by the fact that information about prospects may come in the form of descriptions or sampled outcomes.
+Whereas CPT can be used to model choices in DfD and DfE, the actual information-processing chains that the mind may execute upfront choices in DfE cannot be identical to those in DfD.
+That is, inputs in the form of sampled outcomes require different algorithms to be processed than do descriptions of outcomes and their probabilities.
+
+For DfE, several approaches have been proposed to link the sampling process to the final choice. 
+One such approach is captured by sequential sampling models which approach the information-processing chain as an evidence accumulation process. 
+One core assumption of these models applied to choices between prospects [see, e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015] is that the sampled outcomes are used to sequentially accumulate evidence for or against the respective prospect as the sequences described in (8) grow.
+More specifically, sequential sampling models assume that the values of the sampled outcomes are sequentially integrated into a dynamic decision variable.
+Once the value of the decision variable reaches a threshold, the respective prospect is chosen.
+
+In contrast, @hillsInformationSearchDecisions2010, proposed another potential link between the sampling and the decision process in DfE.
+Specifically, the authors suppose that the sampling pattern may be linked to the choice strategy that people apply. 
+That is, if single samples originating from different prospects are generated in direct succession (piecewise sampling), the evaluation of prospects is based on multiple ordinal comparisons of single samples (round-wise decisions).
+In contrast, if single samples originating from the same prospect are generated in direct succession (comprehensive sampling), it is supposed that the evaluation of prospects is based on a single ordinal comparison of long sequences of single samples (summary decisions).
+Indeed, they found some evidence that people who switch more often, make more choices in line with a piecewise strategy and people who switch rarely make more choices in line with a comprehensive strategy [but see @wulffHowShortLongrun2015].
+
+In this paper, these two ideas are integrated, including speed accuracy tradeoffs etc. with the idea of a link between sampling and decision-making. 
+Specifically, it is assumed that evidence is accumulated over time with a decision variable approaching a threshold, however, the model allows for the possibility that evidence accumulation works not necessarily across the single sampled outcomes but over samples thereof.
+We model the processs as one where evidence is accumulated over multiple ordinal comparisons of samples---their means---respectively, rather than over the raw sampled outcomes. 
+We therefore combine all thing. 
+We show that each follows a Bernoulli distribution:
+
+$$
+D \sim \mathcal{B}\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right) \; ,
+$$
+## CPT Patterns
+
+Given that, ...
 

### 2022-03-06 manuscript.Rmd
Reviews

@@
 In fact, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and returns a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
-Let us therefore treat the choice alternatives as elements $c$ of the set $C$, and decision making as an information-processing problem starting from $C$ and stopping at a proper subset $C' \subset C$ with the inclusion map
-$$
-\begin{aligned}
-  \iota : C' &\to C \\
-  c &\mapsto c  \quad \forall c \in C'
-\end{aligned}
-\tag{1}
-$$
-[cf. @jostMathematicalConcepts2015, p. 15].
 
@@
 Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in past decisions.
-The inputs to DfE therefore take the form of sets of sampled outcomes (hereafter: samples).^[<!--Open footnote-->Note that a sample is defined as a set, with each of its elements being a sampled outcome (or: observation).
-Accordingly, aside empty and infinite sets, a sample can contain one or finite many sampled outcomes.<!--Close footnote-->]
+The inputs to DfE therefore take the form of sets of sampled outcomes (hereafter: samples).^[<!--Open footnote-->Note that a sample is defined as a set of sampled outcomes.
+Aside empty and infinite sets, a sample can therefore contain one or finite many sampled outcomes (see also below).<!--Close footnote-->]
 Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
@@
 
-Similar to other behavioral phenomena that can be explained by the mind being sensitive to the composition of the samples on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE can be explained by the tendency to rely on small samples [see @hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+Similar to other behavioral phenomena that can be explained by the mind being sensitive to the composition of the samples on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE can be explained by peoples' tendency to rely on small samples [@hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
 That is, following from the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequency with which a prospect's outcome occurs in a sample of infinite size converges almost surely to its objective probability.
-In such a case, but also in the less strict case where the samples grow large, then, the binomial distribution associated with each prospect's outcome can be approximated by a symmetric normal distribution [cf.
+In such a case, then, the binomial distribution associated with each prospect's outcome can be approximated by a symmetric normal distribution [cf.
 @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
@@
 Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
-
-Different approaches linking the sampling process to the choices in DfE can explain the as-if underweighting of rare outcomes by the reliance on small samples.
+As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities (without correction of sampling error, respectively) and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
+
+Aside this computational-level explanation, different algorithmic approaches linking the sampling process to the choices in DfE can explain the as-if underweighting of rare outcomes by the reliance on small samples.
 That is, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a single choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
-To couple the sampling process with the decision-making process, sequential sampling models [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] propose that evidence is accumulated over time.
+To couple the sampling with the decision-making process, sequential sampling models [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] propose that evidence is accumulated over time.
 The core assumption shared by these models is that the sampled outcomes are sequentially integrated into one or more dynamic decision variables (or: preference states), and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-Here, the overall number of sample outcomes decreases with threshold values, which can explain an as-if underweighting of rare outcomes [see @markantModelingChoiceSearch2015].
-
-In another approach, @hillsInformationSearchDecisions2010 propose a dependency between sampling patterns and decision strategies.
-This approach distinguishes sampling patterns along the frequency of switches between prospects during the sampling phase.
-Depending on the decision strategy, then, all outcomes sampled for a prospect are integrated into either the same sample or integrated into multiple, non-overlapping smaller samples, each of which is used for an independent (mean-based) comparison with a sample of another prospect.
-Accordingly, the choice is determined by the number of won comparisons.
-Here, the core assumption is that a high switching frequency coincides with a larger number of comparisons based on respectively smaller samples, which can explain an as-if underweighting of rare outcomes despite a large overall number of sampled outcomes.
+Moreover, these models use differences in thresholds to explain speed-accuracy trade-offs in decision making, with higher thresholds requiring more evidence in favor of a prospect to be sampled.
+Hence, since the overall number of sampled outcomes decreases with thresholds, the adoption of low thresholds can be used to explain an as-if underweighting of rare outcomes [see @markantModelingChoiceSearch2015].
+
+Yet, in another approach, @hillsInformationSearchDecisions2010 propose a dependency between sampling patterns and decision strategies.
+This approach distinguishes sampling patterns along the frequency of switches between prospects during the sampling phase and assumes that only outcomes that were sampled between each switch are integrated into the same sample.
+Then, assuming that the means of consecutive samples from different prospects are compared, the choice is determined by the number of won comparisons.
+Since each comparison is weighted equally, such a link between sampling patterns and decision strategies can explain an as-if underweighting of rare outcomes despite a large overall number of sampled outcomes.
 Indeed, some studies have found the description-experience gap to appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
-
-Now, considering the sampling paradigm, this paper discusses and demonstrates in a simulation how an integration of both outlined approaches can explain distinct sampling effects on choices in DfE.
+More specifically, while the probability of a rare outcome to be sampled increases with the length of the sampling process, an increasing switching frequency causes the rare outcome not to be considered in an increasing number of comparisons, which, however, are the primitive units of evidence in this model.
+As a consequence, the as-if underweighting of rare outcomes is not predicted to fade with an increase in the overall number of sampled outcomes, if the switching frequency is high.
+
+Given that the mind is indeed sensitive to variations in the property values, the more accurately their descriptions are inferred, the more systematic the choices should become.
+Importantly, this principle is not restricted to any one specific property. 
+Rather, each selection criterion or combination thereof imposes constraints on the assessment of choice alternatives, leading to characteristic choice patterns that are eventually blurred by inaccurate property descriptions.
+
+considering the sampling paradigm, this paper discusses and demonstrates in a simulation how an integration of both outlined approaches can explain distinct sampling effects on choices in DfE.
+
 The paper therefore proceeds as follows:
-In the first section, a formal definition of DfE is provided.
+In the first section, a formal definition of prospects and DfE is provided.
 In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices between prospects in terms of deviations from the principle of mathematical expectation.
@@
 The paper closes with a summary and a conclusion.
-Note that this paper, including the simulations and data analyses, is reproducible---materials and instructions can be found on the GitHub repository.
-
-# Prospects, Decisions from Description, and Decisions from Experience
-
-To begin with, let the axiomatic definition of a prospect be that of a discrete random variable's distribution [see @tverskyAdvancesProspectTheory1992].
+
+# The Description of Choices in CPT
+
+Following @kolmogorovFoundationsTheoryProbability1950,^[The symbolic notation from @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015 is adopted.] let the axiomatic definition of a prospect be that of a discrete random variable's distribution.
 Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space.
-Following the @kolmogorovFoundationsTheoryProbability1950 axioms and the notation of @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, $\Omega$ is the sample space containing a finite set of elements, one of which results from choosing the respective prospect:
-$$
-\omega_i \in \{\omega_1, ..., \omega_n\} = \Omega
-\; .
-\tag{2}
-$$ 
-$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$, where each element $A \in \mathcal{P}(\Omega) = \mathcal{F}$ is a subset of $\Omega$.^[<!--Open footnote-->Note that this paper considers only the case of finite sample spaces.
-The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp.
-2-3 and 14-15], also covers infinite sample spaces and is that of a $\sigma$-algebra.
-For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such [@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1].<!--Close footnote-->]
-$P$ is a probability measure
+Accordingly, $\Omega$ is a finite sample space with each element $\omega \in \Omega$ denoting a possible consequence of choosing the respective prospect.
+$\mathcal{F}$ is the power set $\mathcal{P}(\Omega)$ with each element $A \in \mathcal{F}$ being a subset of $\Omega$.
+$P$ is the probability measure
 $$
 P: \mathcal{F} \to [0,1]
-\; ,
-\tag{3}
-$$
-which assigns each subset $A \in \mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.<!--^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \to [0,1]$, which is used to construct the probability measures $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$.]-->
-According to Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, p.
-21-22],^[<!--Open footnote-->See also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive yet accessible introduction to random variables.<!--Close footnote-->]
-the random variable $X$ is the measure
+\tag{1}
+$$
+assigning the elements of $\mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.
+Now, the random variable is a function
 $$
@@
 \end{aligned}
+\tag{2}
+$$
+where $(\Omega', \mathcal{F'})$ is a measurable space with each element $x \in \Omega'$ denoting a possible outcome of a prospect and each element $A' \in \mathcal{F'}$ being a subset of $\Omega'$.
+An outcome's probability $p_X(x)$ is then provided by the pushforward measure
+$$
+P_X : \mathcal{F'} \to [0,1]
+\tag{3}
+$$
+with 
+$$
+P_X(A' \in \mathcal{F'}) := P(\{\omega: X(\omega) = x \in A'\})
+\; .
 \tag{4}
 $$
-where $(\Omega', \mathcal{F'})$ is a measurable space with each element $x \in \Omega'$ being a possible outcome of a prospect and each element $A' \in \mathcal{F'}$ being a subset of $\Omega'$.
-An outcome's probability $p_X(x)$ is then provided by the pushforward probability measure
-$$
-P_X : \mathcal{F'} \to [0,1]
+To summarize and simplify, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
+$$
+\{P_{X_1}, ... , P_{X_k}\}
+\; ,
 \tag{5}
 $$
-with 
-$$
-P_X(A' \in \mathcal{F'}) := P(X^{-1} \ A') = P(\{\omega: X(\omega) = x \in A'\})
-\; .
-\tag{6}
-$$
-That is, the set consisting of a single outcome $x$ is a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(\{\omega : X(\omega) = x \in \{x\}\})$.
-Note that the probability measure in (5) and (6), respectively, is a discrete random variable's distribution and therefore a prospect.
-To summarize and simplify, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
-$$
-C = \{P_{X_1}, ... , P_{X_k}\}
+where each element $P_X$ can itself be considered a set of outcome-probability pairs $\{(x_, p_X(x)\}$.
+
+The choices people actually make between prospects are often described in terms of deviations from the principle of mathematical expectation, according to which the prospect with the largest expected value (EV)
+$$
+EV = \sum_i^n x_i \times p_X(x_i)
 \tag{7}
-$$
-with each element $c \in C$ being a distribution $P_X$ of a random variable defined on its own probability space.
-Accordingly, each $c$ can itself be considered a set of outcome-probability pairs $(x_i, p_X(x_i)) \in \{(x_1, p_X(x_1)), ..., (x_n, p_X(x_n))\}$.
-
-However, only occasionally in peoples' daily life, inputs take the form of explicit descriptions of all outcome-probability pairs.
-In such cases, people would make DfD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
-Yet, rather often, people make DfE, where the mind can learn about the latent properties of prospects only by experiental sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
-Accordingly, considering the sampling paradigm,^[<!--Open footnote-->Note that it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
-660].
-See, e.g., @plonskyRelianceSmallSamples2015, who drop the i.i.d.-assumption for DfE.<!--Close footnote-->]
-let a sample of a prospect be a set of realizations of the respective random variable.
-More specifically, for the choice between $1, ..., k$ prospects, the inputs to DfE---i.e., the sampled outcomes---are generated by a set $S$ of prospect-specific discrete-time stochastic processes
-$$
-S = \{\{X_{1t}\}, ... , \{X_{kt}\}\}
-\; ,
-\tag{8}
-$$
-where each $s \in S$ is a sequence of independent and identically distributed (i.i.d.) random variables, each $t \in \{t_1, ..., t_N\}$ corresponds to the position of the respective random variable in such a sequence, and $N$ denotes the length of the respective sequence, which corresponds to the overall number of sampled outcomes for this prospect.
-Now, one core assumption of this paper is that, for a stochastic process $s \in S$ of length $N$, the mind sequentially integrates the sampled outcomes into either one enumerated sample growing to the size $N$ or into multiple smaller enumerated samples, each corresponding to a unique sub-sequence of s.
-Assuming that the mind uses all samples so obtained during a process of evidence accumulation, this paper discusses and demonstrates how different sampling strategies that alter the number and size of these samples can produce distinct choice patterns in DfE.
-Before so doing, however, the following section reviews how CPT can be used as a data model that captures systematic deviations from the principle of mathematical expectation in the parameter estimates of a *value* and a *weighting function*.
-
-# The Description of Choices and Weighting Patterns in CPT
-
-The choices people actually make between prospects---be that in DfD or DfE---are often described in terms of deviations from the principle of mathematical expectation, according to which the prospect with the largest expected value (EV)
-$$
-EV = \sum_i^n x_i \times p_X(x_i)
-\tag{9}
 $$ 
@@
 \; ,
-\tag{10}
+\tag{8}
 $$ 
@@
      x_i^\alpha &\forall x_i \geq 0, \\
-     -\lambda \times |x_i|^\alpha &\text{else}
+     -\lambda |x_i|^\alpha &\text{else}
      \; ,
@@
 \end{aligned}
-\tag{11}
+\tag{9}
 $$
@@
   \end{cases}
-\tag{12}
+\tag{10}
 $$
@@
 \end{aligned}
-\tag{13}
+\tag{11}
 $$
@@
 That is, inputs in the form of sampled outcomes require different algorithms to be processed than do descriptions of outcomes and their probabilities.
-
-For DfE, several approaches have been proposed to link the sampling process to the final choice. 
-One such approach is captured by sequential sampling models which approach the information-processing chain as an evidence accumulation process. 
-One core assumption of these models applied to choices between prospects [see, e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015] is that the sampled outcomes are used to sequentially accumulate evidence for or against the respective prospect as the sequences described in (8) grow.
-More specifically, sequential sampling models assume that the values of the sampled outcomes are sequentially integrated into a dynamic decision variable.
-Once the value of the decision variable reaches a threshold, the respective prospect is chosen.
+More specifically, the core difference between DfD and DfE is that in the latter case, the properties must be inferred. 
+However, as has been outlined in the introduction, for such an inference rather many sampled outcomes must be integrated.
+
+However, only rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcome-probability pairs.
+In such cases, people would make DfD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
+Yet, rather often, people make DfE, where the mind can learn about the latent properties of prospects only by experiental sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
+That is, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set of prospect-specific stochastic processes
+$$
+\{\{X_{1t}\}, ... , \{X_{kt}\}\}
+\; ,
+\tag{6}
+$$
+where each $\{X_{t}\}_{t \in \mathbb N}$ is a collection of independent and identically distributed (i.i.d.) random variables.
+Then, in other words, each stochastic process produces a sequence sampled outcomes. 
+Now, one core assumption of this paper is that, in order to infer the latent properties of a prospect, the mind sequentially integrates the sampled outcomes into either one sample or into multiple smaller samples.
+Assuming that the mind uses all samples so obtained during a process of evidence accumulation, this paper discusses and demonstrates how different sampling strategies that alter the number and size of these samples can produce distinct choice patterns in DfE.
+Before so doing, however, the following section reviews how CPT can be used as a data model that captures systematic deviations from the principle of mathematical expectation in the parameter estimates of a *value* and a *weighting function*.
+
+## The model
+
+To model the information-processing chain in DfE, the current paper integrates two approaches that have been proposed to link the sampling process and the decision-making process. 
+Specifically,
+
+One such approach is captured by sequential sampling models, which approach the information-processing chain as an evidence accumulation process. 
+One core assumption of these models applied to choices between prospects [see, e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] is that the sampled outcomes are used to sequentially accumulate evidence for or against the respective prospect as the sequences in (8) grow.
+More specifically, sequential sampling models assume that the values of the sampled outcomes are sequentially integrated into one or more dynamic decision variables.
+Once the value of a decision variable reaches a threshold in favor of a prospect, a respective choice is made.
 
@@
 Indeed, they found some evidence that people who switch more often, make more choices in line with a piecewise strategy and people who switch rarely make more choices in line with a comprehensive strategy [but see @wulffHowShortLongrun2015].
-
-In this paper, these two ideas are integrated, including speed accuracy tradeoffs etc. with the idea of a link between sampling and decision-making. 
-Specifically, it is assumed that evidence is accumulated over time with a decision variable approaching a threshold, however, the model allows for the possibility that evidence accumulation works not necessarily across the single sampled outcomes but over samples thereof.
-We model the processs as one where evidence is accumulated over multiple ordinal comparisons of samples---their means---respectively, rather than over the raw sampled outcomes. 
-We therefore combine all thing. 
-We show that each follows a Bernoulli distribution:
-
-$$
-D \sim \mathcal{B}\left( p \left(\overline{X}_{N_X} - \overline{Y}_{N_Y} > 0\right), n\right) \; ,
-$$
-## CPT Patterns
-
-Given that, ...
+However, in this approach no causal claims are made.
+
+Therefore, model assumes that evidence is accumulated over a sequence of mean-based comparisons between the samples.
+The results of each comparison is defined as a random variable
+$$
+\begin{aligned}
+  Z : \mathbb{R} &\to \mathbb{N} \\
+  (\overline{X}, \overline{Y}) &\mapsto 
+  \begin{cases}
+     1 &\text{if} \quad \overline{X} > \overline{Y}, \\
+     -1 &\text{if} \quad \overline{X} < \overline{Y}, \\
+     0 &\text{else}
+     \; . 
+  \end{cases}
+\end{aligned}
+\tag{}
+$$
+The evidence accumulation process can therefore be defined as a random walk 
+$$
+D_n = \sum_t^n Z_t \quad n \in \mathbb N
+$$
 
@@
 
-# Acknowledgement
+\newpage
 
 # References
+
+<div id="refs"></div>
+
+\newpage
+
+# Appendix

### 2022-03-09 manuscript.Rmd
Secure Version

@@
 Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
-As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities (without correction of sampling error, respectively) and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
+As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
 
@@
 To couple the sampling with the decision-making process, sequential sampling models [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] propose that evidence is accumulated over time.
-The core assumption shared by these models is that the sampled outcomes are sequentially integrated into one or more dynamic decision variables (or: preference states), and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+The core assumption shared by these models is that the sampled outcomes are sequentially integrated into one or more dynamic decision variables, and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
 Moreover, these models use differences in thresholds to explain speed-accuracy trade-offs in decision making, with higher thresholds requiring more evidence in favor of a prospect to be sampled.
@@
 Yet, in another approach, @hillsInformationSearchDecisions2010 propose a dependency between sampling patterns and decision strategies.
-This approach distinguishes sampling patterns along the frequency of switches between prospects during the sampling phase and assumes that only outcomes that were sampled between each switch are integrated into the same sample.
-Then, assuming that the means of consecutive samples from different prospects are compared, the choice is determined by the number of won comparisons.
+Considering the choice between two prospects, this approach distinguishes sampling patterns along the frequency of switches between the prospects during the sampling phase and assumes that only outcomes that were sampled from the same prospect between switches are integrated into the same sample.
+Then, it is assumed that each time after a new sample for both prospects was generated, their means are compared, and the choice is determined by the number of won comparisons.^[<!--Open footnote-->Note that @hillsInformationSearchDecisions2010 describe only the two paradigmatic cases, where prospects are either switched just once (comprehensive sampling) or after each sampled outcome (piecewise sampling).
+Accordingly, in the former case choices depend on a single comparison between the means of samples that contain all outcomes sampled for the respective prospect (summary strategy); in the latter case, however, choices depend on multiple comparisons between samples that contain only one sampled outcome (round-wise strategy).
+Nevertheless, Hills and Hertwig [-@hillsInformationSearchDecisions2010, p.
+1788] acknowledge that "many [sampling] strategies will fall on the continuum between [these cases]", which is why the general description is used above.<!--Close footnote-->]
 Since each comparison is weighted equally, such a link between sampling patterns and decision strategies can explain an as-if underweighting of rare outcomes despite a large overall number of sampled outcomes.
 Indeed, some studies have found the description-experience gap to appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
-More specifically, while the probability of a rare outcome to be sampled increases with the length of the sampling process, an increasing switching frequency causes the rare outcome not to be considered in an increasing number of comparisons, which, however, are the primitive units of evidence in this model.
-As a consequence, the as-if underweighting of rare outcomes is not predicted to fade with an increase in the overall number of sampled outcomes, if the switching frequency is high.
-
-Given that the mind is indeed sensitive to variations in the property values, the more accurately their descriptions are inferred, the more systematic the choices should become.
-Importantly, this principle is not restricted to any one specific property. 
-Rather, each selection criterion or combination thereof imposes constraints on the assessment of choice alternatives, leading to characteristic choice patterns that are eventually blurred by inaccurate property descriptions.
-
-considering the sampling paradigm, this paper discusses and demonstrates in a simulation how an integration of both outlined approaches can explain distinct sampling effects on choices in DfE.
-
-The paper therefore proceeds as follows:
-In the first section, a formal definition of prospects and DfE is provided.
-In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices between prospects in terms of deviations from the principle of mathematical expectation.
+More specifically, while the probability of a rare outcome to be sampled increases with the overall number of sampled outcomes, an increasing switching frequency causes the rare outcome not to be considered in an increasing number of comparisons.
+
+Now, this paper integrates both approaches to discuss in some more detail how the effect of small samples may exert its influence on the choices between two prospects in DfE.
+The main argument here is that whereas the reliance on small samples generally explains the as-if underweighting of rare outcomes in DfE, this explanation cannot be equated with inaccurate inferences about the latent properties of prospects that carry over to the subsequent choices.
+Rather the opposite can be the case.
+That is, the latent properties may imply different relations among the prospects in the form that choices according to the differences in one latent property may not coincide with the choices according to the differences in another latent property.
+Hence, although technically the reliance on small samples caused deviations from the principle of mathematical expectation, these deviations may reflect an accurate assessment of differences in a latent property other than the expected values.
+
+To substantiate this claim, this paper defines a *sampling strategy* as the probability of sampling outcomes from different prospects in direct succession (hereafter: switching probability) and presents a sequential sampling model that accumulates the evidence obtained from the comparisons between sample means.
+More specifically, similar to @hillsInformationSearchDecisions2010, the model only integrates the outcomes that are sampled from the same prospect between switches into the same sample and each time after a new sample for both prospects was generated, their respective means are compared.
+The information about the outcomes of these comparisons are integrated into either one dynamic decision variable capturing the difference in the number of won comparisons or into two dynamic decision variables capturing the absolute number of won comparisons for both prospects separately.
+Accordingly, the thresholds determine how much (more) comparisons a prospect must win in order to be chosen. 
+The model demonstrates that sampling strategies, through their probabilistic relation to the size of the samples, determine which differences in the latent properties of the prospects are represented in the outcomes of the comparisons.
+That is, for a decreasing switching probability, the number of outcomes that are successively sampled from a given prospect increases such that the size of the sample grows.
+Accordingly, the model shows how with decreasing switching probability a mean comparison becomes more indicative for differences of the prospects in their expected values.
+In turn, for an increasing switching probability, the number of outcomes that are successively sampled from a given prospect decreases such that the size of the sample decreases.
+Accordingly, the growing sequence of sample comparisons becomes more indicative for which prospect produces the higher outcomes most of the time.
+
+The paper proceeds as follows:
+The first section provides a formal definition of prospects and reviews cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] as a data model that can be used to describe choices between prospects in terms of deviations from the principle of mathematical expectation.
 In the section that follows, a computational model is proposed that integrates the assumption of evidence accumulation over time and of a link between sampling patterns and decision strategies.
-More specifically, the model sequentially accumulates evidence obtained from ordinal comparisons between the prospects' samples, with different strategies of sampling and integrating the prospects outcomes (hereafter: *sampling strategies*) altering the size of these samples.
-Thereafter, choices between a safe and a two-outcome prospect are simulated from the model.
-The simulations demonstrate how different sampling strategies and thresholds interact with the LLN to produce distinct choice patterns in DfE that can be captured in the parameters of CPT.
-In this regard, one key prediction of the model is that the overall number of sampled outcomes can increase without the underweighting of rare outcomes fading, given the sampling strategy translates this increase into a greater number of samples over which evidence is accumulated, but not samples of greater size.
-<!--The last section supplements the rather technical inquiry into the sampling process and its consequences with a theoretical inroad into the question how the idea of sampling strategies can be integrated into the broader study of the computationally limited mind as an adaptive cognitive system.-->
+
 The paper closes with a summary and a conclusion.
@@
 
-# Discussion
-
 <!-- Old

### 2022-03-11 manuscript.Rmd
Add appendix with anlyses of comprehensive simulation

@@
 
-bibliography      : ["references_sampling-in-dfe.bib"]
-csl               : apa.csl
+bibliography      : references_sampling-in-dfe.bib
+csl               : /Users/Linus Hof/Documents/Psychologie/ARC/sampling-in-dfe/apa.csl
+appendix          : manuscript_appendix.Rmd
 
@@
 documentclass     : "apa7"
-output            : papaja::apa6_pdf
+output: papaja::apa6_pdf
 
@@
 
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = F, fig.pos = "t", fig.align = "l")
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = F, #omit messages
+                      fig.align = "l", #align figures to left margin
+                      fig.pos = "t"
+                      )
 ```
 
-```{r packages}
-# load required packages
+```{r packages, include=FALSE}
+#load required packages
 pacman::p_load(papaja,
@@
 
-Similar to other behavioral phenomena that can be explained by the mind being sensitive to the composition of the samples on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE can be explained by peoples' tendency to rely on small samples [@hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+Similar to other behavioral phenomena that could be explained by assuming that the mind is sensitive to the composition of the samples on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE could be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [@hertwigDecisionsExperienceEffect2004; @plonskyRelianceSmallSamples2015; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
 That is, following from the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequency with which a prospect's outcome occurs in a sample of infinite size converges almost surely to its objective probability.
-In such a case, then, the binomial distribution associated with each prospect's outcome can be approximated by a symmetric normal distribution [cf.
+In such a case, then, according to the de Moivre-Laplace theorem, the binomial distribution associated with each prospect's outcome can be approximated by a symmetric normal distribution [cf.
 @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
@@
 Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
-As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
 
-Aside this computational-level explanation, different algorithmic approaches linking the sampling process to the choices in DfE can explain the as-if underweighting of rare outcomes by the reliance on small samples.
-That is, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a single choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
-To couple the sampling with the decision-making process, sequential sampling models [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] propose that evidence is accumulated over time.
-The core assumption shared by these models is that the sampled outcomes are sequentially integrated into one or more dynamic decision variables, and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-Moreover, these models use differences in thresholds to explain speed-accuracy trade-offs in decision making, with higher thresholds requiring more evidence in favor of a prospect to be sampled.
-Hence, since the overall number of sampled outcomes decreases with thresholds, the adoption of low thresholds can be used to explain an as-if underweighting of rare outcomes [see @markantModelingChoiceSearch2015].
+Consistent with this statistical regularity, sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] assume that the information-processing chain upfront choices in DfE takes the form of an evidence accumulation process over time, with choices becoming more accurate the more evidence must be accumulated.
+Specifically, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
+To relate the sampling process to the choice, sequential sampling models assume that the sampled outcomes are sequentially accumulated into one or more dynamic decision variables, and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+Accordingly, the number of outcomes required to sample decreases with thresholds, which could account for an as-if underweighting of rare outcomes [see @markantModelingChoiceSearch2015].
+
+However, some studies found the as-if underweighting of rare outcomes in DfE to appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
+While this finding demonstrates that the as-if underweighting of rare outcomes in DfE cannot be reduced to a small overall number of sampled outcomes, it may still be the case that the respective deviations from the principle of mathematical expectation were caused by the reliance on small samples.
+For example, given a large overall number of sampled outcomes, an as-if underweighting of rare outcomes could be explained, if only a small subset of all the sampled outcomes was considered for the assessment of prospects.
+<!---->
 
@@
 1788] acknowledge that "many [sampling] strategies will fall on the continuum between [these cases]", which is why the general description is used above.<!--Close footnote-->]
-Since each comparison is weighted equally, such a link between sampling patterns and decision strategies can explain an as-if underweighting of rare outcomes despite a large overall number of sampled outcomes.
-Indeed, some studies have found the description-experience gap to appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
+Since each comparison is weighted equally, such a link between sampling patterns and decision strategies can explain an as-if underweighting of rare outcomes despite a large overall number of sampled outcomes being considered.
 More specifically, while the probability of a rare outcome to be sampled increases with the overall number of sampled outcomes, an increasing switching frequency causes the rare outcome not to be considered in an increasing number of comparisons.
@@
 Accordingly, the growing sequence of sample comparisons becomes more indicative for which prospect produces the higher outcomes most of the time.
-
-The paper proceeds as follows:
-The first section provides a formal definition of prospects and reviews cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] as a data model that can be used to describe choices between prospects in terms of deviations from the principle of mathematical expectation.
-In the section that follows, a computational model is proposed that integrates the assumption of evidence accumulation over time and of a link between sampling patterns and decision strategies.
-
-The paper closes with a summary and a conclusion.
 
@@
 Given that the value of each cumulative decision weight depends on the two transformed cumulative probabilities in (12)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the weighting pattern are reviewed by considering the actual weighting function.
-Therefore, Figure\ \@ref(fig:w-shapes) illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
+Therefore, Figure\ \@ref(fig:weighting-function) illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
 Now, let each $p$ on the abscissa be one of the four cumulative probabilities from (12). 
-Then each graph in Figure\ \@ref(fig:w-shapes) displays the graphical shape of the weighting function
+Then each graph in Figure\ \@ref(fig:weighting-function) displays the graphical shape of the weighting function
 $$
@@
 
-(ref:weighting) Possible Graphical Shapes of Goldstein and Einhorn's -@goldsteinExpressionTheoryPreference1987 Weighting Function
+(ref:weighting-function) Possible Graphical Shapes of Goldstein and Einhorn's -@goldsteinExpressionTheoryPreference1987 Weighting Function
 
-```{r w-shapes, fig.cap="(ref:weighting)", fig.height=7, fig.width=10}
+```{r weighting-function, fig.cap="(ref:weighting-function)", fig.height=7, fig.width=10}
+#compute images of weighting function (wf)
+wf <- tibble(p = seq(0, 1, .01)) %>%  #cumulative probabilities
+  expand_grid(gamma = seq(.1, 2, .1), #gamma values
+              delta = c(.1, .5, 1, 2, 5, 10)) %>% #delta values
+  mutate(wp = (delta*(p^gamma))/((delta*p^gamma)+(1-p)^gamma)) #images of wf
 
-# prepare vector with cumulative probabilities
-p <- tibble(p = seq(0, 1, .01))
-
-# compute weighting function for different combinations of gamma and delta 
-wf <- p %>% expand_grid(gamma = seq(.1, 2, .1), 
-                        delta = c(.1, .5, 1, 2, 5, 10)) %>%
-  mutate(wp = (delta*(p^gamma))/((delta*p^gamma)+(1-p)^gamma))
-
-# labeller function for LaTeX math expressions in facet labels 
-labeller_delta <- function(string) {
+#labeller function for facet labels with LateX math expressions 
+label_delta <- function(string) {
   TeX(paste("$\\delta=$", string, sep = ""))  
@@
 
-# plot
-ggplot(wf, aes(p, wp, group = gamma)) +
-  facet_wrap(~delta, labeller = as_labeller(labeller_delta, default = label_parsed)) + 
+#plot shapes of weighting function
+wf %>% 
+  ggplot(aes(p, wp, group = gamma)) +
+  facet_wrap(~delta, labeller = as_labeller(label_delta, default = label_parsed)) + 
   scale_x_continuous(breaks = seq(0, 1, .2)) +
@@
   scale_color_viridis(option = "plasma") + 
-  geom_abline(intercept = 0, slope = 1, color = "gray", linetype = "dashed") # identity line
+  geom_abline(intercept = 0, slope = 1, color = "gray", linetype = "dashed")
 ```
 
-In some more detail, the gray-dashed identity lines in Figure\ \@ref(fig:w-shapes) imply a linear weighting pattern.
+In some more detail, the gray-dashed identity lines in Figure\ \@ref(fig:weighting-function) imply a linear weighting pattern.
 That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are derived according to (12) would be equal to the differences between the respective objective cumulative probabilities and therefore also to the objective probabilities of the outcomes for which the weights are determined.
@@
 
-To demonstrate the impact of different sampling strategies on the inferences about the latent properties of prospects and the resulting choices in DfE, a simulation study was conducted.
-Therefore, computational models were implemented that generate and integrate samples from prospects according to varying parameters reflecting different sampling strategies.
-
 ## Choice Problems
 
-We test a set of 2-prospect choice problems, where one of the prospects contains a safe outcome, i.e., $p(\omega) = 1$ and the other two outcomes where all $p(\omega) \neq 1$.
-Both outcomes and probabilities are drawn from uniform distributions, ranging from 0 to 20 for outcomes and from .01 to .99 for probabilities of the smaller outcome of the risky prospect.
-To omit dominant prospects within a choice problem, outcomes of the safe prospect always fall between both outcomes of the risky prospect.
-Table A1 in contains the test set of 60 choice problems, which were sampled from an initial set of 10,000.
-Sampling of gambles was stratified, randomly drawing an equal number of 20 gambles with no, an attractive, and an unattractive rare outcome.
-Risky outcomes are considered *"rare"* if their probability is $p < .2$ and *"attractive"* (*"unattractive"*) if they are higher (lower) than the safe outcome.
-
-For each parameter combination of the generating model, 100 synthetic agents are presented with 60 choices problems.
-In sum, 100 (parameter combinations) x 100 (agents) x 60 (choices) = 600,000 choices are simulated.
+The test set of $60$ choice problems, each consisting of a safe prospect and a two-outcome prospect, was obtained by stratified sampling from an initial set of $10,000$ choice problems.
+The stratification was used to assure that some of the choice problems contain a small (high) outcome of a probability smaller than $.20$.
+The exact procedure was as follows:
+For each of the $10.000$ problems in the initial set, three outcomes were randomly drawn from a uniform distribution over the interval $[0, 20]$, with the smallest and highest of these three outcomes being assigned to the risky prospect in order to omit the case of dominant prospects.
+The probability for the smaller outcome of the risky prospect, $p_{small}$, was drawn from a uniform distribution over the interval $[.01, .99]$, with the probability of the higher outcome being set to $p_{high} = 1-p_{small}$.
+To obtain the $60$ choice problems of the test set, the initial set was divided into three subsets, where each subset contained either all problems with $p_{high} \in (0,.2)$ or $p_{high} \in [.2,.8]$ or $p_{high} \in (.8,1)$.
+From each of these subset, then, $20$ choice problems were randomly sampled.
 
@@
 
-The switching probability $s$ is the probability with which agents draw a single sample from the prospect they did not get their most recent single sample from.
-$s$ is varied between .1 to 1 in increments of .1.
-The two boundary parameters resemble the concept of a decision threshold, i.e., if a prospect reaches a boundary, it is chosen by the synthetic agent.
-The boundary type is either the minimum number of comparisons any prospect must win (absolute boundary) or the minimum difference between the number of won comparisons (relative boundary).
-The boundary value $a$ is varied between 1 to 5 in increments of 1.
+The evidence accumulation model presented in this paper was implemented as a computational model to simulate the sampling process and the final choice for each of the $60$ choice problems in the test set.
+All of the following parameter values were combined with each other:
+
+* **Switching probability**: 
+The switching probability $s$, defined as the probability of sampling outcomes from different prospects in direct succession, was varied in the interval $[.1, 1]$ in increments of $.1$.
+
+* **Decision variable**: The decision variable of a prospect either counts the absolute number of won comparisons or how much more comparisons were won relative to the other prospect.
+
+* **Threshold**: 
+The value of the threshold $\theta$, determining how much (more) comparisons a prospect must win, was varied in the interval $[1,5]$ in increments of 1.
+
+\noindent
+In sum, 100 (parameter combinations) x 60 (choices) x 100 (agents) = 600,000 sampling processes and choices were simulated.
 
@@
 
-(ref:fr-rates-p) Effect of Switching Probability on Rates of False Risky and False Safe Choices for 2-Outcome Prospects with High Rank Outcomes of Different Probability
-
-```{r fig.cap="(ref:fr-rates-p)", fig.height=7, fig.width=10}
-cols <- list(.default = col_double(),
+```{r data, include=FALSE}
+#load choice data
+cols_choices <- list(.default = col_double(),
                      boundary = col_factor(),
@@
                      choice = col_factor())
-choices_p <- read_csv("data/choices/choices.csv", col_types = cols) # piecewise integration
+choices <- read_csv("data/choices/choices.csv", col_types = cols_choices)
 
-# false response (fr) rates
+#load CPT estimates
+cols_cpt <- list(.default = col_double(),
+                 boundary = col_factor(),
+                 a = col_factor(),
+                 parameter = col_factor())
+cpt <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols_cpt)
+```
 
-## determine normative choice according to latent and sampled EV
-fr_rates_p <- choices_p %>%
-  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B"), # normative choice latent EV
+<!-- Plots choice rates -->
+
+(ref:choice-rates) Effect of Switching Probability on Rates of False Risky and False Safe Choices for 2-Outcome Prospects with High Rank Outcomes of Different Probability
+
+```{r choice-rates, fig.cap="(ref:choice-rates)", fig.height=7, fig.width=10}
+#prepare data
+
+##determine normative choice according to latent and sampled EV
+fr_rates <- choices %>%
+  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B"), #normative choice latent EV
          ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2),
-         norm_exp = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) # normative choice sampled EV
+         norm_exp = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) #normative choice sampled EV
 
-# fr rates latent EV
-fr_rates_p_o <- fr_rates_p %>%
-  filter(!is.na(norm)) %>% # exclude choices under EV equality
-  group_by(s, boundary, a, rare, norm, choice) %>% # to distinguish type of rare event and type of false response
-  summarise(n = n()) %>% # determine absolute number of responses per category
-  mutate(rate = round(n/sum(n), 2), # determine correct and false response rates
-         type = case_when(norm == "A" & choice == "B" ~ "Safe", norm == "B" & choice == "A" ~ "Risky")) %>% # type false response
+##compute false response rates
+
+###latent EV
+fr_rates_l <- fr_rates %>%
+  filter(!is.na(norm)) %>% #exclude trials with equal EV
+  group_by(s, boundary, a, rare, norm, choice) %>% #separate by model parameter and type of rare event
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), #compute response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", #determine false response type
+                          norm == "B" & choice == "A" ~ "Risky")) %>%
   ungroup() %>%
-  filter(!is.na(type)) %>% # remove correct response rates
+  filter(!is.na(type)) %>% #remove correct responses
   select(-c(norm, choice, n)) %>%
-  mutate(norm_ev = "Latent")
+  mutate(norm_ev = "Latent") #assign facet label
 
-# fr rates sampled EV
-fr_rates_p_e <- fr_rates_p %>%
+###sampled EV
+fr_rates_s <- fr_rates %>%
   filter(!is.na(norm_exp)) %>%
@@
   mutate(rate = round(n/sum(n), 2),
-         type = case_when(norm_exp == "A" & choice == "B" ~ "Safe", norm_exp == "B" & choice == "A" ~ "Risky")) %>%
+         type = case_when(norm_exp == "A" & choice == "B" ~ "Safe",
+                          norm_exp == "B" & choice == "A" ~ "Risky")) %>%
   ungroup() %>%
@@
 
-# merge data frame
-fr_rates_p <- bind_rows(fr_rates_p_o, fr_rates_p_e) %>%
-  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]",
+### merge latent and sampled data
+fr_rates <- bind_rows(fr_rates_l, fr_rates_s) %>%
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]", #change facet labels for rare events
                           rare == "attractive" ~ "\\in (0,.2)",
-                          rare == "unattractive" ~ "\\in (.8,1)")) # Change fact labels
+                          rare == "unattractive" ~ "\\in (.8,1)"))
 
-# labeller function for LaTeX math expressions in facet labels
-labeller_a <- function(string) {
-  TeX(paste("$\\a=$", string, sep = ""))
+# labeller functions
+label_theta <- function(string) {
+  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
 }
 
-labeller_rare <- function(string) {
-  TeX(paste("$\\p_{High}$", string, sep = ""))
+label_rare <- function(string) {
+  TeX(paste("$\\p_{High}$", string, sep = "")) #type of rare event
 }
 
-ggplot(fr_rates_p, aes(s, rate)) +
-  facet_grid(rare~a, labeller = labeller(rare = as_labeller(labeller_rare, default = label_parsed), a = as_labeller(labeller_a, default = label_parsed))) +
-  labs(x = "s",
-       y = "False Response Rate",
-       color = "Normative\nEV",
-       shape = "False\nResponse") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+#plot
+fr_rates %>%
+  ggplot(aes(s, rate)) +
+  facet_grid(rare~a, labeller = labeller(rare = as_labeller(label_rare, default = label_parsed), 
+                                         a = as_labeller(label_theta, default = label_parsed))) +
   labs(x = "Switching Probability",
@@
        shape = "False\nResponse\nType") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
   geom_point(aes(color = norm_ev, shape = type)) +
@@
 
-<!-- Test set-->
+<!-- Plots CPT -->
 
@@
 
-```{r fig.cap="(ref:weighting-parameters)", fig.height=7, fig.width=10}
+```{r weighting-parameters, fig.cap="(ref:weighting-parameters)", fig.height=7, fig.width=10}
+#prepare data
+cpt <- cpt %>% mutate(boundary = if_else(boundary == "absolute", "Absolute", "Relative"))
 
-# load data
+#plot estimates
 
-cols <- list(.default = col_double(),
-             boundary = col_factor(),
-             a = col_factor(),
-             parameter = col_factor())
-cpt_p <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols) # piecewise integration
-cpt_p <- cpt_p %>% mutate(boundary = if_else(boundary == "absolute", "Absolute", "Relative"))
-
-gamma <- cpt_p %>%
+##gamma
+gamma <- cpt %>%
   filter(parameter == "gamma") %>%
   ggplot(aes(s, mean, color = s, shape = boundary)) +
-  geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_color_viridis(option = "plasma") +
-  scale_shape_manual(values = c(4, 16)) +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
-  labs(x = "Switching Probability",
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
+  labs(x = element_blank(), #omit axis title
        y = expression(gamma),
@@
        shape = "Boundary") +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(labeller_a, default = label_parsed))) + 
-  theme_apa() + 
-  theme(axis.title.x = element_blank())
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_shape_manual(values = c(4, 16)) +
+  scale_color_viridis(option = "plasma") +
+  theme_apa()
 
-delta <- cpt_p %>%
+##delta
+delta <- cpt %>%
   filter(parameter == "delta") %>% 
   ggplot(aes(s, mean, color = s, shape = boundary)) +
-  geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_color_viridis(option = "plasma") +
-  scale_shape_manual(values = c(4, 16)) +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
   facet_wrap(~a, nrow = 1) + 
@@
        shape = "Boundary") +
-  theme_apa() + 
-  theme(strip.text.x = element_blank())
-
-ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
-```
-
-(ref:value-choice-parameters) Parameter Estimates of the Value Function of @tverskyAdvancesProspectTheory1992 and of the Logit Choice Rule for Different Simulation Parameters
-
-```{r fig.cap="(ref:value-choice-parameters)", fig.height=7, fig.width=10}
-
-alpha <- cpt_p %>%
-  filter(parameter == "alpha") %>% 
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
   geom_point() +
@@
   scale_shape_manual(values = c(4, 16)) +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
-  labs(x = "Switching Probability",
+  theme_apa() + 
+  theme(strip.text.x = element_blank()) #omit facet labels
+
+##merge figures
+ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
+```
+
+(ref:value-parameters) Parameter Estimates of the Value Function of @tverskyAdvancesProspectTheory1992 and of the Logit Choice Rule for Different Simulation Parameters
+
+```{r value-parameters, fig.cap="(ref:value-parameters)", fig.height=7, fig.width=10}
+#plot estimates
+
+##alpha
+alpha <- cpt %>%
+  filter(parameter == "alpha") %>% 
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
+  labs(x = element_blank(),
        y = expression(alpha),
@@
        shape = "Boundary") +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(labeller_a, default = label_parsed))) + 
-  theme_apa() + 
-  theme(axis.title.x = element_blank())
-
-rho <- cpt_p %>%
-  filter(parameter == "rho") %>% 
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
   geom_point() +
@@
   scale_shape_manual(values = c(4, 16)) +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1,.5)) +
+  theme_apa()
+
+##rho
+rho <- cpt %>%
+  filter(parameter == "rho") %>% 
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  facet_wrap(~a, nrow = 1) + 
   labs(x = "Switching Probability",
@@
        shape = "Boundary") +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(labeller_a, default = label_parsed))) + 
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1,.5)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_color_viridis(option = "plasma") +
+  scale_shape_manual(values = c(4, 16)) +
   theme_apa() + 
@@
 
+##merge figure
 ggarrange(alpha, rho, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
@@
 
-(ref:shapes) Estimated Graphical Shapes of the Weighting and Value Function for Different Simulation Parameters
+(ref:cpt-graphs) Estimated Graphical Shapes of the Weighting and Value Function for Different Simulation Parameters
 
-```{r fig.cap="(ref:shapes)", fig.height=7, fig.width=10}
+```{r cpt-graphs, fig.cap="(ref:cpt-graphs)", fig.height=7, fig.width=10}
+#prepare data
 
-## weighting function
+##compute images of weighting and value function
 
-wf_p <- cpt_p %>%
+###weighting function
+wf <- cpt %>%
   select(s, boundary, a, parameter, mean) %>%
@@
 
-wf_p_a <- wf_p %>%
-  filter(boundary == "Absolute")
-wf_p_r <- wf_p %>%
-  filter(boundary == "Relative")
-weight <- ggplot(wf_p_a, aes(x = p, y = w, group = s, color = s)) +
-  geom_line(size = .5) +
-  geom_line(data = wf_p_r, size = .5) + 
-  scale_color_viridis(option = "plasma") +
-  scale_x_continuous(breaks = seq(0, 1, .5)) +
-  scale_y_continuous(breaks = seq(0, 1, .5)) +
-  labs(x = "Experienced Probability",
-       y = "Decision Weight",
-       color = "Switching\nProbability") +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(labeller_a, default = label_parsed))) + 
-  theme_apa() + 
-  theme(strip.text.x = element_blank())
-
-vf_p <- cpt_p %>%
+###value function
+vf <- cpt %>%
   select(s, boundary, a, parameter, mean) %>%
@@
 
-vf_p_a <- vf_p %>%
-  filter(boundary == "Absolute")
-vf_p_r <- vf_p %>%
-  filter(boundary == "Relative")
-value <- ggplot(vf_p_a, aes(x = x, y = v, group = s, color = s)) +
+##split data to avoid passing two y-values to the same x-value in geom_line()
+wf_a <- wf %>% filter(boundary == "Absolute")
+wf_r <- wf %>% filter(boundary == "Relative")
+vf_a <- vf %>% filter(boundary == "Absolute")
+vf_r <- vf %>% filter(boundary == "Relative")
+
+#plots
+
+##weighting function
+weight <- wf_a %>% #graphs for absolute boundary
+  ggplot(aes(p, w, group = s, color = s)) +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  labs(x = "Experienced Probability",
+       y = "Decision Weight",
+       color = "Switching\nProbability") +
+  scale_x_continuous(breaks = seq(0, 1, .5)) +
+  scale_y_continuous(breaks = seq(0, 1, .5)) +
   geom_line(size = .5) +
-  geom_line(data = vf_p_r, size = .5) + 
+  geom_line(data = wf_r, size = .5) +  #add curves for relative boundary
   scale_color_viridis(option = "plasma") +
-  scale_x_continuous(breaks = seq(0, 20, 10)) +
-  scale_y_continuous(breaks = seq(0, 20, 10)) +
+  theme_apa()
+
+##value function
+value <- vf_a %>% 
+  ggplot(aes(x, v, group = s, color = s)) +
+  facet_wrap(~a, nrow = 1)+ 
   labs(x = "Objective Outcome",
@@
        color="Switching\nProbability") +
-  facet_wrap(~a, nrow = 1)+ 
+  scale_x_continuous(breaks = seq(0, 20, 10)) +
+  scale_y_continuous(breaks = seq(0, 20, 10)) +
+  geom_line(size = .5) +
+  geom_line(data = vf_r, size = .5) + 
+  scale_color_viridis(option = "plasma") +
   theme_apa() + 
@@
 
+##merge figures
 ggarrange(weight, value, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
-```
-
-```{r}
-
-# read cpt data
-
-cols <- list(.default = col_double(),
-             boundary = col_factor(),
-             a = col_factor(),
-             parameter = col_factor())
-cpt_long <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols)
-
-# store convergence diagnostics
-
-gel_92 <- cpt_long %>% select(s, boundary, a, parameter, Rhat, n.eff) 
 ```
@@
 To reduce potential autocorrelation during the sampling process, we only kept every 20th sample (thinning).
-The potential scale reduction factor $\hat{R}$ [@gelmanInferenceIterativeSimulation1992] was $\leq$ `r round(max(gel_92$Rhat), 3)` for all parameters, indicating good convergence.
-The minimum effective sample size was `r min(gel_92$n.eff)`.
+The potential scale reduction factor $\hat{R}$ [@gelmanInferenceIterativeSimulation1992] was $\leq$ `r round(max(cpt$Rhat), 3)` for all parameters, indicating good convergence.
+The minimum effective sample size was `r min(cpt$n.eff)`.
 
-<!-- Plausibility Check: Relationship between Switching Probability and Trial Length -->
-
-```{r include=FALSE}
-
-# read choice data
-
-cols <- list(.default = col_double(),
-             boundary = col_factor(),
-             gamble = col_factor(),
-             rare = col_factor(),
-             agent = col_factor(),
-             choice = col_factor())
-choices <- read_csv("data/choices/choices.csv", col_types = cols)
-
-# get median trial length for each parameter combination
-trial_length <- choices %>% 
-  group_by(s, boundary, a) %>% 
-  summarise(med = median(n_sample))
-```
-
-The median length of trials, i.e., the number of single samples drawn in a trial, generated by different parameter combinations ranged from `r min(trial_length$med)` to `r max(trial_length$med)`.
 As expected, the scatter plot below shows an inverse relationship between switching probability and trial length.
@@
 This effect is particularly pronounced for low probabilities such that the increase in trial length accelerates as switching probability decreases.
-
-```{r eval=FALSE}
-
-# get median trial length for each switching probability
-
-trial_length_s <- choices %>% 
-  group_by(s) %>%
-  summarise(med = median(n_sample))
-
-# plot
-
-trial_length %>%
-  ggplot(aes(x = s, y = med)) +
-  geom_jitter(color = "#CECECE", size = 3) +
-  geom_point(data = trial_length_s, aes(color = s), size = 3) +
-  geom_path(data = trial_length_s, aes(color = s)) +
-  scale_color_scico(palette = "acton") + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) + 
-  scale_y_continuous(breaks = seq(0, 120, 10)) +
-  labs(title = "Trial Length", 
-       x ="Switching Probability",
-       y = "Median Trial Length", 
-       color="Switching Probability") + 
-  theme_apa()
-```
-
-<!-- Weighting function -->
-
-```{r eval=FALSE}
-
-# tidy CPT data: parameters as separate columns
-
-cpt_wide <- cpt_long %>% 
-  select(s, boundary, a, parameter, mean) %>% 
-  pivot_wider(names_from = parameter, values_from = mean)
-```
 
@@
 
-```{r eval=FALSE}
-cpt_long %>% 
-  filter(parameter == "delta", a!= 1) %>% 
-  ggplot(aes(x=s, y = mean, color = s)) +
-  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  geom_point(size = 2) +
-  scale_color_scico(palette = "acton") + 
-  scale_x_continuous(breaks = seq(0,1,.2)) +
-  facet_grid(boundary~a) + 
-  theme_minimal() 
+<!-- Plots Appendix -->
+
+```{r A-data, include=FALSE}
+#load choice data
+choices_c <- read_csv("data/choices/choices_comprehensive.csv", col_types = cols_choices)
+cpt_c <- read_csv("data/estimates/estimates_cpt_comprehensive.csv", col_types = cols_cpt)
 ```
 
-```{r eval=FALSE}
+```{r A-choice-rates, fig.height=7, fig.width=10, include=FALSE}
+#prepare data
+fr_rates_c <- choices_c %>%
+  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B"),
+         ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2),
+         norm_exp = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B"))
 
-# Density Plot
+fr_rates_c_l <- fr_rates_c %>%
+  filter(!is.na(norm)) %>%
+  group_by(s, boundary, a, rare, norm, choice) %>% 
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2),
+         type = case_when(norm == "A" & choice == "B" ~ "Safe",
+                          norm == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>%
+  select(-c(norm, choice, n)) %>%
+  mutate(norm_ev = "Latent")
 
-cpt_long %>% 
-  filter(parameter == "gamma" | parameter == "delta") %>% 
-  ggplot(aes(x = s, y = mean)) +
-  geom_density_2d_filled(contour_var = "ndensity") + 
-  scale_fill_scico_d(palette = "acton") +
-  scale_color_scico_d(palette = "acton") + 
-  scale_x_continuous(breaks = seq(0, 1, .2)) + 
-  scale_y_continuous(limits = c(0,2), breaks = seq(0, 2, .2)) +
-  labs(x ="Switching Probability",
-       y = "Parameter Value",  
-       fill="Density") + 
-  facet_grid(parameter~a) + 
+fr_rates_c_s <- fr_rates_c %>%
+  filter(!is.na(norm_exp)) %>%
+  group_by(s, boundary, a, rare, norm_exp, choice) %>%
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2),
+         type = case_when(norm_exp == "A" & choice == "B" ~ "Safe",
+                          norm_exp == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>%
+  select(-c(norm_exp, choice, n)) %>%
+  mutate(norm_ev = "Sample")
+
+fr_rates_c <- bind_rows(fr_rates_c_l, fr_rates_c_s) %>%
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]",
+                          rare == "attractive" ~ "\\in (0,.2)",
+                          rare == "unattractive" ~ "\\in (.8,1)"))
+
+fr_rates_c %>%
+  ggplot(aes(s, rate)) +
+  facet_grid(rare~a, labeller = labeller(rare = as_labeller(label_rare, default = label_parsed), 
+                                         a = as_labeller(label_theta, default = label_parsed))) +
+  labs(x = "Switching Probability",
+       y = "False Response Rate",
+       color = "Normative\nExpected\nValue",
+       shape = "False\nResponse\nType") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  geom_point(aes(color = norm_ev, shape = type)) +
+  scale_shape_manual(values = c(4, 16)) +
+  scale_color_viridis_d(option = "plasma", end = .7) +
   theme_apa()
@@
 
-```{r eval=FALSE}
+```{r A-weighting-parameters, fig.height=7, fig.width=10, include=FALSE}
+#prepare data
+cpt_c <- cpt_c %>% mutate(boundary = if_else(boundary == "absolute", "Absolute", "Relative"))
 
-# Scatter Plots
+#plot estimates
 
-# Gamma
+##gamma
+gamma_c <- cpt_c %>%
+  filter(parameter == "gamma") %>%
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
+  labs(x = element_blank(),
+       y = expression(gamma),
+       color = "Switching\nProbability",
+       shape = "Boundary") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_shape_manual(values = c(4, 16)) +
+  scale_color_viridis(option = "plasma") +
+  theme_apa()
 
-cpt_wide %>% 
-  ggplot(aes(x = s, y = gamma, color = s)) +
-  geom_point(size = 2) +
-  geom_line(size = 1) +
-  scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .2)) + 
-  scale_y_continuous(breaks = seq(0, 2, .2)) +
-  facet_grid(boundary~a) +
-  labs(title = expression(paste("Curvature ", gamma)),
-       x ="Switching Probability",
-       y = expression(gamma), 
-       color="Switching Probability") + 
-  theme_minimal()
+##delta
+delta_c <- cpt_c %>%
+  filter(parameter == "delta") %>% 
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  facet_wrap(~a, nrow = 1) + 
+  labs(x = "Switching Probability",
+       y = expression(delta),
+       color = "Switching\nProbability",
+       shape = "Boundary") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_color_viridis(option = "plasma") +
+  scale_shape_manual(values = c(4, 16)) +
+  theme_apa() + 
+  theme(strip.text.x = element_blank()) #omit facet labels
 
-# Delta
-
-cpt_wide %>% 
-  ggplot(aes(x = s, y = delta, color = s)) +
-  geom_point(size = 2) +
-  geom_line(size = 1) +
-  scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .2)) + 
-  scale_y_continuous(breaks = seq(0, 2, .2)) +
-  facet_grid(boundary~a, switch = "y") +
-  labs(title = expression(paste("Curvature ", delta)),
-       x ="Switching Probability",
-       y = expression(delta), 
-       color="Switching Probability") + 
-  theme_minimal()
+##merge figures
+ggarrange(gamma_c, delta_c, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
 ```
 
-Below, the resulting probability weighting functions are displayed.
+```{r A-value-parameters, fig.height=7, fig.width=10, include=FALSE}
+#plot estimates
 
-```{r eval=FALSE}
+##alpha
+alpha_c <- cpt_c %>%
+  filter(parameter == "alpha") %>% 
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
+  labs(x = element_blank(),
+       y = expression(alpha),
+       color = "Switching\nProbability",
+       shape = "Boundary") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_color_viridis(option = "plasma") +
+  scale_shape_manual(values = c(4, 16)) +
+  theme_apa()
 
-# Weighting Functions
+##rho
+rho_c <- cpt_c %>%
+  filter(parameter == "rho") %>% 
+  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  facet_wrap(~a, nrow = 1) + 
+  labs(x = "Switching Probability",
+       y = expression(rho),
+       color = "Switching\nProbability",
+       shape = "Boundary") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1,.5)) +
+  geom_point() +
+  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  scale_color_viridis(option = "plasma") +
+  scale_shape_manual(values = c(4, 16)) +
+  theme_apa() + 
+  theme(strip.text.x = element_blank())
 
-## compute decision weights
-
-cpt_w <- cpt_wide %>% 
-  select(-c(alpha, rho)) %>% 
-  expand_grid(ep = seq(0, 1, .1)) %>% #
-  mutate(w = round(  (delta * ep^gamma)/ ((delta * ep^gamma)+(1-ep)^gamma), 2))
-
-## plot curves
-
-cpt_w %>% 
-  group_by(boundary, a, s) %>% 
-  ggplot(aes(x = ep, y = w, color = s)) +
-  geom_path() + 
-  scale_color_scico(palette = "tokyo") + 
-  scale_x_continuous(breaks = seq(0, 1, .2)) +
-  scale_y_continuous(breaks = seq(0, 1, .2)) + 
-  labs(x ="Experienced Probability",
-       y = "Probability Weighting", 
-       color="Switching Probability") + 
-  theme_minimal()
-
-cpt_w %>% 
-  group_by(boundary, a, s) %>% 
-  ggplot(aes(x = ep, y = w, color = s)) +
-  geom_path(size = 1) + 
-  scale_color_scico(palette = "tokyo") + 
-  scale_x_continuous(breaks = seq(0, 1, .2)) +
-  scale_y_continuous(breaks = seq(0, 1, .2)) + 
-  facet_grid(boundary~a) +
-  labs(x ="Experienced Probability",
-       y = "Probability Weighting", 
-       color="Switching Probability") + 
-  theme_dark()
+##merge figure
+ggarrange(alpha_c, rho_c, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
 ```
 
-The false response rates for different parameter values of the generating model reflect the probability weighting patterns from above. 
-That is, the strong curvature resulting from large switching probabilities produces an underweighting of small probabilities.
-This in turn has the effect that the rarity of an attractive (unattractive) outcome leads to higher rates of choosing the safe (risky) prospect although the risky (safe) prospect had a higher experienced expected value.
+```{r A-cpt-graphs, fig.height=7, fig.width=10, include=FALSE}
+#prepare data
 
-```{r eval=FALSE}
+##compute images of weighting and value function
 
-# compute false response rates
+###weighting function
+wf_c <- cpt_c %>%
+  select(s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
+  select(-c(alpha, rho)) %>%
+  expand_grid(p = seq(0, 1, .05)) %>%
+  mutate(w = round(  (delta * p^gamma)/ ((delta * p^gamma)+(1-p)^gamma), 2))
 
-fr_rates <- choices %>% 
-  mutate(ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2), # experienced EV (eEV)
-         norm = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) %>% # normative choice according to eEV
-  filter(!is.na(norm)) %>% # exclude trials with normative indifferent prospects
-  group_by(s, boundary, a, rare, norm, choice) %>% # group correct and incorrect responses
-  summarise(n = n()) %>% # absolute numbers 
-  mutate(rate = round(n/sum(n), 2), # response rates 
-         type = case_when(norm == "A" & choice == "B" ~ "false safe", norm == "B" & choice == "A" ~ "false risky")) %>% filter(!is.na(type))  # remove correct responses
-
-# violin scatter plot
-
-fr_rates %>% 
-  ggplot(aes(x = rare, y = rate, color = s)) +
-  geom_quasirandom(aes(shape = type), size = 3) +  
-  scale_y_continuous(breaks = seq(0, 1, .2)) +
-  scale_color_scico(palette = "buda") + 
-  scale_shape_manual(values=c(8, 16))+
-  labs(x = "Rare Event", 
-       y = "False Response Rate", 
-       color = "Switching Probability",
-       shape = "False Response") + 
-  theme_minimal() 
-```
-
-```{r eval=FALSE}
-fr_rates %>% 
-  ggplot(aes(a, s, fill = rate)) + 
-  geom_tile(colour="white", size=0.1) +
-  scale_fill_scico(palette = "buda") + 
-  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
-  scale_x_continuous(expand=c(0,0), breaks = seq(1, 5, 1)) +
-  scale_y_continuous(expand=c(0,0), breaks = seq(.1, 1, .1)) +
-  labs(title = "False Response Rates", 
-       x = "a", 
-       y= "s", 
-       fill = "% False Responses") + 
-  theme_minimal()
-
-fr_rates %>% 
-  ggplot(aes(s, rate, color = s)) + 
-  facet_grid(type ~ fct_relevel(rare, "attractive", "none", "unattractive"), switch = "y") +
-  geom_jitter(size = 3) + 
-  scale_x_continuous(breaks = seq(0, 1, .1)) +
-  scale_y_continuous(breaks = seq(0, 1, .1)) +
-  scale_color_scico(palette = "buda") + 
-  labs(title = "False Response Rates", 
-       x = "s", 
-       y= "% False Responses", 
-       color = "a") + 
-  theme_minimal()
-```
-
-<!-- Weighting function -->
-
-```{r eval=FALSE}
-
-# Density Plot
-
-cpt_wide %>%
-  ggplot(aes(x = s, y = alpha)) +
-  geom_density_2d_filled(contour_var = "ndensity") + 
-  scale_fill_scico_d(palette = "grayC") +
-  scale_x_continuous(breaks = seq(0, 1, .2)) + 
-  scale_y_continuous(limits = c(0,2), breaks = seq(0, 2, .2)) +
-  labs(x ="Switching Probability",
-       y = "Parameter Value",  
-       fill="Density") + 
-  facet_wrap(~a, nrow = 1) + 
-  theme_minimal()
-```
-
-```{r eval=FALSE}
-# value function
-
-## compute values
-
-cpt_v <- cpt_wide %>% 
+###value function
+vf_c <- cpt_c %>%
+  select(s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
   select(-c(gamma, delta, rho)) %>%
-  expand_grid(x = seq(0, 20, 2)) %>%  
+  expand_grid(x = seq(0, 20, .5)) %>%  
   mutate(v = round(x^alpha, 2))
 
-## plot curves
+##split data to avoid passing two y-values to the same x-value in geom_line()
+wf_c_a <- wf_c %>% filter(boundary == "Absolute")
+wf_c_r <- wf_c %>% filter(boundary == "Relative")
+vf_c_a <- vf_c %>% filter(boundary == "Absolute")
+vf_c_r <- vf_c %>% filter(boundary == "Relative")
 
-cpt_v %>% 
-  group_by(boundary, a, s) %>% 
-  ggplot(aes(x = x, y = v)) +
-  geom_path(aes(color = s)) +
-  scale_color_scico(palette = "grayC") + 
-  scale_x_continuous(breaks = seq(0, 20, 5)) +
-  scale_y_continuous(breaks = seq(0, 20, 5)) + 
-  labs(title = "Value Function",
-       x ="Objective Value",
+#plots
+
+##weighting function
+weight_c <- wf_c_a %>% 
+  ggplot(aes(p, w, group = s, color = s)) +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  labs(x = "Experienced Probability",
+       y = "Decision Weight",
+       color = "Switching\nProbability") +
+  scale_x_continuous(breaks = seq(0, 1, .5)) +
+  scale_y_continuous(breaks = seq(0, 1, .5)) +
+  geom_line(size = .5) +
+  geom_line(data = wf_c_r, size = .5) + 
+  scale_color_viridis(option = "plasma") +
+  theme_apa()
+
+##value function
+value_c <- vf_c_a %>% 
+  ggplot(aes(x, v, group = s, color = s)) +
+  facet_wrap(~a, nrow = 1)+ 
+  labs(x = "Objective Outcome",
        y = "Subjective Value",
-       color="Switching Probability") + 
-  theme_minimal()
+       color="Switching\nProbability") +
+  scale_x_continuous(breaks = seq(0, 20, 10)) +
+  scale_y_continuous(breaks = seq(0, 20, 10)) +
+  geom_line(size = .5) +
+  geom_line(data = vf_c_r, size = .5) + 
+  scale_color_viridis(option = "plasma") +
+  theme_apa() + 
+  theme(strip.text.x = element_blank())
 
-cpt_v %>% 
-  group_by(boundary, a, s) %>% 
-  ggplot(aes(x = x, y = v)) +
-  geom_path(aes(color = s)) +
-  scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 20, 5)) +
-  scale_y_continuous(breaks = seq(0, 20, 5)) + 
-  facet_wrap(~a) +
-  labs(title = "Value Function",
-       x ="Objective Value",
-       y = "Subjective Value", 
-       color="Switching Probability") + 
-  theme_minimal()
+##merge figures
+ggarrange(weight_c, value_c, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
 ```
-
-```{r eval=FALSE}
-
-# alpha
-cpt_wide %>% 
-  ggplot(aes(x = s, y = alpha, color = s)) +
-  geom_point(size = 2) +
-  geom_line(size = 1) +
-  scale_color_scico(palette = "buda") + 
-  scale_x_continuous(breaks = seq(0, 1, .2)) + 
-  scale_y_continuous(breaks = seq(0, 2, .2)) +
-  facet_grid(boundary~a, switch = "y") +
-  labs(title = expression(alpha),
-       x ="Switching Probability",
-       y = expression(alpha), 
-       color="Switching Probability") + 
-  theme_minimal()
-```
-
-<!-- Old
-
-Given that the choice is perfectly systematic---as opposed to random or noisy---the chosen alternatives in $I'$ should share some property or combination of several properties which the other alternatives in the complementary subset $I \setminus I'$ do not possess.
-In the following, I will refer to statements about properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
-
-Often, however, the properties used by the mind to make a choice are not readily described and cannot be directly evaluated [cf.
-@brunswikRepresentativeDesignProbabilistic1955; see @brunswikPerceptionRepresentativeDesign1956, for a detailed treatment]; rather, proper descriptions must be inferred from whatever information the inputs provide about the properties of choice alternatives, using transformation rules, statistical generalizations, or both.
-Since how the inputs are represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information, the feasibility and ease of these inferences depends greatly on the choice of *representation* [@marrVisionComputationalInvestigation1982; see also, e.g., @gigerenzerHowImproveBayesian1995; @griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
-Hence, to explain how the mind makes a selection among choice alternatives, one needs to understand the output controlling properties, i.e., the applied selection criteria, the representation that is used to describe these properties, and the costs of inferring the descriptions in that representation, including their susceptibility to distortions from uncertainty or noise.
-The process is sketched in Figure 1.
-
-(ref:figure1) A rough computational level sketch of decision making as an information processing problem.
-To make a selection among choice alternatives on the basis of particular selection criteria, the mind requires explicit descriptions of the relevant properties before they can be evaluated.
-Descriptions are either readily available or must be inferred from the inputs.
-
-```{r fig.cap= "(ref:figure1)"}
-knitr::include_graphics("images/dm-sketch.png")
-```
-
-In what follows, the paper elaborates on the concepts touched upon thus far, certainly only a subset of the factors involved in the decision making process, yet central enough to illustrate a rather important principle:
-Given that the mind is indeed sensitive to variations in the property values, the more accurately their descriptions are inferred, the more systematic the choices should become.
-Importantly, this principle is not restricted to any one specific property. 
-Rather, each selection criterion or combination thereof imposes constraints on the assessment of choice alternatives, leading to characteristic choice patterns that are eventually blurred by inaccurate property descriptions.
-
-For the sake of example, I argue that a choice pattern robustly emerging in *decisions from experience* (DfE), the apparent underweighting of small probability events [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; see also @wulffMetaanalyticReviewTwo2018, for a meta-analytic review], may be caused by the assessment constraints associated with a round-wise decision strategy.
-This particular claim has already been made by @hillsInformationSearchDecisions2010 and follows quite directly from probability theory.
-However, the current paper suggests to subordinate decision strategies to the adoption of selection criteria and addresses in some detail two "problems" in the context of DfE, in which descriptions of the properties of choice alternatives must be inferred from sampling data.
-
-For one, there is an *induction problem*, well known from inferential statistics, according to which the sample size determines the margin of error within which any true property of a choice alternative can be inferred, given an otherwise perfect inference process.
-Yet, it follows that if an underweighting pattern is caused by the adoption of an arbitrary selection criterion, it is *a priori* predicted to become more stable with increasing sample size. 
-This prediction is in line with the principle already stated above, i.e., that selection-criteria-induced choice patterns should become more systematic as property descriptions become more accurate.
-Nevertheless, the prediction contrasts the explanation that underweighting is caused by the reliance on small samples [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @rakowBiasedSamplesNot2008], highlighting that outside of the *statistical* models used to describe the choice data, *causal* decision making models of quite different nature may be at play, and that a rather important difference between these causal models resides in the selection criteria they incorporate.
-I will elaborate on this matter as I proceed, however, to be clear from the outset, what the mind does in neither case is performing a probability weighting computation in its literal sense, but it processes the inputs in a way that the outputs approximate the solutions of what can be considered probability weighting on an abstract computational level [cf., e.g., @griffithsRationalUseCognitive2015].
-
-For another, this paper approaches the problem of organizing the sampling data in such a way that it allows chains of inferences connecting the input set $I$ with the output set $I' \subset I$ that are algorithmically short and simple enough to be carried out by minds whose cognitive capacities are bounded [cf.
-@simonInvariantsHumanBehavior1990; @simonBehavioralModelRational1955].
-This may be considered a *representation problem* since the inference chains are constructed around explicit descriptions of the properties of choice alternatives and representations are the "formal schemes" of symbols and rules with which these descriptions are derived [@marrRepresentationRecognitionSpatial1978, p.
-270].
-Specifically, representations differ in how they organize the information used to infer the descriptions of certain properties and these organizations determine the algorithms that can be built into the inference chain [@marrVisionComputationalInvestigation1982].
-In this paper, *sampling strategies* in DfE are considered as representation systems used to organize the samples in a way that subserves the property inferences required by the application of particular selection criteria.
-Though most of my expositions on the role of sampling strategies remain speculative, the core idea is not new to decision research [see, e.g., @hillsInformationSearchDecisions2010; @wulffHowShortLongrun2015].
-By restating this idea and adopting some terms and concepts that have well defined meaning in math and cognitive science, I hope to integrate it into the rich study of the computationally limited mind as an adaptive cognitive system whose processes interact with the information structures in the environment or memory.
-
-The theoretical arguments sketched in this introduction are substantiated by a simulation study. 
-For this purpose, the sampling and decision making processes are implemented in a computational model to simulate choice data from DfE.
-The simulated data is modeled in cumulative prospect theory (CPT), a data model commonly used for describing decisions under risk and uncertainty [@goldsteinExpressionTheoryPreference1987; see also @tverskyAdvancesProspectTheory1992].
-All simulations and analyses are reproducible---materials and instructions can be found on the GitHub repository.
-
-# Inputs to the Decision Making Process and Property Descriptions
-
-By defining decision making as an information processing problem whose solution requires a selection among choice alternatives of the form described in (1), much weight is given to the properties of choice alternatives---whatever those may be for the moment---since it is only through them that any necessary distinction between the alternatives or collections thereof can be made.
-To stress this point, consider the power set $\mathcal{P}(I)$, which is the set of all possible subsets of $I$ (see example in Figure 2).
-
-(ref:figure2) A.
-The power set of the set $I$ including the choice alternatives A, B, and C.
-Black (white) circles indicate that an alternative does (not) possess a property.
-Each column displays a possible subset that could result from assessing whether the alternatives posses a relevant property.
-The properties determine the various relations among the choice alternatives.
-Note that properties resulting in the empty set $\{\}$ and the subset $\{A,B,C\}$ do not discriminate between choice alternatives.
-B.
-A Venn diagram visualizing the inclusion map $\iota : I' \mapsto I$.
-$\iota$ maps every element $i$ of the subset $I'$ to its image $i$, treated as element of the superset $I$.
-
-```{r fig.cap= "(ref:figure2)"}
-knitr::include_graphics("images/power-set.png")
-```
-
-Each of the subsets $I' \in \mathcal{P}(I)$ corresponds to a possible distinction between the choice alternatives in $I$ that could result from assessing for each alternative whether it possesses an arbitrary property (collection) or not [cf.
-@jostMathematicalConcepts2015, p.
-16].
-The concept of the power set thereby illustrates how different selection criteria can alter the consequential choice.
-That is, in rather abstract terms, selection criteria are statements regarding the properties of choice alternatives that the mind evaluates as either true or false during the decision making process; accordingly, the subset $I'$ only contains the alternatives for which the statement is evaluated to be true.
-It follows that if there is some variance in the properties across choice alternatives and the properties are not perfectly correlated, changing the selection criteria can eventually change the subset $I'$.
-
-## What Are the Choice Alternatives and Their Properties?
-
-Given (3), it is evident that the prospects can only be distinguished by the elements of their tuples. 
-These elements are, generally speaking, symbols, some of which describe properties on their own, e.g., the outcome $\omega$, whereas other properties can only be described by collections of symbols, e.g., the sample space $\Omega$ by a set of outcomes as in (2.1), or more complex combinations thereof, e.g., the weighted average which is obtained by first multiplying all outcomes in $\Omega$ by their respective probabilities in $P$ and then summing the resulting products.^[I do not refer to this quantity as expected value, since the term is reserved for random variables, which were not introduced so far.]
-In turn, for choices between prospects, selection criteria are statements about the elements of their tuples that are true or false and these statements imply relations among prospects that are at least nominal, but may also draw on other levels of measurement.
-
-## Inferring Property Descriptions from Sampling Data
-
-Note that a selection criterion may refer to a property for which the raw input, i.e., the symbols, their organization, and the information they encode, do not yet provide an explicit description.
-Even more so, it has been repeatedly stated that for quite many decisions the mind faces, it is simply not possible to draw on direct descriptions of the properties, since they are part of the distal environment  [e.g., @brunswikOrganismicAchievementEnvironmental1943; @fiedlerExplainingSimulatingJudgment1996; @hertwigDescriptionexperienceGapRisky2009; see also @brunswikRepresentativeDesignProbabilistic1955; @brunswikPerceptionRepresentativeDesign1956; @kozyrevaInterpretationUncertaintyEcological2021].
-In either case, some form of description must be inferred from whatever information the input provides about the property in question.
-Consider first the counterfactual case of the prospect whose tuple is not part of the distal environment but is directly described. 
-Since all information about the prospect is given, one may in principle consider the input complete, yet, 
-the tuple implies properties of the prospect which are not explicitly described.
-For example, to obtain the description of the prospect's weighted average, still a calculus according to the algebraic rules described in the preceding paragraph must be carried out. 
-In general, in cases like the one just considered, where the properties are not distal and all information about them is available, property inferences take the form of a mere transformation, where the symbols from the input are ordered and combined according to some transformation rules [cf.
-@marrVisionComputationalInvestigation1982, p.
-20].
-
-In natural world decisions, however, the properties of choice alternatives are often distal and amenable only through their probabilistic relation to proximal cues or samples, which provide the input to the decision making process [cf.
-@brunswikOrganismicAchievementEnvironmental1943].
-Such a proximal information basis is obtained by experience or, more technically, by *sampling*, and is neither consistent nor complete but varies in its degree of representativeness. 
-In turn, the mind is not merely required to transform the inputs but to draw inductive inferences to arrive at property descriptions which then, by definition, are only probable. 
-Importantly, the probability, or accuracy, of the description depends on both the sampling process that determines the representativeness of the sample and the use of the probabilistic information that is entailed in the sample [e.g., @fiedlerBewareSamplesCognitiveecological2000].
-
-To adapt (3) for the case of decisions from experience [@hertwigDecisionsExperienceEffect2004], the tuples $(\Omega, \mathcal{F}, P)$ must be replaced by samples, which in this paper are treated as collections of independent and identically distributed (i.i.d.) random variables $X$.^[Note that this paper considers the counterfactual case where samples are random, although it has been stated that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
-660].
-To account for non-random sampling, e.g., in the form of sampling biases [e.g., @fiedlerBewareSamplesCognitiveecological2000] or dynamic information structures [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], the i.i.d-assumption would need to be dropped, which is out of the scope of this paper.]
-Specifically, random variables are defined as a measurable function
-
-$$
-X: (\Omega, \mathcal{F})  \mapsto (\Omega', \mathcal{F'}) 
-\; ,
-\tag{4}
-$$
-
-where $\Omega'$ is a set of real numbered values $X$ can take and $\mathcal{F'}$ is a set of subsets of $\Omega'$. 
-I.e., $\Omega$ maps into $\Omega'$ such that correspondingly each subset $A' \in \mathcal{F'}$ has a pre-image $X^{-1}A' \in \mathcal{F}$, which is the set $\{\omega \in \Omega: X(\omega) \in A'\}$ [@kolmogorovFoundationsTheoryProbability1950, p.
-21].
-
-$$
-\begin{aligned}
-  & \iota : I' \mapsto I, \ \text{where} \ I = \{X_{1i}, ..., X_{ki}\} \\
-  & i \in \{1, ..., N\} 
-  \; .
-\end{aligned}
-\tag{5}
-$$
-
-To provide a formal definition of sampling in risky choice, we make use of the mathematical concept of a random variable and start by referring to a prospect as *"risky"* in the case where $p(\omega) \neq 1$ for all $\omega \in \Omega$.
-Here, risky describes the fact that if agents would choose a prospect and any of its outcomes in $\Omega$ must occur, none of these outcomes will occur with certainty. 
-It is acceptable to speak of the occurrence of $\omega$ as a realization of a random variable $X$ defined on a prospect iff the following conditions (1) and (2) are met:
-
-(2) The mapping is such that $X(\omega) = x \equiv \omega$.
-
-In (2), $x \equiv \omega$ means that the realization of a random variable $X(\omega) = x$ is numerically equivalent to its pre-image $\omega$.  
-Given conditions (1) and (2), we denote any observation of $\omega$ as a *"single sample"*, or realization, of a random variable defined on a prospect and the act of generating a sequence of single samples in discrete time as *"sequential sampling"*.
-Note that, since random variables defined on the same prospect are independent and identically distributed (iid), the weak law of the large number applies to the relative frequency of occurrence of an outcome $\omega$ in a sequence of single samples originating from the same prospect.
-Thus, long sample sequences in principle allow to obtain the same information about a prospect by sampling as by symbolic description.
-
-Consider now a choice between prospects $1, ..., k$.
-To construct a stochastic sampling model for DfE, we assume that agents base their decision on the information related to these prospects and define a decision variable as a function of the latter:
-
-$$
-D:= f((\Omega_1, \mathcal{F}_1, P_1), ..., (\Omega_k, \mathcal{F}_k, P_k))
-\;.
-$$
-
-Now, since in DfE no symbolic descriptions of the prospects are provided, the model must be restricted to the case where decisions are based on sequences of single samples originating from the respective prospects:
-
-$$
-D := f(X_{i1}, ..., X_{ik}) 
-\; ,
-$$
-
-where $i \in \{1, ..., N\}$ denotes a sequence of length $N$ of random variables that are iid.
-
-Concerning the form of $f$ and the measures it utilizes, it is quite proper to say that they reflect our assumptions about the exact kind of information agents process and the way they do and that these choices should be informed by psychological theory and empirical protocols.
-Taking the case of different sampling and decision strategies previously assumed to play a role in DfE, the following section demonstrates how such assumptions can be explicated in a stochastic model that builds on the sampling approach outlined so far.
-
--->
 
@@
 # References
-
-<div id="refs"></div>
-
-\newpage
-
-# Appendix

### 2022-03-11 manuscript_appendix.Rmd
Add appendix with anlyses of comprehensive simulation

```{r A-setup, include=FALSE}
knitr::opts_chunk$set(echo = F, #omit messages
                      fig.align = "l", #align figures to left margin
                      fig.pos = "t")
```

\begin{figure}
\caption{Effect of Switching Probability on Rates of False Risky and False Safe Choices for 2-Outcome Prospects with High Rank Outcomes of Different Probability}\label{fig:A-choice-rates}
\includegraphics{manuscript_files/figure-latex/A-choice-rates-1}
\textit{Note.} A note.
\end{figure}

\newpage

\begin{figure}
\caption{Parameter Estimates of the Weighting Function of Goldstein and Einhorn (1987) for Different Simulation Parameters}\label{fig:A-weighting-parameters}
\includegraphics{manuscript_files/figure-latex/A-weighting-parameters-1}
\end{figure}

\newpage

\begin{figure}
\caption{Parameter Estimates of the Value Function of Tversky and Kahneman (1992) and of the Logit Choice Rule for Different Simulation Parameters}\label{fig:A-value-parameters}
\includegraphics{manuscript_files/figure-latex/A-value-parameters-1}
\end{figure}

\newpage

\begin{figure}
\caption{Estimated Graphical Shapes of the Weighting and Value Function for Different Simulation Parameters}\label{fig:A-cpt-graphs}
\includegraphics{manuscript_files/figure-latex/A-cpt-graphs-1}
\end{figure}

### 2022-03-11 manuscript.Rmd
Review introduction

@@
 Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in past decisions.
-The inputs to DfE therefore take the form of sets of sampled outcomes (hereafter: samples).^[<!--Open footnote-->Note that a sample is defined as a set of sampled outcomes.
-Aside empty and infinite sets, a sample can therefore contain one or finite many sampled outcomes (see also below).<!--Close footnote-->]
+The inputs to DfE therefore take the form of sets of sampled outcomes (hereafter: samples).
 Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
@@
 Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
+As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
 
-Consistent with this statistical regularity, sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] assume that the information-processing chain upfront choices in DfE takes the form of an evidence accumulation process over time, with choices becoming more accurate the more evidence must be accumulated.
-Specifically, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
-To relate the sampling process to the choice, sequential sampling models assume that the sampled outcomes are sequentially accumulated into one or more dynamic decision variables, and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-Accordingly, the number of outcomes required to sample decreases with thresholds, which could account for an as-if underweighting of rare outcomes [see @markantModelingChoiceSearch2015].
+One class of process models that link the actual sampling process to the decision-making process and can account for the as-if underweighting of rare outcomes by assuming a reliance on small samples, are sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004].
+That is, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
+To relate the sampling process to the final choice, sequential sampling models assume that the information-processing chain upfront the final choice takes the form of an evidence accumulation process over time, with choices becoming more accurate the more evidence must be accumulated.
+Specifically, the models assume that the sampled outcomes are sequentially accumulated into one or more dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+Now, since the thresholds determine how much (more) evidence a prospect must accumulate in order to be chosen and since the amount of evidence for either prospect can only increase by sampling, these models predict, ceteris paribus, an as-if underweighting of rare outcomes for low thresholds [see @markantModelingChoiceSearch2015].
+In other words, a decrease in the threshold leads to a decrease in the number of sampled outcomes that are required to reach this threshold. 
+Accordingly, for low thresholds, small-probability outcomes are predicted to contribute less to the accumulated evidence than warranted by their objective probability.
 
-However, some studies found the as-if underweighting of rare outcomes in DfE to appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
+Yet, some studies found the as-if underweighting of rare outcomes in DfE to appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
 While this finding demonstrates that the as-if underweighting of rare outcomes in DfE cannot be reduced to a small overall number of sampled outcomes, it may still be the case that the respective deviations from the principle of mathematical expectation were caused by the reliance on small samples.
@@
 # References
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```

### 2022-03-15 manuscript.Rmd
Review introduction

@@
                       fig.align = "l", #align figures to left margin
-                      fig.pos = "t"
-                      )
+                      fig.pos = "t")
 ```
@@
 
-Now, let a *prospect* be a choice alternative that possesses only two kinds of properties: the possible outcomes of the alternative and the probabilities with which these outcomes occur following its choice.
+Now, let a *prospect* be a choice alternative that possesses only two kinds of primitive properties: the possible outcomes of the alternative and the probabilities with which these outcomes occur following its choice.
 Importantly, the information that inputs provide about the properties of a prospect can come in different forms.
@@
 Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in past decisions.
-The inputs to DfE therefore take the form of sets of sampled outcomes (hereafter: samples).
-Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
+The inputs to DfE therefore take the form of sampled outcomes.
+Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taken a rather general perspective---there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
 In one reading of the gap, empirical choice patterns indicate that in DfD people choose as if a small-probability outcome is given more weight in the evaluation of a prospect than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
@@
 
-Similar to other behavioral phenomena that could be explained by assuming that the mind is sensitive to the composition of the samples on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE could be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [@hertwigDecisionsExperienceEffect2004; @plonskyRelianceSmallSamples2015; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
-That is, following from the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequency with which a prospect's outcome occurs in a sample of infinite size converges almost surely to its objective probability.
-In such a case, then, according to the de Moivre-Laplace theorem, the binomial distribution associated with each prospect's outcome can be approximated by a symmetric normal distribution [cf.
+Similar to other behavioral phenomena that could be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE could be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [see @hertwigDecisionsExperienceEffect2004; @plonskyRelianceSmallSamples2015; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+That is, following from the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
+In such a case, or in the less strict case of large samples, then, the binomial distributions of the outcomes can be approximated by a symmetric normal distribution [cf.
 @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
@@
 Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
-As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
 
-One class of process models that link the actual sampling process to the decision-making process and can account for the as-if underweighting of rare outcomes by assuming a reliance on small samples, are sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004].
+One class of process models that provide a mechanistic link between the actual sampling process, the reliance on small samples, and the as-if underweighting of rare outcomes are sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004].
 That is, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
-To relate the sampling process to the final choice, sequential sampling models assume that the information-processing chain upfront the final choice takes the form of an evidence accumulation process over time, with choices becoming more accurate the more evidence must be accumulated.
-Specifically, the models assume that the sampled outcomes are sequentially accumulated into one or more dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-Now, since the thresholds determine how much (more) evidence a prospect must accumulate in order to be chosen and since the amount of evidence for either prospect can only increase by sampling, these models predict, ceteris paribus, an as-if underweighting of rare outcomes for low thresholds [see @markantModelingChoiceSearch2015].
-In other words, a decrease in the threshold leads to a decrease in the number of sampled outcomes that are required to reach this threshold. 
-Accordingly, for low thresholds, small-probability outcomes are predicted to contribute less to the accumulated evidence than warranted by their objective probability.
+To relate the sampling process to the final choice, sequential sampling models assume that the information-processing chain upfront the choice takes the form of an evidence accumulation process over time, with choices becoming more accurate the more evidence must be accumulated.
+Specifically, these models assume that the sampled outcomes are sequentially accumulated into one or more dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+Now, since the thresholds determine how much (more) evidence a prospect must accumulate in order to be chosen and since the amount of evidence for either prospect can only increase by sampling more outcomes, these models predict, ceteris paribus, an as-if underweighting of rare outcomes for low thresholds [see @markantModelingChoiceSearch2015].
+In other words, a decrease in the threshold leads to a decrease in the number of outcomes that must be sampled to reach this threshold.
+Because of the skewness of their binomial distribution, then, small-probability outcomes are predicted to contribute less to the accumulated evidence than would be warranted by their objective probabilities.
+In turn, the higher a threshold, and thus the higher the number of outcomes that must be sampled to reach this threshold, the more should the amount of evidence contributed by small-probability outcomes correspond to what would be objectively warranted.
 
-Yet, some studies found the as-if underweighting of rare outcomes in DfE to appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
-While this finding demonstrates that the as-if underweighting of rare outcomes in DfE cannot be reduced to a small overall number of sampled outcomes, it may still be the case that the respective deviations from the principle of mathematical expectation were caused by the reliance on small samples.
-For example, given a large overall number of sampled outcomes, an as-if underweighting of rare outcomes could be explained, if only a small subset of all the sampled outcomes was considered for the assessment of prospects.
-<!---->
+Yet, the as-if underweighting of rare outcomes in DfE may appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
+While this suggests that the as-if underweighting of rare outcomes in DfE cannot be reduced to a small overall number of sampled outcomes, this paper emphasizes that it may still be the case that the respective deviations from the principle of mathematical expectation were caused by the reliance on small samples.
+That is, there may be a discrepancy between the overall number of sampled outcomes and the size of the samples that are actually used to evaluate the prospects or to make an inference about their latent properties, respectively.
+Accordingly, one approach to explain the as-if underweighting of rare outcomes in the light of a large overall number of sampled outcomes is to assume that some of the sampled outcomes are discounted or ignored in the evaluation of prospects.
+For example, some studies suggest that outcomes that were sampled more recently receive more weight in the evaluation of a prospect [see @hertwigDecisionsExperienceEffect2004] or that only those outcomes are considered right before a decision that followed some sequential pattern [see @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015].
 
-Yet, in another approach, @hillsInformationSearchDecisions2010 propose a dependency between sampling patterns and decision strategies.
+Specifically, a core assumption of this paper is that any number of sampled outcomes from a prospect may either be integrated into the same sample or into multiple respectively smaller samples, and that each of these samples serves an independent evaluation of a prospect.
+Accordingly, to explain the as-if underweighting of rare outcomes in the light of a large overall number of sampled outcomes,
+
+his paper presents a process model that can explain an as-if underweighting of rare outcomes, this approach differs in two respects from other approaches:
+It does not assume that the overall number of sampled outcomes is small and it does also not assume that some of the sampled outcomes are discounted or ignored.
+
+Rather, in another approach, @hillsInformationSearchDecisions2010 propose a dependency between sampling patterns and decision strategies that provides a link between the reliance on small samples and the as-if underweighting of rare outcomes that does not assume a discounting or omission of sampled outcomes.
 Considering the choice between two prospects, this approach distinguishes sampling patterns along the frequency of switches between the prospects during the sampling phase and assumes that only outcomes that were sampled from the same prospect between switches are integrated into the same sample.
@@
 More specifically, while the probability of a rare outcome to be sampled increases with the overall number of sampled outcomes, an increasing switching frequency causes the rare outcome not to be considered in an increasing number of comparisons.
-
-Now, this paper integrates both approaches to discuss in some more detail how the effect of small samples may exert its influence on the choices between two prospects in DfE.
-The main argument here is that whereas the reliance on small samples generally explains the as-if underweighting of rare outcomes in DfE, this explanation cannot be equated with inaccurate inferences about the latent properties of prospects that carry over to the subsequent choices.
-Rather the opposite can be the case.
-That is, the latent properties may imply different relations among the prospects in the form that choices according to the differences in one latent property may not coincide with the choices according to the differences in another latent property.
-Hence, although technically the reliance on small samples caused deviations from the principle of mathematical expectation, these deviations may reflect an accurate assessment of differences in a latent property other than the expected values.
 
@@
 Accordingly, the growing sequence of sample comparisons becomes more indicative for which prospect produces the higher outcomes most of the time.
+
+Now, this paper integrates both approaches to discuss in some more detail how the effect of small samples may exert its influence on the choices between two prospects in DfE.
+The main argument here is that whereas the reliance on small samples generally explains the as-if underweighting of rare outcomes in DfE, this explanation cannot be equated with inaccurate inferences about the latent properties of prospects that carry over to the subsequent choices.
+Rather the opposite can be the case.
+That is, the latent properties may imply different relations among the prospects in the form that choices according to the differences in one latent property may not coincide with the choices according to the differences in another latent property.
+Hence, although technically the reliance on small samples caused deviations from the principle of mathematical expectation, these deviations may reflect an accurate assessment of differences in a latent property other than the expected values.
 
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```

### 2022-03-18 manuscript.Rmd
Review Intorduction

@@
 The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the choice alternatives between which people can choose.
-In fact, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and returns a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
+In fact, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
 
@@
 For example, in *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
-Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in past decisions.
+Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in past consequential or non-consequential decisions.
 The inputs to DfE therefore take the form of sampled outcomes.
-Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taken a rather general perspective---there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
+Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
 In one reading of the gap, empirical choice patterns indicate that in DfD people choose as if a small-probability outcome is given more weight in the evaluation of a prospect than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
@@
 
-Similar to other behavioral phenomena that could be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE could be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [see @hertwigDecisionsExperienceEffect2004; @plonskyRelianceSmallSamples2015; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+Similar to other behavioral phenomena that could be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE could be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
 That is, following from the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
@@
 Accordingly, one approach to explain the as-if underweighting of rare outcomes in the light of a large overall number of sampled outcomes is to assume that some of the sampled outcomes are discounted or ignored in the evaluation of prospects.
-For example, some studies suggest that outcomes that were sampled more recently receive more weight in the evaluation of a prospect [see @hertwigDecisionsExperienceEffect2004] or that only those outcomes are considered right before a decision that followed some sequential pattern [see @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015].
+For example, some studies suggest that outcomes that were sampled more recently receive more weight in the evaluation of a prospect [see @hertwigDecisionsExperienceEffect2004] or that only those outcomes are considered right before a choice that followed some sequential pattern [see @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015].
+In either way, the effective sample that is used to evaluate the prospect is smaller than the number of sampled outcomes and thus more prone to underrepresent a small-probability outcome.
 
-Specifically, a core assumption of this paper is that any number of sampled outcomes from a prospect may either be integrated into the same sample or into multiple respectively smaller samples, and that each of these samples serves an independent evaluation of a prospect.
-Accordingly, to explain the as-if underweighting of rare outcomes in the light of a large overall number of sampled outcomes,
+However, in contrast to the approaches outlined so far, this paper presents a process model that demonstrates that people may rely on small samples and choose as if they were underweighting rare outcomes while still sampling and taking into account a large number of outcomes.
+Therefore, consider first the finding that *sampling strategies* were indicative for the final choice in DfE.
+Specifically, considering the choice between two prospects in the sampling paradigm, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^[<!--Open footnote-->Note that @hillsInformationSearchDecisions2010 proposed two paradigmatic sampling strategies, where prospects are either switched just once (comprehensive sampling) or after each sampled outcome (piecewise sampling).
+Nevertheless, in their analyses of empirical sampling data, they used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and further acknowledged that "many [sampling] strategies will fall on the continuum between [the two paradigmatic strategies]" [@hillsInformationSearchDecisions2010, p.
+1788].
+Respectively, in the current paper sampling strategies are defined as switching probabilities (see below).
+<!--Close footnote-->] 
+and proposed two different decision strategies that people may adopt.
+That is, for a summary decision strategy, the prospect is chosen that produced the greater mean across all sampled outcomes.
+In turn, for a round-wise decision strategy, the prospect is chosen that produced the greater outcome most of the time.
+In other words, the round-wise strategy assumes that over multiple rounds one outcome from each of the two prospects is sampled.
+In each round, then, the two sampled outcomes are compared and the prospect is chosen that wins most of these comparison rounds.
+Then, @hillsInformationSearchDecisions2010 found that the choices of people who switched frequently between prospects during the sampling phase were better predicted by assuming that they adopted a round-wise strategy (rather than a summary strategy), and that this predictive pattern reversed for people who switched infrequently.
 
-his paper presents a process model that can explain an as-if underweighting of rare outcomes, this approach differs in two respects from other approaches:
-It does not assume that the overall number of sampled outcomes is small and it does also not assume that some of the sampled outcomes are discounted or ignored.
+Now, one explanation for such a reversed predictive pattern would be if the differences in the sampling strategies determine which of the two decision strategies is used.
+To this end, this paper presents a process model that provides a mechanistic link between the *switching probability*---i.e., the probability of sampling outcomes from different prospects in direct succession during the sampling phase---, the decision strategy, and the respective choice.
+That is, the proposed model is such that the higher (lower) the switching probability during the sampling phase, the more the evaluation of the prospects resembles the round-wise strategy (summary strategy).
+However, to allow for a gradual transition from the summary to the round-wise strategy for increases in the switching probability, the model also captures hybrids of both decision strategies.
+Specifically, the model accumulates the evidence obtained from the comparisons between sample means---rather than from single outcomes, as in the sequential sampling models outlined above---with the size of the samples underlying each mean comparison decreasing with an increasing switching probability, and thresholds determining how much (more) of such mean comparisons a prospect must win in order to be chosen.
+Thus, the model presented in this paper is such that the higher (lower) the switching probabilities and the higher (lower) the thresholds, the more the evaluation of prospects or the accumulation process, respectively, resembles a round-wise strategy (summary strategy).
 
-Rather, in another approach, @hillsInformationSearchDecisions2010 propose a dependency between sampling patterns and decision strategies that provides a link between the reliance on small samples and the as-if underweighting of rare outcomes that does not assume a discounting or omission of sampled outcomes.
-Considering the choice between two prospects, this approach distinguishes sampling patterns along the frequency of switches between the prospects during the sampling phase and assumes that only outcomes that were sampled from the same prospect between switches are integrated into the same sample.
-Then, it is assumed that each time after a new sample for both prospects was generated, their means are compared, and the choice is determined by the number of won comparisons.^[<!--Open footnote-->Note that @hillsInformationSearchDecisions2010 describe only the two paradigmatic cases, where prospects are either switched just once (comprehensive sampling) or after each sampled outcome (piecewise sampling).
-Accordingly, in the former case choices depend on a single comparison between the means of samples that contain all outcomes sampled for the respective prospect (summary strategy); in the latter case, however, choices depend on multiple comparisons between samples that contain only one sampled outcome (round-wise strategy).
-Nevertheless, Hills and Hertwig [-@hillsInformationSearchDecisions2010, p.
-1788] acknowledge that "many [sampling] strategies will fall on the continuum between [these cases]", which is why the general description is used above.<!--Close footnote-->]
-Since each comparison is weighted equally, such a link between sampling patterns and decision strategies can explain an as-if underweighting of rare outcomes despite a large overall number of sampled outcomes being considered.
-More specifically, while the probability of a rare outcome to be sampled increases with the overall number of sampled outcomes, an increasing switching frequency causes the rare outcome not to be considered in an increasing number of comparisons.
+Moreover, this paper demonstrates in a simulation that the proposed model can be used to explain how peoples' evaluations of prospects can rely on small samples and lead to an as-if underweighting of rare outcomes, even if the number of sampled outcomes that is taken into account increases.
+Specifically, considering choices between a two-outcome prospect and a safe prospect, the model is used to simulate the evidence accumulation process and the respective choices for different combinations of switching probabilities and threshold values.
+Then, in a computational analyses using choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], it is shown that an increase in the switching probability causes a stronger as-if underweighting of rare outcomes, whereas for decreasing switching probabilities, choices converge to the solutions of the principle of mathematical expectation.
+The analyses moreover show that these differences between switching probabilities in the choice rates and CPT parameter estimates they produce remain stable as the thresholds increase.
+Accordingly, the results of the simulations and analyses substantiate the claim that the reliance on small samples but not necessarily the amount of sampled outcomes considered during the decision-making process cause an as-if underweighting of rare outcomes.
+That is, whereas the thresholds govern the length of the evidence accumulation process, the proposed model allows this process to unfold over mean comparisons between samples that tend to be small for high switching probabilities and large for low switching probabilities.
+Now, because in this model each comparison's contribution to the accumulated evidence is weighted equally in the form of round wins but ignores the magnitude of outcomes once a comparison is carried out, differences in the threshold values cannot predict differences in the amount a small-probability outcome contributes to the accumulated evidence relative to what would have been warranted by the principle of mathematical expectation.
+However, because high switching probabilities reduce the size of the samples on which a mean comparison is based, they cause small-probability outcomes to contribute to the outcome of each mean comparison less than would be objectively warranted.
+To this end, then, this paper argues that sampling strategies or switching probabilities, respectively, may serve to alter which differences in the latent properties of prospects are represented in the outcomes of the mean comparisons.
+Before presenting the model and the simulation study, the following section provides a formal definition of prospects and reviews how CPT can be used to describe choices between prospects in DfE in terms of deviations from the principle of mathematical expectation.
 
-To substantiate this claim, this paper defines a *sampling strategy* as the probability of sampling outcomes from different prospects in direct succession (hereafter: switching probability) and presents a sequential sampling model that accumulates the evidence obtained from the comparisons between sample means.
-More specifically, similar to @hillsInformationSearchDecisions2010, the model only integrates the outcomes that are sampled from the same prospect between switches into the same sample and each time after a new sample for both prospects was generated, their respective means are compared.
-The information about the outcomes of these comparisons are integrated into either one dynamic decision variable capturing the difference in the number of won comparisons or into two dynamic decision variables capturing the absolute number of won comparisons for both prospects separately.
-Accordingly, the thresholds determine how much (more) comparisons a prospect must win in order to be chosen. 
-The model demonstrates that sampling strategies, through their probabilistic relation to the size of the samples, determine which differences in the latent properties of the prospects are represented in the outcomes of the comparisons.
-That is, for a decreasing switching probability, the number of outcomes that are successively sampled from a given prospect increases such that the size of the sample grows.
-Accordingly, the model shows how with decreasing switching probability a mean comparison becomes more indicative for differences of the prospects in their expected values.
-In turn, for an increasing switching probability, the number of outcomes that are successively sampled from a given prospect decreases such that the size of the sample decreases.
-Accordingly, the growing sequence of sample comparisons becomes more indicative for which prospect produces the higher outcomes most of the time.
+# Prospects and the Description of Choices in CPT
 
-Now, this paper integrates both approaches to discuss in some more detail how the effect of small samples may exert its influence on the choices between two prospects in DfE.
-The main argument here is that whereas the reliance on small samples generally explains the as-if underweighting of rare outcomes in DfE, this explanation cannot be equated with inaccurate inferences about the latent properties of prospects that carry over to the subsequent choices.
-Rather the opposite can be the case.
-That is, the latent properties may imply different relations among the prospects in the form that choices according to the differences in one latent property may not coincide with the choices according to the differences in another latent property.
-Hence, although technically the reliance on small samples caused deviations from the principle of mathematical expectation, these deviations may reflect an accurate assessment of differences in a latent property other than the expected values.
+Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
+Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[<!--Open footnote-->See @knightRiskUncertaintyProfit1921, Chapter 1, for a discussion of the reasonableness of such abstractions.<!--Close footnote-->]
+These fundamental properties are considered the possible outcomes of a choice alternative (hereafter: $x_i$) and the probabilities with which these outcomes occur following the choice of the alternative (hereafter: $p_X(x_i)$).
+Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs $(x_i, p_X(x_i))$ are prospects (or: gambles).
 
-# The Description of Choices in CPT
+## Prospects
 
@@
 where each element $P_X$ can itself be considered a set of outcome-probability pairs $\{(x_, p_X(x)\}$.
+
+## CPT
 
@@
 
-## Choice Problems
+...
+
+## Method
+
+### Choice Problems
 
@@
 
-## Data Generation
+### Data Generation
 
@@
 In sum, 100 (parameter combinations) x 60 (choices) x 100 (agents) = 600,000 sampling processes and choices were simulated.
+
+### Modeling
 
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```

### 2022-03-21 manuscript.Rmd
Preliminary Draft Introduction + Section 1

@@
                       fig.align = "l", #align figures to left margin
-                      fig.pos = "t")
+                      fig.pos = "t" # display figures at the top of a page
+                      )
 ```
@@
 The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the choice alternatives between which people can choose.
-In fact, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
+Indeed, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
 
-Now, let a *prospect* be a choice alternative that possesses only two kinds of primitive properties: the possible outcomes of the alternative and the probabilities with which these outcomes occur following its choice.
-Importantly, the information that inputs provide about the properties of a prospect can come in different forms.
+Now, let a *prospect* be a choice alternative that possesses only two kinds of fundamental properties: the possible outcomes of the alternative (e.g., monetary gains or losses of some amount) and the probabilities with which these outcomes occur following the choice of the alternative.
+Importantly, the information that inputs provide about these properties of a prospect can come in different forms.
 For example, in *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
-Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in past consequential or non-consequential decisions.
+Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in similar past decisions.
 The inputs to DfE therefore take the form of sampled outcomes.
 Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
-In one reading of the gap, empirical choice patterns indicate that in DfD people choose as if a small-probability outcome is given more weight in the evaluation of a prospect than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructBehaviorGap2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
+empirical choice patterns indicate that in DfD people choose as if a small-probability outcome is given more weight in the evaluation of a prospect than would be warranted by its objective probability, following the principle of mathematical expectation (see below);
+in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcome is given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
 Hereafter, these choice patterns are referred to as the *as-if overweighting* and *as-if underweighting of rare outcomes*, respectively.
 
-Similar to other behavioral phenomena that could be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE could be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
-That is, following from the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
-In such a case, or in the less strict case of large samples, then, the binomial distributions of the outcomes can be approximated by a symmetric normal distribution [cf.
+Similar to other behavioral phenomena that could be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE could be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @plonskyRelianceSmallSamples2015; @wulffMetaanalyticReviewTwo2018].
+That is, following from the laws of large numbers [see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
+In such a case, then, or in the less strict case of large samples, the binomial distributions of the outcomes can be approximated by a symmetric normal distribution according to the de Moivre-Laplace theorem [cf.
 @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
-However, for small samples, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
+However, for samples of small size, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
 Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
+As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
 
-One class of process models that provide a mechanistic link between the actual sampling process, the reliance on small samples, and the as-if underweighting of rare outcomes are sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004].
-That is, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
-To relate the sampling process to the final choice, sequential sampling models assume that the information-processing chain upfront the choice takes the form of an evidence accumulation process over time, with choices becoming more accurate the more evidence must be accumulated.
-Specifically, these models assume that the sampled outcomes are sequentially accumulated into one or more dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-Now, since the thresholds determine how much (more) evidence a prospect must accumulate in order to be chosen and since the amount of evidence for either prospect can only increase by sampling more outcomes, these models predict, ceteris paribus, an as-if underweighting of rare outcomes for low thresholds [see @markantModelingChoiceSearch2015].
-In other words, a decrease in the threshold leads to a decrease in the number of outcomes that must be sampled to reach this threshold.
-Because of the skewness of their binomial distribution, then, small-probability outcomes are predicted to contribute less to the accumulated evidence than would be warranted by their objective probabilities.
-In turn, the higher a threshold, and thus the higher the number of outcomes that must be sampled to reach this threshold, the more should the amount of evidence contributed by small-probability outcomes correspond to what would be objectively warranted.
+Now, sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] form one class of process models that provide an algorithmic link between the actual sampling process, the reliance on small samples, and the as-if underweighting of rare outcomes.
+That is, in one paradigm used to study DfE, namely, the sampling paradigm [see @weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
+To relate the sampling process to the final choice, sequential sampling models assume that the entire information-processing chain upfront the choice takes the form of an evidence accumulation process over time, with choices becoming more accurate the more evidence must be accumulated.
+Specifically, considering the choice between two prospects, these models assume that the sampled outcomes are sequentially accumulated into one or two dynamic decision variables---i.e., the value of a decision variable is either the sum of all outcomes sampled from one prospect or the differences between both prospect-specific sums---and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+Notably, since the thresholds determine how much (more) evidence a prospect must accumulate in order to be chosen and since a decrease in the threshold leads to a decrease in the number of outcomes that must be sampled to reach this threshold, these models predict, ceteris paribus, an as-if underweighting of rare outcomes for low thresholds [see @markantModelingChoiceSearch2015].
+That is, for low thresholds, small-probability outcomes are predicted to contribute less (rather than more) to the accumulated evidence than would be warranted by their objective probabilities because of the positive skewness of their binomial distribution.
+In turn, the higher a threshold, and thus the higher the number of outcomes that must be sampled, the more should the amount of evidence contributed by small-probability outcomes correspond to what would be objectively warranted.
+In other words, the larger the thresholds and required number of sampled outcomes, the more should the as-if underweighting of rare outcomes fade and choices approximate the solutions of the principle of mathematical expectation.
 
-Yet, the as-if underweighting of rare outcomes in DfE may appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
-While this suggests that the as-if underweighting of rare outcomes in DfE cannot be reduced to a small overall number of sampled outcomes, this paper emphasizes that it may still be the case that the respective deviations from the principle of mathematical expectation were caused by the reliance on small samples.
-That is, there may be a discrepancy between the overall number of sampled outcomes and the size of the samples that are actually used to evaluate the prospects or to make an inference about their latent properties, respectively.
-Accordingly, one approach to explain the as-if underweighting of rare outcomes in the light of a large overall number of sampled outcomes is to assume that some of the sampled outcomes are discounted or ignored in the evaluation of prospects.
-For example, some studies suggest that outcomes that were sampled more recently receive more weight in the evaluation of a prospect [see @hertwigDecisionsExperienceEffect2004] or that only those outcomes are considered right before a choice that followed some sequential pattern [see @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015].
-In either way, the effective sample that is used to evaluate the prospect is smaller than the number of sampled outcomes and thus more prone to underrepresent a small-probability outcome.
+Yet, some studies show that the as-if underweighting of rare outcomes may appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
+To this end, this paper argues that there may be a discrepancy between the overall number of sampled outcomes and the size of the samples that the mind actually relies on to evaluate the prospects or to make an inference about their latent properties, respectively.
+That is, a core assumption of this paper is that any number of outcomes sampled from a prospect may either be integrated into the same sample---as it is implied by the sequential sampling models described above---or into multiple respectively smaller samples.
+Then, in contrast to other approaches that assume that some of the sampled outcomes are discounted [e.g., @hertwigDecisionsExperienceEffect2004] or ignored [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], this paper presents a process model that links the sampling process to the choices in DfE and demonstrates that a reliance on multiple small samples can cause an as-if underweighting of rare outcomes while fully accounting for a large number of sampled outcomes.
 
-However, in contrast to the approaches outlined so far, this paper presents a process model that demonstrates that people may rely on small samples and choose as if they were underweighting rare outcomes while still sampling and taking into account a large number of outcomes.
 Therefore, consider first the finding that *sampling strategies* were indicative for the final choice in DfE.
@@
 Now, one explanation for such a reversed predictive pattern would be if the differences in the sampling strategies determine which of the two decision strategies is used.
-To this end, this paper presents a process model that provides a mechanistic link between the *switching probability*---i.e., the probability of sampling outcomes from different prospects in direct succession during the sampling phase---, the decision strategy, and the respective choice.
+To this end, this paper presents a model that provides an algorithmic link between the *switching probability*---i.e., the probability of sampling outcomes from different prospects in direct succession during the sampling phase---, the decision strategy, and the respective choice.
 That is, the proposed model is such that the higher (lower) the switching probability during the sampling phase, the more the evaluation of the prospects resembles the round-wise strategy (summary strategy).
-However, to allow for a gradual transition from the summary to the round-wise strategy for increases in the switching probability, the model also captures hybrids of both decision strategies.
-Specifically, the model accumulates the evidence obtained from the comparisons between sample means---rather than from single outcomes, as in the sequential sampling models outlined above---with the size of the samples underlying each mean comparison decreasing with an increasing switching probability, and thresholds determining how much (more) of such mean comparisons a prospect must win in order to be chosen.
-Thus, the model presented in this paper is such that the higher (lower) the switching probabilities and the higher (lower) the thresholds, the more the evaluation of prospects or the accumulation process, respectively, resembles a round-wise strategy (summary strategy).
+However, to allow for a gradual transition from the summary to the round-wise strategy with increases in the switching probability, the model also captures hybrids of both strategies.
+Specifically, the proposed model accumulates the evidence obtained from the comparisons between sample means---i.e.
+won comparisons---with the size of the samples underlying each mean comparison decreasing with an increase in the switching probability, and thresholds determining how much (more) of such mean comparisons a prospect must win in order to be chosen.
+Thus, the model presented in this paper is such that the higher (lower) the switching probabilities and the higher (lower) the thresholds, the more the evaluation of prospects or the evidence accumulation process, respectively, resembles the round-wise strategy (summary strategy).
 
-Moreover, this paper demonstrates in a simulation that the proposed model can be used to explain how peoples' evaluations of prospects can rely on small samples and lead to an as-if underweighting of rare outcomes, even if the number of sampled outcomes that is taken into account increases.
-Specifically, considering choices between a two-outcome prospect and a safe prospect, the model is used to simulate the evidence accumulation process and the respective choices for different combinations of switching probabilities and threshold values.
-Then, in a computational analyses using choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], it is shown that an increase in the switching probability causes a stronger as-if underweighting of rare outcomes, whereas for decreasing switching probabilities, choices converge to the solutions of the principle of mathematical expectation.
-The analyses moreover show that these differences between switching probabilities in the choice rates and CPT parameter estimates they produce remain stable as the thresholds increase.
-Accordingly, the results of the simulations and analyses substantiate the claim that the reliance on small samples but not necessarily the amount of sampled outcomes considered during the decision-making process cause an as-if underweighting of rare outcomes.
-That is, whereas the thresholds govern the length of the evidence accumulation process, the proposed model allows this process to unfold over mean comparisons between samples that tend to be small for high switching probabilities and large for low switching probabilities.
-Now, because in this model each comparison's contribution to the accumulated evidence is weighted equally in the form of round wins but ignores the magnitude of outcomes once a comparison is carried out, differences in the threshold values cannot predict differences in the amount a small-probability outcome contributes to the accumulated evidence relative to what would have been warranted by the principle of mathematical expectation.
-However, because high switching probabilities reduce the size of the samples on which a mean comparison is based, they cause small-probability outcomes to contribute to the outcome of each mean comparison less than would be objectively warranted.
-To this end, then, this paper argues that sampling strategies or switching probabilities, respectively, may serve to alter which differences in the latent properties of prospects are represented in the outcomes of the mean comparisons.
-Before presenting the model and the simulation study, the following section provides a formal definition of prospects and reviews how CPT can be used to describe choices between prospects in DfE in terms of deviations from the principle of mathematical expectation.
+Moreover, this paper demonstrates in a computational analysis that the evaluation of prospects, while taking into account an increasing number of sampled outcomes, can rely on multiple small samples, causing an as-if underweighting of rare outcomes.
+Specifically, considering choices between a two-outcome prospect and a safe prospect, the proposed model is used to simulate the evidence accumulation process for different combinations of switching probabilities and threshold values.
+Then, on the basis of choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], it is shown that the simulated choices converge to the solutions of the principle of mathematical expectation for decreasing switching probabilities, but reflect an increasingly pronounced as-if underweighting of rare outcomes, the more the switching probabilities increase.
+The analysis also shows that these differences between switching probabilities remain stable for different threshold values.
+Accordingly, the computational analysis substantiates the claim that the reliance on (multiple) small samples, but not necessarily the consideration of a small number of sampled outcomes, causes an as-if underweighting of rare outcomes in DfE.
+In other words, because the switching probabilities change the size of the samples underlying each mean comparison, the model predicts them to affect whether a low-probability outcome contributes to the majority of required mean comparisons about as much as would be warranted based on its objective probabilities, or whether they contribute rather less.
+Yet, since each comparison's contribution to the accumulated evidence is weighted equally in the form of round wins, the model does not predict the thresholds to have a similar effect.
+Rather, whatever systematic differences in the latent properties of prospects may be represented in a mean comparison, should be more accurately assessed as the thresholds---and therefore also the number of sampled outcomes that are taken into account during the evaluation of prospects---increase.
+To this end, this paper argues that the mind may rely on different sampling strategies or switching probabilities, respectively, to change for which differences in the latent properties of prospects evidence is accumulated.
+Before presenting the model and the computational analysis, the following section provides a formal definition of prospects and reviews how CPT can be used to describe choices between prospects in terms of deviations from the principle of mathematical expectation.
 
@@
 
-Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].^[<!--Open footnote-->See @knightRiskUncertaintyProfit1921, Chapter 1, for a discussion of the reasonableness of such abstractions.<!--Close footnote-->]
-These fundamental properties are considered the possible outcomes of a choice alternative (hereafter: $x_i$) and the probabilities with which these outcomes occur following the choice of the alternative (hereafter: $p_X(x_i)$).
-Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs $(x_i, p_X(x_i))$ are prospects (or: gambles).
+Since there is an uncountable number of choices people confront in the natural world, behavioral decision research routinely abstracts from choices between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
+Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.
+These fundamental properties are considered the possible outcomes of a choice alternative and the probabilities with which these outcomes occur following the choice of the alternative.
+Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs are prospects (or: gambles).
+As such, prospects can be understood as the distribution of a discrete random variable, for which the following section briefly provides an axiomatic basis (see @kolmogorovFoundationsTheoryProbability1950, Chapters 1-3, and @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive and an accessible treatment of random variables, respectively).
 
-## Prospects
+## Formal Definition of Prospects and Sets Thereof
 
-Following @kolmogorovFoundationsTheoryProbability1950,^[The symbolic notation from @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015 is adopted.] let the axiomatic definition of a prospect be that of a discrete random variable's distribution.
-Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space.
-Accordingly, $\Omega$ is a finite sample space with each element $\omega \in \Omega$ denoting a possible consequence of choosing the respective prospect.
-$\mathcal{F}$ is the power set $\mathcal{P}(\Omega)$ with each element $A \in \mathcal{F}$ being a subset of $\Omega$.
+Following @kolmogorovFoundationsTheoryProbability1950 and adopting the symbolic notation from @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, let the tuple $(\Omega, \mathcal{F}, P)$ be a probability space.
+Accordingly, $\Omega$ is a finite sample space with each element $\omega$ in $\Omega$ denoting a possible consequence of choosing the respective prospect.
+$\mathcal{F}$ is the power set $\mathcal{P}(\Omega)$ with each element $A$ in $\mathcal{F}$ being a subset of $\Omega$, also denoted a random event.
 $P$ is the probability measure
@@
 $$
-To summarize and simplify, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
+Note that the measure in (3) and (4), respectively, is a random variable's distribution and therefore a prospect. 
+Accordingly, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
 $$
@@
 $$
-where each element $P_X$ can itself be considered a set of outcome-probability pairs $\{(x_, p_X(x)\}$.
+where each element $P_X$ can itself be considered a set of outcome-probability pairs $\{(x_i, p_X(x_i)\}$.
 
-## CPT
+## CPT and the Concept of Probability Weighting
 
@@
 EV = \sum_i^n x_i \times p_X(x_i)
-\tag{7}
+\tag{6}
 $$ 
@@
 \; ,
-\tag{8}
+\tag{7}
 $$ 
@@
 \end{aligned}
-\tag{9}
+\tag{8}
 $$
@@
   \end{cases}
-\tag{10}
+\tag{9}
 $$
@@
 <!--Accordingly, one may adopt an as-if weighting terminology, stating that people choose *as if* they maximized the value in (10) and applied the weighting pattern that was estimated in CPT.-->
-Now, several consequences for the weighting pattern that can be estimated in CPT follow from (12), which are reviewed next:
+Now, several consequences for the weighting pattern that can be estimated in CPT follow from (9), which are reviewed next:
 
@@
 
-* The value of a cumulative decision weight depends on the estimated shape of the graph of $w$, the weighting function's parameters respectively.
-That is, the shape of the graph of $w$ displays in which interval on the cumulative probability scale $[0,1]$ the images of $w$, $w(p)$, take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
+* The value of a cumulative decision weight depends on the estimated shape of the graph of $w$ or the weighting function's parameters, respectively.
+That is, the shape of the graph of $w$ displays over which interval on the cumulative probability scale $[0,1]$ the images of $w$, $w(p)$, take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
 Hence, assuming a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
@@
 Therefore, Figure\ \@ref(fig:weighting-function) illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
-Now, let each $p$ on the abscissa be one of the four cumulative probabilities from (12). 
+Now, let each $p$ on the abscissa be one of the four cumulative probabilities from (9). 
 Then each graph in Figure\ \@ref(fig:weighting-function) displays the graphical shape of the weighting function
@@
 \end{aligned}
-\tag{11}
+\tag{10}
 $$
@@
 Evidently, both parameters have distinct effects on the graphs' shape, with $\gamma$ affecting the curvature and $\delta$ the elevation.
-As a consequence from (12) then, each combination of parameters implies a particular weighting pattern, with some of them being similar and others being rather distinct.
+As a consequence from (9) then, each combination of parameters implies a particular weighting pattern, with some of them being similar and others being rather distinct.
 
@@
 In some more detail, the gray-dashed identity lines in Figure\ \@ref(fig:weighting-function) imply a linear weighting pattern.
-That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are derived according to (12) would be equal to the differences between the respective objective cumulative probabilities and therefore also to the objective probabilities of the outcomes for which the weights are determined.
+That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are derived according to (9) would be equal to the differences between the respective objective cumulative probabilities and therefore also to the objective probabilities of the outcomes for which the weights are determined.
 Such a linear weighting pattern is implied by $\gamma = 1$ and $\delta = 1$. 
@@
 Importantly, each estimated weighting function implies a weighting pattern.
-Although the possible weighting patterns depend on the exact parameterization of the weighting function [e.g., @goldsteinExpressionTheoryPreference1987], the latter's graph usually takes a more or less accentuated (inverse) S-shape, which implies a weighting pattern where small-probability outcomes of low and high rank are underweighted (overweighted) in CPT's overall evaluation of a prospect according to (10).
+Although the possible weighting patterns depend on the exact parameterization of the weighting function [e.g., @goldsteinExpressionTheoryPreference1987], the latter's graph usually takes a more or less accentuated (inverse) S-shape, which implies a weighting pattern where small-probability outcomes of low and high rank are underweighted (overweighted) in CPT's overall evaluation of a prospect according to (7).
 Notably, for the case of choices between at most two-outcome prospects, the weighting pattern reduces to either an underweighting or overweighting of rare outcomes.
-For the description of such choices, one may then adopt the as-if weighting terminology from above, by stating that people decide as if they were either underweighting or overweighting rare outcomes.
-<!-- Add paragraph about CPT analysis of DfE-->
+For the description of such choices, one may then adopt the as-if weighting terminology from the introduction, by stating that people decide as if they were either underweighting or overweighting rare outcomes.
 
@@
 However, as such, CPT cannot substitute algorithmic-level theories that make claims about how exactly the mind transforms the inputs to the decision making process into outputs which approximate the solutions of CPT's calculus [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
-Therefore, this paper uses CPT merely as a data model and continues to inquire how on the algorithmic level the mind may integrate sampling strategies into the information-processing chain upfront choices in DfE.
-More specifically, the following two sections discuss and demonstrate how different strategies of generating outcomes and integrating them into samples produce distinct choice patterns in DfE, and how these choice patterns translate to the weighting pattern in CPT.^[<!--Open footnote-->CPT's value function will also be considered but emphasis is put on the weighting function.<!--Close footnote-->]
+<!--Therefore, this paper uses CPT merely as a data model and continues to inquire how on the algorithmic level the mind may integrate sampling strategies into the information-processing chain upfront choices in DfE.
+More specifically, the following two sections discuss and demonstrate how different strategies of generating outcomes and integrating them into samples produce distinct choice patterns in DfE, and how these choice patterns translate to the weighting pattern in CPT.-->
 
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```

### 2022-03-23 manuscript.Rmd
Preliminary draft: Accumulating evidence

@@
 abstract: |
-  Add short abstract.
+  Add abstract
 
@@
 Indeed, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
+Decision making can therefore be understood as an information-processing problem whose solution requires a selection among choice alternatives.
 
@@
 Similar to other behavioral phenomena that could be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE could be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @plonskyRelianceSmallSamples2015; @wulffMetaanalyticReviewTwo2018].
-That is, following from the laws of large numbers [see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
-In such a case, then, or in the less strict case of large samples, the binomial distributions of the outcomes can be approximated by a symmetric normal distribution according to the de Moivre-Laplace theorem [cf.
+Specifically, following from the laws of large numbers [see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
+In such a case, then, or in the less strict case of large samples, the binomial distributions of the outcomes can be approximated by a symmetric normal distribution [cf.
 @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
@@
 
-Now, sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] form one class of process models that provide an algorithmic link between the actual sampling process, the reliance on small samples, and the as-if underweighting of rare outcomes.
+<!--Now, sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] form one class of process models that provide an algorithmic link between the actual sampling process and the choices in DfE.
 That is, in one paradigm used to study DfE, namely, the sampling paradigm [see @weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
 To relate the sampling process to the final choice, sequential sampling models assume that the entire information-processing chain upfront the choice takes the form of an evidence accumulation process over time, with choices becoming more accurate the more evidence must be accumulated.
-Specifically, considering the choice between two prospects, these models assume that the sampled outcomes are sequentially accumulated into one or two dynamic decision variables---i.e., the value of a decision variable is either the sum of all outcomes sampled from one prospect or the differences between both prospect-specific sums---and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-Notably, since the thresholds determine how much (more) evidence a prospect must accumulate in order to be chosen and since a decrease in the threshold leads to a decrease in the number of outcomes that must be sampled to reach this threshold, these models predict, ceteris paribus, an as-if underweighting of rare outcomes for low thresholds [see @markantModelingChoiceSearch2015].
+Specifically, considering the choice between two prospects, these models assume that the prospects' outcomes are sequentially sampled and integrated into dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+Notably, since the thresholds determine how much (more) evidence a prospect must accumulate in order to be chosen and since a decrease in the threshold leads to a decrease in the number of outcomes that must be sampled to reach this threshold, a sequential sampling model may be used to relate the reliance on small samples to an as-if underweighting of rare outcomes [see @markantModelingChoiceSearch2015].
 That is, for low thresholds, small-probability outcomes are predicted to contribute less (rather than more) to the accumulated evidence than would be warranted by their objective probabilities because of the positive skewness of their binomial distribution.
-In turn, the higher a threshold, and thus the higher the number of outcomes that must be sampled, the more should the amount of evidence contributed by small-probability outcomes correspond to what would be objectively warranted.
-In other words, the larger the thresholds and required number of sampled outcomes, the more should the as-if underweighting of rare outcomes fade and choices approximate the solutions of the principle of mathematical expectation.
+In turn, the higher a threshold, and thus the higher the number of outcomes that must be sampled, the more should the amount of evidence contributed by small-probability outcomes correspond to what would be objectively warranted.-->
 
@@
 To this end, this paper argues that there may be a discrepancy between the overall number of sampled outcomes and the size of the samples that the mind actually relies on to evaluate the prospects or to make an inference about their latent properties, respectively.
-That is, a core assumption of this paper is that any number of outcomes sampled from a prospect may either be integrated into the same sample---as it is implied by the sequential sampling models described above---or into multiple respectively smaller samples.
-Then, in contrast to other approaches that assume that some of the sampled outcomes are discounted [e.g., @hertwigDecisionsExperienceEffect2004] or ignored [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015], this paper presents a process model that links the sampling process to the choices in DfE and demonstrates that a reliance on multiple small samples can cause an as-if underweighting of rare outcomes while fully accounting for a large number of sampled outcomes.
+However, in contrast to other approaches, this paper does not assume that some of the sampled outcomes are discounted [e.g., @hertwigDecisionsExperienceEffect2004] or ignored [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015].
+Rather, a core assumption of this paper is that any number of outcomes sampled from a prospect may either be integrated into the same sample<!-- ---as it is implied by the sequential sampling models described above--- --> or into multiple respectively smaller samples.
+Then, this paper presents a process model that links the actual sampling process to the choices in DfE and demonstrates that a reliance on multiple small samples can cause an as-if underweighting of rare outcomes while fully accounting for a large number of sampled outcomes.
 
 Therefore, consider first the finding that *sampling strategies* were indicative for the final choice in DfE.
-Specifically, considering the choice between two prospects in the sampling paradigm, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^[<!--Open footnote-->Note that @hillsInformationSearchDecisions2010 proposed two paradigmatic sampling strategies, where prospects are either switched just once (comprehensive sampling) or after each sampled outcome (piecewise sampling).
+Specifically, in one paradigm used to study DfE, namely, the sampling paradigm [see @weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
+Considering this paradigm and the choice between two prospects, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^[<!--Open footnote-->Note that @hillsInformationSearchDecisions2010 proposed two paradigmatic sampling strategies, where prospects are either switched just once (comprehensive sampling) or after each sampled outcome (piecewise sampling).
 Nevertheless, in their analyses of empirical sampling data, they used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and further acknowledged that "many [sampling] strategies will fall on the continuum between [the two paradigmatic strategies]" [@hillsInformationSearchDecisions2010, p.
@@
 Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs are prospects (or: gambles).
-As such, prospects can be understood as the distribution of a discrete random variable, for which the following section briefly provides an axiomatic basis (see @kolmogorovFoundationsTheoryProbability1950, Chapters 1-3, and @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive and an accessible treatment of random variables, respectively).
+As such, prospects can be understood as the distribution of a discrete random variable, for which the following section briefly provides an axiomatic basis.
 
-## Formal Definition of Prospects and Sets Thereof
+## Formal Definition of Prospects
 
@@
 \noindent
-Given that the value of each cumulative decision weight depends on the two transformed cumulative probabilities in (12)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the weighting pattern are reviewed by considering the actual weighting function.
+Given that the value of each cumulative decision weight depends on the two transformed cumulative probabilities in (9)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the weighting pattern are reviewed by considering the actual weighting function.
 Therefore, Figure\ \@ref(fig:weighting-function) illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
@@
 The as-if weighting terminology is therefore reminiscent of the distinction between different levels of explanation [@marrVisionComputationalInvestigation1982].
-That is, CPT may be considered a computational-level theory that specifies the computational problem the mind faces during decisions between prospects, and how this problem may be solved by the abstract calculus reviewed above.
-However, as such, CPT cannot substitute algorithmic-level theories that make claims about how exactly the mind transforms the inputs to the decision making process into outputs which approximate the solutions of CPT's calculus [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
-<!--Therefore, this paper uses CPT merely as a data model and continues to inquire how on the algorithmic level the mind may integrate sampling strategies into the information-processing chain upfront choices in DfE.
-More specifically, the following two sections discuss and demonstrate how different strategies of generating outcomes and integrating them into samples produce distinct choice patterns in DfE, and how these choice patterns translate to the weighting pattern in CPT.-->
+That is, CPT may be considered a computational-level theory that specifies the computational problem the mind faces when being confronted with the choice between prospects, and how this problem may be solved by the abstract calculus reviewed above.
+However, as such, CPT cannot substitute algorithmic-level theories that make claims about how exactly the mind transforms the inputs to the decision-making process into outputs which approximate the solutions of CPT's calculus [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
+Therefore, this paper uses CPT merely as a data model and continues to inquire how on the algorithmic level the mind may integrate sampling strategies into the information-processing chain upfront choices in DfE.
 
@@
 The need to distinguish between the computational and the algorithmic level in the domain of decision making is exemplified by the fact that information about prospects may come in the form of descriptions or sampled outcomes.
-Whereas CPT can be used to model choices in DfD and DfE, the actual information-processing chains that the mind may execute upfront choices in DfE cannot be identical to those in DfD.
-That is, inputs in the form of sampled outcomes require different algorithms to be processed than do descriptions of outcomes and their probabilities.
-More specifically, the core difference between DfD and DfE is that in the latter case, the properties must be inferred. 
-However, as has been outlined in the introduction, for such an inference rather many sampled outcomes must be integrated.
-
-However, only rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcome-probability pairs.
+Specifically, only rarely in peoples' daily life, the inputs to the decision-making process take the form of explicit descriptions of all outcome-probability pairs.
 In such cases, people would make DfD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
 Yet, rather often, people make DfE, where the mind can learn about the latent properties of prospects only by experiental sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
-That is, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set of prospect-specific stochastic processes
+Accordingly, for the choice between $1, ..., k$ prospects, the inputs to the decision-making process are generated by a set of prospect-specific stochastic processes
 $$
@@
 \; ,
-\tag{6}
+\tag{11}
 $$
-where each $\{X_{t}\}_{t \in \mathbb N}$ is a collection of independent and identically distributed (i.i.d.) random variables.
-Then, in other words, each stochastic process produces a sequence sampled outcomes. 
-Now, one core assumption of this paper is that, in order to infer the latent properties of a prospect, the mind sequentially integrates the sampled outcomes into either one sample or into multiple smaller samples.
-Assuming that the mind uses all samples so obtained during a process of evidence accumulation, this paper discusses and demonstrates how different sampling strategies that alter the number and size of these samples can produce distinct choice patterns in DfE.
-Before so doing, however, the following section reviews how CPT can be used as a data model that captures systematic deviations from the principle of mathematical expectation in the parameter estimates of a *value* and a *weighting function*.
+where each $\{X_{t}\}_{t \in \mathbb N}$ is a collection of independent and identically distributed (i.i.d.) random variables.^[Note that it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+660].
+However, in the sampling paradigm, i.i.d.
+random variables are commonly assumed.]
+The inputs to DfE are then the realizations of the random variables in (11), which require different algorithms to be processed than do descriptions of the outcomes and their probabilities.
 
-## The model
+## Accumulating Evidence About Differences in Latent Properties
 
-To model the information-processing chain in DfE, the current paper integrates two approaches that have been proposed to link the sampling process and the decision-making process. 
-Specifically,
+Since it is only through their fundamental properties, or combinations thereof, that any distinction between the prospects can be made, systematic choices in DfE must be based on the assessment of differences in the latent properties of prospects.
+Accordingly, the mind may use the sampled outcomes to first infer the latent objective probabilities of all possible outcomes, and then proceed by selecting a property, or combinations thereof, to assess differences among the prospects and make a respective choice.
+However, the mind may also approximate such a process by using an algorithm that omits explicit inferences and directly accumulates evidence about the differences in latent properties from the sampled outcomes.
+To this end, sequential sampling models of decision making assume that the outcomes of prospects are sequentially sampled and integrated into dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DfE and has shown to explain some of the robust deviations from the EV or EU principle, respectively [@busemeyerDecisionFieldTheory1993; @bhatiaSequentialSamplingParadoxes2014], including the underweighting of rare outcomes in the sampling paradigm [@markantModelingChoiceSearch2015].
+Moreover, these models implement speed-accuracy tradeoffs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more (less) accurate but slower (faster) choices for high (low) thresholds.
 
-One such approach is captured by sequential sampling models, which approach the information-processing chain as an evidence accumulation process. 
-One core assumption of these models applied to choices between prospects [see, e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] is that the sampled outcomes are used to sequentially accumulate evidence for or against the respective prospect as the sequences in (8) grow.
-More specifically, sequential sampling models assume that the values of the sampled outcomes are sequentially integrated into one or more dynamic decision variables.
-Once the value of a decision variable reaches a threshold in favor of a prospect, a respective choice is made.
+Yet, there are distinct latent properties and combinations thereof that can be used to assess differences between prospects and for which evidence may be accumulated.
+Respectively, this paper presents a computational model in which the latent properties, whose differences among prospects are represented in the decision variable, can change.
+To this end, the model implements the summary and the round-wise decision strategy---for which either the prospect is chosen that produced the greater mean across all sampled outcomes or the prospect that won more comparisons between single sampled outcomes, respectively [see @hillsInformationSearchDecisions2010]---into a common evidence accumulation model.
+That is, the model accumulates the evidence obtained from a sequence of comparisons between sample means, with the size of the samples underlying each mean comparison decreasing with increasing switching probabilities.
+Accordingly, whereas the decision variables of the model capture how much (more) comparisons between sample means a prospect has won, the evidence accumulation process more closely resembles the round-wise strategy for high switching probabilities and small sample sizes, and the summary strategy for low switching probabilities and large sample sizes.
+Now, since for a large overall number of sampled outcomes the summary strategy is more indicative for differences in the EV and the round-wise strategy is more indicative for differences in the likelihood to produce a higher outcome than the respective other prospect, the proposed model shows how the mind may rely on different sampling strategies to change for which differences in the latent properties of prospects evidence is accumulated.
 
-In contrast, @hillsInformationSearchDecisions2010, proposed another potential link between the sampling and the decision process in DfE.
-Specifically, the authors suppose that the sampling pattern may be linked to the choice strategy that people apply.
-That is, if single samples originating from different prospects are generated in direct succession (piecewise sampling), the evaluation of prospects is based on multiple ordinal comparisons of single samples (round-wise decisions).
-In contrast, if single samples originating from the same prospect are generated in direct succession (comprehensive sampling), it is supposed that the evaluation of prospects is based on a single ordinal comparison of long sequences of single samples (summary decisions).
-Indeed, they found some evidence that people who switch more often, make more choices in line with a piecewise strategy and people who switch rarely make more choices in line with a comprehensive strategy [but see @wulffHowShortLongrun2015].
-However, in this approach no causal claims are made.
+## Model
 
-Therefore, model assumes that evidence is accumulated over a sequence of mean-based comparisons between the samples.
+The model assumes that evidence is accumulated over a sequence of mean-based comparisons between the samples.
 The results of each comparison is defined as a random variable
@@
   Z : \mathbb{R} &\to \mathbb{N} \\
-  (\overline{X}, \overline{Y}) &\mapsto 
+  (\overline{X} - \overline{Y}) &\mapsto 
   \begin{cases}
@@
 
+### Model Predictions
+
+<!-- Pachur et al. ... -->
+
+```{r}
+predictions <- tibble("Simulation Pararameter" = c("s", "$\\theta$"),
+                      "$\\gamma$" = c(0,0),
+                      "$\\delta$" = c(0,0),
+                      "$\\alpha$" = c(0,0))
+apa_table(predictions, caption = "Model Predictions", escape = FALSE)
+```
+
 # Simulation Study
-
-...
 

### 2022-03-24 manuscript.Rmd
Preliminary Draft Model

@@
 bibliography      : references_sampling-in-dfe.bib
-csl               : /Users/Linus Hof/Documents/Psychologie/ARC/sampling-in-dfe/apa.csl
-appendix          : manuscript_appendix.Rmd
+csl               : apa.csl
 
@@
 $$
-P_X : \mathcal{F'} \to [0,1]
+P' : \mathcal{F'} \to [0,1]
 \tag{3}
@@
 $$
-P_X(A' \in \mathcal{F'}) := P(\{\omega: X(\omega) = x \in A'\})
+P'(A' \in \mathcal{F'}) := P(\{\omega: X(\omega) = x \in A'\})
 \; .
@@
 $$
-\{P_{X_1}, ... , P_{X_k}\}
+\{P'^1, ... , P'^k\}
 \; ,
@@
 $$
-where each element $P_X$ can itself be considered a set of outcome-probability pairs $\{(x_i, p_X(x_i)\}$.
+where each element $P'$ can itself be considered a set of outcome-probability pairs $\{(x_i, p_X(x_i)\}$.
 
@@
 $$ 
-with objective outcomes $x_i$ being transformed by a value function $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P_X$.
+with objective outcomes $x_i$ being transformed by a value function $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P'$.
 More specifically, following @tverskyAdvancesProspectTheory1992, the objective outcomes are transformed by a value function
@@
   \begin{cases}
-     w^+(P(X \geq x_i)) - w^+(P(X > x_i)) \quad \forall x_i \geq 0, \\
-     w^-(P(X \leq x_i)) - w^-(P(X < x_i)) \quad \text{else}
+     w^+(P(X(\omega) \geq x_i)) - w^+(P(X(\omega) > x_i)) \quad \forall x_i \geq 0, \\
+     w^-(P(X(\omega) \leq x_i)) - w^-(P(X(\omega) < x_i)) \quad \text{else}
      \; , 
@@
 * The value of a cumulative decision weight depends on the estimated shape of the graph of $w$ or the weighting function's parameters, respectively.
-That is, the shape of the graph of $w$ displays over which interval on the cumulative probability scale $[0,1]$ the images of $w$, $w(p)$, take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
+That is, the shape of the graph of $w$ displays over which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
 Hence, assuming a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
@@
 $$
-\{\{X_{1t}\}, ... , \{X_{kt}\}\}
+\{\{X^1_t\}, ... , \{X^k_t\}\}
 \; ,
@@
 
-Yet, there are distinct latent properties and combinations thereof that can be used to assess differences between prospects and for which evidence may be accumulated.
-Respectively, this paper presents a computational model in which the latent properties, whose differences among prospects are represented in the decision variable, can change.
-To this end, the model implements the summary and the round-wise decision strategy---for which either the prospect is chosen that produced the greater mean across all sampled outcomes or the prospect that won more comparisons between single sampled outcomes, respectively [see @hillsInformationSearchDecisions2010]---into a common evidence accumulation model.
+Yet, there are distinct latent properties that can be used to assess differences between prospects.
+Respectively, this paper presents a computational model which implements the summary and the round-wise decision strategy---for which either the prospect is chosen that produced the greater mean across all sampled outcomes or the prospect that won more comparisons between single sampled outcomes, respectively [see @hillsInformationSearchDecisions2010]---into a common evidence accumulation model.
 That is, the model accumulates the evidence obtained from a sequence of comparisons between sample means, with the size of the samples underlying each mean comparison decreasing with increasing switching probabilities.
@@
 
-The model assumes that evidence is accumulated over a sequence of mean-based comparisons between the samples.
-The results of each comparison is defined as a random variable
+We consider the sampling paradigm and a choice between two prospects denoted by the distributions $P'^X$ and $P'^Y$ of the discrete random variables $X$ and $Y$, respectively.
+The model assumes that the information-processing chain starts at random with a stochastic process on one of the two random variables.
+Specifically, it is assumed that an agent starts with equal probability to sample from one of the prospects, say $P'^X$, and generates a sequence of random variables $X_1, X_2,...$, where the mean over the sequence is computed or updated with each new outcome that is sampled.
+The respective stochastic process $\{S^X_n\}_{n \in \mathbb{N}}$ is defined by
+$$
+S^X_n = \frac{1}{n} \sum_{t = 1}^n X_t, \quad n \in \mathbb{N}
+\; ,
+\tag{12}
+$$
+and terminates as soon as an outcome is sampled from the other prospect.
+The switching probability $\psi \in (0,1]$, which is adopted prior the start of the information-processing chain and is fixed throughout, controls the probability with which outcomes from different prospects are sampled in direct succession.
+In other words, the switching probability is the probability with which the stochastic process on the current random variable stops and a new stochastic process on the other random variable starts with the subsequently sampled outcome.
+To implement an evidence accumulation process, the model assumes that each time after a new stochastic process was started and terminated on both random variables, their respective values are compared, with the prospect underlying the stochastic process with the greater final value receiving a round-win.
+Accordingly, for the prospect $P'^X$, this stage is modeled by the mapping
 $$
 \begin{aligned}
-  Z : \mathbb{R} &\to \mathbb{N} \\
-  (\overline{X} - \overline{Y}) &\mapsto 
+  Z^X : \mathbb{R} &\to \mathbb{N} \\
+  S^X_n - S^Y_n &\mapsto 
   \begin{cases}
-     1 &\text{if} \quad \overline{X} > \overline{Y}, \\
-     -1 &\text{if} \quad \overline{X} < \overline{Y}, \\
+     1 &\text{if} \quad  S^X_n > S^Y_n, \\
      0 &\text{else}
-     \; . 
+     \; ,
   \end{cases}
 \end{aligned}
-\tag{}
+\tag{13}
 $$
-The evidence accumulation process can therefore be defined as a random walk 
+where $Z^X$ is a random variable that takes only the two values $0$ and $1$, denoting a lost or won mean comparison, respectively. 
+The model assumes that a round consisting of two stochastic processes---i.e., one from each prospect---and the subsequent comparison of their values is repeated until the sum of round wins for one of the two prospects reaches a threshold $\theta \in \mathbb{N}$.
+Similar to the switching probability, it is assumed that the threshold is adopted prior the start of the information-processing chain and is fixed throughout.
+For $P'^X$, then, we obtain a sequence of independent comparisons $Z^X_1, Z^X_2, ...$ and model the respective evidence accumulation process as a random walk $\{D^X_m\}_{m \in \mathbb{N}}$ defined by 
 $$
-D_n = \sum_t^n Z_t \quad n \in \mathbb N
+D^X_m = \sum_{i = 1}^m Z^X_i, \quad m \in \mathbb{N}
+\;,
+\tag{14}
 $$
+resembling a dynamic decision variable.
+Note that since (13) describes a Bernoulli trial, the random walk in (14) is based on a Bernoulli process.
+
+Finally, note that the described model assumes two random walks---i.e., one for each prospect---approaching the same threshold, which is the absolute number of mean comparisons a prospect must win in order to be chosen.
+However, one may also define a single random walk, resembling a common dynamic decision variable, which approaches a positive threshold $\theta^+$ and a negative threshold $\theta^-$.
+Therefore, (13) may be adapted such that $Z$ takes the value $-1$ instead of $0$, such that the threshold determines how many more mean comparisons a prospect must win in order to be chosen.
 
@@
 
-<!-- Pachur et al. ... -->
-
-```{r}
+```{r eval=FALSE}
 predictions <- tibble("Simulation Pararameter" = c("s", "$\\theta$"),
@@
 # References
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('manuscript_appendix.Rmd')
-```

### 2022-03-24 manuscript.Rmd
Model predictions and minor reviews

@@
 pacman::p_load(papaja,
+               knitr,
                readr,
@@
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructBehaviorGap2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
-empirical choice patterns indicate that in DfD people choose as if a small-probability outcome is given more weight in the evaluation of a prospect than would be warranted by its objective probability, following the principle of mathematical expectation (see below);
+empirical choice patterns in DfD deviate from the principle of expected value (EV) maximization (see below) as if a small-probability outcome is given more weight than would be warranted by its objective probability;
 in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcome is given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
@@
 Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
-As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes.
+As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities and to follow the principle of EV maximization, the reliance on small samples could explain the as-if underweighting of rare outcomes.
 
@@
 Specifically, considering choices between a two-outcome prospect and a safe prospect, the proposed model is used to simulate the evidence accumulation process for different combinations of switching probabilities and threshold values.
-Then, on the basis of choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], it is shown that the simulated choices converge to the solutions of the principle of mathematical expectation for decreasing switching probabilities, but reflect an increasingly pronounced as-if underweighting of rare outcomes, the more the switching probabilities increase.
+Then, on the basis of choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], it is shown that the simulated choices converge to the solutions of the principle of EV maximization for decreasing switching probabilities, but reflect an increasingly pronounced as-if underweighting of rare outcomes, the more the switching probabilities increase.
 The analysis also shows that these differences between switching probabilities remain stable for different threshold values.
@@
 To this end, this paper argues that the mind may rely on different sampling strategies or switching probabilities, respectively, to change for which differences in the latent properties of prospects evidence is accumulated.
-Before presenting the model and the computational analysis, the following section provides a formal definition of prospects and reviews how CPT can be used to describe choices between prospects in terms of deviations from the principle of mathematical expectation.
+Before presenting the model and the computational analysis, the following section provides a formal definition of prospects and reviews how CPT can be used to describe choices between prospects in terms of deviations from the principle of EV maximization.
 
@@
 
-The choices people actually make between prospects are often described in terms of deviations from the principle of mathematical expectation, according to which the prospect with the largest expected value (EV)
+The choices people actually make between prospects are often described in terms of deviations from the principle of EV maximization, according to which the prospect with the largest EV
 $$
@@
 To *describe* how people's actual choices deviate from this principle [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, which were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
-Together, these empirical choice patterns indicate a violation of the principle of mathematical expectation and the expected utility (EU) principle [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
+Together, these empirical choice patterns indicate a violation of the principle of EV and expected utility (EU) maximization [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
 CPT and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT may be amended by a stochastic choice rule to account for the probabilistic nature of choices [@rieskampProbabilisticNaturePreferential2008].
@@
   geom_line(aes(color = gamma)) +
-  scale_color_viridis(option = "plasma") + 
+  scale_color_viridis(option = "viridis") + 
   geom_abline(intercept = 0, slope = 1, color = "gray", linetype = "dashed")
@@
 
-To summarize the preceding paragraphs, CPT is data model that can be used to describe choices between prospects by capturing systematic deviations from the principle of mathematical expectation in the parameter estimates of its value and weighting function.
+To summarize the preceding paragraphs, CPT is data model that can be used to describe choices between prospects by capturing systematic deviations from the principle of EV maximization in the parameter estimates of its value and weighting function.
 Importantly, each estimated weighting function implies a weighting pattern.
@@
 
-We consider the sampling paradigm and a choice between two prospects denoted by the distributions $P'^X$ and $P'^Y$ of the discrete random variables $X$ and $Y$, respectively.
+We consider the sampling paradigm and a choice between two prospects denoting the distributions $P'^X$ and $P'^Y$ of the discrete random variables $X$ and $Y$, respectively.
 The model assumes that the information-processing chain starts at random with a stochastic process on one of the two random variables.
@@
 In other words, the switching probability is the probability with which the stochastic process on the current random variable stops and a new stochastic process on the other random variable starts with the subsequently sampled outcome.
-To implement an evidence accumulation process, the model assumes that each time after a new stochastic process was started and terminated on both random variables, their respective values are compared, with the prospect underlying the stochastic process with the greater final value receiving a round-win.
-Accordingly, for the prospect $P'^X$, this stage is modeled by the mapping
+To implement an evidence accumulation process, the model assumes that each time after a new stochastic process was started and terminated on both random variables, their respective values---i.e., the means over the sequences---are compared, with the prospect underlying the stochastic process with the greater final value receiving a round win.
+Accordingly, for the prospect $P'^X$, this stage is modeled as the mapping
 $$
@@
 where $Z^X$ is a random variable that takes only the two values $0$ and $1$, denoting a lost or won mean comparison, respectively. 
-The model assumes that a round consisting of two stochastic processes---i.e., one from each prospect---and the subsequent comparison of their values is repeated until the sum of round wins for one of the two prospects reaches a threshold $\theta \in \mathbb{N}$.
+The model assumes that a round consisting of a pair of stochastic processes---i.e., one for each prospect---and the subsequent comparison of their final values is repeated until the sum of round wins for one of the two prospects reaches a threshold $\theta \in \mathbb{N}$.
 Similar to the switching probability, it is assumed that the threshold is adopted prior the start of the information-processing chain and is fixed throughout.
@@
 ### Model Predictions
+
+Below, the key predictions concerning the effects of the model parameters---i.e., the switching probability $\psi$ and the threshold $\theta$---on the length of the information-processing chain and the final choice are outlined.
+In addition, previous research has shown that differences as to how information about the properties of prospects is processed can translate to characteristic shapes of CPT's value and weighting function [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021].
+Respectively, this section also contains predictions about the potential relations between $\psi$ and $\theta$ and the CPT parameters.
+
+#### Length of Information-Processing Chain
+
+The model predicts the overall number of sampled outcomes to increase with thresholds.
+Specifically, the required number of independent mean comparisons increases with thresholds.
+Then, since each comparison is based on its own pair of stochastic processes, an increase in thresholds translates to a larger number of required stochastic processes and, ceteris paribus, therefore also to a larger overall number of sampled outcomes.
+In turn, the model predicts the overall number of sampled outcomes to decrease with increasing switching probabilities.
+Specifically, each stochastic process is predicted to terminate faster, the higher the probability that the subsequent outcome is sampled from the other prospect---i.e., the switching probability.
+Accordingly, an increase in the switching probability leads to shorter stochastic processes which translates, ceteris paribus, to a smaller overall number of sampled outcomes.
+
+#### Final Choice
+
+First note that the threshold and switching probability can be used to alter the degree to which the evidence accumulation process resembles the summary or the round-wise strategy.
+That is, for low thresholds and switching probabilities, only a few mean comparisons based on pairs of long stochastic processes---i.e., large samples---are carried out, thereby resembling the summary strategy.
+Accordingly, for such a parameter combination, the model tends to choose the prospect that possesses the larger EV.
+In turn, for high thresholds and switching probabilities, many mean comparisons based on pairs of short stochastic process---i.e., small samples---are carried out, thereby resembling the round-wise strategy.
+Accordingly, for such a parameter combination, the model tends to choose the prospect that is more likely to return a higher outcome.
+Yet, if the prospect that is more likely to return a higher outcome does not also possess the higher EV, the parameter combination resembling the round-wise strategy is predicted to cause a deviation form the principle of EV maximization.
+
+Now, more specifically, because the switching probability is predicted to alter the length of the stochastic processes underlying each mean comparison, the switching probability should affect whether a low-probability outcome contributes to the majority of the required mean comparisons about as much as would be warranted based on its objective probabilities, or whether it contributes rather less.
+Specifically, for short stochastic processes, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur over the course of such a process to be smaller rather than larger than their latent objective probabilities.
+Respectively, if the small-probability outcome is smaller (larger) than the expected value, high switching probabilities---and therefore pairs of short stochastic processes---cause the mean to be an inflated (deflated) estimate of the expected value.
+Thus, high switching probabilities are predicted to cause an as-if underweighting of rare outcomes that can translate to choices that deviate from the principle of EV maximization.
+In turn, low switching probabilities---and therefore pairs of long stochastic processes---cause the mean to closely correspond to the expected value, leading to choices that tend to conform the principle of EV maximization.
+
+Because each comparison’s contribution to the accumulated evidence is weighted equally, the predictions made for a given switching probability should become more robust as the thresholds and therefore the number of independent comparisons increases.
+The thresholds therefore serve to implement
+
+#### Cumulative Prospect Theory
 

### 2022-03-25 manuscript.Rmd
Reviews introduction

@@
 The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the choice alternatives between which people can choose.
-Indeed, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
-Decision making can therefore be understood as an information-processing problem whose solution requires a selection among choice alternatives.
+Indeed, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
+Therefore, decision making can be understood as an information-processing problem whose solution requires a selection among choice alternatives.
 
-Now, let a *prospect* be a choice alternative that possesses only two kinds of fundamental properties: the possible outcomes of the alternative (e.g., monetary gains or losses of some amount) and the probabilities with which these outcomes occur following the choice of the alternative.
-Importantly, the information that inputs provide about these properties of a prospect can come in different forms.
-For example, in *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
-Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in similar past decisions.
+Now, let a *prospect* be a choice alternative that possesses only two kinds of fundamental properties: the possible outcomes of the alternative (e.g., gains or losses of some amount) and the probabilities with which these outcomes occur following the choice of the alternative.
+Importantly, the information that the inputs provide about these properties can come in different forms.
+Specifically, in *decisions from description* (DfD), the inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
+Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospect was chosen in similar past decisions.
 The inputs to DfE therefore take the form of sampled outcomes.
@@
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructBehaviorGap2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
-empirical choice patterns in DfD deviate from the principle of expected value (EV) maximization (see below) as if a small-probability outcome is given more weight than would be warranted by its objective probability;
-in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcome is given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+empirical choice patterns in DfD deviate from the principle of expected value (EV) maximization (see below), as if people give more weight to small-probability outcomes than would be warranted by their objective probabilities;
+in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcomes are given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
 Hereafter, these choice patterns are referred to as the *as-if overweighting* and *as-if underweighting of rare outcomes*, respectively.
 
-Similar to other behavioral phenomena that could be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE could be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @plonskyRelianceSmallSamples2015; @wulffMetaanalyticReviewTwo2018].
-Specifically, following from the laws of large numbers [see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
-In such a case, then, or in the less strict case of large samples, the binomial distributions of the outcomes can be approximated by a symmetric normal distribution [cf.
-@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
+Similar to other behavioral phenomena that can be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE can be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+More specifically, following from the laws of large numbers [see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
+In such a case or in the less strict case of large samples, then, the binomial distribution of each outcome can be approximated by a symmetric normal distribution.^[<!--Open footnote-->The binomial distribution of an outcome is the probability distribution of the number of times an outcome occurs in a sample.
+According to the *de Moivre-Laplace theorem* [see, e.g., @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015], the binomial distribution can be approximated by a normal distribution given a large number of sampled outcomes.
+Respectively, for large samples, the relative relative frequencies with which an outcome occurs in the sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher and vice versa.<!--Close footnote-->]
 However, for samples of small size, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
 Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
-As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities and to follow the principle of EV maximization, the reliance on small samples could explain the as-if underweighting of rare outcomes.
+As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities---without correcting for the sampling error---and to follow the principle of EV maximization, the reliance on small samples could explain the as-if underweighting of rare outcomes.
 
-<!--Now, sequential sampling models of decision making [e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993; @markantModelingChoiceSearch2015; @ratcliffComparisonSequentialSampling2004] form one class of process models that provide an algorithmic link between the actual sampling process and the choices in DfE.
-That is, in one paradigm used to study DfE, namely, the sampling paradigm [see @weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
-To relate the sampling process to the final choice, sequential sampling models assume that the entire information-processing chain upfront the choice takes the form of an evidence accumulation process over time, with choices becoming more accurate the more evidence must be accumulated.
-Specifically, considering the choice between two prospects, these models assume that the prospects' outcomes are sequentially sampled and integrated into dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-Notably, since the thresholds determine how much (more) evidence a prospect must accumulate in order to be chosen and since a decrease in the threshold leads to a decrease in the number of outcomes that must be sampled to reach this threshold, a sequential sampling model may be used to relate the reliance on small samples to an as-if underweighting of rare outcomes [see @markantModelingChoiceSearch2015].
-That is, for low thresholds, small-probability outcomes are predicted to contribute less (rather than more) to the accumulated evidence than would be warranted by their objective probabilities because of the positive skewness of their binomial distribution.
-In turn, the higher a threshold, and thus the higher the number of outcomes that must be sampled, the more should the amount of evidence contributed by small-probability outcomes correspond to what would be objectively warranted.-->
-
-Yet, some studies show that the as-if underweighting of rare outcomes may appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
-To this end, this paper argues that there may be a discrepancy between the overall number of sampled outcomes and the size of the samples that the mind actually relies on to evaluate the prospects or to make an inference about their latent properties, respectively.
-However, in contrast to other approaches, this paper does not assume that some of the sampled outcomes are discounted [e.g., @hertwigDecisionsExperienceEffect2004] or ignored [e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015].
-Rather, a core assumption of this paper is that any number of outcomes sampled from a prospect may either be integrated into the same sample<!-- ---as it is implied by the sequential sampling models described above--- --> or into multiple respectively smaller samples.
-Then, this paper presents a process model that links the actual sampling process to the choices in DfE and demonstrates that a reliance on multiple small samples can cause an as-if underweighting of rare outcomes while fully accounting for a large number of sampled outcomes.
+Yet, studies show that the as-if underweighting of rare outcomes may appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes correspond closely to the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
+Respectively, in the current paper it is assumed that there may be a discrepancy between the overall number of sampled outcomes and the size of the samples that the mind relies on in the evaluation of prospects.
+However, in contrast to other approaches, it is not assumed that some of the sampled outcomes are discounted [see, e.g., @hertwigDecisionsExperienceEffect2004, who assume recency effects] or ignored [see, e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015, who assume that only outcomes that followed some sequential pattern are considered].
+Rather, assuming that any number of outcomes sampled from a prospect may either be integrated into the same sample or into multiple smaller samples, this paper presents a computational model that shows that---given a reliance on multiple small samples---an as-if underweighting of rare outcomes can occur, even if a large number of sampled outcomes is fully accounted for.
 
 Therefore, consider first the finding that *sampling strategies* were indicative for the final choice in DfE.
-Specifically, in one paradigm used to study DfE, namely, the sampling paradigm [see @weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
+Specifically, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
 Considering this paradigm and the choice between two prospects, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^[<!--Open footnote-->Note that @hillsInformationSearchDecisions2010 proposed two paradigmatic sampling strategies, where prospects are either switched just once (comprehensive sampling) or after each sampled outcome (piecewise sampling).
@@
 1788].
-Respectively, in the current paper sampling strategies are defined as switching probabilities (see below).
+Respectively, in the current paper sampling strategies are defined as switching probabilities.
 <!--Close footnote-->] 
 and proposed two different decision strategies that people may adopt.
-That is, for a summary decision strategy, the prospect is chosen that produced the greater mean across all sampled outcomes.
-In turn, for a round-wise decision strategy, the prospect is chosen that produced the greater outcome most of the time.
-In other words, the round-wise strategy assumes that over multiple rounds one outcome from each of the two prospects is sampled.
-In each round, then, the two sampled outcomes are compared and the prospect is chosen that wins most of these comparison rounds.
-Then, @hillsInformationSearchDecisions2010 found that the choices of people who switched frequently between prospects during the sampling phase were better predicted by assuming that they adopted a round-wise strategy (rather than a summary strategy), and that this predictive pattern reversed for people who switched infrequently.
+That is, for a summary strategy, it is assumed that the prospect is chosen which produced the greater mean across all sampled outcomes.
+In turn, for a round-wise strategy, it is assumed that over multiple rounds one outcome from each of the two prospects is sampled and that the prospect is chosen for which in most of the rounds the higher outcome was sampled.
+Then, @hillsInformationSearchDecisions2010 found that the choices of people who switched frequently between prospects during the sampling phase were better predicted by a round-wise strategy (rather than a summary strategy), and that this predictive pattern reversed for people who switched infrequently.
 
 Now, one explanation for such a reversed predictive pattern would be if the differences in the sampling strategies determine which of the two decision strategies is used.
-To this end, this paper presents a model that provides an algorithmic link between the *switching probability*---i.e., the probability of sampling outcomes from different prospects in direct succession during the sampling phase---, the decision strategy, and the respective choice.
-That is, the proposed model is such that the higher (lower) the switching probability during the sampling phase, the more the evaluation of the prospects resembles the round-wise strategy (summary strategy).
-However, to allow for a gradual transition from the summary to the round-wise strategy with increases in the switching probability, the model also captures hybrids of both strategies.
-Specifically, the proposed model accumulates the evidence obtained from the comparisons between sample means---i.e.
-won comparisons---with the size of the samples underlying each mean comparison decreasing with an increase in the switching probability, and thresholds determining how much (more) of such mean comparisons a prospect must win in order to be chosen.
-Thus, the model presented in this paper is such that the higher (lower) the switching probabilities and the higher (lower) the thresholds, the more the evaluation of prospects or the evidence accumulation process, respectively, resembles the round-wise strategy (summary strategy).
+To this end, this paper presents a computational model that provides a link between *switching probabilities*---i.e., the probability of sampling outcomes from different prospects in direct succession during the sampling phase---and the decision strategies.
+Specifically, the proposed model accumulates the outcomes obtained from the comparisons between sample means, with switching probabilities determining the size of the samples underlying each mean comparison and thresholds determining how much (more) of such comparisons a prospect must win in order to be chosen.
+Accordingly, the model is such that the higher (lower) the switching probabilities and the higher (lower) the thresholds, the more the accumulation process resembles the round-wise (summary) strategy.
 
-Moreover, this paper demonstrates in a computational analysis that the evaluation of prospects, while taking into account an increasing number of sampled outcomes, can rely on multiple small samples, causing an as-if underweighting of rare outcomes.
-Specifically, considering choices between a two-outcome prospect and a safe prospect, the proposed model is used to simulate the evidence accumulation process for different combinations of switching probabilities and threshold values.
-Then, on the basis of choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], it is shown that the simulated choices converge to the solutions of the principle of EV maximization for decreasing switching probabilities, but reflect an increasingly pronounced as-if underweighting of rare outcomes, the more the switching probabilities increase.
-The analysis also shows that these differences between switching probabilities remain stable for different threshold values.
-Accordingly, the computational analysis substantiates the claim that the reliance on (multiple) small samples, but not necessarily the consideration of a small number of sampled outcomes, causes an as-if underweighting of rare outcomes in DfE.
-In other words, because the switching probabilities change the size of the samples underlying each mean comparison, the model predicts them to affect whether a low-probability outcome contributes to the majority of required mean comparisons about as much as would be warranted based on its objective probabilities, or whether they contribute rather less.
-Yet, since each comparison's contribution to the accumulated evidence is weighted equally in the form of round wins, the model does not predict the thresholds to have a similar effect.
-Rather, whatever systematic differences in the latent properties of prospects may be represented in a mean comparison, should be more accurately assessed as the thresholds---and therefore also the number of sampled outcomes that are taken into account during the evaluation of prospects---increase.
-To this end, this paper argues that the mind may rely on different sampling strategies or switching probabilities, respectively, to change for which differences in the latent properties of prospects evidence is accumulated.
-Before presenting the model and the computational analysis, the following section provides a formal definition of prospects and reviews how CPT can be used to describe choices between prospects in terms of deviations from the principle of EV maximization.
+Using the proposed model, this paper shows in a computational analysis that an as-if underweighting of rare outcomes can occur even if a large number of sampled outcomes is fully accounted for.
+Specifically, considering choices between a two-outcome prospect and a safe prospect, the model is used to simulate the accumulation process for different combinations of switching probabilities and thresholds.
+Considering choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], the analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
+Importantly, the analysis also shows that these differences between switching probabilities remain stable with increasing thresholds.
+In other words, the proposed model predicts an as-if underweighting of rare outcomes to occur when high switching probabilities cause the accumulation process to unfold over mean comparisons that are based on small samples.
+Thus, the analysis substantiates the claim that not only the reliance on just a portion of a large number of sampled outcomes can explain an as-if underweighting of rare outcomes in DfE, but also the reliance on multiple or many small samples.
+Before presenting the model and the computational analysis, the following section provides a formal definition of prospects and reviews how CPT can be used to capture deviations from EV maximization.
 
@@
 Below, the key predictions concerning the effects of the model parameters---i.e., the switching probability $\psi$ and the threshold $\theta$---on the length of the information-processing chain and the final choice are outlined.
-In addition, previous research has shown that differences as to how information about the properties of prospects is processed can translate to characteristic shapes of CPT's value and weighting function [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021].
+In addition, previous research has shown that differences as to how information about the properties of prospects is processed can translate to characteristic shapes of CPT's value and weighting function [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021; @stewartDecisionSampling2006].
 Respectively, this section also contains predictions about the potential relations between $\psi$ and $\theta$ and the CPT parameters.
@@
 Because each comparison’s contribution to the accumulated evidence is weighted equally, the predictions made for a given switching probability should become more robust as the thresholds and therefore the number of independent comparisons increases.
-The thresholds therefore serve to implement
+The thresholds therefore serve to implement a speed-accuracy trade-off of the form that whatever systematic differences in the latent properties of prospects may be represented in a mean comparison, should be more accurately assessed as the thresholds increase.
+Hence, the as-if underweighting of rare outcomes that is predicted for high switching probabilities is predicted to remain and become more robust the higher the thresholds are.
+Respectively, the model should substantiate the claim made at the outset of the paper,
+namely, that the reliance on multiple small samples---in the form of pairs of short stochastic processes---can cause an as-if underweighting of rare outcomes while fully accounting for a large number of sampled outcomes.
 
@@
 
-```{r eval=FALSE}
-predictions <- tibble("Simulation Pararameter" = c("s", "$\\theta$"),
-                      "$\\gamma$" = c(0,0),
-                      "$\\delta$" = c(0,0),
-                      "$\\alpha$" = c(0,0))
-apa_table(predictions, caption = "Model Predictions", escape = FALSE)
+Since CPT is a statistical or data model designed to capture deviations from the principle of EV maximization, the predicted effects of the model parameters $\psi$ and $\theta$ on the final choices may also translate to the estimates of the parameters in CPT' value and weighting function.
+Hence, this section elaborates how the differences in the predictions made for the model parameters may be described in CPT' parameters.
+Therefore, the value function of Tversky and Kahneman [-@tverskyAdvancesProspectTheory1992, see Equation (8)] and the weighting function of Goldstein and Einhorn [-@goldsteinExpressionTheoryPreference1987, see Equation (10)] are used.
+
+Now, in the previous two sections, it was predicted that switching probabilities change the length of the stochastic processes underlying each mean comparison and that these changes cause changes as to which prospect is chosen.
+Specifically, for low switching probabilities it was predicted that the stochastic processes are rather long and cause a mean comparison to be indicative for differences in the expected value, thereby resembling the summary strategy.
+In turn, for high switching probabilities it was predicted that the stochastic processes are rather short and cause a mean comparison to be indicative for which prospect produces the higher outcome most of the time, thereby resembling the round-wise strategy.
+
+Because for low switching probabilities the prospect should be chosen that possesses the larger expected value, we predict the parameters of the value and weighting function to be in line with a linear weighting, therefore to be close to 1.
+Now, because for high switching probabilities the prospect is chosen that produces the greater outcome most of the time, it is predicted that small-probability outcomes are underweighted and and high-probability outcomes are overweighted.
+Respectively, it is assumed that $\gamma$ increases with the switching probability.
+More specifically, because each comparison is weighted equally the prospect should win, that produces the higher outcome with a probability greater than chance. 
+Accordingly, $\delta$ should be such that cumulative probabilities smaller (greater) than $.5$ are underweighted (overweighted).
+
+```{r}
+predictions <- tibble("CPT parameter" = 
+                        c("$\\gamma$",
+                          "$\\delta$",
+                          "$\\alpha$"),
+                      "Predictions for changes in $\\psi$" = 
+                        c("$\\geq 1$, increases with $\\psi$",
+                          "1, no effect of $\\psi$",
+                          "$\\leq 1$, decreases with increasing $\\psi$"))
+apa_table(predictions, caption = "Model Predictions", note = "The prediction for changes in $\\psi$ should become more robust for increasing values of $\\theta$.", escape = FALSE)
 ```

### 2022-03-27 manuscript.Rmd
Draft Introduction

@@
 Indeed, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
-Therefore, decision making can be understood as an information-processing problem whose solution requires a selection among choice alternatives.
+<!--Therefore, decision making can be understood as an information-processing problem whose solution requires a selection among choice alternatives.-->
 
@@
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructBehaviorGap2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
-empirical choice patterns in DfD deviate from the principle of expected value (EV) maximization (see below), as if people give more weight to small-probability outcomes than would be warranted by their objective probabilities;
-in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcomes are given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+choice patterns in DfD deviate from the principle of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities;
+in turn, in DfE, choice patterns deviate from EV maximization as if the same small-probability outcomes are given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
 Hereafter, these choice patterns are referred to as the *as-if overweighting* and *as-if underweighting of rare outcomes*, respectively.
 
-Similar to other behavioral phenomena that can be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE can be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+Similar to other behavioral phenomena that can be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes can be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on in DfE [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
 More specifically, following from the laws of large numbers [see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
@@
 According to the *de Moivre-Laplace theorem* [see, e.g., @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015], the binomial distribution can be approximated by a normal distribution given a large number of sampled outcomes.
-Respectively, for large samples, the relative relative frequencies with which an outcome occurs in the sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher and vice versa.<!--Close footnote-->]
+Respectively, for large samples, the relative relative frequencies with which an outcome occurs in the sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.<!--Close footnote-->]
 However, for samples of small size, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
@@
 
-Yet, studies show that the as-if underweighting of rare outcomes may appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes correspond closely to the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
-Respectively, in the current paper it is assumed that there may be a discrepancy between the overall number of sampled outcomes and the size of the samples that the mind relies on in the evaluation of prospects.
+Yet, some studies show that the as-if underweighting of rare outcomes may appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes correspond closely to the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
+Respectively, in the current paper it is assumed that there may be a disconnect between the overall number of sampled outcomes and the size of the samples the mind relies on in the evaluation of prospects.
 However, in contrast to other approaches, it is not assumed that some of the sampled outcomes are discounted [see, e.g., @hertwigDecisionsExperienceEffect2004, who assume recency effects] or ignored [see, e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015, who assume that only outcomes that followed some sequential pattern are considered].
-Rather, assuming that any number of outcomes sampled from a prospect may either be integrated into the same sample or into multiple smaller samples, this paper presents a computational model that shows that---given a reliance on multiple small samples---an as-if underweighting of rare outcomes can occur, even if a large number of sampled outcomes is fully accounted for.
+Rather, assuming that any number of outcomes sampled from a prospect may either be integrated into the same sample or into multiple smaller samples, this paper presents an accumulation model that shows that---given a reliance on multiple or many small samples---an as-if underweighting of rare outcomes can occur, even if a large number of sampled outcomes is fully accounted for.
 
@@
 That is, for a summary strategy, it is assumed that the prospect is chosen which produced the greater mean across all sampled outcomes.
-In turn, for a round-wise strategy, it is assumed that over multiple rounds one outcome from each of the two prospects is sampled and that the prospect is chosen for which in most of the rounds the higher outcome was sampled.
+In turn, for a round-wise strategy, it is assumed that over multiple rounds two sampled outcomes---i.e., one from each of the prospects---are compared and that the prospect is chosen which won the comparison in most rounds.
 Then, @hillsInformationSearchDecisions2010 found that the choices of people who switched frequently between prospects during the sampling phase were better predicted by a round-wise strategy (rather than a summary strategy), and that this predictive pattern reversed for people who switched infrequently.
@@
 
-Using the proposed model, this paper shows in a computational analysis that an as-if underweighting of rare outcomes can occur even if a large number of sampled outcomes is fully accounted for.
-Specifically, considering choices between a two-outcome prospect and a safe prospect, the model is used to simulate the accumulation process for different combinations of switching probabilities and thresholds.
-Considering choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], the analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
-Importantly, the analysis also shows that these differences between switching probabilities remain stable with increasing thresholds.
+The current paper discusses and demonstrates in a computational analysis how such a simple accumulation model can explain an as-if underweighting of rare outcomes, even if a large number of sampled outcomes is fully accounted for.
+More specifically, since the switching probabilities alter the size of the samples underlying each mean comparison, the model predicts the switching probabilities to affect whether a low-probability outcome contributes to the majority of required mean comparisons about as much as would be warranted by its objective probabilities, or whether it contributes rather less.
+Respectively, if the small-probability outcome is smaller (larger) than the EV, high switching probabilities cause the mean to be an inflated (deflated) estimate of the EV in most of the comparisons, which can translate to an as-if underweighting of rare outcomes, irrespective of what the thresholds determine the required number of mean comparisons to be.
+Yet, since the EV is not the only property which can be used to distinguish among the prospects, the proposed model shows how the mind may rely on different sampling strategies to change which differences in the latent properties of prospects evidence is accumulate for.
+Specifically, for low switching probabilities, the accumulation process unfolds over mean comparisons based on large samples and is therefore more indicative for differences in the EV; in turn, for high switching probabilities, the accumulation process unfolds over mean comparisons based on small samples and is therefore more indicative for differences in the probability to produce a higher outcome than the respective other prospect most of the time.
+In either case, then, the model implements a speed-accuracy trade-off of the form that the respective differences in the latent properties are more accurately assessed, the larger the thresholds are, i.e., the more evidence must be accumulated in favor of a prospect.
+
+To substantiate the discussion, the model is used to simulate the accumulation process for different combinations of switching probabilities and thresholds and to predict choices between a two-outcome prospect and a safe prospect, respectively.
+Considering choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], the computational analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
+Importantly, the analysis also shows that the differences between switching probabilities become more pronounced with increasing thresholds.
 In other words, the proposed model predicts an as-if underweighting of rare outcomes to occur when high switching probabilities cause the accumulation process to unfold over mean comparisons that are based on small samples.
 Thus, the analysis substantiates the claim that not only the reliance on just a portion of a large number of sampled outcomes can explain an as-if underweighting of rare outcomes in DfE, but also the reliance on multiple or many small samples.
+Moreover, the analysis shows that an as-if underweighting of rare outcomes cannot be equated with inaccurate inferences about latent properties---e.g., the EVs---that carry over to the subsequent choices.
+Rather the opposite, an as-if underweighting of rare outcomes can also be caused by an accurate assessment of the differences among prospects in the latent probability to produce a higher outcome most of the time.
 Before presenting the model and the computational analysis, the following section provides a formal definition of prospects and reviews how CPT can be used to capture deviations from EV maximization.
@@
 These fundamental properties are considered the possible outcomes of a choice alternative and the probabilities with which these outcomes occur following the choice of the alternative.
-Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs are prospects (or: gambles).
+Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs are prospects.
 As such, prospects can be understood as the distribution of a discrete random variable, for which the following section briefly provides an axiomatic basis.
@@
 Following @kolmogorovFoundationsTheoryProbability1950 and adopting the symbolic notation from @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, let the tuple $(\Omega, \mathcal{F}, P)$ be a probability space.
-Accordingly, $\Omega$ is a finite sample space with each element $\omega$ in $\Omega$ denoting a possible consequence of choosing the respective prospect.
-$\mathcal{F}$ is the power set $\mathcal{P}(\Omega)$ with each element $A$ in $\mathcal{F}$ being a subset of $\Omega$, also denoted a random event.
+Accordingly, $\Omega$ is a finite sample space with each element $\omega \in \Omega$ denoting a possible consequence of choosing the respective prospect.
+$\mathcal{F}$ is the power set $\mathcal{P}(\Omega)$ with each element $A \in \mathcal{F}$ being a subset of $\Omega$, also denoted a random event.
 $P$ is the probability measure
@@
 $$
-where each element $P'$ can itself be considered a set of outcome-probability pairs $\{(x_i, p_X(x_i)\}$.
+where each element $P'$ can itself be considered a set of outcome-probability pairs $\{(x_i, p_X(x_i)\}_{i \in \mathbb{N}}$.
 
@@
 $$ 
-should be chosen (EV maximization).
-To *describe* how people's actual choices deviate from this principle [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, which were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
-Together, these empirical choice patterns indicate a violation of the principle of EV and expected utility (EU) maximization [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
-CPT and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by maximizing^[<!--Open footnote-->Note that CPT may be amended by a stochastic choice rule to account for the probabilistic nature of choices [@rieskampProbabilisticNaturePreferential2008].
-Stochastic choice rules [@stottCumulativeProspectTheory2006, for an overview] make the choice of a prospect more probable the better its valuation relative to those of other prospects.<!--Close footnote-->]
-the value
+should be chosen.
+To *describe* how people's actual choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, which were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
+Together, these empirical choice patterns indicate a violation of EV and expected utility (EU) maximization [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
+CPT and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by assuming that people maximize the value
 $$

### 2022-03-29 manuscript.Rmd
Update model predictions

@@
 Indeed, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
-<!--Therefore, decision making can be understood as an information-processing problem whose solution requires a selection among choice alternatives.-->
+Respectively, decision making can be understood as an information-processing problem whose solution requires a selection among choice alternatives.
 
@@
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructBehaviorGap2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
-choice patterns in DfD deviate from the principle of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities;
-in turn, in DfE, choice patterns deviate from EV maximization as if the same small-probability outcomes are given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+choice patterns in DfD deviate from the solutions of expected value (EV) maximization, as if small-probability outcomes were given more weight than would be warranted by their objective probabilities;
+in turn, in DfE, choice patterns deviate from the solutions of EV maximization as if the same small-probability outcomes were given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
 Hereafter, these choice patterns are referred to as the *as-if overweighting* and *as-if underweighting of rare outcomes*, respectively.
@@
 However, for samples of small size, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
-Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
-As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities---without correcting for the sampling error---and to follow the principle of EV maximization, the reliance on small samples could explain the as-if underweighting of rare outcomes.
+As a consequence, were the mind to use the relative frequencies of outcomes in a sample to infer their latent objective probabilities and to follow the principle of EV maximization, the as-if underweighting of rare outcomes in DfE could be explained by the reliance on small samples.
 
 Yet, some studies show that the as-if underweighting of rare outcomes may appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes correspond closely to the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
-Respectively, in the current paper it is assumed that there may be a disconnect between the overall number of sampled outcomes and the size of the samples the mind relies on in the evaluation of prospects.
-However, in contrast to other approaches, it is not assumed that some of the sampled outcomes are discounted [see, e.g., @hertwigDecisionsExperienceEffect2004, who assume recency effects] or ignored [see, e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015, who assume that only outcomes that followed some sequential pattern are considered].
+Respectively, there may be a disconnect between the overall number of sampled outcomes and the size of the samples the mind relies on in the evaluation of prospects.
+However, in contrast to other approaches, in the current paper it is not assumed that some of the sampled outcomes are discounted [see, e.g., @hertwigDecisionsExperienceEffect2004, who assume recency effects] or ignored [see, e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015, who assume that only outcomes that followed some sequential pattern are considered].
 Rather, assuming that any number of outcomes sampled from a prospect may either be integrated into the same sample or into multiple smaller samples, this paper presents an accumulation model that shows that---given a reliance on multiple or many small samples---an as-if underweighting of rare outcomes can occur, even if a large number of sampled outcomes is fully accounted for.
@@
 Rather the opposite, an as-if underweighting of rare outcomes can also be caused by an accurate assessment of the differences among prospects in the latent probability to produce a higher outcome most of the time.
-Before presenting the model and the computational analysis, the following section provides a formal definition of prospects and reviews how CPT can be used to capture deviations from EV maximization.
+Before presenting the model and the computational analysis, the following section provides a formal definition of prospects and reviews how CPT in general and its weighting function in particular can be used to capture deviations from EV maximization.
 
@@
 should be chosen.
-To *describe* how people's actual choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, which were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
+To *describe* how people's actual choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, where the latter were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
 Together, these empirical choice patterns indicate a violation of EV and expected utility (EU) maximization [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
@@
   \begin{cases}
-     w^+(P(X(\omega) \geq x_i)) - w^+(P(X(\omega) > x_i)) \quad \forall x_i \geq 0, \\
-     w^-(P(X(\omega) \leq x_i)) - w^-(P(X(\omega) < x_i)) \quad \text{else}
+     w^+(P(X \geq x_i)) - w^+(P(X > x_i)) \quad \forall x_i \geq 0, \\
+     w^-(P(X \leq x_i)) - w^-(P(X < x_i)) \quad \text{else}
      \; , 
@@
 
-Essentially, the proposed model is such that the cumulative decision weights derived for the outcomes may be greater or smaller than their objective probabilities, causing the transformed outcomes---i.e., the subjective values---to be over- or underweighted *in* CPT, respectively.
-<!--Accordingly, one may adopt an as-if weighting terminology, stating that people choose *as if* they maximized the value in (10) and applied the weighting pattern that was estimated in CPT.-->
-Now, several consequences for the weighting pattern that can be estimated in CPT follow from (9), which are reviewed next:
+Essentially, the model is such that the cumulative decision weights derived for the outcomes may be greater or smaller than their objective probabilities, causing the transformed outcomes---i.e., the subjective values---to be over- or underweighted *in* CPT, respectively.
+Accordingly, for the description of choices, one may adopt the as-if weighting terminology from the introduction by stating that people choose as if they maximized the value in (7) and applied the weighting pattern that was estimated in CPT.
+Importantly, the as-if prefix indicates that it cannot be concluded from the estimated weighting pattern that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, the mind processes the information about the choice alternatives in a way that the resulting choices translate to the estimated weighting pattern.
+The as-if weighting terminology is therefore reminiscent of the distinction between different levels of explanation [cf. @marrVisionComputationalInvestigation1982; @vanrooijTheoryTestHow2021].
+That is, CPT may be considered a computational-level theory that specifies the computational problem the mind faces when being confronted with the choice between prospects, and how this problem may be solved by the abstract calculus of CPT.
+However, as such, CPT cannot substitute algorithmic-level theories and process models that make claims about how exactly the mind transforms the inputs to the decision-making process into outputs which approximate the solutions of CPT [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
+Respectively, this paper uses CPT as a mere data model to show how differences in the information-processing chain upfront choices in DfE---considered in the following section---may cause particular weighting patterns, among them the as-if underweighting of rare outcomes which has been found to be a robust behavioral phenomena in DfE.
+To this end, the paper first continues to review the weighting patterns that can possibly estimated in CPT.
 
-* From the transformation of cumulative probabilities it necessarily follows that the value of a cumulative decision weight $\pi$ depends on the rank of the outcome $x$ for which $\pi$ is determined.
+Now, several consequences for the weighting pattern that can be estimated in CPT follow from (9):
 
-* The value of a cumulative decision weight depends on the estimated shape of the graph of $w$ or the weighting function's parameters, respectively.
+* From the transformation of cumulative probabilities it follows that the value of a cumulative decision weight $\pi$ depends on the rank of the outcome $x$ for which $\pi$ is determined.
+
+* The value of $\pi$ depends on the estimated shape of the graph of $w$ or the weighting function's parameters, respectively.
 That is, the shape of the graph of $w$ displays over which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
-Hence, assuming a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
+Hence, for a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
 
@@
 
-To summarize the preceding paragraphs, CPT is data model that can be used to describe choices between prospects by capturing systematic deviations from the principle of EV maximization in the parameter estimates of its value and weighting function.
+To summarize the preceding paragraphs, CPT is a statistical or data model that can be used to describe choices between prospects by capturing systematic deviations from EV maximization in the parameter estimates of its value and weighting function.
 Importantly, each estimated weighting function implies a weighting pattern.
@@
 For the description of such choices, one may then adopt the as-if weighting terminology from the introduction, by stating that people decide as if they were either underweighting or overweighting rare outcomes.
-
-To be clear, however, the as-if prefix indicates that it cannot be concluded from the estimated weighting pattern that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, the mind processes the information about the choice alternatives in a way that the resulting choices translate to the estimated CPT model.
-The as-if weighting terminology is therefore reminiscent of the distinction between different levels of explanation [@marrVisionComputationalInvestigation1982].
-That is, CPT may be considered a computational-level theory that specifies the computational problem the mind faces when being confronted with the choice between prospects, and how this problem may be solved by the abstract calculus reviewed above.
-However, as such, CPT cannot substitute algorithmic-level theories that make claims about how exactly the mind transforms the inputs to the decision-making process into outputs which approximate the solutions of CPT's calculus [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
-Therefore, this paper uses CPT merely as a data model and continues to inquire how on the algorithmic level the mind may integrate sampling strategies into the information-processing chain upfront choices in DfE.
 
@@
 random variables are commonly assumed.]
-The inputs to DfE are then the realizations of the random variables in (11), which require different algorithms to be processed than do descriptions of the outcomes and their probabilities.
+The inputs to DfE are then the realizations of the random variables in (11), which require different algorithms to be processed than do descriptions of the outcomes and their probabilities in DfD.
 
@@
 However, the mind may also approximate such a process by using an algorithm that omits explicit inferences and directly accumulates evidence about the differences in latent properties from the sampled outcomes.
-To this end, sequential sampling models of decision making assume that the outcomes of prospects are sequentially sampled and integrated into dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DfE and has shown to explain some of the robust deviations from the EV or EU principle, respectively [@busemeyerDecisionFieldTheory1993; @bhatiaSequentialSamplingParadoxes2014], including the underweighting of rare outcomes in the sampling paradigm [@markantModelingChoiceSearch2015].
+To this end, sequential sampling models of decision making [e.g., @busemeyerDecisionFieldTheory1993] assume that the outcomes of prospects are sequentially sampled and integrated into dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DfE, and has shown to explain some of the robust deviations from EV maximization [see @busemeyerDecisionFieldTheory1993; @bhatiaSequentialSamplingParadoxes2014], including the underweighting of rare outcomes in the sampling paradigm [see @markantModelingChoiceSearch2015].
 Moreover, these models implement speed-accuracy tradeoffs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more (less) accurate but slower (faster) choices for high (low) thresholds.
 
-Yet, there are distinct latent properties that can be used to assess differences between prospects.
-Respectively, this paper presents a computational model which implements the summary and the round-wise decision strategy---for which either the prospect is chosen that produced the greater mean across all sampled outcomes or the prospect that won more comparisons between single sampled outcomes, respectively [see @hillsInformationSearchDecisions2010]---into a common evidence accumulation model.
-That is, the model accumulates the evidence obtained from a sequence of comparisons between sample means, with the size of the samples underlying each mean comparison decreasing with increasing switching probabilities.
-Accordingly, whereas the decision variables of the model capture how much (more) comparisons between sample means a prospect has won, the evidence accumulation process more closely resembles the round-wise strategy for high switching probabilities and small sample sizes, and the summary strategy for low switching probabilities and large sample sizes.
-Now, since for a large overall number of sampled outcomes the summary strategy is more indicative for differences in the EV and the round-wise strategy is more indicative for differences in the likelihood to produce a higher outcome than the respective other prospect, the proposed model shows how the mind may rely on different sampling strategies to change for which differences in the latent properties of prospects evidence is accumulated.
+Yet, there are several distinct properties that can be used to assess differences among the prospects.
+Specifically, the summary and the round-wise decision strategy---for which either the prospect is chosen that produced the greater mean across all sampled outcomes or the prospect that won more comparisons between single sampled outcomes, respectively [see @hillsInformationSearchDecisions2010]---can each be indicative for differences in a distinct latent property.
+That is, for a large number of sampled outcomes, the summary strategy is indicative for differences in the latent EV as the mean of a large collection of i.i.d.
+random variables converges to the EV of the respective random variable.
+In turn, the round-wise strategy is indicative for differences in the likelihood to produce a higher outcome than the other prospect.
+Respectively, in the following section, the summary and the round-wise strategy are implemented into a common accumulation model that shows how the mind may accumulate evidence for differences in distinct latent properties [see also @bhatiaChoiceRulesAccumulator2017, where heuristic choice rules are integrated into an accumulation model].
+More specifically, the proposed model accumulates the outcomes obtained from a sequence of comparisons between sample means, with the size of the samples underlying each mean comparison tending to be small (large) for high (low) switching probabilities.
+Accordingly, whereas the decision variables of the model capture how much (more) comparisons between sample means a prospect has won, the unfolding accumulation process more closely resembles the round-wise strategy for high switching probabilities and the summary strategy for low switching probabilities.
+Hence, the model also shows how the mind may rely on different sampling strategies to alter which differences in the latent properties of prospects evidence is accumulated for.
 
@@
 and terminates as soon as an outcome is sampled from the other prospect.
-The switching probability $\psi \in (0,1]$, which is adopted prior the start of the information-processing chain and is fixed throughout, controls the probability with which outcomes from different prospects are sampled in direct succession.
+The switching probability $\psi \in (0,1]$, which is assumed to be adopted prior the start of the information-processing chain and to be fixed throughout, controls the probability with which outcomes from different prospects are sampled in direct succession.
 In other words, the switching probability is the probability with which the stochastic process on the current random variable stops and a new stochastic process on the other random variable starts with the subsequently sampled outcome.
@@
 Below, the key predictions concerning the effects of the model parameters---i.e., the switching probability $\psi$ and the threshold $\theta$---on the length of the information-processing chain and the final choice are outlined.
-In addition, previous research has shown that differences as to how information about the properties of prospects is processed can translate to characteristic shapes of CPT's value and weighting function [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021; @stewartDecisionSampling2006].
+Moreover, previous research has shown that differences as to how information about the properties of prospects is processed can translate to characteristic shapes of CPT's value and weighting function [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021].
 Respectively, this section also contains predictions about the potential relations between $\psi$ and $\theta$ and the CPT parameters.
@@
 
-First note that the threshold and switching probability can be used to alter the degree to which the evidence accumulation process resembles the summary or the round-wise strategy.
+Note first that the thresholds and switching probabilities alter the degree to which the accumulation process resembles the summary or the round-wise strategy.
 That is, for low thresholds and switching probabilities, only a few mean comparisons based on pairs of long stochastic processes---i.e., large samples---are carried out, thereby resembling the summary strategy.
-Accordingly, for such a parameter combination, the model tends to choose the prospect that possesses the larger EV.
+Accordingly, for such parameter combinations, the model predicts the prospect to be chosen that possesses the larger EV.
 In turn, for high thresholds and switching probabilities, many mean comparisons based on pairs of short stochastic process---i.e., small samples---are carried out, thereby resembling the round-wise strategy.
-Accordingly, for such a parameter combination, the model tends to choose the prospect that is more likely to return a higher outcome.
-Yet, if the prospect that is more likely to return a higher outcome does not also possess the higher EV, the parameter combination resembling the round-wise strategy is predicted to cause a deviation form the principle of EV maximization.
+Accordingly, for such parameter combinations, the model predicts the prospect to be chosen that is more likely to return a higher outcome.
+Yet, if the prospect that is more likely to return a higher outcome does not possess the higher EV, the parameter combinations resembling the round-wise strategy are predicted to cause a deviation from the solutions of EV maximization.
 
-Now, more specifically, because the switching probability is predicted to alter the length of the stochastic processes underlying each mean comparison, the switching probability should affect whether a low-probability outcome contributes to the majority of the required mean comparisons about as much as would be warranted based on its objective probabilities, or whether it contributes rather less.
-Specifically, for short stochastic processes, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur over the course of such a process to be smaller rather than larger than their latent objective probabilities.
-Respectively, if the small-probability outcome is smaller (larger) than the expected value, high switching probabilities---and therefore pairs of short stochastic processes---cause the mean to be an inflated (deflated) estimate of the expected value.
-Thus, high switching probabilities are predicted to cause an as-if underweighting of rare outcomes that can translate to choices that deviate from the principle of EV maximization.
-In turn, low switching probabilities---and therefore pairs of long stochastic processes---cause the mean to closely correspond to the expected value, leading to choices that tend to conform the principle of EV maximization.
+Now, more specifically, because the switching probability is predicted to alter the length of the stochastic processes underlying each mean comparison, the switching probability should affect whether low-probability outcomes contribute to the majority of the required mean comparisons about as much as would be warranted based on their objective probabilities, or whether they contribute rather less.
+That is, for short stochastic processes, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur over the course of such a process to be smaller rather than larger than their latent objective probabilities.
+Respectively, if the small-probability outcome is smaller (larger) than the EV, high switching probabilities---and therefore pairs of short stochastic processes---cause the mean to be an inflated (deflated) estimate of the EV.
+Such an inflation and deflation of the means for high switching probabilities can then translate to an as-if underweighting of rare outcomes.
+Specifically, if the mean of the prospect with the lower (higher) EV is inflated (deflated), the outcome of the comparison between the means may be a reversal---in sign---of the outcome of a comparison between the EVs, leading to choices that take the form of an as-if underweighting of rare outcomes.
+Yet, if the mean of the prospect with the lower (higher) EV is deflated (inflated), the difference between the means is an amplification of the differences between the EV, which can actually simplify EV maximization [@hertwigDecisionsExperienceWhy2010].
+In turn, low switching probabilities---and therefore pairs of long stochastic processes---cause the mean to closely correspond to the EV, leading to choices that are in line with EV maximization.
 
-Because each comparison’s contribution to the accumulated evidence is weighted equally, the predictions made for a given switching probability should become more robust as the thresholds and therefore the number of independent comparisons increases.
-The thresholds therefore serve to implement a speed-accuracy trade-off of the form that whatever systematic differences in the latent properties of prospects may be represented in a mean comparison, should be more accurately assessed as the thresholds increase.
-Hence, the as-if underweighting of rare outcomes that is predicted for high switching probabilities is predicted to remain and become more robust the higher the thresholds are.
-Respectively, the model should substantiate the claim made at the outset of the paper,
-namely, that the reliance on multiple small samples---in the form of pairs of short stochastic processes---can cause an as-if underweighting of rare outcomes while fully accounting for a large number of sampled outcomes.
+Finally, because each comparison’s contribution to the accumulated evidence is weighted equally, the predictions made for given switching probabilities should become more robust as the thresholds and therefore the number of independent comparisons increases.
+That is, the thresholds implement a speed-accuracy trade-off of the form that whatever systematic differences in the latent properties of prospects may be represented in a sequence of mean comparisons, should be more accurately assessed as the thresholds increase.
+Accordingly, the as-if underweighting of rare outcomes that is predicted to occur for high switching probabilities should remain and become more pronounced the higher the thresholds are.
+Thus, the model's predictions should substantiate the claim made at the outset of the paper, namely, that the reliance on multiple or many small samples---in the form of comparisons between pairs of short stochastic processes---can cause an as-if underweighting of rare outcomes while fully accounting for a large number of sampled outcomes.
 
@@
 
-Since CPT is a statistical or data model designed to capture deviations from the principle of EV maximization, the predicted effects of the model parameters $\psi$ and $\theta$ on the final choices may also translate to the estimates of the parameters in CPT' value and weighting function.
-Hence, this section elaborates how the differences in the predictions made for the model parameters may be described in CPT' parameters.
-Therefore, the value function of Tversky and Kahneman [-@tverskyAdvancesProspectTheory1992, see Equation (8)] and the weighting function of Goldstein and Einhorn [-@goldsteinExpressionTheoryPreference1987, see Equation (10)] are used.
+To elaborate how the differences in the predictions made for the model parameters may be described in CPT's parameters, the value function of Tversky and Kahneman [-@tverskyAdvancesProspectTheory1992, see (8)] and the weighting function of Goldstein and Einhorn [-@goldsteinExpressionTheoryPreference1987, see (10)] are used.
+To simplify matters, the further discussion and the computational analysis are constrained to choices between a safe prospect---possessing just one outcome that occurs with certainty---and a two-outcome risky prospect.
+All outcomes are assumed to be positive and the safe outcome is assumed to fall between the the low-rank outcome, $x_{low}$, and the high-rank outcome, $x_{high}$, of the risky prospect in order to omit dominant prospects that always lead to a higher outcome than the respective other prospect.
 
-Now, in the previous two sections, it was predicted that switching probabilities change the length of the stochastic processes underlying each mean comparison and that these changes cause changes as to which prospect is chosen.
-Specifically, for low switching probabilities it was predicted that the stochastic processes are rather long and cause a mean comparison to be indicative for differences in the expected value, thereby resembling the summary strategy.
-In turn, for high switching probabilities it was predicted that the stochastic processes are rather short and cause a mean comparison to be indicative for which prospect produces the higher outcome most of the time, thereby resembling the round-wise strategy.
+Now, since for low switching probabilities the model tends to choose the prospect possessing the larger EV, the parameters of the value and weighting function are predicted to correspond to a linear weighting of outcomes and probabilities.
+Thus, the lower the switching probabilities, the more should the choices translate to parameter estimates that satisfy $\alpha = 1$, $\gamma = 1$, and $\delta = 1$.
+However, for high switching probabilities, the model predicts systematic deviations from the solutions of EV maximization, which take the form of an as-if underweighting of rare outcomes:
+More specifically, for $\psi = 1$, the model tends to choose the risky prospect, if the probability of its high-rank outcome satisfies $p_x(x_{high}) > .5$, irrespective of its EV.
+Vice versa, the model tends to choose the safe outcome, if $p_x(x_{high}) < .5$ is satisfied.
+Accordingly, for high switching probabilities, the weighting pattern should be such that the high-rank outcome is overweighted for $p_x(x_{high}) > .5$ and otherwise underweighted.
+Note now that the possible weighting patterns for choices between at most two-outcome prospects readily reduces to an over- or underweighting of the high-rank outcome [@zilkerNonlinearProbabilityWeighting2021]:
+$$
+\begin{aligned}
+  \pi_{high} &= w(p_x(x_{high})) \\
+  \pi_{low} &= w(p_x(x_{low}) + p_x(x_{high})) - w(p_x(x_{high})) \\
+  &= 1 - \pi_{high}
+  \; .
+\end{aligned}
+\tag{15}
+$$
+That is, the images of the weighting function equal the decision weights assigned to the high-rank outcome of the risky prospect.
+Hence, for high switching probabilities, the graph of the weighting function is predicted to run below the identity line for $p_x(x_{high}) < .5$---leading to an underweighting of small-probability outcomes---and above the identity line for $p_x(x_{high}) > .5$---leading to an overweighting of high-probability outcomes.
+Accordingly, the graph of the weighting function should take a S-shape, which is given by $\gamma > 1$ and $\delta = 1$.
+Yet, since the model tends to approximate the solutions of EV maximization the lower the switching probabilities are, the S-shape should be most pronounced for high switching probabilities.
+Thus, $\gamma$ should increase with $\psi$.
+Note further that the predicted shape of the weighting function for high switching probabilities reflects the round-wise strategy's sensitivity to differences in the outcome's probabilities.
+That is, the slope of the weighting function increases around the midpoint of the probability scale and flattens to both ends.
+reflecting that the round-wise strategy is more sensitive to the differences in the 
+Accordingly, the round-wise strategy
 
-Because for low switching probabilities the prospect should be chosen that possesses the larger expected value, we predict the parameters of the value and weighting function to be in line with a linear weighting, therefore to be close to 1.
-Now, because for high switching probabilities the prospect is chosen that produces the greater outcome most of the time, it is predicted that small-probability outcomes are underweighted and and high-probability outcomes are overweighted.
-Respectively, it is assumed that $\gamma$ increases with the switching probability.
-More specifically, because each comparison is weighted equally the prospect should win, that produces the higher outcome with a probability greater than chance. 
-Accordingly, $\delta$ should be such that cumulative probabilities smaller (greater) than $.5$ are underweighted (overweighted).
+Finally, an increase in the switching probability should lead to a more concave value function.
+Similar to the slope of the weighting function,
 
@@
 # Simulation Study
+
+Below
 
@@
   scale_shape_manual(values = c(4, 16)) +
-  scale_color_viridis_d(option = "plasma", end = .7) +
+  scale_color_viridis_d(option = "viridis", begin = .1, end = .7) +
   theme_apa()
@@
   scale_shape_manual(values = c(4, 16)) +
-  scale_color_viridis(option = "plasma") +
+  scale_color_viridis(option = "viridis") +
   theme_apa()
@@
   geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_color_viridis(option = "plasma") +
+  scale_color_viridis(option = "viridis") +
   scale_shape_manual(values = c(4, 16)) +
@@
   geom_line(data = wf_r, size = .5) +  #add curves for relative boundary
-  scale_color_viridis(option = "plasma") +
+  scale_color_viridis(option = "viridis") +
   theme_apa()
@@
   geom_line(data = vf_r, size = .5) + 
-  scale_color_viridis(option = "plasma") +
+  scale_color_viridis(option = "viridis") +
   theme_apa() + 

### 2022-03-30 manuscript.Rmd
Add abstract

@@
 
-abstract: |
-  Add abstract
+abstract: "In decisions from experience, systematic choices between prospects are based on the assessment of differences in their latent properties.
+Yet, distinct properties can be used to distinguish among the prospects, and the choices may vary respectively.
+This paper presents a model that shows how the mind may rely on sampling strategies---i.e., the probability of sampling outcomes from different prospects in direct succession (switching probability)---to alter which differences in the latent properties evidence is accumulated for.
+Specifically, the model sequentially samples outcomes from two prospects and accumulates the results obtained from a sequence of ordinal comparisons between sample means, with switching probabilities determining the size of the samples underlying each comparison and thresholds determining how much comparisons a prospect must win to be chosen.
+In a computational analysis, the model is used to simulate the information-processing chain for choices between two prospects, while varying switching probabilities and thresholds.
+The analysis shows that the accumulation process provides evidence for differences in the expected values when low switching probabilities cause each comparison to be carried out on large samples.
+In turn, when high switching probabilities cause the accumulation process to unfold over comparisons based on small samples, evidence is accumulated for differences in the probability to produce a higher outcome most of the time.
+The respective choices for high switching probabilities reflect an as-if underweighting of rare outcomes that becomes more pronounced with increasing thresholds, demonstrating that the reliance on many small samples can explain the as-if underweighting of rare outcomes, while a large number of sampled outcomes is fully accounted for.
+The analysis also shows that the differences in the information-processing chain translate to systematic differences in the parameter estimitates of cumulative prospect theory's value and weighting function."
 
-keywords          : ""
+keywords          : "risky choice, information sampling, evidence accumulation, cognitive modeling, cumulative prospect theory"
 wordcount         : ""

### 2022-03-31 manuscript.Rmd
Update simulation study

@@
 abstract: "In decisions from experience, systematic choices between prospects are based on the assessment of differences in their latent properties.
-Yet, distinct properties can be used to distinguish among the prospects, and the choices may vary respectively.
+Yet, distinct properties can be used to distinguish among the prospects and the choices may vary respectively.
 This paper presents a model that shows how the mind may rely on sampling strategies---i.e., the probability of sampling outcomes from different prospects in direct succession (switching probability)---to alter which differences in the latent properties evidence is accumulated for.
@@
 The respective choices for high switching probabilities reflect an as-if underweighting of rare outcomes that becomes more pronounced with increasing thresholds, demonstrating that the reliance on many small samples can explain the as-if underweighting of rare outcomes, while a large number of sampled outcomes is fully accounted for.
-The analysis also shows that the differences in the information-processing chain translate to systematic differences in the parameter estimitates of cumulative prospect theory's value and weighting function."
+The analysis also shows that the differences in the information-processing chain translate to systematic differences in the parameter estimates of cumulative prospect theory's value and weighting function."
 
@@
 Respectively, this section also contains predictions about the potential relations between $\psi$ and $\theta$ and the CPT parameters.
+A summary of the model predictions can be found in Table\ \@ref(tab:predictions).
 
@@
 Thus, $\gamma$ should increase with $\psi$.
-Note further that the predicted shape of the weighting function for high switching probabilities reflects the round-wise strategy's sensitivity to differences in the outcome's probabilities.
-That is, the slope of the weighting function increases around the midpoint of the probability scale and flattens to both ends.
-reflecting that the round-wise strategy is more sensitive to the differences in the 
-Accordingly, the round-wise strategy
+Note further that the predicted shape of the weighting function for high switching probabilities reflects the round-wise strategy's high sensitivity to differences in the probability to produce the higher outcome most of the time.
+That is, the slope of the weighting function increases around the midpoint of the probability scale.
+The predicted flat ends of the graph, however, indicate that the round-wise strategy more or less ignores how much larger the probability to produce a higher outcome is.
 
-Finally, an increase in the switching probability should lead to a more concave value function.
-Similar to the slope of the weighting function,
+Moreover, an increase in the switching probability should lead to a more concave value function, since all mean comparisons are ordinal and weighted equally in their contribution to the accumulated evidence.
+Specifically, the model is such that the magnitudes of outcomes are ignored once a comparison is carried out.
+Hence, for high switching probabilities, the choices depend on which prospect produces the higher outcome most of the time, irrespective of how much larger the outcomes are.
+Therefore, $\alpha$ is predicted to decrease as $\psi$.
+Finally, all predictions concerning the parameters of CPT's value and weighting function should become more robust with increases in $\theta$ as increasing thresholds lead to more systematic choices.
 
-```{r}
-predictions <- tibble("CPT parameter" = 
-                        c("$\\gamma$",
-                          "$\\delta$",
-                          "$\\alpha$"),
+(ref:predictions) Summary of Model Predictions
+
+```{r predictions}
+predictions <- tibble("Measure" = 
+                        c("Choices pattern",
+                          "",
+                          "$\\gamma$ (curvature of $w$)",
+                          "$\\delta$ (elevation of $w$)",
+                          "$\\alpha$ (concavity of $v$)"),
                       "Predictions for changes in $\\psi$" = 
-                        c("$\\geq 1$, increases with $\\psi$",
+                        c("More EV maximization for decreasing $\\psi$",
+                          "More as-if underweighting of rare outcomes for increasing $\\psi$",
+                          "$\\geq 1$, increases with $\\psi$",
                           "1, no effect of $\\psi$",
                           "$\\leq 1$, decreases with increasing $\\psi$"))
-apa_table(predictions, caption = "Model Predictions", note = "The prediction for changes in $\\psi$ should become more robust for increasing values of $\\theta$.", escape = FALSE)
+apa_table(predictions, caption = "(ref:predictions)", note = "The predictions for changes in $\\psi$ should become more robust for increasing values of $\\theta$ as choices become more systematic for high thresholds.", escape = FALSE)
 ```
@@
 
-Below
+To substantiate and refine the predictions of the model, a computational implementation was used to simulate the sampling and accumulation process for a set of choices between a safe prospect and a two-outcome (risky) prospect.
+The computational model was written in `R` [@rcoreteamLanguageEnvironmentStatistical2021] and is embodied in the GitHub repository accompanying this paper.
+The simulation was conducted for varying combinations of switching probabilities and thresholds.
+For each of these combinations, the simulated data was modeled with CPT's value and weighting function, using a Bayesian parameter estimation.
+The simulated choices and estimated CPT parameters can be understood as theory-implied data and data models which remain to be tested against empirical data [see @guestHowComputationalModeling2021; @haslbeckModelingPsychopathologyData2021].
 
@@
 
+Below, the data generation and data modeling procedure is briefly reviewed.
+
 ### Choice Problems
 
-The test set of $60$ choice problems, each consisting of a safe prospect and a two-outcome prospect, was obtained by stratified sampling from an initial set of $10,000$ choice problems.
-The stratification was used to assure that some of the choice problems contain a small (high) outcome of a probability smaller than $.20$.
+A test set of $60$ choice problems was obtained by stratified sampling from an initial set of $10,000$ problems.
+The stratification procedure was used to ensure that the test set contained choice problems with small-probability outcomes of different rank---i.e., small-probability outcomes that are either higher or lower than the EV of the two-outcome prospect---as well as choice problems without small-probability outcomes.
 The exact procedure was as follows:
-For each of the $10.000$ problems in the initial set, three outcomes were randomly drawn from a uniform distribution over the interval $[0, 20]$, with the smallest and highest of these three outcomes being assigned to the risky prospect in order to omit the case of dominant prospects.
-The probability for the smaller outcome of the risky prospect, $p_{small}$, was drawn from a uniform distribution over the interval $[.01, .99]$, with the probability of the higher outcome being set to $p_{high} = 1-p_{small}$.
-To obtain the $60$ choice problems of the test set, the initial set was divided into three subsets, where each subset contained either all problems with $p_{high} \in (0,.2)$ or $p_{high} \in [.2,.8]$ or $p_{high} \in (.8,1)$.
+For each of the $10.000$ problems in the initial set, three outcomes were randomly drawn from a uniform distribution over the interval $[0, 20]$, with the smallest and highest of these three outcomes being assigned to the risky prospect to omit dominant prospects.
+The probability for the lower outcome of the risky prospect, $p_x(x_{low})$, was drawn from a uniform distribution over the interval $(0, 1)$, with the probability of the higher outcome being set to $p_x(x_{high}) = 1-p_x(x_{low})$.
+To obtain the $60$ choice problems of the test set, the initial set was divided into three subsets, where each subset contained either all problems with $p_x(x_{high}) \in (0,.2)$ or $p_x(x_{high}) \in [.2,.8]$ or $p_x(x_{high}) \in (.8,1)$.
 From each of these subset, then, $20$ choice problems were randomly sampled.
@@
 
-The evidence accumulation model presented in this paper was implemented as a computational model to simulate the sampling process and the final choice for each of the $60$ choice problems in the test set.
-All of the following parameter values were combined with each other:
+To simulate the sampling and accumulation processes, the following parameter values were used and combined with each other.
+That is, each parameter combination was used to solve the test set.
 
-* **Switching probability**: 
-The switching probability $s$, defined as the probability of sampling outcomes from different prospects in direct succession, was varied in the interval $[.1, 1]$ in increments of $.1$.
+* *Switching probability* $\psi$ : 
+The switching probability was varied in the interval $[.1, 1]$ in increments of $.1$.
 
-* **Decision variable**: The decision variable of a prospect either counts the absolute number of won comparisons or how much more comparisons were won relative to the other prospect.
+* *Threshold* $\theta$: 
+The threshold was varied in the interval $[1,5]$ in increments of 1.
 
-* **Threshold**: 
-The value of the threshold $\theta$, determining how much (more) comparisons a prospect must win, was varied in the interval $[1,5]$ in increments of 1.
+* *Decision variable*: The decision variable of a prospect either counts the number of won comparisons---implying an absolute threshold---or how much more comparisons were won relative to the other prospect---implying a relative threshold.
 
 \noindent
-In sum, 100 (parameter combinations) x 60 (choices) x 100 (agents) = 600,000 sampling processes and choices were simulated.
+Since the switching probability introduces some stochasticity into the information-processing chain, each of the 100 resulting parameter combinations was used 100 times---resembling 100 agents---to solve the test set.
+In sum, then 100 (parameter combinations) $\times$ 100 (agents) $\times$ 60 (choice problems)  = 600,000 sampling and accumulation processes were simulated. 
+The respective dataset can be retrieved from the accompanying GitHub repository.
 
-### Modeling
+### Bayesian CPT Analysis of Choice Data
 
-## Results
+The choice data generated for each parameter combination was separately modeled in CPT, using Tversky and Kahneman's (1992) value function and Goldstein and Einhorn's (1987) weighting function.
+To demonstrate that the distortions from linear probability weighting are not just due to the difference between the latent objective probabilities and the relative number of times the outcomes are sampled over the course of any accumulation process, the sampled relative frequencies are supplied as probability information to the weighting function.
+To accommodate for possible random choice behavior that may be exerted by some parameter combinations of the data-generating accumulation model, the CPT model was amended with the logit choice rule
+$$
+p(P'^{safe}) = \frac{1} {1 + e^{-\rho(V_{safe}^{\frac{1}{\alpha}}-V_{risky}^{\frac{1}{\alpha}})}}
+\; ,
+\tag{16}
+$$
+where $p(P'^{safe})$ is the probability that the safe prospect is chosen over the risky prospect, $V_{safe}$ and $V_{risky}$ are the valuations of the safe and risky prospect that result from the parameter estimates of the value and weighting function, and $\rho \geq 0$ is a sensitivity parameter.
+The sensitivity parameter governs how strongly the choice between prospects depends on the differences in the valuations of the prospects---i.e., the core CPT model.
+Specifically, $\rho = 0$ implies no sensibility and therefore random choices.
+In turn, for increasing values of $\rho$, the probability of choosing the prospect with the higher valuation increases.
+Note further that the valuation of the prospects were rescaled by $\frac{1}{\alpha}$, as proposed by @stewartPsychologicalParametersHave2018, to guard against possible parameter interdependencies between $\alpha$ and $\rho$ [see @krefeld-schwalbStructuralParameterInterdependencies2021; @scheibehenneUsingBayesianHierarchical2015].
+In sum, then, the model has four free parameters $\alpha, \gamma, \delta, \rho$.
+
+Since for a given choice problem and parameter combination of the accumulation model there should be no systematic differences among the 100 iterations (agents), their data is combined and free parameters are estimated across them.
+Such a grouped approach is expected to reveal the main effects of a given parameter combination of the accumulation model on the choice patterns and ignores unsystematic differences or noise that may be caused by the switching probability [see @nilssonHierarchicalBayesianParameter2011].
+To facilitate comparisons across parameter combinations of the accumulation model, uninformative prior distributions were used throughout for all four parameters of the data model.
+Specifically, the prior distribution $\alpha \sim U(0,1)$, $\gamma \sim U(0,2)$, $\delta \sim U(0,10)$, and $\rho \sim U(0,5)$ were used.
 
@@
 cpt <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols_cpt)
+```
+
+To estimate the posterior distributions of the parameters, Markov Chain Monte Carlo sampling was used, where 20 chains of 40,000 samples each were run after a warm-up period of 1000 samples.
+To reduce potential autocorrelation during the sampling process, only every 20th sample was kept (thinning), leaving a total of 40,000 samples across chains.
+The minimum effective sample size was `r min(cpt$n.eff)`.
+The potential scale reduction factor $\hat{R}$ [see @gelmanInferenceIterativeSimulation1992] was $\leq$ `r round(max(cpt$Rhat), 4)` for all parameters, indicating good convergence.
+
+## Results
+
+```{r}
+choices %>%
+  group_by(s, a) %>% 
+  summarize(n_med = median(n_sample)) %>% 
+  ggplot(aes(x = s, y = n_med, group = as.factor(a), color = as.factor(a))) + 
+   labs(x = expression(psi),
+       y = "Sampled Outcomes",
+       color = expression(theta)) +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  scale_y_continuous(limits = c(0, 150), breaks = seq(0, 150, 50)) +
+  geom_point() +
+  geom_line() + 
+  scale_color_viridis_d(option = "viridis") +
+  theme_apa()
 ```
@@
   filter(parameter == "gamma") %>%
+  filter(a != 1, boundary != "relative") %>% 
   ggplot(aes(s, mean, color = s, shape = boundary)) +
@@
   filter(parameter == "delta") %>% 
+  filter(a != 1, boundary != "relative") %>% 
   ggplot(aes(s, mean, color = s, shape = boundary)) +
@@
 ##merge figures
-ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
+ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
 ```
@@
   filter(parameter == "alpha") %>% 
+  filter(a != 1) %>% 
   ggplot(aes(s, mean, color = s, shape = boundary)) +
@@
   filter(parameter == "rho") %>% 
+  filter(a != 1) %>% 
   ggplot(aes(s, mean, color = s, shape = boundary)) +
@@
 ##merge figure
-ggarrange(alpha, rho, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
+ggarrange(alpha, rho, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
 ```
@@
 ##merge figures
-ggarrange(weight, value, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
-```
-
-For each distinct parameter combination, we ran 20 chains of 40,000 iterations each, after a warm-up period of 1000 samples.
-To reduce potential autocorrelation during the sampling process, we only kept every 20th sample (thinning).
-The potential scale reduction factor $\hat{R}$ [@gelmanInferenceIterativeSimulation1992] was $\leq$ `r round(max(cpt$Rhat), 3)` for all parameters, indicating good convergence.
-The minimum effective sample size was `r min(cpt$n.eff)`.
-
-As expected, the scatter plot below shows an inverse relationship between switching probability and trial length.
-I.e., the lower the switching probability, the larger become the sample sequences on which each comparison between prospects is based, which in turn leads to longer trials.  
-This effect is particularly pronounced for low probabilities such that the increase in trial length accelerates as switching probability decreases.
-
-The figures below display the estimates of the $\gamma$ and $\delta$ parameter of the probability weighting function [@prelecProbabilityWeightingFunction1998] fitted to DfE simulated for different parameter values of the generating model.
-The estimates are plotted against the switching probability, where each panel represents a distinct boundary type and level, i.e., number of comparisons. 
-Grey dots represent agent level estimates, colored dots represent the mean across all agent level estimates.
-
-Most significantly, there is a strong relationship between the switching probability in the generating model and the $\gamma$ parameter.
-I.e., large switching probabilities, which are indicative for small sample sequences, lead to larger estimates for $\gamma$. 
-The resulting strong curvature leads to a compression of probabilities in the lower and upper range, reflecting underweighting of small probabilities and overweighting of large probabilities. 
-This pattern is robust for varying degrees of the boundary level, except for $a = 1$. 
-The latter deviation may be explained by the potential scale reduction factors for the respective parameter estimates, which indicate that the MCMC chains did not converge (see [Appendix 3][Appendix 3: Convergence Diagnostics for CPT Parameters]).
-
-<!-- Plots Appendix -->
-
-```{r A-data, include=FALSE}
-#load choice data
-choices_c <- read_csv("data/choices/choices_comprehensive.csv", col_types = cols_choices)
-cpt_c <- read_csv("data/estimates/estimates_cpt_comprehensive.csv", col_types = cols_cpt)
-```
-
-```{r A-choice-rates, fig.height=7, fig.width=10, include=FALSE}
-#prepare data
-fr_rates_c <- choices_c %>%
-  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B"),
-         ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2),
-         norm_exp = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B"))
-
-fr_rates_c_l <- fr_rates_c %>%
-  filter(!is.na(norm)) %>%
-  group_by(s, boundary, a, rare, norm, choice) %>% 
-  summarise(n = n()) %>%
-  mutate(rate = round(n/sum(n), 2),
-         type = case_when(norm == "A" & choice == "B" ~ "Safe",
-                          norm == "B" & choice == "A" ~ "Risky")) %>%
-  ungroup() %>%
-  filter(!is.na(type)) %>%
-  select(-c(norm, choice, n)) %>%
-  mutate(norm_ev = "Latent")
-
-fr_rates_c_s <- fr_rates_c %>%
-  filter(!is.na(norm_exp)) %>%
-  group_by(s, boundary, a, rare, norm_exp, choice) %>%
-  summarise(n = n()) %>%
-  mutate(rate = round(n/sum(n), 2),
-         type = case_when(norm_exp == "A" & choice == "B" ~ "Safe",
-                          norm_exp == "B" & choice == "A" ~ "Risky")) %>%
-  ungroup() %>%
-  filter(!is.na(type)) %>%
-  select(-c(norm_exp, choice, n)) %>%
-  mutate(norm_ev = "Sample")
-
-fr_rates_c <- bind_rows(fr_rates_c_l, fr_rates_c_s) %>%
-  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]",
-                          rare == "attractive" ~ "\\in (0,.2)",
-                          rare == "unattractive" ~ "\\in (.8,1)"))
-
-fr_rates_c %>%
-  ggplot(aes(s, rate)) +
-  facet_grid(rare~a, labeller = labeller(rare = as_labeller(label_rare, default = label_parsed), 
-                                         a = as_labeller(label_theta, default = label_parsed))) +
-  labs(x = "Switching Probability",
-       y = "False Response Rate",
-       color = "Normative\nExpected\nValue",
-       shape = "False\nResponse\nType") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
-  geom_point(aes(color = norm_ev, shape = type)) +
-  scale_shape_manual(values = c(4, 16)) +
-  scale_color_viridis_d(option = "plasma", end = .7) +
-  theme_apa()
-```
-
-```{r A-weighting-parameters, fig.height=7, fig.width=10, include=FALSE}
-#prepare data
-cpt_c <- cpt_c %>% mutate(boundary = if_else(boundary == "absolute", "Absolute", "Relative"))
-
-#plot estimates
-
-##gamma
-gamma_c <- cpt_c %>%
-  filter(parameter == "gamma") %>%
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
-  labs(x = element_blank(),
-       y = expression(gamma),
-       color = "Switching\nProbability",
-       shape = "Boundary") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
-  geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_shape_manual(values = c(4, 16)) +
-  scale_color_viridis(option = "plasma") +
-  theme_apa()
-
-##delta
-delta_c <- cpt_c %>%
-  filter(parameter == "delta") %>% 
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
-  facet_wrap(~a, nrow = 1) + 
-  labs(x = "Switching Probability",
-       y = expression(delta),
-       color = "Switching\nProbability",
-       shape = "Boundary") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
-  geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_color_viridis(option = "plasma") +
-  scale_shape_manual(values = c(4, 16)) +
-  theme_apa() + 
-  theme(strip.text.x = element_blank()) #omit facet labels
-
-##merge figures
-ggarrange(gamma_c, delta_c, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
-```
-
-```{r A-value-parameters, fig.height=7, fig.width=10, include=FALSE}
-#plot estimates
-
-##alpha
-alpha_c <- cpt_c %>%
-  filter(parameter == "alpha") %>% 
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
-  labs(x = element_blank(),
-       y = expression(alpha),
-       color = "Switching\nProbability",
-       shape = "Boundary") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
-  geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_color_viridis(option = "plasma") +
-  scale_shape_manual(values = c(4, 16)) +
-  theme_apa()
-
-##rho
-rho_c <- cpt_c %>%
-  filter(parameter == "rho") %>% 
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
-  facet_wrap(~a, nrow = 1) + 
-  labs(x = "Switching Probability",
-       y = expression(rho),
-       color = "Switching\nProbability",
-       shape = "Boundary") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1,.5)) +
-  geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_color_viridis(option = "plasma") +
-  scale_shape_manual(values = c(4, 16)) +
-  theme_apa() + 
-  theme(strip.text.x = element_blank())
-
-##merge figure
-ggarrange(alpha_c, rho_c, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
-```
-
-```{r A-cpt-graphs, fig.height=7, fig.width=10, include=FALSE}
-#prepare data
-
-##compute images of weighting and value function
-
-###weighting function
-wf_c <- cpt_c %>%
-  select(s, boundary, a, parameter, mean) %>%
-  pivot_wider(names_from = parameter, values_from = mean) %>%
-  select(-c(alpha, rho)) %>%
-  expand_grid(p = seq(0, 1, .05)) %>%
-  mutate(w = round(  (delta * p^gamma)/ ((delta * p^gamma)+(1-p)^gamma), 2))
-
-###value function
-vf_c <- cpt_c %>%
-  select(s, boundary, a, parameter, mean) %>%
-  pivot_wider(names_from = parameter, values_from = mean) %>%
-  select(-c(gamma, delta, rho)) %>%
-  expand_grid(x = seq(0, 20, .5)) %>%  
-  mutate(v = round(x^alpha, 2))
-
-##split data to avoid passing two y-values to the same x-value in geom_line()
-wf_c_a <- wf_c %>% filter(boundary == "Absolute")
-wf_c_r <- wf_c %>% filter(boundary == "Relative")
-vf_c_a <- vf_c %>% filter(boundary == "Absolute")
-vf_c_r <- vf_c %>% filter(boundary == "Relative")
-
-#plots
-
-##weighting function
-weight_c <- wf_c_a %>% 
-  ggplot(aes(p, w, group = s, color = s)) +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
-  labs(x = "Experienced Probability",
-       y = "Decision Weight",
-       color = "Switching\nProbability") +
-  scale_x_continuous(breaks = seq(0, 1, .5)) +
-  scale_y_continuous(breaks = seq(0, 1, .5)) +
-  geom_line(size = .5) +
-  geom_line(data = wf_c_r, size = .5) + 
-  scale_color_viridis(option = "plasma") +
-  theme_apa()
-
-##value function
-value_c <- vf_c_a %>% 
-  ggplot(aes(x, v, group = s, color = s)) +
-  facet_wrap(~a, nrow = 1)+ 
-  labs(x = "Objective Outcome",
-       y = "Subjective Value",
-       color="Switching\nProbability") +
-  scale_x_continuous(breaks = seq(0, 20, 10)) +
-  scale_y_continuous(breaks = seq(0, 20, 10)) +
-  geom_line(size = .5) +
-  geom_line(data = vf_c_r, size = .5) + 
-  scale_color_viridis(option = "plasma") +
-  theme_apa() + 
-  theme(strip.text.x = element_blank())
-
-##merge figures
-ggarrange(weight_c, value_c, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right", labels = "AUTO") 
+ggarrange(weight, value, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
 ```

### 2022-04-04 manuscript.Rmd
Review Figure and title page

@@
 ---
-title             : "Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation"
+title             : |
+  Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation
+
 shorttitle        : "Sampling strategies"
@@
   - name          : "Linus Hof"
-    affiliation   : "1"
     corresponding : yes    
-    address       : "Department of Psychology, Heidelberg University, Hauptstraße 47-51, 69117 Heidelberg, Germany"
     email         : "linushof@posteo.de"
 
-affiliation:
-  - id            : "1"
-    institution   : "Heidelberg University"
-
 note: |
-  **Unsubmitted draft created from the commit with the hash**: ``r repro::current_hash()``
+    Unsubmitted draft created from the commit `r repro::current_hash()`
 
 authornote: |
- This is a dynamic document which can be reproduced from the accompanying GitHub repository: https://github.com/linushof/sampling-in-dfe.
+ The article is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at
 
- The current version of this manuscript is prepared for submission as a master's thesis.
- Supervisors: Thorsten Pachur & Veronika Zilker.
+ Heidelberg University
+
+ Faculty of Behavioural and Cultural Studies
+
+ Institute of Psychology
+
+  \noindent
+  under the supervision of
+
+  \indent
+  1. Prof. Dr. Thorsten Pachur, Technical University of Munich
+
+  \indent
+  2. Dr. Veronika Zilker, Max Planck Institute for Human Development
 
@@
                       fig.align = "l", #align figures to left margin
-                      fig.pos = "t" # display figures at the top of a page
-                      )
+                      fig.pos = "t", # display figures at the top of a page
+                      fig.height=7, 
+                      fig.width=10)
 ```
@@
 
-```{r weighting-function, fig.cap="(ref:weighting-function)", fig.height=7, fig.width=10}
+```{r weighting-function, fig.cap="(ref:weighting-function)"}
 #compute images of weighting function (wf)
@@
   facet_wrap(~delta, labeller = as_labeller(label_delta, default = label_parsed)) + 
-  scale_x_continuous(breaks = seq(0, 1, .2)) +
-  scale_y_continuous(breaks = seq(0, 1, .2)) + 
+  scale_x_continuous(breaks = seq(0, 1, .5)) +
+  scale_y_continuous(breaks = seq(0, 1, .5)) + 
   labs(x = expression(p),
@@
   theme_apa() + 
-  geom_line(aes(color = gamma)) +
+  geom_line(aes(color = gamma), size = .5) +
   scale_color_viridis(option = "viridis") + 
@@
 choices <- read_csv("data/choices/choices.csv", col_types = cols_choices)
+choices <- choices %>% 
+  filter(boundary == "absolute")
 
@@
 cpt <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols_cpt)
+cpt <- cpt %>% 
+  filter(boundary == "absolute")
 ```
@@
 
-```{r}
+We start by inspecting how the number of outcomes sampled over the course of a sampling and accumulation process changes with varying combinations of switching probabilities and thresholds.
+Figure\ \@ref(fig:chain-length) shows the respective median for each parameter combination.
+The model predicts an inverse relationship between the switching probability and the overall number of sampled outcomes, since the stochastic processes tend to terminate faster, the higher the switching probabilities.
+In other words, the higher the switching probability, the smaller the samples on which each mean comparison is based, resulting in a decreasing overall number of sampled outcomes.
+Since the relative change in the switching probability decreases as $\psi$ approaches certainty, the relative change in the number of sampled outcomes decreases respectively.
+Furthermore, because it determines the number of mean comparisons---and therefore stochastic processes---that must be carried out, any increase in the threshold leads to an increase in the number of sampled outcomes.
+
+(ref:chain-length) Lengths of Information-Processing Chains
+
+```{r chain-length, fig.cap="(ref:chain-length)"}
 choices %>%
@@
    labs(x = expression(psi),
-       y = "Sampled Outcomes",
+       y = "Median of Overall Sampled Outcomes",
        color = expression(theta)) +
   scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
-  scale_y_continuous(limits = c(0, 150), breaks = seq(0, 150, 50)) +
+  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 150, 50)) +
   geom_point() +
@@
 
-<!-- Plots choice rates -->
+### Final Choice
 
-(ref:choice-rates) Effect of Switching Probability on Rates of False Risky and False Safe Choices for 2-Outcome Prospects with High Rank Outcomes of Different Probability
+Figure\ \@ref(fig:choice-rates) displays the rates of choices that did not maximize the EV for each combination of the switching probabilities and thresholds.
+The top panel of the figure shows the rates for choice problems where the low-rank outcome of the risky prospect has a low probability.
+Respectively, for high switching probabilities and therefore short stochastic processes, the low-rank outcome is expected to occur less often over the course of a stochastic process than would be objectively warranted, leading to an inflation of the respective mean of the risky prospect.
+Accordingly, if the safe prospect possesses the higher EV, the number of false responses increases with the switching probability.
+However, if the risky prospect has the higher EV, the mean inflation causes the choices to be generally in line with EV maximization.
+Note from the middle panel that this pattern reverses, if the high-rank outcome has a small probability.
 
-```{r choice-rates, fig.cap="(ref:choice-rates)", fig.height=7, fig.width=10}
+(ref:choice-rates) Rates of False Risky and False Safe Choices
+
+```{r choice-rates, fig.cap="(ref:choice-rates)"}
 #prepare data
@@
 fr_rates <- choices %>%
-  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B"), #normative choice latent EV
-         ev_ratio_exp = round(a_ev_exp/b_ev_exp, 2),
-         norm_exp = case_when(ev_ratio_exp > 1 ~ "A", ev_ratio_exp < 1 ~ "B")) #normative choice sampled EV
-
-##compute false response rates
-
-###latent EV
-fr_rates_l <- fr_rates %>%
+  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B")) %>% # determine normative choice
   filter(!is.na(norm)) %>% #exclude trials with equal EV
@@
   select(-c(norm, choice, n)) %>% 
-  mutate(norm_ev = "Latent") #assign facet label
-
-###sampled EV
-fr_rates_s <- fr_rates %>%
-  filter(!is.na(norm_exp)) %>%
-  group_by(s, boundary, a, rare, norm_exp, choice) %>%
-  summarise(n = n()) %>%
-  mutate(rate = round(n/sum(n), 2),
-         type = case_when(norm_exp == "A" & choice == "B" ~ "Safe",
-                          norm_exp == "B" & choice == "A" ~ "Risky")) %>%
-  ungroup() %>%
-  filter(!is.na(type)) %>%
-  select(-c(norm_exp, choice, n)) %>%
-  mutate(norm_ev = "Sample")
-
-### merge latent and sampled data
-fr_rates <- bind_rows(fr_rates_l, fr_rates_s) %>%
   mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]", #change facet labels for rare events
@@
 fr_rates %>%
-  ggplot(aes(s, rate)) +
+  ggplot(aes(s, rate, group = type)) +
   facet_grid(rare~a, labeller = labeller(rare = as_labeller(label_rare, default = label_parsed), 
                                          a = as_labeller(label_theta, default = label_parsed))) +
-  labs(x = "Switching Probability",
+  labs(x = expression(psi),
        y = "False Response Rate",
-       color = "Normative\nExpected\nValue",
-       shape = "False\nResponse\nType") +
+       color = expression(psi),
+       shape = "False\nResponse") +
   scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
   scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
-  geom_point(aes(color = norm_ev, shape = type)) +
+  geom_line(aes(color = s, group = type)) + 
+  geom_point(aes(color = s, shape = type), size = 2) +
   scale_shape_manual(values = c(4, 16)) +
-  scale_color_viridis_d(option = "viridis", begin = .1, end = .7) +
+  scale_color_viridis(option = "viridis") +
   theme_apa()
@@
 
-<!-- Plots CPT -->
+### Cumulative Prospect Theory
 
-(ref:weighting-parameters) Parameter Estimates of the Weighting Function of @goldsteinExpressionTheoryPreference1987 for Different Simulation Parameters
+(ref:weighting-parameters) Parameter Estimates and Graphical Shape of the Weighting Function
 
-```{r weighting-parameters, fig.cap="(ref:weighting-parameters)", fig.height=7, fig.width=10}
-#prepare data
-cpt <- cpt %>% mutate(boundary = if_else(boundary == "absolute", "Absolute", "Relative"))
+```{r weighting-parameters, fig.cap="(ref:weighting-parameters)"}
 
@@
   filter(parameter == "gamma") %>%
-  filter(a != 1, boundary != "relative") %>% 
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  ggplot(aes(s, mean, color = s)) +
   facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
+  scale_y_continuous(limits = c(0,2), breaks = seq(0,2.0,1.0))+
   labs(x = element_blank(), #omit axis title
        y = expression(gamma),
-       color = "Switching\nProbability",
-       shape = "Boundary") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+       color = expression(psi)) +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
   geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_shape_manual(values = c(4, 16)) +
   scale_color_viridis(option = "viridis") +
-  theme_apa()
+  theme_apa() +
+  theme(axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.x = element_blank())
 
@@
   filter(parameter == "delta") %>% 
-  filter(a != 1, boundary != "relative") %>% 
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  ggplot(aes(s, mean, color = s)) +
   facet_wrap(~a, nrow = 1) + 
-  labs(x = "Switching Probability",
+  scale_y_continuous(limits = c(0,10), breaks = seq(0,10,5)) +
+  scale_x_continuous(limits = c(0, 1.1), breaks = seq(0,1,.5)) +
+  labs(x = expression(psi),
        y = expression(delta),
-       color = "Switching\nProbability",
-       shape = "Boundary") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+       color = expression(psi)) +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
   geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
   scale_color_viridis(option = "viridis") +
-  scale_shape_manual(values = c(4, 16)) +
+  theme_apa() + 
+  theme(strip.text.x = element_blank()) #omit facet labels
+
+wf <- cpt %>%
+  select(s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
+  select(-c(alpha, rho)) %>%
+  expand_grid(p = seq(0, 1, .05)) %>%
+  mutate(w = round(  (delta * p^gamma)/ ((delta * p^gamma)+(1-p)^gamma), 2))
+
+##weighting function
+weight <- wf %>% #graphs for absolute boundary
+  ggplot(aes(p, w, group = s, color = s)) +
+  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  labs(x = "Experienced Probability",
+       y = expression(pi),
+       color = expression(psi)) +
+  scale_x_continuous(breaks = seq(0, 1, .5)) +
+  scale_y_continuous(breaks = seq(0, 1, .5)) +
+  geom_line(size = .5) +
+  scale_color_viridis(option = "viridis") +
   theme_apa() + 
@@
 ##merge figures
-ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
+ggarrange(gamma, delta, weight, ncol = 1, nrow = 3, common.legend = TRUE, legend = "right")
 ```
 
-(ref:value-parameters) Parameter Estimates of the Value Function of @tverskyAdvancesProspectTheory1992 and of the Logit Choice Rule for Different Simulation Parameters
+(ref:value-parameters) Parameter Estimates and Graphical Shape of the Value Function
 
-```{r value-parameters, fig.cap="(ref:value-parameters)", fig.height=7, fig.width=10}
+```{r value-parameters, fig.cap="(ref:value-parameters)"}
 #plot estimates
@@
   filter(parameter == "alpha") %>% 
-  filter(a != 1) %>% 
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  ggplot(aes(s, mean, color = s)) +
   facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
-  labs(x = element_blank(),
+  scale_x_continuous(limits = c(0, 1.1), breaks = seq(0,1,.5)) +
+  scale_y_continuous(limits = c(0,1), breaks = seq(0,1, .5)) + 
+  labs(x = expression(psi),
        y = expression(alpha),
-       color = "Switching\nProbability",
-       shape = "Boundary") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0,1,.5)) +
+       color = expression(psi)) +
   geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
   scale_color_viridis(option = "viridis") +
-  scale_shape_manual(values = c(4, 16)) +
   theme_apa()
+
+###value function
+vf <- cpt %>%
+  select(s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
+  select(-c(gamma, delta, rho)) %>%
+  expand_grid(x = seq(0, 20, .5)) %>%  
+  mutate(v = round(x^alpha, 2))
+
+value <- vf %>% 
+  ggplot(aes(x, v, group = s, color = s)) +
+  facet_wrap(~a, nrow = 1)+ 
+  labs(x = "Objective Outcome",
+       y = "Subjective Value",
+       color=expression(psi)) +
+  scale_x_continuous(limits = c(0,20), breaks = seq(0, 20, 10)) +
+  scale_y_continuous(limits = c(0,20), breaks = seq(0, 20, 10)) +
+  geom_line(size = .5) +
+  scale_color_viridis(option = "viridis") +
+  theme_apa() + 
+  theme(strip.text.x = element_blank())
 
@@
   filter(parameter == "rho") %>% 
-  filter(a != 1) %>% 
   ggplot(aes(s, mean, color = s, shape = boundary)) +
@@
        shape = "Boundary") +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1,.5)) +
+  scale_x_continuous(limits = c(0, 1.1), breaks = seq(0, 1,.5)) +
   geom_point() +
-  geom_pointrange(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
   scale_color_viridis(option = "viridis") +
@@
 ##merge figure
-ggarrange(alpha, rho, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
+ggarrange(alpha, value, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
 ```
@@
 
-```{r cpt-graphs, fig.cap="(ref:cpt-graphs)", fig.height=7, fig.width=10}
+```{r cpt-graphs, fig.cap="(ref:cpt-graphs)", eval = FALSE}
 #prepare data

### 2022-04-05 manuscript.Rmd
Update Results

@@
 Figure\ \@ref(fig:chain-length) shows the respective median for each parameter combination.
-The model predicts an inverse relationship between the switching probability and the overall number of sampled outcomes, since the stochastic processes tend to terminate faster, the higher the switching probabilities.
-In other words, the higher the switching probability, the smaller the samples on which each mean comparison is based, resulting in a decreasing overall number of sampled outcomes.
-Since the relative change in the switching probability decreases as $\psi$ approaches certainty, the relative change in the number of sampled outcomes decreases respectively.
-Furthermore, because it determines the number of mean comparisons---and therefore stochastic processes---that must be carried out, any increase in the threshold leads to an increase in the number of sampled outcomes.
+Since the two stochastic processes underlying a mean comparison tend to terminate faster the higher the switching probabilities are, the model predicts the overall number of sampled outcomes to decrease with increasing switching probabilities.
+As can be seen from the changing slopes of the lines in Figure\ \@ref(fig:chain-length), the decrease in the number of sampled outcomes diminishes as the relative increase in the switching probability diminishes.
+Moreover, the overall number of sampled outcomes increases with thresholds at a relatively constant rate, reflecting the latters impact on the number of required mean comparisons.
+Finally, consider the dashed horizontal line which displays the median number of 14 outcomes that @wulffMetaanalyticReviewTwo2018 found to be sampled in 10,712 trials involving a choice between a safe and a two-outcome prospect in the sampling paradigm.
+Notably, the parameter combinations that closely resemble the round-wise strategy---i.e., high switching probabilities and thresholds---or the summary strategy---i.e., low switching probabilities and thresholds---lead to overall numbers of sampled outcomes that come fairly close to this meta-analytic median.
+In turn, hybrids of both strategies produce overall numbers of sampled outcomes that are considerably lower or higher.
 
@@
   geom_line() + 
+  geom_hline(yintercept = 14, linetype = "dashed", color = "gray") +
+  annotate(geom="text", x=.95, y=16, label="Wulff et al. (2018)", color="gray") + 
   scale_color_viridis_d(option = "viridis") +
@@
 
-Figure\ \@ref(fig:choice-rates) displays the rates of choices that did not maximize the EV for each combination of the switching probabilities and thresholds.
-The top panel of the figure shows the rates for choice problems where the low-rank outcome of the risky prospect has a low probability.
-Respectively, for high switching probabilities and therefore short stochastic processes, the low-rank outcome is expected to occur less often over the course of a stochastic process than would be objectively warranted, leading to an inflation of the respective mean of the risky prospect.
-Accordingly, if the safe prospect possesses the higher EV, the number of false responses increases with the switching probability.
-However, if the risky prospect has the higher EV, the mean inflation causes the choices to be generally in line with EV maximization.
-Note from the middle panel that this pattern reverses, if the high-rank outcome has a small probability.
+Figure\ \@ref(fig:choice-rates) displays the rates of choices that did not maximize the latent EV (hereafter: false response rates) for each combination of switching probabilities and thresholds.
+Moreover, the rates are separated by the presence and rank of a small-probability outcome.
+Consider first the top panel which shows the false response rates across all problems where the low-rank outcome of the risky prospect has a small probability:
+Over the course of short stochastic processes, then, the low-rank outcomes tend to be sampled less often than would be objectively warranted, leading to an inflation of the respective means of the risky prospect.
+Accordingly, the top panels show that the rates of false choices of the risky prospect increase with the switching probability, but the rates of false safe choices remain generally low.
+More specifically, the higher the switching probabilities, the more severe should the inflation of the means---and the overestimation of the EVs---of the risky prospects be. 
+As a consequence, if the risky prospects possesses the smaller EV, an increase in the switching probability increases the risk to deviate from EV maximization by falsely choosing the risky prospects on the basis of mean comparisons.
+Importantly, these deviations take the form of an as-if underweighting of rare outcomes.
+In turn, if the risky prospects possess the larger EV, the inflation of their means decreases the risk to falsely choose the safe prospect.
+Note from the middle panel that the pattern of false response rates reverses across all problems where the high-rank outcome of the risky prospect has a small probability.
+In this case, then, the means of the risky prospects tend to be more deflated, the higher the switching probability is, which, however, again results in an as-if underweighting of rare outcomes.
+Furthermore, the differences between the switching probabilities concerning the false response rates tend to be more pronounced for high thresholds, showing that over the course of multiple mean comparisons the inflation and deflation of the means of the risky prospect is more robust.
 
@@
 ### Cumulative Prospect Theory
+
+Figure\ \@ref(fig:weighting-patterns) shows the means and the 95%-intervals of the posterior distributions of the curvature parameter $\gamma$ and elevation parameter $\delta$ as well as the resulting shape of the weighting function.
+Note first that because the relative frequencies were supplied as probability information, the parameter estimates for the threshold value $\theta = 1$ in combination with high switching probabilities have large posterior intervals.
+The estimates substantiate the prediction that $\gamma$ takes values over $1$ and increases with the switching probability, resulting in an S-shaped weighting function. 
+Because the images of the function equal the decision weights, the estimates show that high switching probabilities translate to an underweighting of rare outcomes in CPT.
+The estimates of $\delta$ also tend to increase with increasing switching probabilities.
 

### 2022-04-07 manuscript.Rmd
Review of abstract and introduction + formatting

@@
   - name          : "Linus Hof"
+    affiliation   : "1"
     corresponding : yes
-    email         : "linushof@posteo.de"
+    address       : "Institute of Psychology, Heidelberg University, Hauptstr. 47 – 51, 69117 Heidelberg"    
+    email         : "linus.hof@stud.uni-heidelberg.de"
 
-note: |
-    Unsubmitted draft created from the commit `r repro::current_hash()`
+affiliation:
+  - id            : "1"
+    institution   : "Heidelberg University"
 
 authornote: |
- The article is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at
-
- Heidelberg University
-
- Faculty of Behavioural and Cultural Studies
-
- Institute of Psychology
-
-  \noindent
-  under the supervision of
+ This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the GitHub repository: https://github.com/linushof/sampling-in-dfe.
+The current version of the manuscript, created from the commit with the hash `r repro::current_hash()`, is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
+Supervisors:
 
@@
 
-abstract: "In decisions from experience, systematic choices between prospects are based on the assessment of differences in their latent properties.
-Yet, distinct properties can be used to distinguish among the prospects and the choices may vary respectively.
-This paper presents a model that shows how the mind may rely on sampling strategies---i.e., the probability of sampling outcomes from different prospects in direct succession (switching probability)---to alter which differences in the latent properties evidence is accumulated for.
-Specifically, the model sequentially samples outcomes from two prospects and accumulates the results obtained from a sequence of ordinal comparisons between sample means, with switching probabilities determining the size of the samples underlying each comparison and thresholds determining how much comparisons a prospect must win to be chosen.
-In a computational analysis, the model is used to simulate the information-processing chain for choices between two prospects, while varying switching probabilities and thresholds.
-The analysis shows that the accumulation process provides evidence for differences in the expected values when low switching probabilities cause each comparison to be carried out on large samples.
-In turn, when high switching probabilities cause the accumulation process to unfold over comparisons based on small samples, evidence is accumulated for differences in the probability to produce a higher outcome most of the time.
-The respective choices for high switching probabilities reflect an as-if underweighting of rare outcomes that becomes more pronounced with increasing thresholds, demonstrating that the reliance on many small samples can explain the as-if underweighting of rare outcomes, while a large number of sampled outcomes is fully accounted for.
-The analysis also shows that the differences in the information-processing chain translate to systematic differences in the parameter estimates of cumulative prospect theory's value and weighting function."
+abstract: "In decisions from experience, systematic choices between prospects are based on the assessment of differences in latent properties.
+Yet, several properties can be used to distinguish among the prospects.
+To this end, this paper presents a sampling and accumulation model that allows sampling  strategies—i.e., the probability of sampling outcomes from different prospects in direct succession (switching probability)—to alter which differences in the latent properties evidence is accumulated for.
+Specifically, the proposed model sequentially samples outcomes from two prospects and accumulates the results obtained from a sequence of ordinal comparisons between sample means, with switching probabilities determining the size of the samples underlying each comparison and thresholds determining how much comparisons a prospect must win in order to be chosen.
+A computational implementation of the model is used to simulate the respective information-processing chains upfront choices between a safe and a two-outcome prospect, while varying switching probabilities and thresholds.
+The analysis of the simulation data shows that, depending on whether the accumulation process unfolds over mean comparisons based on small or large samples, evidence is accumulated for differences either in the probability to produce a higher outcome most of the time or in the expected value.
+The respective choice patterns reflect an as-if underweighting of rare outcomes or expected value maximization, both of which become more robust with increasing thresholds.
+The analysis moreover shows how the distinct choice patterns resulting from differences in the information-processing chains translate to the parameters of cumulative prospect theory’s value and weighting function."
 
@@
 linkcolor         : "blue"
+link-citations    : true
 mask              : no
@@
                       fig.align = "l", #align figures to left margin
-                      fig.pos = "t", # display figures at the top of a page
+                      fig.pos = "t", #display figures at the top of a page
                       fig.height=7, 
@@
 
-The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the choice alternatives between which people can choose.
-Indeed, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
+The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the alternatives between which people can choose.
+In fact, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
 Respectively, decision making can be understood as an information-processing problem whose solution requires a selection among choice alternatives.
@@
 Importantly, the information that the inputs provide about these properties can come in different forms.
-Specifically, in *decisions from description* (DfD), the inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
-Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospect was chosen in similar past decisions.
-The inputs to DfE therefore take the form of sampled outcomes.
-Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
+Specifically, in *decisions from description* (DFD), the inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
+Yet, in *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospect was chosen in similar past decisions.
+The inputs to DFE therefore take the form of sampled outcomes.
+Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DFD and DFE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructBehaviorGap2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
-choice patterns in DfD deviate from the solutions of expected value (EV) maximization, as if small-probability outcomes were given more weight than would be warranted by their objective probabilities;
-in turn, in DfE, choice patterns deviate from the solutions of EV maximization as if the same small-probability outcomes were given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+choice patterns in DFD deviate from the solutions of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities;
+in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructBehaviorGap2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
 Hereafter, these choice patterns are referred to as the *as-if overweighting* and *as-if underweighting of rare outcomes*, respectively.
 
-Similar to other behavioral phenomena that can be explained by assuming that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes can be explained by assuming that the mind is sensitive to the information provided by the small samples that people tend to rely on in DfE [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
-More specifically, following from the laws of large numbers [see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
-In such a case or in the less strict case of large samples, then, the binomial distribution of each outcome can be approximated by a symmetric normal distribution.^[<!--Open footnote-->The binomial distribution of an outcome is the probability distribution of the number of times an outcome occurs in a sample.
-According to the *de Moivre-Laplace theorem* [see, e.g., @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015], the binomial distribution can be approximated by a normal distribution given a large number of sampled outcomes.
-Respectively, for large samples, the relative relative frequencies with which an outcome occurs in the sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.<!--Close footnote-->]
+Similar to explanations for other behavioral phenomena that rest on the assumption that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [cf.
+@fiedlerBewareSamplesCognitiveecological2000], an explanation for the as-if underweighting of rare outcomes may be build on the assumption that the mind is sensitive to the information provided by small samples [@hertwigDecisionsExperienceEffect2004; @plonskyRelianceSmallSamples2015; see also @erevChoicePredictionCompetition2010; @erevAnomaliesForecastsDescriptive2017, for the performance of models assuming reliance on small samples in prediction competitions]:
+Specifically, following from the laws of large numbers [cf., e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
+In such a case---or in the less strict case of large samples---, then, the binomial distribution of each outcome can be approximated by a symmetric normal distribution.^[<!--Open footnote-->The binomial distribution of an outcome is the probability distribution of the number of times an outcome occurs in a sample.
+According to the *de Moivre-Laplace theorem* [see, e.g., @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015], the binomial distribution can be approximated by a normal distribution given a large sample.
+Respectively, the relative relative frequencies with which an outcome occurs in a large sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.<!--Close footnote-->]
 However, for samples of small size, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
-As a consequence, were the mind to use the relative frequencies of outcomes in a sample to infer their latent objective probabilities and to follow the principle of EV maximization, the as-if underweighting of rare outcomes in DfE could be explained by the reliance on small samples.
 
-Yet, some studies show that the as-if underweighting of rare outcomes may appear, even if the overall number of sampled outcomes is large and the relative frequencies across all sampled outcomes correspond closely to the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
-Respectively, there may be a disconnect between the overall number of sampled outcomes and the size of the samples the mind relies on in the evaluation of prospects.
-However, in contrast to other approaches, in the current paper it is not assumed that some of the sampled outcomes are discounted [see, e.g., @hertwigDecisionsExperienceEffect2004, who assume recency effects] or ignored [see, e.g., @cohenEffectPerceivedPatterns2021; @plonskyRelianceSmallSamples2015, who assume that only outcomes that followed some sequential pattern are considered].
-Rather, assuming that any number of outcomes sampled from a prospect may either be integrated into the same sample or into multiple smaller samples, this paper presents an accumulation model that shows that---given a reliance on multiple or many small samples---an as-if underweighting of rare outcomes can occur, even if a large number of sampled outcomes is fully accounted for.
+In fact, in DFE, people tend to sample only a small number of outcomes from each prospect [@hertwigDecisionsExperienceEffect2004; @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; see also @wulffMetaanalyticReviewTwo2018], which is a sufficient condition for the reliance on small samples in the evaluation of prospects.
+Yet, the as-if underweighting of rare outcomes may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018].
+While this latter finding does not preclude the reliance on small samples---i.e., the mind may rely on only a portion of the sampled outcomes, discount them, or, as proposed in the current paper, distribute them over multiple smaller samples---, it suggests that an explanation for the as-if underweighting of rare outcomes cannot be reduced to inaccurate inferences about the latent properties of prospects that are caused by frugal sampling and the implied sampling error.
+Rather the opposite, this paper presents a simple sampling and accumulation model that suggests that the as-if underweighting of rare outcomes can be the consequence of an accurate assessment of differences among prospects in a latent property [but see @hertwigDescriptionexperienceGapRisky2009; @plonskyRelianceSmallSamples2015;  @wulffMetaanalyticReviewTwo2018, for alternative explanations].
 
-Therefore, consider first the finding that *sampling strategies* were indicative for the final choice in DfE.
-Specifically, in one paradigm used to study DfE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
+Therefore, consider first the finding that *sampling strategies* were indicative for the final choice in DFE.
+Specifically, in one paradigm used to study DFE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
 Considering this paradigm and the choice between two prospects, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^[<!--Open footnote-->Note that @hillsInformationSearchDecisions2010 proposed two paradigmatic sampling strategies, where prospects are either switched just once (comprehensive sampling) or after each sampled outcome (piecewise sampling).
@@
 In other words, the proposed model predicts an as-if underweighting of rare outcomes to occur when high switching probabilities cause the accumulation process to unfold over mean comparisons that are based on small samples.
-Thus, the analysis substantiates the claim that not only the reliance on just a portion of a large number of sampled outcomes can explain an as-if underweighting of rare outcomes in DfE, but also the reliance on multiple or many small samples.
+Thus, the analysis substantiates the claim that not only the reliance on just a portion of a large number of sampled outcomes can explain an as-if underweighting of rare outcomes in DFE, but also the reliance on multiple or many small samples.
 Moreover, the analysis shows that an as-if underweighting of rare outcomes cannot be equated with inaccurate inferences about latent properties---e.g., the EVs---that carry over to the subsequent choices.
@@
 Importantly, the as-if prefix indicates that it cannot be concluded from the estimated weighting pattern that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, the mind processes the information about the choice alternatives in a way that the resulting choices translate to the estimated weighting pattern.
-The as-if weighting terminology is therefore reminiscent of the distinction between different levels of explanation [cf. @marrVisionComputationalInvestigation1982; @vanrooijTheoryTestHow2021].
+The as-if weighting terminology is therefore reminiscent of the distinction between different levels of explanation [cf. @marrVisionComputationalInvestigation1982].
 That is, CPT may be considered a computational-level theory that specifies the computational problem the mind faces when being confronted with the choice between prospects, and how this problem may be solved by the abstract calculus of CPT.
 However, as such, CPT cannot substitute algorithmic-level theories and process models that make claims about how exactly the mind transforms the inputs to the decision-making process into outputs which approximate the solutions of CPT [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
-Respectively, this paper uses CPT as a mere data model to show how differences in the information-processing chain upfront choices in DfE---considered in the following section---may cause particular weighting patterns, among them the as-if underweighting of rare outcomes which has been found to be a robust behavioral phenomena in DfE.
+Respectively, this paper uses CPT as a mere data model to show how differences in the information-processing chain upfront choices in DFE---considered in the following section---may cause particular weighting patterns, among them the as-if underweighting of rare outcomes which has been found to be a robust behavioral phenomena in DFE.
 To this end, the paper first continues to review the weighting patterns that can possibly estimated in CPT.
@@
 More so, the fact that CPT may weigh outcomes of the same small probability differently, adds another reasons why the description-experience gap should not be equated with a reversed weighting pattern in CPT [see @hertwigConstructBehaviorGap2018].
-I.e., neither could the gap then be interpreted in terms of an as-if underweighting (overweighting) of rare outcomes in DfE (DfD), nor would any of the potential contributors to the gap considered so far [see, e.g., @hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than other small-probability outcomes.<!--Close footnote-->]
+I.e., neither could the gap then be interpreted in terms of an as-if underweighting (overweighting) of rare outcomes in DFE (DFD), nor would any of the potential contributors to the gap considered so far [see, e.g., @hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than other small-probability outcomes.<!--Close footnote-->]
 Note that for all $\gamma < 1$ the graph of $w$ takes an inverse S-shape and the entire weighting pattern is reversed.
@@
 
-# Sampling Strategies in DfE
+# Sampling Strategies in DFE
 
@@
 Specifically, only rarely in peoples' daily life, the inputs to the decision-making process take the form of explicit descriptions of all outcome-probability pairs.
-In such cases, people would make DfD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
-Yet, rather often, people make DfE, where the mind can learn about the latent properties of prospects only by experiental sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
+In such cases, people would make DFD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
+Yet, rather often, people make DFE, where the mind can learn about the latent properties of prospects only by experiental sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
 Accordingly, for the choice between $1, ..., k$ prospects, the inputs to the decision-making process are generated by a set of prospect-specific stochastic processes
@@
 random variables are commonly assumed.]
-The inputs to DfE are then the realizations of the random variables in (11), which require different algorithms to be processed than do descriptions of the outcomes and their probabilities in DfD.
+The inputs to DFE are then the realizations of the random variables in (11), which require different algorithms to be processed than do descriptions of the outcomes and their probabilities in DFD.
 
@@
 
-Since it is only through their fundamental properties, or combinations thereof, that any distinction between the prospects can be made, systematic choices in DfE must be based on the assessment of differences in the latent properties of prospects.
+Since it is only through their fundamental properties, or combinations thereof, that any distinction between the prospects can be made, systematic choices in DFE must be based on the assessment of differences in the latent properties of prospects.
 Accordingly, the mind may use the sampled outcomes to first infer the latent objective probabilities of all possible outcomes, and then proceed by selecting a property, or combinations thereof, to assess differences among the prospects and make a respective choice.
@@
 To this end, sequential sampling models of decision making [e.g., @busemeyerDecisionFieldTheory1993] assume that the outcomes of prospects are sequentially sampled and integrated into dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DfE, and has shown to explain some of the robust deviations from EV maximization [see @busemeyerDecisionFieldTheory1993; @bhatiaSequentialSamplingParadoxes2014], including the underweighting of rare outcomes in the sampling paradigm [see @markantModelingChoiceSearch2015].
+This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DFE, and has shown to explain some of the robust deviations from EV maximization [see @busemeyerDecisionFieldTheory1993; @bhatiaSequentialSamplingParadoxes2014], including the underweighting of rare outcomes in the sampling paradigm [see @markantModelingChoiceSearch2015].
 Moreover, these models implement speed-accuracy tradeoffs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more (less) accurate but slower (faster) choices for high (low) thresholds.
@@
 
-Figure\ \@ref(fig:weighting-patterns) shows the means and the 95%-intervals of the posterior distributions of the curvature parameter $\gamma$ and elevation parameter $\delta$ as well as the resulting shape of the weighting function.
-Note first that because the relative frequencies were supplied as probability information, the parameter estimates for the threshold value $\theta = 1$ in combination with high switching probabilities have large posterior intervals.
-The estimates substantiate the prediction that $\gamma$ takes values over $1$ and increases with the switching probability, resulting in an S-shaped weighting function. 
-Because the images of the function equal the decision weights, the estimates show that high switching probabilities translate to an underweighting of rare outcomes in CPT.
-The estimates of $\delta$ also tend to increase with increasing switching probabilities.
+Figure\ \@ref(fig:weighting-parameters) shows the means and the 95%-intervals of the posterior distributions of the curvature parameter $\gamma$ and elevation parameter $\delta$ as well as the resulting graphical shape of the weighting function.
+The findings are fairly consinstent with the predictions.
+Note first that the estimates for the parameter combination $\theta = 1$ and $\psi = 1$ have large posterior intervals.
+In these cases, no other relative frequencies than 0 and 1 are supplied to the weighting function, which may explain why the values in between cannot reliably be accounted for.
+However, for $\theta = 1$ and $\psi < 1$, the parameter estimates indicate a linear weighting pattern, demonstrating the well-established explanation that if the prospect with the higher mean across all sampled outcomes is chosen, sampling error can account for any deviations from EV maximization.
+
+For $\theta > 1$, the estimates substantiate the prediction that $\gamma$ takes values $\geq 1$ which increase with the switching probability, resulting in a increasingly pronounced S-shaped weighting function.
+In other words, the higher the switching probability, the more severe is the underweighting (overweighting) of high-rank outcomes of small (large) probability in CPT.
+Moreover, $\delta$ takes values $\geq 1$ and increases slightly with the switching probability, causing the high-rank outcome to be overweighted the most, if its probability is just above the mid-point.
 
@@
 
+Figure\ \@ref(fig:value-parameters) shows the means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$, as well as the shape of the value function.
+As predicted, an increase in the switching probability leads to a decrease in $\alpha$, reflecting that the outcome information is largely ignored if choices are based on ordinal comparisons of single outcomes rather than of means of large samples.
+Note further that the estimates are stable across thresholds.
+Finally, note that the choice sensitivity parameter varied systematically with the switching probability, such that the choices were more sensitive to the valuations in CPT for low values of $\psi$.
+However, even for high values of $\psi$, the choices did not appear to be random.
+
 (ref:value-parameters) Parameter Estimates and Graphical Shape of the Value Function
@@
   scale_y_continuous(limits = c(0,1), breaks = seq(0,1, .5)) + 
-  labs(x = expression(psi),
+  labs(x = element_blank(),
        y = expression(alpha),
@@
   scale_color_viridis(option = "viridis") +
-  theme_apa()
+  theme_apa() + 
+  theme(axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.x = element_blank())
 
@@
   facet_wrap(~a, nrow = 1) + 
-  labs(x = "Switching Probability",
+  labs(x = expression(psi),
        y = expression(rho),
-       color = "Switching\nProbability",
-       shape = "Boundary") +
+       color = expression(psi)) +
   scale_x_continuous(limits = c(0, 1.1), breaks = seq(0, 1,.5)) +
+  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5,2.5)) +
   geom_point() +
@@
 ##merge figure
-ggarrange(alpha, value, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
+ggarrange(alpha, rho, value, ncol = 1, nrow = 3, common.legend = TRUE, legend = "right") 
 ```
 
-(ref:cpt-graphs) Estimated Graphical Shapes of the Weighting and Value Function for Different Simulation Parameters
+In sum, then, the computational analysis substantiates the claim that sampling strategies can be used to alter which difference in the latent properties of prospects evidence is accumulated for and that the choices vary respectively.
+Moreover, it has been demonstrated how these differences in the choice patterns translate to characteristic shapes in CPT's weighting and value function.
 
-```{r cpt-graphs, fig.cap="(ref:cpt-graphs)", eval = FALSE}
-#prepare data
-
-##compute images of weighting and value function
-
-###weighting function
-wf <- cpt %>%
-  select(s, boundary, a, parameter, mean) %>%
-  pivot_wider(names_from = parameter, values_from = mean) %>%
-  select(-c(alpha, rho)) %>%
-  expand_grid(p = seq(0, 1, .05)) %>%
-  mutate(w = round(  (delta * p^gamma)/ ((delta * p^gamma)+(1-p)^gamma), 2))
-
-###value function
-vf <- cpt %>%
-  select(s, boundary, a, parameter, mean) %>%
-  pivot_wider(names_from = parameter, values_from = mean) %>%
-  select(-c(gamma, delta, rho)) %>%
-  expand_grid(x = seq(0, 20, .5)) %>%  
-  mutate(v = round(x^alpha, 2))
-
-##split data to avoid passing two y-values to the same x-value in geom_line()
-wf_a <- wf %>% filter(boundary == "Absolute")
-wf_r <- wf %>% filter(boundary == "Relative")
-vf_a <- vf %>% filter(boundary == "Absolute")
-vf_r <- vf %>% filter(boundary == "Relative")
-
-#plots
-
-##weighting function
-weight <- wf_a %>% #graphs for absolute boundary
-  ggplot(aes(p, w, group = s, color = s)) +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
-  labs(x = "Experienced Probability",
-       y = "Decision Weight",
-       color = "Switching\nProbability") +
-  scale_x_continuous(breaks = seq(0, 1, .5)) +
-  scale_y_continuous(breaks = seq(0, 1, .5)) +
-  geom_line(size = .5) +
-  geom_line(data = wf_r, size = .5) +  #add curves for relative boundary
-  scale_color_viridis(option = "viridis") +
-  theme_apa()
-
-##value function
-value <- vf_a %>% 
-  ggplot(aes(x, v, group = s, color = s)) +
-  facet_wrap(~a, nrow = 1)+ 
-  labs(x = "Objective Outcome",
-       y = "Subjective Value",
-       color="Switching\nProbability") +
-  scale_x_continuous(breaks = seq(0, 20, 10)) +
-  scale_y_continuous(breaks = seq(0, 20, 10)) +
-  geom_line(size = .5) +
-  geom_line(data = vf_r, size = .5) + 
-  scale_color_viridis(option = "viridis") +
-  theme_apa() + 
-  theme(strip.text.x = element_blank())
-
-##merge figures
-ggarrange(weight, value, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
-```
-
-# Summary and Conclusion
+# Discussion
 

### 2022-04-08 manuscript.Rmd
Review of Structure: Moved CPT review into prediction section

@@
 To this end, this paper presents a sampling and accumulation model that allows sampling  strategies—i.e., the probability of sampling outcomes from different prospects in direct succession (switching probability)—to alter which differences in the latent properties evidence is accumulated for.
-Specifically, the proposed model sequentially samples outcomes from two prospects and accumulates the results obtained from a sequence of ordinal comparisons between sample means, with switching probabilities determining the size of the samples underlying each comparison and thresholds determining how much comparisons a prospect must win in order to be chosen.
+Specifically, the proposed model sequentially samples outcomes from two prospects and accumulates the results obtained from a sequence of ordinal comparisons between sample means, with switching probabilities determining the size of the samples underlying each comparison and thresholds determining how many comparisons a prospect must win in order to be chosen.
 A computational implementation of the model is used to simulate the respective information-processing chains upfront choices between a safe and a two-outcome prospect, while varying switching probabilities and thresholds.
@@
 Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DFD and DFE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
-In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructBehaviorGap2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
+In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructbehaviorGapDescription2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
 choice patterns in DFD deviate from the solutions of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities;
-in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructBehaviorGap2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructbehaviorGapBehavioral2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
 Hereafter, these choice patterns are referred to as the *as-if overweighting* and *as-if underweighting of rare outcomes*, respectively.
@@
 
-Therefore, consider first the finding that *sampling strategies* were indicative for the final choice in DFE.
-Specifically, in one paradigm used to study DFE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
+Therefore, first consider the finding that in DFE *sampling strategies* were indicative for the final choice.
+That is, in one paradigm used to study DFE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
 Considering this paradigm and the choice between two prospects, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^[<!--Open footnote-->Note that @hillsInformationSearchDecisions2010 proposed two paradigmatic sampling strategies, where prospects are either switched just once (comprehensive sampling) or after each sampled outcome (piecewise sampling).
@@
 and proposed two different decision strategies that people may adopt.
-That is, for a summary strategy, it is assumed that the prospect is chosen which produced the greater mean across all sampled outcomes.
+Specifically, for a summary strategy, it is assumed that the prospect is chosen which produced the greater mean across all sampled outcomes.
 In turn, for a round-wise strategy, it is assumed that over multiple rounds two sampled outcomes---i.e., one from each of the prospects---are compared and that the prospect is chosen which won the comparison in most rounds.
@@
 
-Now, one explanation for such a reversed predictive pattern would be if the differences in the sampling strategies determine which of the two decision strategies is used.
-To this end, this paper presents a computational model that provides a link between *switching probabilities*---i.e., the probability of sampling outcomes from different prospects in direct succession during the sampling phase---and the decision strategies.
-Specifically, the proposed model accumulates the outcomes obtained from the comparisons between sample means, with switching probabilities determining the size of the samples underlying each mean comparison and thresholds determining how much (more) of such comparisons a prospect must win in order to be chosen.
-Accordingly, the model is such that the higher (lower) the switching probabilities and the higher (lower) the thresholds, the more the accumulation process resembles the round-wise (summary) strategy.
+Now, the current paper presents a sampling and accumulation model that provides an algorithmic link between sampling and decision strategies, and uses the model to discuss how the mind may rely on sampling strategies to alter which differences in the latent properties of prospects evidence is accumulated for.
+More specifically, the proposed model assumes an accumulation process over a sequence of mean comparisons, with switching probabilities---i.e., the probability of sampling
+outcomes from different prospects in direct succession---determining the size of the samples underlying each mean comparison and thresholds determining how many comparisons a prospect must win in order to be chosen.
+The model is such that when switching probabilities are high, the accumulation process unfolds over mean comparisons based on small samples, thus resembling the round-wise strategy and accumulating evidence for differences in the probability to produce a higher outcome most of the time.
+Notably, in this case, small-probability outcomes are predicted to contribute to the majority of mean comparisons less than would be objectively warranted, which can translate to an as-if underweighting of rare outcomes, irrespective of what the thresholds require the number of won comparisons to be.
+<!--Accordingly, while increases in thresholds---and thus in the number of sampled outcomes distributed over multiple small samples, each of which is considered---allow to choose with increasing accuracy the prospect that is more likely to return a higher outcome, the resulting choices can produce an as-if underweighting of rare outcomes.-->
+In turn, for low switching probabilities, the accumulation process unfolds over mean comparisons based on large samples, thus resembling the summary strategy---for low thresholds, respectively---and accumulating evidence for differences in the EV.
 
-The current paper discusses and demonstrates in a computational analysis how such a simple accumulation model can explain an as-if underweighting of rare outcomes, even if a large number of sampled outcomes is fully accounted for.
-More specifically, since the switching probabilities alter the size of the samples underlying each mean comparison, the model predicts the switching probabilities to affect whether a low-probability outcome contributes to the majority of required mean comparisons about as much as would be warranted by its objective probabilities, or whether it contributes rather less.
-Respectively, if the small-probability outcome is smaller (larger) than the EV, high switching probabilities cause the mean to be an inflated (deflated) estimate of the EV in most of the comparisons, which can translate to an as-if underweighting of rare outcomes, irrespective of what the thresholds determine the required number of mean comparisons to be.
-Yet, since the EV is not the only property which can be used to distinguish among the prospects, the proposed model shows how the mind may rely on different sampling strategies to change which differences in the latent properties of prospects evidence is accumulate for.
-Specifically, for low switching probabilities, the accumulation process unfolds over mean comparisons based on large samples and is therefore more indicative for differences in the EV; in turn, for high switching probabilities, the accumulation process unfolds over mean comparisons based on small samples and is therefore more indicative for differences in the probability to produce a higher outcome than the respective other prospect most of the time.
-In either case, then, the model implements a speed-accuracy trade-off of the form that the respective differences in the latent properties are more accurately assessed, the larger the thresholds are, i.e., the more evidence must be accumulated in favor of a prospect.
+To substantiate the discussion, the model is used to simulate the sampling and accumulation process for choices between a safe and a two-outcome prospect, while systematically combining different switching probabilities and thresholds.
+Considering choice rates and parameter estimates of cumulative prospect theory [@tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], the computational analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
+Importantly, the analysis also shows that these distinct choice patterns become more robust with increasing thresholds.
+Before presenting the model and the computational analysis, the following section provides a formal definition of prospects.
 
-To substantiate the discussion, the model is used to simulate the accumulation process for different combinations of switching probabilities and thresholds and to predict choices between a two-outcome prospect and a safe prospect, respectively.
-Considering choice rates and parameter estimates of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], the computational analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
-Importantly, the analysis also shows that the differences between switching probabilities become more pronounced with increasing thresholds.
-In other words, the proposed model predicts an as-if underweighting of rare outcomes to occur when high switching probabilities cause the accumulation process to unfold over mean comparisons that are based on small samples.
-Thus, the analysis substantiates the claim that not only the reliance on just a portion of a large number of sampled outcomes can explain an as-if underweighting of rare outcomes in DFE, but also the reliance on multiple or many small samples.
-Moreover, the analysis shows that an as-if underweighting of rare outcomes cannot be equated with inaccurate inferences about latent properties---e.g., the EVs---that carry over to the subsequent choices.
-Rather the opposite, an as-if underweighting of rare outcomes can also be caused by an accurate assessment of the differences among prospects in the latent probability to produce a higher outcome most of the time.
-Before presenting the model and the computational analysis, the following section provides a formal definition of prospects and reviews how CPT in general and its weighting function in particular can be used to capture deviations from EV maximization.
-
-# Prospects and the Description of Choices in CPT
+# Formal Definition of Prospects
 
 Since there is an uncountable number of choices people confront in the natural world, behavioral decision research routinely abstracts from choices between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.
+Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.^[<!--Open footnote-->See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion on the reasonableness of such abstractions.<!--Close footnote-->]
 These fundamental properties are considered the possible outcomes of a choice alternative and the probabilities with which these outcomes occur following the choice of the alternative.
 Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs are prospects.
-As such, prospects can be understood as the distribution of a discrete random variable, for which the following section briefly provides an axiomatic basis.
-
-## Formal Definition of Prospects
-
-Following @kolmogorovFoundationsTheoryProbability1950 and adopting the symbolic notation from @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, let the tuple $(\Omega, \mathcal{F}, P)$ be a probability space.
+As such, prospects can be understood as the distribution of a discrete random variable.
+More specifically, following @kolmogorovFoundationsTheoryProbability1950 and adopting the notation from @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, let the tuple $(\Omega, \mathcal{F}, P)$ be a probability space.
 Accordingly, $\Omega$ is a finite sample space with each element $\omega \in \Omega$ denoting a possible consequence of choosing the respective prospect.
@@
 $$
-where each element $P'$ can itself be considered a set of outcome-probability pairs $\{(x_i, p_X(x_i)\}_{i \in \mathbb{N}}$.
+where each element $P'$ can itself be considered a finite set of outcome-probability pairs $\{(x_i, p_X(x_i)\}_{i \in \mathbb{N}}$.
 
-## CPT and the Concept of Probability Weighting
+# Sampling Strategies and the Accumulation of Evidence
 
-The choices people actually make between prospects are often described in terms of deviations from the principle of EV maximization, according to which the prospect with the largest EV
+Since it is only through their fundamental properties, or combinations thereof, that any distinction between the prospects can be made, systematic---as opposed to random---choices between prospects must be based on the assessment of differences in their properties.
+However, only rarely in peoples' daily life, the inputs to the decision-making process take the form of explicit descriptions of all outcome-probability pairs.
+In such cases, people would make DFD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
+Yet, rather often, people make DFE, where the mind can learn about the latent properties only by experiential sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
+Accordingly, for the choice between $1, ..., k$ prospects, the inputs to the decision-making process are generated by a set of prospect-specific stochastic processes
+$$
+\{\{X^1_t\}, ... , \{X^k_t\}\}
+\; ,
+\tag{6}
+$$
+where each $\{X_{t}\}_{t \in \mathbb N}$ is a collection of independent and identically distributed (i.i.d.) random variables.^[Note that it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
+660].
+However, in the sampling paradigm, i.i.d.
+random variables are commonly assumed.]
+The inputs to DFE are then the realizations of the random variables in (6).
+
+The mind may use these realizations---i.e., the sampled outcomes---to first infer the latent properties and then proceed by selecting a property, or combinations thereof, to assess differences among the prospects and make a respective choice.
+However, the mind may also approximate such a process by directly accumulating evidence about the differences in latent properties from the sampled outcomes.
+To this end, sequential sampling models of decision making [e.g., @busemeyerDecisionFieldTheory1993] assume that the outcomes of prospects are sequentially sampled and integrated into dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
+This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DFE, and has shown to explain some of the robust deviations from EV maximization [see @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993], including the as-if underweighting of rare outcomes in the sampling paradigm [see @markantModelingChoiceSearch2015].
+Moreover, these models implement speed-accuracy trade-offs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more (less) accurate but slower (faster) choices for high (low) thresholds.
+
+Yet, there are several distinct properties that can be used to assess differences between the prospects, among them the EV, for which the summary decision strategy is indicative, and the probability to produce a higher outcome most of the time, for which the round-wise decision strategy is indicative [see @hillsInformationSearchDecisions2010].
+Respectively, in the following, both decision strategies are implemented into a common sampling and accumulation model to demonstrate how the mind may rely on different sampling strategies to alter the degree to which evidence is accumulated for differences in either one of these properties.
+More specifically, the proposed model accumulates the outcomes obtained from a sequence of comparisons between sample means, with the size of the samples underlying each mean comparison tending to be large (small) for low (high) switching probabilities.
+Accordingly, whereas the decision variables of the model capture how many comparisons a prospect has won, the unfolding accumulation process more closely resembles the summary strategy for low switching probabilities and the round-wise strategy for high switching probabilities.
+
+## Model
+
+We consider the sampling paradigm and a choice between two prospects denoting the distributions $P'^X$ and $P'^Y$ of the discrete random variables $X$ and $Y$, respectively.
+The model assumes that the sampling process starts at random with a stochastic process on one of the two random variables.
+Specifically, it is assumed that an agent starts with equal probability to sample from one of the prospects, say $P'^X$, and generates a sequence of random variables $X_1, X_2,...$, where the mean over the sequence is computed or updated with each new outcome that is sampled.
+The respective stochastic process $\{S^X_n\}_{n \in \mathbb{N}}$ is defined by
+$$
+S^X_n = \frac{1}{n} \sum_{t = 1}^n X_t, \quad n \in \mathbb{N}
+\; ,
+\tag{7}
+$$
+and terminates as soon as an outcome is sampled from the other prospect.
+The switching probability $\psi \in (0,1]$, which is assumed to be adopted prior the start of the information-processing chain and is fixed throughout, controls the probability with which outcomes from different prospects are sampled in direct succession.
+In other words, the switching probability is the probability with which the stochastic process on the current random variable stops and a new stochastic process on the other random variable starts with the subsequently sampled outcome.
+To implement the accumulation process, the model assumes that each time after a new stochastic process was started and terminated on both random variables, their respective values are compared, with the prospect underlying the stochastic process with the greater final value receiving a round win.
+Accordingly, for the prospect $P'^X$, this stage is modeled as the mapping
+$$
+\begin{aligned}
+  Z^X : \mathbb{R} &\to \mathbb{N} \\
+  S^X_n - S^Y_n &\mapsto 
+  \begin{cases}
+     1 &\text{if} \quad  S^X_n > S^Y_n, \\
+     0 &\text{else}
+     \; ,
+  \end{cases}
+\end{aligned}
+\tag{8}
+$$
+where $Z^X$ is a random variable that takes only the two values $0$ and $1$, denoting a lost or won mean comparison, respectively. 
+The model assumes that a round consisting of a pair of stochastic processes---i.e., one for each prospect---and the subsequent comparison of their final values is repeated until the sum of round wins for one of the two prospects reaches a threshold $\theta \in \mathbb{N}$.
+Similar to the switching probability, it is assumed that the threshold is adopted prior the start of the information-processing chain and is fixed throughout.
+For $P'^X$, then, we obtain a sequence of independent comparisons $Z^X_1, Z^X_2, ...$ and model the respective evidence accumulation process as a random walk $\{D^X_m\}_{m \in \mathbb{N}}$ defined by 
+$$
+D^X_m = \sum_{i = 1}^m Z^X_i, \quad m \in \mathbb{N}
+\;,
+\tag{9}
+$$
+resembling a dynamic decision variable.
+Note that since (8) describes a Bernoulli trial, the random walk in (9) is based on a Bernoulli process.
+
+Finally, note that the described model assumes two random walks---i.e., one for each prospect---approaching the same threshold, which is the absolute number of mean comparisons a prospect must win in order to be chosen.
+However, one may also define a single random walk, resembling a common dynamic decision variable, which approaches a positive threshold $\theta^+$ and a negative threshold $\theta^-$.
+Therefore, (8) may be adapted such that $Z$ takes the value $-1$ instead of $0$, such that the threshold determines how many more mean comparisons a prospect must win in order to be chosen.
+
+# Model Predictions
+
+Below, the key predictions concerning the effects of the model parameters $\psi$ and $\theta$ on the length of the sampling and accumulation process and the resulting choice are outlined.
+Moreover, previous research has shown that differences as to how information about the properties of prospects is processed can translate to characteristic shapes of cumulative prospect theory's (CPT) value and weighting function [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021].
+Respectively, this section also contains predictions about the relations between $\psi$ and $\theta$ and the CPT parameters.
+A summary of the model predictions can be found in Table\ \@ref(tab:predictions).
+
+(ref:predictions) Summary of Model Predictions
+
+```{r predictions}
+predictions <- tibble("Measure" = 
+                        c("Choices pattern",
+                          "",
+                          "$\\gamma$ (curvature of $w$)",
+                          "$\\delta$ (elevation of $w$)",
+                          "$\\alpha$ (concavity of $v$)"),
+                      "Predictions for changes in $\\psi$" = 
+                        c("More EV maximization for decreasing $\\psi$",
+                          "More as-if underweighting of rare outcomes for increasing $\\psi$",
+                          "$\\geq 1$, increases with $\\psi$",
+                          "1, no effect of $\\psi$",
+                          "$\\leq 1$, decreases with increasing $\\psi$"))
+apa_table(predictions, caption = "(ref:predictions)", note = "The predictions for changes in $\\psi$ should become more robust for increasing values of $\\theta$ as choices become more systematic for high thresholds.", escape = FALSE)
+```
+
+## Length of Information-Processing Chains
+
+The required number of independent mean comparisons increases with thresholds $\theta$.
+Since each comparison is based on its own pair of stochastic processes, an increase in $\theta$ translates to a larger number of required stochastic processes and, ceteris paribus, therefore also to a larger overall number of outcomes sampled over the course of a sampling and accumulation process.
+In turn, each stochastic process is predicted to terminate faster, the higher the probability that the subsequent outcome is sampled from the other prospect, determined by the switching probability $\psi$.
+Accordingly, an increase in $\psi$ leads to shorter stochastic processes, which translate, ceteris paribus, to a smaller overall number of sampled outcomes.
+
+## Final Choice
+
+Because the switching probability $\psi$ is predicted to alter the length of the stochastic processes underlying each mean comparison, $\psi$ should affect whether low-probability outcomes contribute to the majority of the required mean comparisons about as much as would be warranted based on their objective probabilities, or whether they contribute rather less.
+That is, for short stochastic processes, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur over the course of such a process to be smaller rather than larger than their latent objective probabilities.
+Respectively, if the small-probability outcome is smaller (larger) than the EV, high values of $\psi$---and therefore pairs of short stochastic processes---cause the mean to be an inflated (deflated) estimate of the EV.
+Such an inflation and deflation of the means can then translate to an as-if underweighting of rare outcomes.
+Specifically, if the mean of the prospect with the lower (higher) EV is inflated (deflated), the outcome of the comparison between the means may be a reversal---in sign---of the outcome of a comparison between the EVs, leading to choices that take the form of an as-if underweighting of rare outcomes.
+Yet, if the mean of the prospect with the lower (higher) EV is deflated (inflated), the difference between the means should be larger than the differences between the EV, which can simplify EV maximization [see @hertwigDecisionsExperienceWhy2010].
+In turn, for low values of $\psi$---and therefore pairs of long stochastic processes---the means should closely correspond to the EVs, leading to choices that are in line with EV maximization.
+To summarize the choice predictions for $\psi$ and simplify: 
+If the prospect that is more likely to return a higher outcome most of the time does not also possess the higher EV, high values of $\psi$ are predicted to cause an as-if underweighting of rare outcomes.
+Respectively, while these predictions emphasize the close link between small samples and the underweighting of rare outcomes, they suggest that the reliance on small samples can serve the accumulation of evidence for differences in a latent property.
+
+More so, for an increasing sequence of independent comparisons between single outcomes sampled from two prospects, the relative winning frequency of a prospect should converge against the objective probability of producing a higher outcome in each comparison.
+Accordingly, the as-if underweighting of rare outcomes should become more robust as the thresholds $\theta$ increase.
+
+## Cumulative Prospect Theory
+
+Before elaborating how the above model predictions may translate into estimates of the CPT parameters, the following section reviews how CPT in general and its weighting function in particular capture deviations from EV maximization.
+
+### Formal Review of CPT
+
+The choices people make between prospects are often *described* in terms of deviations from EV maximization, according to which the prospect with the largest EV
 $$
 EV = \sum_i^n x_i \times p_X(x_i)
-\tag{6}
+\tag{10}
 $$ 
 should be chosen.
-To *describe* how people's actual choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, where the latter were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
+To describe how people's choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, where the latter were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
 Together, these empirical choice patterns indicate a violation of EV and expected utility (EU) maximization [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
-CPT and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by assuming that people maximize the value
+CPT and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by assuming that people maximize the valuation
 $$
@@
 \; ,
-\tag{7}
+\tag{11}
 $$ 
@@
 \end{aligned}
-\tag{8}
+\tag{12}
 $$
@@
   \end{cases}
-\tag{9}
+\tag{13}
 $$
@@
 Essentially, the model is such that the cumulative decision weights derived for the outcomes may be greater or smaller than their objective probabilities, causing the transformed outcomes---i.e., the subjective values---to be over- or underweighted *in* CPT, respectively.
-Accordingly, for the description of choices, one may adopt the as-if weighting terminology from the introduction by stating that people choose as if they maximized the value in (7) and applied the weighting pattern that was estimated in CPT.
-Importantly, the as-if prefix indicates that it cannot be concluded from the estimated weighting pattern that the mind does indeed perform any of the computations associated with the weighting of subjective values in CPT; rather, the mind processes the information about the choice alternatives in a way that the resulting choices translate to the estimated weighting pattern.
-The as-if weighting terminology is therefore reminiscent of the distinction between different levels of explanation [cf. @marrVisionComputationalInvestigation1982].
-That is, CPT may be considered a computational-level theory that specifies the computational problem the mind faces when being confronted with the choice between prospects, and how this problem may be solved by the abstract calculus of CPT.
-However, as such, CPT cannot substitute algorithmic-level theories and process models that make claims about how exactly the mind transforms the inputs to the decision-making process into outputs which approximate the solutions of CPT [see @zilkerMeasuringModelingConstruction2020; see also @griffithsProbabilisticModelsCognition2010].
-Respectively, this paper uses CPT as a mere data model to show how differences in the information-processing chain upfront choices in DFE---considered in the following section---may cause particular weighting patterns, among them the as-if underweighting of rare outcomes which has been found to be a robust behavioral phenomena in DFE.
-To this end, the paper first continues to review the weighting patterns that can possibly estimated in CPT.
+Accordingly, for the description of choices, one may adopt an as-if weighting terminology by stating that people choose as if they maximized the value in (11) and applied the weighting pattern that was estimated in CPT.
+Importantly, the as-if prefix indicates that it cannot be concluded from the estimated weighting pattern that the mind indeed performs any of the computations associated with the weighting of subjective values;
+rather, the mind processes the information about the properties of choice alternatives in a way that the resulting choices translate to the estimated weighting pattern [@gigerenzerHowExplainBehavior2020].
+Respectively, this paper treats CPT as a data model and discusses---and refines in a simulation---what weighting patterns can be expected, were the mind to carry out the information-processing chains that are assumed by the proposed sampling and accumulation model [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021, for similar theoretical inquiries].
 
-Now, several consequences for the weighting pattern that can be estimated in CPT follow from (9):
+Now, several consequences for the weighting patterns that can be estimated in CPT follow from (13), which are briefly reviewed next:
 
@@
 
-* The value of $\pi$ depends on the estimated shape of the graph of $w$ or the weighting function's parameters, respectively.
-That is, the shape of the graph of $w$ displays over which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
+* The value of $\pi$ depends on the estimated shape of the graph of $w$, i.e., the weighting function's parameters.
+Specifically, the shape of the graph of $w$ displays over which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
 Hence, for a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
@@
 \noindent
-Given that the value of each cumulative decision weight depends on the two transformed cumulative probabilities in (9)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the weighting pattern are reviewed by considering the actual weighting function.
+Because the value of each $\pi$ depends on the two transformed cumulative probabilities in (13)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the possible weighting patterns are reviewed by considering the actual weighting function.
 Therefore, Figure\ \@ref(fig:weighting-function) illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
-Now, let each $p$ on the abscissa be one of the four cumulative probabilities from (9). 
+Now, let each $p$ on the abscissa be one of the four cumulative probabilities from (13). 
 Then each graph in Figure\ \@ref(fig:weighting-function) displays the graphical shape of the weighting function
@@
 \end{aligned}
-\tag{10}
+\tag{14}
 $$
@@
 Evidently, both parameters have distinct effects on the graphs' shape, with $\gamma$ affecting the curvature and $\delta$ the elevation.
-As a consequence from (9) then, each combination of parameters implies a particular weighting pattern, with some of them being similar and others being rather distinct.
+As a consequence from (13), then, each combination of parameters implies a particular weighting pattern, with some of them being similar and others being rather distinct.
 
@@
 
-In some more detail, the gray-dashed identity lines in Figure\ \@ref(fig:weighting-function) imply a linear weighting pattern.
-That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are derived according to (9) would be equal to the differences between the respective objective cumulative probabilities and therefore also to the objective probabilities of the outcomes for which the weights are determined.
+More specifically: The gray-dashed identity lines in Figure\ \@ref(fig:weighting-function) imply a linear weighting pattern.
+That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are derived according to (13) would be equal to the differences between the respective objective cumulative probabilities---and therefore also to the objective probabilities of the outcomes for which the weights are determined.
 Such a linear weighting pattern is implied by $\gamma = 1$ and $\delta = 1$. 
@@
 Specifically, because of the S-shaped curvature, the differences between the images $w(p)$ may be smaller than those between the respective cumulative probabilities in the lower and upper part of the cumulative probability scale, but may be considerably greater in the middle part.
-As a consequence, the cumulative decisions weights are smaller than the respective objective probabilities for small-probability outcomes of either a low rank or a high rank, but they are larger for small-probability outcomes of a middle rank.^[<!--Open footnote-->Note that the distinction between outcomes of either low/high rank or middle rank is unnecessary for two-outcome prospects [see @tverskyAdvancesProspectTheory1992].
+As a consequence, the cumulative decisions weights are smaller than the respective objective probabilities for small-probability outcomes of low and high rank, but they are larger for small-probability outcomes of a middle rank.^[<!--Open footnote-->Note that the distinction between outcomes of either low/high rank or middle rank is unnecessary for at most two-outcome prospects [see @tverskyAdvancesProspectTheory1992].
 However, for finite many outcomes, the distinction is critical.
-More so, the fact that CPT may weigh outcomes of the same small probability differently, adds another reasons why the description-experience gap should not be equated with a reversed weighting pattern in CPT [see @hertwigConstructBehaviorGap2018].
-I.e., neither could the gap then be interpreted in terms of an as-if underweighting (overweighting) of rare outcomes in DFE (DFD), nor would any of the potential contributors to the gap considered so far [see, e.g., @hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than other small-probability outcomes.<!--Close footnote-->]
+More so, the fact that CPT may weigh outcomes of the same small probability differently, adds another reasons why the description-experience gap should not be equated with a reversed weighting pattern in CPT [see @hertwigConstructbehaviorGapDescription2018].
+I.e., neither could one interpretation of the gap be in terms of an as-if underweighting (overweighting) of rare outcomes in DFE (DFD), nor would any of the potential contributors to the gap considered so far [cf.
+@hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than other small-probability outcomes.<!--Close footnote-->]
 Note that for all $\gamma < 1$ the graph of $w$ takes an inverse S-shape and the entire weighting pattern is reversed.
@@
 That is, for $\delta < 1$, the interval on the cumulative probability scale over which the weighting function runs below the identity line is greater than the interval over which the weighting function runs above the identity line; and this pattern reverses for $\delta > 1$.
-More specifically, $\delta$ shifts across the entire cumulative probability scale the intervals within which small differences between objective cumulative probabilities translate to either smaller or greater cumulative decision weights.
-In other words then, for any decrease (increase) in $\delta$, the underweighting of small probability outcomes extends to more outcomes at the lower (higher) end of the outcome range.
+In other words, $\delta$ shifts across the entire cumulative probability scale the intervals within which small differences between objective cumulative probabilities translate to either smaller or greater cumulative decision weights.
 
-To summarize the preceding paragraphs, CPT is a statistical or data model that can be used to describe choices between prospects by capturing systematic deviations from EV maximization in the parameter estimates of its value and weighting function.
-Importantly, each estimated weighting function implies a weighting pattern.
-Although the possible weighting patterns depend on the exact parameterization of the weighting function [e.g., @goldsteinExpressionTheoryPreference1987], the latter's graph usually takes a more or less accentuated (inverse) S-shape, which implies a weighting pattern where small-probability outcomes of low and high rank are underweighted (overweighted) in CPT's overall evaluation of a prospect according to (7).
-Notably, for the case of choices between at most two-outcome prospects, the weighting pattern reduces to either an underweighting or overweighting of rare outcomes.
-For the description of such choices, one may then adopt the as-if weighting terminology from the introduction, by stating that people decide as if they were either underweighting or overweighting rare outcomes.
+To summarize the preceding paragraphs: CPT is a data model that can be used to describe choices between prospects by capturing systematic deviations from EV maximization in the parameter estimates of its value and weighting function.
+Because the graph of the weighting function usually takes a more or less accentuated (inverse) S-shape, the implied weighting pattern is such that small probability outcomes of low and high rank are underweighted (overweighted) in CPT's valuation of a prospect according to (11).
 
-# Sampling Strategies in DFE
+### How Is CPT Expected to Reflect the Model Predictions?
 
-The need to distinguish between the computational and the algorithmic level in the domain of decision making is exemplified by the fact that information about prospects may come in the form of descriptions or sampled outcomes.
-Specifically, only rarely in peoples' daily life, the inputs to the decision-making process take the form of explicit descriptions of all outcome-probability pairs.
-In such cases, people would make DFD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
-Yet, rather often, people make DFE, where the mind can learn about the latent properties of prospects only by experiental sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
-Accordingly, for the choice between $1, ..., k$ prospects, the inputs to the decision-making process are generated by a set of prospect-specific stochastic processes
-$$
-\{\{X^1_t\}, ... , \{X^k_t\}\}
-\; ,
-\tag{11}
-$$
-where each $\{X_{t}\}_{t \in \mathbb N}$ is a collection of independent and identically distributed (i.i.d.) random variables.^[Note that it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
-660].
-However, in the sampling paradigm, i.i.d.
-random variables are commonly assumed.]
-The inputs to DFE are then the realizations of the random variables in (11), which require different algorithms to be processed than do descriptions of the outcomes and their probabilities in DFD.
+To simplify matters, the further discussion and the computational analysis are constrained to choices between a safe prospect---possessing just one outcome that occurs with certainty---and a two-outcome prospect (hereafter: risky prospect).
+All outcomes are assumed to be positive and the safe outcome is assumed to fall between the the low-rank outcome, $x_{low}$, and the high-rank outcome, $x_{high}$, of the risky prospect to omit dominant prospects.
 
-## Accumulating Evidence About Differences in Latent Properties
-
-Since it is only through their fundamental properties, or combinations thereof, that any distinction between the prospects can be made, systematic choices in DFE must be based on the assessment of differences in the latent properties of prospects.
-Accordingly, the mind may use the sampled outcomes to first infer the latent objective probabilities of all possible outcomes, and then proceed by selecting a property, or combinations thereof, to assess differences among the prospects and make a respective choice.
-However, the mind may also approximate such a process by using an algorithm that omits explicit inferences and directly accumulates evidence about the differences in latent properties from the sampled outcomes.
-To this end, sequential sampling models of decision making [e.g., @busemeyerDecisionFieldTheory1993] assume that the outcomes of prospects are sequentially sampled and integrated into dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DFE, and has shown to explain some of the robust deviations from EV maximization [see @busemeyerDecisionFieldTheory1993; @bhatiaSequentialSamplingParadoxes2014], including the underweighting of rare outcomes in the sampling paradigm [see @markantModelingChoiceSearch2015].
-Moreover, these models implement speed-accuracy tradeoffs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more (less) accurate but slower (faster) choices for high (low) thresholds.
-
-Yet, there are several distinct properties that can be used to assess differences among the prospects.
-Specifically, the summary and the round-wise decision strategy---for which either the prospect is chosen that produced the greater mean across all sampled outcomes or the prospect that won more comparisons between single sampled outcomes, respectively [see @hillsInformationSearchDecisions2010]---can each be indicative for differences in a distinct latent property.
-That is, for a large number of sampled outcomes, the summary strategy is indicative for differences in the latent EV as the mean of a large collection of i.i.d.
-random variables converges to the EV of the respective random variable.
-In turn, the round-wise strategy is indicative for differences in the likelihood to produce a higher outcome than the other prospect.
-Respectively, in the following section, the summary and the round-wise strategy are implemented into a common accumulation model that shows how the mind may accumulate evidence for differences in distinct latent properties [see also @bhatiaChoiceRulesAccumulator2017, where heuristic choice rules are integrated into an accumulation model].
-More specifically, the proposed model accumulates the outcomes obtained from a sequence of comparisons between sample means, with the size of the samples underlying each mean comparison tending to be small (large) for high (low) switching probabilities.
-Accordingly, whereas the decision variables of the model capture how much (more) comparisons between sample means a prospect has won, the unfolding accumulation process more closely resembles the round-wise strategy for high switching probabilities and the summary strategy for low switching probabilities.
-Hence, the model also shows how the mind may rely on different sampling strategies to alter which differences in the latent properties of prospects evidence is accumulated for.
-
-## Model
-
-We consider the sampling paradigm and a choice between two prospects denoting the distributions $P'^X$ and $P'^Y$ of the discrete random variables $X$ and $Y$, respectively.
-The model assumes that the information-processing chain starts at random with a stochastic process on one of the two random variables.
-Specifically, it is assumed that an agent starts with equal probability to sample from one of the prospects, say $P'^X$, and generates a sequence of random variables $X_1, X_2,...$, where the mean over the sequence is computed or updated with each new outcome that is sampled.
-The respective stochastic process $\{S^X_n\}_{n \in \mathbb{N}}$ is defined by
-$$
-S^X_n = \frac{1}{n} \sum_{t = 1}^n X_t, \quad n \in \mathbb{N}
-\; ,
-\tag{12}
-$$
-and terminates as soon as an outcome is sampled from the other prospect.
-The switching probability $\psi \in (0,1]$, which is assumed to be adopted prior the start of the information-processing chain and to be fixed throughout, controls the probability with which outcomes from different prospects are sampled in direct succession.
-In other words, the switching probability is the probability with which the stochastic process on the current random variable stops and a new stochastic process on the other random variable starts with the subsequently sampled outcome.
-To implement an evidence accumulation process, the model assumes that each time after a new stochastic process was started and terminated on both random variables, their respective values---i.e., the means over the sequences---are compared, with the prospect underlying the stochastic process with the greater final value receiving a round win.
-Accordingly, for the prospect $P'^X$, this stage is modeled as the mapping
+To begin with, note through simplifying (13) to
 $$
 \begin{aligned}
-  Z^X : \mathbb{R} &\to \mathbb{N} \\
-  S^X_n - S^Y_n &\mapsto 
-  \begin{cases}
-     1 &\text{if} \quad  S^X_n > S^Y_n, \\
-     0 &\text{else}
+  \pi_{high} &= w(p_x(x_{high})) \\
+  \pi_{low} &= w(p_x(x_{low}) + p_x(x_{high})) - w(p_x(x_{high})) \\
+  &= 1 - \pi_{high}
   \; ,
-  \end{cases}
 \end{aligned}
-\tag{13}
+\tag{15}
 $$
-where $Z^X$ is a random variable that takes only the two values $0$ and $1$, denoting a lost or won mean comparison, respectively. 
-The model assumes that a round consisting of a pair of stochastic processes---i.e., one for each prospect---and the subsequent comparison of their final values is repeated until the sum of round wins for one of the two prospects reaches a threshold $\theta \in \mathbb{N}$.
-Similar to the switching probability, it is assumed that the threshold is adopted prior the start of the information-processing chain and is fixed throughout.
-For $P'^X$, then, we obtain a sequence of independent comparisons $Z^X_1, Z^X_2, ...$ and model the respective evidence accumulation process as a random walk $\{D^X_m\}_{m \in \mathbb{N}}$ defined by 
-$$
-D^X_m = \sum_{i = 1}^m Z^X_i, \quad m \in \mathbb{N}
-\;,
-\tag{14}
-$$
-resembling a dynamic decision variable.
-Note that since (13) describes a Bernoulli trial, the random walk in (14) is based on a Bernoulli process.
-
-Finally, note that the described model assumes two random walks---i.e., one for each prospect---approaching the same threshold, which is the absolute number of mean comparisons a prospect must win in order to be chosen.
-However, one may also define a single random walk, resembling a common dynamic decision variable, which approaches a positive threshold $\theta^+$ and a negative threshold $\theta^-$.
-Therefore, (13) may be adapted such that $Z$ takes the value $-1$ instead of $0$, such that the threshold determines how many more mean comparisons a prospect must win in order to be chosen.
-
-### Model Predictions
-
-Below, the key predictions concerning the effects of the model parameters---i.e., the switching probability $\psi$ and the threshold $\theta$---on the length of the information-processing chain and the final choice are outlined.
-Moreover, previous research has shown that differences as to how information about the properties of prospects is processed can translate to characteristic shapes of CPT's value and weighting function [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021].
-Respectively, this section also contains predictions about the potential relations between $\psi$ and $\theta$ and the CPT parameters.
-A summary of the model predictions can be found in Table\ \@ref(tab:predictions).
-
-#### Length of Information-Processing Chain
-
-The model predicts the overall number of sampled outcomes to increase with thresholds.
-Specifically, the required number of independent mean comparisons increases with thresholds.
-Then, since each comparison is based on its own pair of stochastic processes, an increase in thresholds translates to a larger number of required stochastic processes and, ceteris paribus, therefore also to a larger overall number of sampled outcomes.
-In turn, the model predicts the overall number of sampled outcomes to decrease with increasing switching probabilities.
-Specifically, each stochastic process is predicted to terminate faster, the higher the probability that the subsequent outcome is sampled from the other prospect---i.e., the switching probability.
-Accordingly, an increase in the switching probability leads to shorter stochastic processes which translates, ceteris paribus, to a smaller overall number of sampled outcomes.
-
-#### Final Choice
-
-Note first that the thresholds and switching probabilities alter the degree to which the accumulation process resembles the summary or the round-wise strategy.
-That is, for low thresholds and switching probabilities, only a few mean comparisons based on pairs of long stochastic processes---i.e., large samples---are carried out, thereby resembling the summary strategy.
-Accordingly, for such parameter combinations, the model predicts the prospect to be chosen that possesses the larger EV.
-In turn, for high thresholds and switching probabilities, many mean comparisons based on pairs of short stochastic process---i.e., small samples---are carried out, thereby resembling the round-wise strategy.
-Accordingly, for such parameter combinations, the model predicts the prospect to be chosen that is more likely to return a higher outcome.
-Yet, if the prospect that is more likely to return a higher outcome does not possess the higher EV, the parameter combinations resembling the round-wise strategy are predicted to cause a deviation from the solutions of EV maximization.
-
-Now, more specifically, because the switching probability is predicted to alter the length of the stochastic processes underlying each mean comparison, the switching probability should affect whether low-probability outcomes contribute to the majority of the required mean comparisons about as much as would be warranted based on their objective probabilities, or whether they contribute rather less.
-That is, for short stochastic processes, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur over the course of such a process to be smaller rather than larger than their latent objective probabilities.
-Respectively, if the small-probability outcome is smaller (larger) than the EV, high switching probabilities---and therefore pairs of short stochastic processes---cause the mean to be an inflated (deflated) estimate of the EV.
-Such an inflation and deflation of the means for high switching probabilities can then translate to an as-if underweighting of rare outcomes.
-Specifically, if the mean of the prospect with the lower (higher) EV is inflated (deflated), the outcome of the comparison between the means may be a reversal---in sign---of the outcome of a comparison between the EVs, leading to choices that take the form of an as-if underweighting of rare outcomes.
-Yet, if the mean of the prospect with the lower (higher) EV is deflated (inflated), the difference between the means is an amplification of the differences between the EV, which can actually simplify EV maximization [@hertwigDecisionsExperienceWhy2010].
-In turn, low switching probabilities---and therefore pairs of long stochastic processes---cause the mean to closely correspond to the EV, leading to choices that are in line with EV maximization.
-
-Finally, because each comparison’s contribution to the accumulated evidence is weighted equally, the predictions made for given switching probabilities should become more robust as the thresholds and therefore the number of independent comparisons increases.
-That is, the thresholds implement a speed-accuracy trade-off of the form that whatever systematic differences in the latent properties of prospects may be represented in a sequence of mean comparisons, should be more accurately assessed as the thresholds increase.
-Accordingly, the as-if underweighting of rare outcomes that is predicted to occur for high switching probabilities should remain and become more pronounced the higher the thresholds are.
-Thus, the model's predictions should substantiate the claim made at the outset of the paper, namely, that the reliance on multiple or many small samples---in the form of comparisons between pairs of short stochastic processes---can cause an as-if underweighting of rare outcomes while fully accounting for a large number of sampled outcomes.
-
-#### Cumulative Prospect Theory
-
-To elaborate how the differences in the predictions made for the model parameters may be described in CPT's parameters, the value function of Tversky and Kahneman [-@tverskyAdvancesProspectTheory1992, see (8)] and the weighting function of Goldstein and Einhorn [-@goldsteinExpressionTheoryPreference1987, see (10)] are used.
-To simplify matters, the further discussion and the computational analysis are constrained to choices between a safe prospect---possessing just one outcome that occurs with certainty---and a two-outcome risky prospect.
-All outcomes are assumed to be positive and the safe outcome is assumed to fall between the the low-rank outcome, $x_{low}$, and the high-rank outcome, $x_{high}$, of the risky prospect in order to omit dominant prospects that always lead to a higher outcome than the respective other prospect.
+that the possible weighting patterns amount to an over- and underweighting of the high-rank outcome of the risky prospect.
+That is, the images of the weighting function equal the decision weights assigned to the high-rank outcome of the risky prospect.
 
@@
 Accordingly, for high switching probabilities, the weighting pattern should be such that the high-rank outcome is overweighted for $p_x(x_{high}) > .5$ and otherwise underweighted.
-Note now that the possible weighting patterns for choices between at most two-outcome prospects readily reduces to an over- or underweighting of the high-rank outcome [@zilkerNonlinearProbabilityWeighting2021]:
-$$
-\begin{aligned}
-  \pi_{high} &= w(p_x(x_{high})) \\
-  \pi_{low} &= w(p_x(x_{low}) + p_x(x_{high})) - w(p_x(x_{high})) \\
-  &= 1 - \pi_{high}
-  \; .
-\end{aligned}
-\tag{15}
-$$
-That is, the images of the weighting function equal the decision weights assigned to the high-rank outcome of the risky prospect.
+
 Hence, for high switching probabilities, the graph of the weighting function is predicted to run below the identity line for $p_x(x_{high}) < .5$---leading to an underweighting of small-probability outcomes---and above the identity line for $p_x(x_{high}) > .5$---leading to an overweighting of high-probability outcomes.
@@
 
-(ref:predictions) Summary of Model Predictions
-
-```{r predictions}
-predictions <- tibble("Measure" = 
-                        c("Choices pattern",
-                          "",
-                          "$\\gamma$ (curvature of $w$)",
-                          "$\\delta$ (elevation of $w$)",
-                          "$\\alpha$ (concavity of $v$)"),
-                      "Predictions for changes in $\\psi$" = 
-                        c("More EV maximization for decreasing $\\psi$",
-                          "More as-if underweighting of rare outcomes for increasing $\\psi$",
-                          "$\\geq 1$, increases with $\\psi$",
-                          "1, no effect of $\\psi$",
-                          "$\\leq 1$, decreases with increasing $\\psi$"))
-apa_table(predictions, caption = "(ref:predictions)", note = "The predictions for changes in $\\psi$ should become more robust for increasing values of $\\theta$ as choices become more systematic for high thresholds.", escape = FALSE)
-```
-
 # Simulation Study
@@
 To substantiate and refine the predictions of the model, a computational implementation was used to simulate the sampling and accumulation process for a set of choices between a safe prospect and a two-outcome (risky) prospect.
-The computational model was written in `R` [@rcoreteamLanguageEnvironmentStatistical2021] and is embodied in the GitHub repository accompanying this paper.
+The computational model was written in the *R* [@rcoreteamLanguageEnvironmentStatistical2021] and is embodied in the GitHub repository accompanying this paper.
 The simulation was conducted for varying combinations of switching probabilities and thresholds.

### 2022-04-09 manuscript.Rmd
Preliminary Draft

@@
 authornote: |
- This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the GitHub repository: https://github.com/linushof/sampling-in-dfe.
+ This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub` repository: https://github.com/linushof/sampling-in-dfe.
 The current version of the manuscript, created from the commit with the hash `r repro::current_hash()`, is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
@@
                           "$\\leq 1$, decreases with increasing $\\psi$"))
-apa_table(predictions, caption = "(ref:predictions)", note = "The predictions for changes in $\\psi$ should become more robust for increasing values of $\\theta$ as choices become more systematic for high thresholds.", escape = FALSE)
+apa_table(predictions, caption = "(ref:predictions)", note = "The predictions should become more robust for high values of $\\theta$.", escape = FALSE)
 ```
@@
 In turn, for low values of $\psi$---and therefore pairs of long stochastic processes---the means should closely correspond to the EVs, leading to choices that are in line with EV maximization.
-To summarize the choice predictions for $\psi$ and simplify: 
-If the prospect that is more likely to return a higher outcome most of the time does not also possess the higher EV, high values of $\psi$ are predicted to cause an as-if underweighting of rare outcomes.
-Respectively, while these predictions emphasize the close link between small samples and the underweighting of rare outcomes, they suggest that the reliance on small samples can serve the accumulation of evidence for differences in a latent property.
 
-More so, for an increasing sequence of independent comparisons between single outcomes sampled from two prospects, the relative winning frequency of a prospect should converge against the objective probability of producing a higher outcome in each comparison.
-Accordingly, the as-if underweighting of rare outcomes should become more robust as the thresholds $\theta$ increase.
+To summarize the choice predictions and simplify: 
+If the prospect that is more likely to return a higher outcome most of the time does not also possess the higher EV, high values of $\psi$---and therefore pairs of short stochastic processes---are predicted to cause an as-if underweighting of rare outcomes.
+While these predictions emphasize the close link between small samples and the as-if underweighting of rare outcomes, they suggest that the reliance on multiple or many small samples can serve the accumulation of evidence for differences in a latent property.
+Specifically, for an increasing sequence of independent comparisons between single outcomes sampled from two prospects, the relative winning frequency of a prospect should converge against the objective probability of producing a higher outcome in each comparison.
+Respectively, then, the as-if underweighting of rare outcomes should become more robust as the thresholds $\theta$ increase.^[This clarifies the role of $\theta$: Whatever systematic differences between the prospects is reflected in a mean comparison should be more accurately assessed for high values of $\theta$.]
 
@@
 Specifically, because of the S-shaped curvature, the differences between the images $w(p)$ may be smaller than those between the respective cumulative probabilities in the lower and upper part of the cumulative probability scale, but may be considerably greater in the middle part.
-As a consequence, the cumulative decisions weights are smaller than the respective objective probabilities for small-probability outcomes of low and high rank, but they are larger for small-probability outcomes of a middle rank.^[<!--Open footnote-->Note that the distinction between outcomes of either low/high rank or middle rank is unnecessary for at most two-outcome prospects [see @tverskyAdvancesProspectTheory1992].
+As a consequence, the cumulative decisions weights are smaller than the respective objective probabilities for small-probability outcomes of low and high rank, but they are larger for small-probability outcomes of a middle rank.^[<!--Open footnote-->Note that the distinction between outcomes of either low/high rank or middle rank is unnecessary for at most two-outcome prospects [see @tverskyAdvancesProspectTheory1992, see also below].
 However, for finite many outcomes, the distinction is critical.
@@
 To simplify matters, the further discussion and the computational analysis are constrained to choices between a safe prospect---possessing just one outcome that occurs with certainty---and a two-outcome prospect (hereafter: risky prospect).
-All outcomes are assumed to be positive and the safe outcome is assumed to fall between the the low-rank outcome, $x_{low}$, and the high-rank outcome, $x_{high}$, of the risky prospect to omit dominant prospects.
+All outcomes are assumed to be positive and the safe outcome is assumed to fall between the the low-rank outcome, $x_{low}$, and the high-rank outcome, $x_{high}$, of the risky prospect to omit dominance.
+A summary of the predictions for the CPT parameters can be found in Table\ \@ref(tab:predictions).
 
@@
 $$
-that the possible weighting patterns amount to an over- and underweighting of the high-rank outcome of the risky prospect.
-That is, the images of the weighting function equal the decision weights assigned to the high-rank outcome of the risky prospect.
+that the possible weighting patterns amount to an over- and underweighting of the high-rank outcome of the risky prospect, depending on its probability.
+That is, the weighting function is supplied with the probability of the high-rank outcome of the risky prospect and its images are the decision weights assigned to this outcome.
+Respectively, as can be seen from Figure\ \@ref(fig:weighting-function), for $\gamma > 1$, the high-rank outcome of the risky prospect is overweighted (underweighted) in CPT, if it is of large (small) probability, and $\delta \neq 1$ shifts the range of the over- and underweighting.
 
-Now, since for low switching probabilities the model tends to choose the prospect possessing the larger EV, the parameters of the value and weighting function are predicted to correspond to a linear weighting of outcomes and probabilities.
-Thus, the lower the switching probabilities, the more should the choices translate to parameter estimates that satisfy $\alpha = 1$, $\gamma = 1$, and $\delta = 1$.
-However, for high switching probabilities, the model predicts systematic deviations from the solutions of EV maximization, which take the form of an as-if underweighting of rare outcomes:
-More specifically, for $\psi = 1$, the model tends to choose the risky prospect, if the probability of its high-rank outcome satisfies $p_x(x_{high}) > .5$, irrespective of its EV.
-Vice versa, the model tends to choose the safe outcome, if $p_x(x_{high}) < .5$ is satisfied.
-Accordingly, for high switching probabilities, the weighting pattern should be such that the high-rank outcome is overweighted for $p_x(x_{high}) > .5$ and otherwise underweighted.
+Now, since for low values of $\psi$ the model tends to choose the prospect possessing the larger EV, the parameters of the value and weighting function in this case are predicted to correspond to a linear weighting of outcomes and probabilities, which is given for $\alpha = 1$, $\gamma = 1$, and $\delta = 1$.
+However, for high values of $\psi$, the model tends to choose the risky prospect for $p_x(x_{high}) > .5$---i.e., the risky prospect produces the higher outcome most of the time---, irrespective of the differences in the EV.
+Vice versa, the model tends to choose the safe outcome for $p_x(x_{high}) < .5$---i.e., the safe prospect produces the higher outcome most of the time.
+Respectively, for high values of $\psi$, the weighting pattern should be such that the high-rank outcome of the risky prospect is overweighted for $p_x(x_{high}) > .5$, and underweighted otherwise.
+Hence, the graph of the weighting function should take a S-shape, which is given for $\gamma > 1$.
+Because the over- and underweighting of the high-rank outcome is not predicted to extend across the mid-point of the probability scale, $\delta$ should take values around 1.
+Note that the graph of the weighting function for high values of $\psi$ reflects the round-wise strategy's high sensitivity to differences in the probability to produce the higher outcome most of the time:
+Specifically, the slope of the weighting function's graph is most severe around the midpoint of the probability scale.
+The predicted flat ends of the graph, however, indicate that the round-wise strategy more or less ignores how much larger the probability to produce a higher outcome is. 
+In sum, then, we do not predict $\delta$ to change with $\psi$.
+However, we expect $\gamma$ to increase with $\psi$, thereby reflecting differences in the extent to which the prospect with the higher EV or with the probability to produce a higher outcome most of the time is chosen.
 
-Hence, for high switching probabilities, the graph of the weighting function is predicted to run below the identity line for $p_x(x_{high}) < .5$---leading to an underweighting of small-probability outcomes---and above the identity line for $p_x(x_{high}) > .5$---leading to an overweighting of high-probability outcomes.
-Accordingly, the graph of the weighting function should take a S-shape, which is given by $\gamma > 1$ and $\delta = 1$.
-Yet, since the model tends to approximate the solutions of EV maximization the lower the switching probabilities are, the S-shape should be most pronounced for high switching probabilities.
-Thus, $\gamma$ should increase with $\psi$.
-Note further that the predicted shape of the weighting function for high switching probabilities reflects the round-wise strategy's high sensitivity to differences in the probability to produce the higher outcome most of the time.
-That is, the slope of the weighting function increases around the midpoint of the probability scale.
-The predicted flat ends of the graph, however, indicate that the round-wise strategy more or less ignores how much larger the probability to produce a higher outcome is.
-
-Moreover, an increase in the switching probability should lead to a more concave value function, since all mean comparisons are ordinal and weighted equally in their contribution to the accumulated evidence.
-Specifically, the model is such that the magnitudes of outcomes are ignored once a comparison is carried out.
-Hence, for high switching probabilities, the choices depend on which prospect produces the higher outcome most of the time, irrespective of how much larger the outcomes are.
-Therefore, $\alpha$ is predicted to decrease as $\psi$.
-Finally, all predictions concerning the parameters of CPT's value and weighting function should become more robust with increases in $\theta$ as increasing thresholds lead to more systematic choices.
+Moreover, because the model is such that the magnitudes of outcomes are ignored once a comparison is carried out, increases in $\psi$ should lead to a more concave value function.
+That is, the higher the values of $\psi$, the more the choices depend on which prospect produces the higher outcome most of the time, irrespective of how much larger the outcomes are.
+Respectively, $\alpha$ is predicted to decrease with increases in $\psi$.
 
@@
 To substantiate and refine the predictions of the model, a computational implementation was used to simulate the sampling and accumulation process for a set of choices between a safe prospect and a two-outcome (risky) prospect.
-The computational model was written in the *R* [@rcoreteamLanguageEnvironmentStatistical2021] and is embodied in the GitHub repository accompanying this paper.
-The simulation was conducted for varying combinations of switching probabilities and thresholds.
-For each of these combinations, the simulated data was modeled with CPT's value and weighting function, using a Bayesian parameter estimation.
-The simulated choices and estimated CPT parameters can be understood as theory-implied data and data models which remain to be tested against empirical data [see @guestHowComputationalModeling2021; @haslbeckModelingPsychopathologyData2021].
+The computational model was written in `R` and is embodied in the `GitHub` repository accompanying this paper.
+The simulation was conducted for varying combinations of $\psi$ and $\theta$.
+For each of these combinations, the simulated data was modeled with a stochastic version of CPT, using Bayesian parameter estimation.
+The simulated choices and estimated CPT parameters can be roughly understood as theory-implied data and data models, which remain to be tested against empirical data [see, e.g., @guestHowComputationalModeling2021; @haslbeckModelingPsychopathologyData2021].
 
@@
 
-Below, the data generation and data modeling procedure is briefly reviewed.
+Below, the simulation and modeling procedure is briefly described.
 
@@
 A test set of $60$ choice problems was obtained by stratified sampling from an initial set of $10,000$ problems.
-The stratification procedure was used to ensure that the test set contained choice problems with small-probability outcomes of different rank---i.e., small-probability outcomes that are either higher or lower than the EV of the two-outcome prospect---as well as choice problems without small-probability outcomes.
+The stratification procedure was used to ensure that the test set contained choice problems with small-probability outcomes of different rank---i.e., small-probability outcomes that are either higher or lower than the EV of the risky prospect---as well as choice problems without small-probability outcomes.
 The exact procedure was as follows:
-For each of the $10.000$ problems in the initial set, three outcomes were randomly drawn from a uniform distribution over the interval $[0, 20]$, with the smallest and highest of these three outcomes being assigned to the risky prospect to omit dominant prospects.
+For each of the $10.000$ problems in the initial set, three outcomes were randomly drawn from a uniform distribution over the interval $[0, 20]$, with the smallest and highest of these three outcomes being assigned to the risky prospect to omit dominance.^[I.e., when one prospect always produces a higher outcome.]
 The probability for the lower outcome of the risky prospect, $p_x(x_{low})$, was drawn from a uniform distribution over the interval $(0, 1)$, with the probability of the higher outcome being set to $p_x(x_{high}) = 1-p_x(x_{low})$.
@@
 
-* *Switching probability* $\psi$ : 
-The switching probability was varied in the interval $[.1, 1]$ in increments of $.1$.
+* *Switching probability*: 
+$\psi$ was varied in the interval $[.1, 1]$ in increments of $.1$.
 
-* *Threshold* $\theta$: 
-The threshold was varied in the interval $[1,5]$ in increments of 1.
+* *Threshold*: 
+$\theta$ was varied in the interval $[1,5]$ in increments of 1.
 
-* *Decision variable*: The decision variable of a prospect either counts the number of won comparisons---implying an absolute threshold---or how much more comparisons were won relative to the other prospect---implying a relative threshold.
+* *Decision variable*: The decision variable of a prospect either counts the number of won comparisons---implying an absolute threshold---or how many more comparisons were won relative to the other prospect---implying a relative threshold.^[The results are similar for absolute and relative thresholds.
+For simplification, only the results of the absolute thresholds are reported in the main text.]
 
 \noindent
-Since the switching probability introduces some stochasticity into the information-processing chain, each of the 100 resulting parameter combinations was used 100 times---resembling 100 agents---to solve the test set.
+Since $\psi$ introduces some stochasticity into the sampling and accumulation process, each of the 100 resulting parameter combinations was used 100 times---resembling 100 independent agents---to solve the test set.
 In sum, then 100 (parameter combinations) $\times$ 100 (agents) $\times$ 60 (choice problems)  = 600,000 sampling and accumulation processes were simulated.
-The respective dataset can be retrieved from the accompanying GitHub repository.
+The respective dataset can be retrieved from the accompanying `GitHub` repository.
 
-### Bayesian CPT Analysis of Choice Data
+### Estimation of Stochastic CPT
 
-The choice data generated for each parameter combination was separately modeled in CPT, using Tversky and Kahneman's (1992) value function and Goldstein and Einhorn's (1987) weighting function.
-To demonstrate that the distortions from linear probability weighting are not just due to the difference between the latent objective probabilities and the relative number of times the outcomes are sampled over the course of any accumulation process, the sampled relative frequencies are supplied as probability information to the weighting function.
-To accommodate for possible random choice behavior that may be exerted by some parameter combinations of the data-generating accumulation model, the CPT model was amended with the logit choice rule
+The choice data for each parameter combination was separately modeled in CPT, using the value function of @tverskyAdvancesProspectTheory1992 and the weighting function of @goldsteinExpressionTheoryPreference1987.
+To demonstrate that the distortions from linear probability weighting are not just due to differences between the latent objective probabilities and the relative frequencies with which the outcomes were actually sampled over the course of a sampling and accumulation process, the latter were supplied as probability information to the weighting function.
+To accommodate for possible random choice behavior that may be exerted by a parameter combination, the CPT model was amended with the logit choice rule
 $$
@@
 where $p(P'^{safe})$ is the probability that the safe prospect is chosen over the risky prospect, $V_{safe}$ and $V_{risky}$ are the valuations of the safe and risky prospect that result from the parameter estimates of the value and weighting function, and $\rho \geq 0$ is a sensitivity parameter.
-The sensitivity parameter governs how strongly the choice between prospects depends on the differences in the valuations of the prospects---i.e., the core CPT model.
-Specifically, $\rho = 0$ implies no sensibility and therefore random choices.
+$\rho$ governs how strongly the choice between prospects depends on the differences in the valuations of the prospects, i.e., the core CPT model.
+Specifically, $\rho = 0$ implies no sensitivity, and thus a random choice.
 In turn, for increasing values of $\rho$, the probability of choosing the prospect with the higher valuation increases.
-Note further that the valuation of the prospects were rescaled by $\frac{1}{\alpha}$, as proposed by @stewartPsychologicalParametersHave2018, to guard against possible parameter interdependencies between $\alpha$ and $\rho$ [see @krefeld-schwalbStructuralParameterInterdependencies2021; @scheibehenneUsingBayesianHierarchical2015].
-In sum, then, the model has four free parameters $\alpha, \gamma, \delta, \rho$.
+Note further that the valuation of the prospects were rescaled by $\frac{1}{\alpha}$, as proposed by @stewartPsychologicalParametersHave2018, to guard against possible parameter interdependencies between $\alpha$ and $\rho$ [@krefeld-schwalbStructuralParameterInterdependencies2021; @scheibehenneUsingBayesianHierarchical2015].
+In sum, then, the model has four free parameters: $\alpha, \gamma, \delta, \rho$.
 
-Since for a given choice problem and parameter combination of the accumulation model there should be no systematic differences among the 100 iterations (agents), their data is combined and free parameters are estimated across them.
-Such a grouped approach is expected to reveal the main effects of a given parameter combination of the accumulation model on the choice patterns and ignores unsystematic differences or noise that may be caused by the switching probability [see @nilssonHierarchicalBayesianParameter2011].
-To facilitate comparisons across parameter combinations of the accumulation model, uninformative prior distributions were used throughout for all four parameters of the data model.
-Specifically, the prior distribution $\alpha \sim U(0,1)$, $\gamma \sim U(0,2)$, $\delta \sim U(0,10)$, and $\rho \sim U(0,5)$ were used.
+Since for a given choice problem and parameter combination of the sampling and accumulation model there should be no systematic differences among the 100 iterations (synthetic agents), their data is combined for the estimation of the free parameters.
+Such a grouped approach should reveal the main effects of a given parameter combination of the sampling and accumulation model on the resulting choices and ignore unsystematic differences or noise that may be caused by the stochasticity introduced by $\psi$.
+To facilitate comparisons across parameter combinations of the sampling and accumulation model, uninformative prior distributions were used throughout for all four parameters.
+Specifically, the prior distributions $\alpha \sim U(0,1)$, $\gamma \sim U(0,2)$, $\delta \sim U(0,10)$, and $\rho \sim U(0,5)$ were used.
 
@@
 
-To estimate the posterior distributions of the parameters, Markov Chain Monte Carlo sampling was used, where 20 chains of 40,000 samples each were run after a warm-up period of 1000 samples.
+To estimate the posterior distributions of the free parameters, Markov Chain Monte Carlo sampling as implemented in `JAGS` was used, where 20 chains of 40,000 samples each were run after a warm-up period of 1000 samples.
 To reduce potential autocorrelation during the sampling process, only every 20th sample was kept (thinning), leaving a total of 40,000 samples across chains.
 The minimum effective sample size was `r min(cpt$n.eff)`.
-The potential scale reduction factor $\hat{R}$ [see @gelmanInferenceIterativeSimulation1992] was $\leq$ `r round(max(cpt$Rhat), 4)` for all parameters, indicating good convergence.
+The potential scale reduction factor $\hat{R}$ [@gelmanInferenceIterativeSimulation1992] was $\leq$ `r round(max(cpt$Rhat), 4)` for all models and parameters, indicating good convergence.
 
@@
 
-We start by inspecting how the number of outcomes sampled over the course of a sampling and accumulation process changes with varying combinations of switching probabilities and thresholds.
-Figure\ \@ref(fig:chain-length) shows the respective median for each parameter combination.
-Since the two stochastic processes underlying a mean comparison tend to terminate faster the higher the switching probabilities are, the model predicts the overall number of sampled outcomes to decrease with increasing switching probabilities.
-As can be seen from the changing slopes of the lines in Figure\ \@ref(fig:chain-length), the decrease in the number of sampled outcomes diminishes as the relative increase in the switching probability diminishes.
-Moreover, the overall number of sampled outcomes increases with thresholds at a relatively constant rate, reflecting the latters impact on the number of required mean comparisons.
-Finally, consider the dashed horizontal line which displays the median number of 14 outcomes that @wulffMetaanalyticReviewTwo2018 found to be sampled in 10,712 trials involving a choice between a safe and a two-outcome prospect in the sampling paradigm.
-Notably, the parameter combinations that closely resemble the round-wise strategy---i.e., high switching probabilities and thresholds---or the summary strategy---i.e., low switching probabilities and thresholds---lead to overall numbers of sampled outcomes that come fairly close to this meta-analytic median.
-In turn, hybrids of both strategies produce overall numbers of sampled outcomes that are considerably lower or higher.
+Overall, the results of the simulation match the predictions from Table\ \@ref(tab:predictions), however, with some exceptions concerning the estimates for the parameter $\delta$ of the weighting function.
+We start by inspecting how the length of the information-processing chain changes with varying combinations of $\psi$ and $\theta$.
+
+### Simulated Length of the Information-Processing Chains
+
+Figure\ \@ref(fig:chain-length) displays the median number of outcomes sampled over the course of a sampling and accumulation process for each parameter combination.
+The model predicts a decrease in the overall number of sampled outcomes with increases in the switching probability $\psi$.
+As can be seen from the change in the slopes of the lines in Figure\ \@ref(fig:chain-length), the magnitude of this decrease diminishes as the relative increase in $\psi$ diminishes.^[<!--Open footnote-->I.e., the ratio of high values of $\psi$ is smaller than the ratio of small values of $\psi$.<!--Close footnote-->]
+Moreover, the overall number of sampled outcomes increases with thresholds at a relatively constant rate.
+Consider also the dashed horizontal line in Figure\ \@ref(fig:chain-length), which displays the median number of 14 outcomes that @wulffMetaanalyticReviewTwo2018 found to be sampled in 10,712 trials involving a choice between a safe and a two-outcome prospect in the sampling paradigm.
+Notably, the parameter combinations that closely resemble the round-wise strategy---i.e., high values of $\psi$ and $\theta$---or the summary strategy---i.e., low values of $\psi$ and $\theta$---lead to overall numbers of sampled outcomes that come close to the meta-analytic median.
+Moreover, while parameter combinations that can be understood as falling in between the round-wise and the summary strategy also lead to overall numbers of sampled outcomes that approximate the meta-analytic median, extreme combinations produce numbers that are considerably lower or higher, and thus less plausible from an empirical stance.
 
@@
 
-### Final Choice
+### Simulated Final Choice
 
-Figure\ \@ref(fig:choice-rates) displays the rates of choices that did not maximize the latent EV (hereafter: false response rates) for each combination of switching probabilities and thresholds.
-Moreover, the rates are separated by the presence and rank of a small-probability outcome.
-Consider first the top panel which shows the false response rates across all problems where the low-rank outcome of the risky prospect has a small probability:
-Over the course of short stochastic processes, then, the low-rank outcomes tend to be sampled less often than would be objectively warranted, leading to an inflation of the respective means of the risky prospect.
-Accordingly, the top panels show that the rates of false choices of the risky prospect increase with the switching probability, but the rates of false safe choices remain generally low.
-More specifically, the higher the switching probabilities, the more severe should the inflation of the means---and the overestimation of the EVs---of the risky prospects be. 
-As a consequence, if the risky prospects possesses the smaller EV, an increase in the switching probability increases the risk to deviate from EV maximization by falsely choosing the risky prospects on the basis of mean comparisons.
-Importantly, these deviations take the form of an as-if underweighting of rare outcomes.
-In turn, if the risky prospects possess the larger EV, the inflation of their means decreases the risk to falsely choose the safe prospect.
-Note from the middle panel that the pattern of false response rates reverses across all problems where the high-rank outcome of the risky prospect has a small probability.
-In this case, then, the means of the risky prospects tend to be more deflated, the higher the switching probability is, which, however, again results in an as-if underweighting of rare outcomes.
-Furthermore, the differences between the switching probabilities concerning the false response rates tend to be more pronounced for high thresholds, showing that over the course of multiple mean comparisons the inflation and deflation of the means of the risky prospect is more robust.
+Figure\ \@ref(fig:choice-rates) displays the rates of choices that did not maximize the latent EV (hereafter: false response rates) for each combination of $\psi$ and $\theta$.
+To demonstrate that the deviations from EV maximization are not just due to sampling error, the rates of choices that did not maximize the sampled mean are displayed in gray. 
+Rates are separated for presence and rank of small-probability outcomes.
+Consider first the top panel showing the false response rates across all problems where the low-rank outcome of the risky prospect possesses a small probability:
+Over the course of short stochastic processes, then, the low-rank outcome tends to be sampled less often than would be objectively warranted, leading to an inflation of the respective mean of the risky prospect.
+Accordingly, the top panels show that the rates of false choices of the risky prospect increase with $\psi$, but the rates of false safe choices remain generally low.
+More specifically, the higher the values of $\psi$, the more severe should the inflation of the mean of the risky prospect be. 
+As a consequence, if the risky prospect possesses the smaller EV, an increase in $\psi$ increases the risk to deviate from EV maximization---taking the form of an as-if underweighting of rare outcomes---by falsely choosing the risky prospect on the basis of a mean comparison.
+In turn, if the risky prospect possesses the larger EV, the inflation of their means decreases the risk to falsely choose the safe prospect.
+Note from the middle panel that the pattern of false response rates reverses for problems where the high-rank outcome of the risky prospect possesses a small probability.
+In this case, then, the mean of the risky prospect tends to be more deflated the higher the value of $\psi$, which increases the risk of falsely choosing the safe prospect.
+From the reduced false response rates in the bottom panel, we see that the inflation and deflation of the means for high values of $\psi$ is significantly attenuated when a prospect possesses no small-probability outcome.
 
@@
 
-##determine normative choice according to latent and sampled EV
+## determine normative choice according to latent and sampled EV
 fr_rates <- choices %>%
@@
 
+###
+fr_rates_m <- choices %>%
+  mutate(norm = case_when(a_ev_exp/b_ev_exp > 1 ~ "A", a_ev_exp/b_ev_exp < 1 ~ "B")) %>% # determine normative choice
+  filter(!is.na(norm)) %>% #exclude trials with equal EV
+  group_by(s, boundary, a, rare, norm, choice) %>% #separate by model parameter and type of rare event
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), #compute response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", #determine false response type
+                          norm == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>% #remove correct responses
+  select(-c(norm, choice, n)) %>% 
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]", #change facet labels for rare events
+                          rare == "attractive" ~ "\\in (0,.2)",
+                          rare == "unattractive" ~ "\\in (.8,1)"))
+
+###
+
 #plot
@@
   scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  geom_line(data = fr_rates_m, aes(group = type), color = "gray") + 
+  geom_point(data = fr_rates_m, aes(shape = type), color = "gray", size = 2) +
   geom_line(aes(color = s, group = type)) + 
@@
 
-### Cumulative Prospect Theory
+### Simulation-Implied Cumulative Prospect Theory
 
-Figure\ \@ref(fig:weighting-parameters) shows the means and the 95%-intervals of the posterior distributions of the curvature parameter $\gamma$ and elevation parameter $\delta$ as well as the resulting graphical shape of the weighting function.
-The findings are fairly consinstent with the predictions.
-Note first that the estimates for the parameter combination $\theta = 1$ and $\psi = 1$ have large posterior intervals.
-In these cases, no other relative frequencies than 0 and 1 are supplied to the weighting function, which may explain why the values in between cannot reliably be accounted for.
-However, for $\theta = 1$ and $\psi < 1$, the parameter estimates indicate a linear weighting pattern, demonstrating the well-established explanation that if the prospect with the higher mean across all sampled outcomes is chosen, sampling error can account for any deviations from EV maximization.
+Figure\ \@ref(fig:weighting-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the curvature parameter $\gamma$ and the elevation parameter $\delta$, as well as the resulting graphical shape of the weighting function.
+Note that the estimates for the parameter combination $\theta = 1$ and $\psi = 1$ have large posterior intervals.
+In these cases, no relative frequencies other than 0 and 1 are supplied to the weighting function, which may explain that the values in between cannot be reliably accounted for.
+However, for $\theta = 1$ and $\psi < 1$, the estimates imply a linear weighting pattern, in line with the explanation that if the mind were to infer the latent objective probabilities of outcomes from the sampled relative frequencies and to follow the principle of EV maximization, sampling error can account for any deviations from it.^[<!--Open footnote-->Note that the same line of reasoning holds, were the mind to approximate the solutions of EV maximization by choosing the prospect with higher sampled mean.<!--Close footnote-->]
+Note also Figure\ \@ref(fig:choice-rates), where there are no choices for $\theta = 1$ that do not maximize the sampled mean.
 
-For $\theta > 1$, the estimates substantiate the prediction that $\gamma$ takes values $\geq 1$ which increase with the switching probability, resulting in a increasingly pronounced S-shaped weighting function.
-In other words, the higher the switching probability, the more severe is the underweighting (overweighting) of high-rank outcomes of small (large) probability in CPT.
-Moreover, $\delta$ takes values $\geq 1$ and increases slightly with the switching probability, causing the high-rank outcome to be overweighted the most, if its probability is just above the mid-point.
+For $\theta > 1$, the estimates substantiate the prediction that $\gamma$ takes values $\geq 1$ which increase with $\psi$, resulting in a increasingly pronounced S-shaped weighting function.
+In other words, the higher the value of $\psi$, the more severe is the underweighting (overweighting) of the high-rank outcome of the risky prospect in CPT, if it is of small (large) probability.
+$\delta$ takes values $\geq 1$ and increases slightly with $\psi$, causing the overweighting of the high-rank outcome of the risky prospect to extend across the mid-point. [...]
 
@@
 
-Figure\ \@ref(fig:value-parameters) shows the means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$, as well as the shape of the value function.
-As predicted, an increase in the switching probability leads to a decrease in $\alpha$, reflecting that the outcome information is largely ignored if choices are based on ordinal comparisons of single outcomes rather than of means of large samples.
-Note further that the estimates are stable across thresholds.
-Finally, note that the choice sensitivity parameter varied systematically with the switching probability, such that the choices were more sensitive to the valuations in CPT for low values of $\psi$.
-However, even for high values of $\psi$, the choices did not appear to be random.
+Figure\ \@ref(fig:value-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$, as well as the shape of the value function.
+An increase in $\psi$ leads to a decrease in $\alpha$, reflecting that outcome information are largely ignored if choices are based on ordinal comparisons of single outcomes rather than on means of large samples.
+The respective shape of the value function is more concave, the higher the values of $\psi$. 
+Finally, $\rho$ varied systematically such that the choices were more sensitive to the valuations of the core CPT model for low values of $\psi$.
+However, even for high values of $\psi$, the choices did not appear to be random. [...]
 
@@
 
-In sum, then, the computational analysis substantiates the claim that sampling strategies can be used to alter which difference in the latent properties of prospects evidence is accumulated for and that the choices vary respectively.
-Moreover, it has been demonstrated how these differences in the choice patterns translate to characteristic shapes in CPT's weighting and value function.
+# Discussion
 
-# Discussion
+[...]
 

### 2022-04-21 code/prepare_choices.R
Rename folder

@@ -19,6 +19,7 @@ if(hash_sim != "295e1a7b23402dd50a1dae5a54141f78"){
 
   cat(green("Data is valid. Continuing preparation of choice data."))
 
+
   ## transform data to obtain trial summaries
 
   choices <- simulation %>%

### 2022-04-21 code/simulate_dfe.R
Tidy rep: Rename data file

@@ -2,7 +2,7 @@ pacman::p_load(tidyverse)
 source("R/fun_cumulative_stats.R") # call functions for computing cumulative stats
 
 # test set
-gambles <- read_csv("data/gambles/sr_subset.csv")
+gambles <- read_csv("data/choice_problems.csv")
 n_agents <- 100
 
 # simulation parameters
@@ -136,4 +136,4 @@ for (set in seq_len(nrow(theta))) {  # loop over parameter combinations
   param_list[[set]] <- expand_grid(theta[set, ], all_gambles)
 }
 simulation <- param_list %>% map_dfr(as.list)
-write_csv(simulation, "data/simulation/simulation.csv")
+write_csv(simulation, "data/simulation.csv")

### 2022-04-21 code/simulate_gambles.R

@@ -1,25 +1,24 @@
 pacman::p_load(tidyverse)
-source("R/fun_generate_gambles.R") # call function for generating 2-outcome gambles
+source("code/fun_generate_gambles.R") # call function for generating 2-outcome gambles
 
 # generate 10,000 safe-risky gambles
 
 set.seed(349)
-sr_gambles <- generate_gambles(n = 10000, safe = TRUE, lower = 0, upper = 20)
-sr_gambles <- sr_gambles %>% mutate(rare = case_when(a_p1 >= .2 & a_p1 <= .8 ~ "none",
+initial_set <- generate_gambles(n = 10000, safe = TRUE, lower = 0, upper = 20)
+initial_set <- initial_set %>% mutate(rare = case_when(a_p1 >= .2 & a_p1 <= .8 ~ "none",
                                                      a_p1 < .2 ~ "unattractive", # a_o1 is the smaller outcome
                                                      a_p1 > .8 ~ "attractive"))
-write_csv(sr_gambles, "data/gambles/sr_gambles.csv")
-
 
 # select subset of 60 gambles
 # stratified sampling of 20 gambles with no/attractive/unattractive rare event
 
-sr_subset <- tibble()
+test_set <- tibble()
 
 set.seed(735)
-for(i in unique(sr_gambles$rare)) {
-  type <- sr_gambles %>% filter(rare == i) # type of rare event
+for(i in unique(initial_set$rare)) {
+  type <- initial_set %>% filter(rare == i) # type of rare event
   smpl <- sample(seq_len(nrow(type)), size = 20) # random sample of 20 rows/gambles
-  sr_subset <- bind_rows(sr_subset, type[smpl, ])
+  test_set <- bind_rows(test_set, type[smpl, ])
 }
-write_csv(sr_subset, "data/gambles/sr_subset.csv")
+
+write_csv(test_set, "data/choice_problems.csv")

### 2022-04-21 code/estimate_cpt.R
Tidy rep: rename data files

@@ -1,5 +1,5 @@
 pacman::p_load(tidyverse, R2jags)
-source("R/fun_inits_MCMC.R") # call function creating initial values for MCMC
+source("code/fun_inits_MCMC.R") # call function creating initial values for MCMC
 
 # read choice data
 cols <- list(.default = col_double(),
@@ -8,7 +8,7 @@ cols <- list(.default = col_double(),
              rare = col_factor(),
              agent = col_factor(),
              choice = col_factor())
-choices <- read_csv("data/choices/choices.csv", col_types = cols)
+choices <- read_csv("data/choices.csv", col_types = cols)
 
 # prepare data for JAGS
 
@@ -72,4 +72,4 @@ for(set in seq_len(nrow(params_sim))){
 # save data
 
 estimates_cpt <- estimates_cpt %>% map_dfr(as.list)
-write_csv(estimates_cpt, "data/estimates/estimates_cpt.csv")
+write_csv(estimates_cpt, "data/cpt_paramters.csv")

### 2022-04-21 code/prepare_choices.R

@@ -8,7 +8,7 @@ cols <- list(.default = col_double(),
              rare = col_factor(),
              attended = col_factor(),
              choice = col_factor())
-simulation <- read_csv("data/simulation/simulation.csv", col_types = cols)
+simulation <- read_csv("data/simulation.csv", col_types = cols)
 
 # use hash to validate simulation data
 
@@ -40,7 +40,7 @@ if(hash_sim != "295e1a7b23402dd50a1dae5a54141f78"){
 
   # save data
   ## required: 60 gambles x 100 subjects x 100 parameter combinations = 600.000 choices
-  write_csv(choices, "data/choices/choices.csv")
+  write_csv(choices, "data/choices.csv")
 
 }
 

### 2022-04-21 code/estimate_cpt.R
rename files

@@ -1,5 +1,5 @@
 pacman::p_load(tidyverse, R2jags)
-source("code/fun_inits_MCMC.R") # call function creating initial values for MCMC
+source("code/fun_initialize_MCMC.R") # call function creating initial values for MCMC
 
 # read choice data
 cols <- list(.default = col_double(),
@@ -8,7 +8,7 @@ cols <- list(.default = col_double(),
              rare = col_factor(),
              agent = col_factor(),
              choice = col_factor())
-choices <- read_csv("data/choices.csv", col_types = cols)
+choices <- read_csv("data/simulation_summary.csv", col_types = cols)
 
 # prepare data for JAGS
 
@@ -54,7 +54,7 @@ for(set in seq_len(nrow(params_sim))){
   current_sample <- jags.parallel(data = current_trials,
                                   inits = inits_MCMC,
                                   parameters.to.save = params_cpt,
-                                  model.file = "JAGS/cpt_model.txt",
+                                  model.file = "code/cpt_JAGS_model.txt",
                                   n.chains = n_chains,
                                   n.iter = 41000,
                                   n.burnin = 1000,
@@ -72,4 +72,4 @@ for(set in seq_len(nrow(params_sim))){
 # save data
 
 estimates_cpt <- estimates_cpt %>% map_dfr(as.list)
-write_csv(estimates_cpt, "data/cpt_paramters.csv")
+write_csv(estimates_cpt, "data/cpt_parameters.csv")

### 2022-04-21 code/generate_choice_problems.R

@@ -1,5 +1,5 @@
 pacman::p_load(tidyverse)
-source("code/fun_generate_gambles.R") # call function for generating 2-outcome gambles
+source("code/fun_generate_choice_problems.R") # call function for generating 2-outcome gambles
 
 # generate 10,000 safe-risky gambles
 

### 2022-04-21 code/model_implementation_and_simulation.R

@@ -1,5 +1,5 @@
 pacman::p_load(tidyverse)
-source("R/fun_cumulative_stats.R") # call functions for computing cumulative stats
+source("R/fun_compute_cumulative_stats.R") # call functions for computing cumulative stats
 
 # test set
 gambles <- read_csv("data/choice_problems.csv")

### 2022-04-21 code/summarize_simulation.R

@@ -40,7 +40,7 @@ if(hash_sim != "295e1a7b23402dd50a1dae5a54141f78"){
 
   # save data
   ## required: 60 gambles x 100 subjects x 100 parameter combinations = 600.000 choices
-  write_csv(choices, "data/choices.csv")
+  write_csv(choices, "data/simulation_summary.csv")
 
 }
 

### 2022-04-22 manuscript.Rmd
Minor reviews

@@
 
-shorttitle        : "Sampling strategies"
+shorttitle        : |
+  Sampling strategies
 
@@
 authornote: |
- This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub` repository: https://github.com/linushof/sampling-in-dfe.
+ This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the GitHub repository: https://github.com/linushof/sampling-in-dfe.
 The current version of the manuscript, created from the commit with the hash `r repro::current_hash()`, is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
@@
 
-abstract: "In decisions from experience, systematic choices between prospects are based on the assessment of differences in latent properties.
-Yet, several properties can be used to distinguish among the prospects.
-To this end, this paper presents a sampling and accumulation model that allows sampling  strategies—i.e., the probability of sampling outcomes from different prospects in direct succession (switching probability)—to alter which differences in the latent properties evidence is accumulated for.
-Specifically, the proposed model sequentially samples outcomes from two prospects and accumulates the results obtained from a sequence of ordinal comparisons between sample means, with switching probabilities determining the size of the samples underlying each comparison and thresholds determining how many comparisons a prospect must win in order to be chosen.
-A computational implementation of the model is used to simulate the respective information-processing chains upfront choices between a safe and a two-outcome prospect, while varying switching probabilities and thresholds.
-The analysis of the simulation data shows that, depending on whether the accumulation process unfolds over mean comparisons based on small or large samples, evidence is accumulated for differences either in the probability to produce a higher outcome most of the time or in the expected value.
-The respective choice patterns reflect an as-if underweighting of rare outcomes or expected value maximization, both of which become more robust with increasing thresholds.
-The analysis moreover shows how the distinct choice patterns resulting from differences in the information-processing chains translate to the parameters of cumulative prospect theory’s value and weighting function."
+abstract: |
+  In decisions from experience, the probability to produce a higher outcome most of the time and the expected value are two latent properties that can be used to distinguish among the prospects of choice.
+This paper sketches a sampling and accumulation model that allows sampling strategies—i.e., the probability of sampling outcomes from different prospects in direct succession (switching probability)—to alter the degree to which evidence is accumulated for either one of these properties.
+A computational implementation of the model is used to simulate the respective sampling and accumulation process upfront choices between a safe and a two-outcome prospect, while varying switching probabilities and evidence thresholds.
+The simulation data shows that, depending on which latent property evidence is accumulated for and to which extent, respectively, choice patterns reflect various degrees of an as-if underweighting of rare outcomes or expected value maximization.
+Both choice patterns become more robust the more evidence is sampled and translate to characteristic parameter estimates for cumulative prospect theory’s value and weighting function.
 
@@
 
-bibliography      : references_sampling-in-dfe.bib
+bibliography      : references.bib
 csl               : apa.csl
@@
 header-includes:
-   - \usepackage[capposition=top]{floatrow}
+   - |
+    \usepackage[capposition=top]{floatrow}
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
 ---
@@
 
-<!-- Introduction -->
-
 The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the alternatives between which people can choose.
@@
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructbehaviorGapDescription2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
-choice patterns in DFD deviate from the solutions of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities;
-in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructbehaviorGapBehavioral2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
-Hereafter, these choice patterns are referred to as the *as-if overweighting* and *as-if underweighting of rare outcomes*, respectively.
+choice patterns in DFD deviate from the solutions of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities (*as-if overweighting of rare outcomes*);
+in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [*as-if underweighting of rare outcomes*, e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructbehaviorGapBehavioral2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
 
@@
 To substantiate the discussion, the model is used to simulate the sampling and accumulation process for choices between a safe and a two-outcome prospect, while systematically combining different switching probabilities and thresholds.
-Considering choice rates and parameter estimates of cumulative prospect theory [@tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993], the computational analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
+Considering choice rates and parameter estimates of cumulative prospect theory [@tverskyAdvancesProspectTheory1992], the computational analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
 Importantly, the analysis also shows that these distinct choice patterns become more robust with increasing thresholds.
@@
 Since there is an uncountable number of choices people confront in the natural world, behavioral decision research routinely abstracts from choices between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.^[<!--Open footnote-->See @knightRiskUncertaintyProfit1921, Chapter 1, for a timeless discussion on the reasonableness of such abstractions.<!--Close footnote-->]
+Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.^[<!--Open footnote-->See @knightRiskUncertaintyProfit1921, Chapter 1, for a discussion on the reasonableness of such abstractions.<!--Close footnote-->]
 These fundamental properties are considered the possible outcomes of a choice alternative and the probabilities with which these outcomes occur following the choice of the alternative.
@@
 
-Yet, there are several distinct properties that can be used to assess differences between the prospects, among them the EV, for which the summary decision strategy is indicative, and the probability to produce a higher outcome most of the time, for which the round-wise decision strategy is indicative [see @hillsInformationSearchDecisions2010].
+Yet, there are several distinct properties that can be used to assess differences between the prospects, among them the EV, for which the summary decision strategy is indicative, and the probability to produce a higher outcome most of the time, for which the round-wise decision strategy is indicative [@hillsInformationSearchDecisions2010; see also @wulffHowShortLongrun2015].
 Respectively, in the following, both decision strategies are implemented into a common sampling and accumulation model to demonstrate how the mind may rely on different sampling strategies to alter the degree to which evidence is accumulated for differences in either one of these properties.
@@
 To substantiate and refine the predictions of the model, a computational implementation was used to simulate the sampling and accumulation process for a set of choices between a safe prospect and a two-outcome (risky) prospect.
-The computational model was written in `R` and is embodied in the `GitHub` repository accompanying this paper.
+The computational model was written in R and is embodied in the GitHub repository accompanying this paper.
 The simulation was conducted for varying combinations of $\psi$ and $\theta$.
@@
 In turn, for increasing values of $\rho$, the probability of choosing the prospect with the higher valuation increases.
-Note further that the valuation of the prospects were rescaled by $\frac{1}{\alpha}$, as proposed by @stewartPsychologicalParametersHave2018, to guard against possible parameter interdependencies between $\alpha$ and $\rho$ [@krefeld-schwalbStructuralParameterInterdependencies2021; @scheibehenneUsingBayesianHierarchical2015].
+Note further that the valuation of the prospects were rescaled by $\frac{1}{\alpha}$, as proposed by @stewartPsychologicalParametersHave2018, to guard against possible parameter interdependencies between $\alpha$ and $\rho$ [@krefeld-schwalbStructuralParameterInterdependencies2022; @scheibehenneUsingBayesianHierarchical2015].
 In sum, then, the model has four free parameters: $\alpha, \gamma, \delta, \rho$.
@@
                      choice = col_factor())
-choices <- read_csv("data/choices/choices.csv", col_types = cols_choices)
+choices <- read_csv("data/simulation_summary.csv", col_types = cols_choices)
 choices <- choices %>% 
@@
                  parameter = col_factor())
-cpt <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols_cpt)
+cpt <- read_csv("data/cpt_parameters.csv", col_types = cols_cpt)
 cpt <- cpt %>% 
@@
 
-To estimate the posterior distributions of the free parameters, Markov Chain Monte Carlo sampling as implemented in `JAGS` was used, where 20 chains of 40,000 samples each were run after a warm-up period of 1000 samples.
+To estimate the posterior distributions of the free parameters, Markov Chain Monte Carlo sampling as implemented in JAGS was used, where 20 chains of 40,000 samples each were run after a warm-up period of 1000 samples.
 To reduce potential autocorrelation during the sampling process, only every 20th sample was kept (thinning), leaving a total of 40,000 samples across chains.

### 2022-04-22 manuscript.Rmd
minor reviews

@@
 
-shorttitle        : |
-  Sampling strategies
+shorttitle        : "Sampling strategies"
 
@@
 header-includes:
-   - |
-    \usepackage[capposition=top]{floatrow}
-    \makeatletter
-    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-1em}%
-      {\normalfont\normalsize\bfseries\typesectitle}}
-
-    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-\z@\relax}%
-      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-    \makeatother
+   - \usepackage[capposition=top]{floatrow}
 ---

### 2022-04-26 manuscript.Rmd
Update Discussion

@@
 title             : |
-  Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation
+  Sampling Strategies in Decisions from Experience
 
@@
 Importantly, the analysis also shows that these distinct choice patterns become more robust with increasing thresholds.
-Before presenting the model and the computational analysis, the following section provides a formal definition of prospects.
+Before presenting the model and the computational analysis, the following section provides a definition of prospects.
 
-# Formal Definition of Prospects
+# Definition of Prospects
 
@@
 
-### Formal Review of CPT
+### Desription of CPT
 
@@
 
-[...]
+The predictions of the choice patterns and CPT parameters alone do not render the model theoretically or empirically meaningful. 
+It is right that cognitive models are underdetermined by "locally obtained" data and that they should not aim to merely explain effects---e.g., the as-if underweighting of rare outcomes---but fundamental capacities such as learning, reasoning, and decision making [@vanrooijTheoryTestHow2021].
+In explaining these capacities, cognitive models must be constrained to the extent that neither the computational resources of the human mind nor other relevant resources---e.g., time---are limitless [see, e.g., @jareckiFrameworkBuildingCognitive2020; @liederResourcerationalAnalysisUnderstanding2020; @vanrooijTheoryTestHow2021].
+Acknowledging these limitations, different theoretical frameworks can be used to narrow down the still abundant number of possible mechanisms the mind might employ in the decision-making process.
+Such frameworks build on different, sometimes related or complementary assumptions, e.g.: *ecological rationality* holds that the mind uses simple (decision) heuristics that exploit the information structures of the environment in which it operates [see, e.g., @payneAdaptiveStrategySelection1988; see also @simonRationalChoiceStructure1956]; sequential sampling models assume that the mind trades of processing speed and accuracy while accumulating evidence for or against choice alternatives [see, e.g., @ratcliffComparisonSequentialSampling2004; @bogaczPhysicsOptimalDecision2006]; and *resource rationality* assumes that the mind employs mechanisms that make optimal use of its actual resources in obtaining a specific goal [see, e.g.; @liederResourcerationalAnalysisUnderstanding2020].
+
+Admittingly, although the current paper ought to sketch how the mind might exercise the capacity of making decisions from experience, it dealt with these constraints and frameworks rather implicitly and loosely.
+
+<!-- Marr: What is the goal and how can it be achieved -->
+
+<!-- Using CPT as effects -->
+
+# Conclusion
 

### 2022-04-26 manuscript.Rmd
Update discussion

@@
 Acknowledging these limitations, different theoretical frameworks can be used to narrow down the still abundant number of possible mechanisms the mind might employ in the decision-making process.
-Such frameworks build on different, sometimes related or complementary assumptions, e.g.: *ecological rationality* holds that the mind uses simple (decision) heuristics that exploit the information structures of the environment in which it operates [see, e.g., @payneAdaptiveStrategySelection1988; see also @simonRationalChoiceStructure1956]; sequential sampling models assume that the mind trades of processing speed and accuracy while accumulating evidence for or against choice alternatives [see, e.g., @ratcliffComparisonSequentialSampling2004; @bogaczPhysicsOptimalDecision2006]; and *resource rationality* assumes that the mind employs mechanisms that make optimal use of its actual resources in obtaining a specific goal [see, e.g.; @liederResourcerationalAnalysisUnderstanding2020].
+Such frameworks build on different, sometimes related or complementary assumptions, e.g.:
+*ecological rationality* holds that the mind uses simple (decision) heuristics that exploit the information structures of the environment in which it operates [see, e.g., @payneAdaptiveStrategySelection1988; see also @simonRationalChoiceStructure1956];
+sequential sampling models assume that the mind trades of processing speed and accuracy while accumulating evidence for or against choice alternatives [see, e.g.,  @bogaczPhysicsOptimalDecision2006; @ratcliffComparisonSequentialSampling2004];
+and *resource rationality* assumes that the mind employs mechanisms that make optimal use of its actual resources in obtaining a specific goal [see @liederResourcerationalAnalysisUnderstanding2020].
 
 Admittingly, although the current paper ought to sketch how the mind might exercise the capacity of making decisions from experience, it dealt with these constraints and frameworks rather implicitly and loosely.
-
-<!-- Marr: What is the goal and how can it be achieved -->
-
-<!-- Using CPT as effects -->
+The goal of this discussion therefore is to make some of the relations to the existing frameworks for the study of decision making more explicit. 
+Most importantly, this paper showed how the assumption that the sampling process is not random
 

### 2022-04-29 manuscript.Rmd
Update discussion

--- 2022-04-22 manuscript.Rmd
@@
 
-# Discussion
+# Summary and Discussion
 
-[...]
+The presented sampling and accumulation model ought to sketch how the mind might exercise the capacity of making decisions from experience.
+In DFE, one cannot rely on symbolic descriptions of all relevant properties of the choice alternatives, but only on samples of past experiences, e.g., when the alternatives were chosen in similar decisions in the past.
+To study DFE experimentally, one may use the sampling paradigm where people can sequentially sample the outcomes of prospects according to their probability of occurrence before making a final choice.
+To model the process by which people arrive at the final choice in this paradigm, one must explicate a number of assumptions, e.g.: How do people decide when to switch between prospects; how do they integrate the information obtained from the sampled outcomes; and, because they can sample as much as they want, how do they decide to stop sampling.
+To approach these questions, this paper presented a model that integrated a proposed link between sampling and decision strategies into the computational framework of sequential sampling models.
+
+## Modeling Sampling Strategies and the Decision-Making Process
+
+@hillsInformationSearchDecisions2010 proposed---and provided tentative empirical support for---a systematic relation between what they considered two paradigmatic sampling and decision strategies. 
+That is, the authors assumed that people either switch prospects after each sampled outcome (piecewise sampling) to compare single outcomes over repeated rounds (round-wise decision strategy), or they switch only once between prospects (comprehensive sampling) and make only one comparison between the means across all sampled outcomes (summary decision strategy).
+In sequential sampling models [see, e.g., @ratcliffComparisonSequentialSampling2004], the decision-making process is modeled as accumulation of evidence for or against a prospect over time, with the prospect being chosen for which the accumulated evidence first reaches a threshold.
+The sampling and accumulation model that was presented in this paper integrates both propositions by assuming that people accumulate the wins and losses resulting from a sequence of mean comparisons, with switching probabilities determining the size of the samples underlying each comparison and thresholds determining how much (more) comparisons a prospect must win in order to be chosen.
+Hence, the model treats the two paradigmatic sampling and decision strategies as the extreme ends of possible continua, allowing the switching probability not only to take values close to 0 and 1 but also values in between, and allowing single and multiple mean comparisons between prospects to be based on samples of varying size.
+Moreover, the model explicates the suggested link between sampling and decision strategies by assuming that the accumulation process more closely resembles the round-wise strategy for high switching probabilities, and, vice versa, the summary strategy for low switching probabilities.
+This is because high (low) switching probabilities cause the accumulation process to unfold over mean comparisons based on samples of small (large) size.
+
+## Sampling Strategies Might Shape Final Choice
+
+In a computational analysis, the presented model was used to simulate how the proposed sampling and accumulation processes shape the final choice.
+Therefore, the switching probabilities and evidence thresholds were systematically varied, while simulating choices between a safe and a risky prospect.
+The model predicts the choices to vary systematically with the switching probability.
+Specifically, whereas the choice patterns correspond closely to the solutions of EV maximization for low switching probabilities, increases in the switching probability can lead to an increasingly pronounced as-if underweighting of rare outcomes pattern.
+This is because for high switching probabilities, each independent mean comparison is based on small samples, in which small-probability outcomes are underrepresented rather than overrepresented.
+As a consequence, then, small-probability outcomes are predicted to contribute to the accumulated evidence less rather than more than would be warranted by their objective probabilities.
+Accordingly, the analyses showed that the structure of the choice problem---i.e., whether a small-probability outcome is present and which value it takes---is an important moderator for the effect of sampling strategies on the choice pattern.
+Importantly, while this explanation emphasizes that the reliance on small samples is a strong contributor to the as-if underweighting of rare outcomes pattern in DFE, it has little to do with the common notion of sampling error [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004].
+That is, the as-if underweighting of rare outcomes is not caused by a deviation of the sampled relative frequencies from the objective probabilities, but by the way the sampled outcomes are integrated and processed to evaluate the prospects.
+The analyses made this clear by showing that an as-if underweighting of rare outcomes pattern occurred, even if the sampling error is controlled for.
+In sum, by explicitly modeling their link, the current computational analysis showed how the interplay of sampling and decision strategies can shape the final choice.
+
+## CPT Can Reflect the Adoption of Sampling Strategies
+
+The current paper further extended the analysis of @hillsInformationSearchDecisions2010 by showing that the effects of sampling and decision strategies on the final choice can translate to characteristic signatures in cumulative prospect theory's value and weighting function.
+Having controlled for sampling error, the estimated CPT parameters and the resulting shapes of the value and weighting function primarily reflected how sensitive the combinations of sampling and decision strategies are to particular changes in the outcomes and their probabilities.
+Thereby, the analyses extends the notion that CPT can be used as a measurement tool to characterize information processing [@pachurHowTwainCan2017] from risky to uncertain choice.
+
+# Conclusion
 

### 2022-04-29 manuscript.Rmd
Major review

@@
 The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the alternatives between which people can choose.
-In fact, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
-Respectively, decision making can be understood as an information-processing problem whose solution requires a selection among choice alternatives.
-
-Now, let a *prospect* be a choice alternative that possesses only two kinds of fundamental properties: the possible outcomes of the alternative (e.g., gains or losses of some amount) and the probabilities with which these outcomes occur following the choice of the alternative.
+<!--Accordingly, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
+Thus, decision making can be understood as an information-processing problem whose solution requires a selection among choice alternatives, where the selection can only be systematic to the extent it is based on the assessment of differences in the alternatives' properties.-->
+Now, let a prospect be a choice alternative that possesses only two kinds of fundamental properties: the possible outcomes of the alternative (e.g., gains or losses of some amount) and the probabilities with which these outcomes occur following the choice of the alternative.
 Importantly, the information that the inputs provide about these properties can come in different forms.
 Specifically, in *decisions from description* (DFD), the inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
-Yet, in *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospect was chosen in similar past decisions.
-The inputs to DFE therefore take the form of sampled outcomes.
-Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DFD and DFE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
+In this case, people make decisions under risks, given that choosing one of the prospects does not inevitably lead to a certain outcome.
+Yet, in *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], the properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospect was chosen in similar past decisions.
+In other words, in DFE, the inputs take the form of sampled outcomes, with the lack of precise knowledge about all possible outcomes and their probabilities rendering the decision one under uncertainty rather than just risk.
+The differences in the input formats between DFD and DFE are illustrated in the following `code example`:
+
+```{r echo=TRUE}
+# define prospect
+outcomes <- c(5, 0)
+probabilities <- c(.2, .8)
+
+# input to decisions from description
+input_DFD <- data.frame(outcomes, probabilities)
+print(input_DFD)
+
+# input to decisions from experience, here: 10 sampled outcomes
+set.seed(2022)
+input_DFE <- sample(outcomes, size = 10, prob = probabilities, replace = T)
+print(input_DFE)
+```
+
+Although these distinct input forms---i.e., descriptions or sampled outcomes---may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DFD and DFE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructbehaviorGapDescription2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
-choice patterns in DFD deviate from the solutions of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities (*as-if overweighting of rare outcomes*);
+choice patterns in DFD deviate from the solutions of expected value (EV) maximization, *as if* small-probability outcomes are given more weight than would be warranted by their objective probabilities (*as-if overweighting of rare outcomes*);
 in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [*as-if underweighting of rare outcomes*, e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructbehaviorGapBehavioral2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
 
-Similar to explanations for other behavioral phenomena that rest on the assumption that the mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [cf.
-@fiedlerBewareSamplesCognitiveecological2000], an explanation for the as-if underweighting of rare outcomes may be build on the assumption that the mind is sensitive to the information provided by small samples [@hertwigDecisionsExperienceEffect2004; @plonskyRelianceSmallSamples2015; see also @erevChoicePredictionCompetition2010; @erevAnomaliesForecastsDescriptive2017, for the performance of models assuming reliance on small samples in prediction competitions]:
+The current paper presents a model that aims to sketch how the mind might exercise the capacity of making decisions from experience and shows how such a model comes to imply an as-if underweighting of rare outcomes pattern.
+<!--Similar to explanations for other behavioral phenomena that rest on the assumption that the human mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [cf.
+@fiedlerBewareSamplesCognitiveecological2000], an explanation for the as-if underweighting of rare outcomes may build on the assumption that the mind is sensitive to the information provided by small samples [@hertwigDecisionsExperienceEffect2004; @plonskyRelianceSmallSamples2015; see also @erevChoicePredictionCompetition2010; @erevAnomaliesForecastsDescriptive2017, for the performance of models assuming reliance on small samples in prediction competitions]:
 Specifically, following from the laws of large numbers [cf., e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
-In such a case---or in the less strict case of large samples---, then, the binomial distribution of each outcome can be approximated by a symmetric normal distribution.^[<!--Open footnote-->The binomial distribution of an outcome is the probability distribution of the number of times an outcome occurs in a sample.
+In such a case---or in the less strict case of large samples---, then, the binomial distribution of each outcome can be approximated by a symmetric normal distribution.^[The binomial distribution of an outcome is the probability distribution of the number of times an outcome occurs in a sample.
 According to the *de Moivre-Laplace theorem* [see, e.g., @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015], the binomial distribution can be approximated by a normal distribution given a large sample.
-Respectively, the relative relative frequencies with which an outcome occurs in a large sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.<!--Close footnote-->]
+Respectively, the relative relative frequencies with which an outcome occurs in a large sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.]
 However, for samples of small size, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
@@
 While this latter finding does not preclude the reliance on small samples---i.e., the mind may rely on only a portion of the sampled outcomes, discount them, or, as proposed in the current paper, distribute them over multiple smaller samples---, it suggests that an explanation for the as-if underweighting of rare outcomes cannot be reduced to inaccurate inferences about the latent properties of prospects that are caused by frugal sampling and the implied sampling error.
-Rather the opposite, this paper presents a simple sampling and accumulation model that suggests that the as-if underweighting of rare outcomes can be the consequence of an accurate assessment of differences among prospects in a latent property [but see @hertwigDescriptionexperienceGapRisky2009; @plonskyRelianceSmallSamples2015; @wulffMetaanalyticReviewTwo2018, for alternative explanations].
-
-Therefore, first consider the finding that in DFE *sampling strategies* were indicative for the final choice.
+Rather the opposite, this paper presents a sampling and accumulation model that suggests that the as-if underweighting of rare outcomes can be the consequence of an accurate assessment of differences among prospects in a latent property [but see @hertwigDescriptionexperienceGapRisky2009; @plonskyRelianceSmallSamples2015; @wulffMetaanalyticReviewTwo2018, for alternative explanations].
+-->
+Therefore, consider first what @hillsInformationSearchDecisions2010 consider the finding that in DFE *sampling strategies* were indicative for the final choice.
 That is, in one paradigm used to study DFE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
@@
 Since there is an uncountable number of choices people confront in the natural world, behavioral decision research routinely abstracts from choices between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.^[<!--Open footnote-->See @knightRiskUncertaintyProfit1921, Chapter 1, for a discussion on the reasonableness of such abstractions.<!--Close footnote-->]
+Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.
 These fundamental properties are considered the possible outcomes of a choice alternative and the probabilities with which these outcomes occur following the choice of the alternative.
@@
 
-### Desription of CPT
+### Description of CPT
 
@@
 
+## Why Sampling and Decision Strategies?
+
+[...]
+
 # Conclusion

### 2022-05-02 manuscript.Rmd
Review introduction

@@
                viridis,
+               scico,
                ggpubr,
@@
 Specifically, in *decisions from description* (DFD), the inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
-In this case, people make decisions under risks, given that choosing one of the prospects does not inevitably lead to a certain outcome.
+In this case, people make decisions under risk, provided that choosing one of the prospects does not inevitably lead to a certain outcome.
 Yet, in *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], the properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospect was chosen in similar past decisions.
@@
 ```{r echo=TRUE}
-# define prospect
+# define a prospect with two outcomes
 outcomes <- c(5, 0)
@@
 
-Although these distinct input forms---i.e., descriptions or sampled outcomes---may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DFD and DFE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
+\noindent
+To study DFE experimentally, one can use several paradigms, one of which is the sampling paradigm [see @hertwigDescriptionexperienceGapRisky2009], where people can, as much as they want, sequentially sample the outcomes of two prospects according to their objective probabilities before making a final choice between the prospects (see Figure\ \@ref(fig:sampling-paradigm)).
+
+Although the distinct input forms---i.e., descriptions or sampled outcomes---may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DFD and DFE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructbehaviorGapDescription2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
-choice patterns in DFD deviate from the solutions of expected value (EV) maximization, *as if* small-probability outcomes are given more weight than would be warranted by their objective probabilities (*as-if overweighting of rare outcomes*);
+choice patterns in DFD deviate from the solutions of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities (*as-if overweighting of rare outcomes*);
 in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [*as-if underweighting of rare outcomes*, e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructbehaviorGapBehavioral2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
+In other words, in DFD, people choose as if small-probability outcomes are more probable than objectively warranted, and in DFE, people choose as if the same small-probability outcomes are less probable than objectively warranted.
 
-The current paper presents a model that aims to sketch how the mind might exercise the capacity of making decisions from experience and shows how such a model comes to imply an as-if underweighting of rare outcomes pattern.
 <!--Similar to explanations for other behavioral phenomena that rest on the assumption that the human mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [cf.
@@
 -->
-Therefore, consider first what @hillsInformationSearchDecisions2010 consider the finding that in DFE *sampling strategies* were indicative for the final choice.
-That is, in one paradigm used to study DFE, namely, the sampling paradigm [@weberPredictingRiskSensitivity2004], before making a final choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
-Considering this paradigm and the choice between two prospects, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^[<!--Open footnote-->Note that @hillsInformationSearchDecisions2010 proposed two paradigmatic sampling strategies, where prospects are either switched just once (comprehensive sampling) or after each sampled outcome (piecewise sampling).
-Nevertheless, in their analyses of empirical sampling data, they used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and further acknowledged that "many [sampling] strategies will fall on the continuum between [the two paradigmatic strategies]" [@hillsInformationSearchDecisions2010, p.
-1788].
-Respectively, in the current paper sampling strategies are defined as switching probabilities.
+
+@hillsInformationSearchDecisions2010 argued that one contributing factor to the description-experience gap might be a potential link between what they considered two paradigmatic sampling and decision strategies (see Figure\ \@ref(fig:sampling-paradigm)).
+That is, the authors assumed that in the sampling paradigm, people either switch prospects after each sampled outcome (piecewise sampling) to compare single outcomes over repeated rounds (round-wise decision), or they switch just once between prospects (comprehensive sampling) and make only one comparison between the means across all sampled outcomes (summary decision).
+In fact, @hillsInformationSearchDecisions2010 provided tentative evidence for such a coupling of sampling and decision strategies by finding that the choices of people who switched frequently between prospects during the sampling phase were better predicted by a round-wise strategy (rather than a summary strategy), and that this predictive pattern reversed for people who switched infrequently.^[<!--Open footnote-->
+Note that in their analyses of empirical sampling data,  @hillsInformationSearchDecisions2010 used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and acknowledged that "many [sampling] strategies will fall on the continuum in between [the two paradigmatic strategies]" (p.
+1788).
 <!--Close footnote-->]
+Using the round-wise strategy may translate to an as-if underweighting of rare events pattern and the description-experience gap because the strategy selects the prospect that wins a majority of comparisons, while small-probability outcomes are predicted not to be considered in most of these comparisons.
+
+(ref:sampling-paradigm) Possible Sampling and Decision Strategies in the Sampling Paradigm and Their Impact on the Final Choice
+
+```{r sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
+knitr::include_graphics(path = "manuscript_files/sampling-paradigm.png")
+```
+
+<!-- Problems of Hills and Hertwig -->
+
+<!--Considering this paradigm and the choice between two prospects, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^
 and proposed two different decision strategies that people may adopt.
 Specifically, for a summary strategy, it is assumed that the prospect is chosen which produced the greater mean across all sampled outcomes.
-In turn, for a round-wise strategy, it is assumed that over multiple rounds two sampled outcomes---i.e., one from each of the prospects---are compared and that the prospect is chosen which won the comparison in most rounds.
-Then, @hillsInformationSearchDecisions2010 found that the choices of people who switched frequently between prospects during the sampling phase were better predicted by a round-wise strategy (rather than a summary strategy), and that this predictive pattern reversed for people who switched infrequently.
+In turn, for a round-wise strategy, it is assumed that over multiple rounds two sampled outcomes---i.e., one from each of the prospects---are compared and that the prospect is chosen which won the comparison in most rounds.-->
 
+<!--To model the process by which people arrive at the final choice, one must explicate a number of assumptions, e.g.: How do people decide when to switch between prospects during the sampling phase; how do they integrate and process the information obtained from the sampled outcomes; and, because they can sample as much as they want, how do they decide to stop sampling.
+To approach these questions, the model presented in this paper integrates the proposed link between sampling and decision strategies into the computational framework of sequential sampling models.-->
 Now, the current paper presents a sampling and accumulation model that provides an algorithmic link between sampling and decision strategies, and uses the model to discuss how the mind may rely on sampling strategies to alter which differences in the latent properties of prospects evidence is accumulated for.
@@
   geom_line(aes(color = gamma), size = .5) +
-  scale_color_viridis(option = "viridis") + 
+  scale_color_viridis(option = "inferno") + 
   geom_abline(intercept = 0, slope = 1, color = "gray", linetype = "dashed")
@@
   annotate(geom="text", x=.95, y=16, label="Wulff et al. (2018)", color="gray") + 
-  scale_color_viridis_d(option = "viridis") +
+  scale_color_viridis_d(option = "plasma") +
   theme_apa()
@@
 
-## determine normative choice according to latent and sampled EV
-fr_rates <- choices %>%
+## determine normative choice according to latent EV and sampled mean
+
+### latent EV
+
+fr_rates_EV <- choices %>%
   mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B")) %>% # determine normative choice
@@
                           rare == "attractive" ~ "\\in (0,.2)",
-                          rare == "unattractive" ~ "\\in (.8,1)"))
+                          rare == "unattractive" ~ "\\in (.8,1)"),
+         Norm = "EV")
 
-# labeller functions
-label_theta <- function(string) {
-  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
-}
+### sampled mean
 
-label_rare <- function(string) {
-  TeX(paste("$\\p_{High}$", string, sep = "")) #type of rare event
-}
-
-###
-fr_rates_m <- choices %>%
+fr_rates_mean <- choices %>%
   mutate(norm = case_when(a_ev_exp/b_ev_exp > 1 ~ "A", a_ev_exp/b_ev_exp < 1 ~ "B")) %>% # determine normative choice
@@
                           rare == "attractive" ~ "\\in (0,.2)",
-                          rare == "unattractive" ~ "\\in (.8,1)"))
+                          rare == "unattractive" ~ "\\in (.8,1)"),
+         Norm = "Mean")
 
-###
+fr_rates <- bind_rows(fr_rates_EV, fr_rates_mean)
+
+# labeller functions
+label_theta <- function(string) {
+  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
+}
+
+label_rare <- function(string) {
+  TeX(paste("$\\p_{High}$", string, sep = "")) #type of rare event
+}
 
 #plot
-fr_rates %>%
-  ggplot(aes(s, rate, group = type)) +
+
+fr_rates_risky <- fr_rates %>% filter(type == "Risky")
+fr_rates_safe <- fr_rates %>% filter(type == "Safe")
+
+fr_rates_risky %>%
+  ggplot(aes(s, rate, color = Norm)) +
   facet_grid(rare~a, labeller = labeller(rare = as_labeller(label_rare, default = label_parsed), 
@@
        y = "False Response Rate",
-       color = expression(psi),
+       color = "Norm",
        shape = "False\nResponse") +
@@
   scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
-  geom_line(data = fr_rates_m, aes(group = type), color = "gray") + 
-  geom_point(data = fr_rates_m, aes(shape = type), color = "gray", size = 2) +
-  geom_line(aes(color = s, group = type)) + 
-  geom_point(aes(color = s, shape = type), size = 2) +
+  geom_point(aes(shape = type), size = 2) +
+  geom_line() + 
+  geom_point(data = fr_rates_safe, aes(shape = type), size = 2) +
+  geom_line(data = fr_rates_safe) +
   scale_shape_manual(values = c(4, 16)) +
-  scale_color_viridis(option = "viridis") +
+  scale_color_viridis_d(option = "magma", begin = .3, end = .8) +
   theme_apa()
@@
   filter(parameter == "gamma") %>%
-  ggplot(aes(s, mean, color = s)) +
+  ggplot(aes(s, mean)) +
   facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
@@
   labs(x = element_blank(), #omit axis title
-       y = expression(gamma),
-       color = expression(psi)) +
+       y = expression(gamma)) +
   geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
   geom_point() +
-  scale_color_viridis(option = "viridis") +
   theme_apa() +
@@
   filter(parameter == "delta") %>% 
-  ggplot(aes(s, mean, color = s)) +
+  ggplot(aes(s, mean)) +
   facet_wrap(~a, nrow = 1) + 
@@
   labs(x = expression(psi),
-       y = expression(delta),
-       color = expression(psi)) +
+       y = expression(delta)) +
   geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
   geom_point() +
-  scale_color_viridis(option = "viridis") +
   theme_apa() + 
-  theme(strip.text.x = element_blank()) #omit facet labels
+  theme(strip.text.x = element_blank()) # omit facet labels
 
@@
   filter(parameter == "alpha") %>% 
-  ggplot(aes(s, mean, color = s)) +
+  ggplot(aes(s, mean)) +
   facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
@@
   geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_color_viridis(option = "viridis") +
   theme_apa() + 
@@
   filter(parameter == "rho") %>% 
-  ggplot(aes(s, mean, color = s, shape = boundary)) +
+  ggplot(aes(s, mean)) +
   facet_wrap(~a, nrow = 1) + 
@@
   geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  scale_color_viridis(option = "viridis") +
-  scale_shape_manual(values = c(4, 16)) +
   theme_apa() + 

### 2022-05-03 manuscript.Rmd
Review Introduction

@@
 In this case, people make decisions under risk, provided that choosing one of the prospects does not inevitably lead to a certain outcome.
-Yet, in *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], the properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospect was chosen in similar past decisions.
-In other words, in DFE, the inputs take the form of sampled outcomes, with the lack of precise knowledge about all possible outcomes and their probabilities rendering the decision one under uncertainty rather than just risk.
+Yet, in *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], the same properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospect was chosen in similar past decisions.
+In other words, in DFE, the inputs take the form of sampled outcomes, with the lack of precise knowledge about all possible outcomes and their probabilities rendering the decision one under uncertainty rather than just risk [@knightRiskUncertaintyProfit1921].
 The differences in the input formats between DFD and DFE are illustrated in the following `code example`:
@@
 \noindent
-To study DFE experimentally, one can use several paradigms, one of which is the sampling paradigm [see @hertwigDescriptionexperienceGapRisky2009], where people can, as much as they want, sequentially sample the outcomes of two prospects according to their objective probabilities before making a final choice between the prospects (see Figure\ \@ref(fig:sampling-paradigm)).
+To study DFE experimentally, one can use several paradigms, one of which is the sampling paradigm [see @hertwigDescriptionexperienceGapRisky2009], where people can, as much as they want, sequentially sample the outcomes of two prospects according to their objective probabilities before making a final choice (Figure\ \@ref(fig:sampling-paradigm)).
 
@@
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructbehaviorGapDescription2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
-choice patterns in DFD deviate from the solutions of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities (*as-if overweighting of rare outcomes*);
+choice patterns in DFD deviate from the normative solutions of expected value (EV) maximization, as if small-probability outcomes are given more weight than would be warranted by their objective probabilities (*as-if overweighting of rare outcomes*);
 in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [*as-if underweighting of rare outcomes*, e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructbehaviorGapBehavioral2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
-In other words, in DFD, people choose as if small-probability outcomes are more probable than objectively warranted, and in DFE, people choose as if the same small-probability outcomes are less probable than objectively warranted.
+In other words, in DFD, people choose as if small-probability outcomes are more probable than they objectively are, and in DFE, people choose as if the same small-probability outcomes are less probable.
 
-<!--Similar to explanations for other behavioral phenomena that rest on the assumption that the human mind is sensitive to the composition of the *samples*---i.e., sets of sampled outcomes---on which it operates [cf.
-@fiedlerBewareSamplesCognitiveecological2000], an explanation for the as-if underweighting of rare outcomes may build on the assumption that the mind is sensitive to the information provided by small samples [@hertwigDecisionsExperienceEffect2004; @plonskyRelianceSmallSamples2015; see also @erevChoicePredictionCompetition2010; @erevAnomaliesForecastsDescriptive2017, for the performance of models assuming reliance on small samples in prediction competitions]:
-Specifically, following from the laws of large numbers [cf., e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequencies with which the prospect's outcomes occur in a sample of infinite size converge almost surely to the respective objective probabilities.
-In such a case---or in the less strict case of large samples---, then, the binomial distribution of each outcome can be approximated by a symmetric normal distribution.^[The binomial distribution of an outcome is the probability distribution of the number of times an outcome occurs in a sample.
-According to the *de Moivre-Laplace theorem* [see, e.g., @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015], the binomial distribution can be approximated by a normal distribution given a large sample.
-Respectively, the relative relative frequencies with which an outcome occurs in a large sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.]
-However, for samples of small size, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
-
+<!--
 In fact, in DFE, people tend to sample only a small number of outcomes from each prospect [@hertwigDecisionsExperienceEffect2004; @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; see also @wulffMetaanalyticReviewTwo2018], which is a sufficient condition for the reliance on small samples in the evaluation of prospects.
@@
 -->
+
+What causes the description-experience gap?
+A quite common notion is that of the mind being sensitive to the information provided by the small number of sampled outcomes that people tend to rely on in DFE [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+According to this notion, small *samples*---i.e., sets of sampled outcomes---differ from descriptions in the information they actually provide about the prospects because they tend to underrepresent small-probability outcomes (Box 1).
+This difference is then assumed to carry over to the decision-making process, eventually causing distinct choice patterns in DFD and DFE.
+\newline
+
+\noindent
+\fbox{
+    \parbox{\textwidth}{
+        \textbf{Box 1.} 
+        \textit{Reliance on Small Samples in DFE.}
+        The binomial distribution of an outcome is the probability distribution of the number of times an outcome occurs in a sample.
+        According to the \textit{de Moivre-Laplace theorem} (see, e.g., \protect\hyperlink{ref-georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015}{Georgii, 2015}), the binomial distribution can be approximated by a normal distribution given a large sample.
+        That is, the relative relative frequency with which an outcome occurs in a large sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.
+        However, for small samples, the binomial distribution associated with a small-probability outcome is positive skewed, causing the relative frequency with which this outcome occurs in the sample to be smaller rather than larger than its objective probability.
+        That is, small-probability outcomes tend to be underrepresented in small samples.
+        An explanation for the as-if underweighting of rare outcomes pattern may thus build on the assumption that the mind is sensitive to the information provided by small samples (\protect\hyperlink{ref-hertwigDecisionsExperienceEffect2004}{Hertwig et al., 2004}; \protect\hyperlink{ref-plonskyRelianceSmallSamples2015}{Plonsky et al., 2015}; see also \protect\hyperlink{ref-erevChoicePredictionCompetition2010}{Erev et al., 2010}, \protect\hyperlink{ref-erevAnomaliesForecastsDescriptive2017}{2017}, for the performance of models assuming reliance on small samples in prediction competitions).
+    }
+}
+\newline
+
+Yet, the description-experience gap might not be solely caused by the reliance on a small number of sampled outcomes and the associated differences between the information underlying the decision-making process in DFD and DFE [see also @hauDecisionsExperienceStatistical2010; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
+Rather, the decision-making process itself may contribute to the gap.
+That is, in DFE, people must ...
 

### 2022-05-04 manuscript.Rmd
Revised Structure

@@
 title             : |
-  Sampling Strategies in Decisions from Experience
+  Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation
 
@@
 abstract: |
-  In decisions from experience, the probability to produce a higher outcome most of the time and the expected value are two latent properties that can be used to distinguish among the prospects of choice.
-This paper sketches a sampling and accumulation model that allows sampling strategies—i.e., the probability of sampling outcomes from different prospects in direct succession (switching probability)—to alter the degree to which evidence is accumulated for either one of these properties.
-A computational implementation of the model is used to simulate the respective sampling and accumulation process upfront choices between a safe and a two-outcome prospect, while varying switching probabilities and evidence thresholds.
-The simulation data shows that, depending on which latent property evidence is accumulated for and to which extent, respectively, choice patterns reflect various degrees of an as-if underweighting of rare outcomes or expected value maximization.
-Both choice patterns become more robust the more evidence is sampled and translate to characteristic parameter estimates for cumulative prospect theory’s value and weighting function.
+  Add abstract
 
@@
 
+<!-- Introduction -->
+
 The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the alternatives between which people can choose.
@@
 A quite common notion is that of the mind being sensitive to the information provided by the small number of sampled outcomes that people tend to rely on in DFE [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
-According to this notion, small *samples*---i.e., sets of sampled outcomes---differ from descriptions in the information they actually provide about the prospects because they tend to underrepresent small-probability outcomes (Box 1).
-This difference is then assumed to carry over to the decision-making process, eventually causing distinct choice patterns in DFD and DFE.
+Specifically, small *samples*---i.e., sets of sampled outcomes---often differ from descriptions in the information they actually provide about the prospects because they tend to underrepresent small-probability outcomes (Box \hyperlink{box}{1}, see also for illustrative purposes the `code example`, where the objective probability of outcome `5` is `.2`, and the sampled relative frequency is `.1`).
 \newline
@@
     \parbox{\textwidth}{
-        \textbf{Box 1.} 
+        \textbf{\hypertarget{box}{Box 1.}} 
         \textit{Reliance on Small Samples in DFE.}
         The binomial distribution of an outcome is the probability distribution of the number of times an outcome occurs in a sample.
-        According to the \textit{de Moivre-Laplace theorem} (see, e.g., \protect\hyperlink{ref-georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015}{Georgii, 2015}), the binomial distribution can be approximated by a normal distribution given a large sample.
-        That is, the relative relative frequency with which an outcome occurs in a large sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.
+        According to the \textit{de Moivre-Laplace theorem} (see, e.g., \protect\hyperlink{ref-georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015}{Georgii, 2015}), the binomial distribution can be approximated by a symmetric normal distribution given a large sample.
+        That is, the relative frequency with which an outcome occurs in a large sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.
         However, for small samples, the binomial distribution associated with a small-probability outcome is positive skewed, causing the relative frequency with which this outcome occurs in the sample to be smaller rather than larger than its objective probability.
@@
 
-Yet, the description-experience gap might not be solely caused by the reliance on a small number of sampled outcomes and the associated differences between the information underlying the decision-making process in DFD and DFE [see also @hauDecisionsExperienceStatistical2010; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
-Rather, the decision-making process itself may contribute to the gap.
-That is, in DFE, people must ...
+\noindent
+This distortion of the sampled information (sampling error) is then assumed to carry over to the decision-making process, eventually causing distinct choice patterns in DFD and DFE.
 
-@hillsInformationSearchDecisions2010 argued that one contributing factor to the description-experience gap might be a potential link between what they considered two paradigmatic sampling and decision strategies (see Figure\ \@ref(fig:sampling-paradigm)).
-That is, the authors assumed that in the sampling paradigm, people either switch prospects after each sampled outcome (piecewise sampling) to compare single outcomes over repeated rounds (round-wise decision), or they switch just once between prospects (comprehensive sampling) and make only one comparison between the means across all sampled outcomes (summary decision).
-In fact, @hillsInformationSearchDecisions2010 provided tentative evidence for such a coupling of sampling and decision strategies by finding that the choices of people who switched frequently between prospects during the sampling phase were better predicted by a round-wise strategy (rather than a summary strategy), and that this predictive pattern reversed for people who switched infrequently.^[<!--Open footnote-->
-Note that in their analyses of empirical sampling data,  @hillsInformationSearchDecisions2010 used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and acknowledged that "many [sampling] strategies will fall on the continuum in between [the two paradigmatic strategies]" (p.
-1788).
+Yet, the description-experience gap might not be solely caused by the reliance on a small number of sampled outcomes and the associated differences in the information underlying the decision-making processes in DFD and DFE [see also @hauDecisionsExperienceStatistical2010; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
+Rather, the specifics of the decision-making processes themselves may contribute to the gap.
+To this end, the current paper models how the mind might exercise the capacity of making decisions from experience in the sampling paradigm and examines the choice patterns that result from the modeled decision-making processes.
+More specifically, controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper investigates in a computational analysis whether and how the interplay of previously proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010, see also below] shapes DFE, and comes to imply choice patterns and functional forms in cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
+Note that CPT's value function is also considered.
+However, the focus of this paper is on the weighting function, as it is commonly used to describe an as-if overweighting and underweighting of rare outcomes, as well as the description-experience gap [see, e.g., @kellenHowVariantAre2016; @regenwetterConstructbehaviorGapBehavioral2017; but see @hertwigConstructbehaviorGapDescription2018].
 <!--Close footnote-->]
-Using the round-wise strategy may translate to an as-if underweighting of rare events pattern and the description-experience gap because the strategy selects the prospect that wins a majority of comparisons, while small-probability outcomes are predicted not to be considered in most of these comparisons.
 
-(ref:sampling-paradigm) Possible Sampling and Decision Strategies in the Sampling Paradigm and Their Impact on the Final Choice
+The remainder of the paper is structured as follows:
+[...]
 
-```{r sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
-knitr::include_graphics(path = "manuscript_files/sampling-paradigm.png")
-```
-
-<!-- Problems of Hills and Hertwig -->
-
-<!--Considering this paradigm and the choice between two prospects, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^
-and proposed two different decision strategies that people may adopt.
-Specifically, for a summary strategy, it is assumed that the prospect is chosen which produced the greater mean across all sampled outcomes.
-In turn, for a round-wise strategy, it is assumed that over multiple rounds two sampled outcomes---i.e., one from each of the prospects---are compared and that the prospect is chosen which won the comparison in most rounds.-->
-
-<!--To model the process by which people arrive at the final choice, one must explicate a number of assumptions, e.g.: How do people decide when to switch between prospects during the sampling phase; how do they integrate and process the information obtained from the sampled outcomes; and, because they can sample as much as they want, how do they decide to stop sampling.
-To approach these questions, the model presented in this paper integrates the proposed link between sampling and decision strategies into the computational framework of sequential sampling models.-->
-Now, the current paper presents a sampling and accumulation model that provides an algorithmic link between sampling and decision strategies, and uses the model to discuss how the mind may rely on sampling strategies to alter which differences in the latent properties of prospects evidence is accumulated for.
-More specifically, the proposed model assumes an accumulation process over a sequence of mean comparisons, with switching probabilities---i.e., the probability of sampling
-outcomes from different prospects in direct succession---determining the size of the samples underlying each mean comparison and thresholds determining how many comparisons a prospect must win in order to be chosen.
-The model is such that when switching probabilities are high, the accumulation process unfolds over mean comparisons based on small samples, thus resembling the round-wise strategy and accumulating evidence for differences in the probability to produce a higher outcome most of the time.
-Notably, in this case, small-probability outcomes are predicted to contribute to the majority of mean comparisons less than would be objectively warranted, which can translate to an as-if underweighting of rare outcomes, irrespective of what the thresholds require the number of won comparisons to be.
-<!--Accordingly, while increases in thresholds---and thus in the number of sampled outcomes distributed over multiple small samples, each of which is considered---allow to choose with increasing accuracy the prospect that is more likely to return a higher outcome, the resulting choices can produce an as-if underweighting of rare outcomes.-->
-In turn, for low switching probabilities, the accumulation process unfolds over mean comparisons based on large samples, thus resembling the summary strategy---for low thresholds, respectively---and accumulating evidence for differences in the EV.
-
-To substantiate the discussion, the model is used to simulate the sampling and accumulation process for choices between a safe and a two-outcome prospect, while systematically combining different switching probabilities and thresholds.
+<!-- To substantiate the discussion, the model is used to simulate the sampling and accumulation process for choices between a safe and a two-outcome prospect, while systematically combining different switching probabilities and thresholds.
 Considering choice rates and parameter estimates of cumulative prospect theory [@tverskyAdvancesProspectTheory1992], the computational analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
 Importantly, the analysis also shows that these distinct choice patterns become more robust with increasing thresholds.
-Before presenting the model and the computational analysis, the following section provides a definition of prospects.
+Before presenting the model and the computational analysis, the following section provides a definition of prospects.-->
 
-# Definition of Prospects
+# Explaining Decision Making in the Sampling Paradigm
+
+<!-- Formal Definition of Prospects / Notation -->
 
@@
 
-# Sampling Strategies and the Accumulation of Evidence
+<!-- Modeling steps and assumptions -->
 
@@
 
+[...]
+
+To model the process by which people arrive at the final choice in the sampling paradigm, one must explicate a number of assumptions, e.g.:
+
+* How does the mind decide when to switch between prospects during the sampling phase?
+
+* How does the mind decide when to stop sampling?
+
+* How does the mind integrate and evaluate the information obtained from the sampled outcomes?
+
+To approach the above questions, this paper presents a model that integrates two proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010] into the computational framework of sequential sampling models of decision-making [see, e.g., @markantModelingChoiceSearch2015].
+
+# Sampling and Decision Strategies
+
+Specifically, @hillsInformationSearchDecisions2010 argued that one contributing factor to the description-experience gap might be a potential link between what they considered two paradigmatic sampling and decision strategies (see Figure\ \@ref(fig:sampling-paradigm)).
+That is, the authors assumed that in the sampling paradigm, people either switch prospects after each sampled outcome (piecewise sampling) to compare single outcomes over repeated rounds (round-wise decision), or they switch just once between prospects (comprehensive sampling) and make only one comparison between the means across all sampled outcomes (summary decision).
+In fact, @hillsInformationSearchDecisions2010 provided tentative evidence for such a coupling of sampling and decision strategies by finding that the choices of people who switched frequently between prospects during the sampling phase were better predicted by a round-wise strategy (rather than a summary strategy), and that this predictive pattern reversed for people who switched infrequently.^[<!--Open footnote-->
+Note that in their analyses of empirical sampling data,  @hillsInformationSearchDecisions2010 used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and acknowledged that "many [sampling] strategies will fall on the continuum in between [the two paradigmatic strategies]" (p.
+1788).
+<!--Close footnote-->]
+Using the round-wise strategy may translate to an as-if underweighting of rare events pattern and the description-experience gap because the strategy selects the prospect that wins a majority of comparisons, while small-probability outcomes are predicted not to be considered in most of these comparisons.
+
+(ref:sampling-paradigm) Possible Sampling and Decision Strategies in the Sampling Paradigm and Their Impact on the Final Choice
+
+```{r sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
+knitr::include_graphics(path = "manuscript_files/sampling-paradigm.png")
+```
+
+<!--Considering this paradigm and the choice between two prospects, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^
+and proposed two different decision strategies that people may adopt.
+Specifically, for a summary strategy, it is assumed that the prospect is chosen which produced the greater mean across all sampled outcomes.
+In turn, for a round-wise strategy, it is assumed that over multiple rounds two sampled outcomes---i.e., one from each of the prospects---are compared and that the prospect is chosen which won the comparison in most rounds.-->
+
+<!-- Critique -->
+
+[...]
+
+# Current Approach: Sampling Strategies and the Accumulation of Different Types of Evidence
+
+<!-- How to overcome the problems + Evidence accumulation -->
+
+Now, the current paper presents a sampling and accumulation model that provides an algorithmic link between sampling and decision strategies, and uses the model to discuss how the mind may rely on sampling strategies to alter which differences in the latent properties of prospects evidence is accumulated for.
+More specifically, the proposed model assumes an accumulation process over a sequence of mean comparisons, with switching probabilities---i.e., the probability of sampling
+outcomes from different prospects in direct succession---determining the size of the samples underlying each mean comparison and thresholds determining how many comparisons a prospect must win in order to be chosen.
+The model is such that when switching probabilities are high, the accumulation process unfolds over mean comparisons based on small samples, thus resembling the round-wise strategy and accumulating evidence for differences in the probability to produce a higher outcome most of the time.
+Notably, in this case, small-probability outcomes are predicted to contribute to the majority of mean comparisons less than would be objectively warranted, which can translate to an as-if underweighting of rare outcomes, irrespective of what the thresholds require the number of won comparisons to be.
+<!--Accordingly, while increases in thresholds---and thus in the number of sampled outcomes distributed over multiple small samples, each of which is considered---allow to choose with increasing accuracy the prospect that is more likely to return a higher outcome, the resulting choices can produce an as-if underweighting of rare outcomes.-->
+In turn, for low switching probabilities, the accumulation process unfolds over mean comparisons based on large samples, thus resembling the summary strategy---for low thresholds, respectively---and accumulating evidence for differences in the EV.
+
 The mind may use these realizations---i.e., the sampled outcomes---to first infer the latent properties and then proceed by selecting a property, or combinations thereof, to assess differences among the prospects and make a respective choice.
@@
 
-## Model
+[...]
+
+## Models
 
 We consider the sampling paradigm and a choice between two prospects denoting the distributions $P'^X$ and $P'^Y$ of the discrete random variables $X$ and $Y$, respectively.
+
+### Round-Wise Integration Model
+
 The model assumes that the sampling process starts at random with a stochastic process on one of the two random variables.
@@
 Therefore, (8) may be adapted such that $Z$ takes the value $-1$ instead of $0$, such that the threshold determines how many more mean comparisons a prospect must win in order to be chosen.
+
+### Summary Integration Model
+
+[...]
 

### 2022-05-04 manuscript.Rmd
Example plot round-wise and summary integration

@@
 authornote: |
- This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the GitHub repository: https://github.com/linushof/sampling-in-dfe.
-The current version of the manuscript, created from the commit with the hash `r repro::current_hash()`, is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
+ This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub repository`: https://github.com/linushof/sampling-in-dfe.
+The current version of the manuscript, created from the commit with the `hash `r repro::current_hash()``, is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
 Supervisors:
@@
 The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the alternatives between which people can choose.
-<!--Accordingly, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and return a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
-Thus, decision making can be understood as an information-processing problem whose solution requires a selection among choice alternatives, where the selection can only be systematic to the extent it is based on the assessment of differences in the alternatives' properties.-->
-Now, let a prospect be a choice alternative that possesses only two kinds of fundamental properties: the possible outcomes of the alternative (e.g., gains or losses of some amount) and the probabilities with which these outcomes occur following the choice of the alternative.
+Now, let a prospect (or: gamble) be a choice alternative that possesses only two kinds of fundamental properties: the possible outcomes of the alternative (e.g., gains or losses of some amount) and the probabilities with which these outcomes occur following the choice of the alternative.
 Importantly, the information that the inputs provide about these properties can come in different forms.
@@
 In this case, people make decisions under risk, provided that choosing one of the prospects does not inevitably lead to a certain outcome.
-Yet, in *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], the same properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospect was chosen in similar past decisions.
+Yet, in *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], the same properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospects were chosen in similar past decisions.
 In other words, in DFE, the inputs take the form of sampled outcomes, with the lack of precise knowledge about all possible outcomes and their probabilities rendering the decision one under uncertainty rather than just risk [@knightRiskUncertaintyProfit1921].
@@
 \noindent
-To study DFE experimentally, one can use several paradigms, one of which is the sampling paradigm [see @hertwigDescriptionexperienceGapRisky2009], where people can, as much as they want, sequentially sample the outcomes of two prospects according to their objective probabilities before making a final choice (Figure\ \@ref(fig:sampling-paradigm)).
+To study DFE experimentally, one can use several paradigms, one of which is the sampling paradigm [see @hertwigDescriptionexperienceGapRisky2009], where people can, as much as they want, sequentially sample the outcomes of two prospects according to their objective probabilities before making a final choice between the prospects (Figure\ \@ref(fig:sampling-paradigm)).
 
@@
 in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [*as-if underweighting of rare outcomes*, e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructbehaviorGapBehavioral2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
-In other words, in DFD, people choose as if small-probability outcomes are more probable than they objectively are, and in DFE, people choose as if the same small-probability outcomes are less probable.
+More general, in DFD, people choose as if small-probability outcomes are more probable than they objectively are, and in DFE, people choose as if the same small-probability outcomes are less probable.
 
@@
 
-Yet, the description-experience gap might not be solely caused by the reliance on a small number of sampled outcomes and the associated differences in the information underlying the decision-making processes in DFD and DFE [see also @hauDecisionsExperienceStatistical2010; @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
+Yet, the description-experience gap might not be solely caused by the reliance on a small number of sampled outcomes in DFE and the associated sampling error [see also @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
 Rather, the specifics of the decision-making processes themselves may contribute to the gap.
-To this end, the current paper models how the mind might exercise the capacity of making decisions from experience in the sampling paradigm and examines the choice patterns that result from the modeled decision-making processes.
-More specifically, controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper investigates in a computational analysis whether and how the interplay of previously proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010, see also below] shapes DFE, and comes to imply choice patterns and functional forms in cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
-Note that CPT's value function is also considered.
-However, the focus of this paper is on the weighting function, as it is commonly used to describe an as-if overweighting and underweighting of rare outcomes, as well as the description-experience gap [see, e.g., @kellenHowVariantAre2016; @regenwetterConstructbehaviorGapBehavioral2017; but see @hertwigConstructbehaviorGapDescription2018].
+To this end, the current paper presents a model that sketches how the mind might exercise the capacity of making decisions from experience in the sampling paradigm, and examines the choice patterns that result from the modeled decision-making processes.
+More specifically, controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper investigates in a computational analysis whether and how the interplay of previously proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010, see also below] shapes DFE and comes to imply choice patterns and functional forms of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
+CPT's value function is also considered in this paper.
+However, the focus is on the weighting function, as it is commonly used to describe an as-if overweighting and underweighting of rare outcomes, and the description-experience gap [see, e.g., @kellenHowVariantAre2016; @regenwetterConstructbehaviorGapBehavioral2017; but see @hertwigConstructbehaviorGapDescription2018].
 <!--Close footnote-->]
 
-The remainder of the paper is structured as follows:
+The rest of the paper is structured as follows:
+In the first section, it is briefly discussed how DFE in the sampling paradigm differ from DFD in terms of the tasks involved in the decision-making process and thus the assumptions that must be made when modeling the respective process.
+In the section that follows, 
 [...]
+Thereafter, a simulation study is presented, where the proposed models are used to simulate the sampling and accumulation processes for a set of choices between a safe and a two-outcome prospect.
+Considering choice rates and parameter estimates of CPT, the computational analysis shows that which translate to characteristic patterns in the psychoeconomic functions of CPT.
+The paper closes with a discussion and conclusion.
+Note that all materials, including the can be retrieved from the accompanying `GitHub repository`.
 
@@
 
-To approach the above questions, this paper presents a model that integrates two proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010] into the computational framework of sequential sampling models of decision-making [see, e.g., @markantModelingChoiceSearch2015].
+To approach the above questions, this paper presents a couple of models that integrate two proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010] into the computational framework of sequential sampling models of decision-making [see, e.g., @markantModelingChoiceSearch2015].
 
@@
 
+```{r}
+#load CPT estimates
+cols_cpt <- list(.default = col_double(),
+                               boundary = col_factor(),
+                               a = col_factor(),
+                               parameter = col_factor())
+cpt_c <- read_csv("supplements/estimates_cpt_comprehensive.csv", col_types = cols_cpt)
+cpt_c <- cpt_c %>% 
+  filter(boundary == "absolute")
+
+cpt <- cpt %>% mutate(integration = "round")
+cpt_c <- cpt_c %>% mutate(integration = "summary")
+cpt_both <- bind_rows(cpt, cpt_c)
+```
+
+```{r test}
+
+#plot estimates
+
+gamma_2 <- cpt_both %>%
+  filter(parameter == "gamma") %>%
+  ggplot(aes(s, mean, color = integration)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free_y") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  scale_color_scico_d(palette = "berlin") + 
+  labs(x = expression(psi), 
+       y = expression(gamma)) +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() + 
+  theme_apa()
+
+delta_2 <- cpt_both %>%
+  filter(parameter == "delta") %>%
+  ggplot(aes(s, mean, color = integration)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free_y") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  scale_color_scico_d(palette = "berlin") + 
+  labs(y = expression(delta)) +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() + 
+  theme_apa()
+
+ggarrange(gamma_2, delta_2, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
+```
+
 \newpage

### 2022-05-05 manuscript.Rmd
Refine plots (add summary analysis)

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F, #omit messages
-                      fig.align = "l", #align figures to left margin
-                      fig.pos = "t", #display figures at the top of a page
+# set global chunk options
+knitr::opts_chunk$set(echo = FALSE, 
+                      fig.align = "l", 
+                      fig.pos = "t", 
                       fig.height=7, 
@@
 ```{r packages, include=FALSE}
-#load required packages
+# load required packages
 pacman::p_load(papaja,
-               knitr,
-               readr,
-               tidyr, 
-               dplyr,
-               ggplot2,
+               tidyverse,
                viridis, 
@@
                ggpubr,  
-               latex2exp)
+               latex2exp 
+               )
+```
+
+```{r data, include=FALSE}
+# load and prepare required data
+
+## choice data
+
+### specify column types
+cols_choices <- list(.default = col_double(),
+                     boundary = col_factor(),
+                     gamble = col_factor(),
+                     rare = col_factor(),
+                     agent = col_factor(),
+                     choice = col_factor())
+
+### load data files from round-wise and summary model
+choices_roundwise <- read_csv("data/choices_roundwise.csv", col_types = cols_choices)
+choices_summary <- read_csv("data/choices_summary.csv", col_types = cols_choices)
+
+### merge data files 
+choices_roundwise <- choices_roundwise %>%
+  mutate(model = "roundwise") %>% 
+  select(model, everything())
+
+choices_summary <- choices_summary %>%
+  mutate(model = "summary") %>% 
+  select(model, everything())
+
+choices <- bind_rows(choices_roundwise, choices_summary)
+
+## cpt estimates
+cols_cpt <- list(.default = col_double(),
+                 boundary = col_factor(),
+                 a = col_factor(),
+                 parameter = col_factor())
+
+cpt_roundwise <- read_csv("data/cpt-parameters_roundwise.csv", col_types = cols_cpt)
+cpt_summary <- read_csv("data/cpt-parameters_summary.csv", col_types = cols_cpt)
+
+cpt_roundwise <- cpt_roundwise %>%
+  mutate(model = "roundwise") %>% 
+  select(model, everything())
+
+cpt_summary <- cpt_summary %>%
+  mutate(model = "summary") %>% 
+  select(model, everything())
+
+cpt <- bind_rows(cpt_roundwise, cpt_summary)
 ```
@@
 
-```{r echo=TRUE}
+```{r code-example-1, echo=TRUE}
 # define a prospect with two outcomes
@@
 
-```{r sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
+```{r fig-sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
 knitr::include_graphics(path = "manuscript_files/sampling-paradigm.png")
@@
 Respectively, this section also contains predictions about the relations between $\psi$ and $\theta$ and the CPT parameters.
-A summary of the model predictions can be found in Table\ \@ref(tab:predictions).
+A summary of the model predictions can be found in Table\ \@ref(tab:tab-predictions).
 
@@
 
-```{r predictions}
+```{r tab-predictions}
 predictions <- tibble("Measure" = 
@@
 
-```{r weighting-function, fig.cap="(ref:weighting-function)"}
+```{r fig-weighting-function, fig.cap="(ref:weighting-function)"}
 #compute images of weighting function (wf)
@@
 
-* *Decision variable*: The decision variable of a prospect either counts the number of won comparisons---implying an absolute threshold---or how many more comparisons were won relative to the other prospect---implying a relative threshold.^[The results are similar for absolute and relative thresholds.
-For simplification, only the results of the absolute thresholds are reported in the main text.]
+* *Decision variable*: The decision variable of a prospect either counts the number of won comparisons---implying an absolute threshold---or how many more comparisons were won relative to the other prospect---implying a relative threshold.^[<!--Open footnote-->
+The results are similar for absolute and relative thresholds. 
+For simplification, only the results of the absolute thresholds are reported in the main text.
+The results for relative thresholds are reported in the Appendix.
+<!--Close footnote-->]
+
+```{r subset-absolute, include=FALSE}
+choices_absolute <- choices %>% filter(boundary == "absolute")
+cpt_absolute <- cpt %>% filter(boundary == "absolute")
+```
 
@@
 
-```{r data, include=FALSE}
-#load choice data
-cols_choices <- list(.default = col_double(),
-                     boundary = col_factor(),
-                     gamble = col_factor(),
-                     rare = col_factor(),
-                     agent = col_factor(),
-                     choice = col_factor())
-choices <- read_csv("data/simulation_summary.csv", col_types = cols_choices)
-choices <- choices %>% 
-  filter(boundary == "absolute")
-
-#load CPT estimates
-cols_cpt <- list(.default = col_double(),
-                 boundary = col_factor(),
-                 a = col_factor(),
-                 parameter = col_factor())
-cpt <- read_csv("data/cpt_parameters.csv", col_types = cols_cpt)
-cpt <- cpt %>% 
-  filter(boundary == "absolute")
-```
-
 To estimate the posterior distributions of the free parameters, Markov Chain Monte Carlo sampling as implemented in JAGS was used, where 20 chains of 40,000 samples each were run after a warm-up period of 1000 samples.
@@
 
-Overall, the results of the simulation match the predictions from Table\ \@ref(tab:predictions), however, with some exceptions concerning the estimates for the parameter $\delta$ of the weighting function.
+Overall, the results of the simulation match the predictions from Table\ \@ref(tab:tab-predictions), however, with some exceptions concerning the estimates for the parameter $\delta$ of the weighting function.
 We start by inspecting how the length of the information-processing chain changes with varying combinations of $\psi$ and $\theta$.
@@
 
-```{r chain-length, fig.cap="(ref:chain-length)"}
-choices %>%
-  group_by(s, a) %>% 
+```{r chain-length, fig.cap="(ref:chain-length)", eval = FALSE}
+choices_absolute %>%
+  group_by(model, s, a) %>% 
   summarize(n_med = median(n_sample)) %>% 
   ggplot(aes(x = s, y = n_med, group = as.factor(a), color = as.factor(a))) + 
+  facet_wrap(~model, nrow = 1) + 
    labs(x = expression(psi),
@@
 
-```{r choice-rates, fig.cap="(ref:choice-rates)"}
+```{r choice-rates, fig.cap="(ref:choice-rates)", eval = FALSE}
 #prepare data
@@
 
-(ref:weighting-parameters) Parameter Estimates and Graphical Shape of the Weighting Function
+(ref:weighting-parameters) Parameter Estimates of the Weighting Function
 
@@
 
-#plot estimates
-
-##gamma
-gamma <- cpt %>%
+label_theta <- function(string) {
+  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
+}
+
+# plot gamma estimates
+gamma <- cpt_absolute %>%
   filter(parameter == "gamma") %>%
-  ggplot(aes(s, mean)) +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
-  scale_y_continuous(limits = c(0,2), breaks = seq(0,2.0,1.0))+
-  labs(x = element_blank(), #omit axis title
-       y = expression(gamma)) +
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(gamma),
+       color = "Model") +
   geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
   geom_point() +
-  theme_apa() +
-  theme(axis.line.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.text.x = element_blank())
-
-##delta
-delta <- cpt %>%
+  geom_line() +
+  scale_color_viridis_d(option = "viridis", begin = .3, end = .8) + 
+  theme_minimal()
+
+# plot delta estimates
+delta <- cpt_absolute %>%
   filter(parameter == "delta") %>%
-  ggplot(aes(s, mean)) +
-  facet_wrap(~a, nrow = 1) + 
-  scale_y_continuous(limits = c(0,10), breaks = seq(0,10,5)) +
-  scale_x_continuous(limits = c(0, 1.1), breaks = seq(0,1,.5)) +
-  labs(x = expression(psi),
-       y = expression(delta)) +
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(delta),
+       color = "Model") +
   geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
   geom_point() +
-  theme_apa() + 
-  theme(strip.text.x = element_blank()) # omit facet labels
-
-wf <- cpt %>%
-  select(s, boundary, a, parameter, mean) %>%
+  geom_line() +
+  scale_color_viridis_d(option = "viridis", begin = .3, end = .8) + 
+  theme_minimal()
+
+# merge plots
+ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
+```
+
+Figure\ \@ref(fig:value-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$, as well as the shape of the value function.
+An increase in $\psi$ leads to a decrease in $\alpha$, reflecting that outcome information are largely ignored if choices are based on ordinal comparisons of single outcomes rather than on means of large samples.
+The respective shape of the value function is more concave, the higher the values of $\psi$. 
+Finally, $\rho$ varied systematically such that the choices were more sensitive to the valuations of the core CPT model for low values of $\psi$.
+However, even for high values of $\psi$, the choices did not appear to be random. [...]
+
+(ref:sensitivity-parameters) Parameter Estimates of the Outcome and Choice Sensitivity Parameter
+
+```{r sensitivity-parameters, fig.cap="(ref:sensitivity-parameters)"}
+
+# plot alpha estimates
+alpha <- cpt_absolute %>%
+  filter(parameter == "alpha") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(alpha),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_viridis_d(option = "viridis", begin = .3, end = .8) + 
+  theme_minimal()
+
+# plot rho estimates
+rho <- cpt_absolute %>%
+  filter(parameter == "rho") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(rho),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_viridis_d(option = "viridis", begin = .3, end = .8) + 
+  theme_minimal()
+
+# merge plots
+ggarrange(alpha, rho, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
+```
+
+Figure\ \@ref(fig:function-forms) displays the resulting graphical shapes of the weighting and value function.
+
+(ref:function-forms) Estimated Graphical Shape of the Weighting and Value Function
+
+```{r function-forms, fig.cap="(ref:function-forms)"}
+
+# plot weighting function
+
+## compute decision weights
+
+weights <- cpt_absolute %>%
+  select(model, s, boundary, a, parameter, mean) %>%
   pivot_wider(names_from = parameter, values_from = mean) %>%
@@
 
-##weighting function
-weight <- wf %>% #graphs for absolute boundary
+## plot graphs
+
+wf <- weights %>% 
   ggplot(aes(p, w, group = s, color = s)) +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  facet_wrap(~a~model, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
   labs(x = "Experienced Probability",
@@
   geom_line(size = .5) +
-  scale_color_viridis(option = "viridis") +
-  theme_apa() + 
-  theme(strip.text.x = element_blank()) #omit facet labels
-
-##merge figures
-ggarrange(gamma, delta, weight, ncol = 1, nrow = 3, common.legend = TRUE, legend = "right")
-```
-
-Figure\ \@ref(fig:value-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$, as well as the shape of the value function.
-An increase in $\psi$ leads to a decrease in $\alpha$, reflecting that outcome information are largely ignored if choices are based on ordinal comparisons of single outcomes rather than on means of large samples.
-The respective shape of the value function is more concave, the higher the values of $\psi$. 
-Finally, $\rho$ varied systematically such that the choices were more sensitive to the valuations of the core CPT model for low values of $\psi$.
-However, even for high values of $\psi$, the choices did not appear to be random. [...]
-
-(ref:value-parameters) Parameter Estimates and Graphical Shape of the Value Function
-
-```{r value-parameters, fig.cap="(ref:value-parameters)"}
-#plot estimates
-
-##alpha
-alpha <- cpt %>%
-  filter(parameter == "alpha") %>% 
-  ggplot(aes(s, mean)) +
-  facet_wrap(~a, nrow = 1, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) +
-  scale_x_continuous(limits = c(0, 1.1), breaks = seq(0,1,.5)) +
-  scale_y_continuous(limits = c(0,1), breaks = seq(0,1, .5)) + 
-  labs(x = element_blank(),
-       y = expression(alpha),
-       color = expression(psi)) +
-  geom_point() +
-  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  theme_apa() + 
-  theme(axis.line.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.text.x = element_blank())
-
-###value function
-vf <- cpt %>%
-  select(s, boundary, a, parameter, mean) %>%
+  scale_color_viridis(option = "plasma") +
+  theme_minimal()
+
+# value functions
+
+values <- cpt_absolute %>%
+  select(model, s, boundary, a, parameter, mean) %>%
   pivot_wider(names_from = parameter, values_from = mean) %>%
@@
 
-value <- vf %>% 
+vf <- values %>% 
   ggplot(aes(x, v, group = s, color = s)) +
-  facet_wrap(~a, nrow = 1)+ 
+  facet_wrap(~a~model, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
   labs(x = "Objective Outcome",
@@
   scale_x_continuous(limits = c(0,20), breaks = seq(0, 20, 10)) +
-  scale_y_continuous(limits = c(0,20), breaks = seq(0, 20, 10)) +
   geom_line(size = .5) +
-  scale_color_viridis(option = "viridis") +
-  theme_apa() + 
-  theme(strip.text.x = element_blank())
-
-##rho
-rho <- cpt %>%
-  filter(parameter == "rho") %>% 
-  ggplot(aes(s, mean)) +
-  facet_wrap(~a, nrow = 1) + 
-  labs(x = expression(psi),
-       y = expression(rho),
-       color = expression(psi)) +
-  scale_x_continuous(limits = c(0, 1.1), breaks = seq(0, 1,.5)) +
-  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5,2.5)) +
-  geom_point() +
-  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  theme_apa() + 
-  theme(strip.text.x = element_blank())
-
-##merge figure
-ggarrange(alpha, rho, value, ncol = 1, nrow = 3, common.legend = TRUE, legend = "right") 
-```
-
-# Summary and Discussion
+  scale_color_viridis(option = "plasma") +
+  theme_minimal()
+
+# merge plots
+ggarrange(wf, vf, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
+```
+
+# Discussion
 
@@
 
-```{r}
-#load CPT estimates
-cols_cpt <- list(.default = col_double(),
-                               boundary = col_factor(),
-                               a = col_factor(),
-                               parameter = col_factor())
-cpt_c <- read_csv("supplements/estimates_cpt_comprehensive.csv", col_types = cols_cpt)
-cpt_c <- cpt_c %>% 
-  filter(boundary == "absolute")
-
-cpt <- cpt %>% mutate(integration = "round")
-cpt_c <- cpt_c %>% mutate(integration = "summary")
-cpt_both <- bind_rows(cpt, cpt_c)
-```
-
-```{r test}
-
-#plot estimates
-
-gamma_2 <- cpt_both %>%
-  filter(parameter == "gamma") %>%
-  ggplot(aes(s, mean, color = integration)) +
-  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free_y") +
-  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
-  scale_color_scico_d(palette = "berlin") + 
-  labs(x = expression(psi), 
-       y = expression(gamma)) +
-  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  geom_point() +
-  geom_line() + 
-  theme_apa()
-
-delta_2 <- cpt_both %>%
-  filter(parameter == "delta") %>%
-  ggplot(aes(s, mean, color = integration)) +
-  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free_y") +
-  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
-  scale_color_scico_d(palette = "berlin") + 
-  labs(y = expression(delta)) +
-  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  geom_point() +
-  geom_line() + 
-  theme_apa()
-
-ggarrange(gamma_2, delta_2, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
-```
+[...]
 

### 2022-05-05 manuscript.Rmd
Complete Figure update

@@
                viridis,
-               scico, 
+               viridisLite, 
                ggpubr,  
@@
 
-```{r chain-length, fig.cap="(ref:chain-length)", eval = FALSE}
-choices_absolute %>%
-  group_by(model, s, a) %>% 
-  summarize(n_med = median(n_sample)) %>% 
-  ggplot(aes(x = s, y = n_med, group = as.factor(a), color = as.factor(a))) + 
-  facet_wrap(~model, nrow = 1) + 
+```{r prepare-chain-length, eval = FALSE}
+chain_lengths <- choices_absolute %>%
+  ggplot(aes(x = s, y = n_sample, color = model)) +
+  facet_wrap(~a, nrow = 2, scales = "free") + 
   labs(x = expression(psi),
-       y = "Median of Overall Sampled Outcomes",
-       color = expression(theta)) +
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
-  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 150, 50)) +
-  geom_point() +
-  geom_line() + 
+       y = "Number of Sampled Outcomes",
+       color = "Model") + 
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5))+
+  geom_jitter(alpha = .05) + 
+  geom_smooth(color = "gray") + 
   geom_hline(yintercept = 14, linetype = "dashed", color = "gray") +
-  annotate(geom="text", x=.95, y=16, label="Wulff et al. (2018)", color="gray") + 
-  scale_color_viridis_d(option = "plasma") +
-  theme_apa()
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
+  guides(color = guide_legend(override.aes = list(alpha = 1))) +
+  theme_minimal()
+```
+
+```{r chain-length, fig.cap="(ref:chain-length)", out.width="100%"}
+knitr::include_graphics(path = "manuscript_files/chain-lengths.png")
 ```
@@
 
-Figure\ \@ref(fig:choice-rates) displays the rates of choices that did not maximize the latent EV (hereafter: false response rates) for each combination of $\psi$ and $\theta$.
+Figures\ \@ref(fig:choice-rates-roundwise) and \@ref(fig:choice-rates-summary) display the rates of choices that did not maximize the latent EV (hereafter: false response rates) for each combination of $\psi$ and $\theta$.
 To demonstrate that the deviations from EV maximization are not just due to sampling error, the rates of choices that did not maximize the sampled mean are displayed in gray. 
@@
 
-(ref:choice-rates) Rates of False Risky and False Safe Choices
-
-```{r choice-rates, fig.cap="(ref:choice-rates)", eval = FALSE}
+(ref:choice-rates-roundwise) Rates of False Risky and False Safe Choices in the Round-Wise Integration Model
+
+```{r choice-rates-roundwise, fig.cap="(ref:choice-rates-roundwise)"}
 #prepare data
@@
 
-fr_rates_EV <- choices %>%
+fr_rates_EV <- choices_absolute %>%
+  filter(model == "roundwise") %>% 
   mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B")) %>% # determine normative choice
@@
 
-fr_rates_mean <- choices %>%
+fr_rates_mean <- choices_absolute %>% 
+  filter(model == "roundwise") %>% 
   mutate(norm = case_when(a_ev_exp/b_ev_exp > 1 ~ "A", a_ev_exp/b_ev_exp < 1 ~ "B")) %>% # determine normative choice
@@
   geom_line(data = fr_rates_safe) +
-  scale_shape_manual(values = c(4, 16)) +
-  scale_color_viridis_d(option = "magma", begin = .3, end = .8) +
-  theme_apa()
+  scale_shape_manual(values = c(8, 16)) +
+  scale_color_manual(values = c("#d3d3d3", "#35b779")) + 
+  theme_minimal()
+```
+
+(ref:choice-rates-summary) Rates of False Risky and False Safe Choices in the Summary Integration Model
+
+```{r choice-rates-summary, fig.cap="(ref:choice-rates-summary)"}
+#prepare data
+
+## determine normative choice according to latent EV and sampled mean
+
+### latent EV
+
+fr_rates_EV <- choices_absolute %>%
+  filter(model == "summary") %>% 
+  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B")) %>% # determine normative choice
+  filter(!is.na(norm)) %>% #exclude trials with equal EV
+  group_by(s, boundary, a, rare, norm, choice) %>% #separate by model parameter and type of rare event
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), #compute response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", #determine false response type
+                          norm == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>% #remove correct responses
+  select(-c(norm, choice, n)) %>% 
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]", #change facet labels for rare events
+                          rare == "attractive" ~ "\\in (0,.2)",
+                          rare == "unattractive" ~ "\\in (.8,1)"),
+         Norm = "EV")
+
+### sampled mean
+
+fr_rates_mean <- choices_absolute %>% 
+  filter(model == "summary") %>% 
+  mutate(norm = case_when(a_ev_exp/b_ev_exp > 1 ~ "A", a_ev_exp/b_ev_exp < 1 ~ "B")) %>% # determine normative choice
+  filter(!is.na(norm)) %>% #exclude trials with equal EV
+  group_by(s, boundary, a, rare, norm, choice) %>% #separate by model parameter and type of rare event
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), #compute response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", #determine false response type
+                          norm == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>% #remove correct responses
+  select(-c(norm, choice, n)) %>% 
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]", #change facet labels for rare events
+                          rare == "attractive" ~ "\\in (0,.2)",
+                          rare == "unattractive" ~ "\\in (.8,1)"),
+         Norm = "Mean")
+
+fr_rates <- bind_rows(fr_rates_EV, fr_rates_mean)
+
+# labeller functions
+label_theta <- function(string) {
+  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
+}
+
+label_rare <- function(string) {
+  TeX(paste("$\\p_{High}$", string, sep = "")) #type of rare event
+}
+
+#plot
+
+fr_rates_risky <- fr_rates %>% filter(type == "Risky")
+fr_rates_safe <- fr_rates %>% filter(type == "Safe")
+
+fr_rates_risky %>%
+  ggplot(aes(s, rate, color = Norm)) +
+  facet_grid(rare~a, labeller = labeller(rare = as_labeller(label_rare, default = label_parsed), 
+                                         a = as_labeller(label_theta, default = label_parsed))) +
+  labs(x = expression(psi),
+       y = "False Response Rate",
+       color = "Norm",
+       shape = "False\nResponse") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  geom_point(aes(shape = type), size = 2) +
+  geom_line() + 
+  geom_point(data = fr_rates_safe, aes(shape = type), size = 2) +
+  geom_line(data = fr_rates_safe) +
+  scale_shape_manual(values = c(8, 16)) +
+  scale_color_manual(values = c("#d3d3d3", "#3e4989")) + 
+  theme_minimal()
 ```
@@
   geom_line() +
-  scale_color_viridis_d(option = "viridis", begin = .3, end = .8) + 
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
   theme_minimal()
@@
 
-Figure\ \@ref(fig:value-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$, as well as the shape of the value function.
+Figure\ \@ref(fig:sensitivity-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$.
 An increase in $\psi$ leads to a decrease in $\alpha$, reflecting that outcome information are largely ignored if choices are based on ordinal comparisons of single outcomes rather than on means of large samples.
@@
   ggplot(aes(p, w, group = s, color = s)) +
-  facet_wrap(~a~model, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  facet_wrap(~model~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
   labs(x = "Experienced Probability",
@@
   geom_line(size = .5) +
-  scale_color_viridis(option = "plasma") +
+  scale_color_viridis(option = "mako") +
   theme_minimal()
@@
   ggplot(aes(x, v, group = s, color = s)) +
-  facet_wrap(~a~model, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  facet_wrap(model~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
   labs(x = "Objective Outcome",

### 2022-05-14 manuscript.Rmd
Simplify definition of prospects

@@
 
-```{r code-example-1, echo=TRUE}
+```{r code-example, echo=TRUE}
 # define a prospect with two outcomes
@@
 More general, in DFD, people choose as if small-probability outcomes are more probable than they objectively are, and in DFE, people choose as if the same small-probability outcomes are less probable.
-
-<!--
-In fact, in DFE, people tend to sample only a small number of outcomes from each prospect [@hertwigDecisionsExperienceEffect2004; @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; see also @wulffMetaanalyticReviewTwo2018], which is a sufficient condition for the reliance on small samples in the evaluation of prospects.
-Yet, the as-if underweighting of rare outcomes may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018].
-While this latter finding does not preclude the reliance on small samples---i.e., the mind may rely on only a portion of the sampled outcomes, discount them, or, as proposed in the current paper, distribute them over multiple smaller samples---, it suggests that an explanation for the as-if underweighting of rare outcomes cannot be reduced to inaccurate inferences about the latent properties of prospects that are caused by frugal sampling and the implied sampling error.
-Rather the opposite, this paper presents a sampling and accumulation model that suggests that the as-if underweighting of rare outcomes can be the consequence of an accurate assessment of differences among prospects in a latent property [but see @hertwigDescriptionexperienceGapRisky2009; @plonskyRelianceSmallSamples2015; @wulffMetaanalyticReviewTwo2018, for alternative explanations].
--->
 
@@
 Yet, the description-experience gap might not be solely caused by the reliance on a small number of sampled outcomes in DFE and the associated sampling error [see also @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
-Rather, the specifics of the decision-making processes themselves may contribute to the gap.
+Rather, the specifics of the actual decision-making process, such as how the outcomes of the prospects of choice are sampled, integrated, and evaluated, might contribute to the gap.
 To this end, the current paper presents a model that sketches how the mind might exercise the capacity of making decisions from experience in the sampling paradigm, and examines the choice patterns that result from the modeled decision-making processes.
-More specifically, controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper investigates in a computational analysis whether and how the interplay of previously proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010, see also below] shapes DFE and comes to imply choice patterns and functional forms of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
+More specifically, controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper investigates in a computational analysis whether and how the potential interplay of sampling and decision strategies shapes DFE and comes to imply choice patterns and functional forms of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
 CPT's value function is also considered in this paper.
@@
 
+<!-- Outline -->
+
+<!--
 The rest of the paper is structured as follows:
 In the first section, it is briefly discussed how DFE in the sampling paradigm differ from DFD in terms of the tasks involved in the decision-making process and thus the assumptions that must be made when modeling the respective process.
-In the section that follows, 
+In the section that follows, two previously proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010, see also below] are described.
+It is discussed 
 [...]
 Thereafter, a simulation study is presented, where the proposed models are used to simulate the sampling and accumulation processes for a set of choices between a safe and a two-outcome prospect.
-Considering choice rates and parameter estimates of CPT, the computational analysis shows that which translate to characteristic patterns in the psychoeconomic functions of CPT.
+Considering choice rates and parameter estimates of CPT, the computational analysis shows that ... which translate to characteristic patterns in the psychoeconomic functions of CPT.
+[...]
 The paper closes with a discussion and conclusion.
 Note that all materials, including the can be retrieved from the accompanying `GitHub repository`.
-
-<!-- To substantiate the discussion, the model is used to simulate the sampling and accumulation process for choices between a safe and a two-outcome prospect, while systematically combining different switching probabilities and thresholds.
-Considering choice rates and parameter estimates of cumulative prospect theory [@tverskyAdvancesProspectTheory1992], the computational analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
-Importantly, the analysis also shows that these distinct choice patterns become more robust with increasing thresholds.
-Before presenting the model and the computational analysis, the following section provides a definition of prospects.-->
+-->
 
@@
 
-Since there is an uncountable number of choices people confront in the natural world, behavioral decision research routinely abstracts from choices between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.
-These fundamental properties are considered the possible outcomes of a choice alternative and the probabilities with which these outcomes occur following the choice of the alternative.
-Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs are prospects.
-As such, prospects can be understood as the distribution of a discrete random variable.
-More specifically, following @kolmogorovFoundationsTheoryProbability1950 and adopting the notation from @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, let the tuple $(\Omega, \mathcal{F}, P)$ be a probability space.
-Accordingly, $\Omega$ is a finite sample space with each element $\omega \in \Omega$ denoting a possible consequence of choosing the respective prospect.
-$\mathcal{F}$ is the power set $\mathcal{P}(\Omega)$ with each element $A \in \mathcal{F}$ being a subset of $\Omega$, also denoted a random event.
-$P$ is the probability measure
-$$
-P: \mathcal{F} \to [0,1]
+<!--Since there is an uncountable number of choices people confront in their daily life, behavioral decision research routinely abstracts from choices between particular alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
+Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.-->
+With the choice between at least two prospects, behavioral decision research studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.
+These fundamental properties are considered the $n$ possible outcomes of a choice alternative, denoted by the set $\{x_i\}_{i \in \{1, ..., n\}}$, and the probabilities with which these outcomes occur following the choice of the alternative, denoted by the set $\{p(x_i)\}$.
+That is, each choice alternative that is fully described by a set of outcome-probability pairs $\{(x_i, p(x_i))\}$ satisfying $\sum_{i = 1}^n p(x_i) = 1$ is a prospect.
+Note that a prospect can be conceptualized as the distribution $P$ of a discrete random variable $X$, where each outcome in $\{x_i\}$ denotes a possible value that $X$ can take.
+In other words, then, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
+$$
+\{P^1, ... , P^k\}
+\; .
 \tag{1}
 $$
-assigning the elements of $\mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.
-Now, the random variable is a function
-$$
-\begin{aligned}
-  X : (\Omega, \mathcal{F}) &\to (\Omega', \mathcal{F'})  \\
-  \omega &\mapsto x
-  \; ,
-\end{aligned}
-\tag{2}
-$$
-where $(\Omega', \mathcal{F'})$ is a measurable space with each element $x \in \Omega'$ denoting a possible outcome of a prospect and each element $A' \in \mathcal{F'}$ being a subset of $\Omega'$.
-An outcome's probability $p_X(x)$ is then provided by the pushforward measure
-$$
-P' : \mathcal{F'} \to [0,1]
-\tag{3}
-$$
-with 
-$$
-P'(A' \in \mathcal{F'}) := P(\{\omega: X(\omega) = x \in A'\})
-\; .
-\tag{4}
-$$
-Note that the measure in (3) and (4), respectively, is a random variable's distribution and therefore a prospect. 
-Accordingly, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
-$$
-\{P'^1, ... , P'^k\}
-\; ,
-\tag{5}
-$$
-where each element $P'$ can itself be considered a finite set of outcome-probability pairs $\{(x_i, p_X(x_i)\}_{i \in \mathbb{N}}$.
-
 <!-- Modeling steps and assumptions -->
@@
 
-```{r fig-sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
+```{r sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
 knitr::include_graphics(path = "manuscript_files/sampling-paradigm.png")
 ```
-
-<!--Considering this paradigm and the choice between two prospects, @hillsInformationSearchDecisions2010 distinguished sampling strategies along the frequency of switches between the two prospects during the sampling phase,^
-and proposed two different decision strategies that people may adopt.
-Specifically, for a summary strategy, it is assumed that the prospect is chosen which produced the greater mean across all sampled outcomes.
-In turn, for a round-wise strategy, it is assumed that over multiple rounds two sampled outcomes---i.e., one from each of the prospects---are compared and that the prospect is chosen which won the comparison in most rounds.-->
 
@@
 Respectively, this section also contains predictions about the relations between $\psi$ and $\theta$ and the CPT parameters.
-A summary of the model predictions can be found in Table\ \@ref(tab:tab-predictions).
+A summary of the model predictions can be found in Table\ \@ref(tab:predictions).
 
@@
 
-```{r tab-predictions}
+```{r predictions}
 predictions <- tibble("Measure" = 
@@
 should be chosen.
-To describe how people's choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, where the latter were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
-Together, these empirical choice patterns indicate a violation of EV and expected utility (EU) maximization [see @bernoulliExpositionNewTheory1954\/1738].<!--Close footnote-->]
+To describe how people's choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->
+@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, where the latter were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
+Together, these empirical choice patterns indicate a violation of EV and expected utility (EU) maximization [see @bernoulliExpositionNewTheory1954\/1738].
+<!--Close footnote-->]
 CPT and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by assuming that people maximize the valuation
@@
 
-```{r fig-weighting-function, fig.cap="(ref:weighting-function)"}
+```{r weighting-function, fig.cap="(ref:weighting-function)"}
 #compute images of weighting function (wf)
@@
        color = expression(gamma)) + 
-  theme_apa() + 
+  theme_minimal() + 
   geom_line(aes(color = gamma), size = .5) +
@@
 Specifically, because of the S-shaped curvature, the differences between the images $w(p)$ may be smaller than those between the respective cumulative probabilities in the lower and upper part of the cumulative probability scale, but may be considerably greater in the middle part.
-As a consequence, the cumulative decisions weights are smaller than the respective objective probabilities for small-probability outcomes of low and high rank, but they are larger for small-probability outcomes of a middle rank.^[<!--Open footnote-->Note that the distinction between outcomes of either low/high rank or middle rank is unnecessary for at most two-outcome prospects [see @tverskyAdvancesProspectTheory1992, see also below].
+As a consequence, the cumulative decisions weights are smaller than the respective objective probabilities for small-probability outcomes of low and high rank, but they are larger for small-probability outcomes of a middle rank.^[<!--Open footnote-->
+Note that the distinction between outcomes of either low/high rank or middle rank is unnecessary for at most two-outcome prospects [see @tverskyAdvancesProspectTheory1992, see also below].
 However, for finite many outcomes, the distinction is critical.
@@
 I.e., neither could one interpretation of the gap be in terms of an as-if underweighting (overweighting) of rare outcomes in DFE (DFD), nor would any of the potential contributors to the gap considered so far [cf.
-@hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than other small-probability outcomes.<!--Close footnote-->]
+@hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than other small-probability outcomes.
+<!--Close footnote-->]
 Note that for all $\gamma < 1$ the graph of $w$ takes an inverse S-shape and the entire weighting pattern is reversed.
@@
 In sum, then 100 (parameter combinations) $\times$ 100 (agents) $\times$ 60 (choice problems)  = 600,000 sampling and accumulation processes were simulated.
-The respective dataset can be retrieved from the accompanying `GitHub` repository.
+The respective dataset can be retrieved from the accompanying `GitHub repository`.
 
@@
 
-Overall, the results of the simulation match the predictions from Table\ \@ref(tab:tab-predictions), however, with some exceptions concerning the estimates for the parameter $\delta$ of the weighting function.
+Overall, the results of the simulation match the predictions from Table\ \@ref(tab:predictions), however, with some exceptions concerning the estimates for the parameter $\delta$ of the weighting function.
 We start by inspecting how the length of the information-processing chain changes with varying combinations of $\psi$ and $\theta$.
@@
 
-```{r prepare-chain-length, eval = FALSE}
+```{r fig.cap="(ref:chain-length)", eval = FALSE}
 chain_lengths <- choices_absolute %>%
@@
   theme_minimal()
+chain_lengths
 ```
@@
 In these cases, no relative frequencies other than 0 and 1 are supplied to the weighting function, which may explain that the values in between cannot be reliably accounted for.
-However, for $\theta = 1$ and $\psi < 1$, the estimates imply a linear weighting pattern, in line with the explanation that if the mind were to infer the latent objective probabilities of outcomes from the sampled relative frequencies and to follow the principle of EV maximization, sampling error can account for any deviations from it.^[<!--Open footnote-->Note that the same line of reasoning holds, were the mind to approximate the solutions of EV maximization by choosing the prospect with higher sampled mean.<!--Close footnote-->]
-Note also Figure\ \@ref(fig:choice-rates), where there are no choices for $\theta = 1$ that do not maximize the sampled mean.
+However, for $\theta = 1$ and $\psi < 1$, the estimates imply a linear weighting pattern, in line with the explanation that if the mind were to infer the latent objective probabilities of outcomes from the sampled relative frequencies and to follow the principle of EV maximization, sampling error can account for any deviations from it.^[<!--Open footnote-->
+Note that the same line of reasoning holds, were the mind to approximate the solutions of EV maximization by choosing the prospect with higher sampled mean.
+<!--Close footnote-->]
+Note also Figure\ \@ref(fig:choice-rates-roundwise), where there are no choices for $\theta = 1$ that do not maximize the sampled mean.
 
@@
 In other words, the higher the value of $\psi$, the more severe is the underweighting (overweighting) of the high-rank outcome of the risky prospect in CPT, if it is of small (large) probability.
-$\delta$ takes values $\geq 1$ and increases slightly with $\psi$, causing the overweighting of the high-rank outcome of the risky prospect to extend across the mid-point. [...]
+$\delta$ takes values $\geq 1$ and increases slightly with $\psi$, causing the overweighting of the high-rank outcome of the risky prospect to extend across the mid-point. 
+[...]
 

### 2022-05-16 manuscript.Rmd
Reviews introduction

@@
 The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the alternatives between which people can choose.
-Now, let a prospect (or: gamble) be a choice alternative that possesses only two kinds of fundamental properties: the possible outcomes of the alternative (e.g., gains or losses of some amount) and the probabilities with which these outcomes occur following the choice of the alternative.
+Let a prospect (or: gamble) be a choice alternative that possesses only two kinds of fundamental properties: the possible outcomes of the alternative (e.g., gains or losses of some amount) and the probabilities with which these outcomes occur following the choice of the alternative.
 Importantly, the information that the inputs provide about these properties can come in different forms.
 Specifically, in *decisions from description* (DFD), the inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
-In this case, people make decisions under risk, provided that choosing one of the prospects does not inevitably lead to a certain outcome.
+In this case, people make decisions under risk, provided that choosing one of the prospects does not inevitably lead to a particular outcome.
 Yet, in *decisions from experience* [DFE, @hertwigDecisionsExperienceEffect2004], the same properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred in the past, e.g., when the prospects were chosen in similar past decisions.
-In other words, in DFE, the inputs take the form of sampled outcomes, with the lack of precise knowledge about all possible outcomes and their probabilities rendering the decision one under uncertainty rather than just risk [@knightRiskUncertaintyProfit1921].
+In other words, in DFE, the inputs take the form of sampled outcomes, with the lack of precise knowledge about all possible outcomes and their probabilities rendering the decision one under uncertainty rather than just risk.
 The differences in the input formats between DFD and DFE are illustrated in the following `code example`:
@@
 
-\noindent
-To study DFE experimentally, one can use several paradigms, one of which is the sampling paradigm [see @hertwigDescriptionexperienceGapRisky2009], where people can, as much as they want, sequentially sample the outcomes of two prospects according to their objective probabilities before making a final choice between the prospects (Figure\ \@ref(fig:sampling-paradigm)).
-
-Although the distinct input forms---i.e., descriptions or sampled outcomes---may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that---taking a quite general perspective---there are robust differences between the choices that are made in DFD and DFE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
+Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that there are robust differences between the choices that are made in DFD and DFE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
 In one reading of the gap,^[<!--Open footnote-->See @hertwigConstructbehaviorGapDescription2018, for a discussion on the interpretation of the gap.<!--Close footnote-->]
@@
 in turn, in DFE, choice patterns deviate from the solutions of EV maximization, as if the same small-probability outcomes are given less weight than would be objectively warranted [*as-if underweighting of rare outcomes*, e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; @regenwetterConstructbehaviorGapBehavioral2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
-More general, in DFD, people choose as if small-probability outcomes are more probable than they objectively are, and in DFE, people choose as if the same small-probability outcomes are less probable.
+More generally, in DFD, people choose as if small-probability outcomes are more probable than they objectively are, and in DFE, people choose as if the same small-probability outcomes are less probable.
 
 What causes the description-experience gap?
-A quite common notion is that of the mind being sensitive to the information provided by the small number of sampled outcomes that people tend to rely on in DFE [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
+A common notion is that of the mind being sensitive to the information provided by the small number of sampled outcomes that people tend to rely on in DFE [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
 Specifically, small *samples*---i.e., sets of sampled outcomes---often differ from descriptions in the information they actually provide about the prospects because they tend to underrepresent small-probability outcomes (Box \hyperlink{box}{1}, see also for illustrative purposes the `code example`, where the objective probability of outcome `5` is `.2`, and the sampled relative frequency is `.1`).
+This distortion of the sampled information (sampling error) is then assumed to carry over to the decision-making process, eventually causing, ceteris paribus, distinct choice patterns in DFD and DFE.
 \newline
@@
 
-\noindent
-This distortion of the sampled information (sampling error) is then assumed to carry over to the decision-making process, eventually causing distinct choice patterns in DFD and DFE.
-
-Yet, the description-experience gap might not be solely caused by the reliance on a small number of sampled outcomes in DFE and the associated sampling error [see also @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
-Rather, the specifics of the actual decision-making process, such as how the outcomes of the prospects of choice are sampled, integrated, and evaluated, might contribute to the gap.
-To this end, the current paper presents a model that sketches how the mind might exercise the capacity of making decisions from experience in the sampling paradigm, and examines the choice patterns that result from the modeled decision-making processes.
+Yet, peoples' reliance on a small number of sampled outcomes in DFE, and the associated sampling error, are presumably not the sole cause of the description-experience gap [see @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
+Rather, the specifics of the actual decision-making process---i.e, how the mind exercises the capacity of making decisions from experience as opposed to descriptions---might contribute to the gap.
+In experimental studies of DFE using the *sampling paradigm*, people can, as much as they want, sequentially sample the outcomes of two latent prospects according to their objective probabilities before making a final, consequential choice between the prospects [see @hertwigDescriptionexperienceGapRisky2009, see also Figure\ \@ref(fig:sampling-paradigm)].
+Because in the sampling paradigm people cannot rely on the descriptions of outcomes and probabilities to make a decision, but are required to learn about the prospects from experiential sampling of outcomes over time, the tasks involved in the decision-making process differ from those in DFD.
+That is, in order to model the process by which people arrive at the final choice in the sampling paradigm, one must explicate a number of assumptions concerning, in particular, the sampling process and the mind's operations on the sequence of sampled outcomes that are of no relevance to DFD whatsoever, e.g.: How the mind
+
+* decides when to switch between prospects during the sampling phase;
+
+* decides when to stop sampling;
+
+* integrates the information obtained from the sampled outcomes.
+
+To approach the above questions, this paper presents a couple of models that integrate two proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010] into the computational framework of sequential sampling models of decision-making [see, e.g., @markantModelingChoiceSearch2015].
+Sampling strategies [...].
+
+The current paper presents two models that sketch how the mind might exercise the capacity of making decisions from experience in the sampling paradigm, and examines the choice patterns that result from the modeled decision-making processes.
 More specifically, controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper investigates in a computational analysis whether and how the potential interplay of sampling and decision strategies shapes DFE and comes to imply choice patterns and functional forms of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
@@
 [...]
-
-To model the process by which people arrive at the final choice in the sampling paradigm, one must explicate a number of assumptions, e.g.:
-
-* How does the mind decide when to switch between prospects during the sampling phase?
-
-* How does the mind decide when to stop sampling?
-
-* How does the mind integrate and evaluate the information obtained from the sampled outcomes?
-
-To approach the above questions, this paper presents a couple of models that integrate two proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010] into the computational framework of sequential sampling models of decision-making [see, e.g., @markantModelingChoiceSearch2015].
 

### 2022-05-16 manuscript.Rmd
Update introduction

@@
 bibliography      : references.bib
-csl               : apa.csl
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
 
@@
 documentclass     : "apa7"
-output: papaja::apa6_pdf
+output            : papaja::apa6_pdf
 
@@
 Rather, the specifics of the actual decision-making process---i.e, how the mind exercises the capacity of making decisions from experience as opposed to descriptions---might contribute to the gap.
-In experimental studies of DFE using the *sampling paradigm*, people can, as much as they want, sequentially sample the outcomes of two latent prospects according to their objective probabilities before making a final, consequential choice between the prospects [see @hertwigDescriptionexperienceGapRisky2009, see also Figure\ \@ref(fig:sampling-paradigm)].
+In experimental studies of DFE using the *sampling paradigm*, people can, as much as they want, sequentially sample the outcomes of two latent prospects according to their objective probabilities before making a final, consequential choice between the prospects [see @hertwigDescriptionexperienceGapRisky2009, see also Fig.\ \@ref(fig:sampling-paradigm)].
 Because in the sampling paradigm people cannot rely on the descriptions of outcomes and probabilities to make a decision, but are required to learn about the prospects from experiential sampling of outcomes over time, the tasks involved in the decision-making process differ from those in DFD.
-That is, in order to model the process by which people arrive at the final choice in the sampling paradigm, one must explicate a number of assumptions concerning, in particular, the sampling process and the mind's operations on the sequence of sampled outcomes that are of no relevance to DFD whatsoever, e.g.: How the mind
+That is, in order to model the process by which people arrive at the final choice in the sampling paradigm, one must explicate a number of assumptions concerning, in particular, the sampling process and the mind's operations on the sequence of sampled outcomes, which are of no relevance to DFD whatsoever, e.g.: How the mind
 
@@
 
-To approach the above questions, this paper presents a couple of models that integrate two proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010] into the computational framework of sequential sampling models of decision-making [see, e.g., @markantModelingChoiceSearch2015].
-Sampling strategies [...].
-
-The current paper presents two models that sketch how the mind might exercise the capacity of making decisions from experience in the sampling paradigm, and examines the choice patterns that result from the modeled decision-making processes.
-More specifically, controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper investigates in a computational analysis whether and how the potential interplay of sampling and decision strategies shapes DFE and comes to imply choice patterns and functional forms of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
+\noindent
+The questions of interest are then how the mind solves these tasks and, subordinate to that,^[<!--Open footnote-->
+As van Rooij and Baggio [-@vanrooijTheoryTestHow2021] put it: "Only in the manner in which we postulate that
+such capacities [i.e., decision making] are exercised do our explanations of capacities come to imply effects [e.g., as-if underweighting of rare outcomes]" (p. 682, square brackets added).
+<!--Close footnote-->]
+whether this leads to choice patterns that are consistent with an as-if underweighting of rare outcomes pattern, irrespective of the existence or absence of sampling error.
+
+While approaching the above questions, the current paper focuses on the effects of the potential interplay between sampling and decisions strategies.
+Figure\ \@ref(fig:sampling-paradigm) displays what Hills and Hertwig [-@hillsInformationSearchDecisions2010] considered to be paradigmatic instances of both types of strategies. 
+Sampling strategies refer to the sequential pattern with which people sample outcomes from the two prospects over time.
+That is, in the sampling paradigm, people can decide without costs when to sample outcomes from which prospect and when to switch between them.
+They can do so entirely randomly, resulting in no discernible sequential sampling pattern, or they proceed more systematically.
+Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that people may either switch just once between prospects (comprehensive sampling) or after each sampled outcome (piecewise sampling).^[<!--Open footnote-->
+Note that in their analyses of empirical sampling data,  Hills and Hertwig [-@hillsInformationSearchDecisions2010] used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and acknowledged that "many [sampling] strategies will fall on the continuum in between [the two paradigmatic strategies]" (p.
+1788).
+<!--Close footnote-->]
+Decision strategies refer to the way people integrate the information obtained from the sampled outcomes in order to evaluate the prospects and make a corresponding decision.
+Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that people compare the prospects either on the basis of the means across all sampled outcomes (summary decision) or they compare two sampled outcomes---i.e., one from each prospect---over repeated rounds and choose the prospect that won the majority of comparisons (round-wise decision).
+In more general terms, whereas sampling strategies determine how the information about prospects are collected, decision strategies determine how the collected information are processed or transformed to arrive at a final choice.
+
+```{r sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
+knitr::include_graphics(path = "manuscript_files/sampling-paradigm.png")
+```
+
+To provide an explanation for the as-if underweighting of rare outcomes pattern and the related description-experience gap, Hills and Hertwig [-@hillsInformationSearchDecisions2010] suggested a systematic link between sampling and decision strategies.
+Specifically, they assumed that comprehensive sampling is associated with making summary decisions, while piecewise sampling is associated with making round-wise decisions.
+Since in round-wise decisions small-probability outcomes are predicted not to be considered in the majority of comparisons, such a coupling could indeed explain an as-if underweighting of rare events (see also Fig.\ \@ref(fig:sampling-paradigm), for illustrative purposes).
+
+Pointing to such a coupling of sampling and decision strategies, they found that a larger proportion choices of people who, on average, switched infrequently between prospects during the sampling phase were better predicted by a summary strategy (rather than a round-wise strategy), and that this predictive pattern reversed for people who switched frequently [but see @wulffHowShortLongrun2015].
+
+This paper presents a couple of models that integrate two proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010] into the computational framework of sequential sampling models of decision-making [see, e.g., @markantModelingChoiceSearch2015].
+More specifically, controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper seeks to investigate in a computational analysis whether and how the potential interplay of sampling and decision strategies shapes DFE and comes to imply choice patterns and functional forms of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
 CPT's value function is also considered in this paper.
@@
 <!-- Outline -->
-
-<!--
 The rest of the paper is structured as follows:
-In the first section, it is briefly discussed how DFE in the sampling paradigm differ from DFD in terms of the tasks involved in the decision-making process and thus the assumptions that must be made when modeling the respective process.
+In the first section, it is briefly discussed 
 In the section that follows, two previously proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010, see also below] are described.
@@
 Note that all materials, including the can be retrieved from the accompanying `GitHub repository`.
--->
 
@@
 (ref:sampling-paradigm) Possible Sampling and Decision Strategies in the Sampling Paradigm and Their Impact on the Final Choice
-
-```{r sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
-knitr::include_graphics(path = "manuscript_files/sampling-paradigm.png")
-```
 

### 2022-05-17 manuscript.Rmd
update introduction

@@
 
-keywords          : "risky choice, information sampling, evidence accumulation, cognitive modeling, cumulative prospect theory"
+keywords          : "risky choice, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
 wordcount         : ""
@@
 ```{r code-example, echo=TRUE}
-# define a prospect with two outcomes
-outcomes <- c(5, 0)
+# define prospect with two outcomes: 6 with 20%, 0 otherwise (80%)
+outcomes <- c(6, 0)
 probabilities <- c(.2, .8)
@@
 A common notion is that of the mind being sensitive to the information provided by the small number of sampled outcomes that people tend to rely on in DFE [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
-Specifically, small *samples*---i.e., sets of sampled outcomes---often differ from descriptions in the information they actually provide about the prospects because they tend to underrepresent small-probability outcomes (Box \hyperlink{box}{1}, see also for illustrative purposes the `code example`, where the objective probability of outcome `5` is `.2`, and the sampled relative frequency is `.1`).
+Specifically, small *samples*---i.e., sets of sampled outcomes---often differ from descriptions in the information they actually provide about the prospects because they tend to underrepresent small-probability outcomes (Box \hyperlink{box}{1}, see also for illustrative purposes the `code example`, where the objective probability of outcome `6` is `.2`, and the sampled relative frequency is `.1`).
 This distortion of the sampled information (sampling error) is then assumed to carry over to the decision-making process, eventually causing, ceteris paribus, distinct choice patterns in DFD and DFE.
@@
 Decision strategies refer to the way people integrate the information obtained from the sampled outcomes in order to evaluate the prospects and make a corresponding decision.
-Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that people compare the prospects either on the basis of the means across all sampled outcomes (summary decision) or they compare two sampled outcomes---i.e., one from each prospect---over repeated rounds and choose the prospect that won the majority of comparisons (round-wise decision).
-In more general terms, whereas sampling strategies determine how the information about prospects are collected, decision strategies determine how the collected information are processed or transformed to arrive at a final choice.
+Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that people compare the prospects either on the basis of the means across all sampled outcomes (summary integration/decision) or they compare two sampled outcomes---i.e., one from each prospect---over repeated rounds and choose the prospect that won the majority of such comparisons (round-wise integration/decision).
+In more general terms, whereas sampling strategies determine how the information about prospects are collected, decision strategies determine how the collected information are processed, or transformed, to arrive at a final choice.
 
@@
 Specifically, they assumed that comprehensive sampling is associated with making summary decisions, while piecewise sampling is associated with making round-wise decisions.
-Since in round-wise decisions small-probability outcomes are predicted not to be considered in the majority of comparisons, such a coupling could indeed explain an as-if underweighting of rare events (see also Fig.\ \@ref(fig:sampling-paradigm), for illustrative purposes).
-
-Pointing to such a coupling of sampling and decision strategies, they found that a larger proportion choices of people who, on average, switched infrequently between prospects during the sampling phase were better predicted by a summary strategy (rather than a round-wise strategy), and that this predictive pattern reversed for people who switched frequently [but see @wulffHowShortLongrun2015].
+Since in round-wise decisions small-probability outcomes are expected to be left unconsidered in the majority of comparisons---each of which is weighted equally---, such a coupling could translate to an as-if underweighting of rare events pattern, even if a large number of outcomes is sampled.
+That is, if the prospect that is more likely to produce a higher outcome most of the time does *not* also possess a higher EV, round-wise decisions are expected to cause deviations from the solutions of EV maximization that take the form of an as-if underweighting of rare outcomes pattern (see Fig.\ \@ref(fig:sampling-paradigm), for illustrative purposes).
+Pointing to the suggested coupling of sampling and decision strategies, Hills and Hertwig [-@hillsInformationSearchDecisions2010] found that a larger proportion of the choices of people who, on average, switched infrequently between prospects were better predicted by a summary strategy (rather than a round-wise strategy), and that this predictive pattern reversed for people who switched frequently.
+Moreover, simulating both round-wise and summary decisions on the basis of peoples' sampled outcomes, they showed that round-wise decisions led to a higher proportion of choices that are consistent with an as-if underweighting of rare outcomes.
+
+To summarize the preceding paragraphs: 
+Since small samples may distort the information about the properties of latent prospects, a great deal of research on the sampling paradigm has been invested into the question which factors affect how much people sample [see @wulffAdaptiveExplorationWhat2019, Table 7.2, for a recent summary of relevant factors and papers].
+Assuming that people proceed systematically when sampling outcomes, and that their sampling strategies are systematically related to decision strategies, Hills and Hertwig [-@hillsInformationSearchDecisions2010] emphasize that in order to understand how people make DFE and how this comes to imply certain choice patterns, one might need a richer understanding of peoples' sampling behavior.
+That is, not only we need to know how much outcomes are sampled, but also in what way they are sampled, and how this interplays with the way the obtained information is processed to evaluate the latent prospects.
+
+Yet, the presented approach invites objections, both theoretical and methodological.
+The following gaps and problems in Hills and Hertwig's [-@hillsInformationSearchDecisions2010] work stand out:
+
+1.
+*Lack of formal modeling/unstated theoretical commitments:* The authors offer a verbal description of their theoretical claim that sampling strategies are systematically linked to decision strategies.
+Yet, they do not provide a formal specification or computational implementation of their theory.
+Such a lack of formal, mathematical or computational modeling can, among others, hide gaps and inconsistencies in the theory [@guestHowComputationalModeling2021; @vanrooijPsychologicalModelsTheir2022].
+For instance, although the proposed links between sampling and decision strategies are used to explain the (non)occurrence of an as-if underweighting of rare outcomes pattern, no formal and complete accounts of the potential choice-generating mechanisms---which must contain the proposed links---are provided.
+One key characteristic of the sampling paradigm is that people can freely decide when to stop sampling.
+Thus, in order to be considered complete, models aiming to explain how the mind exercises the capacity of making DFE in the sampling paradigm must account for stopping.
+Theoretical frameworks that do so, e.g., sequential sampling models [e.g., @markantModelingChoiceSearch2015], may, however, make themselves assumptions about the decision-making process that constrain how such a proposed link between sampling and decision strategies can be
+Failing to explicitly spell out theoretical commitments and/or to formally model the decision-making process
+
+2.
+*Vague consideration of hybrid models:* In principal, the sampling and decision strategies, as proposed, are independent of each other and can be freely combined---i.e., each instance of a sampling strategy can be combined with each instance of a decision strategy.
+
+3. *Use of heuristic analysis methods:*
+
+4. *Strong analysis constraints:*
+
+<!-- Outline -->
+The current paper aims to address these four problems.
+The rest of the paper is structured as follows:
+In the first section, the current approach is described
 
@@
 
-<!-- Outline -->
-The rest of the paper is structured as follows:
-In the first section, it is briefly discussed 
-In the section that follows, two previously proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010, see also below] are described.
-It is discussed 
-[...]
 Thereafter, a simulation study is presented, where the proposed models are used to simulate the sampling and accumulation processes for a set of choices between a safe and a two-outcome prospect.

### 2022-05-17 manuscript.Rmd
Using latex code for figures to add figure notes

@@
 
-```{r sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
-knitr::include_graphics(path = "manuscript_files/sampling-paradigm.png")
-```
+\begin{figure}[t]
+\caption{Possible Sampling and Decision Strategies in the Sampling Paradigm and Their Impact on the Final Choice}
+\includegraphics{manuscript_files/sampling-paradigm} \label{fig:sampling-paradigm}
+\raggedright \textit{Note.} Add note
+\end{figure}
 
@@
 
-1.
-*Lack of formal modeling/unstated theoretical commitments:* The authors offer a verbal description of their theoretical claim that sampling strategies are systematically linked to decision strategies.
-Yet, they do not provide a formal specification or computational implementation of their theory.
+1. *Lack of formal modeling/unstated theoretical commitments:*
+The authors offer a verbal description of their theoretical claim that sampling strategies are systematically linked to decision strategies, but do not provide a formal specification or computational implementation of their claim.
+Moreover, although the proposed links between sampling and decision strategies are used to "explain" the (non)occurrence of an as-if underweighting of rare outcomes pattern, no formal and complete accounts of the potential choice-generating mechanisms---which must contain the proposed links---are provided.
 Such a lack of formal, mathematical or computational modeling can, among others, hide gaps and inconsistencies in the theory [@guestHowComputationalModeling2021; @vanrooijPsychologicalModelsTheir2022].
-For instance, although the proposed links between sampling and decision strategies are used to explain the (non)occurrence of an as-if underweighting of rare outcomes pattern, no formal and complete accounts of the potential choice-generating mechanisms---which must contain the proposed links---are provided.
-One key characteristic of the sampling paradigm is that people can freely decide when to stop sampling.
+For instance, one key characteristic of the sampling paradigm is that people can freely decide when to stop sampling.
 Thus, in order to be considered complete, models aiming to explain how the mind exercises the capacity of making DFE in the sampling paradigm must account for stopping.
-Theoretical frameworks that do so, e.g., sequential sampling models [e.g., @markantModelingChoiceSearch2015], may, however, make themselves assumptions about the decision-making process that constrain how such a proposed link between sampling and decision strategies can be
-Failing to explicitly spell out theoretical commitments and/or to formally model the decision-making process
-
-2.
-*Vague consideration of hybrid models:* In principal, the sampling and decision strategies, as proposed, are independent of each other and can be freely combined---i.e., each instance of a sampling strategy can be combined with each instance of a decision strategy.
+Theoretical frameworks that do so, e.g., sequential sampling models [e.g., @markantModelingChoiceSearch2015], make themselves assumptions about the decision-making process that may constrain how the a proposed link between sampling and decision strategies can be specified.
+Failing to explicitly spell out theoretical commitments and/or to formally model the decision-making process can later on
+
+2. *Vague consideration of hybrid models:*
+In principal, the sampling and decision strategies, as proposed, are independent of each other and can be freely combined---i.e., each instance of a sampling strategy can be combined with each instance of a decision strategy.
 

### 2022-05-17 manuscript.Rmd
Figures via latex expressions

@@
 authornote: |
- This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub repository`: https://github.com/linushof/sampling-in-dfe.
-The current version of the manuscript, created from the commit with the `hash `r repro::current_hash()``, is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
+ This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub` repository: https://github.com/linushof/sampling-in-dfe.
+The current version of the manuscript, created from the commit with the hash ``r repro::current_hash()``, is submitted as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
 Supervisors:
@@
 
-(ref:weighting-function) Possible Graphical Shapes of Goldstein and Einhorn's -@goldsteinExpressionTheoryPreference1987 Weighting Function
-
-```{r weighting-function, fig.cap="(ref:weighting-function)"}
+```{r weighting-function, include=FALSE}
 #compute images of weighting function (wf)
@@
 ```
+
+\begin{figure}[t]
+\caption{Possible Graphical Shapes of Goldstein and Einhorn's (\protect\hyperlink{ref-goldsteinExpressionTheoryPreference1987}{1987}) Weighting Function}
+\includegraphics{manuscript_files/figure-latex/weighting-function-1} \label{fig:weighting-function}
+\raggedright \textit{Note.} Add note
+\end{figure}
 
@@
 
-(ref:chain-length) Lengths of Information-Processing Chains
-
-```{r fig.cap="(ref:chain-length)", eval = FALSE}
+```{r chain-length, eval = FALSE}
 chain_lengths <- choices_absolute %>%
@@
 
-```{r chain-length, fig.cap="(ref:chain-length)", out.width="100%"}
-knitr::include_graphics(path = "manuscript_files/chain-lengths.png")
-```
+\begin{figure}[t]
+\caption{Lengths of Information-Processing Chains}
+\includegraphics[width=1\linewidth]{manuscript_files/chain-length} \label{fig:chain-length}
+\raggedright \textit{Note.} Add note
+\end{figure}
 
@@
 
-(ref:choice-rates-roundwise) Rates of False Risky and False Safe Choices in the Round-Wise Integration Model
-
-```{r choice-rates-roundwise, fig.cap="(ref:choice-rates-roundwise)"}
+```{r choice-rates-roundwise, include=FALSE}
 #prepare data
@@
 
-(ref:choice-rates-summary) Rates of False Risky and False Safe Choices in the Summary Integration Model
-
-```{r choice-rates-summary, fig.cap="(ref:choice-rates-summary)"}
+\begin{figure}[t]
+\caption{Rates of False Risky and False Safe Choices in the Round-Wise Integration Model}
+\includegraphics{manuscript_files/figure-latex/choice-rates-roundwise-1} \label{fig:choice-rates-roundwise}
+\raggedright \textit{Note.} Add note
+\end{figure}
+
+```{r choice-rates-summary, include=FALSE}
 #prepare data
@@
 
+\begin{figure}[t]
+\caption{Rates of False Risky and False Safe Choices in the Summary Integration Model}
+\includegraphics{manuscript_files/figure-latex/choice-rates-summary-1} \label{fig:choice-rates-summary}
+\raggedright \textit{Note.} Add note
+\end{figure}
+
 ### Simulation-Implied Cumulative Prospect Theory
@@
 
-(ref:weighting-parameters) Parameter Estimates of the Weighting Function
-
-```{r weighting-parameters, fig.cap="(ref:weighting-parameters)"}
+```{r weighting-parameters, include=FALSE}
 
@@
 
+\begin{figure}[t]
+\caption{Parameter Estimates of the Weighting Function}
+\includegraphics{manuscript_files/figure-latex/weighting-parameters-1} \label{fig:weighting-parameters}
+\raggedright \textit{Note.} Add note
+\end{figure}
+
 Figure\ \@ref(fig:sensitivity-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$.
@@
 
-(ref:sensitivity-parameters) Parameter Estimates of the Outcome and Choice Sensitivity Parameter
-
-```{r sensitivity-parameters, fig.cap="(ref:sensitivity-parameters)"}
+```{r sensitivity-parameters, include=FALSE}
 
@@
 
+\begin{figure}[t]
+\caption{Parameter Estimates of the Outcome and Choice Sensitivity Parameter}
+\includegraphics{manuscript_files/figure-latex/sensitivity-parameters-1} \label{fig:sensitivity-parameters}
+\raggedright \textit{Note.} Add note
+\end{figure}
+
 Figure\ \@ref(fig:function-forms) displays the resulting graphical shapes of the weighting and value function.
 
-(ref:function-forms) Estimated Graphical Shape of the Weighting and Value Function
-
-```{r function-forms, fig.cap="(ref:function-forms)"}
+```{r function-forms, include=FALSE}
 
@@
 
+\begin{figure}[t]
+\caption{Estimated Graphical Shape of the Weighting and Value Function}
+\includegraphics{manuscript_files/figure-latex/function-forms-1} \label{fig:function-forms}
+\raggedright \textit{Note.} Add note
+\end{figure}
+
 # Discussion
@@
 
+# Acknowledgements
+
+\newpage
+
 # References

### 2022-05-18 manuscript.Rmd
Update Introduction (Hills & Hertwig critique)

@@
 A common notion is that of the mind being sensitive to the information provided by the small number of sampled outcomes that people tend to rely on in DFE [see @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004; @hertwigDecisionsExperienceWhy2010; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
-Specifically, small *samples*---i.e., sets of sampled outcomes---often differ from descriptions in the information they actually provide about the prospects because they tend to underrepresent small-probability outcomes (Box \hyperlink{box}{1}, see also for illustrative purposes the `code example`, where the objective probability of outcome `6` is `.2`, and the sampled relative frequency is `.1`).
+Specifically, small samples---i.e., sets of sampled outcomes---often differ from descriptions in the information they actually provide about the prospects because they tend to underrepresent small-probability outcomes (Box \hyperlink{box}{1}, see also for illustrative purposes the `code example`, where the objective probability of outcome `6` is `.2`, and the sampled relative frequency is `.1`).
 This distortion of the sampled information (sampling error) is then assumed to carry over to the decision-making process, eventually causing, ceteris paribus, distinct choice patterns in DFD and DFE.
@@
 Assuming that people proceed systematically when sampling outcomes, and that their sampling strategies are systematically related to decision strategies, Hills and Hertwig [-@hillsInformationSearchDecisions2010] emphasize that in order to understand how people make DFE and how this comes to imply certain choice patterns, one might need a richer understanding of peoples' sampling behavior.
-That is, not only we need to know how much outcomes are sampled, but also in what way they are sampled, and how this interplays with the way the obtained information is processed to evaluate the latent prospects.
-
-Yet, the presented approach invites objections, both theoretical and methodological.
-The following gaps and problems in Hills and Hertwig's [-@hillsInformationSearchDecisions2010] work stand out:
-
-1. *Lack of formal modeling/unstated theoretical commitments:*
-The authors offer a verbal description of their theoretical claim that sampling strategies are systematically linked to decision strategies, but do not provide a formal specification or computational implementation of their claim.
-Moreover, although the proposed links between sampling and decision strategies are used to "explain" the (non)occurrence of an as-if underweighting of rare outcomes pattern, no formal and complete accounts of the potential choice-generating mechanisms---which must contain the proposed links---are provided.
-Such a lack of formal, mathematical or computational modeling can, among others, hide gaps and inconsistencies in the theory [@guestHowComputationalModeling2021; @vanrooijPsychologicalModelsTheir2022].
+That is, not only we need to know how much outcomes are sampled, but also in what way they are sampled, and how this affects the way the obtained information is processed to evaluate the latent prospects.
+
+While offering a novel, convincing inroad into the broader question how sampling and information-processing can act together to shape DFE in environments where people can sample without costs,^[<!--Open footnote-->
+Meaning that people do not gain/loose the amount of each sampled outcome. Of course, sampling implies other costs, such as time and cognitive capacities.
+<!--Close footnote-->]
+Hills and Hertwig's [-@hillsInformationSearchDecisions2010] work invites some objections, both theoretical and methodological.
+The following gaps and problems stand out:
+
+1. *No formal modeling/unstated theoretical commitments:*
+The authors provide a verbal description of their theoretical claims, but no formal specification or computational implementation thereof.
+That is, they claim that sampling strategies are systematically linked to decision strategies, and that the proposed links can explain the (non)occurrence of an as-if underweighting of rare outcomes pattern.
+Yet, no formal and complete accounts of the potential choice-generating mechanisms---which must contain the proposed links---are offered.
+Such a lack of mathematical and/or computational modeling can, among others, hide needed auxiliary assumptions and potential gaps and inconsistencies in the theory [@guestHowComputationalModeling2021; @vanrooijPsychologicalModelsTheir2022].
 For instance, one key characteristic of the sampling paradigm is that people can freely decide when to stop sampling.
 Thus, in order to be considered complete, models aiming to explain how the mind exercises the capacity of making DFE in the sampling paradigm must account for stopping.
-Theoretical frameworks that do so, e.g., sequential sampling models [e.g., @markantModelingChoiceSearch2015], make themselves assumptions about the decision-making process that may constrain how the a proposed link between sampling and decision strategies can be specified.
-Failing to explicitly spell out theoretical commitments and/or to formally model the decision-making process can later on
-
-2. *Vague consideration of hybrid models:*
-In principal, the sampling and decision strategies, as proposed, are independent of each other and can be freely combined---i.e., each instance of a sampling strategy can be combined with each instance of a decision strategy.
+However, theoretical frameworks and their model members that do so, e.g., sequential sampling models [e.g., @markantModelingChoiceSearch2015], make their own assumptions about the decision-making process that not only have implications for what choice data is expected, but may also constrain how the proposed link between sampling and decision strategies can plausibly be integrated in a given framework (see model specifications/implementations in this paper).
+Assuming that "every scientific output is model- and theory-laden (i.e., contains theoretical and modeling commitments)" [@guestHowComputationalModeling2021, p.
+5], not explicitly spelling out such commitments and/or formally modeling the respective decision-making process reduces (at least) the clarity of the theoretical claims and everything that follows in the scientific inference process.
+
+2. *No systematic consideration of intermediate and hybrid models:*
+In principal, the sampling and decision strategies, as proposed, can be combined without constraints---i.e., each instance of a sampling strategy can be combined with each instance of a decision strategy.
+Moreover, the discussed sampling strategies (comprehensive and piecewise sampling) are considered paradigmatic not in the sense that people are expected to adopt either one or the other sampling strategy, but in the sense that they are the ends of a continuum and that many people are expected to adopt strategies that fall in between these two (see Fig.\ \@ref(fig:sampling-paradigm)).
+Focusing only on the proposed links between sampling and decision strategies, the authors do not discuss the potential implications of either one of these points for the resulting choice patterns.
+That is, the presented work does not systematically consider the potential interplay between sampling and decision strategies and its effects.
+In defense, one might object that the decision strategies determine how the prospects are evaluated on the basis of the sampled outcomes, and thus, once a given decision strategy is adopted, the sampling strategy upfront has no more impact on the final choice.
+In other words, sampling strategies may alter which decision strategies are used, but they do not alter how a given decision strategy evaluates a prospect.
+But this would be a superficial and vulnerable argument for reasons that become obvious when trying to specify or implement a plausible model of the decision-making process.
+For instance, if people do not exactly follow the piecewise sampling strategy, one might still be willing to allow for the adoption of a round-wise decision strategy and, in order to make this go through, assume that a comparison-round may encompass more than one outcome sampled from each prospect.
+In this case, however, sampling strategies can have a severe impact on the evaluation of prospects because they alter the size of the samples that a round encompasses (see analyses in this paper).
+One may otherwise waive the assumption that a comparison-round encompasses more than one outcome per prospect, but this can cause the decision-making process to take a form that is fundamentally different from how it might have been perceived---at least implicitly according to unstated theoretical commitments---when only the paradigmatic instances were considered.
+In sum, to understand whether and how sampling and decision strategies act together to shape DFE, one should not only explicitly model their links, but also consider their interplay more broadly and systematically.
 
 3. *Use of heuristic analysis methods:*
-
-4. *Strong analysis constraints:*
+[...]
+For reasons that can be found in Regenwetter and Robinson's [-@regenwetterConstructbehaviorGapBehavioral2017] rigorous work,
+
+4. *Narrow scope of analysis:*
 
 <!-- Outline -->
-The current paper aims to address these four problems.
+The current paper aims to address the outlined problems and thereby to extend and improve the work of Hills and Hertwig [@hillsInformationSearchDecisions2010].
 The rest of the paper is structured as follows:

### 2022-05-18 manuscript.Rmd
Update introduction

@@
 One may otherwise waive the assumption that a comparison-round encompasses more than one outcome per prospect, but this can cause the decision-making process to take a form that is fundamentally different from how it might have been perceived---at least implicitly according to unstated theoretical commitments---when only the paradigmatic instances were considered.
-In sum, to understand whether and how sampling and decision strategies act together to shape DFE, one should not only explicitly model their links, but also consider their interplay more broadly and systematically.
+In sum, to understand whether and how sampling and decision strategies act together to shape DFE, one should not only explicitly model their links, but also consider their interplay broadly and systematically.
 
 3. *Use of heuristic analysis methods:*
+The empirical re-analyses relies on various heuristic methods to assess whether the observed choices are consistent with the claimed links between sampling and decision strategies and their impact on the as-if weighting of rare events pattern.
+For instance, aggregated data over participants and choice problems is used to compare, within and between sampling strategies, the proportions of choices that are consistent with the predictions of the decision strategies and an as-if underweighting of rare outcomes.
+In addition, to obtain indicators for the applied sampling strategies, each participant's mean switching frequency across all choice problems was calculated and a median split was used to identify infrequently and frequently switching people, supposedly indicating comprehensive and piecewise sampling, respectively.
+While acknowledging that existing data was used, such heuristic methods can be problematic, e.g., because they can cause a construct-behavior gap where inferences from the data to the tested theory, although statistically sound, become logically invalid.
+@regenwetterConstructbehaviorGapBehavioral2017 show that ...
+For example, aggregate data may ignore potential individual differences and heterogeneity within people, which may be permitted by a theory.
+Also, aggregating across choice problems and using the frequent vs. infrequent switchers render confuses process vs. individual trait.
+Moreover, sampling error and the undersampling of small-probability outcomes is only accounted for to the extent that choice trials in which small-probability outcomes were not sampled are excluded.
+This does not control for systematic distortions.
+
+4. *Narrow scope of analysis:*
 [...]
-For reasons that can be found in Regenwetter and Robinson's [-@regenwetterConstructbehaviorGapBehavioral2017] rigorous work,
-
-4. *Narrow scope of analysis:*
 
 <!-- Outline -->
-The current paper aims to address the outlined problems and thereby to extend and improve the work of Hills and Hertwig [@hillsInformationSearchDecisions2010].
+The current paper aims to address the outlined problems.
 The rest of the paper is structured as follows:

### 2022-05-19 manuscript.Rmd
update critique hills and hertwig (heuristic methods and scope)

@@
  This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub` repository: https://github.com/linushof/sampling-in-dfe.
-The current version of the manuscript, created from the commit with the hash ``r repro::current_hash()``, is submitted as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
+The current version of the manuscript, created from the commit with the hash ``r repro::current_hash()``, is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
 Supervisors:
@@
 While acknowledging that existing data was used, such heuristic methods can be problematic, e.g., because they can cause a construct-behavior gap where inferences from the data to the tested theory, although statistically sound, become logically invalid.
-@regenwetterConstructbehaviorGapBehavioral2017 show that ...
-For example, aggregate data may ignore potential individual differences and heterogeneity within people, which may be permitted by a theory.
-Also, aggregating across choice problems and using the frequent vs. infrequent switchers render confuses process vs. individual trait.
-Moreover, sampling error and the undersampling of small-probability outcomes is only accounted for to the extent that choice trials in which small-probability outcomes were not sampled are excluded.
-This does not control for systematic distortions.
-
-4. *Narrow scope of analysis:*
-[...]
-
-<!-- Outline -->
-The current paper aims to address the outlined problems.
+In a rigorous analysis, @regenwetterConstructbehaviorGapBehavioral2017 demonstrate how the use of aggregate data and heuristic scoring rules, e.g., counting the proportion of correct choice predictions across problems and people, lead at least to hard-to-interpret inferences about individuals' as-if weighting patterns and the description-experience gap.
+One can alleviate such risks by taking heterogeneity between individuals into account and modeling the as-if weighting more explicitly.
+Also, the averaging of switching frequencies across choice problems to group into frequent and infrequent switchers can be falsely interpreted as if sampling strategies are more a characteristic of the decision maker than of the sampling process.
+Finally, sampling error is only controlled for to the extent that choice trials in which small-probability outcomes were not sampled at least once are excluded from the analyses.
+This still leaves room for the sampled relative frequencies to deviate from the latent objective probabilities.
+
+4. *No discussion of choice problems:*
+Assuming representative sampled frequencies, summary and round-wise decisions only predict different choices, if the prospect with the larger EV is not also more likely to produce a higher outcome most of the time ((see Fig.\ \@ref(fig:sampling-paradigm)).
+In consequence, the structure of the choice problems---i.e, whether a small-probability outcome exists and how desirable it is---can quite dramatically shape how the (interplay of) strategies differ in the choices and as-if weighting patterns they produce.
+Focusing only on problems of such a structure may provide a parsimonious but narrow-in-scope interpretation.
+
+The current paper aims to extend the work of @hillsInformationSearchDecisions2010 and to address the outlined problems.
 The rest of the paper is structured as follows:
@@
 The inputs to DFE are then the realizations of the random variables in (6).
-
-[...]
-
-# Sampling and Decision Strategies
-
-Specifically, @hillsInformationSearchDecisions2010 argued that one contributing factor to the description-experience gap might be a potential link between what they considered two paradigmatic sampling and decision strategies (see Figure\ \@ref(fig:sampling-paradigm)).
-That is, the authors assumed that in the sampling paradigm, people either switch prospects after each sampled outcome (piecewise sampling) to compare single outcomes over repeated rounds (round-wise decision), or they switch just once between prospects (comprehensive sampling) and make only one comparison between the means across all sampled outcomes (summary decision).
-In fact, @hillsInformationSearchDecisions2010 provided tentative evidence for such a coupling of sampling and decision strategies by finding that the choices of people who switched frequently between prospects during the sampling phase were better predicted by a round-wise strategy (rather than a summary strategy), and that this predictive pattern reversed for people who switched infrequently.^[<!--Open footnote-->
-Note that in their analyses of empirical sampling data,  @hillsInformationSearchDecisions2010 used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and acknowledged that "many [sampling] strategies will fall on the continuum in between [the two paradigmatic strategies]" (p.
-1788).
-<!--Close footnote-->]
-Using the round-wise strategy may translate to an as-if underweighting of rare events pattern and the description-experience gap because the strategy selects the prospect that wins a majority of comparisons, while small-probability outcomes are predicted not to be considered in most of these comparisons.
-
-(ref:sampling-paradigm) Possible Sampling and Decision Strategies in the Sampling Paradigm and Their Impact on the Final Choice
-
-<!-- Critique -->
 

### 2022-05-19 manuscript.Rmd
update section 1: sequential sampling framework

@@
 \newline
+(ref:references-box-1) @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015; @hertwigDecisionsExperienceEffect2004; @erevChoicePredictionCompetition2010; @plonskyRelianceSmallSamples2015; @erevAnomaliesForecastsDescriptive2017
 
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \caption{Possible Sampling and Decision Strategies in the Sampling Paradigm and Their Impact on the Final Choice}
 \includegraphics{manuscript_files/sampling-paradigm} \label{fig:sampling-paradigm}
-\raggedright \textit{Note.} Add note
+\raggedright \textit{Note.} In the sampling paradigm, people are offered the choice between at least two prospects (here: violet vs.
+orange), whose exact properties (outcomes and probabilities) remain hidden.
+To learn about the properties, people can, as much as they want, sample the prospects' outcomes according to their probabilities.
+Sampling strategies: Refer to the sequential pattern with which people sample the outcomes from both prospects over time.
+People may switch infrequently (comprehensive sampling) or frequently (piecewise sampling) or something in between.
+Decision strategies: Refer to the way people integrate the sampled outcomes in order to evaluate the prospects.
+People may integrate all outcomes stemming from the same prospect in order to compute and compare summary scores (summary integration/decision); or they integrate and compare outcomes of the two prospects over repeated rounds (round-wise integration/decision).
 \end{figure}
@@
 4. *No discussion of choice problems:*
-Assuming representative sampled frequencies, summary and round-wise decisions only predict different choices, if the prospect with the larger EV is not also more likely to produce a higher outcome most of the time ((see Fig.\ \@ref(fig:sampling-paradigm)).
+Assuming representative sampled frequencies, summary and round-wise decisions only predict different choices, if the prospect with the larger EV is not also more likely to produce a higher outcome most of the time (see Fig.\ \@ref(fig:sampling-paradigm)).
 In consequence, the structure of the choice problems---i.e, whether a small-probability outcome exists and how desirable it is---can quite dramatically shape how the (interplay of) strategies differ in the choices and as-if weighting patterns they produce.
@@
 The rest of the paper is structured as follows:
-In the first section, the current approach is described
-
-This paper presents a couple of models that integrate two proposed sampling and decision strategies [see @hillsInformationSearchDecisions2010] into the computational framework of sequential sampling models of decision-making [see, e.g., @markantModelingChoiceSearch2015].
-More specifically, controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper seeks to investigate in a computational analysis whether and how the potential interplay of sampling and decision strategies shapes DFE and comes to imply choice patterns and functional forms of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
+In the first section, the current approach and its theoretical commitments are briefly outlined.
+The paper starts from the proposition that systematic choices in DFE must be based on the assessment of differences in the latent properties of prospects (e.g., differences in EV or differences in the probability to produce a higher outcome most of the time).
+Sequential sampling models of decision making are considered as a theoretical framework that can be used to explain how the mind samples and accumulates evidence about such differences over time, and---importantly---how the mind stops sampling once an evidence threshold is reached.
+In the section that follows, two models are specified, each of which integrates the continuum of sampling strategies and one of the proposed decision strategies into the computational framework of sequential sampling models.
+The expected behavior of the models are outlined.
+Thereafter, a simulation study is presented, where the proposed models are used to simulate the sampling and accumulation processes for a set of choices between a safe and a two-outcome prospect, the latter of which may or may not possess a small-probability outcome of different rank/desirability.
+Controlling for sampling error---i.e., considering the sampled relative frequencies rather than the latent objective probabilities---, this paper then seeks to investigate in a computational analysis whether and how the potential interplay of sampling and decision strategies shapes DFE and comes to imply choice patterns and functional forms of cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992] that are consistent with an as-if underweighting of rare outcomes pattern.^[<!--Open footnote-->
 CPT's value function is also considered in this paper.
@@
 <!--Close footnote-->]
-
-Thereafter, a simulation study is presented, where the proposed models are used to simulate the sampling and accumulation processes for a set of choices between a safe and a two-outcome prospect.
-Considering choice rates and parameter estimates of CPT, the computational analysis shows that ... which translate to characteristic patterns in the psychoeconomic functions of CPT.
+It is shown that within a sequential sampling framework, the interplay of sampling and integration/decision strategies produces systematically different choice patterns that depend on the structure of the choice problems and translate to distinct signatures in CPT's weighting and value function.
+The simulated choices and estimated CPT parameters can be understood as model-implied data and data models, which remain to be tested against empirical data.
+The paper closes with a brief discussion and conclusion.
+Note that all materials---i.e., code and data---underlying this paper, including instructions on how to reproduce this manuscript, can be retrieved from the accompanying `GitHub` repository.
+
+# Sampling and Decision Strategies Within a Sequential Sampling Framework
+
+Because there is an uncountable number of decisions people confront in their daily life, behavioral decision research routinely abstracts from choices between particular alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
+Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.
+These fundamental properties are considered the $n$ possible outcomes of a choice alternative, denoted as $x_1, ..., x_n$, and the probabilities with which these outcomes occur following the choice of the alternative, denoted as $p_X(x_1), ..., p_X(x_n)$.
+That is, each choice alternative that is fully described by a set of outcome-probability pairs, $\{(x_i, p_X(x_i))\}_{i \in \{1, ..., n\}}$, satisfying $\sum_{i = 1}^n p_X(x_i) = 1$, is a prospect.
+It is only through these fundamental properties, or combinations thereof, that any necessary distinction between the prospects can be made.
+Hence, systematic---as opposed to random---choices between prospects must be based on the assessment of differences in their properties.
+
+Rarely in peoples' daily life, the information provided about the prospects take the form of explicit and complete descriptions of all their outcome-probability pairs.
+In such rare cases, people would make DFD and can---strongly simplified---proceed by selecting a property or combinations thereof to assess differences among the prospects and make a respective choice.
+In stark contrast and rather often, people are required to make DFE, where the mind can learn about the latent properties only by "experiential sampling [of outcomes] over time" [@hertwigDescriptionexperienceGapRisky2009, p.
+517, square bracket added].
+The sampling paradigm is just one paradigm that can be used to study DFE and allows people to sample the prospects' outcomes without costs and without constraints regarding the sequential pattern and the amount of sampled outcomes.
+
+How do people arrive at a final choice in the sampling paradigm? 
+Sequential sampling models of decision making under risk (DFD) and/or uncertainty [DFE, see @markantModelingChoiceSearch2015, who explicitly consider DFE and the sampling paradigm; see also, e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993] assume that the decision-making process takes the form of an accumulation of evidence for the prospects over time.
+The process is assumed to stop---i.e., a choice is made---once the accumulated evidence for one of the prospects reaches a certain threshold.
+More specifically, for DFE, it is assumed that the outcomes of prospects are sequentially sampled and integrated into dynamic decision variables and that a choice is made once the value of a decision variable exceeds a threshold.
+How exactly this integration is carried out and what the value of a dynamic decision variable represents, is a theoretical question---and thus a matter of the exact specification of the model---largely concerning the way .
+
+This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DFE, and has shown to explain some of the robust deviations from EV maximization [see @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993], including the as-if underweighting of rare outcomes in the sampling paradigm [see @markantModelingChoiceSearch2015].
+Moreover, these models implement speed-accuracy trade-offs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more (less) accurate but slower (faster) choices for high (low) thresholds.
+
 [...]
-The paper closes with a discussion and conclusion.
-Note that all materials, including the can be retrieved from the accompanying `GitHub repository`.
-
-# Explaining Decision Making in the Sampling Paradigm
-
-<!-- Formal Definition of Prospects / Notation -->
-
-<!--Since there is an uncountable number of choices people confront in their daily life, behavioral decision research routinely abstracts from choices between particular alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.-->
-With the choice between at least two prospects, behavioral decision research studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.
-These fundamental properties are considered the $n$ possible outcomes of a choice alternative, denoted by the set $\{x_i\}_{i \in \{1, ..., n\}}$, and the probabilities with which these outcomes occur following the choice of the alternative, denoted by the set $\{p(x_i)\}$.
-That is, each choice alternative that is fully described by a set of outcome-probability pairs $\{(x_i, p(x_i))\}$ satisfying $\sum_{i = 1}^n p(x_i) = 1$ is a prospect.
-Note that a prospect can be conceptualized as the distribution $P$ of a discrete random variable $X$, where each outcome in $\{x_i\}$ denotes a possible value that $X$ can take.
-In other words, then, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
-$$
-\{P^1, ... , P^k\}
-\; .
-\tag{1}
-$$
-<!-- Modeling steps and assumptions -->
-
-Since it is only through their fundamental properties, or combinations thereof, that any distinction between the prospects can be made, systematic---as opposed to random---choices between prospects must be based on the assessment of differences in their properties.
-However, only rarely in peoples' daily life, the inputs to the decision-making process take the form of explicit descriptions of all outcome-probability pairs.
-In such cases, people would make DFD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
-Yet, rather often, people make DFE, where the mind can learn about the latent properties only by experiential sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
-Accordingly, for the choice between $1, ..., k$ prospects, the inputs to the decision-making process are generated by a set of prospect-specific stochastic processes
-$$
-\{\{X^1_t\}, ... , \{X^k_t\}\}
-\; ,
-\tag{6}
-$$
-where each $\{X_{t}\}_{t \in \mathbb N}$ is a collection of independent and identically distributed (i.i.d.) random variables.^[Note that it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p.
-660].
-However, in the sampling paradigm, i.i.d.
-random variables are commonly assumed.]
-The inputs to DFE are then the realizations of the random variables in (6).
+
+Yet, there are several distinct properties that can be used to assess differences between the prospects, among them the EV, for which the summary decision strategy is indicative, and the probability to produce a higher outcome most of the time, for which the round-wise decision strategy is indicative [@hillsInformationSearchDecisions2010; see also @wulffHowShortLongrun2015].
+Respectively, in the following, both decision strategies are implemented into a common sampling and accumulation model to demonstrate how the mind may rely on different sampling strategies to alter the degree to which evidence is accumulated for differences in either one of these properties.
+More specifically, the proposed model accumulates the outcomes obtained from a sequence of comparisons between sample means, with the size of the samples underlying each mean comparison tending to be large (small) for low (high) switching probabilities.
+Accordingly, whereas the decision variables of the model capture how many comparisons a prospect has won, the unfolding accumulation process more closely resembles the summary strategy for low switching probabilities and the round-wise strategy for high switching probabilities.
 
 [...]
-
-# Current Approach: Sampling Strategies and the Accumulation of Different Types of Evidence
-
-<!-- How to overcome the problems + Evidence accumulation -->
 
@@
 
-The mind may use these realizations---i.e., the sampled outcomes---to first infer the latent properties and then proceed by selecting a property, or combinations thereof, to assess differences among the prospects and make a respective choice.
-However, the mind may also approximate such a process by directly accumulating evidence about the differences in latent properties from the sampled outcomes.
-To this end, sequential sampling models of decision making [e.g., @busemeyerDecisionFieldTheory1993] assume that the outcomes of prospects are sequentially sampled and integrated into dynamic decision variables and that a choice is made once a decision variable exceeds a threshold in favor for one of the prospects.
-This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DFE, and has shown to explain some of the robust deviations from EV maximization [see @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993], including the as-if underweighting of rare outcomes in the sampling paradigm [see @markantModelingChoiceSearch2015].
-Moreover, these models implement speed-accuracy trade-offs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more (less) accurate but slower (faster) choices for high (low) thresholds.
-
-Yet, there are several distinct properties that can be used to assess differences between the prospects, among them the EV, for which the summary decision strategy is indicative, and the probability to produce a higher outcome most of the time, for which the round-wise decision strategy is indicative [@hillsInformationSearchDecisions2010; see also @wulffHowShortLongrun2015].
-Respectively, in the following, both decision strategies are implemented into a common sampling and accumulation model to demonstrate how the mind may rely on different sampling strategies to alter the degree to which evidence is accumulated for differences in either one of these properties.
-More specifically, the proposed model accumulates the outcomes obtained from a sequence of comparisons between sample means, with the size of the samples underlying each mean comparison tending to be large (small) for low (high) switching probabilities.
-Accordingly, whereas the decision variables of the model capture how many comparisons a prospect has won, the unfolding accumulation process more closely resembles the summary strategy for low switching probabilities and the round-wise strategy for high switching probabilities.
-
-[...]
-
-## Models
+# Models
+
+<!--Note that a prospect can be conceptualized as the distribution $P$ of a discrete random variable $X$, where each outcome in $\{x_i\}$ denotes a possible value that $X$ can take.
+In other words, then, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
+$$
+\{P^1, ... , P^k\}
+\; .
+\tag{1}
+$$
+-->
 
@@
 
-### Round-Wise Integration Model
+## Round-Wise Integration Model
 
@@
 
-### Summary Integration Model
+## Summary Integration Model
 
@@
 
-# Model Predictions
+# What Model Behaviors Are Expected?
 

### 2022-05-19 manuscript.Rmd
updates section 1: sequential sampling framework / outlook

@@
 Rarely in peoples' daily life, the information provided about the prospects take the form of explicit and complete descriptions of all their outcome-probability pairs.
-In such rare cases, people would make DFD and can---strongly simplified---proceed by selecting a property or combinations thereof to assess differences among the prospects and make a respective choice.
+In such rare cases, people would make DFD and can---strongly simplified---directly proceed by selecting a property or combinations thereof to assess differences among the prospects and make a respective choice.
 In stark contrast and rather often, people are required to make DFE, where the mind can learn about the latent properties only by "experiential sampling [of outcomes] over time" [@hertwigDescriptionexperienceGapRisky2009, p.
 517, square bracket added].
-The sampling paradigm is just one paradigm that can be used to study DFE and allows people to sample the prospects' outcomes without costs and without constraints regarding the sequential pattern and the amount of sampled outcomes.
+The sampling paradigm is just one paradigm that can be used to study DFE experimentally and allows people to sample the prospects' outcomes without costs and without constraints regarding the sequential pattern and the amount of sampled outcomes.
 
@@
 Sequential sampling models of decision making under risk (DFD) and/or uncertainty [DFE, see @markantModelingChoiceSearch2015, who explicitly consider DFE and the sampling paradigm; see also, e.g., @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993] assume that the decision-making process takes the form of an accumulation of evidence for the prospects over time.
-The process is assumed to stop---i.e., a choice is made---once the accumulated evidence for one of the prospects reaches a certain threshold.
+The process is assumed to stop---i.e., a choice is made---once the accumulated evidence for one of the prospects reaches an evidence threshold.
 More specifically, for DFE, it is assumed that the outcomes of prospects are sequentially sampled and integrated into dynamic decision variables and that a choice is made once the value of a decision variable exceeds a threshold.
-How exactly this integration is carried out and what the value of a dynamic decision variable represents, is a theoretical question---and thus a matter of the exact specification of the model---largely concerning the way .
-
-This class of process models thereby provides an algorithmic link between the actual sampling process and the choices in DFE, and has shown to explain some of the robust deviations from EV maximization [see @bhatiaSequentialSamplingParadoxes2014; @busemeyerDecisionFieldTheory1993], including the as-if underweighting of rare outcomes in the sampling paradigm [see @markantModelingChoiceSearch2015].
-Moreover, these models implement speed-accuracy trade-offs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more (less) accurate but slower (faster) choices for high (low) thresholds.
-
-[...]
-
-Yet, there are several distinct properties that can be used to assess differences between the prospects, among them the EV, for which the summary decision strategy is indicative, and the probability to produce a higher outcome most of the time, for which the round-wise decision strategy is indicative [@hillsInformationSearchDecisions2010; see also @wulffHowShortLongrun2015].
+How exactly this integration is carried out and what the value of a dynamic decision variable represents, is a theoretical question---and thus a matter of the exact specification of the model---largely concerned with the way the prospects are assumed to be evaluated.
+Depending on the integration and evaluation mechanisms they assume, the member models of the sequential sampling framework have been shown to explain some of the robust deviations from EV maximization, including the as-if underweighting of rare outcomes in the sampling paradigm [@markantModelingChoiceSearch2015].
+Moreover, these models implement speed-accuracy trade-offs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more accurate but slower choices for high thresholds, and vice versa.
+
+The current paper commits to the core assumptions of the sequential sampling framework and uses its flexibility regarding the exact mechanisms of sampling, integration, and evaluation to incorporate the idea of sampling and decision strategies, including their interplay.
+The two models presented below, one assuming an integration and evaluation mechanism resembling the round-wise strategy, the other assuming mechanisms resembling the summary strategy, offer a formal route to explore the potential interplay between sampling and integration/decision strategies, and their effects on the choice behavior.
+The sequential sampling framework is chosen as a modeling outlet not only because it makes parsimonious assumptions and has assembled a good *"track record"* [cf.
+@meehlAppraisingAmendingTheories1990] by explaining and predicting actual choice behavior, but primarily because it makes explicit a core part of the computational problem the mind is trying to solve:
+in order to make systematic choices, the mind must assess differences in latent properties.
+And in accumulating evidence for and against propsects, what should the mind accumulate evidence for if not such differences?
+round-wise and summary decisions are both indicative for distinct properties the expected value and the probability to produce a higher outcome most of the time.
+The remainder of the paper discusses and demonstrates in a simulation, how sampling and decision strategies as well as thresholds can act together to alter the degree and the accuracy with which these differences are assessed.
+
+<!--Yet, there are several distinct properties that can be used to assess differences between the prospects, among them the EV, for which the summary decision strategy is indicative, and the probability to produce a higher outcome most of the time, for which the round-wise decision strategy is indicative [@hillsInformationSearchDecisions2010; see also @wulffHowShortLongrun2015].
 Respectively, in the following, both decision strategies are implemented into a common sampling and accumulation model to demonstrate how the mind may rely on different sampling strategies to alter the degree to which evidence is accumulated for differences in either one of these properties.
@@
 Accordingly, whereas the decision variables of the model capture how many comparisons a prospect has won, the unfolding accumulation process more closely resembles the summary strategy for low switching probabilities and the round-wise strategy for high switching probabilities.
-
-[...]
 
@@
 Notably, in this case, small-probability outcomes are predicted to contribute to the majority of mean comparisons less than would be objectively warranted, which can translate to an as-if underweighting of rare outcomes, irrespective of what the thresholds require the number of won comparisons to be.
-<!--Accordingly, while increases in thresholds---and thus in the number of sampled outcomes distributed over multiple small samples, each of which is considered---allow to choose with increasing accuracy the prospect that is more likely to return a higher outcome, the resulting choices can produce an as-if underweighting of rare outcomes.-->
-In turn, for low switching probabilities, the accumulation process unfolds over mean comparisons based on large samples, thus resembling the summary strategy---for low thresholds, respectively---and accumulating evidence for differences in the EV.
+In turn, for low switching probabilities, the accumulation process unfolds over mean comparisons based on large samples, thus resembling the summary strategy---for low thresholds, respectively---and accumulating evidence for differences in the EV.-->
 

### 2022-05-20 manuscript.Rmd
Final Version: Section 1

@@
 The two models presented below, one assuming an integration and evaluation mechanism resembling the round-wise strategy, the other assuming mechanisms resembling the summary strategy, offer a formal route to explore the potential interplay between sampling and integration/decision strategies, and their effects on the choice behavior.
-The sequential sampling framework is chosen as a modeling outlet not only because it makes parsimonious assumptions and has assembled a good *"track record"* [cf.
-@meehlAppraisingAmendingTheories1990] by explaining and predicting actual choice behavior, but primarily because it makes explicit a core part of the computational problem the mind is trying to solve:
-in order to make systematic choices, the mind must assess differences in latent properties.
-And in accumulating evidence for and against propsects, what should the mind accumulate evidence for if not such differences?
-round-wise and summary decisions are both indicative for distinct properties the expected value and the probability to produce a higher outcome most of the time.
-The remainder of the paper discusses and demonstrates in a simulation, how sampling and decision strategies as well as thresholds can act together to alter the degree and the accuracy with which these differences are assessed.
-
-<!--Yet, there are several distinct properties that can be used to assess differences between the prospects, among them the EV, for which the summary decision strategy is indicative, and the probability to produce a higher outcome most of the time, for which the round-wise decision strategy is indicative [@hillsInformationSearchDecisions2010; see also @wulffHowShortLongrun2015].
-Respectively, in the following, both decision strategies are implemented into a common sampling and accumulation model to demonstrate how the mind may rely on different sampling strategies to alter the degree to which evidence is accumulated for differences in either one of these properties.
-More specifically, the proposed model accumulates the outcomes obtained from a sequence of comparisons between sample means, with the size of the samples underlying each mean comparison tending to be large (small) for low (high) switching probabilities.
-Accordingly, whereas the decision variables of the model capture how many comparisons a prospect has won, the unfolding accumulation process more closely resembles the summary strategy for low switching probabilities and the round-wise strategy for high switching probabilities.
-
-Now, the current paper presents a sampling and accumulation model that provides an algorithmic link between sampling and decision strategies, and uses the model to discuss how the mind may rely on sampling strategies to alter which differences in the latent properties of prospects evidence is accumulated for.
-More specifically, the proposed model assumes an accumulation process over a sequence of mean comparisons, with switching probabilities---i.e., the probability of sampling
-outcomes from different prospects in direct succession---determining the size of the samples underlying each mean comparison and thresholds determining how many comparisons a prospect must win in order to be chosen.
-The model is such that when switching probabilities are high, the accumulation process unfolds over mean comparisons based on small samples, thus resembling the round-wise strategy and accumulating evidence for differences in the probability to produce a higher outcome most of the time.
-Notably, in this case, small-probability outcomes are predicted to contribute to the majority of mean comparisons less than would be objectively warranted, which can translate to an as-if underweighting of rare outcomes, irrespective of what the thresholds require the number of won comparisons to be.
-In turn, for low switching probabilities, the accumulation process unfolds over mean comparisons based on large samples, thus resembling the summary strategy---for low thresholds, respectively---and accumulating evidence for differences in the EV.-->
+The sequential sampling framework is chosen as a modeling outlet not only because it makes parsimonious assumptions about the decision-making process and accounts for the behavior in various decision-making tasks [@ratcliffComparisonSequentialSampling2004], but primarily because it makes---taking a Marrian perspective [cf.
+@marrVisionComputationalInvestigation1982; @marrUnderstandingComputationUnderstanding1977; see also, e.g., @griffithsProbabilisticModelsCognition2010]---explicit a core part of the computational problem the mind is trying to solve in DFE, and the principle logic that governs the solution:
+In order to make systematic choices between prospects, the mind must assess true differences in their *latent* properties, and it can only do so by searching for evidence for such differences in information samples.
+Sequential sampling models of DFE make this clear by assuming an evidence accumulation process over sampled outcomes that is more or less directed towards particular latent properties.
+Round-wise and summary decisions are both indicative for distinct latent properties, i.e., the expected value and the probability to produce a higher outcome most of the time, respectively.
+The remainder of the paper discusses and demonstrates in a simulation, how integration/decision strategies can act together with sampling strategies and evidence thresholds to alter the degree and the accuracy with which differences about either one of these properties are assessed.
 

### 2022-05-20 manuscript.Rmd
Section 2: Add Figure 2 (Model Sketches)

@@
 
-We consider the sampling paradigm and a choice between two prospects denoting the distributions $P'^X$ and $P'^Y$ of the discrete random variables $X$ and $Y$, respectively.
+Let us consider the sampling paradigm and a choice between two prospects, $P^X$ and $P^Y$.
+Let $P^X$ be a probability---or pushforward---measure assigning to each possible outcome $x$ of the random variable $X$ a probability $p_X(x)$.
+$P^Y$ is defined in a similar way.
+Graphical sketches of the round-wise and summary integration model are displayed in Figure\ \@ref(fig:models).
+
+\begin{figure}[t!]
+\caption{Integration of Sampling and Integration/Decision Strategies into a Sequential Sampling Model}
+\includegraphics{manuscript_files/models} \label{fig:models}
+\raggedright \textit{Note.} In both models, to arrive at a final choice, it is assumed that outcomes from two prospects (here: violet vs.
+orange, see Fig.~\ref{fig:sampling-paradigm}, for details), are sequentially sampled and integrated
+into dynamic decision variables until one of the variables reaches a threshold (not displayed).
+Round-wise integration model: The value of the decision variable is the cumulative sum of won mean comparisons.
+Each mean comparison encompasses the outcomes that were sampled from the same prospect in direct succession (without a switch in between).
+The thresholds govern the required (difference in the) number of won comparisons.
+Summary integration: The value of the decision variable is the cumulative sum across all outcomes sampled from a prospect.
+The thresholds govern the required (difference in the) cumulative sums.
+Both integration models allow for differences in thresholds and switching probabilities.
+\end{figure}
 

### 2022-05-20 manuscript.Rmd
Final version: Section 2

@@
 
-<!--Note that a prospect can be conceptualized as the distribution $P$ of a discrete random variable $X$, where each outcome in $\{x_i\}$ denotes a possible value that $X$ can take.
-In other words, then, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
-$$
-\{P^1, ... , P^k\}
-\; .
-\tag{1}
-$$
--->
-
 Let us consider the sampling paradigm and a choice between two prospects, $P^X$ and $P^Y$.
@@
 
-The model assumes that the sampling process starts at random with a stochastic process on one of the two random variables.
-Specifically, it is assumed that an agent starts with equal probability to sample from one of the prospects, say $P'^X$, and generates a sequence of random variables $X_1, X_2,...$, where the mean over the sequence is computed or updated with each new outcome that is sampled.
-The respective stochastic process $\{S^X_n\}_{n \in \mathbb{N}}$ is defined by
-$$
-S^X_n = \frac{1}{n} \sum_{t = 1}^n X_t, \quad n \in \mathbb{N}
+The model assumes that the sampling process starts at random with a stochastic process on one of the two prospects.
+Specifically, it is assumed that an agent starts with equal probability to sample from one of the prospects, say $P^X$, and generates a sequence of sampled outcomes, denoted by the random variables $X_1, X_2,...$, where the mean over this sequence is computed or updated with each new sampled outcome.
+The respective stochastic process $\{S^X_t\}_{t \in \mathbb{N}}$ is defined by
+$$
+S^X_t = \frac{1}{t} \sum_{k = 1}^t X_k, \quad k,t \in \mathbb{N}
 \; ,
-\tag{7}
-$$
-and terminates as soon as an outcome is sampled from the other prospect.
-The switching probability $\psi \in (0,1]$, which is assumed to be adopted prior the start of the information-processing chain and is fixed throughout, controls the probability with which outcomes from different prospects are sampled in direct succession.
-In other words, the switching probability is the probability with which the stochastic process on the current random variable stops and a new stochastic process on the other random variable starts with the subsequently sampled outcome.
-To implement the accumulation process, the model assumes that each time after a new stochastic process was started and terminated on both random variables, their respective values are compared, with the prospect underlying the stochastic process with the greater final value receiving a round win.
-Accordingly, for the prospect $P'^X$, this stage is modeled as the mapping
+\tag{1}
+$$
+where $S^X_t$ is the mean across $t$ outcomes that were *successively* sampled from prospect $P^X$.
+Each such stochastic process terminates as soon as an outcome is sampled from the other prospect, i.e., the stochastic process on prospect $P^X$ stops as soon as an outcome is sampled from prospect $P^Y$, and vice versa.
+The switching probability $\psi \in (0,1]$, which is assumed to be adopted prior the start of the sampling and accumulation process, is fixed throughout and controls the probability with which outcomes from different prospects are sampled in direct succession.
+In other words, the switching probability $\psi$ governs the probability with which the stochastic process on a given prospect, defined as in (1), stops and a new stochastic process on the other prospect starts with the subsequently sampled outcome.
+
+To implement the evidence accumulation process, the round-wise integration model assumes that each time after a *new* stochastic process was started and terminated on both prospects, their respective means are compared, with the prospect underlying the stochastic process with the greater mean receiving a round win.
+Accordingly, assuming that $S^Y_m$ is the mean across $m$ outcomes successively sampled from prospect $P^Y$, this stage is modeled for the prospect $P^X$as the mapping
 $$
@@
   Z^X : \mathbb{R} &\to \mathbb{N} \\
-  S^X_n - S^Y_n &\mapsto 
+  S^X_t - S^Y_m &\mapsto 
   \begin{cases}
-     1 &\text{if} \quad  S^X_n > S^Y_n, \\
+     1 &\text{if} \qquad  S^X_t > S^Y_m, \\
      0 &\text{else}
@@
 \end{aligned}
-\tag{8}
+\tag{2}
 $$
 where $Z^X$ is a random variable that takes only the two values $0$ and $1$, denoting a lost or won mean comparison, respectively.
-The model assumes that a round consisting of a pair of stochastic processes---i.e., one for each prospect---and the subsequent comparison of their final values is repeated until the sum of round wins for one of the two prospects reaches a threshold $\theta \in \mathbb{N}$.
-Similar to the switching probability, it is assumed that the threshold is adopted prior the start of the information-processing chain and is fixed throughout.
-For $P'^X$, then, we obtain a sequence of independent comparisons $Z^X_1, Z^X_2, ...$ and model the respective evidence accumulation process as a random walk $\{D^X_m\}_{m \in \mathbb{N}}$ defined by 
-$$
-D^X_m = \sum_{i = 1}^m Z^X_i, \quad m \in \mathbb{N}
-\;,
-\tag{9}
-$$
-resembling a dynamic decision variable.
-Note that since (8) describes a Bernoulli trial, the random walk in (9) is based on a Bernoulli process.
+Let us denote the steps defined in (1) and (2) as a round of mean comparison (short: *comparison round*, see Fig.\ \@ref(fig:models)).
+
+The model assumes that such comparison rounds are repeatedly carried out until the cumulative sum of round wins for one of the two prospects reaches a threshold $\theta \in \mathbb{N}$.
+Similar to the switching probability, it is assumed that the threshold $\theta$ is adopted prior the start of the sampling and accumulation process and is fixed throughout.
+For $P^X$, then, one obtains a sequence of mean comparisons, denoted as $Z^X_1, Z^X_2, ...$, and an evidence accumulation process taking the form of a random walk $\{D^X_v\}_{v \in \mathbb{N}}$ defined by
+$$
+D^X_v = \sum_{c = 1}^v Z^X_c, \quad c,v \in \mathbb{N}
+\;.
+\tag{3}
+$$
+$D^X_v$ is the cumulative sum of round wins of prospect $P^X$ after $v$ comparison rounds, and resembles a dynamic decision variable.
+Note that since (2) describes a Bernoulli trial, the random walk in (3) is based on a Bernoulli process.
+Prospect $P^X$ would be chosen, if $D^Y_v < \theta \leq D^X_v$ is satisfied, and vice versa.
 
@@
 However, one may also define a single random walk, resembling a common dynamic decision variable, which approaches a positive threshold $\theta^+$ and a negative threshold $\theta^-$.
-Therefore, (8) may be adapted such that $Z$ takes the value $-1$ instead of $0$, such that the threshold determines how many more mean comparisons a prospect must win in order to be chosen.
+That is, (2) may be adapted such that $Z$ takes the value $-1$ instead of $0$, such that the threshold determines how many more mean comparisons a prospect must win in order to be chosen.
 
@@
 
-[...]
+The model assumes that an agent starts with equal probability to sample outcomes from one of the prospects and continues sampling while switching between prospects according to the switching probability $\psi$.
+As in the round-wise integration model, the switching probability $\psi$ is assumed to be adopted prior the start of the sampling and accumulation process and is fixed throughout.
+
+To implement the evidence accumulation process, the summary integration model assumes that an agent continues sampling from both prospects until the cumulative sum across all outcomes sampled from one of the prospects reaches a threshold $\theta$.
+As in the round-wise integration model, the threshold $\theta$ is assumed to be adopted prior the start of the sampling and accumulation process and is fixed throughout.
+For $P^X$, then, one obtains a sequence of sampled outcomes, $X_1, X_2, ...$, and an evidence accumulation process taking the form of a random walk $\{D^X_t\}_{t \in \mathbb{N}}$ defined by 
+$$
+D^X_t = \sum_{k = 1}^t X_k, \quad k,t \in \mathbb{N}
+\; ,
+\tag{4}
+$$
+where $D^X_t$ is the cumulative sum after $t$ outcomes sampled from prospect $P^X$ and resembles a dynamic decision variable.
+Assuming that $D^Y_m$ is the cumulative sum after $m$ sampled outcomes from prospect $P^Y$, prospect $P^X$ would be chosen, if $D^Y_m < \theta \leq D^X_t$ is satisfied, and vice versa.
+
+Note again that the described model assumes two random walks---i.e., one for each prospect---approaching the same threshold, which now is the cumulative sum across all sampled outcomes a prospect must produce in order to be chosen.
+However, one may also define a single random walk, resembling a common dynamic decision variable, which approaches a positive threshold $\theta^+$ and a negative threshold $\theta^-$.
+That is, (4) may be substituted by
+$$
+D^X_{t,m} = \sum_{k = 1}^t X_k - \sum_{j = 1}^m Y_j \quad k,t,j,m \in \mathbb{N}
+\; ,
+\tag{5}
+$$
+where $D^X_{t,m}$ is the difference between the cumulative sums after $t$ and $m$ outcomes sampled from prospects $P^X$ and $P^Y$, respectively.
+The thresholds thus determine how much larger the cumulative sum of a prospect must be in order for the prospect to be chosen.
+
+\newpage
 

### 2022-05-21 manuscript.Rmd
Update Section 3: Expectations

@@
 Note that since (2) describes a Bernoulli trial, the random walk in (3) is based on a Bernoulli process.
-Prospect $P^X$ would be chosen, if $D^Y_v < \theta \leq D^X_v$ is satisfied, and vice versa.
+Prospect $P^X$ would be chosen once $D^Y_v < \theta \leq D^X_v$ is satisfied, and vice versa.
 
@@
 $$
-where $D^X_t$ is the cumulative sum after $t$ outcomes sampled from prospect $P^X$ and resembles a dynamic decision variable.
-Assuming that $D^Y_m$ is the cumulative sum after $m$ sampled outcomes from prospect $P^Y$, prospect $P^X$ would be chosen, if $D^Y_m < \theta \leq D^X_t$ is satisfied, and vice versa.
+where $D^X_t$ is the cumulative sum across $t$ outcomes sampled from prospect $P^X$ and resembles a dynamic decision variable.
+Assuming that $D^Y_m$ is the cumulative sum across $m$ sampled outcomes from prospect $P^Y$, prospect $P^X$ would be chosen once $D^Y_m < \theta \leq D^X_t$ is satisfied, and vice versa.
 
@@
 $$
-where $D^X_{t,m}$ is the difference between the cumulative sums after $t$ and $m$ outcomes sampled from prospects $P^X$ and $P^Y$, respectively.
+where $D^X_{t,m}$ is the difference between the cumulative sums across $t$ and $m$ outcomes sampled from prospects $P^X$ and $P^Y$, respectively.
 The thresholds thus determine how much larger the cumulative sum of a prospect must be in order for the prospect to be chosen.
 
-\newpage
-
 # What Model Behaviors Are Expected?
 
-Below, the key predictions concerning the effects of the model parameters $\psi$ and $\theta$ on the length of the sampling and accumulation process and the resulting choice are outlined.
-Moreover, previous research has shown that differences as to how information about the properties of prospects is processed can translate to characteristic shapes of cumulative prospect theory's (CPT) value and weighting function [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021].
-Respectively, this section also contains predictions about the relations between $\psi$ and $\theta$ and the CPT parameters.
-A summary of the model predictions can be found in Table\ \@ref(tab:predictions).
-
-(ref:predictions) Summary of Model Predictions
-
-```{r predictions}
-predictions <- tibble("Measure" = 
-                        c("Choices pattern",
-                          "",
-                          "$\\gamma$ (curvature of $w$)",
-                          "$\\delta$ (elevation of $w$)",
-                          "$\\alpha$ (concavity of $v$)"),
-                      "Predictions for changes in $\\psi$" = 
-                        c("More EV maximization for decreasing $\\psi$",
-                          "More as-if underweighting of rare outcomes for increasing $\\psi$",
-                          "$\\geq 1$, increases with $\\psi$",
-                          "1, no effect of $\\psi$",
-                          "$\\leq 1$, decreases with increasing $\\psi$"))
-apa_table(predictions, caption = "(ref:predictions)", note = "The predictions should become more robust for high values of $\\theta$.", escape = FALSE)
-```
-
-## Length of Information-Processing Chains
+Below, it is discussed which effects the key model parameters, i.e., the switching probability $\psi$ and the threshold $\theta$, could have on the choices and the corresponding as-if weighting pattern that are implied by the round-wise and the summary integration model.
+The effects of the switching probability $\psi$ should be informative about the interplay between different sampling strategies and the integration/decision strategy each model resembles.
+Assuming that both models aim to assess true differences in the latent properties of prospects, the effects of the threshold $\theta$ should indicate whether these differences are indeed more accurately assessed---thus, leading to more systematic choices and as-if weighting patterns---the more evidence is accumulated.
+In addition, previous research has shown that differences as to how information about the properties of prospects is processed can translate to distinct signatures in CPT's psychoeconomic value and weighting function, without actually assuming these functions to be computed whatsoever [see @pachurHowTwainCan2017; @stewartDecisionSampling2006; @zilkerNonlinearProbabilityWeighting2021].^[<!--Open footnote-->
+Note that it has been argued that the distinction between CPT's functions used to describe choice data and models aiming to explain how this data is generated in first place are reminiscent of Marr's [-@marrVisionComputationalInvestigation1982] different levels of explanation [@zilkerMeasuringModelingConstruction2020; also cf.
+@griffithsProbabilisticModelsCognition2010].
+That is, whereas CPT may be considered a computational-level theory that describes an abstract solution to the problem the mind aims to solve when offered a choice between prospects, process models [cf.
+@jareckiFrameworkBuildingCognitive2020] such as heuristics and sequential sampling models may be considered algorithmic-level theories that specify how the mind can approximate the abstract solution with the capacity limits it possesses.
+<!--Close footnote-->]
+Accordingly, this section also formulates expectations regarding the potential relations between the switching probability $\psi$ and threshold $\theta$ (data-generating parameters) and the CPT parameters (data-modeling parameters).
+Summaries of the expected model behaviors can be found in Tables\ \@ref(tab:expectations-roundwise) and \@ref(tab:expectations-summary).
+
+## Length of Sampling and Accumulation Processes and Final Choice
+
+### Round-Wise Integration Model
 
@@
 Accordingly, an increase in $\psi$ leads to shorter stochastic processes, which translate, ceteris paribus, to a smaller overall number of sampled outcomes.
-
-## Final Choice
 
@@
 
+### Summary Integration Model
+
+[...]
+
 ## Cumulative Prospect Theory
 
-Before elaborating how the above model predictions may translate into estimates of the CPT parameters, the following section reviews how CPT in general and its weighting function in particular capture deviations from EV maximization.
+Before elaborating how the expectation outlined above may translate into estimates of the CPT parameters, the following section reviews how CPT in general and its weighting function in particular capture deviations from EV maximization.
 
@@
 
-The choices people make between prospects are often *described* in terms of deviations from EV maximization, according to which the prospect with the largest EV
-$$
-EV = \sum_i^n x_i \times p_X(x_i)
-\tag{10}
+The actual choices people make between prospects are often *described* in terms of deviations from EV maximization, according to which the prospect with the largest EV
+$$
+EV = \sum_{i \in \mathbb{N}}^n x_i \times p_X(x_i)
+\tag{6}
 $$ 
 should be chosen.
-To describe how people's choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations],^[<!--Open footnote-->
-@tverskyAdvancesProspectTheory1992 addressed the *fourfold pattern of risk attitudes*---i.e., choices between prospects indicate risk aversion for gains of high probability and losses of low probability, and risk seeking for gains of low probability and losses of high probability---and related effects, e.g., the *certainty effect* and the *reflection effect*, where the latter were already addressed by CPT's predecessor, prospect theory [@kahnemanProspectTheoryAnalysis1979].
-Together, these empirical choice patterns indicate a violation of EV and expected utility (EU) maximization [see @bernoulliExpositionNewTheory1954\/1738].
-<!--Close footnote-->]
-CPT and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by assuming that people maximize the valuation
-$$
-V = \sum_i^n v(x_i) \times \pi_i
+To describe how people's choices deviate from EV maximization [see @erevAnomaliesForecastsDescriptive2017, for a recent replication of classical demonstrations; see also @kahnemanProspectTheoryAnalysis1979; @tverskyAdvancesProspectTheory1992], CPT and similar rank-dependent models [see @stottCumulativeProspectTheory2006, for an overview of models] fit choice data by assuming that people maximize the valuation
+$$
+V = \sum_{i \in \mathbb{N}}^n v(x_i) \times \pi_i
 \; ,
-\tag{11}
-$$ 
-with objective outcomes $x_i$ being transformed by a value function $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P'$.
+\tag{7}
+$$ 
+with objective outcomes $x_i$ being transformed by a value function $v$, and *cumulative decision weights* $\pi_i$ being determined by the difference between transformed cumulative probabilities of the distribution $P$.
 More specifically, following @tverskyAdvancesProspectTheory1992, the objective outcomes are transformed by a value function
@@
 \end{aligned}
-\tag{12}
+\tag{8}
 $$
@@
   \end{cases}
-\tag{13}
-$$
-where $w$ is a monotonic increasing, nonlinear weighting function $w: [0,1] \to [0,1]$ satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
-
-Essentially, the model is such that the cumulative decision weights derived for the outcomes may be greater or smaller than their objective probabilities, causing the transformed outcomes---i.e., the subjective values---to be over- or underweighted *in* CPT, respectively.
-Accordingly, for the description of choices, one may adopt an as-if weighting terminology by stating that people choose as if they maximized the value in (11) and applied the weighting pattern that was estimated in CPT.
-Importantly, the as-if prefix indicates that it cannot be concluded from the estimated weighting pattern that the mind indeed performs any of the computations associated with the weighting of subjective values;
-rather, the mind processes the information about the properties of choice alternatives in a way that the resulting choices translate to the estimated weighting pattern [@gigerenzerHowExplainBehavior2020].
-Respectively, this paper treats CPT as a data model and discusses---and refines in a simulation---what weighting patterns can be expected, were the mind to carry out the information-processing chains that are assumed by the proposed sampling and accumulation model [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021, for similar theoretical inquiries].
-
-Now, several consequences for the weighting patterns that can be estimated in CPT follow from (13), which are briefly reviewed next:
-
-* From the transformation of cumulative probabilities it follows that the value of a cumulative decision weight $\pi$ depends on the rank of the outcome $x$ for which $\pi$ is determined.
-
-* The value of $\pi$ depends on the estimated shape of the graph of $w$, i.e., the weighting function's parameters.
-Specifically, the shape of the graph of $w$ displays over which interval on the cumulative probability scale $[0,1]$ the images of $w$ take values that are greater or smaller than the respective cumulative probabilities and how much greater or smaller these images are.
-Hence, for a nonlinear graphical shape of $w$, the same numerical difference between objective cumulative probabilities may translate to cumulative decision weights of different value.
-
-* For prospects containing either only positive or only negative outcomes, $\sum_i^n\pi_i = 1$ is satisfied.
-Accordingly, for such prospects, the weighting of subjective values with cumulative decision weights rather than with objective probabilities may be roughly understood as a redistribution of the entire probability mass of $P(\Omega') = 1$ across outcomes [@zilkerNonlinearProbabilityWeighting2021].
-
-\noindent
-Because the value of each $\pi$ depends on the two transformed cumulative probabilities in (13)---i.e., the probability of obtaining a positive (negative) outcome equal to or greater (smaller) than a respective outcome $x$, and the probability of obtaining a strictly greater (smaller) outcome---the remaining consequences for the possible weighting patterns are reviewed by considering the actual weighting function.
+\tag{9}
+$$
+where $w$ is a monotonic increasing, nonlinear weighting function satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
+To simplify matters, the further discussion and the computational analysis are constrained to choices between a safe prospect---possessing just one outcome that occurs with certainty---and a two-outcome prospect (hereafter: risky prospect).
+All outcomes are assumed to be positive and the safe outcome is assumed to fall between the the low-rank outcome, $x_{low}$, and the high-rank outcome, $x_{high}$, of the risky prospect to omit dominance.
+One can then disregard the negative parts of (8) and (9), including the parameter $\lambda$ of the value function, and (9) simplifies to
+$$
+\begin{aligned}
+  \pi_{high} &= w(p_x(x_{high})) \\
+  \pi_{low} &= w(p_x(x_{low}) + p_x(x_{high})) - w(p_x(x_{high})) \\
+  &= 1 - \pi_{high}
+  \; .
+\end{aligned}
+\tag{10}
+$$
+
+Essentially, the model is such that the cumulative decision weights derived for the outcomes of the risky prospect may be greater or smaller than their objective probabilities, causing the transformed outcomes---i.e., the subjective values---to be over- or underweighted *within* CPT, respectively.
+Accordingly, for the description of choices, one may adopt an as-if weighting terminology by stating that people choose as if they maximized the value in (7) and applied the weighting pattern that was estimated in CPT.
+Importantly, the as-if prefix indicates that there is no claim that the mind indeed performs any of the computations associated with the weighting of subjective values; 
+rather, the mind processes the information about the properties of choice alternatives in a way that the resulting choices translate to the estimated weighting pattern [cf.
+@gigerenzerHowExplainBehavior2020].
+Accordingly, once again, this paper treats CPT as a data model and discusses---and refines in a simulation---what weighting patterns can be expected, were the mind to carry out the sampling and accumulation processes that are assumed by the presented round-wise and summary integration model [see @pachurHowTwainCan2017; @zilkerNonlinearProbabilityWeighting2021, for similar theoretical inquiries].
+
+Now, several consequences for the weighting patterns that can be estimated in CPT follow from the exact specification of the weighting function $w$, which are briefly reviewed next:
 Therefore, Figure\ \@ref(fig:weighting-function) illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
-Now, let each $p$ on the abscissa be one of the four cumulative probabilities from (13). 
-Then each graph in Figure\ \@ref(fig:weighting-function) displays the graphical shape of the weighting function
+Each graph in Figure\ \@ref(fig:weighting-function) displays the graphical shape of the weighting function
 $$
@@
   w : [0,1] &\to [0,1] \\
-  p &\mapsto \frac{\delta \times p^{\gamma}}
-  {\delta \times p^{\gamma} + (1-p)^{\gamma}}
+  p_X(x_{high}) &\mapsto \frac{\delta \times (p_X(x_{high}))^{\gamma}}
+  {\delta \times (p_X(x_{high}))^{\gamma} + (1-p_X(x_{high}))^{\gamma}}
   \; ,
 \end{aligned}
-\tag{14}
+\tag{11}
 $$
@@
 Evidently, both parameters have distinct effects on the graphs' shape, with $\gamma$ affecting the curvature and $\delta$ the elevation.
-As a consequence from (13), then, each combination of parameters implies a particular weighting pattern, with some of them being similar and others being rather distinct.
+[As a consequence from (13), then, each combination of parameters implies a particular weighting pattern, with some of them being similar and others being rather distinct.]
 
@@
   scale_y_continuous(breaks = seq(0, 1, .5)) + 
-  labs(x = expression(p),
-       y = expression(w(p)), 
+  labs(x = "Probability of High-Rank Risky Outcome",
+       y = "Transformed Probability / Decision Weight", 
        color = expression(gamma)) + 
@@
 
-To simplify matters, the further discussion and the computational analysis are constrained to choices between a safe prospect---possessing just one outcome that occurs with certainty---and a two-outcome prospect (hereafter: risky prospect).
-All outcomes are assumed to be positive and the safe outcome is assumed to fall between the the low-rank outcome, $x_{low}$, and the high-rank outcome, $x_{high}$, of the risky prospect to omit dominance.
 A summary of the predictions for the CPT parameters can be found in Table\ \@ref(tab:predictions).
@@
 Respectively, as can be seen from Figure\ \@ref(fig:weighting-function), for $\gamma > 1$, the high-rank outcome of the risky prospect is overweighted (underweighted) in CPT, if it is of large (small) probability, and $\delta \neq 1$ shifts the range of the over- and underweighting.
+
+#### Round-Wise Integration Model
 
@@
 Respectively, $\alpha$ is predicted to decrease with increases in $\psi$.
+
+(ref:expectations-roundwise) Expected Effects of Switching Probability $\psi$ and Threshold $\theta$ in the Round-Wise Integration Model
+
+```{r expectations-roundwise}
+exp_roundwise <- tibble("Measure" = 
+                        c("Choices pattern",
+                          "",
+                          "$\\gamma$ (curvature of $w$)",
+                          "$\\delta$ (elevation of $w$)",
+                          "$\\alpha$ (concavity of $v$)"),
+                      "Predictions for changes in $\\psi$" = 
+                        c("More EV maximization for decreasing $\\psi$",
+                          "More as-if underweighting of rare outcomes for increasing $\\psi$",
+                          "$\\geq 1$, increases with $\\psi$",
+                          "1, no effect of $\\psi$",
+                          "$\\leq 1$, decreases with increasing $\\psi$"))
+
+apa_table(exp_roundwise, caption = "(ref:expectations-roundwise)", note = "The predictions should become more robust for high values of $\\theta$.", escape = FALSE)
+```
+
+#### Summary Integration Model
+
+[...]
+
+(ref:expectations-summary) Expected Effects of Switching Probability $\psi$ and Threshold $\theta$ in the Summary Integration Model
+
+```{r expectations-summary}
+exp_summary <- tibble("Measure" = 
+                        c("Choices pattern",
+                          "",
+                          "$\\gamma$ (curvature of $w$)",
+                          "$\\delta$ (elevation of $w$)",
+                          "$\\alpha$ (concavity of $v$)"),
+                      "Predictions for changes in $\\psi$" = 
+                        c("More EV maximization for decreasing $\\psi$",
+                          "More as-if underweighting of rare outcomes for increasing $\\psi$",
+                          "$\\geq 1$, increases with $\\psi$",
+                          "1, no effect of $\\psi$",
+                          "$\\leq 1$, decreases with increasing $\\psi$"))
+
+apa_table(exp_summary, caption = "(ref:expectations-summary)", note = "The predictions should become more robust for high values of $\\theta$.", escape = FALSE)
+```
 

### 2022-05-22 manuscript.Rmd
Final version section 3 (expectations)

@@
 
-Below, it is discussed which effects the key model parameters, i.e., the switching probability $\psi$ and the threshold $\theta$, could have on the choices and the corresponding as-if weighting pattern that are implied by the round-wise and the summary integration model.
+Below, it is discussed which effects the key model parameters, i.e., the switching probability $\psi$ and the threshold $\theta$, could have on the choices and the corresponding as-if weighting patterns that are implied by the round-wise and the summary integration model.
 The effects of the switching probability $\psi$ should be informative about the interplay between different sampling strategies and the integration/decision strategy each model resembles.
 Assuming that both models aim to assess true differences in the latent properties of prospects, the effects of the threshold $\theta$ should indicate whether these differences are indeed more accurately assessed---thus, leading to more systematic choices and as-if weighting patterns---the more evidence is accumulated.
-In addition, previous research has shown that differences as to how information about the properties of prospects is processed can translate to distinct signatures in CPT's psychoeconomic value and weighting function, without actually assuming these functions to be computed whatsoever [see @pachurHowTwainCan2017; @stewartDecisionSampling2006; @zilkerNonlinearProbabilityWeighting2021].^[<!--Open footnote-->
+In addition, previous research has shown that differences as to how information about the properties of prospects is processed can translate to distinct signatures in CPT's psychoeconomic value and weighting function, without actually assuming that these functions are computed whatsoever [see @pachurHowTwainCan2017; @stewartDecisionSampling2006; @zilkerNonlinearProbabilityWeighting2021].^[<!--Open footnote-->
 Note that it has been argued that the distinction between CPT's functions used to describe choice data and models aiming to explain how this data is generated in first place are reminiscent of Marr's [-@marrVisionComputationalInvestigation1982] different levels of explanation [@zilkerMeasuringModelingConstruction2020; also cf.
@@
 That is, whereas CPT may be considered a computational-level theory that describes an abstract solution to the problem the mind aims to solve when offered a choice between prospects, process models [cf.
-@jareckiFrameworkBuildingCognitive2020] such as heuristics and sequential sampling models may be considered algorithmic-level theories that specify how the mind can approximate the abstract solution with the capacity limits it possesses.
+@jareckiFrameworkBuildingCognitive2020], such as heuristics and sequential sampling models, may be considered algorithmic-level theories that specify how the mind can approximate the abstract solution with the capacity limits it is constrained by.
 <!--Close footnote-->]
 Accordingly, this section also formulates expectations regarding the potential relations between the switching probability $\psi$ and threshold $\theta$ (data-generating parameters) and the CPT parameters (data-modeling parameters).
+
+## Potential Impact on Final Choices
+
+The discussion below is constrained to choices between prospects that possess only positive outcomes. 
 Summaries of the expected model behaviors can be found in Tables\ \@ref(tab:expectations-roundwise) and \@ref(tab:expectations-summary).
 
-## Length of Sampling and Accumulation Processes and Final Choice
-
 ### Round-Wise Integration Model
 
-The required number of independent mean comparisons increases with thresholds $\theta$.
-Since each comparison is based on its own pair of stochastic processes, an increase in $\theta$ translates to a larger number of required stochastic processes and, ceteris paribus, therefore also to a larger overall number of outcomes sampled over the course of a sampling and accumulation process.
-In turn, each stochastic process is predicted to terminate faster, the higher the probability that the subsequent outcome is sampled from the other prospect, determined by the switching probability $\psi$.
-Accordingly, an increase in $\psi$ leads to shorter stochastic processes, which translate, ceteris paribus, to a smaller overall number of sampled outcomes.
-
-Because the switching probability $\psi$ is predicted to alter the length of the stochastic processes underlying each mean comparison, $\psi$ should affect whether low-probability outcomes contribute to the majority of the required mean comparisons about as much as would be warranted based on their objective probabilities, or whether they contribute rather less.
-That is, for short stochastic processes, the binomial distribution associated with small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur over the course of such a process to be smaller rather than larger than their latent objective probabilities.
-Respectively, if the small-probability outcome is smaller (larger) than the EV, high values of $\psi$---and therefore pairs of short stochastic processes---cause the mean to be an inflated (deflated) estimate of the EV.
-Such an inflation and deflation of the means can then translate to an as-if underweighting of rare outcomes.
-Specifically, if the mean of the prospect with the lower (higher) EV is inflated (deflated), the outcome of the comparison between the means may be a reversal---in sign---of the outcome of a comparison between the EVs, leading to choices that take the form of an as-if underweighting of rare outcomes.
-Yet, if the mean of the prospect with the lower (higher) EV is deflated (inflated), the difference between the means should be larger than the differences between the EV, which can simplify EV maximization [see @hertwigDecisionsExperienceWhy2010].
-In turn, for low values of $\psi$---and therefore pairs of long stochastic processes---the means should closely correspond to the EVs, leading to choices that are in line with EV maximization.
+Considering a *single* comparison round, the stochastic process for each prospect---which results in a mean computed across the outcomes sampled from the prospect---is predicted to terminate faster, the higher the probability that the subsequent outcome is sampled from the other prospect, i.e., the higher the switching probability $\psi$.
+Because the switching probability is predicted to alter the length of the stochastic processes underlying *each independent* mean comparison, it should affect whether low-probability outcomes contribute to each required mean comparisons about as much as would be warranted based on their objective probabilities, or whether they contribute rather less.
+That is, for high switching probabilities and thus, short stochastic processes, the binomial distribution associated with small-probability outcomes is positive skewed, causing the relative frequencies with which these outcomes occur within each comparison round to be smaller rather than larger than their latent objective probabilities.
+Because such a distortion of the relative sampled frequencies from the objective probabilities is expected for each comparison round, increases in the thresholds $\theta$ should not affect the following expectations concerning the model behavior; rather because each comparison is independent and increases in sample size (here: number of comparisons) reduce random error, the expectations should be more accurately met for higher thresholds:
+If the small-probability outcome is smaller (larger) than the EV, high switching probabilities cause the mean within each comparison round to be an inflated (deflated) estimate of the EV.
+Such an inflation and deflation of the means within each round can then translate to choices that take the form of an as-if underweighting of rare outcomes:
+Specifically, if the means of the prospect with the lower (higher) EV are inflated (deflated), the outcomes of each mean comparison may be a reversal---in sign---of the outcome of a comparison between the EVs, eventually translating to choices resembling an as-if underweighting of rare outcomes.
+Yet, if the means of the prospect with the lower (higher) EV are deflated (inflated), the difference between the means should be larger than the differences between the EV, which can simplify EV maximization [see @hertwigDecisionsExperienceWhy2010].
+In contrast, for low values of the switching probability $\psi$---and therefore pairs of long stochastic processes---the means in each round should closely correspond to the EVs, leading to choices that are in line with EV maximization.
+
+Note that the entire line of reasoning from above should also apply, if sampling error is controlled for.
+That is, if the EVs are substituted by the means across all outcomes sampled from a prospect over the course of the entire sampling and accumulation process, the means within each comparison round are still expected to deviate from this sampling error-encompassing substitute in the manner outlined above.
+Moreover, because the mean across the entire sampling and accumulation process is expected to converge to the EV the more outcomes are sampled overall, the choice patterns with and without sampling error accounted for should resemble each other more closely, the higher the thresholds get.
 
 To summarize the choice predictions and simplify: 
-If the prospect that is more likely to return a higher outcome most of the time does not also possess the higher EV, high values of $\psi$---and therefore pairs of short stochastic processes---are predicted to cause an as-if underweighting of rare outcomes.
-While these predictions emphasize the close link between small samples and the as-if underweighting of rare outcomes, they suggest that the reliance on multiple or many small samples can serve the accumulation of evidence for differences in a latent property.
-Specifically, for an increasing sequence of independent comparisons between single outcomes sampled from two prospects, the relative winning frequency of a prospect should converge against the objective probability of producing a higher outcome in each comparison.
-Respectively, then, the as-if underweighting of rare outcomes should become more robust as the thresholds $\theta$ increase.^[This clarifies the role of $\theta$: Whatever systematic differences between the prospects is reflected in a mean comparison should be more accurately assessed for high values of $\theta$.]
+If the prospect that is more likely to return a higher outcome most of the time does not also possess the higher EV or mean across all outcomes sampled over the course of a sampling and accumulation process, high values of the switching probability $\psi$ are predicted to cause an as-if underweighting of rare outcomes pattern.
+For low switching probabilities, choices are expected to maximize the EV or mean across all sampled outcomes.
+Hence, in the round-wise integration model, the switching probability is expected to alter the degree and thus, also the accuracy with which differences among prospects are assessed in either one of these latent properties: the expected value or the probability to produce a higher outcome most of the time.
+These expectations concerning the model behavior should be more accurately met, the larger the thresholds $\theta$.
 
@@
 
-[...]
+First, note that the summary integration model differs from the summary strategy proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010] to the extent that cumulative sums rather than means are calculated across all outcomes sampled from a prospect.^[<!--Open footnote-->
+I.e., one must ensure that the summary statistic in fact approaches and reaches a threshold in order for the code to not run endlessly.
+Note that this is not a mere technical issue, but implied by the theoretical assumptions of the sequential sampling framework.
+<!--Close footnote-->] 
+This could introduce interactions between the switching probability $\psi$ and the threshold $\theta$ that are not implied by a model that assumes comparisons between means.
+
+Because the required (difference in) cumulative sums across all outcomes sampled from each prospect increases with thresholds $\theta$, the number of outcomes that is required to be sampled to reach the thresholds should increase accordingly.
+Hence, in principle, the larger the thresholds, the more should small-probability outcomes contribute to the cumulative sum as much as would be warranted by their objective probabilities.
+Accordingly, one might expect that the implied choices converge to the solutions of EV maximization, the larger the thresholds get.
+However, the switching probabilities $\psi$ should introduce temporal imbalances between prospects regarding the number of sampled outcomes over which the sums are computed (and compared, assuming relative thresholds, respectively).
+That is, whatever prospect is first sampled from is allowed to start accumulating evidence sooner than the respective other prospect.
+This is likely to be a negligible factor for large but not for small switching probabilities.
+Specifically, the temporal imbalances---i.e., the temporal advantage for the prospect which is first sampled from---grows as the switching probabilities decrease.
+Accordingly, for small switching probabilities, choices might be largely driven by the truly random event which prospect is first sampled from.
+This random choice behavior should diminish with increases in the switching probability and choices should converge to the solutions of EV maximization the higher the thresholds get.
+
+Taking together the expected effects for thresholds and switching probabilities, the expectations for the choices implied by the summary integration model are summarized as follows:
+For small switching probabilities, choice behavior should be more or less random.
+With increasing switching probabilities, choice behavior should become more systematic and driven by differences in the thresholds:
+For small thresholds, an as-if underweighting of rare outcomes pattern is expected to occur because small-probability outcomes should be systematically underrepresented due to their skewed binomial distribution.
+This pattern should be alleviated, if sampling error is taken into account.
+For large thresholds, choices should converge more to the solutions of EV maximization, even more so to the solutions of sampled mean maximization (i.e., when sampling error is accounted for).
 
@@
 
-Before elaborating how the expectation outlined above may translate into estimates of the CPT parameters, the following section reviews how CPT in general and its weighting function in particular capture deviations from EV maximization.
+Before elaborating how the expectations outlined above may translate into estimates of the CPT parameters, the following section reviews how CPT in general and its weighting function in particular capture deviations from EV maximization.
 
@@
 where $w$ is a monotonic increasing, nonlinear weighting function satisfying $w^+(0) = w^-(0) = 0$ and $w^+(1) = w^-(1) = 1$.
-To simplify matters, the further discussion and the computational analysis are constrained to choices between a safe prospect---possessing just one outcome that occurs with certainty---and a two-outcome prospect (hereafter: risky prospect).
+To simplify matters, the further discussion of CPT and the computational analysis are constrained to choices between a safe prospect---possessing just one outcome that occurs with certainty---and a two-outcome prospect (hereafter: risky prospect).
 All outcomes are assumed to be positive and the safe outcome is assumed to fall between the the low-rank outcome, $x_{low}$, and the high-rank outcome, $x_{high}$, of the risky prospect to omit dominance.
@@
 
-Now, several consequences for the weighting patterns that can be estimated in CPT follow from the exact specification of the weighting function $w$, which are briefly reviewed next:
-Therefore, Figure\ \@ref(fig:weighting-function) illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
+Now, several consequences for the weighting patterns that can be estimated in CPT follow from the exact specification of the weighting function $w$, which are briefly reviewed next.
+Figure\ \@ref(fig:weighting-function) illustrates some of the possible graphical shapes of the two-parameter weighting function of @goldsteinExpressionTheoryPreference1987, which, however, is just one of several parameterizations that have been proposed [e.g., @prelecProbabilityWeightingFunction1998; @tverskyAdvancesProspectTheory1992; see @stottCumulativeProspectTheory2006, for an overview].
 Each graph in Figure\ \@ref(fig:weighting-function) displays the graphical shape of the weighting function
@@
 for the respective values of the parameters $\gamma \in [0,2]$ and $\delta > 0$.
-Evidently, both parameters have distinct effects on the graphs' shape, with $\gamma$ affecting the curvature and $\delta$ the elevation.
-[As a consequence from (13), then, each combination of parameters implies a particular weighting pattern, with some of them being similar and others being rather distinct.]
+Evidently from the figure, both parameters have distinct effects on the graphs' shape, with $\gamma$ affecting the curvature and $\delta$ the elevation.
+As a consequence from (10) and (11), each combination of parameters implies a particular weighting pattern that amounts to either a linear or an over- and underweighting of the high-rank outcome of the risky prospect, depending on its probability.
+Hence, for the considered case---choices between a safe and a two-outcome risky prospect---, the estimated weighting function can be directly interpreted in terms of an as-if over- or underweighting of small-probability outcomes.
 
@@
   labs(x = "Probability of High-Rank Risky Outcome",
-       y = "Transformed Probability / Decision Weight", 
+       y = "Transformed Probability (Decision Weight)", 
        color = expression(gamma)) + 
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \caption{Possible Graphical Shapes of Goldstein and Einhorn's (\protect\hyperlink{ref-goldsteinExpressionTheoryPreference1987}{1987}) Weighting Function}
 \includegraphics{manuscript_files/figure-latex/weighting-function-1} \label{fig:weighting-function}
-\raggedright \textit{Note.} Add note
+\raggedright \textit{Note.} The gray-dashed identity lines indicate a linear weighting pattern, implied by \(\gamma = 1\) and \(\delta = 1\).
+Deviations produce a nonlinear graphical shape.
+\(\gamma\): For \(\gamma > 1\), graphs take a S-shape---running below (above) the identity line for small (large) probabilities---which is more accentuated for larger deviations from \(\gamma = 1\).
+Hence, decisions weights are smaller (larger) than the objective probabilities for small-probability (high-probability) outcomes.
+For \(\gamma < 1\), the graph of \(w\) takes an inverse S-shape and the weighting pattern reverses.
+\(\delta\): Shifts across the entire probability scale the intervals within which objective probabilities translate to either smaller or greater decision weights.
+For \(\delta < 1\), the interval over which the graph runs below the identity line is greater than the interval over which the graph runs above the identity line; the pattern reverses for \(\delta > 1\).
 \end{figure}
 
-More specifically: The gray-dashed identity lines in Figure\ \@ref(fig:weighting-function) imply a linear weighting pattern.
-That is, since the images of $w$, $w(p)$, are equal to the respective cumulative probabilities $p$, all cumulative decision weights $\pi$ that are derived according to (13) would be equal to the differences between the respective objective cumulative probabilities---and therefore also to the objective probabilities of the outcomes for which the weights are determined.
-Such a linear weighting pattern is implied by $\gamma = 1$ and $\delta = 1$. 
-Now, both deviations from $\gamma = 1$ and $\delta = 1$ produce a nonlinear graphical shape.
-That is, for $\gamma > 1$, the graphs take a S-shape---running below (above) the identity line for small (large) cumulative probabilities---which is more accentuated for larger deviations from $\gamma = 1$.
-Importantly, the same *small* numerical difference between two cumulative probabilities $p$ then translates to varying differences between the respective images $w(p)$ depending on the interval on the cumulative probability scale.
-Specifically, because of the S-shaped curvature, the differences between the images $w(p)$ may be smaller than those between the respective cumulative probabilities in the lower and upper part of the cumulative probability scale, but may be considerably greater in the middle part.
-As a consequence, the cumulative decisions weights are smaller than the respective objective probabilities for small-probability outcomes of low and high rank, but they are larger for small-probability outcomes of a middle rank.^[<!--Open footnote-->
-Note that the distinction between outcomes of either low/high rank or middle rank is unnecessary for at most two-outcome prospects [see @tverskyAdvancesProspectTheory1992, see also below].
-However, for finite many outcomes, the distinction is critical.
-More so, the fact that CPT may weigh outcomes of the same small probability differently, adds another reasons why the description-experience gap should not be equated with a reversed weighting pattern in CPT [see @hertwigConstructbehaviorGapDescription2018].
-I.e., neither could one interpretation of the gap be in terms of an as-if underweighting (overweighting) of rare outcomes in DFE (DFD), nor would any of the potential contributors to the gap considered so far [cf.
-@hertwigDescriptionexperienceGapRisky2009; @wulffMetaanalyticReviewTwo2018] treat some small-probability outcomes differently than other small-probability outcomes.
-<!--Close footnote-->]
-Note that for all $\gamma < 1$ the graph of $w$ takes an inverse S-shape and the entire weighting pattern is reversed.
-Moreover, the shape of the weighting function, and thus the weighting pattern, depends strongly on $\delta$, which affects the overall elevation of the graph.
-That is, for $\delta < 1$, the interval on the cumulative probability scale over which the weighting function runs below the identity line is greater than the interval over which the weighting function runs above the identity line; and this pattern reverses for $\delta > 1$.
-In other words, $\delta$ shifts across the entire cumulative probability scale the intervals within which small differences between objective cumulative probabilities translate to either smaller or greater cumulative decision weights.
-
-To summarize the preceding paragraphs: CPT is a data model that can be used to describe choices between prospects by capturing systematic deviations from EV maximization in the parameter estimates of its value and weighting function.
-Because the graph of the weighting function usually takes a more or less accentuated (inverse) S-shape, the implied weighting pattern is such that small probability outcomes of low and high rank are underweighted (overweighted) in CPT's valuation of a prospect according to (11).
-
-### How Is CPT Expected to Reflect the Model Predictions?
-
-A summary of the predictions for the CPT parameters can be found in Table\ \@ref(tab:predictions).
-
-To begin with, note through simplifying (13) to
-$$
-\begin{aligned}
-  \pi_{high} &= w(p_x(x_{high})) \\
-  \pi_{low} &= w(p_x(x_{low}) + p_x(x_{high})) - w(p_x(x_{high})) \\
-  &= 1 - \pi_{high}
-  \; ,
-\end{aligned}
-\tag{15}
-$$
-that the possible weighting patterns amount to an over- and underweighting of the high-rank outcome of the risky prospect, depending on its probability.
-That is, the weighting function is supplied with the probability of the high-rank outcome of the risky prospect and its images are the decision weights assigned to this outcome.
-Respectively, as can be seen from Figure\ \@ref(fig:weighting-function), for $\gamma > 1$, the high-rank outcome of the risky prospect is overweighted (underweighted) in CPT, if it is of large (small) probability, and $\delta \neq 1$ shifts the range of the over- and underweighting.
+### How Is CPT Expected to Reflect the Model-Implied Choices?
+
+To begin with, as evident from Figure\ \@ref(fig:weighting-function), for $\gamma > 1$, the high-rank outcome of the risky prospect is underweighted (overweighted) in CPT, if it is of small (large) probability, and $\delta \neq 1$ shifts the range of the over- and underweighting.
+In the following discussion, it is assumed that sampling error is controlled for. 
+That is, for each sampling and accumulation process, the weighting function is supplied with the overall sampled relative frequencies (hereafter: sampled probability) rather than with the objective probabilities.
 
@@
 
-Now, since for low values of $\psi$ the model tends to choose the prospect possessing the larger EV, the parameters of the value and weighting function in this case are predicted to correspond to a linear weighting of outcomes and probabilities, which is given for $\alpha = 1$, $\gamma = 1$, and $\delta = 1$.
-However, for high values of $\psi$, the model tends to choose the risky prospect for $p_x(x_{high}) > .5$---i.e., the risky prospect produces the higher outcome most of the time---, irrespective of the differences in the EV.
-Vice versa, the model tends to choose the safe outcome for $p_x(x_{high}) < .5$---i.e., the safe prospect produces the higher outcome most of the time.
-Respectively, for high values of $\psi$, the weighting pattern should be such that the high-rank outcome of the risky prospect is overweighted for $p_x(x_{high}) > .5$, and underweighted otherwise.
-Hence, the graph of the weighting function should take a S-shape, which is given for $\gamma > 1$.
-Because the over- and underweighting of the high-rank outcome is not predicted to extend across the mid-point of the probability scale, $\delta$ should take values around 1.
-Note that the graph of the weighting function for high values of $\psi$ reflects the round-wise strategy's high sensitivity to differences in the probability to produce the higher outcome most of the time:
-Specifically, the slope of the weighting function's graph is most severe around the midpoint of the probability scale.
-The predicted flat ends of the graph, however, indicate that the round-wise strategy more or less ignores how much larger the probability to produce a higher outcome is. 
-In sum, then, we do not predict $\delta$ to change with $\psi$.
-However, we expect $\gamma$ to increase with $\psi$, thereby reflecting differences in the extent to which the prospect with the higher EV or with the probability to produce a higher outcome most of the time is chosen.
-
-Moreover, because the model is such that the magnitudes of outcomes are ignored once a comparison is carried out, increases in $\psi$ should lead to a more concave value function.
-That is, the higher the values of $\psi$, the more the choices depend on which prospect produces the higher outcome most of the time, irrespective of how much larger the outcomes are.
+Since for low values of the switching probability $\psi$ the model is expected to choose the prospect that produced the larger overall sample mean, the parameters of the value and weighting function should correspond to a linear weighting of outcomes and sampled probabilities, which is given for $\alpha = 1$, $\gamma = 1$, and $\delta = 1$.
+However, for high switching probabilities, the model is expected to choose the risky prospect for $p_x(x_{high}) > .5$---i.e., if the latent probability of the higher risky prospect is $> .5$, the risky prospect is expected to produce the higher outcome most of the time---, irrespective of the differences in the overall sample mean.
+Vice versa, the model tends to choose the safe outcome for $p_x(x_{high}) < .5$---i.e., the safe prospect is expected to produce the higher outcome most of the time.
+Correspondingly, for high switching probabilities, the weighting pattern should be such that the high-rank outcome of the risky prospect is overweighted for sampled relative frequencies $> .5$, and underweighted otherwise.
+Hence, for high switching probabilities, the graph of the weighting function should take a S-shape, which is given for $\gamma > 1$.
+Because the over- and underweighting of the high-rank outcome is not expected to extend across the mid-point of the probability scale, $\delta$ should take values around 1.
+
+Note that the graph of the weighting function that is expected for high switching probabilities would reflect the round-wise strategy's high sensitivity to differences in the latent probability to produce the higher outcome most of the time:
+Specifically, the slope of the weighting function's graph would be most severe around the midpoint of the probability scale.
+The predicted flat ends of the graph, however, indicate that the round-wise strategy more or less ignores how much larger than $.5$ the probability to produce a higher outcome is. 
+In sum, then, $\delta$ is not expected to change with the switching probability.
+However, $\gamma$ is expected to increase with the switching probability, thereby reflecting differences in the extent to which the prospect with the higher EV or with the probability to produce a higher outcome most of the time is chosen.
+As for the choice patterns, the expectations should be more accurately met for high thresholds.
+
+Moreover, because the model is such that the magnitudes of outcomes are ignored once a comparison is carried out, increases in the switching probability $\psi$ should lead to a more concave value function.
+That is, the higher the switching probabilities, the more the choices depend on which prospect produces the higher outcome most of the time, irrespective of how much larger the outcomes are.
 Respectively, $\alpha$ is predicted to decrease with increases in $\psi$.
 
-(ref:expectations-roundwise) Expected Effects of Switching Probability $\psi$ and Threshold $\theta$ in the Round-Wise Integration Model
+(ref:expectations-roundwise) Expected Effects of Switching Probability $\psi$ and Threshold $\theta$ Implied by the Round-Wise Integration Model
 
@@
                           "$\\alpha$ (concavity of $v$)"),
-                      "Predictions for changes in $\\psi$" = 
-                        c("More EV maximization for decreasing $\\psi$",
+                      "Predictions for changes in $\\psi$ and $\\theta$" = 
+                        c("More maximization of sampled mean for decreasing $\\psi$",
                           "More as-if underweighting of rare outcomes for increasing $\\psi$",
@@
 
-apa_table(exp_roundwise, caption = "(ref:expectations-roundwise)", note = "The predictions should become more robust for high values of $\\theta$.", escape = FALSE)
+apa_table(exp_roundwise, caption = "(ref:expectations-roundwise)", note = "Expectations should be more closely met for high values of $\\theta$.
+Expectations rely on the assumption that sampling error is controlled for.
+The weighting function is assumed to be supplied with sampled relative frequencies.", escape = FALSE)
 ```
@@
 
-[...]
-
-(ref:expectations-summary) Expected Effects of Switching Probability $\psi$ and Threshold $\theta$ in the Summary Integration Model
+For small switching probabilities $\psi$, the model is expected to make random choices to some unknown degree.
+The respective CPT parameter estimates would be hard to interpret (if at all).
+In the computational analysis, a stochastic version of CPT is estimated to account for such random behavior using a choice sensitivity parameter (see equation (12) below).
+Because the summary integration model chooses the prospect that produces the larger cumulative sum across all sampled outcomes, a linear weighting of outcomes and sampled probabilities is expected for high switching probabilities, i.e., $\alpha = 1$, $\gamma = 1$, and $\delta = 1$.
+This is because for high switching probabilities, differences in the cumulative sum across all sampled outcomes should be indicative for differences in the sampled means.
+If thresholds $\theta$ are low, however, even large switching probabilities might produce some random behavior because of the temporal advantage of the prospect that is first sampled from.
+
+(ref:expectations-summary) Expected Effects of Switching Probability $\psi$ and Threshold $\theta$ Implied by the Summary Integration Model
 
@@
                           "$\\alpha$ (concavity of $v$)"),
-                      "Predictions for changes in $\\psi$" = 
-                        c("More EV maximization for decreasing $\\psi$",
-                          "More as-if underweighting of rare outcomes for increasing $\\psi$",
-                          "$\\geq 1$, increases with $\\psi$",
-                          "1, no effect of $\\psi$",
-                          "$\\leq 1$, decreases with increasing $\\psi$"))
-
-apa_table(exp_summary, caption = "(ref:expectations-summary)", note = "The predictions should become more robust for high values of $\\theta$.", escape = FALSE)
-```
+                      "Predictions for changes in $\\psi$ and $\\theta$" = 
+                        c("Random for low $\\psi$",
+                          "More Maximization of sampled mean for high $\\psi$ and $\\theta$",
+                          "",
+                          "1 for high $\\psi$ and $\\theta$, otherwise ?",
+                          ""))
+
+apa_table(exp_summary, caption = "(ref:expectations-summary)", note = "Expectations rely on the assumption that sampling error is controlled for.
+The weighting function is assumed to be supplied with sampled relative frequencies.", escape = FALSE)
+```
+
+\newpage
 
@@
 
-To substantiate and refine the predictions of the model, a computational implementation was used to simulate the sampling and accumulation process for a set of choices between a safe prospect and a two-outcome (risky) prospect.
-The computational model was written in R and is embodied in the GitHub repository accompanying this paper.
+To substantiate the discussion and obtain the actual predictions of the models, computational implementations thereof were used to simulate the sampling and accumulation process for a set of choices between a safe prospect and a two-outcome (risky) prospect.
+The computational models were written in `R` and are embodied in the `GitHub` repository accompanying this paper.
 The simulation was conducted for varying combinations of $\psi$ and $\theta$.
 For each of these combinations, the simulated data was modeled with a stochastic version of CPT, using Bayesian parameter estimation.
-The simulated choices and estimated CPT parameters can be roughly understood as theory-implied data and data models, which remain to be tested against empirical data [see, e.g., @guestHowComputationalModeling2021; @haslbeckModelingPsychopathologyData2021].
+The simulated choices and estimated CPT parameters can be roughly understood as theory-implied data and data models, which remain to be tested against empirical data.
 

### 2022-05-23 manuscript.Rmd
Update Section 4: Methods + Choice Rates (round-wise integration model)

@@
 
-\newpage
-
 # Simulation Study
 
-To substantiate the discussion and obtain the actual predictions of the models, computational implementations thereof were used to simulate the sampling and accumulation process for a set of choices between a safe prospect and a two-outcome (risky) prospect.
+To substantiate the above discussion and obtain the actual predictions of the models, computational implementations thereof were used to simulate the sampling and accumulation process for a set of choices between a safe prospect and a two-outcome (risky) prospect.
 The computational models were written in `R` and are embodied in the `GitHub` repository accompanying this paper.
-The simulation was conducted for varying combinations of $\psi$ and $\theta$.
+The simulation was conducted for varying combinations of the switching probability $\psi$ and threshold $\theta$.
 For each of these combinations, the simulated data was modeled with a stochastic version of CPT, using Bayesian parameter estimation.
-The simulated choices and estimated CPT parameters can be roughly understood as theory-implied data and data models, which remain to be tested against empirical data.
+The simulated data and estimated CPT parameters can be understood as theory-implied data and data models which remain to be tested against empirical data.
 
@@
 
-A test set of $60$ choice problems was obtained by stratified sampling from an initial set of $10,000$ problems.
+A test set of 60 choice problems was obtained by stratified sampling from an initial set of 10,000 problems.
 The stratification procedure was used to ensure that the test set contained choice problems with small-probability outcomes of different rank---i.e., small-probability outcomes that are either higher or lower than the EV of the risky prospect---as well as choice problems without small-probability outcomes.
 The exact procedure was as follows:
-For each of the $10.000$ problems in the initial set, three outcomes were randomly drawn from a uniform distribution over the interval $[0, 20]$, with the smallest and highest of these three outcomes being assigned to the risky prospect to omit dominance.^[I.e., when one prospect always produces a higher outcome.]
+For each of the 10,000 problems in the initial set, three outcomes were randomly drawn from a uniform distribution over the interval $[0, 20]$, with the smallest and highest of these three outcomes being assigned to the risky prospect to omit dominance.^[I.e., when one prospect always produces a higher outcome.]
 The probability for the lower outcome of the risky prospect, $p_x(x_{low})$, was drawn from a uniform distribution over the interval $(0, 1)$, with the probability of the higher outcome being set to $p_x(x_{high}) = 1-p_x(x_{low})$.
-To obtain the $60$ choice problems of the test set, the initial set was divided into three subsets, where each subset contained either all problems with $p_x(x_{high}) \in (0,.2)$ or $p_x(x_{high}) \in [.2,.8]$ or $p_x(x_{high}) \in (.8,1)$.
+To obtain the 60 choice problems of the test set, the initial set was divided into three subsets, where each subset contained either all problems with $p_x(x_{high}) \in (0,.2)$ or $p_x(x_{high}) \in [.2,.8]$ or $p_x(x_{high}) \in (.8,1)$.
 From each of these subset, then, $20$ choice problems were randomly sampled.
@@
 * *Threshold*: 
-$\theta$ was varied in the interval $[1,5]$ in increments of 1.
-
-* *Decision variable*: The decision variable of a prospect either counts the number of won comparisons---implying an absolute threshold---or how many more comparisons were won relative to the other prospect---implying a relative threshold.^[<!--Open footnote-->
-The results are similar for absolute and relative thresholds. 
+Round-wise integration model: $\theta$ was varied in the interval $[1,5]$ in increments of 1. Summary integration model: $\theta$ was varied in the interval $[15, 75]$ in increments of 15.
+
+* *Decision variable*: Round-wise integration model: The decision variable of a prospect either counts the number of won comparisons---implying an absolute threshold---or how many more or less comparisons were won relative to the other prospect---implying a relative threshold.
+Summary integration model: The decision variable of a prospect is either the cumulative sum across all sampled outcomes or the difference in cumulative sums, implying absolute and relative thresholds.^[<!--Open footnote-->
+For both models, the results are similar for absolute and relative thresholds.
 For simplification, only the results of the absolute thresholds are reported in the main text.
@@
 \noindent
-Since $\psi$ introduces some stochasticity into the sampling and accumulation process, each of the 100 resulting parameter combinations was used 100 times---resembling 100 independent agents---to solve the test set.
-In sum, then 100 (parameter combinations) $\times$ 100 (agents) $\times$ 60 (choice problems)  = 600,000 sampling and accumulation processes were simulated.
-The respective dataset can be retrieved from the accompanying `GitHub repository`.
+Since the switching probability $\psi$ introduces some stochasticity into the sampling and accumulation process, each of the 100 resulting parameter combinations was used 100 times---resembling 100 independent agents---to solve the test set.
+In sum, then 2 (models) $\times$ 100 (parameter combinations) $\times$ 100 (agents) $\times$ 60 (choice problems)  = 1,200,000 sampling and accumulation processes were simulated.
+The respective datasets can be both recreated or directly retrieved from the accompanying `GitHub` repository.
 
@@
 
-The choice data for each parameter combination was separately modeled in CPT, using the value function of @tverskyAdvancesProspectTheory1992 and the weighting function of @goldsteinExpressionTheoryPreference1987.
-To demonstrate that the distortions from linear probability weighting are not just due to differences between the latent objective probabilities and the relative frequencies with which the outcomes were actually sampled over the course of a sampling and accumulation process, the latter were supplied as probability information to the weighting function.
+The choice data implied by each integration model and parameter combination was separately modeled in CPT, using the value function of @tverskyAdvancesProspectTheory1992 and the weighting function of @goldsteinExpressionTheoryPreference1987.
+Again, to demonstrate that the distortions from linear probability weighting are not just due to sampling error, the relative frequencies with which the outcomes were actually sampled over the course of a sampling and accumulation process were supplied as probability information to the weighting function.
 To accommodate for possible random choice behavior that may be exerted by a parameter combination, the CPT model was amended with the logit choice rule
 $$
-p(P'^{safe}) = \frac{1} {1 + e^{-\rho(V_{safe}^{\frac{1}{\alpha}}-V_{risky}^{\frac{1}{\alpha}})}}
+p(P^{safe}) = \frac{1} {1 + e^{-\rho(V_{safe}^{\frac{1}{\alpha}}-V_{risky}^{\frac{1}{\alpha}})}}
 \; ,
-\tag{16}
-$$
-where $p(P'^{safe})$ is the probability that the safe prospect is chosen over the risky prospect, $V_{safe}$ and $V_{risky}$ are the valuations of the safe and risky prospect that result from the parameter estimates of the value and weighting function, and $\rho \geq 0$ is a sensitivity parameter.
-$\rho$ governs how strongly the choice between prospects depends on the differences in the valuations of the prospects, i.e., the core CPT model.
-Specifically, $\rho = 0$ implies no sensitivity, and thus a random choice.
+\tag{12}
+$$
+where $p(P^{safe})$ is the probability that the safe prospect is chosen over the risky prospect, $V_{safe}$ and $V_{risky}$ are the valuations of the safe and risky prospect that result from the parameter estimates of the value and weighting function, and $\rho \geq 0$ is a sensitivity parameter.
+$\rho$ governs how strongly the choices between prospects depend on the differences in the valuations of the prospects, i.e., the core CPT model.
+Specifically, $\rho = 0$ implies no sensitivity, and thus a completely random choice.
 In turn, for increasing values of $\rho$, the probability of choosing the prospect with the higher valuation increases.
@@
 Since for a given choice problem and parameter combination of the sampling and accumulation model there should be no systematic differences among the 100 iterations (synthetic agents), their data is combined for the estimation of the free parameters.
-Such a grouped approach should reveal the main effects of a given parameter combination of the sampling and accumulation model on the resulting choices and ignore unsystematic differences or noise that may be caused by the stochasticity introduced by $\psi$.
-To facilitate comparisons across parameter combinations of the sampling and accumulation model, uninformative prior distributions were used throughout for all four parameters.
+Such a grouped approach should reveal the main effects of a given parameter combination of the sampling and accumulation model on the resulting choices and ignore unsystematic differences or noise that may be caused by the stochasticity introduced by the switching probability $\psi$.^[<!--Open footnote-->Note that this is quite a hard assumption that works for this simulation but will be hardly met for empirical data, where heterogeneity among people is common.
+If heterogeneity is assumed, hierarchical implementation of CPT may be used [cf.
+@nilssonHierarchicalBayesianParameter2011] <!--Close footnote-->.]
+To facilitate comparisons across parameter combinations of the sampling and accumulation models, uninformative prior distributions were used throughout for all four parameters.
 Specifically, the prior distributions $\alpha \sim U(0,1)$, $\gamma \sim U(0,2)$, $\delta \sim U(0,10)$, and $\rho \sim U(0,5)$ were used.
 
-To estimate the posterior distributions of the free parameters, Markov Chain Monte Carlo sampling as implemented in JAGS was used, where 20 chains of 40,000 samples each were run after a warm-up period of 1000 samples.
+```{r convergence-statistics, include=FALSE}
+effsize <- min(cpt$n.eff)
+rhat <- round(max(cpt$Rhat), 4)
+```
+
+To estimate the posterior distributions of the free parameters, Markov Chain Monte Carlo sampling as implemented in `JAGS` was used, where 20 chains of 40,000 samples each were run after a warm-up period of 1000 samples.
 To reduce potential autocorrelation during the sampling process, only every 20th sample was kept (thinning), leaving a total of 40,000 samples across chains.
-The minimum effective sample size was `r min(cpt$n.eff)`.
-The potential scale reduction factor $\hat{R}$ [@gelmanInferenceIterativeSimulation1992] was $\leq$ `r round(max(cpt$Rhat), 4)` for all models and parameters, indicating good convergence.
+The minimum effective sample size was `r format(effsize, big.mark=",", trim=TRUE)`.
+The potential scale reduction factor $\hat{R}$ [@gelmanInferenceIterativeSimulation1992] was $\leq$ `r rhat` for all models and parameters, indicating good convergence.
 
@@
 
-Overall, the results of the simulation match the predictions from Table\ \@ref(tab:predictions), however, with some exceptions concerning the estimates for the parameter $\delta$ of the weighting function.
-We start by inspecting how the length of the information-processing chain changes with varying combinations of $\psi$ and $\theta$.
-
-### Simulated Length of the Information-Processing Chains
-
-Figure\ \@ref(fig:chain-length) displays the median number of outcomes sampled over the course of a sampling and accumulation process for each parameter combination.
+Below, the round-wise and the summary integration model are discussed separately.
+However, except for the choice rates, displayed in Figures\ \@ref(fig:choice-rates-roundwise) and \@ref(fig:choice-rates-summary), the results of both models are displayed in the same figures using a green and blue color-coding for the round-wise and the summary integration model, respectively.
+
+### Round-Wise Integration Model
+
+Overall, the results of the simulations (model predictions) match the expectations formulated in Table\  \@ref(tab:expectations-roundwise), however, with some exceptions concerning the estimates for the parameter $\delta$ of the weighting function.
+First, it is inspected how the lengths of the sampling and accumulation processes---measured in the number of sampled outcomes---changes with varying combinations of the switching probability $\psi$ and threshold $\theta$.
+
+#### Number of Sampled Outcomes
+
+Figure\ \@ref(fig:chain-length) displays the number of outcomes sampled over the course of a sampling and accumulation process for each parameter combination.
 The model predicts a decrease in the overall number of sampled outcomes with increases in the switching probability $\psi$.
-As can be seen from the change in the slopes of the lines in Figure\ \@ref(fig:chain-length), the magnitude of this decrease diminishes as the relative increase in $\psi$ diminishes.^[<!--Open footnote-->I.e., the ratio of high values of $\psi$ is smaller than the ratio of small values of $\psi$.<!--Close footnote-->]
-Moreover, the overall number of sampled outcomes increases with thresholds at a relatively constant rate.
-Consider also the dashed horizontal line in Figure\ \@ref(fig:chain-length), which displays the median number of 14 outcomes that @wulffMetaanalyticReviewTwo2018 found to be sampled in 10,712 trials involving a choice between a safe and a two-outcome prospect in the sampling paradigm.
-Notably, the parameter combinations that closely resemble the round-wise strategy---i.e., high values of $\psi$ and $\theta$---or the summary strategy---i.e., low values of $\psi$ and $\theta$---lead to overall numbers of sampled outcomes that come close to the meta-analytic median.
-Moreover, while parameter combinations that can be understood as falling in between the round-wise and the summary strategy also lead to overall numbers of sampled outcomes that approximate the meta-analytic median, extreme combinations produce numbers that are considerably lower or higher, and thus less plausible from an empirical stance.
+As can be seen from the changes in the slopes of the gray lines of the smoothed functions, the magnitude of this decrease diminishes as the relative increase in $\psi$ diminishes.
+The overall number of sampled outcomes increases with thresholds at a relatively constant rate.
+Consider also the dashed horizontal lines, which display the median number of 14 outcomes that @wulffMetaanalyticReviewTwo2018 found to be sampled in 10,712 trials involving a choice between a safe and a two-outcome prospect in the sampling paradigm.
+The parameter combinations that closely resemble the links between sampling and decision strategies proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010]---i.e, high values of $\psi$ and $\theta$ for piecewise sampling and round-wise decisions vs.
+low values of $\psi$ and $\theta = 1$ for comprehensive sampling and summary decisions)---led to overall numbers of sampled outcomes that come close to the meta-analytic median found by @wulffMetaanalyticReviewTwo2018.
+Moreover, while parameter combinations that can be understood as falling in between the originally proposed links---i.e., values in the mid-range for both $\psi$ and $\theta$---also led to overall numbers of sampled outcomes that approximate the meta-analytic median, extreme combinations of both models produce numbers that are considerably lower or higher, and thus less plausible from an empirical stance.
 
@@
 
-\begin{figure}[t]
-\caption{Lengths of Information-Processing Chains}
+\begin{figure}[t!]
+\caption{Lengths of the Sampling and Accumulation Processes}
 \includegraphics[width=1\linewidth]{manuscript_files/chain-length} \label{fig:chain-length}
-\raggedright \textit{Note.} Add note
+\raggedright \textit{Note.} Each point represents a single sampling and accumulation process (choice trial) and is the overall number of outcomes sampled over the course of this process.
+The gray lines are estimates of \textit{ggplot2}'s \texttt{stat\_smooth()} function.
+All gray-dashed horizontal lines represent the meta-analytic median, med = 14, for choices between a safe and a risky prospect, found by \protect\hyperlink{ref-wulffMetaanalyticReviewTwo2018}{Wulff et al., 2018}.
+Note that for better resolution the scales on the y-axis differ for different levels of \(\theta\).
 \end{figure}
 
-### Simulated Final Choice
-
-Figures\ \@ref(fig:choice-rates-roundwise) and \@ref(fig:choice-rates-summary) display the rates of choices that did not maximize the latent EV (hereafter: false response rates) for each combination of $\psi$ and $\theta$.
-To demonstrate that the deviations from EV maximization are not just due to sampling error, the rates of choices that did not maximize the sampled mean are displayed in gray. 
+#### Final Choice
+
+For each combination of the switching probability $\psi$ and the threshold $\theta$, Figure\ \@ref(fig:choice-rates-roundwise) displays the rates of choices that did not maximize the sampled mean (i.e., the mean across all outcomes sampled over the course of a sampling and accumulation process, hereafter: false response rates).
 Rates are separated for presence and rank of small-probability outcomes.
 Consider first the top panel showing the false response rates across all problems where the low-rank outcome of the risky prospect possesses a small probability:
-Over the course of short stochastic processes, then, the low-rank outcome tends to be sampled less often than would be objectively warranted, leading to an inflation of the respective mean of the risky prospect.
-Accordingly, the top panels show that the rates of false choices of the risky prospect increase with $\psi$, but the rates of false safe choices remain generally low.
-More specifically, the higher the values of $\psi$, the more severe should the inflation of the mean of the risky prospect be. 
-As a consequence, if the risky prospect possesses the smaller EV, an increase in $\psi$ increases the risk to deviate from EV maximization---taking the form of an as-if underweighting of rare outcomes---by falsely choosing the risky prospect on the basis of a mean comparison.
-In turn, if the risky prospect possesses the larger EV, the inflation of their means decreases the risk to falsely choose the safe prospect.
+For high switching probabilities $\psi$, the low-rank outcome was expected to be sampled less often than would be objectively warranted *within each* comparison round, leading to an inflation of the respective round means of the risky prospect.
+Accordingly, the top panels show that for each threshold $\theta$ the rates of false choices of the risky prospect increase with the switching probability $\psi$, thereby causing deviation from sampled mean maximization that take the form of an as-if underweighting of rare outcomes.
+In turn, rates of false safe choices remain generally low.
+To demonstrate how the false response rates would have turned out given the normative solutions of EV maximization---i.e., when sampling error is not controlled for---, the rates of choices that did not maximize the latent EV are displayed in gray.
+Here, a similar but more severe pattern can be found, showing that sampling error exercises an influence beyond the effects implied by the interplay of the sampling strategy and the round-wise integration/decision strategy.
 Note from the middle panel that the pattern of false response rates reverses for problems where the high-rank outcome of the risky prospect possesses a small probability.
-In this case, then, the mean of the risky prospect tends to be more deflated the higher the value of $\psi$, which increases the risk of falsely choosing the safe prospect.
-From the reduced false response rates in the bottom panel, we see that the inflation and deflation of the means for high values of $\psi$ is significantly attenuated when a prospect possesses no small-probability outcome.
+In this case, then, the means of the risky prospect within each comparison round tend to be more deflated the higher the switching probability $\psi$, which increases the risk of falsely choosing the safe prospect.
+Again, the resulting choice patterns resemble an as-if underweighting of rare outcomes.
+Importantly, note from the reduced false response rates in the bottom panel that the inflation and deflation of the means for high switching probabilities must be significantly attenuated when a prospect possesses no small-probability outcome.
+In sum, then, the simulated choices show that the potential interplay between sampling strategies and a round-wise integration/decision strategy can lead to distinct choice patterns and as-if weighting patterns in DFE, which, however, strongly depend on the structure of the choice problems.
 
@@
 
+#### CPT Parameters
+
+Figure\ \@ref(fig:weighting-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the curvature parameter $\gamma$ and the elevation parameter $\delta$, as well as the resulting graphical shape of the weighting function.
+Note that the estimates for the parameter combination $\theta = 1$ and $\psi = 1$ have large posterior intervals.
+In these cases, no relative frequencies other than 0 and 1 are supplied to the weighting function, which may explain that the values in between cannot be reliably accounted for.
+However, for $\theta = 1$ and $\psi < 1$, the estimates imply a linear weighting pattern, in line with the explanation that if the mind were to infer the latent objective probabilities of outcomes from the sampled relative frequencies and to follow the principle of EV maximization, sampling error can account for any deviations from it.^[<!--Open footnote-->
+Note that the same line of reasoning holds, were the mind to approximate the solutions of EV maximization by choosing the prospect with higher sampled mean.
+<!--Close footnote-->]
+Note also Figure\ \@ref(fig:choice-rates-roundwise), where there are no choices for $\theta = 1$ that do not maximize the sampled mean.
+
+For $\theta > 1$, the estimates substantiate the prediction that $\gamma$ takes values $\geq 1$ which increase with $\psi$, resulting in a increasingly pronounced S-shaped weighting function.
+In other words, the higher the value of $\psi$, the more severe is the underweighting (overweighting) of the high-rank outcome of the risky prospect in CPT, if it is of small (large) probability.
+$\delta$ takes values $\geq 1$ and increases slightly with $\psi$, causing the overweighting of the high-rank outcome of the risky prospect to extend across the mid-point. 
+[...]
+
+```{r weighting-parameters, include=FALSE}
+
+label_theta <- function(string) {
+  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
+}
+
+# plot gamma estimates
+gamma <- cpt_absolute %>%
+  filter(parameter == "gamma") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(gamma),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
+  theme_minimal()
+
+# plot delta estimates
+delta <- cpt_absolute %>%
+  filter(parameter == "delta") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(delta),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
+  theme_minimal()
+
+# merge plots
+ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
+```
+
+\begin{figure}[t]
+\caption{Parameter Estimates of the Weighting Function}
+\includegraphics{manuscript_files/figure-latex/weighting-parameters-1} \label{fig:weighting-parameters}
+\raggedright \textit{Note.} Add note
+\end{figure}
+
+Figure\ \@ref(fig:sensitivity-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$.
+An increase in $\psi$ leads to a decrease in $\alpha$, reflecting that outcome information are largely ignored if choices are based on ordinal comparisons of single outcomes rather than on means of large samples.
+The respective shape of the value function is more concave, the higher the values of $\psi$. 
+Finally, $\rho$ varied systematically such that the choices were more sensitive to the valuations of the core CPT model for low values of $\psi$.
+However, even for high values of $\psi$, the choices did not appear to be random. [...]
+
+```{r sensitivity-parameters, include=FALSE}
+
+# plot alpha estimates
+alpha <- cpt_absolute %>%
+  filter(parameter == "alpha") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(alpha),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
+  theme_minimal()
+
+# plot rho estimates
+rho <- cpt_absolute %>%
+  filter(parameter == "rho") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(rho),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
+  theme_minimal()
+
+# merge plots
+ggarrange(alpha, rho, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
+```
+
+\begin{figure}[t]
+\caption{Parameter Estimates of the Outcome and Choice Sensitivity Parameter}
+\includegraphics{manuscript_files/figure-latex/sensitivity-parameters-1} \label{fig:sensitivity-parameters}
+\raggedright \textit{Note.} Add note
+\end{figure}
+
+Figure\ \@ref(fig:function-forms) displays the resulting graphical shapes of the weighting and value function.
+
+```{r function-forms, include=FALSE}
+
+# plot weighting function
+
+## compute decision weights
+
+weights <- cpt_absolute %>%
+  select(model, s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
+  select(-c(alpha, rho)) %>%
+  expand_grid(p = seq(0, 1, .05)) %>%
+  mutate(w = round(  (delta * p^gamma)/ ((delta * p^gamma)+(1-p)^gamma), 2))
+
+## plot graphs
+
+wf <- weights %>% 
+  ggplot(aes(p, w, group = s, color = s)) +
+  facet_wrap(~model~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  labs(x = "Experienced Probability",
+       y = expression(pi),
+       color = expression(psi)) +
+  scale_x_continuous(breaks = seq(0, 1, .5)) +
+  scale_y_continuous(breaks = seq(0, 1, .5)) +
+  geom_line(size = .5) +
+  scale_color_viridis(option = "mako") +
+  theme_minimal()
+
+# value functions
+
+values <- cpt_absolute %>%
+  select(model, s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
+  select(-c(gamma, delta, rho)) %>%
+  expand_grid(x = seq(0, 20, .5)) %>%  
+  mutate(v = round(x^alpha, 2))
+
+vf <- values %>% 
+  ggplot(aes(x, v, group = s, color = s)) +
+  facet_wrap(model~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  labs(x = "Objective Outcome",
+       y = "Subjective Value",
+       color=expression(psi)) +
+  scale_x_continuous(limits = c(0,20), breaks = seq(0, 20, 10)) +
+  geom_line(size = .5) +
+  scale_color_viridis(option = "mako") +
+  theme_minimal()
+
+# merge plots
+ggarrange(wf, vf, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
+```
+
+\begin{figure}[t]
+\caption{Estimated Graphical Shape of the Weighting and Value Function}
+\includegraphics{manuscript_files/figure-latex/function-forms-1} \label{fig:function-forms}
+\raggedright \textit{Note.} Add note
+\end{figure}
+
+### Summary Integration Model
+
+#### Number of Sampled Outcomes
+
+#### Final Choice
+
 ```{r choice-rates-summary, include=FALSE}
@@
 
-### Simulation-Implied Cumulative Prospect Theory
-
-Figure\ \@ref(fig:weighting-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the curvature parameter $\gamma$ and the elevation parameter $\delta$, as well as the resulting graphical shape of the weighting function.
-Note that the estimates for the parameter combination $\theta = 1$ and $\psi = 1$ have large posterior intervals.
-In these cases, no relative frequencies other than 0 and 1 are supplied to the weighting function, which may explain that the values in between cannot be reliably accounted for.
-However, for $\theta = 1$ and $\psi < 1$, the estimates imply a linear weighting pattern, in line with the explanation that if the mind were to infer the latent objective probabilities of outcomes from the sampled relative frequencies and to follow the principle of EV maximization, sampling error can account for any deviations from it.^[<!--Open footnote-->
-Note that the same line of reasoning holds, were the mind to approximate the solutions of EV maximization by choosing the prospect with higher sampled mean.
-<!--Close footnote-->]
-Note also Figure\ \@ref(fig:choice-rates-roundwise), where there are no choices for $\theta = 1$ that do not maximize the sampled mean.
-
-For $\theta > 1$, the estimates substantiate the prediction that $\gamma$ takes values $\geq 1$ which increase with $\psi$, resulting in a increasingly pronounced S-shaped weighting function.
-In other words, the higher the value of $\psi$, the more severe is the underweighting (overweighting) of the high-rank outcome of the risky prospect in CPT, if it is of small (large) probability.
-$\delta$ takes values $\geq 1$ and increases slightly with $\psi$, causing the overweighting of the high-rank outcome of the risky prospect to extend across the mid-point. 
-[...]
-
-```{r weighting-parameters, include=FALSE}
-
-label_theta <- function(string) {
-  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
-}
-
-# plot gamma estimates
-gamma <- cpt_absolute %>%
-  filter(parameter == "gamma") %>%
-  ggplot(aes(s, mean, color = model)) +
-  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
-  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
-  labs(x = expression(paste("Switching Probability ", psi)), 
-       y = expression(gamma),
-       color = "Model") +
-  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  geom_point() +
-  geom_line() +
-  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
-  theme_minimal()
-
-# plot delta estimates
-delta <- cpt_absolute %>%
-  filter(parameter == "delta") %>%
-  ggplot(aes(s, mean, color = model)) +
-  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
-  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
-  labs(x = expression(paste("Switching Probability ", psi)), 
-       y = expression(delta),
-       color = "Model") +
-  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  geom_point() +
-  geom_line() +
-  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
-  theme_minimal()
-
-# merge plots
-ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
-```
-
-\begin{figure}[t]
-\caption{Parameter Estimates of the Weighting Function}
-\includegraphics{manuscript_files/figure-latex/weighting-parameters-1} \label{fig:weighting-parameters}
-\raggedright \textit{Note.} Add note
-\end{figure}
-
-Figure\ \@ref(fig:sensitivity-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$.
-An increase in $\psi$ leads to a decrease in $\alpha$, reflecting that outcome information are largely ignored if choices are based on ordinal comparisons of single outcomes rather than on means of large samples.
-The respective shape of the value function is more concave, the higher the values of $\psi$. 
-Finally, $\rho$ varied systematically such that the choices were more sensitive to the valuations of the core CPT model for low values of $\psi$.
-However, even for high values of $\psi$, the choices did not appear to be random. [...]
-
-```{r sensitivity-parameters, include=FALSE}
-
-# plot alpha estimates
-alpha <- cpt_absolute %>%
-  filter(parameter == "alpha") %>%
-  ggplot(aes(s, mean, color = model)) +
-  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
-  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
-  labs(x = expression(paste("Switching Probability ", psi)), 
-       y = expression(alpha),
-       color = "Model") +
-  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  geom_point() +
-  geom_line() +
-  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
-  theme_minimal()
-
-# plot rho estimates
-rho <- cpt_absolute %>%
-  filter(parameter == "rho") %>%
-  ggplot(aes(s, mean, color = model)) +
-  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
-  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
-  labs(x = expression(paste("Switching Probability ", psi)), 
-       y = expression(rho),
-       color = "Model") +
-  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
-  geom_point() +
-  geom_line() +
-  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
-  theme_minimal()
-
-# merge plots
-ggarrange(alpha, rho, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
-```
-
-\begin{figure}[t]
-\caption{Parameter Estimates of the Outcome and Choice Sensitivity Parameter}
-\includegraphics{manuscript_files/figure-latex/sensitivity-parameters-1} \label{fig:sensitivity-parameters}
-\raggedright \textit{Note.} Add note
-\end{figure}
-
-Figure\ \@ref(fig:function-forms) displays the resulting graphical shapes of the weighting and value function.
-
-```{r function-forms, include=FALSE}
-
-# plot weighting function
-
-## compute decision weights
-
-weights <- cpt_absolute %>%
-  select(model, s, boundary, a, parameter, mean) %>%
-  pivot_wider(names_from = parameter, values_from = mean) %>%
-  select(-c(alpha, rho)) %>%
-  expand_grid(p = seq(0, 1, .05)) %>%
-  mutate(w = round(  (delta * p^gamma)/ ((delta * p^gamma)+(1-p)^gamma), 2))
-
-## plot graphs
-
-wf <- weights %>% 
-  ggplot(aes(p, w, group = s, color = s)) +
-  facet_wrap(~model~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
-  labs(x = "Experienced Probability",
-       y = expression(pi),
-       color = expression(psi)) +
-  scale_x_continuous(breaks = seq(0, 1, .5)) +
-  scale_y_continuous(breaks = seq(0, 1, .5)) +
-  geom_line(size = .5) +
-  scale_color_viridis(option = "mako") +
-  theme_minimal()
-
-# value functions
-
-values <- cpt_absolute %>%
-  select(model, s, boundary, a, parameter, mean) %>%
-  pivot_wider(names_from = parameter, values_from = mean) %>%
-  select(-c(gamma, delta, rho)) %>%
-  expand_grid(x = seq(0, 20, .5)) %>%  
-  mutate(v = round(x^alpha, 2))
-
-vf <- values %>% 
-  ggplot(aes(x, v, group = s, color = s)) +
-  facet_wrap(model~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
-  labs(x = "Objective Outcome",
-       y = "Subjective Value",
-       color=expression(psi)) +
-  scale_x_continuous(limits = c(0,20), breaks = seq(0, 20, 10)) +
-  geom_line(size = .5) +
-  scale_color_viridis(option = "mako") +
-  theme_minimal()
-
-# merge plots
-ggarrange(wf, vf, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
-```
-
-\begin{figure}[t]
-\caption{Estimated Graphical Shape of the Weighting and Value Function}
-\includegraphics{manuscript_files/figure-latex/function-forms-1} \label{fig:function-forms}
-\raggedright \textit{Note.} Add note
-\end{figure}
+#### CPT Parameters
 

### 2022-05-24 manuscript_appendix.Rmd
Review introduction
add appendix

@@
-```{r A-setup, include=FALSE}
+```{r include=FALSE}
 knitr::opts_chunk$set(echo = F, #omit messages
-                      fig.align = "l", #align figures to left margin
-                      fig.pos = "t")
+                      fig.align = "l" #align figures to left margin
+                      )
 ```
 
+Note that the figures presented in the appendix differ from those presented in the main text to the extent that the thresholds $\theta$ have a different meaning. 
+That is, for the round-wise integration model, $\theta$ is not the absolute number of mean comparisons a prospect must win (absolute threshold), but the required difference in the number of wins between prospects (relative threshold).
+For the summary integration model, $\theta$ is not the absolute cumulative sum across all sampled outcomes a prospect must reach (absolute threshold), but the differences in these sums between prospects.
+
+\newpage
+
 \begin{figure}
-\caption{Effect of Switching Probability on Rates of False Risky and False Safe Choices for 2-Outcome Prospects with High Rank Outcomes of Different Probability}\label{fig:A-choice-rates}
-\includegraphics{manuscript_files/figure-latex/A-choice-rates-1}
-\textit{Note.} A note.
+\caption{Rates of False Risky and False Safe Choices in the Round-Wise Integration Model}
+\includegraphics{manuscript_files/figure-latex/choice-rates-roundwise-relative-1} \label{fig:choice-rates-roundwise-relative}
 \end{figure}
@@
 \begin{figure}
-\caption{Parameter Estimates of the Weighting Function of Goldstein and Einhorn (1987) for Different Simulation Parameters}\label{fig:A-weighting-parameters}
-\includegraphics{manuscript_files/figure-latex/A-weighting-parameters-1}
+\caption{Rates of False Risky and False Safe Choices in the Round-Wise Integration Model}
+\includegraphics{manuscript_files/figure-latex/choice-rates-summary-relative-1} \label{fig:choice-rates-summary-relative}
 \end{figure}
@@
 \begin{figure}
-\caption{Parameter Estimates of the Value Function of Tversky and Kahneman (1992) and of the Logit Choice Rule for Different Simulation Parameters}\label{fig:A-value-parameters}
-\includegraphics{manuscript_files/figure-latex/A-value-parameters-1}
+\caption{Parameter Estimates of the Weighting Function}
+\includegraphics{manuscript_files/figure-latex/weighting-parameters-relative-1} \label{fig:weighting-parameters-relative}
 \end{figure}
@@
 \begin{figure}
-\caption{Estimated Graphical Shapes of the Weighting and Value Function for Different Simulation Parameters}\label{fig:A-cpt-graphs}
-\includegraphics{manuscript_files/figure-latex/A-cpt-graphs-1}
+\caption{Parameter Estimates of the Outcome and Choice Sensitivity Parameter}
+\includegraphics{manuscript_files/figure-latex/sensitivity-parameters-relative-1} \label{fig:sensitivity-parameters-relative}
 \end{figure}
+
+\newpage
+
+\begin{figure}
+\caption{Estimated Graphical Shape of CPT's Weighting and Value Function}
+\includegraphics{manuscript_files/figure-latex/function-forms-relative-1} \label{fig:function-forms-relative}
+\end{figure}

### 2022-05-24 manuscript.Rmd
Update Section 4: Simulation Study

@@
 bibliography      : references.bib
-csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+appendix          : "manuscript_appendix.Rmd"
+csl               : "C:/Users/Linus Hof/Documents/Psychologie/ARC/sampling-in-dfe/apa.csl"
 
@@
 Below, the round-wise and the summary integration model are discussed separately.
-However, except for the choice rates, displayed in Figures\ \@ref(fig:choice-rates-roundwise) and \@ref(fig:choice-rates-summary), the results of both models are displayed in the same figures using a green and blue color-coding for the round-wise and the summary integration model, respectively.
+However, except for the choice rates, displayed in Figures\ \@ref(fig:choice-rates-roundwise) and \@ref(fig:choice-rates-summary), the results of both models are reported in the same figures using a green and blue color-coding for the round-wise and the summary integration model, respectively.
 
@@
 Overall, the results of the simulations (model predictions) match the expectations formulated in Table\  \@ref(tab:expectations-roundwise), however, with some exceptions concerning the estimates for the parameter $\delta$ of the weighting function.
-First, it is inspected how the lengths of the sampling and accumulation processes---measured in the number of sampled outcomes---changes with varying combinations of the switching probability $\psi$ and threshold $\theta$.
+First, it is inspected how the lengths of the sampling and accumulation processes---measured in the number of sampled outcomes---change with varying combinations of the switching probability $\psi$ and threshold $\theta$.
 
@@
 
-Figure\ \@ref(fig:chain-length) displays the number of outcomes sampled over the course of a sampling and accumulation process for each parameter combination.
-The model predicts a decrease in the overall number of sampled outcomes with increases in the switching probability $\psi$.
-As can be seen from the changes in the slopes of the gray lines of the smoothed functions, the magnitude of this decrease diminishes as the relative increase in $\psi$ diminishes.
+Figure\ \@ref(fig:sample-sizes) displays the number of outcomes sampled over the course of a sampling and accumulation process for each combination of the switching probability $\psi$ and the threshold $\theta$.
+The model predicts a decrease in the overall number of sampled outcomes with increases in the switching probability.
+As can be seen from the changes in the slopes of the gray lines of the smoothed functions, the magnitude of this decrease diminishes as the relative increase in the switching probability diminishes.
 The overall number of sampled outcomes increases with thresholds at a relatively constant rate.
-Consider also the dashed horizontal lines, which display the median number of 14 outcomes that @wulffMetaanalyticReviewTwo2018 found to be sampled in 10,712 trials involving a choice between a safe and a two-outcome prospect in the sampling paradigm.
-The parameter combinations that closely resemble the links between sampling and decision strategies proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010]---i.e, high values of $\psi$ and $\theta$ for piecewise sampling and round-wise decisions vs.
-low values of $\psi$ and $\theta = 1$ for comprehensive sampling and summary decisions)---led to overall numbers of sampled outcomes that come close to the meta-analytic median found by @wulffMetaanalyticReviewTwo2018.
-Moreover, while parameter combinations that can be understood as falling in between the originally proposed links---i.e., values in the mid-range for both $\psi$ and $\theta$---also led to overall numbers of sampled outcomes that approximate the meta-analytic median, extreme combinations of both models produce numbers that are considerably lower or higher, and thus less plausible from an empirical stance.
+Consider also the dashed horizontal lines, which display the median number of 14 outcomes that @wulffMetaanalyticReviewTwo2018 found to be sampled in 10,712 trials involving a choice between a safe and a two-outcome prospect in the sampling paradigm:
+The parameter combinations that closely resemble the links between sampling and decision strategies originally proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010]---i.e, high switching probabilities and thresholds for piecewise sampling and round-wise decisions vs.
+low switching probabilities and a single mean comparison ($\theta = 1$) for comprehensive sampling and summary decisions---lead to overall numbers of sampled outcomes that come close to the meta-analytic median.
+Moreover, while parameter combinations that can be understood as falling in between the originally proposed links---i.e., mid-range values for both switching probability and threshold---also lead to overall numbers of sampled outcomes that approximate the meta-analytic median, extreme combinations (e.g., low switching probability and high threshold) produce numbers that are considerably lower or higher, and thus less plausible from an empirical stance.
 
 ```{r chain-length, eval = FALSE}
+
+# labeller functions
+label_theta <- function(string) {
+  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
+}
+
 chain_lengths <- choices_absolute %>%
   ggplot(aes(x = s, y = n_sample, color = model)) +
-  facet_wrap(~a, nrow = 2, scales = "free") + 
-  labs(x = expression(psi),
+  facet_wrap(~a, nrow = 2, scales = "free", labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  labs(x = expression(paste("Switching Probability ", psi)),
        y = "Number of Sampled Outcomes",
        color = "Model") + 
-  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5))+
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) +
   geom_jitter(alpha = .05) + 
@@
 \caption{Lengths of the Sampling and Accumulation Processes}
-\includegraphics[width=1\linewidth]{manuscript_files/chain-length} \label{fig:chain-length}
-\raggedright \textit{Note.} Each point represents a single sampling and accumulation process (choice trial) and is the overall number of outcomes sampled over the course of this process.
+\includegraphics[width=1\linewidth]{manuscript_files/sample-sizes} \label{fig:sample-sizes}
+\raggedright \textit{Note.} Columns represent different thresholds.
+x-axes display the switching probability.
+Each point represents a single sampling and accumulation process (choice trial) for the respective combination of the threshold and switching probability, and is the overall number of outcomes sampled over the course of this process.
 The gray lines are estimates of \textit{ggplot2}'s \texttt{stat\_smooth()} function.
@@
 
-For each combination of the switching probability $\psi$ and the threshold $\theta$, Figure\ \@ref(fig:choice-rates-roundwise) displays the rates of choices that did not maximize the sampled mean (i.e., the mean across all outcomes sampled over the course of a sampling and accumulation process, hereafter: false response rates).
+For each combination of the switching probability and the threshold, Figure\ \@ref(fig:choice-rates-roundwise) displays the rates of choices that did not maximize the sampled mean (i.e., the mean across all outcomes sampled over the course of a sampling and accumulation process, hereafter: false response rates).
 Rates are separated for presence and rank of small-probability outcomes.
 Consider first the top panel showing the false response rates across all problems where the low-rank outcome of the risky prospect possesses a small probability:
-For high switching probabilities $\psi$, the low-rank outcome was expected to be sampled less often than would be objectively warranted *within each* comparison round, leading to an inflation of the respective round means of the risky prospect.
-Accordingly, the top panels show that for each threshold $\theta$ the rates of false choices of the risky prospect increase with the switching probability $\psi$, thereby causing deviation from sampled mean maximization that take the form of an as-if underweighting of rare outcomes.
+For high switching probabilities, the low-rank outcome was expected to be sampled less often than would be objectively warranted *within each* comparison round, leading to an inflation of the respective round means of the risky prospect.
+Accordingly, the top panels show that for each threshold the rates of false choices of the risky prospect increase with the switching probability, causing deviations from sampled mean maximization that take the form of an as-if underweighting of rare outcomes.
 In turn, rates of false safe choices remain generally low.
-To demonstrate how the false response rates would have turned out given the normative solutions of EV maximization---i.e., when sampling error is not controlled for---, the rates of choices that did not maximize the latent EV are displayed in gray.
-Here, a similar but more severe pattern can be found, showing that sampling error exercises an influence beyond the effects implied by the interplay of the sampling strategy and the round-wise integration/decision strategy.
+To demonstrate how the false response rates would have turned out given the normative solutions of EV maximization (i.e., when sampling error is not controlled for), the rates of choices that did not maximize the latent EV are displayed in gray.
+Here, a similar but more severe pattern can be found, showing that sampling error exercises an influence independent of the effects implied by the interplay of the sampling strategies and the round-wise integration/decision strategy.
 Note from the middle panel that the pattern of false response rates reverses for problems where the high-rank outcome of the risky prospect possesses a small probability.
-In this case, then, the means of the risky prospect within each comparison round tend to be more deflated the higher the switching probability $\psi$, which increases the risk of falsely choosing the safe prospect.
-Again, the resulting choice patterns resemble an as-if underweighting of rare outcomes.
+In this case, then, the means of the risky prospect within each comparison round tend to be more deflated the higher the switching probability, which increases the risk of falsely choosing the safe prospect.
+Again, the resulting choice patterns resemble an as-if underweighting of rare outcomes pattern.
 Importantly, note from the reduced false response rates in the bottom panel that the inflation and deflation of the means for high switching probabilities must be significantly attenuated when a prospect possesses no small-probability outcome.
@@
 
-```{r choice-rates-roundwise, include=FALSE}
+```{r choice-rates-roundwise, include=FALSE, cache=TRUE}
 #prepare data
@@
                                          a = as_labeller(label_theta, default = label_parsed))) +
-  labs(x = expression(psi),
+  labs(x = expression(paste("Switching Probability ", psi)),
        y = "False Response Rate",
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \caption{Rates of False Risky and False Safe Choices in the Round-Wise Integration Model}
 \includegraphics{manuscript_files/figure-latex/choice-rates-roundwise-1} \label{fig:choice-rates-roundwise}
-\raggedright \textit{Note.} Add note
+\raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), stars and points represent the rate of choices that did not maximize the latent EV (gray) or the mean across all outcomes sampled over the course of a sampling and accumulation process (green, false response rates).
+Stars: Rates of choice trials, where risky prospect was chosen, although safe prospect produced the greater mean (false risky response).
+Points: Rates of trials, where safe prospect was chosen, although risky prospect produced the greater mean (false safe response).
+\(p_{high} \in (.8, 1)\): Rates for all choice problems that include a small-probability outcome of low rank.
+\(p_{high} \in (0, 2)\): Rates for problems that include a small-probability outcome of high rank.
+\(p_{high} \in [.2, .8]\): Rates for problems that do not include an outcome with a probability < .2.
 \end{figure}
@@
 
-Figure\ \@ref(fig:weighting-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the curvature parameter $\gamma$ and the elevation parameter $\delta$, as well as the resulting graphical shape of the weighting function.
-Note that the estimates for the parameter combination $\theta = 1$ and $\psi = 1$ have large posterior intervals.
+Figure\ \@ref(fig:weighting-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the curvature parameter $\gamma$ and the elevation parameter $\delta$.
+First, note that the estimates for the parameter combination $\theta = 1$ and $\psi = 1$ have large posterior intervals.
 In these cases, no relative frequencies other than 0 and 1 are supplied to the weighting function, which may explain that the values in between cannot be reliably accounted for.
-However, for $\theta = 1$ and $\psi < 1$, the estimates imply a linear weighting pattern, in line with the explanation that if the mind were to infer the latent objective probabilities of outcomes from the sampled relative frequencies and to follow the principle of EV maximization, sampling error can account for any deviations from it.^[<!--Open footnote-->
-Note that the same line of reasoning holds, were the mind to approximate the solutions of EV maximization by choosing the prospect with higher sampled mean.
-<!--Close footnote-->]
-Note also Figure\ \@ref(fig:choice-rates-roundwise), where there are no choices for $\theta = 1$ that do not maximize the sampled mean.
-
-For $\theta > 1$, the estimates substantiate the prediction that $\gamma$ takes values $\geq 1$ which increase with $\psi$, resulting in a increasingly pronounced S-shaped weighting function.
-In other words, the higher the value of $\psi$, the more severe is the underweighting (overweighting) of the high-rank outcome of the risky prospect in CPT, if it is of small (large) probability.
-$\delta$ takes values $\geq 1$ and increases slightly with $\psi$, causing the overweighting of the high-rank outcome of the risky prospect to extend across the mid-point. 
-[...]
-
-```{r weighting-parameters, include=FALSE}
+For $\theta = 1$ and $\psi < 1$, the estimates imply a linear weighting pattern, since in this case only a single round of comparison is carried out and therefore the round-wise integration strategy always chooses the prospect that produces the larger mean across all outcomes sampled over the course of a sampling and accumulation process.
+This result is well in line with the explanation that if the mind were to infer the latent objective probabilities of outcomes from the sampled relative frequencies and to follow the principle of EV maximization, sampling error can account for any deviations from it.
+In this regard, note also Figure\ \@ref(fig:choice-rates-roundwise), where there are no choices for $\theta = 1$ that do not maximize the sampled mean.
+
+For $\theta > 1$, the curvature parameter $\gamma$ takes values $\geq 1$ which increase with the switching probability, resulting in a increasingly pronounced S-shaped weighting function.
+In other words, the higher the switching probability, the more severe is the underweighting (overweighting) of the high-rank outcome of the risky prospect in CPT, if it is of small (large) probability.
+That is, the as-if underweighting of rare outcomes pattern indicated by the final choices (i.e., the false response rates) translates rather directly to an underweighting of small-probability outcomes in CPT.
+As expected, the elevation parameter $\delta$ takes no values $< 1$, however, the estimates increase slightly with the switching probability, causing the overweighting of the high-rank outcome of the risky prospect to extend across the mid-point of the probability scale.
+It is open for discussion whether this extension of overweighting beyond the mid-point is theoretically implied by the mechanisms of the round-wise integration model:
+That is, for high switching probabilities the model is expected to choose the risky prospect, if the probability of its high-rank outcome is $> .5$.
+To account for the implied choice behavior, CPT might have to overweight high-rank outcomes with a probability far larger than .5 less severely than high-rank outcomes with a probability only little larger than .5.
+Such a pattern is implied for $\delta > 1$.
+Aside this open issue, the estimates for the $\gamma$ and $\delta$ parameter show that the choices implied by the potential interplay of different sampling strategies and the round-wise integration/decision strategy can lead to distinct signatures in CPT's weighting function (see Figure\ \@ref(fig:function-forms), for the resulting graphs of the weighting function).
+Once again, these signatures cannot be due to sampling error.
+
+```{r weighting-parameters, include=FALSE, cache=TRUE}
 
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \caption{Parameter Estimates of the Weighting Function}
 \includegraphics{manuscript_files/figure-latex/weighting-parameters-1} \label{fig:weighting-parameters}
-\raggedright \textit{Note.} Add note
+\raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), points represent the means of the posteriors distributions.
+Error bars represent the 95\%-intervals of the posterior distributions.
+Note that for better resolution the scales on the y-axis differ for different levels of \(\theta\).
 \end{figure}
@@
 Figure\ \@ref(fig:sensitivity-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$.
-An increase in $\psi$ leads to a decrease in $\alpha$, reflecting that outcome information are largely ignored if choices are based on ordinal comparisons of single outcomes rather than on means of large samples.
-The respective shape of the value function is more concave, the higher the values of $\psi$. 
-Finally, $\rho$ varied systematically such that the choices were more sensitive to the valuations of the core CPT model for low values of $\psi$.
-However, even for high values of $\psi$, the choices did not appear to be random. [...]
-
-```{r sensitivity-parameters, include=FALSE}
+As expected, an increase in the switching probability leads to a decrease in $\alpha$, showing that the round-wise integration model largely ignores outcome information, if choices are based on ordinal comparisons of single outcomes rather than of means across larger sets of sampled outcomes.
+In other words, for high switching probabilities, the round-wise integration model is expected to choose the prospect that produces the higher outcome most of the time.
+Once it is established which prospect does so, it is of no more utility to know the exact magnitude of the difference in the outcomes.
+The corresponding shape of the value function is shown in Figure\ \@ref(fig:function-forms) and is more concave for high switching probabilities. 
+Thus, the estimates for the outcome sensitivity parameter $\alpha$ show that the potential interplay between different sampling strategies and the round-wise integration/decision strategy may lead to choice patterns that also translate to distinct signatures in CPT's value function.
+Finally, $\rho$ varied systematically such that the choices were more sensitive to the valuations of the core CPT model for low switching probabilities.
+However, for high switching probabilities, the choices did not appear to be random whatsoever.
+
+```{r sensitivity-parameters, include=FALSE, cache=TRUE}
 
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \caption{Parameter Estimates of the Outcome and Choice Sensitivity Parameter}
 \includegraphics{manuscript_files/figure-latex/sensitivity-parameters-1} \label{fig:sensitivity-parameters}
-\raggedright \textit{Note.} Add note
+\raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), points represent the means of the posteriors distributions.
+Error bars represent the 95\%-intervals of the posterior distributions.
+Note that for better resolution the scales on the y-axis differ for different levels of \(\theta\).
 \end{figure}
 
-Figure\ \@ref(fig:function-forms) displays the resulting graphical shapes of the weighting and value function.
-
-```{r function-forms, include=FALSE}
+```{r function-forms, include=FALSE, cache=TRUE}
 
@@
   labs(x = "Experienced Probability",
-       y = expression(pi),
-       color = expression(psi)) +
+       y = expression(paste("Decision Weight ", pi)),
+       color = expression(paste("Switching\nProbability ", psi))) +
   scale_x_continuous(breaks = seq(0, 1, .5)) +
@@
        y = "Subjective Value",
-       color=expression(psi)) +
+       color= expression(paste("Switching\nProbability ", psi))) +
   scale_x_continuous(limits = c(0,20), breaks = seq(0, 20, 10)) +
@@
 
-\begin{figure}[t]
-\caption{Estimated Graphical Shape of the Weighting and Value Function}
+\begin{figure}[t!]
+\caption{Estimated Graphical Shape of CPT's Weighting and Value Function}
 \includegraphics{manuscript_files/figure-latex/function-forms-1} \label{fig:function-forms}
-\raggedright \textit{Note.} Add note
+\raggedright \textit{Note.} All displayed graphs are computed on the basis of the parameter values that were estimated for the respective model and combination of the switching probability \(\psi\) and the threshold \(\theta\).
 \end{figure}
@@
 
+The choice behavior exercised by the summary integration model is less systematic than that of the round-wise integration model, especially for low switching probabilities.
+The random choice behavior is indicated by false response rates around the value of .5 (see Fig.\ \@ref(fig:choice-rates-summary)) and low estimates for the choice sensitivity parameter $\rho$ (see Fig.\ \@ref(fig:sensitivity-parameters)).
+Because the choices become more systematic with increasing switching probabilities, randomness is likely to be caused by the temporal advantage that one of the prospect gains by chance.
+For high switching probabilities, choice rates and parameter estimates are roughly in line with the expectations formulated in Table\  \@ref(tab:expectations-summary).
+
 #### Number of Sampled Outcomes
 
+The model predicts the number of outcomes sampled over the course of a sampling and accumulation process to increase with thresholds (see Fig.\ \@ref(fig:sample-sizes)).
+As indicated by the gray smoothed functions, the number of sampled outcomes is generally small and reaches the meta-analytic median found by @wulffMetaanalyticReviewTwo2018 only for higher thresholds.
+The switching probability is predicted to exercise no or (at most) a negligible effect on the number of sampled outcomes.
+
 #### Final Choice
 
-```{r choice-rates-summary, include=FALSE}
+For each combination of switching probabilities and the thresholds, Figure\ \@ref(fig:choice-rates-summary) displays the rates of choices that did not maximize the sampled mean.
+As for the round-wise integration model, rates are separated for presence and rank of small-probability outcomes.
+Consider first the bottom panel which displays the choice rates for all choice problems that do not include an outcome with a probability $< .2$.
+Here, the false response rates decrease with increases in the switching probability, going from random choice behavior at rates around .5 for low switching probabilities to a systematic maximization of the sampled mean for high switching probabilities.
+Because sampling error and a systematic underrepresentation of small-probability outcomes is accounted for, a similar pattern would be expected for the choice problems that include outcomes with a probability $<.2$.
+In principle, this is the case, however, choice behavior appears to be more random over a wider range of switching probabilities.
+
+```{r choice-rates-summary, include=FALSE, cache=TRUE}
 #prepare data
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \caption{Rates of False Risky and False Safe Choices in the Summary Integration Model}
 \includegraphics{manuscript_files/figure-latex/choice-rates-summary-1} \label{fig:choice-rates-summary}
-\raggedright \textit{Note.} Add note
+\raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), stars and points represent the rate of choices that did not maximize the latent EV (gray) or the mean across all outcomes sampled over the course of a sampling and accumulation process (blue, false response rates).
+Stars: Rates of choice trials, where risky prospect was chosen, although safe prospect produced the greater mean (false risky response).
+Points: Rates of trials, where safe prospect was chosen, although risky prospect produced the greater mean (false safe response).
+\(p_{high} \in (.8, 1)\): Rates for all choice problems that include a small-probability outcome of low rank.
+\(p_{high} \in (0, 2)\): Rates for problems that include a small-probability outcome of high rank.
+\(p_{high} \in [.2, .8]\): Rates for problems that do not include an outcome with a probability < .2.
 \end{figure}
@@
 
-# Discussion
+First, note that the estimates for the choice sensitivity parameter $rho$ tend to be low for small switching probabilities (see Fig.\ \@ref(fig:sensitivity-parameters)), implying that for these cases the choices are random and thus, more or less insensitive to the evaluations of the core CPT model.
+Interpretation of CPT parameter estimates for small switching probabilities should therefore be made with great caution (if at all).
+For high switching probabilities, the estimates for the weighting function's $\gamma$ and $\delta$ parameter and the value function's $\alpha$ parameter indicate a linear weighting of sampled relative frequencies and outcomes, i.e., $\gamma \approx 1, \delta \approx 1, \alpha \approx 1$.
+
+# Discussion and Conclusion
 
@@
 
-# Conclusion
-
-[...]
-
 \newpage
@@
 # References
+
+<!-- # Appendix -->
+
+```{r subset-relative, include=FALSE}
+choices_relative <- choices %>% filter(boundary == "relative")
+cpt_relative <- cpt %>% filter(boundary == "relative")
+```
+
+<!-- ## False Response Rates -->
+
+```{r choice-rates-roundwise-relative, include=FALSE, cache=TRUE}
+#prepare data
+
+## determine normative choice according to latent EV and sampled mean
+
+### latent EV
+
+fr_rates_EV <- choices_relative %>%
+  filter(model == "roundwise") %>% 
+  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B")) %>% # determine normative choice
+  filter(!is.na(norm)) %>% #exclude trials with equal EV
+  group_by(s, boundary, a, rare, norm, choice) %>% #separate by model parameter and type of rare event
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), #compute response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", #determine false response type
+                          norm == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>% #remove correct responses
+  select(-c(norm, choice, n)) %>% 
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]", #change facet labels for rare events
+                          rare == "attractive" ~ "\\in (0,.2)",
+                          rare == "unattractive" ~ "\\in (.8,1)"),
+         Norm = "EV")
+
+### sampled mean
+
+fr_rates_mean <- choices_relative %>% 
+  filter(model == "roundwise") %>% 
+  mutate(norm = case_when(a_ev_exp/b_ev_exp > 1 ~ "A", a_ev_exp/b_ev_exp < 1 ~ "B")) %>% # determine normative choice
+  filter(!is.na(norm)) %>% #exclude trials with equal EV
+  group_by(s, boundary, a, rare, norm, choice) %>% #separate by model parameter and type of rare event
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), #compute response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", #determine false response type
+                          norm == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>% #remove correct responses
+  select(-c(norm, choice, n)) %>% 
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]", #change facet labels for rare events
+                          rare == "attractive" ~ "\\in (0,.2)",
+                          rare == "unattractive" ~ "\\in (.8,1)"),
+         Norm = "Mean")
+
+fr_rates <- bind_rows(fr_rates_EV, fr_rates_mean)
+
+# labeller functions
+label_theta <- function(string) {
+  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
+}
+
+label_rare <- function(string) {
+  TeX(paste("$\\p_{High}$", string, sep = "")) #type of rare event
+}
+
+#plot
+
+fr_rates_risky <- fr_rates %>% filter(type == "Risky")
+fr_rates_safe <- fr_rates %>% filter(type == "Safe")
+
+fr_rates_risky %>%
+  ggplot(aes(s, rate, color = Norm)) +
+  facet_grid(rare~a, labeller = labeller(rare = as_labeller(label_rare, default = label_parsed), 
+                                         a = as_labeller(label_theta, default = label_parsed))) +
+  labs(x = expression(paste("Switching Probability ", psi)),
+       y = "False Response Rate",
+       color = "Norm",
+       shape = "False\nResponse") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  geom_point(aes(shape = type), size = 2) +
+  geom_line() + 
+  geom_point(data = fr_rates_safe, aes(shape = type), size = 2) +
+  geom_line(data = fr_rates_safe) +
+  scale_shape_manual(values = c(8, 16)) +
+  scale_color_manual(values = c("#d3d3d3", "#35b779")) + 
+  theme_minimal()
+```
+
+```{r choice-rates-summary-relative, include=FALSE, cache=TRUE}
+#prepare data
+
+## determine normative choice according to latent EV and sampled mean
+
+### latent EV
+
+fr_rates_EV <- choices_relative %>%
+  filter(model == "summary") %>% 
+  mutate(norm = case_when(ev_ratio > 1 ~ "A", ev_ratio < 1 ~ "B")) %>% # determine normative choice
+  filter(!is.na(norm)) %>% #exclude trials with equal EV
+  group_by(s, boundary, a, rare, norm, choice) %>% #separate by model parameter and type of rare event
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), #compute response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", #determine false response type
+                          norm == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>% #remove correct responses
+  select(-c(norm, choice, n)) %>% 
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]", #change facet labels for rare events
+                          rare == "attractive" ~ "\\in (0,.2)",
+                          rare == "unattractive" ~ "\\in (.8,1)"),
+         Norm = "EV")
+
+### sampled mean
+
+fr_rates_mean <- choices_relative %>% 
+  filter(model == "summary") %>% 
+  mutate(norm = case_when(a_ev_exp/b_ev_exp > 1 ~ "A", a_ev_exp/b_ev_exp < 1 ~ "B")) %>% # determine normative choice
+  filter(!is.na(norm)) %>% #exclude trials with equal EV
+  group_by(s, boundary, a, rare, norm, choice) %>% #separate by model parameter and type of rare event
+  summarise(n = n()) %>%
+  mutate(rate = round(n/sum(n), 2), #compute response rates
+         type = case_when(norm == "A" & choice == "B" ~ "Safe", #determine false response type
+                          norm == "B" & choice == "A" ~ "Risky")) %>%
+  ungroup() %>%
+  filter(!is.na(type)) %>% #remove correct responses
+  select(-c(norm, choice, n)) %>% 
+  mutate(rare = case_when(rare == "none" ~ "\\in \\[.2,.8\\]", #change facet labels for rare events
+                          rare == "attractive" ~ "\\in (0,.2)",
+                          rare == "unattractive" ~ "\\in (.8,1)"),
+         Norm = "Mean")
+
+fr_rates <- bind_rows(fr_rates_EV, fr_rates_mean)
+
+# labeller functions
+label_theta <- function(string) {
+  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
+}
+
+label_rare <- function(string) {
+  TeX(paste("$\\p_{High}$", string, sep = "")) #type of rare event
+}
+
+#plot
+
+fr_rates_risky <- fr_rates %>% filter(type == "Risky")
+fr_rates_safe <- fr_rates %>% filter(type == "Safe")
+
+fr_rates_risky %>%
+  ggplot(aes(s, rate, color = Norm)) +
+  facet_grid(rare~a, labeller = labeller(rare = as_labeller(label_rare, default = label_parsed), 
+                                         a = as_labeller(label_theta, default = label_parsed))) +
+  labs(x = expression(paste("Switching Probability ", psi)),
+       y = "False Response Rate",
+       color = "Norm",
+       shape = "False\nResponse") +
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .5)) +
+  geom_point(aes(shape = type), size = 2) +
+  geom_line() + 
+  geom_point(data = fr_rates_safe, aes(shape = type), size = 2) +
+  geom_line(data = fr_rates_safe) +
+  scale_shape_manual(values = c(8, 16)) +
+  scale_color_manual(values = c("#d3d3d3", "#3e4989")) + 
+  theme_minimal()
+```
+
+<!-- ## Parameter Estimates and CPT Graphs -->
+
+```{r weighting-parameters-relative, include=FALSE, cache=TRUE}
+
+label_theta <- function(string) {
+  TeX(paste("$\\theta=$", string, sep = "")) #threshold parameter theta
+}
+
+# plot gamma estimates
+gamma <- cpt_relative %>%
+  filter(parameter == "gamma") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(gamma),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
+  theme_minimal()
+
+# plot delta estimates
+delta <- cpt_relative %>%
+  filter(parameter == "delta") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(delta),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
+  theme_minimal()
+
+# merge plots
+ggarrange(gamma, delta, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
+```
+
+```{r sensitivity-parameters-relative, include=FALSE, cache=TRUE}
+
+# plot alpha estimates
+alpha <- cpt_relative %>%
+  filter(parameter == "alpha") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(alpha),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
+  theme_minimal()
+
+# plot rho estimates
+rho <- cpt_relative %>%
+  filter(parameter == "rho") %>%
+  ggplot(aes(s, mean, color = model)) +
+  facet_wrap(~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed)), scales = "free") +
+  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5)) + 
+  labs(x = expression(paste("Switching Probability ", psi)), 
+       y = expression(rho),
+       color = "Model") +
+  geom_errorbar(aes(ymin=`2.5%`, ymax=`97.5%`)) + 
+  geom_point() +
+  geom_line() +
+  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
+  theme_minimal()
+
+# merge plots
+ggarrange(alpha, rho, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right") 
+```
+
+```{r function-forms-relative, include=FALSE, cache=TRUE}
+
+# plot weighting function
+
+## compute decision weights
+
+weights <- cpt_relative %>%
+  select(model, s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
+  select(-c(alpha, rho)) %>%
+  expand_grid(p = seq(0, 1, .05)) %>%
+  mutate(w = round(  (delta * p^gamma)/ ((delta * p^gamma)+(1-p)^gamma), 2))
+
+## plot graphs
+
+wf <- weights %>% 
+  ggplot(aes(p, w, group = s, color = s)) +
+  facet_wrap(~model~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  labs(x = "Experienced Probability",
+       y = expression(paste("Decision Weight ", pi)),
+       color = expression(paste("Switching\nProbability ", psi))) +
+  scale_x_continuous(breaks = seq(0, 1, .5)) +
+  scale_y_continuous(breaks = seq(0, 1, .5)) +
+  geom_line(size = .5) +
+  scale_color_viridis(option = "mako") +
+  theme_minimal()
+
+# value functions
+
+values <- cpt_relative %>%
+  select(model, s, boundary, a, parameter, mean) %>%
+  pivot_wider(names_from = parameter, values_from = mean) %>%
+  select(-c(gamma, delta, rho)) %>%
+  expand_grid(x = seq(0, 20, .5)) %>%  
+  mutate(v = round(x^alpha, 2))
+
+vf <- values %>% 
+  ggplot(aes(x, v, group = s, color = s)) +
+  facet_wrap(model~a, nrow = 2, labeller = labeller(a = as_labeller(label_theta, default = label_parsed))) + 
+  labs(x = "Objective Outcome",
+       y = "Subjective Value",
+       color= expression(paste("Switching\nProbability ", psi))) +
+  scale_x_continuous(limits = c(0,20), breaks = seq(0, 20, 10)) +
+  geom_line(size = .5) +
+  scale_color_viridis(option = "mako") +
+  theme_minimal()
+
+# merge plots
+ggarrange(wf, vf, ncol = 1, nrow = 2, common.legend = TRUE, legend = "right")
+```

### 2022-05-24 manuscript.Rmd
Final version Section 4 (Simulation study), including appendix

@@
 Below, it is discussed which effects the key model parameters, i.e., the switching probability $\psi$ and the threshold $\theta$, could have on the choices and the corresponding as-if weighting patterns that are implied by the round-wise and the summary integration model.
-The effects of the switching probability $\psi$ should be informative about the interplay between different sampling strategies and the integration/decision strategy each model resembles.
-Assuming that both models aim to assess true differences in the latent properties of prospects, the effects of the threshold $\theta$ should indicate whether these differences are indeed more accurately assessed---thus, leading to more systematic choices and as-if weighting patterns---the more evidence is accumulated.
+The effects of the switching probability should be informative about the interplay between different sampling strategies and the integration/decision strategy each model resembles.
+Assuming that both models aim to assess true differences in the latent properties of prospects, the effects of the threshold should indicate whether these differences are indeed more accurately assessed---thus, leading to more systematic choices and as-if weighting patterns---the more evidence is accumulated.
 In addition, previous research has shown that differences as to how information about the properties of prospects is processed can translate to distinct signatures in CPT's psychoeconomic value and weighting function, without actually assuming that these functions are computed whatsoever [see @pachurHowTwainCan2017; @stewartDecisionSampling2006; @zilkerNonlinearProbabilityWeighting2021].^[<!--Open footnote-->
@@
 <!--Close footnote-->]
-Accordingly, this section also formulates expectations regarding the potential relations between the switching probability $\psi$ and threshold $\theta$ (data-generating parameters) and the CPT parameters (data-modeling parameters).
+Accordingly, this section also formulates expectations regarding the potential relations between switching probabilities and thresholds (data-generating parameters) and the CPT parameters (data-modeling parameters).
 
@@
 That is, for high switching probabilities and thus, short stochastic processes, the binomial distribution associated with small-probability outcomes is positive skewed, causing the relative frequencies with which these outcomes occur within each comparison round to be smaller rather than larger than their latent objective probabilities.
-Because such a distortion of the relative sampled frequencies from the objective probabilities is expected for each comparison round, increases in the thresholds $\theta$ should not affect the following expectations concerning the model behavior; rather because each comparison is independent and increases in sample size (here: number of comparisons) reduce random error, the expectations should be more accurately met for higher thresholds:
+Because such a distortion of the relative sampled frequencies from the objective probabilities is expected for each comparison round, increases in the threshold $\theta$ should not affect the following expectations concerning the model behavior; rather because each comparison is independent and increases in sample size (here: number of comparisons) reduce random error, the expectations should be more accurately met for higher thresholds:
 If the small-probability outcome is smaller (larger) than the EV, high switching probabilities cause the mean within each comparison round to be an inflated (deflated) estimate of the EV.
@@
 That is, if the EVs are substituted by the means across all outcomes sampled from a prospect over the course of the entire sampling and accumulation process, the means within each comparison round are still expected to deviate from this sampling error-encompassing substitute in the manner outlined above.
-Moreover, because the mean across the entire sampling and accumulation process is expected to converge to the EV the more outcomes are sampled overall, the choice patterns with and without sampling error accounted for should resemble each other more closely, the higher the thresholds get.
+Moreover, because the mean across the entire sampling and accumulation process is expected to converge to the EV the more outcomes are sampled overall, the choice patterns with and without sampling error should resemble each other more closely, the higher the thresholds get.
 
 To summarize the choice predictions and simplify: 
-If the prospect that is more likely to return a higher outcome most of the time does not also possess the higher EV or mean across all outcomes sampled over the course of a sampling and accumulation process, high values of the switching probability $\psi$ are predicted to cause an as-if underweighting of rare outcomes pattern.
+If the prospect that is more likely to return a higher outcome most of the time does not also possess the higher EV or mean across all outcomes sampled over the course of a sampling and accumulation process, high switching probabilities are predicted to cause an as-if underweighting of rare outcomes pattern.
 For low switching probabilities, choices are expected to maximize the EV or mean across all sampled outcomes.
@@
 <!--Close footnote-->] 
-This could introduce interactions between the switching probability $\psi$ and the threshold $\theta$ that are not implied by a model that assumes comparisons between means.
+This could introduce interactions between switching probabilities and thresholds that are not implied by a model that assumes comparisons between means.
 
@@
 Hence, in principle, the larger the thresholds, the more should small-probability outcomes contribute to the cumulative sum as much as would be warranted by their objective probabilities.
-Accordingly, one might expect that the implied choices converge to the solutions of EV maximization, the larger the thresholds get.
-However, the switching probabilities $\psi$ should introduce temporal imbalances between prospects regarding the number of sampled outcomes over which the sums are computed (and compared, assuming relative thresholds, respectively).
+Accordingly, one might expect that the implied choices generally maximize the overall sampled mean and converge to the solutions of EV maximization, the larger the thresholds get.
+However, the switching probabilities should introduce temporal imbalances between prospects regarding the number of sampled outcomes over which the sums are computed (and compared, assuming relative thresholds, respectively).
 That is, whatever prospect is first sampled from is allowed to start accumulating evidence sooner than the respective other prospect.
@@
 Accordingly, for small switching probabilities, choices might be largely driven by the truly random event which prospect is first sampled from.
-This random choice behavior should diminish with increases in the switching probability and choices should converge to the solutions of EV maximization the higher the thresholds get.
+This random choice behavior should diminish with increases in the switching probability and choices should converge to the solutions of sampled mean and EV maximization the higher the thresholds get.
 
@@
 For small thresholds, an as-if underweighting of rare outcomes pattern is expected to occur because small-probability outcomes should be systematically underrepresented due to their skewed binomial distribution.
-This pattern should be alleviated, if sampling error is taken into account.
+This pattern should be (fully) alleviated, if sampling error is taken into account.
 For large thresholds, choices should converge more to the solutions of EV maximization, even more so to the solutions of sampled mean maximization (i.e., when sampling error is accounted for).
@@
 
-## Results
+## Model Predictions
 
@@
 
-Figure\ \@ref(fig:sample-sizes) displays the number of outcomes sampled over the course of a sampling and accumulation process for each combination of the switching probability $\psi$ and the threshold $\theta$.
-The model predicts a decrease in the overall number of sampled outcomes with increases in the switching probability.
-As can be seen from the changes in the slopes of the gray lines of the smoothed functions, the magnitude of this decrease diminishes as the relative increase in the switching probability diminishes.
-The overall number of sampled outcomes increases with thresholds at a relatively constant rate.
+Figure\ \@ref(fig:sample-sizes) displays the number of outcomes sampled over the course of a sampling and accumulation process for each combination of switching probabilities and thresholds.
+The model predicts a decrease in the overall number of sampled outcomes with increases in the switching probability, whereas the overall number of sampled outcomes is predicted to increase with thresholds at relatively constant rate.
+These differences in the number of sampled outcomes are subtle indicators for how sampling strategies and the mechanisms of the round-wise integration model act together to imply different final choices.
+Essentially, they foreshadow how the round-wise integration model accumulates evidence for differences in the latent EV for low switching probabilities, and for differences in the latent probability to produce a higher outcome most of the time for high switching probabilities.
+
 Consider also the dashed horizontal lines, which display the median number of 14 outcomes that @wulffMetaanalyticReviewTwo2018 found to be sampled in 10,712 trials involving a choice between a safe and a two-outcome prospect in the sampling paradigm:
-The parameter combinations that closely resemble the links between sampling and decision strategies originally proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010]---i.e, high switching probabilities and thresholds for piecewise sampling and round-wise decisions vs.
+The parameter combinations that closely resemble the links between the sampling and decision strategies originally proposed by Hills and Hertwig [-@hillsInformationSearchDecisions2010]---i.e, high switching probabilities and thresholds for piecewise sampling and round-wise decisions vs.
 low switching probabilities and a single mean comparison ($\theta = 1$) for comprehensive sampling and summary decisions---lead to overall numbers of sampled outcomes that come close to the meta-analytic median.
-Moreover, while parameter combinations that can be understood as falling in between the originally proposed links---i.e., mid-range values for both switching probability and threshold---also lead to overall numbers of sampled outcomes that approximate the meta-analytic median, extreme combinations (e.g., low switching probability and high threshold) produce numbers that are considerably lower or higher, and thus less plausible from an empirical stance.
-
-```{r chain-length, eval = FALSE}
+
+```{r chain-length, include=FALSE, cache=TRUE}
 
@@
   geom_jitter(alpha = .05) + 
-  geom_smooth(color = "gray") + 
-  geom_hline(yintercept = 14, linetype = "dashed", color = "gray") +
+  geom_smooth(color = "gray", size = 1) + 
+  geom_hline(yintercept = 14, linetype = "dashed", color = "gray", size = 1) +
   scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
@@
   theme_minimal()
+
 chain_lengths
@@
 \includegraphics[width=1\linewidth]{manuscript_files/sample-sizes} \label{fig:sample-sizes}
-\raggedright \textit{Note.} Columns represent different thresholds.
-x-axes display the switching probability.
-Each point represents a single sampling and accumulation process (choice trial) for the respective combination of the threshold and switching probability, and is the overall number of outcomes sampled over the course of this process.
+\raggedright \textit{Note.} Each point represents a single sampling and accumulation process (choice trial) for the respective combination of thresholds and switching probabilities, and is the overall number of outcomes sampled over the course of this process.
 The gray lines are estimates of \textit{ggplot2}'s \texttt{stat\_smooth()} function.
-All gray-dashed horizontal lines represent the meta-analytic median, med = 14, for choices between a safe and a risky prospect, found by \protect\hyperlink{ref-wulffMetaanalyticReviewTwo2018}{Wulff et al., 2018}.
-Note that for better resolution the scales on the y-axis differ for different levels of \(\theta\).
+All gray-dashed horizontal lines represent the meta-analytic median for choices between a safe and a risky prospect, found by \protect\hyperlink{ref-wulffMetaanalyticReviewTwo2018}{Wulff et al., 2018}.
+Note that for better resolution the scales on the y-axis differ for the levels of \(\theta\).
 \end{figure}
@@
 
-For each combination of the switching probability and the threshold, Figure\ \@ref(fig:choice-rates-roundwise) displays the rates of choices that did not maximize the sampled mean (i.e., the mean across all outcomes sampled over the course of a sampling and accumulation process, hereafter: false response rates).
+For each combination of switching probabilities and thresholds, Figure\ \@ref(fig:choice-rates-roundwise) displays the rates of choices that did not maximize the sampled mean (i.e., the mean across all outcomes sampled over the course of a sampling and accumulation process, hereafter: false response rates).
 Rates are separated for presence and rank of small-probability outcomes.
@@
 Accordingly, the top panels show that for each threshold the rates of false choices of the risky prospect increase with the switching probability, causing deviations from sampled mean maximization that take the form of an as-if underweighting of rare outcomes.
-In turn, rates of false safe choices remain generally low.
+In turn, rates of false safe choices remain low.
 To demonstrate how the false response rates would have turned out given the normative solutions of EV maximization (i.e., when sampling error is not controlled for), the rates of choices that did not maximize the latent EV are displayed in gray.
@@
 Again, the resulting choice patterns resemble an as-if underweighting of rare outcomes pattern.
-Importantly, note from the reduced false response rates in the bottom panel that the inflation and deflation of the means for high switching probabilities must be significantly attenuated when a prospect possesses no small-probability outcome.
+Importantly, note from the reduced false response rates in the bottom panel, that the inflation and deflation of the means for high switching probabilities must be significantly attenuated when the prospects possess no small-probability outcome.
+
 In sum, then, the simulated choices show that the potential interplay between sampling strategies and a round-wise integration/decision strategy can lead to distinct choice patterns and as-if weighting patterns in DFE, which, however, strongly depend on the structure of the choice problems.
+For small switching probabilities, the round-wise integration model accumulates evidence for differences in the latent EVs, which is reflected in low false response rates.
+For high switching probabilities, the round-wise integration model accumulates evidence for differences in the latent probability to produce a higher outcome most of the time.
+This is reflected in low false response rates, if the respective prospect also possesses the higher latent EV, otherwise in high false response rates.
 
@@
 
-For $\theta > 1$, the curvature parameter $\gamma$ takes values $\geq 1$ which increase with the switching probability, resulting in a increasingly pronounced S-shaped weighting function.
+For $\theta > 1$, the curvature parameter $\gamma$ takes values $\geq 1$ which increase with switching probabilities, resulting in a increasingly pronounced S-shaped weighting function.
 In other words, the higher the switching probability, the more severe is the underweighting (overweighting) of the high-rank outcome of the risky prospect in CPT, if it is of small (large) probability.
 That is, the as-if underweighting of rare outcomes pattern indicated by the final choices (i.e., the false response rates) translates rather directly to an underweighting of small-probability outcomes in CPT.
-As expected, the elevation parameter $\delta$ takes no values $< 1$, however, the estimates increase slightly with the switching probability, causing the overweighting of the high-rank outcome of the risky prospect to extend across the mid-point of the probability scale.
+As expected, the elevation parameter $\delta$ takes no values $< 1$, however, the estimates increase slightly with switching probabilities, causing the overweighting of the high-rank outcome of the risky prospect to extend across the mid-point of the probability scale.
 It is open for discussion whether this extension of overweighting beyond the mid-point is theoretically implied by the mechanisms of the round-wise integration model:
-That is, for high switching probabilities the model is expected to choose the risky prospect, if the probability of its high-rank outcome is $> .5$.
+That is, for high switching probabilities, the model is expected to choose the risky prospect, if the probability of its high-rank outcome is $> .5$.
 To account for the implied choice behavior, CPT might have to overweight high-rank outcomes with a probability far larger than .5 less severely than high-rank outcomes with a probability only little larger than .5.
@@
 Once it is established which prospect does so, it is of no more utility to know the exact magnitude of the difference in the outcomes.
+This resonates well with the proposition that round-wise and summary decision strategies are differently equipped to meet short-term and long-term aspirations [cf.
+@hillsInformationSearchDecisions2010; @wulffHowShortLongrun2015].
 The corresponding shape of the value function is shown in Figure\ \@ref(fig:function-forms) and is more concave for high switching probabilities. 
 Thus, the estimates for the outcome sensitivity parameter $\alpha$ show that the potential interplay between different sampling strategies and the round-wise integration/decision strategy may lead to choice patterns that also translate to distinct signatures in CPT's value function.
+
 Finally, $\rho$ varied systematically such that the choices were more sensitive to the valuations of the core CPT model for low switching probabilities.
@@
 
-The choice behavior exercised by the summary integration model is less systematic than that of the round-wise integration model, especially for low switching probabilities.
+As expected, the choice behavior exercised by the summary integration model is less systematic than that of the round-wise integration model, especially for low switching probabilities.
 The random choice behavior is indicated by false response rates around the value of .5 (see Fig.\ \@ref(fig:choice-rates-summary)) and low estimates for the choice sensitivity parameter $\rho$ (see Fig.\ \@ref(fig:sensitivity-parameters)).
-Because the choices become more systematic with increasing switching probabilities, randomness is likely to be caused by the temporal advantage that one of the prospect gains by chance.
+Because choices become more systematic with increasing switching probabilities, randomness is likely to be caused by the temporal advantage that one of the prospect gains by chance.
 For high switching probabilities, choice rates and parameter estimates are roughly in line with the expectations formulated in Table\  \@ref(tab:expectations-summary).
@@
 The model predicts the number of outcomes sampled over the course of a sampling and accumulation process to increase with thresholds (see Fig.\ \@ref(fig:sample-sizes)).
-As indicated by the gray smoothed functions, the number of sampled outcomes is generally small and reaches the meta-analytic median found by @wulffMetaanalyticReviewTwo2018 only for higher thresholds.
-The switching probability is predicted to exercise no or (at most) a negligible effect on the number of sampled outcomes.
+As indicated by the gray smoothed functions and the dashed horizontal line, the number of sampled outcomes tends to be generally small and reaches the meta-analytic median found by @wulffMetaanalyticReviewTwo2018 only for higher thresholds.^[<!--Open footnote-->
+This may indicate that the thresholds used to generate the choice data were set too low.
+However, note that, in contrast to the round-wise integration model, thresholds in the summary integration model are in the same unit as the outcomes.
+Given a particular threshold, the number of sampled outcomes required to reach the threshold can vary substantially between choice problems.
+<!--Close footnote-->]
+Switching probabilities are not predicted to have a meaningful impact on the number of sampled outcomes.
+Since the summary integration model assumes that all outcomes sampled from a prospects are integrated into the same cumulative sum, this is already a strong indicator that changes in the sampling strategy should not cause the model to make systematically different choices.
 
@@
 
-For each combination of switching probabilities and the thresholds, Figure\ \@ref(fig:choice-rates-summary) displays the rates of choices that did not maximize the sampled mean.
+For each combination of switching probabilities and thresholds, Figure\ \@ref(fig:choice-rates-summary) displays the rates of choices that did not maximize the sampled mean.
 As for the round-wise integration model, rates are separated for presence and rank of small-probability outcomes.
-Consider first the bottom panel which displays the choice rates for all choice problems that do not include an outcome with a probability $< .2$.
-Here, the false response rates decrease with increases in the switching probability, going from random choice behavior at rates around .5 for low switching probabilities to a systematic maximization of the sampled mean for high switching probabilities.
-Because sampling error and a systematic underrepresentation of small-probability outcomes is accounted for, a similar pattern would be expected for the choice problems that include outcomes with a probability $<.2$.
-In principle, this is the case, however, choice behavior appears to be more random over a wider range of switching probabilities.
+Consider first the bottom panel, which displays the false response rates for all choice problems in which the risky prospect does not possess an outcome with a probability $< .2$:
+False response rates decrease with increasing switching probabilities, transitioning from random choice behavior at rates around .5 for low switching probabilities to a systematic maximization of the sampled mean for high switching probabilities.
+This actually demonstrates that changes in the sampling strategies do not cause the summary integration model to make systematically different choices.
+Specifically: The mechanisms of the summary integration model are such that evidence is accumulated for difference in the latent EVs, given that approximately the same number of outcomes is sampled from *both* prospects.
+The more outcomes are sampled from both prospects, i.e., the higher the thresholds, the more accurately these differences should be assessed.
+Changes in the sampling strategy do not change the latent property for which evidence is accumulated in the summary integration model.
+Rather they affect whether approximately the same number of outcomes is sampled from both prospects or whether one of the prospects obtains, by chance, a temporal advantage, rendering decision either systematic or unsystematic, respectively.
+
+In sum, then, the differences compared to the round-wise integration model are striking: 
+For the round-wise integration model, changes in the sampling strategy alter the degree to which evidence is sampled for one or the other latent property, which can translate to systematically different choices.
+That is, for low switching probabilities, the round-wise integration model accumulates evidence for differences in the latent EV's, resulting in similar choice patterns (false response rates) as produced by the summary integration model.
+For high switching probabilities, however, the round-wise integration model accumulates evidence for differences in the latent property to produce a higher outcome most of the time. 
+Depending on the structure of the choice problem, this implies an as-if underweighting of rare outcomes pattern, even if sampling error is controlled for.
+In contrast, neither do the mechanisms of the summary integration model imply that evidence is systematically sampled for differences in the latent probability to produce a higher outcome most of a time, nor does it predict an as-if underweighting of rare outcomes pattern ones sampling error is controlled for.
+The false response rates displayed in the top and middle panel of Figure\ \@ref(fig:choice-rates-summary), where choice problems include prospects possessing a small-probability outcome, provide support for this notion.
 
@@
 
-First, note that the estimates for the choice sensitivity parameter $rho$ tend to be low for small switching probabilities (see Fig.\ \@ref(fig:sensitivity-parameters)), implying that for these cases the choices are random and thus, more or less insensitive to the evaluations of the core CPT model.
-Interpretation of CPT parameter estimates for small switching probabilities should therefore be made with great caution (if at all).
+Note that the estimates for the choice sensitivity parameter $rho$ tend to be low for small switching probabilities (see Fig.\ \@ref(fig:sensitivity-parameters)), implying that in these cases the highest model fit is achieved, if a random choice is assumed.
+Thus, for small switching probabilities, interpretations of the parameter estimates for the core CPT model should be made with great caution (if at all).
 For high switching probabilities, the estimates for the weighting function's $\gamma$ and $\delta$ parameter and the value function's $\alpha$ parameter indicate a linear weighting of sampled relative frequencies and outcomes, i.e., $\gamma \approx 1, \delta \approx 1, \alpha \approx 1$.
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('manuscript_appendix.Rmd')
+```

### 2022-05-24 manuscript.Rmd
Use official (declared) title
Update Discussion

@@
 
-# Discussion and Conclusion
-
-The presented sampling and accumulation model ought to sketch how the mind might exercise the capacity of making decisions from experience.
-In DFE, one cannot rely on symbolic descriptions of all relevant properties of the choice alternatives, but only on samples of past experiences, e.g., when the alternatives were chosen in similar decisions in the past.
-To study DFE experimentally, one may use the sampling paradigm where people can sequentially sample the outcomes of prospects according to their probability of occurrence before making a final choice.
-To model the process by which people arrive at the final choice in this paradigm, one must explicate a number of assumptions, e.g.: How do people decide when to switch between prospects; how do they integrate the information obtained from the sampled outcomes; and, because they can sample as much as they want, how do they decide to stop sampling.
-To approach these questions, this paper presented a model that integrated a proposed link between sampling and decision strategies into the computational framework of sequential sampling models.
-
-## Modeling Sampling Strategies and the Decision-Making Process
-
-@hillsInformationSearchDecisions2010 proposed---and provided tentative empirical support for---a systematic relation between what they considered two paradigmatic sampling and decision strategies. 
-That is, the authors assumed that people either switch prospects after each sampled outcome (piecewise sampling) to compare single outcomes over repeated rounds (round-wise decision strategy), or they switch only once between prospects (comprehensive sampling) and make only one comparison between the means across all sampled outcomes (summary decision strategy).
-In sequential sampling models [see, e.g., @ratcliffComparisonSequentialSampling2004], the decision-making process is modeled as accumulation of evidence for or against a prospect over time, with the prospect being chosen for which the accumulated evidence first reaches a threshold.
-The sampling and accumulation model that was presented in this paper integrates both propositions by assuming that people accumulate the wins and losses resulting from a sequence of mean comparisons, with switching probabilities determining the size of the samples underlying each comparison and thresholds determining how much (more) comparisons a prospect must win in order to be chosen.
-Hence, the model treats the two paradigmatic sampling and decision strategies as the extreme ends of possible continua, allowing the switching probability not only to take values close to 0 and 1 but also values in between, and allowing single and multiple mean comparisons between prospects to be based on samples of varying size.
-Moreover, the model explicates the suggested link between sampling and decision strategies by assuming that the accumulation process more closely resembles the round-wise strategy for high switching probabilities, and, vice versa, the summary strategy for low switching probabilities.
-This is because high (low) switching probabilities cause the accumulation process to unfold over mean comparisons based on samples of small (large) size.
-
-## Sampling Strategies Might Shape Final Choice
+# Discussion
+
+The aim of this paper was to sketch how the mind might exercise the capacity of making decisions from experience (DFE).
+In DFE, people cannot rely on symbolic descriptions of the choice alternatives, but only on samples of past experiences.
+One paradigm used to study DFE experimentally is the sampling paradigm, where people can---as much as they want, in the way they want, and without costs---sample the possible outcomes of prospects before making a final choice between them.
+To approach an explanation for how people proceed in such a paradigm, this paper presented two models that integrate the idea of a potential interplay between sampling and decision strategies into the computational framework of sequential sampling models.
+
+## Summary
+
+Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that the way people sample the outcomes of prospects (sampling strategies) may be linked to the way they process the outcomes to evaluate the prospects and make a corresponding choice (decision strategies).
+Specifically, the authors assumed two potential links between what they considered paradigmatic instances of sampling and decision strategies:
+People either switch prospects after each sampled outcome (piecewise sampling) to compare single outcomes over repeated rounds (round-wise decisions), or they switch only once between prospects (comprehensive sampling) and make only one comparison between the means across all sampled outcomes (summary decisions).
+The authors provided tentative empirical support for their claim by showing that a larger proportion of the choices of people who, on average, switched infrequently between prospects were better predicted by a summary strategy (rather than a round-wise strategy), and vice versa.
+Moreover, the authors discussed and demonstrated in a simulation based on empirical sampling data that round-wise decisions may cause an as-if underweighting of rare outcomes pattern in DFE and thus, contribute to the decision-experience gap.
+
+The current paper extended the original discussion and analyses of Hills and Hertwig [-@hillsInformationSearchDecisions2010] in several ways, notably:
+
+1. No fixed links between particular sampling and decision strategies were assumed, but all possible combinations were considered.
+
+2.
+The sequential sampling framework was used as a modeling outlet to incorporate the idea of a potential interplay between sampling and decision strategies into formal models that offer a complete account of the decision-making process in the sampling paradigm and make theoretical commitments explicit.
+
+3.
+Cumulative prospect theory was used to model simulated choice data, allowing to inquire whether the choices implied by the potential interplay between sampling and decision strategies may translate to characteristic signatures in CPT’s psychoeconomic value and weighting function.
+
+4. The structure of choice problems---i.e., the presence and desirability of rare outcomes---was systematically varied.
+
+Relying on the sequential sampling framework, the decision-making processes were modeled as evidence accumulation over time. 
+Two different models were presented ...
 
@@
 
-## CPT Can Reflect the Adoption of Sampling Strategies
-
 The current paper further extended the analysis of @hillsInformationSearchDecisions2010 by showing that the effects of sampling and decision strategies on the final choice can translate to characteristic signatures in cumulative prospect theory's value and weighting function.
@@
 
-## Why Sampling and Decision Strategies?
-
-[...]
+## Limitations and Outlook
+
+### Why Sampling and Decision Strategies?
+
+# Conclusion
 

### 2022-05-26 manuscript.Rmd
Add abstract

@@
 abstract: |
-  Add abstract
-
-keywords          : "risky choice, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
+  In the sampling paradigm, people can---as much as they want, in the way they want, and without costs---sample the possible outcomes of prospects before making a final choice.
+Do the sequential pattern in which the outcomes are sampled (sampling strategy) and the way the sampled outcomes are integrated and processed to evaluate the prospects (integration/decision strategy) act together to shape choices in the sampling paradigm?
+This paper presents two models that incorporate the potential interplay between both types of strategies into the sequential sampling framework.
+Each model assumes an evidence accumulation process representing a distinct integration/decision strategy, and allows for variations in the sampling strategy.
+In a computational analysis, both models are used to simulate choices between a safe and a risky prospect, while systematically varying sampling strategies and evidence thresholds.
+The simulations show that the potential interplay between sampling and integration/decision strategies can lead to systematically different choices patterns and can contribute to the as-if underweighting of rare outcomes pattern in decisions from experience, irrespective of the existence or absence of sampling error.
+The model-implied differences in the choice patterns translate to distinct signatures in cumulative prospect theory’s psychoeconomic value and weighting function.
+
+keywords          : "decisions from experience, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
 wordcount         : ""
@@
 Relying on the sequential sampling framework, the decision-making processes were modeled as evidence accumulation over time. 
-Two different models were presented ...
+Two different models were presented
 

### 2022-05-26 manuscript.Rmd
Update abstract

@@
 The simulations show that the potential interplay between sampling and integration/decision strategies can lead to systematically different choices patterns and can contribute to the as-if underweighting of rare outcomes pattern in decisions from experience, irrespective of the existence or absence of sampling error.
-The model-implied differences in the choice patterns translate to distinct signatures in cumulative prospect theory’s psychoeconomic value and weighting function.
+The model-implied differences in the choice patterns translate to distinct signatures in the psychoeconomic functions of cumulative prospect theory.
 

### 2022-05-26 manuscript.Rmd
Update abstract

--- 2022-05-24 manuscript.Rmd
@@
 abstract: |
-  Add abstract
-
-keywords          : "risky choice, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
+  In the sampling paradigm, people can---as much as they want, in the way they want, and without costs---sample the possible outcomes of prospects before making a final choice.
+Do the sequential pattern in which the outcomes are sampled (sampling strategy) and the way the sampled outcomes are integrated and processed to evaluate the prospects (integration/decision strategy) act together to shape the choice?
+This paper presents two models that incorporate the potential interplay between both types of strategies into the sequential sampling framework.
+Each model assumes an evidence accumulation process representing a distinct integration/decision strategy and is used to simulate choices between a safe and a risky prospect, while systematically varying sampling strategies.
+The simulations show that the potential interplay between both types of strategies can lead to systematically different choice patterns and can contribute to the as-if underweighting of rare outcomes pattern in decisions from experience, irrespective of the existence or absence of sampling error.
+The model-implied differences in the choice patterns translate to distinct signatures in the psychoeconomic functions of cumulative prospect theory.
+
+keywords          : "decisions from experience, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
 wordcount         : ""
@@
 In DFE, people cannot rely on symbolic descriptions of the choice alternatives, but only on samples of past experiences.
-One paradigm used to study DFE experimentally is the sampling paradigm, where people can---as much as they want, in the way they want, and without costs---sample the possible outcomes of prospects before making a final choice between them.
-To approach an explanation for how people proceed in such a paradigm, this paper presented two models that integrate the idea of a potential interplay between sampling and decision strategies into the computational framework of sequential sampling models.
+One paradigm used to study DFE experimentally is the sampling paradigm, where people can---as much as they want, in the way they want, and without costs---sample the possible outcomes of prospects before making a final choice.
+To approach an explanation for how people proceed and choose in such a paradigm, this paper presented two models that integrate the potential interplay between sampling and integration/decision strategies into the sequential sampling framework.
 
@@
 
-Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that the way people sample the outcomes of prospects (sampling strategies) may be linked to the way they process the outcomes to evaluate the prospects and make a corresponding choice (decision strategies).
-Specifically, the authors assumed two potential links between what they considered paradigmatic instances of sampling and decision strategies:
-People either switch prospects after each sampled outcome (piecewise sampling) to compare single outcomes over repeated rounds (round-wise decisions), or they switch only once between prospects (comprehensive sampling) and make only one comparison between the means across all sampled outcomes (summary decisions).
+Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that the way people sample the outcomes of prospects (sampling strategy) may be linked to the way they process the outcomes in order to evaluate the prospects and make a corresponding choice (integration/decision strategy).
+Specifically, the authors assumed two potential links between what they considered paradigmatic instances of both types of strategies:
+People either switch prospects after each sampled outcome (piecewise sampling) to compare single outcomes over repeated rounds (round-wise integration/decision), or they switch only once between prospects (comprehensive sampling) and make one comparison between the means across all sampled outcomes (summary decision).
 The authors provided tentative empirical support for their claim by showing that a larger proportion of the choices of people who, on average, switched infrequently between prospects were better predicted by a summary strategy (rather than a round-wise strategy), and vice versa.
@@
 2.
-The sequential sampling framework was used as a modeling outlet to incorporate the idea of a potential interplay between sampling and decision strategies into formal models that offer a complete account of the decision-making process in the sampling paradigm and make theoretical commitments explicit.
+The sequential sampling framework was used as a modeling outlet to incorporate the potential interplay between sampling and decision strategies into formal models that offer a complete account of the decision-making process and make theoretical commitments explicit.
 
 3.
-Cumulative prospect theory was used to model simulated choice data, allowing to inquire whether the choices implied by the potential interplay between sampling and decision strategies may translate to characteristic signatures in CPT’s psychoeconomic value and weighting function.
+Cumulative prospect theory was used to model simulated choice data, allowing to inquire whether the choices implied by the potential interplay between both types of strategies may translate to characteristic signatures in CPT’s psychoeconomic value and weighting function.
 
@@
 
-Relying on the sequential sampling framework, the decision-making processes were modeled as evidence accumulation over time. 
-Two different models were presented ...
-
-In a computational analysis, the presented model was used to simulate how the proposed sampling and accumulation processes shape the final choice.
-Therefore, the switching probabilities and evidence thresholds were systematically varied, while simulating choices between a safe and a risky prospect.
-The model predicts the choices to vary systematically with the switching probability.
-Specifically, whereas the choice patterns correspond closely to the solutions of EV maximization for low switching probabilities, increases in the switching probability can lead to an increasingly pronounced as-if underweighting of rare outcomes pattern.
-This is because for high switching probabilities, each independent mean comparison is based on small samples, in which small-probability outcomes are underrepresented rather than overrepresented.
-As a consequence, then, small-probability outcomes are predicted to contribute to the accumulated evidence less rather than more than would be warranted by their objective probabilities.
-Accordingly, the analyses showed that the structure of the choice problem---i.e., whether a small-probability outcome is present and which value it takes---is an important moderator for the effect of sampling strategies on the choice pattern.
-Importantly, while this explanation emphasizes that the reliance on small samples is a strong contributor to the as-if underweighting of rare outcomes pattern in DFE, it has little to do with the common notion of sampling error [e.g., @foxDecisionsExperienceSampling2006; @hertwigDecisionsExperienceEffect2004].
-That is, the as-if underweighting of rare outcomes is not caused by a deviation of the sampled relative frequencies from the objective probabilities, but by the way the sampled outcomes are integrated and processed to evaluate the prospects.
-The analyses made this clear by showing that an as-if underweighting of rare outcomes pattern occurred, even if the sampling error is controlled for.
-In sum, by explicitly modeling their link, the current computational analysis showed how the interplay of sampling and decision strategies can shape the final choice.
-
-The current paper further extended the analysis of @hillsInformationSearchDecisions2010 by showing that the effects of sampling and decision strategies on the final choice can translate to characteristic signatures in cumulative prospect theory's value and weighting function.
+This paper started from the computational problem the mind is trying to solve in the sampling paradigm, and the principle logic that governs its solution:
+In order to make systematic choices between prospects, the mind must assess true differences in their latent properties, and it can only do so by searching for evidence in information samples.
+Relying on the sequential sampling framework, the current paper assumed that this search process takes the form of an evidence accumulation over time, where outcomes are sampled until an evidence threshold is reached.
+Two different models were presented, each of which assumed an accumulation process that resembles a distinct decision strategy.
+The round-wise integration model assumed that the means across sets of sampled outcomes are repeatedly compared and a choice is made once the number of won comparisons reaches a threshold.
+The summary integration model assumed that all outcomes sampled from a prospect are integrated into the same cumulative sum and that a choice is made once the sum reaches a threshold.
+
+The current paper discussed and demonstrated in a computational analysis how sampling strategies may or may not alter the latent property for which each of the models accumulates evidence, and thus may or may not cause each model to produce systematically different choice patterns:
+Specifically, in the round-wise integration model, changes in the sampling strategy alter the degree to which evidence is accumulated for differences in either the expected values or in the probability to produce a higher outcome most of the time.
+If the prospect that produces the higher outcome most of the time does not also possess the higher expected value, changes in the sampling strategy come to imply systematically different choice patterns.
+The simulations showed that high switching probabilities led the round-wise integration model to produce systematic deviations from EV maximization that take the form of an as-if underweighting of rare outcomes, even if sampling error is controlled for.
+In contrast, in the summary integration model, changes in the sampling strategy do not cause  alter which latent property evidence is accumulated for, but rather
+
+Finally, it was shown how the effects of the potential interplay between sampling and integration/decision strategies on the final choice can translate to characteristic signatures in cumulative prospect theory's value and weighting function.
 Having controlled for sampling error, the estimated CPT parameters and the resulting shapes of the value and weighting function primarily reflected how sensitive the combinations of sampling and decision strategies are to particular changes in the outcomes and their probabilities.
@@
 
-### Why Sampling and Decision Strategies?
+## Why Particular Sampling and Decision Strategies Could Be Linked?
 

### 2022-05-26 manuscript.Rmd
Final version: Discussion and Edits (SE)

@@
         That is, the relative frequency with which an outcome occurs in a large sample is predicted to correspond to the objective probability of the outcome most of the time and is not predicted to be lower more often than higher or vice versa.
-        However, for small samples, the binomial distribution associated with a small-probability outcome is positive skewed, causing the relative frequency with which this outcome occurs in the sample to be smaller rather than larger than its objective probability.
+        However, for small samples, the binomial distribution associated with a small-probability outcome is positively skewed, causing the relative frequency with which this outcome occurs in the sample to be smaller rather than larger than its objective probability.
         That is, small-probability outcomes tend to be underrepresented in small samples.
@@
 
-Yet, peoples' reliance on a small number of sampled outcomes in DFE, and the associated sampling error, are presumably not the sole cause of the description-experience gap [see @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
+Yet, peoples' reliance on a small number of sampled outcomes in DFE, and the associated sampling error are presumably not the sole cause of the description-experience gap [see @hauDescriptionexperienceGapRisky2008; @ungemachAreProbabilitiesOverweighted2009; @wulffMetaanalyticReviewTwo2018, who show that the as-if underweighting of rare outcomes pattern may appear, even if the overall number of sampled outcomes is large and the relative frequencies closely resemble the latent objective probabilities].
 Rather, the specifics of the actual decision-making process---i.e, how the mind exercises the capacity of making decisions from experience as opposed to descriptions---might contribute to the gap.
@@
 Sampling strategies: Refer to the sequential pattern with which people sample the outcomes from both prospects over time.
-People may switch infrequently (comprehensive sampling) or frequently (piecewise sampling) or something in between.
+People may switch infrequently (comprehensive sampling) or frequently (piecewise sampling) or with a frequency somewhere in between.
 Decision strategies: Refer to the way people integrate the sampled outcomes in order to evaluate the prospects.
@@
 To summarize the preceding paragraphs: 
-Since small samples may distort the information about the properties of latent prospects, a great deal of research on the sampling paradigm has been invested into the question which factors affect how much people sample [see @wulffAdaptiveExplorationWhat2019, Table 7.2, for a recent summary of relevant factors and papers].
+Since small samples may distort the information about the properties of latent prospects, a great deal of research on the sampling paradigm has been invested into the question of which factors affect how much people sample [see @wulffAdaptiveExplorationWhat2019, Table 7.2, for a recent summary of relevant factors and papers].
 Assuming that people proceed systematically when sampling outcomes, and that their sampling strategies are systematically related to decision strategies, Hills and Hertwig [-@hillsInformationSearchDecisions2010] emphasize that in order to understand how people make DFE and how this comes to imply certain choice patterns, one might need a richer understanding of peoples' sampling behavior.
-That is, not only we need to know how much outcomes are sampled, but also in what way they are sampled, and how this affects the way the obtained information is processed to evaluate the latent prospects.
-
-While offering a novel, convincing inroad into the broader question how sampling and information-processing can act together to shape DFE in environments where people can sample without costs,^[<!--Open footnote-->
+That is, not only do we need to know how many outcomes are sampled, but also in what way they are sampled, and how this affects the way the obtained information is processed to evaluate the latent prospects.
+
+While offering a novel, convincing inroad into the broader question of how sampling and information-processing can act together to shape DFE in environments where people can sample without costs,^[<!--Open footnote-->
 Meaning that people do not gain/loose the amount of each sampled outcome. Of course, sampling implies other costs, such as time and cognitive capacities.
@@
 3. *Use of heuristic analysis methods:*
-The empirical re-analyses relies on various heuristic methods to assess whether the observed choices are consistent with the claimed links between sampling and decision strategies and their impact on the as-if weighting of rare events pattern.
+The empirical re-analysis relies on various heuristic methods to assess whether the observed choices are consistent with the claimed links between sampling and decision strategies and their impact on the as-if weighting of rare events pattern.
 For instance, aggregated data over participants and choice problems is used to compare, within and between sampling strategies, the proportions of choices that are consistent with the predictions of the decision strategies and an as-if underweighting of rare outcomes.
@@
 While acknowledging that existing data was used, such heuristic methods can be problematic, e.g., because they can cause a construct-behavior gap where inferences from the data to the tested theory, although statistically sound, become logically invalid.
-In a rigorous analysis, @regenwetterConstructbehaviorGapBehavioral2017 demonstrate how the use of aggregate data and heuristic scoring rules, e.g., counting the proportion of correct choice predictions across problems and people, lead at least to hard-to-interpret inferences about individuals' as-if weighting patterns and the description-experience gap.
+In a rigorous analysis, @regenwetterConstructbehaviorGapBehavioral2017 demonstrate how the use of aggregated data and heuristic scoring rules, e.g., counting the proportion of correct choice predictions across problems and people, lead at least to hard-to-interpret inferences about individuals' as-if weighting patterns and the description-experience gap.
 One can alleviate such risks by taking heterogeneity between individuals into account and modeling the as-if weighting more explicitly.
@@
 
-Because there is an uncountable number of decisions people confront in their daily life, behavioral decision research routinely abstracts from choices between particular alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
-Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.
+Because there is an uncountable number of decisions people confront in their daily life, behavioral decision research routinely abstracts from choices between particular alternatives, e.g., the choice between job offers, political parties to vote for, or investment plans.
+Rather, with the choice between at least two prospects, it studies a case which is counterfactual in that it omits the many particularities of each choice situation but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess.
 These fundamental properties are considered the $n$ possible outcomes of a choice alternative, denoted as $x_1, ..., x_n$, and the probabilities with which these outcomes occur following the choice of the alternative, denoted as $p_X(x_1), ..., p_X(x_n)$.
@@
 
-Rarely in peoples' daily life, the information provided about the prospects take the form of explicit and complete descriptions of all their outcome-probability pairs.
+Rarely in peoples' daily life, does the information provided about the prospects take the form of explicit and complete descriptions of all their outcome-probability pairs.
 In such rare cases, people would make DFD and can---strongly simplified---directly proceed by selecting a property or combinations thereof to assess differences among the prospects and make a respective choice.
@@
 Depending on the integration and evaluation mechanisms they assume, the member models of the sequential sampling framework have been shown to explain some of the robust deviations from EV maximization, including the as-if underweighting of rare outcomes in the sampling paradigm [@markantModelingChoiceSearch2015].
-Moreover, these models implement speed-accuracy trade-offs, with the amount of evidence that must be sampled in favor for a prospect increasing with thresholds, leading to more accurate but slower choices for high thresholds, and vice versa.
+Moreover, these models implement speed-accuracy trade-offs, with the amount of evidence that must be sampled in favor of a prospect increasing with thresholds, leading to more accurate but slower choices for high thresholds, and vice versa.
 
@@
 
-To implement the evidence accumulation process, the round-wise integration model assumes that each time after a *new* stochastic process was started and terminated on both prospects, their respective means are compared, with the prospect underlying the stochastic process with the greater mean receiving a round win.
+To implement the evidence accumulation process, the round-wise integration model assumes that each time a *new* stochastic process gets started and then terminated on both prospects, their respective means are compared, with the prospect underlying the stochastic process with the greater mean receiving a round win.
 Accordingly, assuming that $S^Y_m$ is the mean across $m$ outcomes successively sampled from prospect $P^Y$, this stage is modeled for the prospect $P^X$as the mapping
@@
 The model assumes that an agent starts with equal probability to sample outcomes from one of the prospects and continues sampling while switching between prospects according to the switching probability $\psi$.
-As in the round-wise integration model, the switching probability $\psi$ is assumed to be adopted prior the start of the sampling and accumulation process and is fixed throughout.
+As in the round-wise integration model, the switching probability $\psi$ is assumed to be adopted prior to the start of the sampling and accumulation process and is fixed throughout.
 
@@
 In addition, previous research has shown that differences as to how information about the properties of prospects is processed can translate to distinct signatures in CPT's psychoeconomic value and weighting function, without actually assuming that these functions are computed whatsoever [see @pachurHowTwainCan2017; @stewartDecisionSampling2006; @zilkerNonlinearProbabilityWeighting2021].^[<!--Open footnote-->
-Note that it has been argued that the distinction between CPT's functions used to describe choice data and models aiming to explain how this data is generated in first place are reminiscent of Marr's [-@marrVisionComputationalInvestigation1982] different levels of explanation [@zilkerMeasuringModelingConstruction2020; also cf.
+Note that it has been argued that the distinction between CPT's functions used to describe choice data and models aiming to explain how this data is generated in the first place are reminiscent of Marr's [-@marrVisionComputationalInvestigation1982] different levels of explanation [@zilkerMeasuringModelingConstruction2020; also cf.
 @griffithsProbabilisticModelsCognition2010].
@@
 Considering a *single* comparison round, the stochastic process for each prospect---which results in a mean computed across the outcomes sampled from the prospect---is predicted to terminate faster, the higher the probability that the subsequent outcome is sampled from the other prospect, i.e., the higher the switching probability $\psi$.
-Because the switching probability is predicted to alter the length of the stochastic processes underlying *each independent* mean comparison, it should affect whether low-probability outcomes contribute to each required mean comparisons about as much as would be warranted based on their objective probabilities, or whether they contribute rather less.
-That is, for high switching probabilities and thus, short stochastic processes, the binomial distribution associated with small-probability outcomes is positive skewed, causing the relative frequencies with which these outcomes occur within each comparison round to be smaller rather than larger than their latent objective probabilities.
+Because the switching probability is predicted to alter the length of the stochastic processes underlying *each independent* mean comparison, it should affect whether low-probability outcomes contribute to each required mean comparison about as much as would be warranted based on their objective probabilities, or whether they contribute rather less.
+That is, for high switching probabilities and thus, short stochastic processes, the binomial distribution associated with small-probability outcomes is positively skewed, causing the relative frequencies with which these outcomes occur within each comparison round to be smaller rather than larger than their latent objective probabilities.
 Because such a distortion of the relative sampled frequencies from the objective probabilities is expected for each comparison round, increases in the threshold $\theta$ should not affect the following expectations concerning the model behavior; rather because each comparison is independent and increases in sample size (here: number of comparisons) reduce random error, the expectations should be more accurately met for higher thresholds:
@@
 This is likely to be a negligible factor for large but not for small switching probabilities.
-Specifically, the temporal imbalances---i.e., the temporal advantage for the prospect which is first sampled from---grows as the switching probabilities decrease.
+Specifically, the temporal imbalances---i.e., the temporal advantage for the prospect which is sampled from first---grows as the switching probabilities decrease.
 Accordingly, for small switching probabilities, choices might be largely driven by the truly random event which prospect is first sampled from.
@@
 
-Before elaborating how the expectations outlined above may translate into estimates of the CPT parameters, the following section reviews how CPT in general and its weighting function in particular capture deviations from EV maximization.
+Before elaborating on how the expectations outlined above may translate into estimates of the CPT parameters, the following section reviews how CPT in general and its weighting function in particular capture deviations from EV maximization.
 
@@
 The exact procedure was as follows:
-For each of the 10,000 problems in the initial set, three outcomes were randomly drawn from a uniform distribution over the interval $[0, 20]$, with the smallest and highest of these three outcomes being assigned to the risky prospect to omit dominance.^[I.e., when one prospect always produces a higher outcome.]
+For each of the 10,000 problems in the initial set, three outcomes were randomly drawn from a uniform distribution over the interval $[0, 20]$, with the smallest and highest of these three outcomes being assigned to the risky prospect to omit dominance.^[<!--Open footnote-->I.e., where one prospect always produces a higher outcome.<!--Close footnote-->]
 The probability for the lower outcome of the risky prospect, $p_x(x_{low})$, was drawn from a uniform distribution over the interval $(0, 1)$, with the probability of the higher outcome being set to $p_x(x_{high}) = 1-p_x(x_{low})$.
 To obtain the 60 choice problems of the test set, the initial set was divided into three subsets, where each subset contained either all problems with $p_x(x_{high}) \in (0,.2)$ or $p_x(x_{high}) \in [.2,.8]$ or $p_x(x_{high}) \in (.8,1)$.
-From each of these subset, then, $20$ choice problems were randomly sampled.
+From each of these subsets, then, $20$ choice problems were randomly sampled.
 
@@
 Figure\ \@ref(fig:sample-sizes) displays the number of outcomes sampled over the course of a sampling and accumulation process for each combination of switching probabilities and thresholds.
-The model predicts a decrease in the overall number of sampled outcomes with increases in the switching probability, whereas the overall number of sampled outcomes is predicted to increase with thresholds at relatively constant rate.
+The model predicts a decrease in the overall number of sampled outcomes with increases in the switching probability, whereas the overall number of sampled outcomes is predicted to increase with thresholds at a relatively constant rate.
 These differences in the number of sampled outcomes are subtle indicators for how sampling strategies and the mechanisms of the round-wise integration model act together to imply different final choices.
@@
 That is, for high switching probabilities, the model is expected to choose the risky prospect, if the probability of its high-rank outcome is $> .5$.
-To account for the implied choice behavior, CPT might have to overweight high-rank outcomes with a probability far larger than .5 less severely than high-rank outcomes with a probability only little larger than .5.
+To account for the implied choice behavior, CPT might have to overweight high-rank outcomes with a probability far larger than .5 less severely than high-rank outcomes with a probability only a little larger than .5.
 Such a pattern is implied for $\delta > 1$.
-Aside this open issue, the estimates for the $\gamma$ and $\delta$ parameter show that the choices implied by the potential interplay of different sampling strategies and the round-wise integration/decision strategy can lead to distinct signatures in CPT's weighting function (see Figure\ \@ref(fig:function-forms), for the resulting graphs of the weighting function).
+Leaving this open issue, the estimates for the $\gamma$ and $\delta$ parameter show that the choices implied by the potential interplay of different sampling strategies and the round-wise integration/decision strategy can lead to distinct signatures in CPT's weighting function (see Figure\ \@ref(fig:function-forms), for the resulting graphs of the weighting function).
 Once again, these signatures cannot be due to sampling error.
@@
 Figure\ \@ref(fig:sensitivity-parameters) displays the estimated means and the 95%-intervals of the posterior distributions of the outcome sensitivity parameter $\alpha$ and the choice sensitivity parameter $\rho$.
-As expected, an increase in the switching probability leads to a decrease in $\alpha$, showing that the round-wise integration model largely ignores outcome information, if choices are based on ordinal comparisons of single outcomes rather than of means across larger sets of sampled outcomes.
+As expected, an increase in the switching probability leads to a decrease in $\alpha$, showing that the round-wise integration model largely ignores outcome information if choices are based on ordinal comparisons of single outcomes rather than of means across larger sets of sampled outcomes.
 In other words, for high switching probabilities, the round-wise integration model is expected to choose the prospect that produces the higher outcome most of the time.
@@
 The random choice behavior is indicated by false response rates around the value of .5 (see Fig.\ \@ref(fig:choice-rates-summary)) and low estimates for the choice sensitivity parameter $\rho$ (see Fig.\ \@ref(fig:sensitivity-parameters)).
-Because choices become more systematic with increasing switching probabilities, randomness is likely to be caused by the temporal advantage that one of the prospect gains by chance.
+Because choices become more systematic with increasing switching probabilities, randomness is likely to be caused by the temporal advantage that one of the prospects gains by chance.
 For high switching probabilities, choice rates and parameter estimates are roughly in line with the expectations formulated in Table\  \@ref(tab:expectations-summary).
@@
 Changes in the sampling strategy do not change the latent property for which evidence is accumulated in the summary integration model.
-Rather they affect whether approximately the same number of outcomes is sampled from both prospects or whether one of the prospects obtains, by chance, a temporal advantage, rendering decision either systematic or unsystematic, respectively.
+Rather, they affect whether approximately the same number of outcomes is sampled from both prospects or whether one of the prospects obtains, by chance, a temporal advantage, rendering the decision either systematic or unsystematic, respectively.
 
@@
 
-# Discussion
+# Discussion and Conclusion
 
@@
 In order to make systematic choices between prospects, the mind must assess true differences in their latent properties, and it can only do so by searching for evidence in information samples.
-Relying on the sequential sampling framework, the current paper assumed that this search process takes the form of an evidence accumulation over time, where outcomes are sampled until an evidence threshold is reached.
-Two different models were presented, each of which assumed an accumulation process that resembles a distinct decision strategy.
-The round-wise integration model assumed that the means across sets of sampled outcomes are repeatedly compared and a choice is made once the number of won comparisons reaches a threshold.
-The summary integration model assumed that all outcomes sampled from a prospect are integrated into the same cumulative sum and that a choice is made once the sum reaches a threshold.
+Relying on the sequential sampling framework, the current paper assumed that this search process takes the form of an evidence accumulation over time, where outcomes are sampled until the accumulated evidence reaches a threshold.
+Two different models were presented, each of which assumed an accumulation process that resembles a distinct integration/decision strategy.
+The round-wise integration model assumes that the means across sets of sampled outcomes are repeatedly compared and a choice is made once the number of won comparisons reaches a threshold.
+The summary integration model assumes that all outcomes sampled from a prospect are integrated into the same cumulative sum and that a choice is made once the sum reaches a threshold.
 
 The current paper discussed and demonstrated in a computational analysis how sampling strategies may or may not alter the latent property for which each of the models accumulates evidence, and thus may or may not cause each model to produce systematically different choice patterns:
-Specifically, in the round-wise integration model, changes in the sampling strategy alter the degree to which evidence is accumulated for differences in either the expected values or in the probability to produce a higher outcome most of the time.
-If the prospect that produces the higher outcome most of the time does not also possess the higher expected value, changes in the sampling strategy come to imply systematically different choice patterns.
-The simulations showed that high switching probabilities led the round-wise integration model to produce systematic deviations from EV maximization that take the form of an as-if underweighting of rare outcomes, even if sampling error is controlled for.
-In contrast, in the summary integration model, changes in the sampling strategy do not cause  alter which latent property evidence is accumulated for, but rather
-
-Finally, it was shown how the effects of the potential interplay between sampling and integration/decision strategies on the final choice can translate to characteristic signatures in cumulative prospect theory's value and weighting function.
-Having controlled for sampling error, the estimated CPT parameters and the resulting shapes of the value and weighting function primarily reflected how sensitive the combinations of sampling and decision strategies are to particular changes in the outcomes and their probabilities.
-Thereby, the analyses extends the notion that CPT can be used as a measurement tool to characterize information processing [@pachurHowTwainCan2017] from risky to uncertain choice.
-
-## Limitations and Outlook
-
-## Why Particular Sampling and Decision Strategies Could Be Linked?
-
-# Conclusion
+In the round-wise integration model, changes in the sampling strategy alter the degree to which evidence is accumulated for differences in either the expected values or in the probability to produce a higher outcome most of the time.
+Accordingly, the simulations showed that low switching probabilities lead the round-wise integration model to make choices in line with EV maximization, whereas high switching probabilities lead the model to produce systematic deviations from EV maximization taking the form of an as-if underweighting of rare outcomes, even if sampling error is controlled for.
+In contrast, in the summary integration model, evidence is, in principal, accumulated for differences in the latent EVs.
+Accordingly, the simulations showed that high switching probabilities lead the model to make choices in line with EV maximization. 
+However, low switching probabilities have been shown to introduce random temporal imbalances between the prospects regarding the amount of evidence that can be sampled, resulting in choices that are less sensitive to differences in the EVs but rather unsystematic.
+
+Finally, the current paper demonstrated how the effects of the potential interplay between sampling and integration/decision strategies on the final choice can translate to characteristic signatures in cumulative prospect theory's value and weighting function.
+Having controlled for sampling error, the estimated CPT parameters and the resulting function shapes primarily reflected how sensitive the different  combinations of sampling and integration/decision strategies are to particular changes in the outcomes and their probabilities.
+
+## Why Sampling and Decision Strategies and Why Particular Links?
+
+This concluding section intends to briefly draw attention to one particular limitation of the current paper and to what may be gained from overcoming it.
+Of course, this paper is purely theoretical, and the validity of its claims and simulations eventually depends on whether they stand the test of empirical data.
+Here, however, the concern is less about the current lack of an empirical test, but that more could have been done and should be done in future work to endow the idea of an interplay between sampling and integration/strategies with theoretical plausibility.
+
+In explaining cognitive capacities, such as decision making from experience, models thereof must be constrained to the extent that neither the computational resources of the human mind nor other relevant resources---e.g., time---are limitless [see, e.g., @jareckiFrameworkBuildingCognitive2020; @liederResourcerationalAnalysisUnderstanding2020; @vanrooijTheoryTestHow2021].
+Acknowledging these limitations, different theoretical frameworks can be used to narrow down the still abundant number of possible mechanisms the mind might employ in the decision-making process.
+Such frameworks build on different, sometimes related or complementary assumptions, e.g.:
+*ecological rationality* holds that the mind uses simple (decision) heuristics that exploit the information structures of the environment in which it operates [@payneAdaptiveStrategySelection1988; see also @simonRationalChoiceStructure1956];
+several sequential sampling models have been shown to implement optimal speed-accuracy trade-offs in that they make the most accurate choices for a given speed or the fastest for a given accuracy [@bogaczPhysicsOptimalDecision2006];
+and *resource rationality* assumes that the mind employs mechanisms that make optimal use of its actual resources in obtaining a specific goal [@liederResourcerationalAnalysisUnderstanding2020].
+
+The current paper dealt with these frameworks and their assumptions rather loosely and implicitly.
+A thorough and explicit treatment will help to move the idea of an interplay between sampling and integration/decision strategies beyond the "mere" consideration of its effects and endow it with greater theoretical plausibility, even before contact with data.
+That is, the question of why particular sampling and decision strategies might be employed and linked is not at all answered by the choices and weighting patterns they imply.
+Rather an answer is approached by showing how the idea of an interplay of both types of strategies can be integrated into the wider study of the computationally limited but adaptive mind.
 
@@
 # Acknowledgements
+
+\noindent
+I thank Thorsten Pachur and Veronika Zilker for the opportunity of an internship at the Center for Adaptive Rationality at the Max Planck Institute for Human Development in Berlin and for supervising this thesis.
 

### 2022-05-27 manuscript.Rmd
Submission version of manuscript

@@
     corresponding : yes
-    address       : "Institute of Psychology, Heidelberg University, Hauptstr. 47 – 51, 69117 Heidelberg"    
-    email         : "linus.hof@stud.uni-heidelberg.de"
+    email         : "linushof@posteo.de"
 
@@
  This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub` repository: https://github.com/linushof/sampling-in-dfe.
-The current version of the manuscript, created from the commit with the hash ``r repro::current_hash()``, is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
+The current version of the manuscript, created from the commit with the hash ``r repro::current_hash()``, is submitted as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
+Matr.-Nr.: Removed from online version.
 Supervisors:
@@
   \indent
-  1. Prof. Dr. Thorsten Pachur, Technical University of Munich
+  1. Prof. Dr. Thorsten Pachur, delegated by Prof. Dr. Klaus Fiedler
 
   \indent
-  2. Dr. Veronika Zilker, Max Planck Institute for Human Development
+  2. Dr. Veronika Zilker, delegated by Prof. Dr. Jan Rummel
 
@@
   In the sampling paradigm, people can---as much as they want, in the way they want, and without costs---sample the possible outcomes of prospects before making a final choice.
-Do the sequential pattern in which the outcomes are sampled (sampling strategy) and the way the sampled outcomes are integrated and processed to evaluate the prospects (integration/decision strategy) act together to shape the choice?
+Do the sequential pattern in which the outcomes are sampled (sampling strategy) and the way the sampled outcomes are integrated and processed to evaluate the prospects (decision strategy) act together to shape the choice?
 This paper presents two models that incorporate the potential interplay between both types of strategies into the sequential sampling framework.
-Each model assumes an evidence accumulation process representing a distinct integration/decision strategy and is used to simulate choices between a safe and a risky prospect, while systematically varying sampling strategies.
+Each model assumes an evidence accumulation process representing a distinct decision strategy and is used to simulate choices between a safe and a risky prospect, while systematically varying sampling strategies.
 The simulations show that the potential interplay between both types of strategies can lead to systematically different choice patterns and can contribute to the as-if underweighting of rare outcomes pattern in decisions from experience, irrespective of the existence or absence of sampling error.
@@
 bibliography      : references.bib
-appendix          : "manuscript_appendix.Rmd"
 csl               : "C:/Users/Linus Hof/Documents/Psychologie/ARC/sampling-in-dfe/apa.csl"
+appendix          : 
+  - "manuscript_appendix.Rmd"
 
@@
 Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that people may either switch just once between prospects (comprehensive sampling) or after each sampled outcome (piecewise sampling).^[<!--Open footnote-->
-Note that in their analyses of empirical sampling data,  Hills and Hertwig [-@hillsInformationSearchDecisions2010] used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and acknowledged that "many [sampling] strategies will fall on the continuum in between [the two paradigmatic strategies]" (p.
+Note that in their analysis of empirical sampling data,  Hills and Hertwig [-@hillsInformationSearchDecisions2010] used the number of switches between prospects relative to the overall number of sampled outcomes from both prospects (switching frequency) as an approximate measure for the two proposed sampling strategies, and acknowledged that "many [sampling] strategies will fall on the continuum in between [the two paradigmatic strategies]" (p.
 1788).
 <!--Close footnote-->]
-Decision strategies refer to the way people integrate the information obtained from the sampled outcomes in order to evaluate the prospects and make a corresponding decision.
-Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that people compare the prospects either on the basis of the means across all sampled outcomes (summary integration/decision) or they compare two sampled outcomes---i.e., one from each prospect---over repeated rounds and choose the prospect that won the majority of such comparisons (round-wise integration/decision).
+Decision strategies refer to the way people integrate the information obtained from the sampled outcomes in order to evaluate the prospects and make a corresponding choice.
+Hills and Hertwig [-@hillsInformationSearchDecisions2010] proposed that people compare the prospects either on the basis of the means across all sampled outcomes (summary decision) or they compare two sampled outcomes---i.e., one from each prospect---over repeated rounds and choose the prospect that won the majority of such comparisons (round-wise decision).
 In more general terms, whereas sampling strategies determine how the information about prospects are collected, decision strategies determine how the collected information are processed, or transformed, to arrive at a final choice.
@@
 Decision strategies: Refer to the way people integrate the sampled outcomes in order to evaluate the prospects.
-People may integrate all outcomes stemming from the same prospect in order to compute and compare summary scores (summary integration/decision); or they integrate and compare outcomes of the two prospects over repeated rounds (round-wise integration/decision).
+People may integrate all outcomes stemming from the same prospect in order to compute and compare summary scores (summary decision); or they integrate and compare outcomes of the two prospects over repeated rounds (round-wise decision).
 \end{figure}
 
-To provide an explanation for the as-if underweighting of rare outcomes pattern and the related description-experience gap, Hills and Hertwig [-@hillsInformationSearchDecisions2010] suggested a systematic link between sampling and decision strategies.
+To provide an explanation for the as-if underweighting of rare outcomes pattern and the related description-experience gap, Hills and Hertwig [-@hillsInformationSearchDecisions2010] suggested a systematic link between both types of strategies.
 Specifically, they assumed that comprehensive sampling is associated with making summary decisions, while piecewise sampling is associated with making round-wise decisions.
@@
 In the section that follows, two models are specified, each of which integrates the continuum of sampling strategies and one of the proposed decision strategies into the computational framework of sequential sampling models.
-The expected behavior of the models are outlined.
+The expected behaviors of the models are outlined.
 Thereafter, a simulation study is presented, where the proposed models are used to simulate the sampling and accumulation processes for a set of choices between a safe and a two-outcome prospect, the latter of which may or may not possess a small-probability outcome of different rank/desirability.
@@
 <!--Close footnote-->]
-It is shown that within a sequential sampling framework, the interplay of sampling and integration/decision strategies produces systematically different choice patterns that depend on the structure of the choice problems and translate to distinct signatures in CPT's weighting and value function.
+It is shown that within a sequential sampling framework, the interplay of sampling and decision strategies produces systematically different choice patterns that depend on the structure of the choice problems and translate to distinct signatures in CPT's weighting and value function.
 The simulated choices and estimated CPT parameters can be understood as model-implied data and data models, which remain to be tested against empirical data.
@@
 \raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), stars and points represent the rate of choices that did not maximize the latent EV (gray) or the mean across all outcomes sampled over the course of a sampling and accumulation process (green, false response rates).
-Stars: Rates of choice trials, where risky prospect was chosen, although safe prospect produced the greater mean (false risky response).
-Points: Rates of trials, where safe prospect was chosen, although risky prospect produced the greater mean (false safe response).
+Stars: Rates of choice trials, where the risky prospect was chosen, although the safe prospect produced the greater mean (false risky response).
+Points: Rates of trials, where the safe prospect was chosen, although the risky prospect produced the greater mean (false safe response).
 \(p_{high} \in (.8, 1)\): Rates for all choice problems that include a small-probability outcome of low rank.
@@
 \includegraphics{manuscript_files/figure-latex/weighting-parameters-1} \label{fig:weighting-parameters}
-\raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), points represent the means of the posteriors distributions.
+\raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), points represent the means of the posterior distributions.
 Error bars represent the 95\%-intervals of the posterior distributions.
@@
 \includegraphics{manuscript_files/figure-latex/sensitivity-parameters-1} \label{fig:sensitivity-parameters}
-\raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), points represent the means of the posteriors distributions.
+\raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), points represent the means of the posterior distributions.
 Error bars represent the 95\%-intervals of the posterior distributions.
@@
 \raggedright \textit{Note.} For each combination of the switching probability \(\psi\) and the threshold \(\theta\), stars and points represent the rate of choices that did not maximize the latent EV (gray) or the mean across all outcomes sampled over the course of a sampling and accumulation process (blue, false response rates).
-Stars: Rates of choice trials, where risky prospect was chosen, although safe prospect produced the greater mean (false risky response).
-Points: Rates of trials, where safe prospect was chosen, although risky prospect produced the greater mean (false safe response).
+Stars: Rates of choice trials, where the risky prospect was chosen, although the safe prospect produced the greater mean (false risky response).
+Points: Rates of trials, where the safe prospect was chosen, although the risky prospect produced the greater mean (false safe response).
 \(p_{high} \in (.8, 1)\): Rates for all choice problems that include a small-probability outcome of low rank.
@@
 Relying on the sequential sampling framework, the current paper assumed that this search process takes the form of an evidence accumulation over time, where outcomes are sampled until the accumulated evidence reaches a threshold.
-Two different models were presented, each of which assumed an accumulation process that resembles a distinct integration/decision strategy.
+Two different models were presented, each of which assumes an accumulation process that resembles a distinct integration/decision strategy.
 The round-wise integration model assumes that the means across sets of sampled outcomes are repeatedly compared and a choice is made once the number of won comparisons reaches a threshold.

### 2022-05-27 manuscript_appendix.Rmd
Submission version of manuscript

@@
 \end{figure}
+
+\newpage
+
+\noindent \begin{center} \textbf{Declaration of Independent Work}  \end{center}
+
+\noindent I hereby declare that I completed the master’s thesis independently based only on the stated resources and references.
+I have not submitted the master’s thesis, or parts of it, to another academic institution and the thesis has not been accepted or rejected accordingly.
+I declare that I have acknowledged the regulations for the master’s program in Psychology of the Faculty of Behavioural and Cultural Studies of Heidelberg University of June 22, 2010 and its First Amendment of June 5, 2019.
+Furthermore, I declare that the principles of Heidelberg University for ensuring good academic practice were abided by.
+
+\noindent \begin{center} \textbf{Eigenständigkeitserklärung}  \end{center}
+
+\noindent \textit{Hiermit erkläre ich, die Masterarbeit selbstständig und nur unter Verwendung der angegebenen Hilfen und Quellen angefertigt zu haben.
+Ich erkläre, dass ich die Masterarbeit oder Teile davon nicht bereits bei einer anderen wissenschaftlichen Einrichtung eingereicht habe und dass sie dort weder angenommen noch abgelehnt wurde.
+Ich erkläre die Kenntnisnahme der fachspezifischen Prüfungsordnung für das Masterstudium im Fach Psychologie an der Fakultät für Verhaltens- und Empirische Kulturwissenschaften an der Universität Heidelberg vom 22.
+Juni 2010 und ihrer letzten Änderung vom 05.
+Juni 2019.
+Ich erkläre abschließend, dass die Grundsätze der Universität Heidelberg zur Sicherung guter wissenschaftlicher Praxis eingehalten wurden.}
+
+\hfill \break
+
+\noindent Linus Hof
+
+\noindent Heidelberg, 27.05.2022

### 2022-05-27 manuscript.Rmd
Add word count

@@
 keywords          : "decisions from experience, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
-wordcount         : ""
+wordcount         : "12,450"
 

### 2022-05-27 manuscript.Rmd
Submitted version

--- 2022-05-27 manuscript.Rmd
@@
 authornote: |
- This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub` repository: https://github.com/linushof/sampling-in-dfe.
+ This manuscript is a dynamic document created from the materials provided on the `GitHub` repository: https://github.com/linushof/sampling-in-dfe.
 The current version of the manuscript, created from the commit with the hash ``r repro::current_hash()``, is submitted as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
@@
 keywords          : "decisions from experience, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
-wordcount         : ""
+wordcount         : "12,442"
 
@@
 The paper closes with a brief discussion and conclusion.
-Note that all materials---i.e., code and data---underlying this paper, including instructions on how to reproduce this manuscript, can be retrieved from the accompanying `GitHub` repository.
+Note that all materials---i.e., code and data---underlying this paper can be retrieved from the accompanying `GitHub` repository.
 

### 2022-05-27 manuscript.Rmd
Submitted version (master's thesis)

@@
 The current version of the manuscript, created from the commit with the hash ``r repro::current_hash()``, is submitted as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology.
-Matr.-Nr.: Removed from online version.
+Matr.-Nr.: Hidden in online version.
 Supervisors:
@@
 Do the sequential pattern in which the outcomes are sampled (sampling strategy) and the way the sampled outcomes are integrated and processed to evaluate the prospects (decision strategy) act together to shape the choice?
-This paper presents two models that incorporate the potential interplay between both types of strategies into the sequential sampling framework.
+This paper presents two models that incorporate the potential interplay between both types of strategies into the computational framework of sequential sampling models.
 Each model assumes an evidence accumulation process representing a distinct decision strategy and is used to simulate choices between a safe and a risky prospect, while systematically varying sampling strategies.
@@
 $$
-S^X_t = \frac{1}{t} \sum_{k = 1}^t X_k, \quad k,t \in \mathbb{N}
+S^X_t = \frac{1}{t} \sum_{k = 1}^t X_k, \quad k \in \mathbb{N}
 \; ,
@@
 $$
-D^X_v = \sum_{c = 1}^v Z^X_c, \quad c,v \in \mathbb{N}
+D^X_v = \sum_{c = 1}^v Z^X_c, \quad c \in \mathbb{N}
 \;.
@@
 $$
-D^X_t = \sum_{k = 1}^t X_k, \quad k,t \in \mathbb{N}
+D^X_t = \sum_{k = 1}^t X_k, \quad k \in \mathbb{N}
 \; ,
@@
 $$
-D^X_{t,m} = \sum_{k = 1}^t X_k - \sum_{j = 1}^m Y_j \quad k,t,j,m \in \mathbb{N}
+D^X_{t,m} = \sum_{k = 1}^t X_k - \sum_{j = 1}^m Y_j \quad k,j \in \mathbb{N}
 \; ,
